### 2018-06-20 ideas_functioning.Rmd
created markdown file to generate analysis

---
title: "Ideas_ntw_function"
author: "I. Bartomeus, A. Magrach"
date: "6/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

-------------------------------------
IDEAS
-------------------------------------

I'll start by 
  - showing the relationship between ntw structure (defined as? Niche complementariety?) and overall functioning (defined as mean rep success of plants?)
  - showing the relationship between node position and plant species functioning
  - showing the relationship between ntw structure and functioning maximization (eveness of fucntioning, well, not evenness, you want equity (that is, even and high))

We can use data on both visitation rates (quantity), pollen deposition (quality), its product (pollen delivered) and fruit set and seed set.

AINHOA: We could look at
1) how do perturbations (in this case fragmentation) affect species specialization? in this setting are specialization and 
link conservatism or opportunism (how regional interaction richness of a species differs from what could be expected if species interacted randomly with the available set of partners, see Carstensen et al 2017) constant through time? Carstensen et al also find that specialization is conserved from local to regional levels (correlation between specialization levels), is this the case in a fragmented setting? 
2) are these changes a consequence of turnover in species composition across fragments or interaction composition (rewiring)? or is it temporal turnover?
3) changes in node position in plants with perturbation. what are the consequences for functioning? seed set

-----------------------------------------
ABSTRACT
-----------------------------------------

-----------------------------------------
METHODS
-----------------------------------------

```{r}
setwd("C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun")

all_interactions
summary(all_interactions)

d<-all_interactions
str(d)

library(bipartite)

##1st create a bipartite matrix for each site and round and extract a set of metrics at the network level

sites <- unique(d$Site_ID)
rounds <- unique(d$Round)

out <- data.frame(Site_id = NA, Round = NA, #year= NA,
                  links_sps = NA, num_compartments = NA,NODF  = NA,
                  link_dens=NA, weigh_connectance=NA, Shannon=NA,
                  int_evenness=NA, Alatalo_int_evenness=NA, H2=NA, 
                  species.poll=NA, species.pl=NA, 
                  niche.overlap.poll=NA, niche.overlap.plant=NA,
                  functional.comp.poll=NA, functional.comp.plant=NA,
                  modularity=NA, z=NA)
webs <- list()
for(i in 1:length(sites)){
  temp <- subset(d, Site_ID == sites[i])
  for(j in 1:length(rounds)){
    temp2 <- subset(temp, Round == rounds[j])

        web <- table(temp2$Plant_gen_sp, temp2$Pollinator_gen_sp)
        #p1<-plotweb(web)
        ntw <- networklevel(web)
        #para calcular modularity de la red
        mod<-try(computeModules(web), TRUE)
        #null model for modularity
        nulls <- try(nullmodel(web, N=100, method="r2d"), TRUE)
        modules.nulls <- try(sapply(nulls, computeModules), TRUE)
        like.nulls <- try(sapply(modules.nulls, function(x) x@likelihood), TRUE)
        z <- try((mod@likelihood - mean(like.nulls))/sd(like.nulls), TRUE)

        n <- nrow(out)
        webs[[n]] <- web

        out[n + 1,1] <- as.character(sites[i])
        out[n + 1,2] <- as.character(rounds[j])
        out[n + 1,3:17] <- c(ntw[3:4],ntw[9], ntw[12:13], ntw[15:20],
                             ntw[27:28], ntw[41:42])
        out[n + 1,18] <- try(mod@likelihood, TRUE)#esto sirve para pasar del error cuando no se puede computar la modularidad para una red
        out[n + 1,19] <- try(z, TRUE)
      }  
    }

##sacar la tabla con todas las metrics del network y añadirle el landscape_type
#primero hay que crear una columna con landscape_type y año jutnos porque el tipo
#de landscape varia en algunos años
#especie de iferror(vlookup)
str(out)
tablenetwork<-out[2:61,]

```

### 2018-06-20 ideas_functioning.Rmd
changes to network part of script

@@
 
+#############################################################################
+#####################NETWORK LEVEL METRICS ##############################
+#############################################################################
+
 sites <- unique(d$Site_ID)
@@
 
+str(out)
+head(out)
+out[2:30,]
+
 ##sacar la tabla con todas las metrics del network y añadirle el landscape_type
@@
 
+#############################################################################
+#####################SPECIES LEVEL NETWORK METRICS ##############################
+#############################################################################
+
+## super importante cargar primero igraph antes que network porque se sobrescriben partes de las librerias
+## y el script no funcionaria bien.
+
+require(igraph)
+require(network)
+require(sna)
+require(ggplot2)
+require(sna)
+require(ergm)
+require(bipartite)
+require(dplyr)
+require(reshape)
+require(wesanderson)
+
+sites <- unique(d$Site_ID)
+rounds <- unique(d$Round)
+
+out <- data.frame(Site_id = NA, Round = NA, #year= NA,
+                 links_sps = NA, num_compartments = NA,NODF  = NA,
+                link_dens=NA, weigh_connectance=NA, Shannon=NA,
+               int_evenness=NA, Alatalo_int_evenness=NA, H2=NA)
+
+outsp <- data.frame(Site_id = NA, Round = NA, #year= NA,
+                species=NA,  norm_degree = NA,strength= NA, nestedra= NA,weigh_betweeness  = NA, 
+                weigh_closeness=NA, d=NA, c=NA, z=NA, specificity=NA)
+webs <- list()
+for(i in 1:length(sites)){
+  temp <- subset(sp, Site_ID == sites[i])
+  for(j in 1:length(rounds)){
+    temp2 <- subset(temp, Round == rounds[j])
+
+        web <- table(temp2$Plant_gen_sp, temp2$Pollinator_gen_sp)
+        #p1<-plotweb(web)
+         spntw <- try(specieslevel(web), TRUE)
+         ntw<-try(networklevel(web), TRUE)
+         n <- nrow(out)
+          webs[[n]] <- web
+          mod<-try(computeModules(web), TRUE)
+          cz<-try(czvalues(mod, level="lower", weighted=TRUE), TRUE)
+          spec<-getspe(web)
+
+          n2 <- nrow(outsp)
+          out[n + 1,1] <- as.character(sites[l])
+          out[n + 1,2] <- as.character(rounds[j])
+          out[n + 1,3:11] <- c(ntw[3:4],ntw[9], ntw[12:13], ntw[15:18])
+
+        outsp[n2+seq(nrow(web)),1] <- as.character(sites[l])
+        outsp[n2+seq(nrow(web)),2] <- as.character(rounds[j])
+        outsp[n2+seq(nrow(web)),3] <- try(as.character(rownames(web)), TRUE)
+        outsp[n2+seq(nrow(web)),4:9] <- try(c(spntw$`lower level`[2:3], spntw$`lower level`[5],
+              spntw$`lower level`[12], spntw$`lower level`[14],
+              spntw$`lower level`[20]), TRUE)
+        outsp[n2+seq(nrow(web)),10:11] <- try(c(cz$c,
+                                              cz$z), TRUE)
+        outsp[n2+seq(nrow(web)),12] <- spec
+
+      }  
+    }
+
+str(outsp)
 ```

### 2018-08-20 ideas_functioning.Rmd
code for analyses

--- 2018-06-20 ideas_functioning.Rmd
@@
 date: "6/14/2018"
-output: html_document
+output:
+  pdf_document: default
+  html_document: default
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE)
 ```
@@
 
+NACHO
+-----
 I'll start by 
@@
 
-AINHOA: We could look at
+AINHOA OTHER IDEAS: We could look at
 1) how do perturbations (in this case fragmentation) affect species specialization? in this setting are specialization and 
@@
 
+Natural ecosystems across the globe are increasingly suffering from the pressures of on-going global change.
+Pollinators, in particular, have been reported to decline in abundance and diversity in different parts of the world, with potential implications for many plant species given the dependence of 87.5% of plant species on pollinators for reproduction.
+Although a strong body of research has focused on pollinator visitation frequency and plant reproduction, most of these efforts have been done at the individual species level, largely ignoring community-level implications.
+Indeed, interaction network structure can affect pollinator functional roles, their visitation patterns to different plant species and ultimately the pollination service they deliver to plants.
+Thus, a major knowledge gap at the moment is a mechanistic understanding of how pollinator visitation and the structure of plant-pollinator visitation networks affect plant reproduction.
+Here, we use 16 well-resolved plant-pollinator networks from Mediterranean shrub ecosystems to evaluate how pollinator species diversity, community composition and interaction network structure affect plant reproduction for 19 species of plants.
+Further, we link pollinator visitation frequencies with the efficiency of individual pollinator species.
+To this end, we use data on fruit and seed set for all plant species as well as data on the efficiency of a single visit by different pollinator species on 12 of these plant species.
+This work represents one of the first efforts linking pollination visitation and plant reproduction from a community-wide perspective using a well-replicated dataset.
+
 -----------------------------------------
@@
 
-```{r}
-setwd("C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun")
+1) How does network structure (nestedness, modularity etc.) link to ecosystem function?
+2) How does the location of a particular plant species within a particular network affect its reproductive success? Apparent competition with other plant species? Pollinator diversity visiting?
+3) Is pollination efficiency on reproductive success altered by different network structures?
+For example, increasing apparent competition between pollinators or overlap in niches affect reproductive success despite great efficiency?
 
-all_interactions
-summary(all_interactions)
+First, check sampling completeness
+
+```{r, include=TRUE}
+#First attempt to load the data, etc...
+
+#prepare stuff-----
+#If you don't have devtools install it
+#install.packages("devtools")
+#library(devtools)
+#Then install the data package. Reprot issues 
+#install_github("ibartomeus/BeeFunData", ref = "fun")
+library(BeeFunData)
+
+setwd("~/Dropbox/Beefun/Beefun/functioning")
+ #setwd("C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning")
 
 d<-all_interactions
-str(d)
+f<-fruitset
+s<-seedset
+si<-single_visits
 
-library(bipartite)
+si$Plant.sp<-paste(si$Plant_genus, si$Plant_species)
 
-##1st create a bipartite matrix for each site and round and extract a set of metrics at the network level
+#####################################################################################################################
+########################CALCULATE SAMPLING COMPLETENESS FOR POLLINATORS, PLANTS AND LINKS#############################
+######################################################################################################################
 
-sites <- unique(d$Site_ID)
-rounds <- unique(d$Round)
+#POLLINATORS
+d2<-table(d$Site_ID, d$Pollinator_gen_sp)
+d3<-as.data.frame.array(d2)
 
-out <- data.frame(Site_id = NA, Round = NA, #year= NA,
-                  links_sps = NA, num_compartments = NA,NODF  = NA,
-                  link_dens=NA, weigh_connectance=NA, Shannon=NA,
-                  int_evenness=NA, Alatalo_int_evenness=NA, H2=NA, 
-                  species.poll=NA, species.pl=NA, 
-                  niche.overlap.poll=NA, niche.overlap.plant=NA,
-                  functional.comp.poll=NA, functional.comp.plant=NA,
-                  modularity=NA, z=NA)
-webs <- list()
-for(i in 1:length(sites)){
-  temp <- subset(d, Site_ID == sites[i])
-  for(j in 1:length(rounds)){
-    temp2 <- subset(temp, Round == rounds[j])
+d4 <- t(d3[,1:277])
+#head(d4)
+#str(d4)
+d5<-as.data.frame(d4)
+#str(d5)
+d6<-as.list(d5)
 
-        web <- table(temp2$Plant_gen_sp, temp2$Pollinator_gen_sp)
-        #p1<-plotweb(web)
-        ntw <- networklevel(web)
-        #para calcular modularity de la red
-        mod<-try(computeModules(web), TRUE)
-        #null model for modularity
-        nulls <- try(nullmodel(web, N=100, method="r2d"), TRUE)
-        modules.nulls <- try(sapply(nulls, computeModules), TRUE)
-        like.nulls <- try(sapply(modules.nulls, function(x) x@likelihood), TRUE)
-        z <- try((mod@likelihood - mean(like.nulls))/sd(like.nulls), TRUE)
+library(iNEXT)
+library(ggplot2)
 
-        n <- nrow(out)
-        webs[[n]] <- web
+rar <- iNEXT(d6, q=0, datatype="abundance", endpoint = 400)
+poll<-ggiNEXT.iNEXT(rar, color.var="site", se=FALSE) + ylab("Richness of pollinators") + theme_bw() + theme (legend.position= "none")
+  # theme(text = element_text(size = 12),
+  #       axis.text=element_text(size=rel(1)),
+  #       axis.title=element_text(size=rel(1),face="bold"), legend.direction="horizontal", legend.text=element_text(size=10))
 
-        out[n + 1,1] <- as.character(sites[i])
-        out[n + 1,2] <- as.character(rounds[j])
-        out[n + 1,3:17] <- c(ntw[3:4],ntw[9], ntw[12:13], ntw[15:20],
-                             ntw[27:28], ntw[41:42])
-        out[n + 1,18] <- try(mod@likelihood, TRUE)#esto sirve para pasar del error cuando no se puede computar la modularidad para una red
-        out[n + 1,19] <- try(z, TRUE)
-      }  
+poll
+
+#per site sampling completeness for pollinators
+#Aznalcazar 64/103 = 0.62
+#Bonares  54.000/178.701 = 0.30
+#ConventodelaLuz  33.000/98.950 = 0.33
+#CotitodeSantaTeresa  54.000/190.442 = 0.28
+#Elpinar  29.000/158.657= 0.18
+#Elpozo  32.000/174.000= 0.18
+#Esparragal  39.000/110.859= 0.35
+#LaCunya  32.000/118.672= 0.27
+#LaRocina  74.000/147.129 = 0.50
+#Lasmulas  52.000/127.295 = 0.41
+#Niebla  57.000/124.792 = 0.46
+#PinaresdeHinojos 40.000/168.852 = 0.24
+#Pinodelcuervo  52.000/187.503 = 0.28
+#Urbanizaciones  40.000/109.136 = 0.37 
+#Villamanriqueeste  62.000/141.310 = 0.44
+#Villamanriquesur  48.000/111.326 = 0.43
+
+#(0.62 + 0.30 + 0.33 + 0.28 + 0.18 + 0.18 + 0.35 + 0.27 + 0.50 + 0.41 + 0.46 + 0.24 + 0.28 + 0.37 + 0.44 + 0.43)/16
+#TOTAL AVERAGE sampling completeness of pollinators 0.35
+
+#PLANTS
+d.pl<-table(d$Site_ID, d$Plant_gen_sp)
+d.pl2<-as.data.frame.array(d.pl)
+
+d.pl3 <- t(d.pl2[,1:57])
+#head(d.pl3)
+#str(d.pl3)
+d.pl4<-as.data.frame(d.pl3)
+#str(d.pl4)
+d.pl5<-as.list(d.pl4)
+
+library(iNEXT)
+library(ggplot2)
+
+rar2 <- iNEXT(d.pl5, q=0, datatype="abundance", endpoint = 200)
+plant<-ggiNEXT.iNEXT(rar2, color.var="site", se=FALSE) + ylab("Richness of plants") + 
+  theme_bw()  + theme (legend.position= "none")
+  # theme(text = element_text(size = 12),
+  #       axis.text=element_text(size=rel(1)),
+  #       axis.title=element_text(size=rel(1),face="bold"), legend.direction="horizontal", legend.text=element_text(size=10))
+
+plant
+
+#per site sampling completeness for pollinators
+#Aznalcazar 17.000/18.490 = 0.92
+#Bonares  13.000/13.990 = 0.93
+#ConventodelaLuz  12.000/13.978 = 0.86
+#CotitodeSantaTeresa  10.000/11.973 = 0.84
+#Elpinar  11.000/23.255 = 0.47
+#Elpozo  11.000 /13.219 = 0.83
+#Esparragal  12.000 /16.436 = 0.73
+#LaCunya  13.000/21.847 = 0.60
+#LaRocina  16.000 /21.959 = 0.73 
+#Lasmulas  12.000 /17.940 = 0.67
+#Niebla  21.000/21.743 = 0.97
+#PinaresdeHinojos 14.000/21.889 = 0.64
+#Pinodelcuervo  15.000/27.372 = 0.55
+#Urbanizaciones  10.000 /10.247 = 0.98
+#Villamanriqueeste  9.000 /10.983 = 0.82
+#Villamanriquesur  12.000 /12.989 = 0.92
+
+#(0.92 + 0.93 + 0.86 + 0.84 + 0.47 + 0.83 + 0.73 + 0.60 + 0.73 + 0.67 + 0.97 + 0.64 + 0.55 + 0.98 + 0.82 + 0.92)/16
+
+#TOTAL AVERAGE sampling completeness of plants 0.78
+
+#LINKS
+
+d$link<-paste(d$Plant_gen_sp, d$Pollinator_gen_sp)
+d.l<-table(d$Site_ID, d$link)
+d.l2<-as.data.frame.array(d.l)
+
+d.l3 <- t(d.l2[,1:750])
+#head(d.l3)
+#str(d.l3)
+d.l4<-as.data.frame(d.l3)
+#str(d.l4)
+d.l5<-as.list(d.l4)
+
+library(iNEXT)
+library(ggplot2)
+
+rar3 <- iNEXT(d.l5, q=0, datatype="abundance", endpoint = 500)
+link<-ggiNEXT.iNEXT(rar3, color.var="site", se=FALSE) + ylab("Richness of links") + theme_bw() +
+   theme (legend.position= "none")
+  # theme(text = element_text(size = 12),
+  #       axis.text=element_text(size=rel(1)),
+  #       axis.title=element_text(size=rel(1),face="bold"), legend.direction="horizontal", legend.text=element_text(size=10))
+
+link
+
+#per site sampling completeness for pollinators
+#Aznalcazar 101.000/244.145 = 0.41
+#Bonares  72.000/389.031 = 0.19
+#ConventodelaLuz  52.000/221.285 = 0.23
+#CotitodeSantaTeresa  64.000/478.893 = 0.13
+#Elpinar  37.000/194.026 = 0.19
+#Elpozo   46.000/159.994 = 0.29
+#Esparragal   52.000/196.900 = 0.26
+#LaCunya  44.000/115.025 = 0.38
+#LaRocina  98.000/351.931 = 0.28
+#Lasmulas  69.000/306.883 = 0.22
+#Niebla  84.000/611.776 = 0.14
+#PinaresdeHinojos  56.000/186.413 = 0.30
+#Pinodelcuervo   77.000/273.425 = 0.28
+#Urbanizaciones  55.000/204.100 = 0.27
+#Villamanriqueeste  76.000/193.208 = 0.39
+#Villamanriquesur  67.000/234.221 = 0.29
+
+#(0.41 + 0.19 + 0.23 + 0.13 + 0.19 + 0.29 + 0.26 + 0.38 + 0.28 + 0.22 + 0.14 + 0.30 + 0.28 + 0.27 + 0.39 + 0.29)/16
+
+#TOTAL AVERAGE sampling completeness of links 0.27
+
+```
+
+Sampling completeness for pollinators = 0.35
+                          plants= 0.78
+                          links= 0.27
+
+QUESTION 1:  - relationship between ntw structure defined as nestedness (i.e.
+redundancy) and complementarity (i.e.
+funct compl), also taking into species-level characteristics (e.g., degree and specialization) and relate it to overall functioning (defined as mean rep success of all plant species together per site)
+
+```{r, include=TRUE}
+
+#####################################################################################################################
+######################## NTW STRUCTURE ~ ECOSYSTEM FUNCTION #########################################################
+######################################################################################################################
+#calculate column with fruit set as
+
+#Fruit_Yes +  Fruit_Preyed + Fruit_Dispersed) / (Fruit_Yes + Fruit_No +Fruit_Preyed + Fruit_Dispersed) #Nacho this equation is wrong in your metadata!
+
+#1st eliminate frutos perdidos
+wordList <- c("fruto perdido","frutos perdidos")
+
+require(Hmisc)
+f2<-subset(f, Notes %nin% wordList)
+
+f2$tot.fruitset<-(f2$Fruit_Yes +  f2$Fruit_preyed + f2$Fruit_dispersed)/(f2$Fruit_Yes +f2$Fruit_No + f2$Fruit_preyed + f2$Fruit_dispersed)
+
+s2<-subset(s, Notes %nin% wordList)
+s2$tot.seedset
+
+###### read network and species level files (network analyses to be found at "...scripts/network analysis.R")
+
+outsp.pl.site<-read.csv("SITE_plant_species_level_metrics.csv")
+outsp.site<-read.csv("SITE_species_level_metrics.csv")
+out.site<-read.csv("SITE_network_level_metrics.csv")
+
+#-------------------------------------------------------------------------------------------
+#     QUESTION 1:  - relationship between ntw structure defined as nestedness (i.e.
+redundancy) and complementarity (i.e.
+funct compl), also taking into species-level characteristics (e.g., degree and specialization) and relate it to overall functioning (defined as mean rep success of all plant species together per site)
+
+#join plant species level network metrics with fruit and seed set for each site
+
+#FRUIT SET
+
+#1st calculate average fruit set for all plants per site
+
+library(plyr)
+
+f2$Plant.sp<-paste(f2$Plant_genus, f2$Plant_species)
+
+f.agg <- ddply(f2, c("Site_ID", "Plant.sp"), summarise,
+                         mean.fruitset    = mean(tot.fruitset),
+                         sd.fruitset = sd(tot.fruitset))
+
+#f.agg
+
+f.agg$nodf.corr<-out.site$nodf.corr[match(f.agg$Site_ID, out.site$Site_id)]
+f.agg$int_evenness<-out.site$int_evenness[match(f.agg$Site_ID, out.site$Site_id)]
+f.agg$h2.corr<-out.site$h2.corr[match(f.agg$Site_ID, out.site$Site_id)]
+f.agg$functional.comp.poll<-out.site$functional.comp.poll[match(f.agg$Site_ID, out.site$Site_id)]
+f.agg$niche.overlap.plant<-out.site$niche.overlap.plant[match(f.agg$Site_ID, out.site$Site_id)]
+f.agg$modularity<-out.site$modularity[match(f.agg$Site_ID, out.site$Site_id)]
+
+#also match with plant species level network data
+f.agg$match<-paste(f.agg$Site_ID, f.agg$Plant.sp)
+outsp.pl.site$match<-paste(outsp.pl.site$Site_id, outsp.pl.site$species)
+
+f.agg$norm_degree<-outsp.pl.site$norm_degree[match(f.agg$match, outsp.pl.site$match)]
+f.agg$strength<-outsp.pl.site$strength[match(f.agg$match, outsp.pl.site$match)]
+f.agg$nestedra<-outsp.pl.site$nestedra[match(f.agg$match, outsp.pl.site$match)]
+f.agg$weigh_betweeness<-outsp.pl.site$weigh_betweeness[match(f.agg$match, outsp.pl.site$match)]
+f.agg$weigh_closeness<-outsp.pl.site$weigh_closeness[match(f.agg$match, outsp.pl.site$match)]
+f.agg$d<-outsp.pl.site$d[match(f.agg$match, outsp.pl.site$match)]
+f.agg$c<-outsp.pl.site$c[match(f.agg$match, outsp.pl.site$match)]
+f.agg$z<-outsp.pl.site$z[match(f.agg$match, outsp.pl.site$match)]
+
+#check for structure of data
+#hist(f.agg$mean.fruitset)
+
+f.agg2<-na.omit(f.agg)
+cor(f.agg2[,c(5:10, 12:19)])
+
+library(glmmTMB)
+library(DHARMa)
+
+m1<-glmmTMB(mean.fruitset ~ nodf.corr +  functional.comp.poll + int_evenness + norm_degree + d  +  (1|Plant.sp), family="gaussian", data=f.agg2)
+summary(m1)
+
+#test for problems in residuals
+res<-simulateResiduals(m1)
+plot(res, rank = TRUE)
+
+#plot nodf only significant variable, with different colors for plant species and all together
+
+pl1<-ggplot(f.agg2,  aes(x=nodf.corr, y=mean.fruitset, color=Plant.sp))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Nestedness") +      
+        ylab("Mean fruitset") + theme_bw() + 
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
+
+pl1
+
+#SEED NUMBER
+
+#1st calculate average seed number for all plants per site
+
+s<-s[,-10]
+
+library(plyr)
+
+s$Plant.sp<-paste(s$Plant_genus, s$Plant_species)
+
+s.agg <- ddply(s, c("Site_ID", "Plant.sp"), summarise,
+                         mean.seednumber    = mean(Seeds2),
+                        # sd.seednumber = sd(Seeds2),
+                         mean.seedweight = mean(Seed.weight),
+                        # sd.seedweight = sd(Seed.weight),
+                         mean.fruitweight = mean(Fruit.weight2)#,
+                         #sd.fruitweight = sd(Fruit.weight2)
+                         )
+
+#s.agg
+
+s.agg$nodf.corr<-out.site$nodf.corr[match(s.agg$Site_ID, out.site$Site_id)]
+s.agg$int_evenness<-out.site$int_evenness[match(s.agg$Site_ID, out.site$Site_id)]
+s.agg$h2.corr<-out.site$h2.corr[match(s.agg$Site_ID, out.site$Site_id)]
+s.agg$functional.comp.poll<-out.site$functional.comp.poll[match(s.agg$Site_ID, out.site$Site_id)]
+s.agg$niche.overlap.plant<-out.site$niche.overlap.plant[match(s.agg$Site_ID, out.site$Site_id)]
+s.agg$modularity<-out.site$modularity[match(s.agg$Site_ID, out.site$Site_id)]
+
+#also match with plant species level network data
+s.agg$match<-paste(s.agg$Site_ID, s.agg$Plant.sp)
+outsp.pl.site$match<-paste(outsp.pl.site$Site_id, outsp.pl.site$species)
+
+s.agg$norm_degree<-outsp.pl.site$norm_degree[match(s.agg$match, outsp.pl.site$match)]
+s.agg$strength<-outsp.pl.site$strength[match(s.agg$match, outsp.pl.site$match)]
+s.agg$nestedra<-outsp.pl.site$nestedra[match(s.agg$match, outsp.pl.site$match)]
+s.agg$weigh_betweeness<-outsp.pl.site$weigh_betweeness[match(s.agg$match, outsp.pl.site$match)]
+s.agg$weigh_closeness<-outsp.pl.site$weigh_closeness[match(s.agg$match, outsp.pl.site$match)]
+s.agg$d<-outsp.pl.site$d[match(s.agg$match, outsp.pl.site$match)]
+s.agg$c<-outsp.pl.site$c[match(s.agg$match, outsp.pl.site$match)]
+s.agg$z<-outsp.pl.site$z[match(s.agg$match, outsp.pl.site$match)]
+
+#check for structure of data
+#hist(s.agg$mean.seednumber)
+
+library(glmmTMB)
+library(DHARMa)
+
+m2<-glmmTMB(mean.seednumber ~ nodf.corr +  functional.comp.poll + int_evenness + norm_degree + d  +  (1|Plant.sp), family="poisson", data=s.agg)
+summary(m2)
+
+#test for problems in residuals
+res<-simulateResiduals(m2)
+plot(res, rank = TRUE)
+
+#plot nodf only significant variable, with different colors for plant species and all together
+
+pl2<-ggplot(s.agg,  aes(x=functional.comp.poll, y=mean.seednumber, color=Plant.sp))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Functional complementarity") +      
+        ylab("Mean seed number") + theme_bw() + 
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
+
+pl2
+
+pl3<-ggplot(s.agg,  aes(x=int_evenness, y=mean.seednumber, color=Plant.sp))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Interaction evenness") +      
+        ylab("Mean seed number") + theme_bw() + 
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
+
+pl3
+
+pl4<-ggplot(s.agg,  aes(x=norm_degree, y=mean.seednumber, color=Plant.sp))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Normalized degree") +      
+        ylab("Mean seed number") + theme_bw() + 
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
+
+pl4
+
+#it seems all effects are driven by Cistus ladanifer, re-analyse without this species
+
+s.agg2<-subset(s.agg, s.agg$Plant.sp!="Cistus ladanifer")
+
+library(glmmTMB)
+library(DHARMa)
+
+m2b<-glmmTMB(mean.seednumber ~ nodf.corr +  functional.comp.poll + int_evenness + norm_degree + d  +  (1|Plant.sp), family="poisson", data=s.agg2)
+summary(m2b)
+
+pl5<-ggplot(s.agg2,  aes(x=int_evenness, y=mean.seednumber, color=Plant.sp))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Interaction evenness") +      
+        ylab("Mean seed number") + theme_bw() + 
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
+
+pl5
+
+pl6<-ggplot(s.agg2,  aes(x=nodf.corr, y=mean.seednumber, color=Plant.sp))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Nestedness") +      
+        ylab("Mean seed number") + theme_bw() + 
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
+
+pl6
+
+#driven only by C. salvifolius?
+
+s.agg3<-subset(s.agg2, s.agg2$Plant.sp!="Cistus salvifolius")
+
+library(glmmTMB)
+library(DHARMa)
+
+m2c<-glmmTMB(mean.seednumber ~ nodf.corr +  functional.comp.poll + int_evenness + norm_degree + d  +  (1|Plant.sp), family="poisson", data=s.agg3)
+summary(m2c)
+
+pl7<-ggplot(s.agg3,  aes(x=nodf.corr, y=mean.seednumber, color=Plant.sp))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Nestedness") +      
+        ylab("Mean seed number") + theme_bw() + 
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
+
+pl7
+
+#SEED WEIGHT
+
+#check for structure of data
+#hist(s.agg$mean.seedweight)
+
+library(glmmTMB)
+library(DHARMa)
+
+m3<-glmmTMB(mean.seedweight ~ nodf.corr +  functional.comp.poll + int_evenness + norm_degree + d  +  (1|Plant.sp), family="poisson", data=s.agg)
+summary(m3)
+
+#test for problems in residuals
+res<-simulateResiduals(m3)
+plot(res, rank = TRUE)
+
+#FRUIT WEIGHT
+
+#check for structure of data
+#hist(s.agg$mean.fruitweight)
+
+library(glmmTMB)
+library(DHARMa)
+
+m4<-glmmTMB(mean.fruitweight ~ nodf.corr +  functional.comp.poll + int_evenness + norm_degree + d  +  (1|Plant.sp), family="nbinom2", data=s.agg)
+summary(m4)
+
+#model convergence problem, check fixed effects for extreme values
+
+fixef(m4)
+
+#int_evenn has a very large value, try removing 
+m4b<-glmmTMB(mean.fruitweight ~ nodf.corr +  functional.comp.poll +  norm_degree + d  +  (1|Plant.sp), family="poisson", data=s.agg)
+summary(m4b)
+
+#test for problems in residuals
+res<-simulateResiduals(m4b)
+plot(res, rank = TRUE)
+
+```
+
+#RELATIONSHIP BETWEEN NODE POSITION AND FUNCTIONING
+
+#look at cz plots to see potential connector, hub etc species
+
+```{r, include=TRUE}
+
+czplot<- ggplot(s.agg,  aes(x=c, y=z)) +
+    geom_point(size=4.5, position="jitter", aes(color = factor(Plant.sp)))+
+    #geom_jitter()+
+    geom_vline(xintercept=0.62)+
+    geom_hline(yintercept=2.5)+
+    xlim(0,1)+
+    ylim(0,4)+
+    xlab("Between-module connectivity (c)") +
+    ylab("Within-module degree (z)")  +theme_bw() +
+    theme(axis.text=element_text(size=20),
+          axis.title=element_text(size=20,face="bold"))
+
+czplot
+
+m5<-glmmTMB(mean.fruitset ~ c + z +  (1|Plant.sp), family="gaussian", data=f.agg)
+summary(m5)
+
+#test for problems in residuals
+res<-simulateResiduals(m5)
+plot(res, rank = TRUE)
+
+m6<-glmmTMB(mean.seednumber ~ c + z   + (1|Plant.sp), family="gaussian", data=s.agg)
+summary(m6)
+
+m7<-glmmTMB(mean.seedweight ~ c + z   + (1|Plant.sp), family="gaussian", data=s.agg)
+summary(m7)
+
+m8<-glmmTMB(mean.fruitweight ~ c + z   + (1|Plant.sp), family="gaussian", data=s.agg)
+summary(m8)
+
+m8.c<- ggplot(s.agg,  aes(x=c, y=mean.fruitweight, color=Plant.sp))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("c") +      
+        ylab("Mean fruit weight") + theme_bw() + 
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
+
+m8.c
+
+m8b<-glmmTMB(mean.fruitweight ~ c + z   + (1|Plant.sp), family="gaussian", data=s.agg2)
+summary(m8b)
+
+m8.cbis<- ggplot(s.agg2,  aes(x=c, y=mean.fruitweight, color=Plant.sp))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("c") +      
+        ylab("Mean fruit weight") + theme_bw() + 
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
+
+m8.cbis
+```
+
+#LOOK AT EVENNESSS IN FUNCTION.
+within a site most plant species have very low reproductive success and thus we get incredibly high evenness values.
+therefore we use thresholds, for each sps and site we calculate the # of individuals that are above 50% in fruit production
+
+```{r, include=TRUE}
+library(vegan)
+library(dplyr)
+
+f2$Plant.sp<-paste(f2$Plant_genus, f2$Plant_species)
+f3<-f2[,c(1,13:14)]
+
+f4 <- ddply(f3, c("Site_ID", "Plant.sp"), summarise,
+                         mean.fruitset    = mean(tot.fruitset))
+
+#f4
+
+fr.max<-aggregate(.~ Plant.sp, f4, FUN=max)
+
+f4$fruit.max<-fr.max$mean.fruitset[match(f4$Plant.sp, fr.max$Plant.sp)]
+
+f4$fruit.prop<-f4$mean.fruitset/f4$fruit.max
+f5<-subset(f4, f4$fruit.prop>0.5)
+
+#for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
+f6<-f5 %>% 
+  group_by(Site_ID) %>%
+  summarise(no_rows = length(Site_ID ))
+
+#join this with fruitset data used previously
+
+f6$nodf.corr<-out.site$nodf.corr[match(f6$Site_ID, out.site$Site_id)]
+f6$int_evenness<-out.site$int_evenness[match(f6$Site_ID, out.site$Site_id)]
+f6$h2.corr<-out.site$h2.corr[match(f6$Site_ID, out.site$Site_id)]
+f6$functional.comp.poll<-out.site$functional.comp.poll[match(f6$Site_ID, out.site$Site_id)]
+f6$niche.overlap.plant<-out.site$niche.overlap.plant[match(f6$Site_ID, out.site$Site_id)]
+f6$modularity<-out.site$modularity[match(f6$Site_ID, out.site$Site_id)]
+
+library(glmmTMB)
+library(DHARMa)
+
+m.th<-glmmTMB(no_rows ~ nodf.corr +  functional.comp.poll + int_evenness , family="gaussian", data=f6)
+summary(m.th)
+
+#test for problems in residuals
+res<-simulateResiduals(m.th)
+plot(res, rank = TRUE)
+
+#plot nodf only significant variable, with different colors for plant species and all together
+
+pl.th<-ggplot(f6,  aes(x=nodf.corr, y=no_rows))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        xlab("Nestedness") +      
+        ylab("Evenness in fruitset") + theme_bw() + 
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
+
+pl.th
+
+pl.th2<-ggplot(f6,  aes(x=functional.comp.poll, y=no_rows))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        xlab("Functional complementarity") +      
+        ylab("Evenness in fruitset") + theme_bw() + 
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
+
+pl.th2
+
+```
+
+#look at single visit data for some species to see whether they can be related to network roles or repr success
+#importante
+
+#Control = siempre embolsados
+#Open = embolsados la noche antes, y open durante 6 horas de dia (o sea visitado por lo que sea que pasara durante el dia).
+
+```{r, include=TRUE}
+
+# si.cs<-subset(si, si$Plant.sp=="Cistus  salvifolius") 
+# si.cs
+# 
+# 
+# pl.si.cs<-ggplot(si.cs,  aes(x=Pollinator_genus, y=pollen_tubes))+  
+#   geom_bar(stat="identity")
+#         
+# pl.si.cs
+
+library(ggplot2)
+
+gg_color_hue <- function(n) {
+  hues = seq(15, 375, length=n+1)
+  hcl(h=hues, l=65, c=100)[1:n]
 }
 
-##sacar la tabla con todas las metrics del network y añadirle el landscape_type
-#primero hay que crear una columna con landscape_type y año jutnos porque el tipo
-#de landscape varia en algunos años
-#especie de iferror(vlookup)
-str(out)
-tablenetwork<-out[2:61,]
+mycols <- gg_color_hue(length(unique(si$Pollinator_genus)))
+names(mycols) <- unique(si$Pollinator_genus)
+mycols["Control"] <- "black"
+mycols["Open"] <- "grey"
+
+  pl.si<- ggplot(si,  aes(x=Pollinator_genus, y=pollen_tubes, fill=Pollinator_genus))+  
+    geom_bar(stat="identity")  + scale_fill_manual(values=mycols) + 
+    theme(text = element_text(size = 12),
+        axis.text=element_text(size=rel(1)),
+        axis.title=element_text(size=rel(1),face="bold"), legend.direction="horizontal", legend.text=element_text(size=10))
+
+  pl.si + facet_wrap( ~ Plant.sp, scales="free")
 
 ```
+
+El control tiene valores super altos, esta bien??

### 2018-08-20 scripts/network analysis.R

@@ -1,0 +1,176 @@
+
+#First attempt to load the data, etc...
+
+#prepare stuff-----
+#If you don't have devtools install it
+#install.packages("devtools")
+library(devtools)
+#Then install the data package. Reprot issues 
+install_github("ibartomeus/BeeFunData", ref = "fun")
+library(BeeFunData)
+
+#make the data available
+data(all_interactions)
+head(all_interactions)
+#See metadata
+?all_interactions
+data(sites)
+sites #lat longs
+#load plant functioning data
+data(fruitset)
+?fruitset
+head(fruitset)
+data(seedset)
+?seedset
+data(single_visits)
+?single_visits
+
+#analysis...----
+
+setwd("~/Dropbox/Beefun/Beefun/functioning")
+
+d<-all_interactions
+f<-fruitset
+s<-seedset
+si<-single_visits
+
+
+##1st create a bipartite matrix for each site MERGING ALL ROUNDS TOGETHER and extract a set of metrics at the network level
+
+#############################################################################
+#####################Network and SPECIES LEVEL NETWORK METRICS GLOBAL NETWORK PER SITE##############################
+#############################################################################
+
+## super importante cargar primero igraph antes que network porque se sobrescriben partes de las librerias
+## y el script no funcionaria bien.
+
+require(igraph)
+require(network)
+require(sna)
+require(ggplot2)
+require(sna)
+require(ergm)
+require(bipartite)
+require(dplyr)
+require(reshape)
+require(wesanderson)
+# require(ESM)
+
+
+sites <- unique(d$Site_ID)
+
+
+out.site <- data.frame(Site_id = NA, links_sps = NA, num_compartments = NA,weighted_NODF  = NA,
+                       link_dens=NA, weigh_connectance=NA, Shannon=NA,
+                       int_evenness=NA,  H2=NA, 
+                       species.poll=NA, species.pl=NA, 
+                       niche.overlap.poll=NA, niche.overlap.plant=NA, robustness.poll=NA, robustness.plant=NA,
+                       functional.comp.poll=NA, functional.comp.plant=NA,
[…]

### 2018-11-06 ideas_functioning.Rmd
changes

--- 2018-06-20 ideas_functioning.Rmd
@@
 ---
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
+---
+title: Impact of interaction network structure on community-level plant reproductive success 
+author: "Magrach, A & Bartomeus, I"
+date: "6 November 2018"
+output: html_document
+---
 
@@
 
-AINHOA: We could look at
+AINHOA OTHER IDEAS: We could look at in the future
 1) how do perturbations (in this case fragmentation) affect species specialization? in this setting are specialization and 
@@
 
+Natural ecosystems across the globe are increasingly suffering from the pressures of on-going global change.
+Pollinators, in particular, have been reported to decline in abundance and diversity in different parts of the world, with potential implications for many plant species given the dependence of 87.5% of plant species on pollinators for reproduction.
+Although a strong body of research has focused on pollinator visitation frequency and plant reproduction, most of these efforts have been done at the individual species level, largely ignoring community-level implications.
+Indeed, interaction network structure can affect pollinator functional roles, their visitation patterns to different plant species and ultimately the pollination service they deliver to plants.
+Thus, a major knowledge gap at the moment is a mechanistic understanding of how pollinator visitation and the structure of plant-pollinator visitation networks affect plant reproduction.
+Here, we use 16 well-resolved plant-pollinator networks from Mediterranean shrub ecosystems to evaluate how pollinator species diversity, community composition and interaction network structure affect plant reproduction for 19 species of plants.
+Further, we link pollinator visitation frequencies with the efficiency of individual pollinator species.
+To this end, we use data on fruit and seed set for all plant species as well as data on the efficiency of a single visit by different pollinator species on 12 of these plant species.
+This work represents one of the first efforts linking pollination visitation and plant reproduction from a community-wide perspective using a well-replicated dataset.
+
+-----------------------------------------
+QUESTIONS
+-----------------------------------------
+
+1) How does network structure, and in particular two aspects (nestedness and functional complementarity), that represent redundancy (and thus potentially resilience to species loss) and complementarity in niche (and thus potentially increased reproductive success through niche differentiation, specialization and increased pollen deposition of same species) link to ecosystem function (mean fruit and seed set) at the community level?
+
+2) How does the node position of a plant species within a network affect ecosystem functioning (here reproductive success)?
+Apparent competition with other plant species?
+Pollinator diversity visiting?
+
+3) How does network structure affect equity in functioning?
+
 -----------------------------------------
@@
 
-```{r}
-setwd("C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun")
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE)
+```
 
-all_interactions
-summary(all_interactions)
+First, check sampling completeness
+
+```{r, include=TRUE}
+#First attempt to load the data, etc...
+
+#prepare stuff-----
+#If you don't have devtools install it
+#install.packages("devtools")
+#library(devtools)
+#Then install the data package. Reprot issues 
+#install_github("ibartomeus/BeeFunData", ref = "fun")
+library(BeeFunData)
+
+#setwd("~/Dropbox/Beefun/Beefun/functioning")
+setwd("C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning")
 
 d<-all_interactions
-str(d)
+f<-fruitset
+s<-seedset
+si<-single_visits
 
-library(bipartite)
+si$Plant.sp<-paste(si$Plant_genus, si$Plant_species)
 
-##1st create a bipartite matrix for each site and round and extract a set of metrics at the network level
+#####################################################################################################################
+########################CALCULATE SAMPLING COMPLETENESS FOR POLLINATORS, PLANTS AND LINKS#############################
+######################################################################################################################
 
-sites <- unique(d$Site_ID)
-rounds <- unique(d$Round)
+#POLLINATORS
+d2<-table(d$Site_ID, d$Pollinator_gen_sp)
+d3<-as.data.frame.array(d2)
 
-out <- data.frame(Site_id = NA, Round = NA, #year= NA,
-                  links_sps = NA, num_compartments = NA,NODF  = NA,
-                  link_dens=NA, weigh_connectance=NA, Shannon=NA,
-                  int_evenness=NA, Alatalo_int_evenness=NA, H2=NA, 
-                  species.poll=NA, species.pl=NA, 
-                  niche.overlap.poll=NA, niche.overlap.plant=NA,
-                  functional.comp.poll=NA, functional.comp.plant=NA,
-                  modularity=NA, z=NA)
-webs <- list()
-for(i in 1:length(sites)){
-  temp <- subset(d, Site_ID == sites[i])
-  for(j in 1:length(rounds)){
-    temp2 <- subset(temp, Round == rounds[j])
+d4 <- t(d3[,1:277])
+#head(d4)
+#str(d4)
+d5<-as.data.frame(d4)
+#str(d5)
+d6<-as.list(d5)
 
-        web <- table(temp2$Plant_gen_sp, temp2$Pollinator_gen_sp)
-        #p1<-plotweb(web)
-        ntw <- networklevel(web)
-        #para calcular modularity de la red
-        mod<-try(computeModules(web), TRUE)
-        #null model for modularity
-        nulls <- try(nullmodel(web, N=100, method="r2d"), TRUE)
-        modules.nulls <- try(sapply(nulls, computeModules), TRUE)
-        like.nulls <- try(sapply(modules.nulls, function(x) x@likelihood), TRUE)
-        z <- try((mod@likelihood - mean(like.nulls))/sd(like.nulls), TRUE)
+library(iNEXT)
+library(ggplot2)
 
-        n <- nrow(out)
-        webs[[n]] <- web
+rar <- iNEXT(d6, q=0, datatype="abundance", endpoint = 400)
+poll<-ggiNEXT.iNEXT(rar, color.var="site", se=FALSE) + ylab("pollinators") + theme_bw() + 
+  theme (legend.position= "none") + theme(text = element_text(size = 15), axis.text=element_text(size=rel(1)),
+                                          axis.title.x = element_blank(),
+        axis.title=element_text(size=rel(1),face="bold"), legend.direction="horizontal", legend.text=element_text(size=10))
 
-        out[n + 1,1] <- as.character(sites[i])
-        out[n + 1,2] <- as.character(rounds[j])
-        out[n + 1,3:17] <- c(ntw[3:4],ntw[9], ntw[12:13], ntw[15:20],
-                             ntw[27:28], ntw[41:42])
-        out[n + 1,18] <- try(mod@likelihood, TRUE)#esto sirve para pasar del error cuando no se puede computar la modularidad para una red
-        out[n + 1,19] <- try(z, TRUE)
-      }  
+poll
+
+#per site sampling completeness for pollinators
+#Aznalcazar 64/103 = 0.62
+#Bonares  54.000/178.701 = 0.30
+#ConventodelaLuz  33.000/98.950 = 0.33
+#CotitodeSantaTeresa  54.000/190.442 = 0.28
+#Elpinar  29.000/158.657= 0.18
+#Elpozo  32.000/174.000= 0.18
+#Esparragal  39.000/110.859= 0.35
+#LaCunya  32.000/118.672= 0.27
+#LaRocina  74.000/147.129 = 0.50
+#Lasmulas  52.000/127.295 = 0.41
+#Niebla  57.000/124.792 = 0.46
+#PinaresdeHinojos 40.000/168.852 = 0.24
+#Pinodelcuervo  52.000/187.503 = 0.28
+#Urbanizaciones  40.000/109.136 = 0.37 
+#Villamanriqueeste  62.000/141.310 = 0.44
+#Villamanriquesur  48.000/111.326 = 0.43
+
+#(0.62 + 0.30 + 0.33 + 0.28 + 0.18 + 0.18 + 0.35 + 0.27 + 0.50 + 0.41 + 0.46 + 0.24 + 0.28 + 0.37 + 0.44 + 0.43)/16
+#TOTAL AVERAGE sampling completeness of pollinators 0.35
+
+#PLANTS
+d.pl<-table(d$Site_ID, d$Plant_gen_sp)
+d.pl2<-as.data.frame.array(d.pl)
+
+d.pl3 <- t(d.pl2[,1:57])
+#head(d.pl3)
+#str(d.pl3)
+d.pl4<-as.data.frame(d.pl3)
+#str(d.pl4)
+d.pl5<-as.list(d.pl4)
+
+library(iNEXT)
+library(ggplot2)
+
+rar2 <- iNEXT(d.pl5, q=0, datatype="abundance", endpoint = 200)
+plant<-ggiNEXT.iNEXT(rar2, color.var="site", se=FALSE) + ylab("plants") + 
+  theme_bw()  + theme (legend.position= "none") + theme(text = element_text(size = 15), axis.text=element_text(size=rel(1)),
+                                                         axis.title.x = element_blank(),
+        axis.title=element_text(size=rel(1),face="bold"), legend.direction="horizontal", legend.text=element_text(size=10))
+
+plant
+
+#per site sampling completeness for plants
+#Aznalcazar 17.000/18.490 = 0.92
+#Bonares  13.000/13.990 = 0.93
+#ConventodelaLuz  12.000/13.978 = 0.86
+#CotitodeSantaTeresa  10.000/11.973 = 0.84
+#Elpinar  11.000/23.255 = 0.47
+#Elpozo  11.000 /13.219 = 0.83
+#Esparragal  12.000 /16.436 = 0.73
+#LaCunya  13.000/21.847 = 0.60
+#LaRocina  16.000 /21.959 = 0.73 
+#Lasmulas  12.000 /17.940 = 0.67
+#Niebla  21.000/21.743 = 0.97
+#PinaresdeHinojos 14.000/21.889 = 0.64
+#Pinodelcuervo  15.000/27.372 = 0.55
+#Urbanizaciones  10.000 /10.247 = 0.98
+#Villamanriqueeste  9.000 /10.983 = 0.82
+#Villamanriquesur  12.000 /12.989 = 0.92
+
+#(0.92 + 0.93 + 0.86 + 0.84 + 0.47 + 0.83 + 0.73 + 0.60 + 0.73 + 0.67 + 0.97 + 0.64 + 0.55 + 0.98 + 0.82 + 0.92)/16
+
+#TOTAL AVERAGE sampling completeness of plants 0.78
+
+#LINKS
+
+d$link<-paste(d$Plant_gen_sp, d$Pollinator_gen_sp)
+d.l<-table(d$Site_ID, d$link)
+d.l2<-as.data.frame.array(d.l)
+
+d.l3 <- t(d.l2[,1:750])
+#head(d.l3)
+#str(d.l3)
+d.l4<-as.data.frame(d.l3)
+#str(d.l4)
+d.l5<-as.list(d.l4)
+
+library(iNEXT)
+library(ggplot2)
+
+rar3 <- iNEXT(d.l5, q=0, datatype="abundance", endpoint = 500)
+link<-ggiNEXT.iNEXT(rar3, color.var="site", se=FALSE) + ylab("links") + theme_bw() +
+   theme (legend.position= "none") + theme(text = element_text(size = 15), axis.text=element_text(size=rel(1)),
+        axis.title=element_text(size=rel(1),face="bold"), legend.direction="horizontal", legend.text=element_text(size=10))
+
+link
+
+#per site sampling completeness for links
+#Aznalcazar 101.000/244.145 = 0.41
+#Bonares  72.000/389.031 = 0.19
+#ConventodelaLuz  52.000/221.285 = 0.23
+#CotitodeSantaTeresa  64.000/478.893 = 0.13
+#Elpinar  37.000/194.026 = 0.19
+#Elpozo   46.000/159.994 = 0.29
+#Esparragal   52.000/196.900 = 0.26
+#LaCunya  44.000/115.025 = 0.38
+#LaRocina  98.000/351.931 = 0.28
+#Lasmulas  69.000/306.883 = 0.22
+#Niebla  84.000/611.776 = 0.14
+#PinaresdeHinojos  56.000/186.413 = 0.30
+#Pinodelcuervo   77.000/273.425 = 0.28
+#Urbanizaciones  55.000/204.100 = 0.27
+#Villamanriqueeste  76.000/193.208 = 0.39
+#Villamanriquesur  67.000/234.221 = 0.29
+
+#(0.41 + 0.19 + 0.23 + 0.13 + 0.19 + 0.29 + 0.26 + 0.38 + 0.28 + 0.22 + 0.14 + 0.30 + 0.28 + 0.27 + 0.39 + 0.29)/16
+
+#TOTAL AVERAGE sampling completeness of links 0.27
+
+library(ggplot2)
+library(grid)
+library(dplyr)
+
+grid.newpage()
+grid.draw(rbind(ggplotGrob(poll), ggplotGrob(plant), ggplotGrob(link), size = "last"))
+
+```
+
+Average sampling completeness for pollinators = 0.35, range 18-62%
+                          plants= 0.78, range 47-98%
+                          links= 0.27, range 13-41%
+
+------------------------------------------------------------------------------------------------------
+QUESTION 1:  - relationship between ntw structure defined as nestedness (i.e.
+redundancy) and complementarity (i.e.
+funct compl), also taking into species-level characteristics (e.g., degree and specialization) and relate it to overall functioning (defined as mean rep success of all plant species together per site)
+------------------------------------------------------------------------------------------------------
+
+```{r, include=TRUE}
+
+#####################################################################################################################
+######################## NTW STRUCTURE ~ ECOSYSTEM FUNCTION #########################################################
+######################################################################################################################
+#calculate column with fruit set as
+
+#Fruit_Yes +  Fruit_Preyed + Fruit_Dispersed) / (Fruit_Yes + Fruit_No +Fruit_Preyed + Fruit_Dispersed) #Nacho this equation is wrong in your metadata!
+
+#1st eliminate frutos perdidos
+wordList <- c("fruto perdido","frutos perdidos")
+
+require(Hmisc)
+f2<-subset(f, Notes %nin% wordList)
+
+f2$tot.fruitset<-(f2$Fruit_Yes +  f2$Fruit_preyed + f2$Fruit_dispersed)/(f2$Fruit_Yes +f2$Fruit_No + f2$Fruit_preyed + f2$Fruit_dispersed)
+
+s2<-subset(s, Notes %nin% wordList)
+s2$tot.seedset
+
+###### read network and species level files (network analyses to be found at "...scripts/network analysis.R")
+
+outsp.pl.site<-read.csv("SITE_plant_species_level_metrics.csv")
+outsp.site<-read.csv("SITE_species_level_metrics.csv")
+out.site<-read.csv("SITE_network_level_metrics.csv")
+
+#check correlation between different variables
+
+head(out.site)
+str(out.site)
+c<-cor(out.site[,2:20])
+c2<-round(c,digits=2)
+#write.csv(c2, file= "~/Dropbox/Beefun/Beefun/functioning/tables/variable_correlations.csv", row.names = TRUE, sep = ",")
+
+#♣correlation between weighted nodf and functional complementarity of pollinators : -0.13
+
+#create table with number of individuals per plant species sampled at each site
+
+tableSx <- aggregate(Plant.ID ~ Site_ID + Plant.sp, data = f2, FUN = function(x){NROW(x)})
+
+#write.csv(tableSx, file= "C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/plantindspersite.csv", row.names = FALSE, sep = ",")
+
+#-------------------------------------------------------------------------------------------
+#join plant species level network metrics with fruit and seed set for each site
+
+#FRUIT SET
+
+#1st calculate average fruit set for all plants per site
+
+library(plyr)
+
+f2$Plant.sp<-paste(f2$Plant_genus, f2$Plant_species)
+
+f.agg <- ddply(f2, c("Site_ID", "Plant.sp"), summarise,
+                         mean.fruitset    = mean(tot.fruitset),
+                         sd.fruitset = sd(tot.fruitset))
+
+#f.agg
+
+f.agg$weighted_NODF<-out.site$weighted_NODF[match(f.agg$Site_ID, out.site$Site_id)]
+f.agg$int_evenness<-out.site$int_evenness[match(f.agg$Site_ID, out.site$Site_id)]
+f.agg$H2<-out.site$H2[match(f.agg$Site_ID, out.site$Site_id)]
+f.agg$functional.comp.poll<-out.site$functional.comp.poll[match(f.agg$Site_ID, out.site$Site_id)]
+f.agg$niche.overlap.plant<-out.site$niche.overlap.plant[match(f.agg$Site_ID, out.site$Site_id)]
+f.agg$modularity<-out.site$modularity[match(f.agg$Site_ID, out.site$Site_id)]
+f.agg$nodf.song<-out.site$nodf.song[match(f.agg$Site_ID, out.site$Site_id)]
+f.agg$link_dens<-out.site$link_dens[match(f.agg$Site_ID, out.site$Site_id)]
+f.agg$Shannon<-out.site$Shannon[match(f.agg$Site_ID, out.site$Site_id)]
+
+#also match with plant species level network data
+f.agg$match<-paste(f.agg$Site_ID, f.agg$Plant.sp)
+outsp.pl.site$match<-paste(outsp.pl.site$Site_id, outsp.pl.site$species)
+
+f.agg$norm_degree<-outsp.pl.site$norm_degree[match(f.agg$match, outsp.pl.site$match)]
+f.agg$strength<-outsp.pl.site$strength[match(f.agg$match, outsp.pl.site$match)]
+f.agg$nestedra<-outsp.pl.site$nestedra[match(f.agg$match, outsp.pl.site$match)]
+f.agg$weigh_betweeness<-outsp.pl.site$weigh_betweeness[match(f.agg$match, outsp.pl.site$match)]
+f.agg$weigh_closeness<-outsp.pl.site$weigh_closeness[match(f.agg$match, outsp.pl.site$match)]
+f.agg$d<-outsp.pl.site$d[match(f.agg$match, outsp.pl.site$match)]
+f.agg$c<-outsp.pl.site$c[match(f.agg$match, outsp.pl.site$match)]
+f.agg$z<-outsp.pl.site$z[match(f.agg$match, outsp.pl.site$match)]
+
+#check for structure of data
+#hist(f.agg$mean.fruitset)
+
+f.agg2<-na.omit(f.agg)
+#cor(f.agg2[,c(5:10, 12:19)])
+
+library(glmmTMB)
+library(DHARMa)
+library(MuMIn)
+library(jtools) #plot interactions
+
+#model include nestedness, funct compl and their interaction. check best model with dredge and plot significant variables
+
+#compare AIC of models with and without interaction
+
+m1.fr<-glmmTMB(mean.fruitset ~ nodf.song *  functional.comp.poll  +  (1|Plant.sp), family="gaussian", data=f.agg2)
+summary(m1.fr)
+
+dredge(m1.fr)
+
+m1.fr2<-glmmTMB(mean.fruitset ~ nodf.song +   (1|Plant.sp), family="gaussian", data=f.agg2)
+summary(m1.fr2)
+
+#save results to table to include in paper
+
+b<-summary(m1.fr2)$coefficients$cond
+
+#format table so it only has 2 decimals
+
+y<-round(b,digits=2)
+
+#write.csv(y, file="~/Dropbox/Beefun/Beefun/functioning/tables/resultsnetwfruitset.csv", row.names = TRUE)
+
+#test for problems in residuals
+res<-simulateResiduals(m1.fr2)
+plot(res, rank = TRUE)
+
+#plot nodf only significant variable, with different colors for plant species and all together
+
+pl1<-ggplot(f.agg2,  aes(x=nodf.song, y=mean.fruitset, color=Plant.sp))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Nestedness") +      
+        ylab("Mean fruitset") + theme_bw() +  theme(text = element_text(size = 15), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold")) + labs(col="Plant species")
+
+pl1
+
+#theme (legend.position= "none") +
+
+#SEED NUMBER
+
+#1st calculate average seed number for all plants per site
+
+s<-s[,-10]
+
+library(plyr)
+
+s$Plant.sp<-paste(s$Plant_genus, s$Plant_species)
+
+#create table with number of fruits per individual per plant species sampled at each site
+
+tableSx2 <- aggregate(Fruit.nÂº ~ Site_ID + Plant.sp + Plant.ID, data = s, FUN = function(x){NROW(x)})
+
+#write.csv(tableSx2, file= "C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/fruitnumberperplantindspersite.csv", row.names = FALSE, sep = ",")
+
+s.agg <- ddply(s, c("Site_ID", "Plant.sp"), summarise,
+                         mean.seednumber    = mean(Seeds2),
+                        # sd.seednumber = sd(Seeds2),
+                         mean.seedweight = mean(Seed.weight),
+                        # sd.seedweight = sd(Seed.weight),
+                         mean.fruitweight = mean(Fruit.weight2)#,
+                         #sd.fruitweight = sd(Fruit.weight2)
+                         )
+
+#s.agg
+
+s.agg$weighted_NODF<-out.site$weighted_NODF[match(s.agg$Site_ID, out.site$Site_id)]
+s.agg$int_evenness<-out.site$int_evenness[match(s.agg$Site_ID, out.site$Site_id)]
+s.agg$H2<-out.site$H2[match(s.agg$Site_ID, out.site$Site_id)]
+s.agg$functional.comp.poll<-out.site$functional.comp.poll[match(s.agg$Site_ID, out.site$Site_id)]
+s.agg$niche.overlap.plant<-out.site$niche.overlap.plant[match(s.agg$Site_ID, out.site$Site_id)]
+s.agg$modularity<-out.site$modularity[match(s.agg$Site_ID, out.site$Site_id)]
+s.agg$nodf.song<-out.site$nodf.song[match(s.agg$Site_ID, out.site$Site_id)]
+
+#also match with plant species level network data
+s.agg$match<-paste(s.agg$Site_ID, s.agg$Plant.sp)
+outsp.pl.site$match<-paste(outsp.pl.site$Site_id, outsp.pl.site$species)
+
+s.agg$norm_degree<-outsp.pl.site$norm_degree[match(s.agg$match, outsp.pl.site$match)]
+s.agg$strength<-outsp.pl.site$strength[match(s.agg$match, outsp.pl.site$match)]
+s.agg$nestedra<-outsp.pl.site$nestedra[match(s.agg$match, outsp.pl.site$match)]
+s.agg$weigh_betweeness<-outsp.pl.site$weigh_betweeness[match(s.agg$match, outsp.pl.site$match)]
+s.agg$weigh_closeness<-outsp.pl.site$weigh_closeness[match(s.agg$match, outsp.pl.site$match)]
+s.agg$d<-outsp.pl.site$d[match(s.agg$match, outsp.pl.site$match)]
+s.agg$c<-outsp.pl.site$c[match(s.agg$match, outsp.pl.site$match)]
+s.agg$z<-outsp.pl.site$z[match(s.agg$match, outsp.pl.site$match)]
+
+#check for structure of data
+#hist(s.agg$mean.seednumber)
+
+m2.see<-glmmTMB(mean.seednumber ~ nodf.song *  functional.comp.poll +   (1|Plant.sp), family="poisson", data=s.agg)
+summary(m2.see)
+
+dredge(m2.see)
+
+m2.seeb<-glmmTMB(mean.seednumber ~ functional.comp.poll +   (1|Plant.sp), family="poisson", data=s.agg)
+summary(m2.seeb)
+
+#save results to table to include in paper
+
+b2<-summary(m2.seeb)$coefficients$cond
+
+#format table so it only has 2 decimals
+
+y2<-round(b2,digits=2)
+
+#write.csv(y2, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsnetwseednumFULL.csv", row.names = TRUE)
+
+#test for problems in residuals
+res<-simulateResiduals(m2.seeb)
+plot(res, rank = TRUE)
+
+#plot nodf only significant variable, with different colors for plant species and all together
+
+pl2<-ggplot(s.agg,  aes(x=functional.comp.poll, y=mean.seednumber, color=Plant.sp))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Functional complementarity") +      
+        ylab("Mean seed number") + theme_bw()  + 
+        theme(text = element_text(size = 12), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold")) + labs(col="Plant species")
+
+pl2
+# 
+# interact_plot(m2.see, pred = "functional.comp.poll", modx = "nodf.song", interval = TRUE, plot.points = TRUE, int.type = "confidence",  facet.modx = TRUE, x.label = "Functional complementarity", y.label = "Mean seed number/fruit",
+#               modx.labels= c("Mean nestedness + 1 SD", "Mean nestedness", "Mean nestedness - 1 SD"))
+
+```
+
+#it seems all effects are driven by Cistus ladanifer, re-analyse without this species
+
+```{r, include=TRUE}
+s.agg2<-subset(s.agg, s.agg$Plant.sp!="Cistus ladanifer")
+
+m2.see.2<-glmmTMB(mean.seednumber ~ nodf.song *  functional.comp.poll +   (1|Plant.sp), family="poisson", data=s.agg2)
+summary(m2.see.2)
+
+dredge(m2.see.2)
+
+pl5<-ggplot(s.agg2,  aes(x=functional.comp.poll, y=mean.seednumber, color=Plant.sp))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Functional complementarity") +      
+        ylab("Mean seed number") + theme_bw() + theme (legend.position= "none") + 
+        theme(text = element_text(size = 12), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold")) + labs(col="Plant species")
+
+pl5
+
+interact_plot(m2.see.2, pred = "functional.comp.poll", modx = "nodf.song", interval = TRUE, plot.points = TRUE, int.type = "confidence",  facet.modx = TRUE, x.label = "Functional complementarity", y.label = "Mean seed number/fruit",
+              modx.labels= c("Mean nestedness + 1 SD", "Mean nestedness", "Mean nestedness - 1 SD"))
+```
+#driven only by C. salvifolius and albidus? re-do analyses
+
+```{r, include=TRUE}
+
+s.agg3<-subset(s.agg2, s.agg2$Plant.sp!="Cistus salvifolius")
+
+m2.see.c<-glmmTMB(mean.seednumber ~ nodf.song *  functional.comp.poll  +  (1|Plant.sp), family="poisson", data=s.agg3)
+summary(m2.see.c)
+
+dredge(m2.see.c)
+
+m2.see.c2<-glmmTMB(mean.seednumber ~ nodf.song   +  (1|Plant.sp), family="poisson", data=s.agg3)
+summary(m2.see.c2)
+
+pl7<-ggplot(s.agg3,  aes(x=nodf.song, y=mean.seednumber, color=Plant.sp))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Nestedness") +      
+        ylab("Mean seed number") + theme_bw()  + theme (legend.position= "none") +
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
+
+pl7
+
+s.agg4<-subset(s.agg2, s.agg2$Plant.sp!="Cistus albidus")
+
+m2.see.d<-glmmTMB(mean.seednumber ~ nodf.song *  functional.comp.poll  +  (1|Plant.sp), family="poisson", data=s.agg4)
+summary(m2.see.d)
+
+dredge(m2.see.d)
+
+b3<-summary(m2.see.d)$coefficients$cond
+y3<-round(b3,digits=2)
+#write.csv(y3, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsnetwseednumTRIMMED.csv", row.names = TRUE)
+
+library (jtools)
+interact_plot(m2.see.d, pred = "functional.comp.poll", modx = "nodf.song", interval = TRUE, plot.points = TRUE, int.type = "confidence",  facet.modx = TRUE, x.label = "Functional complementarity", y.label = "Mean seed number/fruit",
+              modx.labels= c("Mean nestedness + 1 SD", "Mean nestedness", "Mean nestedness - 1 SD"))
+
+pl8<-ggplot(s.agg4,  aes(x=nodf.song, y=mean.seednumber, color=Plant.sp))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Nestedness") +      
+        ylab("Mean seed number") + theme_bw()  + theme (legend.position= "none") +
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
+
+pl8
+
+pl9<-ggplot(s.agg4,  aes(x=functional.comp.poll, y=mean.seednumber, color=Plant.sp))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Functional complementarity") +      
+        ylab("Mean seed number") + theme_bw()  + theme (legend.position= "none") +
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
+
+pl9
+
+# 
+# ggplot(out.site,  aes(x= nodf.song, y=functional.comp.poll))+      
+#         geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+#         geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+#         xlab("Nestedness") +      
+#         ylab("Functional compl") + theme_bw()  
+# 
+# 
+# summary(lm(functional.comp.poll ~ nodf.song, data=s.agg4))$r.squared
+
+#SEED WEIGHT
+
+#check for structure of data
+#hist(s.agg$mean.seedweight)
+
+m3<-glmmTMB(mean.seedweight ~ nodf.song *  functional.comp.poll +  (1|Plant.sp), family="poisson", data=s.agg)
+summary(m3)
+
+dredge(m3)
+
+m3b<-glmmTMB(mean.seedweight ~ nodf.song  +  (1|Plant.sp), family="poisson", data=s.agg)
+summary(m3b)
+
+b4<-summary(m3b)$coefficients$cond
+y4<-round(b4,digits=2)
+#write.csv(y4, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsnetwseedweight.csv", row.names = TRUE)
+
+#test for problems in residuals
+res<-simulateResiduals(m3b)
+plot(res, rank = TRUE)
+
+#FRUIT WEIGHT
+
+#check for structure of data
+#hist(s.agg$mean.fruitweight)
+
+m4<-glmmTMB(mean.fruitweight ~ nodf.song *  functional.comp.poll +  (1|Plant.sp), family="nbinom2", data=s.agg)
+summary(m4)
+
+dredge(m4)
+
+m4b<-glmmTMB(mean.fruitweight ~ nodf.song +  (1|Plant.sp), family="nbinom2", data=s.agg)
+summary(m4b)
+
+#test for problems in residuals
+res<-simulateResiduals(m4b)
+plot(res, rank = TRUE)
+
+b5<-summary(m4b)$coefficients$cond
+y5<-round(b5,digits=2)
+#write.csv(y5, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsnetwfruitweight.csv", row.names = TRUE)
+
+```
+
+#RELATIONSHIP BETWEEN NODE POSITION AND FUNCTIONING
+
+#look at cz plots to see potential connector, hub etc species
+
+```{r, include=TRUE}
+
+#for plant species (all species in network)
+
+czplot<- ggplot(outsp.pl.site,  aes(x=c, y=z)) +
+    geom_point(size=4.5, position="jitter", aes(color = factor(species)))+
+    #geom_jitter()+
+    geom_vline(xintercept=0.62)+
+    geom_hline(yintercept=2.5)+
+    xlim(0,1)+
+    ylim(0,4)+
+    xlab("Between-module connectivity (c)") +
+    ylab("Within-module degree (z)")  +theme_bw() + theme (legend.position= "none") +
+    theme(axis.text=element_text(size=20),
+          axis.title=element_text(size=20,face="bold"))
+
+czplot
+
+#for plant species (only those for which we have data on fruit set)
+
+czplot.b<- ggplot(f.agg2,  aes(x=c, y=z)) +
+    geom_point(size=4.5, position="jitter", aes(color = factor(Plant.sp)))+
+    #geom_jitter()+
+    geom_vline(xintercept=0.62)+
+    geom_hline(yintercept=2.5)+
+    xlim(0,1)+
+    ylim(0,4)+
+    xlab("Between-module connectivity (c)") +
+    ylab("Within-module degree (z)")  +theme_bw() + #theme (legend.position= "none") +
+    theme(axis.text=element_text(size=20),
+          axis.title=element_text(size=20,face="bold"))
+
+czplot.b
+
+# 
+# #use f2
+# 
+# f2$match<-paste(f2$Site_ID, f2$Plant.sp)
+# outsp.pl.site$match<-paste(outsp.pl.site$Site_id, outsp.pl.site$species)
+# 
+# 
+# #also match with plant species level network data
+# 
+# 
+# f2$norm_degree<-outsp.pl.site$norm_degree[match(f2$match, outsp.pl.site$match)]
+# f2$strength<-outsp.pl.site$strength[match(f2$match, outsp.pl.site$match)]
+# f2$nestedra<-outsp.pl.site$nestedra[match(f2$match, outsp.pl.site$match)]
+# f2$weigh_betweeness<-outsp.pl.site$weigh_betweeness[match(f2$match, outsp.pl.site$match)]
+# f2$weigh_closeness<-outsp.pl.site$weigh_closeness[match(f2$match, outsp.pl.site$match)]
+# f2$d<-outsp.pl.site$d[match(f2$match, outsp.pl.site$match)]
+# f2$c<-outsp.pl.site$c[match(f2$match, outsp.pl.site$match)]
+# f2$z<-outsp.pl.site$z[match(f2$match, outsp.pl.site$match)]
+# 
+# str(f2)
+
+# 
+# #check correlations between different species level variables
+# 
+# cor(f2[,17:24])
+
+m5<-glmmTMB(mean.fruitset ~  norm_degree + c + z + weigh_betweeness +  weigh_closeness + (1|Site_ID), family="gaussian", data=f.agg2)
+summary(m5)
+
+dredge(m5)
+
+m5b<-glmmTMB(mean.fruitset ~weigh_closeness  + (1|Site_ID), family="gaussian", data=f.agg2)
+summary(m5b)
+
+#test for problems in residuals
+res<-simulateResiduals(m5b)
+plot(res, rank = TRUE)
+
+pl10<-ggplot(f.agg2,  aes(x=weigh_closeness, y=mean.fruitset, color=Plant.sp))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Closeness centrality") +      
+        ylab("Mean fruitset") + theme_bw()  + #theme (legend.position= "none") +
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
+
+pl10
+
+m6<-glmmTMB(mean.seednumber ~ norm_degree + c + z + weigh_betweeness +  weigh_closeness   + (1|Site_ID), family="gaussian", data=s.agg)
+summary(m6)
+
+dredge(m6)
+
+m6b<-glmmTMB(mean.seednumber ~ norm_degree +  z + weigh_closeness   + (1|Site_ID), family="gaussian", data=s.agg)
+summary(m6b)
+
+pl11<-ggplot(s.agg,  aes(x=norm_degree, y=mean.seednumber, color=Plant.sp))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Normalized degree") +      
+        ylab("Mean seed number/fruit") + theme_bw()  + #theme (legend.position= "none") +
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
+
+pl11
+
+#remove C. ladanifer
+
+m7<-glmmTMB(mean.seednumber ~ norm_degree + c + z + weigh_betweeness +  weigh_closeness   + (1|Site_ID), family="gaussian", data=s.agg2)
+summary(m7)
+
+dredge(m7)
+
+m7b<-glmmTMB(mean.seednumber ~  z + weigh_closeness   + (1|Site_ID), family="gaussian", data=s.agg2)
+summary(m7b)
+
+pl12<-ggplot(s.agg2,  aes(x=z, y=mean.seednumber, color=Plant.sp))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("z") +      
+        ylab("Mean seed number/fruit") + theme_bw()  + #theme (legend.position= "none") +
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
+
+pl12
+
+m8<-glmmTMB(mean.seedweight ~ norm_degree + c + z + weigh_betweeness +  weigh_closeness   + (1|Site_ID), family="gaussian", data=s.agg)
+summary(m8)
+
+dredge(m8)
+
+m8b<-glmmTMB(mean.seedweight ~ weigh_betweeness +   (1|Site_ID), family="gaussian", data=s.agg)
+summary(m8b)
+
+m9<-glmmTMB(mean.fruitweight ~ norm_degree + c + z + weigh_betweeness +  weigh_closeness   + (1|Site_ID), family="gaussian", data=s.agg)
+summary(m9)
+
+dredge(m9)
+
+m9b<-glmmTMB(mean.fruitweight ~  c  + (1|Site_ID), family="gaussian", data=s.agg)
+summary(m9b)
+
+#for pollinator species
+
+#create column for apis to see it in different shape in the plot
+
+outsp.site$apis<-outsp.site$species
+outsp.site$apis<-as.character(outsp.site$apis)
+outsp.site$apis[outsp.site$apis!="Apis mellifera"]<-"0"
+outsp.site$apis[outsp.site$apis=="Apis mellifera"]<-"1"
+
+czpoll<- ggplot(outsp.site,  aes(x=c, y=z)) +
+    geom_point(size=4.5, position="jitter", aes(color = factor(species), shape = factor(apis)))+
+    #geom_jitter()+
+    geom_vline(xintercept=0.62)+
+    geom_hline(yintercept=2.5)+
+    xlim(0,1)+
+    ylim(0,4)+
+    xlab("Between-module connectivity (c)") +
+    ylab("Within-module degree (z)")  +theme_bw() + theme (legend.position= "none") +
+    theme(axis.text=element_text(size=20),
+          axis.title=element_text(size=20,face="bold"))
+
+czpoll
+
+```
+
+#LOOK AT EVENNESSS IN FUNCTION.
+within a site most plant species have very low reproductive success and thus we get incredibly high evenness values.
+therefore we use thresholds, for each sps and site we calculate the # of individuals that are above 50% in fruit production
+
+```{r, include=TRUE}
+library(vegan)
+library(dplyr)
+
+f2$Plant.sp<-paste(f2$Plant_genus, f2$Plant_species)
+f3<-f2[,c(1,13:14)]
+
+f4 <- ddply(f3, c("Site_ID", "Plant.sp"), summarise,
+                         mean.fruitset    = mean(tot.fruitset))
+
+#f4
+
+fr.max<-aggregate(.~ Plant.sp, f4, FUN=max)
+
+f4$fruit.max<-fr.max$mean.fruitset[match(f4$Plant.sp, fr.max$Plant.sp)]
+
+f4$fruit.prop<-f4$mean.fruitset/f4$fruit.max
+f5<-subset(f4, f4$fruit.prop>0.5)
+
+#for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
+f6<-f5 %>% 
+  group_by(Site_ID) %>%
+  summarise(no_rows = length(Site_ID ))
+
+#join this with fruitset data used previously
+
+f6$nodf.song<-out.site$nodf.song[match(f6$Site_ID, out.site$Site_id)]
+f6$int_evenness<-out.site$int_evenness[match(f6$Site_ID, out.site$Site_id)]
+f6$H2<-out.site$H2[match(f6$Site_ID, out.site$Site_id)]
+f6$functional.comp.poll<-out.site$functional.comp.poll[match(f6$Site_ID, out.site$Site_id)]
+f6$niche.overlap.plant<-out.site$niche.overlap.plant[match(f6$Site_ID, out.site$Site_id)]
+f6$modularity<-out.site$modularity[match(f6$Site_ID, out.site$Site_id)]
+
+library(glmmTMB)
+library(DHARMa)
+
+m.th<-glmmTMB(no_rows ~ nodf.song *  functional.comp.poll , family="gaussian", data=f6)
+summary(m.th)
+
+dredge(m.th)
+
+m.th2<-glmmTMB(no_rows ~   functional.comp.poll , family="gaussian", data=f6)
+summary(m.th2)
+
+b6<-summary(m.th2)$coefficients$cond
+y6<-round(b6,digits=2)
+#write.csv(y6, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsevennessfruitset.csv", row.names = TRUE)
+
+#test for problems in residuals
+res<-simulateResiduals(m.th2)
+plot(res, rank = TRUE)
+
+#plot nodf only significant variable, with different colors for plant species and all together
+
+pl.th<-ggplot(f6,  aes(x=nodf.song, y=no_rows))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        xlab("Nestedness") +      
+        ylab("Evenness in fruitset") + theme_bw() + 
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
+
+pl.th
+
+pl.th2<-ggplot(f6,  aes(x=functional.comp.poll, y=no_rows))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        xlab("Functional complementarity") +      
+        ylab("Evenness in fruitset") + theme_bw() + 
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
+
+pl.th2
+
+```
+
+#look at single visit data for some species to see whether they can be related to network roles or repr success
+#importante
+
+#Control = siempre embolsados
+#Open = embolsados la noche antes, y open durante 6 horas de dia (o sea visitado por lo que sea que pasara durante el dia).
+
+```{r, include=TRUE}
+
+# si.cs<-subset(si, si$Plant.sp=="Cistus  salvifolius") 
+# si.cs
+# 
+# 
+# pl.si.cs<-ggplot(si.cs,  aes(x=Pollinator_genus, y=pollen_tubes))+  
+#   geom_bar(stat="identity")
+#         
+# pl.si.cs
+
+library(ggplot2)
+
+gg_color_hue <- function(n) {
+  hues = seq(15, 375, length=n+1)
+  hcl(h=hues, l=65, c=100)[1:n]
 }
 
-##sacar la tabla con todas las metrics del network y añadirle el landscape_type
-#primero hay que crear una columna con landscape_type y año jutnos porque el tipo
-#de landscape varia en algunos años
-#especie de iferror(vlookup)
-str(out)
-tablenetwork<-out[2:61,]
+mycols <- gg_color_hue(length(unique(si$Pollinator_genus)))
+names(mycols) <- unique(si$Pollinator_genus)
+mycols["Control"] <- "black"
+mycols["Open"] <- "grey"
+mycols["Apis"] <- "yellow"
+
+  pl.si<- ggplot(si,  aes(x=Pollinator_genus, y=pollen_tubes, fill=Pollinator_genus))+  
+    geom_bar(stat="identity")  + scale_fill_manual(values=mycols) + theme (legend.position= "none") #+ 
+    # theme(text = element_text(size = 12),
+    #     axis.text=element_text(size=rel(1)),
+    #     axis.title=element_text(size=rel(1),face="bold"), legend.direction="horizontal", legend.text=element_text(size=10))
+
+  pl.si + facet_wrap( ~ Plant.sp, scales="free")
 
 ```
+
+El control tiene valores super altos, esta bien?? COntrol es el negro, open el gris

### 2018-11-06 scripts/network analysis.R

@@ -34,6 +34,11 @@ f<-fruitset
 s<-seedset
 si<-single_visits
 
+#we will calculate nestedness based on paper by Song et al 2017 Journal of ANimal ecology based on NODF and its
+#correction by max NODF as NODFc = NODFn/(C  log(S)), where NODFn = NODF/max(NODF).
+#to this end we use the toolbox provided with their paper
+
+source('toolbox.R') #load the toolbox
 
 ##1st create a bipartite matrix for each site MERGING ALL ROUNDS TOGETHER and extract a set of metrics at the network level
 
@@ -66,8 +71,7 @@ out.site <- data.frame(Site_id = NA, links_sps = NA, num_compartments = NA,weigh
                        species.poll=NA, species.pl=NA, 
                        niche.overlap.poll=NA, niche.overlap.plant=NA, robustness.poll=NA, robustness.plant=NA,
                        functional.comp.poll=NA, functional.comp.plant=NA,
-                       modularity=NA, z=NA, links.corr=NA, nodf.corr=NA, linkdens.corr=NA, conn.corr=NA,
-                       even.corr=NA, h2.corr=NA)
+                       modularity=NA, z=NA, nodf.song=NA)
 
 outsp.site <- data.frame(Site_id = NA, species=NA,  norm_degree = NA,strength= NA, nestedra= NA,weigh_betweeness  = NA, 
                          weigh_closeness=NA, d=NA, c=NA, z=NA)#, specificity=NA)
@@ -105,6 +109,13 @@ for(i in 1:length(sites)){
   like.nulls <- try(sapply(modules.nulls, function(x) x@likelihood), TRUE)
   z <- try((mod@likelihood - mean(like.nulls))/sd(like.nulls), TRUE)
   
+  #song et al nestedness corrected with NODF max
+  
+NODF <- nestedness_NODF(web) # this calculates the raw value of NODF
+max_NODF <- max_nest(web) # this calculates the maximum value of NODF for that network
+combined_NODF <- comb_nest(web,NODF,max_NODF) # this calculates the combined NODF statistic as described in the manuscript
+  
+  
[…]

### 2018-11-06 paper.Rmd
paper markdown document

--- 2018-11-06 ideas_functioning.Rmd
@@
 ---
-title: "Ideas_ntw_function"
-author: "I. Bartomeus, A. Magrach"
-date: "6/14/2018"
+title: "Paper"
+author: "Ainhoa Magrach"
+date: "6 November 2018"
 output: html_document
 ---
+
 ---
@@
 
--------------------------------------
-IDEAS
--------------------------------------
-
-I'll start by 
-  - showing the relationship between ntw structure (defined as? Niche complementariety?) and overall functioning (defined as mean rep success of plants?)
-  - showing the relationship between node position and plant species functioning
-  - showing the relationship between ntw structure and functioning maximization (eveness of fucntioning, well, not evenness, you want equity (that is, even and high))
-
-We can use data on both visitation rates (quantity), pollen deposition (quality), its product (pollen delivered) and fruit set and seed set.
-
-AINHOA OTHER IDEAS: We could look at in the future
-1) how do perturbations (in this case fragmentation) affect species specialization? in this setting are specialization and 
-link conservatism or opportunism (how regional interaction richness of a species differs from what could be expected if species interacted randomly with the available set of partners, see Carstensen et al 2017) constant through time?
-Carstensen et al also find that specialization is conserved from local to regional levels (correlation between specialization levels), is this the case in a fragmented setting?
-2) are these changes a consequence of turnover in species composition across fragments or interaction composition (rewiring)? or is it temporal turnover?
-3) changes in node position in plants with perturbation. what are the consequences for functioning? seed set
-
------------------------------------------
-ABSTRACT
------------------------------------------
+# ABSTRACT
 
@@
 
------------------------------------------
-QUESTIONS
------------------------------------------
+#INTRODUCTION
 
-1) How does network structure, and in particular two aspects (nestedness and functional complementarity), that represent redundancy (and thus potentially resilience to species loss) and complementarity in niche (and thus potentially increased reproductive success through niche differentiation, specialization and increased pollen deposition of same species) link to ecosystem function (mean fruit and seed set) at the community level?
-
-2) How does the node position of a plant species within a network affect ecosystem functioning (here reproductive success)?
-Apparent competition with other plant species?
-Pollinator diversity visiting?
-
-3) How does network structure affect equity in functioning?
-
------------------------------------------
-METHODS
------------------------------------------
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
-```
+# METHODS
 
@@
 
-```{r, include=TRUE}
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=9}
 #First attempt to load the data, etc...
@@
 si$Plant.sp<-paste(si$Plant_genus, si$Plant_species)
+
+###### read network and species level files (network analyses to be found at "...scripts/network analysis.R")
+
+outsp.pl.site<-read.csv("SITE_plant_species_level_metrics.csv")
+outsp.site<-read.csv("SITE_species_level_metrics.csv")
+out.site<-read.csv("SITE_network_level_metrics.csv")
 
@@
 
-poll
+#poll
 
@@
 
-plant
+#plant
 
@@
 
-link
+#link
 
@@
 
-------------------------------------------------------------------------------------------------------
-QUESTION 1:  - relationship between ntw structure defined as nestedness (i.e.
-redundancy) and complementarity (i.e.
-funct compl), also taking into species-level characteristics (e.g., degree and specialization) and relate it to overall functioning (defined as mean rep success of all plant species together per site)
-------------------------------------------------------------------------------------------------------
+### QUESTION 1:  
+What is the relationship between network structure and functioning?
 
-```{r, include=TRUE}
+Here, we will define network structure at the community (whole-network level) focusing in particular in two aspects: network nestedness (a measure of redundancy in species roles) and functional complementarity (a measure of complementarity in species niches).
+Functioning will be defined as average fruit set for each species at each site.
+Plant species will be included as a random factor to evaluate whether the reproductive success of different species change across networks with different overall structures.
+Models include nestedness, funct compl and their interaction.
+check best model with "dredge" and plot significant variables
 
+#### Function as FRUITSET
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
 #####################################################################################################################
@@
 
-###### read network and species level files (network analyses to be found at "...scripts/network analysis.R")
-
-outsp.pl.site<-read.csv("SITE_plant_species_level_metrics.csv")
-outsp.site<-read.csv("SITE_species_level_metrics.csv")
-out.site<-read.csv("SITE_network_level_metrics.csv")
-
 #check correlation between different variables
 
-head(out.site)
-str(out.site)
+#head(out.site)
+#str(out.site)
 c<-cor(out.site[,2:20])
@@
 
-tableSx <- aggregate(Plant.ID ~ Site_ID + Plant.sp, data = f2, FUN = function(x){NROW(x)})
+#tableSx <- aggregate(Plant.ID ~ Site_ID + Plant.sp, data = f2, FUN = function(x){NROW(x)})
 
@@
 
+```
+#### Function as SEED NUMBER
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+
 #SEED NUMBER
@@
 
-tableSx2 <- aggregate(Fruit.nÂº ~ Site_ID + Plant.sp + Plant.ID, data = s, FUN = function(x){NROW(x)})
+#tableSx2 <- aggregate(Fruit.nÂº ~ Site_ID + Plant.sp + Plant.ID, data = s, FUN = function(x){NROW(x)})
 
@@
 
-#it seems all effects are driven by Cistus ladanifer, re-analyse without this species
+it seems all effects are driven by Cistus ladanifer, re-analyse without this species
 
-```{r, include=TRUE}
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
 s.agg2<-subset(s.agg, s.agg$Plant.sp!="Cistus ladanifer")
@@
 
-pl5
+#pl5
 
@@
 ```
-#driven only by C. salvifolius and albidus? re-do analyses
 
-```{r, include=TRUE}
+driven only by C. salvifolius and albidus? re-do analyses
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
 
@@
 
-pl7
+#pl7
 
@@
 
-pl8
+#pl8
 
@@
 
-pl9
+#pl9
 
@@
 # summary(lm(functional.comp.poll ~ nodf.song, data=s.agg4))$r.squared
+```
 
-#SEED WEIGHT
+#### fUNCTION AS SEED OR FRUIT WEIGHT
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
 
@@
 
-#RELATIONSHIP BETWEEN NODE POSITION AND FUNCTIONING
+### QUESTION 2:  
+2) How does the position of a plant species within a network affect its reproductive success?
 
-#look at cz plots to see potential connector, hub etc species
+We will focus on the effect of networks metrics measured at the species level: normalised degree, c, z, betweenness and closeness on average fruit set per plant.
+This time site will be included as random to evaluate whether node position of a plant species in a particular networks affects its reproductive success.
 
-```{r, include=TRUE}
+look at cz plots to see potential connector, hub etc species, first for all plant species in the network, then only for species for which we have data on fruit set
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
 
@@
 
+```
+
+remove C. ladanifer which seems to be driving the relationship
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+
 #remove C. ladanifer
@@
 
-#for pollinator species
+```
+
+look at cz plots for pollinator species. triangles are apis mellifera, potential there for study on their effect for repr success??
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
 
@@
 
-#LOOK AT EVENNESSS IN FUNCTION.
+### QUESTION 3:
+
+How does network structure affect equity in functioning?
+
+LOOK AT EVENNESSS IN FUNCTION.
 within a site most plant species have very low reproductive success and thus we get incredibly high evenness values.
@@
 
-```{r, include=TRUE}
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+
 library(vegan)
@@
 f5<-subset(f4, f4$fruit.prop>0.5)
+f5$no_rows<-rep(1, nrow(f5))
 
 #for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
-f6<-f5 %>% 
-  group_by(Site_ID) %>%
-  summarise(no_rows = length(Site_ID ))
+f6<- aggregate(no_rows ~ Site_ID, f5, length)
 
@@
 ```
-
-#look at single visit data for some species to see whether they can be related to network roles or repr success
-#importante
-
-#Control = siempre embolsados
-#Open = embolsados la noche antes, y open durante 6 horas de dia (o sea visitado por lo que sea que pasara durante el dia).
-
-```{r, include=TRUE}
-
-# si.cs<-subset(si, si$Plant.sp=="Cistus  salvifolius") 
-# si.cs
-# 
-# 
-# pl.si.cs<-ggplot(si.cs,  aes(x=Pollinator_genus, y=pollen_tubes))+  
-#   geom_bar(stat="identity")
-#         
-# pl.si.cs
-
-library(ggplot2)
-
-gg_color_hue <- function(n) {
-  hues = seq(15, 375, length=n+1)
-  hcl(h=hues, l=65, c=100)[1:n]
-}
-
-mycols <- gg_color_hue(length(unique(si$Pollinator_genus)))
-names(mycols) <- unique(si$Pollinator_genus)
-mycols["Control"] <- "black"
-mycols["Open"] <- "grey"
-mycols["Apis"] <- "yellow"
-
-  pl.si<- ggplot(si,  aes(x=Pollinator_genus, y=pollen_tubes, fill=Pollinator_genus))+  
-    geom_bar(stat="identity")  + scale_fill_manual(values=mycols) + theme (legend.position= "none") #+ 
-    # theme(text = element_text(size = 12),
-    #     axis.text=element_text(size=rel(1)),
-    #     axis.title=element_text(size=rel(1),face="bold"), legend.direction="horizontal", legend.text=element_text(size=10))
-
-  pl.si + facet_wrap( ~ Plant.sp, scales="free")
-
-```
-
-El control tiene valores super altos, esta bien?? COntrol es el negro, open el gris

### 2018-11-12 paper.Rmd
include motif analyses

@@
 ```
+
+Now look at motifs and indirect interactions.
+To this end, we compare the roles of plant species at each site with low (<0.5) and high (>0.5) fruit set.
+We calculate for each plant species at each site the sum-normalised roles of all plant species in motifs up to 5 nodes and plot them using NMDS.
+ALthough we find a large overlap between the roles of both types ofplant species, we do find that plant species with high fruit set tend to be located in the higher values of NMDS1 which is related to network positions in which a generalist plant species interacts with highly specialized pollinator partners (e.g, positions 16 and 46, see Fig.
+1 in bmotif paper, Simmons et al preprint)
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+#First attempt to load the data, etc...
+
+#prepare stuff-----
+#If you don't have devtools install it
+#install.packages("devtools")
+library(devtools)
+#Then install the data package. Reprot issues 
+#install_github("ibartomeus/BeeFunData", ref = "fun")
+library(BeeFunData)
+
+# load packages
+library(bmotif)
+library(vegan)
+
+#make the data available
+#analysis...----
+
+d<-all_interactions
+f<-fruitset
+s<-seedset
+
+d2<-subset(d, d$Plant_gen_sp!="NA NA")
+#d2$Plant_gen_sp
+
+sites <- unique(d2$Site_ID)
+
+empty_web <- function(x) {
+  # Removes all-zero rows and columns from a matrix
+  cempty <- which(colSums(x) == 0)
+  rempty <- which(rowSums(x) == 0)
+  if(length(rempty) != 0 & length(cempty) == 0){
+    return(x[-rempty,,drop = FALSE])
+  } else if(length(rempty) == 0 & length(cempty) != 0){
+    return(x[,-cempty,drop = FALSE])
+  } else if(length(rempty) != 0 & length(cempty) != 0){
+    return(x[-rempty,-cempty,drop = FALSE])
+  } else if(length(rempty) == 0 & length(cempty) == 0){
+    return(x)
+  }
+}
+
+webs <- list()
+webs.or3<-list()
+for(i in 1:length(sites)){
+  temp <- subset(d2, Site_ID == sites[i])
+  # for(j in 1:length(rounds)){
+  #   temp2 <- subset(temp, Round == rounds[j])
+  #   if (nrow(temp2) == 0) next
+
+  web <- as.matrix.data.frame(table(temp$Plant_gen_sp, temp$Pollinator_gen_sp))
+  web.or<-table(temp$Plant_gen_sp, temp$Pollinator_gen_sp)#keeps names of species
+
+  web2<-empty_web(web)
+  web.or2<-empty_web(web.or)
+
+  webs.or3[[i]]<-web.or2 #keeps names of species
+  webs[[i]]<-as.matrix(web2)
+}
+
+names(webs)<-sites
+names(webs.or3)<-sites
+
+out <- data.frame(web = NA, nrow = NA)
+
+#calculates number of rows in each web and then sums everything to see how many rows we need in total
+for(i in 1:length(webs)){
+  s<- sum(nrow(webs[[i]]))
+
+  n<-nrow(out)
+  out[n + 1,1] <- as.character(sites[i])
+  out[n + 1,2] <- s
+
+}
+
+out<-out[-1,]
+out2<-sum(out$nrow)
+
+mp <- as.data.frame(matrix(nrow = out2, ncol = 48, dimnames = list(NULL,c("web","species",paste0("m",1:46)))))
+wr <- 0
+for(i in names(webs)){
+
+    pv <- positions(webs[[i]], six_node = FALSE, level = "rows", normalisation = "sum") # calculate species positions
+    start_row <- which(is.na(mp$web))[1]
+    end_row <- (start_row + nrow(pv)) - 1
+    wr <- start_row:end_row
+    mp[wr,"web"] <- i
+    mp[wr,"species"] <- rownames(webs.or3[[i]])
+    mp[wr,paste0("m",1:46)] <- pv
+  }
+
+#SUBSET ONLY PLANTS FOR WHICH WE HAVE DATA ON FRUISET
+#f4
+f4$j<-paste(f4$Site_ID, f4$Plant.sp)
+
+mp$j<-paste(mp$web, mp$species)
+
+mp$mean.fruitset<-f4$mean.fruitset[match(mp$j, f4$j)]
+
+mp2<-subset(mp, mp$mean.fruitset!="NA")
+mp2$class[mp2$mean.fruitset>0.5]<-"high"
+mp2$class[mp2$mean.fruitset<0.5]<-"low"
+
+# How many native and introduced species?
+mp2 <- mp2[order(mp2$class, decreasing = TRUE),]
+class_f <- table(mp2$class)
+
+# NMDS
+example_NMDS <- metaMDS(vegdist(mp2[,paste0("m",1:46)], method = "bray"), k=2, distance = "bray", trymax = 100)
+mds.fig <- ordiplot(example_NMDS, type = "none")
+colors=c(rep("darkorange2",class_f["low"]),rep("purple",class_f["high"]))
+treat <- mp2$class
+for(i in unique(treat)) {
+  ordihull(example_NMDS$point[grep(i,treat),],draw="polygon",
+           groups=treat[treat==i],col=colors[grep(i,treat)],label=F) } 
+with(mp2, legend("topright", legend = unique(mp2$class), bty = "n",
+                col = unique(colors), pch = 21, pt.bg = unique(colors)))
+points(mds.fig, "sites", pch = 19, col = "darkorange3", select = mp2$class == 
+         "low")
+points(mds.fig, "sites", pch = 19, col = "purple", select = mp2$class == 
+         "high")
+
+#example_NMDS <- metaMDS(mp2[,paste0("m",1:46)], k=2, distance = "bray", trymax = 100)
+#example_NMDS$species # which positions are associated with which axes
+#example_NMDS$species[order(example_NMDS$species[,"MDS2"]),]
+
+#permanova
+
+adonis(mp2[,3:48]~ class, data=mp2, method = "bray")
+
+#no significant differences
+
+```

### 2018-11-13 paper.Rmd
included relationship between poll div and nestedness and funct compl. also effect of div on fruit set and find interesting results!!!

@@
 f.agg$Shannon<-out.site$Shannon[match(f.agg$Site_ID, out.site$Site_id)]
+f.agg$species.poll<-out.site$species.poll[match(f.agg$Site_ID, out.site$Site_id)]
+f.agg$species.pl<-out.site$species.pl[match(f.agg$Site_ID, out.site$Site_id)]
 
@@
 f.agg2<-na.omit(f.agg)
-#cor(f.agg2[,c(5:10, 12:19)])
+#cor(f.agg2[,c(5:13, 15:24)])
 
@@
 ```
+
+Relationship between pollinator diversity, nestedness and functinal comp.
+Less diverse communities have higher levels of nestedness, hence redundancy while more diverse comm have higher levels of complementarity.
+These variables are highly correlated so analyze separately.
+Communities with greater diversity of pollinators have less fruit set!!
+Opposite to BEF relationships!!!
+the negative effect of diversty on nestedness ends up having an effect on function!
+it would be interesting to see temporal dynamics here.
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+
+m1.fr.div<-glmmTMB(mean.fruitset ~ species.poll +  (1|Plant.sp), family="gaussian", data=f.agg2)
+summary(m1.fr.div)
+
+pl.div<-ggplot(f.agg2,  aes(x=species.poll, y=mean.fruitset, color=Plant.sp))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Pollinator species diversity") +      
+        ylab("Mean fruitset") + theme_bw() +  theme(text = element_text(size = 15), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold")) + labs(col="Plant species")
+
+pl.div
+
+m1.fr.pl.div<-glmmTMB(mean.fruitset ~ species.pl +  (1|Plant.sp), family="gaussian", data=f.agg2)
+summary(m1.fr.pl.div)
+
+```
+
 #### Function as SEED NUMBER
@@
 s.agg$nodf.song<-out.site$nodf.song[match(s.agg$Site_ID, out.site$Site_id)]
+s.agg$species.poll<-out.site$species.poll[match(s.agg$Site_ID, out.site$Site_id)]
+s.agg$species.pl<-out.site$species.pl[match(s.agg$Site_ID, out.site$Site_id)]
 
@@
 # 
-# interact_plot(m2.see, pred = "functional.comp.poll", modx = "nodf.song", interval = TRUE, plot.points = TRUE, int.type = "confidence",  facet.modx = TRUE, x.label = "Functional complementarity", y.label = "Mean seed number/fruit",
+# interact_plot(m2.see, pred = "nodf.song", modx = "species.poll", interval = TRUE, plot.points = TRUE, int.type = "confidence",  facet.modx = TRUE, x.label = "Functional complementarity", y.label = "Mean seed number/fruit",
 #                modx.labels= c("Mean nestedness + 1 SD", "Mean nestedness", "Mean nestedness - 1 SD"))
@@
 # summary(lm(functional.comp.poll ~ nodf.song, data=s.agg4))$r.squared
+```
+
+Relationship between pollinator diversity AND SEED SET
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+
+m1.seed.div<-glmmTMB( mean.seednumber ~ species.poll  +  (1|Plant.sp), family="poisson", data=s.agg4)
+summary(m1.seed.div)
+
+m1.seed.pl.div<-glmmTMB( mean.seednumber ~ species.pl  +  (1|Plant.sp), family="poisson", data=s.agg4)
+summary(m1.seed.pl.div)
+
+pl.div2<-ggplot(s.agg4,  aes(x=species.pl, y=mean.seednumber, color=Plant.sp))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Plant species diversity") +      
+        ylab("Mean number of seeds/fruit") + theme_bw() +  theme(text = element_text(size = 15), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold")) + labs(col="Plant species")
+
+pl.div2
+
 ```

### 2018-11-13 paper.Rmd
more on sps diversity effects

@@
 f6$modularity<-out.site$modularity[match(f6$Site_ID, out.site$Site_id)]
+f6$species.poll<-out.site$species.poll[match(f6$Site_ID, out.site$Site_id)]
+f6$species.pl<-out.site$species.pl[match(f6$Site_ID, out.site$Site_id)]
 
@@
 pl.th2
+
+#also analyze effect of diversity
+
+m.th.poll.div<-glmmTMB(no_rows ~ species.poll , family="gaussian", data=f6)
+summary(m.th.poll.div)
+
+m.th.pl.div<-glmmTMB(no_rows ~ species.pl , family="gaussian", data=f6)
+summary(m.th.pl.div)
+
+pl.th3<-ggplot(f6,  aes(x=species.pl, y=no_rows))+      
+        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        xlab("Plant species diversity") +      
+        ylab("Evenness in fruitset") + theme_bw() + 
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
+
+pl.th3
 

### 2018-11-19 paper.Rmd
comments by nacho

--- 2018-11-13 paper.Rmd
@@
 ---
-title: "Paper"
-author: "Ainhoa Magrach"
+title: Impact of interaction network structure on community-level plant reproductive success 
+author: "Magrach, A, Molina, C, Bartomeus, I"
 date: "6 November 2018"
 output: html_document
----
-
----
-title: Impact of interaction network structure on community-level plant reproductive success 
-author: "Magrach, A & Bartomeus, I"
-date: "6 November 2018"
-output: html_document
+editor_options: 
+  chunk_output_type: console
 ---
@@
 #setwd("~/Dropbox/Beefun/Beefun/functioning")
-setwd("C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning")
+#setwd("C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning") #use rstudio projects and avoid wd issues.
+#I am uploading a Rproj. just cleick there to open it the next time.
 
@@
 
-#Fruit_Yes +  Fruit_Preyed + Fruit_Dispersed) / (Fruit_Yes + Fruit_No +Fruit_Preyed + Fruit_Dispersed) #Nacho this equation is wrong in your metadata!
+#Fruit_Yes +  Fruit_Preyed + Fruit_Dispersed) / (Fruit_Yes + Fruit_No + Fruit_Preyed + Fruit_Dispersed) #Nacho this equation is wrong in your metadata!
 
@@
 
-f2$tot.fruitset<-(f2$Fruit_Yes +  f2$Fruit_preyed + f2$Fruit_dispersed)/(f2$Fruit_Yes +f2$Fruit_No + f2$Fruit_preyed + f2$Fruit_dispersed)
+f2$tot.fruitset<-(f2$Fruit_Yes +  f2$Fruit_preyed + f2$Fruit_dispersed)/(f2$Fruit_Yes +f2$Fruit_No + f2$Fruit_preyed + f2$Fruit_dispersed) #why not use a binomial response and use both the numerator and the denominator?
+mmm...
+this will bias the estimates for plants producing larger number of seeds.
 
 s2<-subset(s, Notes %nin% wordList)
-s2$tot.seedset
+s2$tot.seedset #this variable do not exists
 
@@
 
-f.agg2<-na.omit(f.agg)
+f.agg2<-na.omit(f.agg) #you are ommiting here also NA's on SE, which is consevartive.
 #cor(f.agg2[,c(5:13, 15:24)])
@@
 
+m1.fr3<-glmmTMB(mean.fruitset ~ nodf.song + functional.comp.poll +   (1|Plant.sp), family="gaussian", data=f.agg2)
+summary(m1.fr3)
+
 #save results to table to include in paper
@@
 
-pl1
+pl1 #This suggests random slopes...
 
@@
 mp2<-subset(mp, mp$mean.fruitset!="NA")
-mp2$class[mp2$mean.fruitset>0.5]<-"high"
+mp2$class[mp2$mean.fruitset<0.75]<-"mid"
 mp2$class[mp2$mean.fruitset<0.5]<-"low"
+mp2$class[mp2$mean.fruitset>0.75]<-"high"
 
@@
 class_f <- table(mp2$class)
-
+#lots of empty positions. why?
+
+#test mcount(M = m, six_node = TRUE, normalise = TRUE)
+test <- mcount(M = webs[[1]], six_node = FALSE, normalise = TRUE)
+sum(test$nodes) #74 positions
+
+#see one position model
+plot(mp2$mean.fruitset ~ mp2$m2)
+
+pca <- prcomp(mp2[,3:48]) #there are two cases that break everything...
+biplot(pca)
+summary(pca)
+
+#Notes, before doing the NMDS wes should remove imposible positions (e.g. 1,3,5,7,... for pollinators.)
 # NMDS
-example_NMDS <- metaMDS(vegdist(mp2[,paste0("m",1:46)], method = "bray"), k=2, distance = "bray", trymax = 100)
+example_NMDS <- metaMDS(vegdist(mp2[,paste0("m",1:46)], method = "euclidian"), k=2, distance = "bray", trymax = 100)
 mds.fig <- ordiplot(example_NMDS, type = "none")
-colors=c(rep("darkorange2",class_f["low"]),rep("purple",class_f["high"]))
+colors=c(rep("yellow",class_f["low"]), rep("darkorange2",class_f["mid"]),rep("purple",class_f["high"]))
 treat <- mp2$class
@@
          "low")
+points(mds.fig, "sites", pch = 19, col = "yellow", select = mp2$class == 
+         "mid")
 points(mds.fig, "sites", pch = 19, col = "purple", select = mp2$class == 
@@
 
-#permanova
-
+#permanova... we need to control for the web, right?
+
+adonis(mp2[,3:48]~ mean.fruitset, data=mp2, method = "euclidian", strata = mp2$web)
 adonis(mp2[,3:48]~ class, data=mp2, method = "bray")
 
-#no significant differences
-
-```
+#no significant differences at all.
+
+```

### 2018-11-29 paper_round2.Rmd
new analyses following our last conversation

---
title: "Paper"
author: "Ainhoa Magrach"
date: "6 November 2018"
output: html_document
bibliography: library.bib
---

---
title: Impact of interaction network structure on community-level plant reproductive success 
author: "Magrach, A & Bartomeus, I"
date: "6 November 2018"
output: html_document
---

# ABSTRACT

Natural ecosystems across the globe are increasingly suffering from the pressures of on-going global change. Pollinators, in particular, have been reported to decline in abundance and diversity in different parts of the world, with potential implications for many plant species given the dependence of 87.5% of plant species on pollinators for reproduction. Although a strong body of research has focused on pollinator visitation frequency and plant reproduction, most of these efforts have been done at the individual species level, largely ignoring community-level implications. Indeed, interaction network structure can affect pollinator functional roles, their visitation patterns to different plant species and ultimately the pollination service they deliver to plants. Thus, a major knowledge gap at the moment is a mechanistic understanding of how pollinator visitation and the structure of plant-pollinator visitation networks affect plant reproduction. Here, we use 16 well-resolved plant-pollinator networks from Mediterranean shrub ecosystems to evaluate how pollinator species diversity, community composition and interaction network structure affect plant reproduction for 19 species of plants. Further, we link pollinator visitation frequencies with the efficiency of individual pollinator species. To this end, we use data on fruit and seed set for all plant species as well as data on the efficiency of a single visit by different pollinator species on 12 of these plant species. This work represents one of the first efforts linking pollination visitation and plant reproduction from a community-wide perspective using a well-replicated dataset.

#INTRODUCTION
POllinators provide key services to plants by facilitating pollen flow between individuals. Given recent declining trends found for some pollinator species in some regions of the planet [@Potts2010], efforts have been devoted to study the effect of decreasing pollinator diversity and abundance for plant reproduction. Many of these approaches focus on pairwise plant-pollinator interactions [doi:10.1111/1365-2745.13055]. However, community-level analyses remain to be conducted. In particular, we have some knowledge on the effect of pollinator species richness for plant reproduction for one species of plant [@Albrecht2012]. We also have an understanding of the effects of pollinator diversity and niche complementarity between pollinators for plant reproductive success within an artificially-created community of 9 plant species  [@Frund2013]. Frund et al (2013) found that greater species diversity and functional complementarity led to greater average reproduction for the plant species surveyed. However, these approaches are based on experimental research, where plant and pollinator communities are artificially recreated within enclosures and thus may not reflect real-world conditions. In addition, other aspects of community structure and trade-offs between them remain to be explored. 
Indeed, we know that the diversity of pollinators visiting a plant (the degree in network terms) and the total number of visits they provide, have an important effect for reproductive success. However, we have yet to know whether these variables contribute more to plant reproductive success than others related to the position of a particular plant species within the wider plant community that hosts it. In particular, our study focuses on the importance of pollinator diversity and total number of visits for plant reproductive success in comparison to that of the plant´s position in the community. Specifically, niche overlap between plant species (which could give us a proxy for the existence of competition for pollination between plant species) and the position of the plant given by the connections it establishes with other species, e.g. its centrality within the network, where central species are those receiving the greatest number of connections from other species, could have an influence in a plant´s reproductive success.
Furthermore, we do not know how the overall structure of a community, and the architecture of the network of interactions it hosts, affects the reproductive success of the whole community. In particular, one of the networks metrics that has received the most attention in the community ecology literature is that of nestedness. Nestedness is the property by which specialists interact with a subset of the species that generalists interact with. Although there is ongoing debate in the literature, some studies have found that more nested networks are more stable and resilient to perturbations because nestedness implies a certain level of redundancy and thus the possibility for functional replacement in the case of species loss. However, plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence. Yet at present we do not know how the interplay between redundancy and complementarity determines reproductive success.
Finally, average values of reproductive success at the community level can be driven to a large degree by one single plant species. Yet, what will determine the persistence of a diverse plant community is the presence of some sort of “equity” in reproductive success across the whole community. We thus also focus on the effect of community structure for equity in reproductive success across the plant community.
Our study aims to answer the following questions:
1) How do "pollinator visits" and "plant role" within the community affect its reproductive success? COMO LLAMAMOS A ESTO??

# METHODS

Our study was conducted in SE Spain within the area of influence of Doñana National Park?? Here, we surveyed 16 Mediterranean woodland patches. Each site was surveyed 7 times following a 100-m x 2 m transect for 30 mins. Along each transect we identified all plant species and the pollinators that legitimately visited them. In addition, within each site we evaluated fruit set, seed number per fruit and seed weight for several individuals belonging to 15 plant species. Not all plant species were present in all transects.

#DATA ANALYSES

First, we checked for sampling completeness for the pollinator and the plant community as well as for plant-pollinator links using Chao 1 asymptotic species richness estimators. We first estimated the richness of pollinators, plants and plant–pollinator links accumulated as sampling effort increased up to 100% sampling coverage using package iNEXT.

Species-level

The data for all rounds was pooled to construct one plant-pollinator interaction network per site, for which we calculated a set of relevant network metrics. At the species level, we focused on: degree (i.e., number of pollinator species visiting a particular plant), total number of visits, centrality and average niche overlap between a focal species and other plant species in the community. We fit three models, one including only the diversity of pollinator species and the total number of species. One including only metrics related to a plant´s position in the community and a third one combining both sets of models and used information criterion methods to find the best model. We included plant species nested within site as random effect to account for non-independence of several individuals measured for the same plant species.

Network level

We scaled this at the community following the same logic and evaluated the importance of pollinator diversity and visits compared to that of network structure. Including in this case nestedness and functional complementarity as metrics.
In the case of nestedness. Many approaches to measure it use null-model approaches to compare across different networks. However, this approach has the problem that z-scores depend strongly on network size and connectance as shown by this recent paper by Song et al. 
What these authors propose is to use a normalized value of nestedness, and to control by the effect of connectance and network size, thus obtaining a new value of nestedness NODFc which is independent of network size and thus comparable across different networks.

Equity in reproductive success

Finally, we used the same framework to evaluate the contribution of the different variables we consider to equity in plant reproductive success across the community, by including as a response variable the number of plant species that produce 50% of fruit set recorded for our study area at each site.

#RESULTS

Within our transects we recorded 57 species of plants and 277 species of pollinators (HAY QUE MIRAR MORFOESPECIES!).
Our sampling completeness analyses revealed that with our survey we were able to capture 18-62% of pollinator species (average= 35%), 47-98% for plant species (average= 78%) and 13-41% for plant-pollinator links (average=27%), in line with that obtained with other studies (e.g., Chacoff et al), yet slghtly smaller in the case of pollinators given the great diversity of pollinators found in the Mediterranean region in particular and in the our study area, a hotspot of insect diversity (?¿?).

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=9}

library(citr) #to include citations. use addins to insert references

#First attempt to load the data, etc...

#prepare stuff-----
#If you don't have devtools install it
#install.packages("devtools")
#library(devtools)
#Then install the data package. Reprot issues 
#install_github("ibartomeus/BeeFunData", ref = "fun")
library(BeeFunData)
library(plyr)

setwd("~/Dropbox/Beefun/Beefun/functioning")
#setwd("C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning")

d<-all_interactions
f<-fruitset
s<-seedset
si<-single_visits

d.pl<-unique(all_interactions$Plant_gen_sp)
d.poll<-unique(all_interactions$Pollinator_gen_sp)

si$Plant.sp<-paste(si$Plant_genus, si$Plant_species)

###### read network and species level files (network analyses to be found at "...scripts/network analysis.R")

outsp.pl.site<-read.csv("SITE_plant_species_level_metrics.csv")
outsp.site<-read.csv("SITE_species_level_metrics.csv")
out.site<-read.csv("SITE_network_level_metrics.csv")

#####################################################################################################################
########################CALCULATE SAMPLING COMPLETENESS FOR POLLINATORS, PLANTS AND LINKS#############################
######################################################################################################################

#POLLINATORS
d2<-table(d$Site_ID, d$Pollinator_gen_sp)
d3<-as.data.frame.array(d2)

d4 <- t(d3[,1:277])
#head(d4)
#str(d4)
d5<-as.data.frame(d4)
#str(d5)
d6<-as.list(d5)

library(iNEXT)
library(ggplot2)

rar <- iNEXT(d6, q=0, datatype="abundance", endpoint = 400)
poll<-ggiNEXT.iNEXT(rar, color.var="site", se=FALSE) + ylab("pollinators") + theme_bw() + 
  theme (legend.position= "none") + theme(text = element_text(size = 15), axis.text=element_text(size=rel(1)),
                                          axis.title.x = element_blank(),
        axis.title=element_text(size=rel(1),face="bold"), legend.direction="horizontal", legend.text=element_text(size=10))

#poll

#per site sampling completeness for pollinators
#Aznalcazar 64/103 = 0.62
#Bonares  54.000/178.701 = 0.30
#ConventodelaLuz  33.000/98.950 = 0.33
#CotitodeSantaTeresa  54.000/190.442 = 0.28
#Elpinar  29.000/158.657= 0.18
#Elpozo  32.000/174.000= 0.18
#Esparragal  39.000/110.859= 0.35
#LaCunya  32.000/118.672= 0.27
#LaRocina  74.000/147.129 = 0.50
#Lasmulas  52.000/127.295 = 0.41
#Niebla  57.000/124.792 = 0.46
#PinaresdeHinojos 40.000/168.852 = 0.24
#Pinodelcuervo  52.000/187.503 = 0.28
#Urbanizaciones  40.000/109.136 = 0.37 
#Villamanriqueeste  62.000/141.310 = 0.44
#Villamanriquesur  48.000/111.326 = 0.43

#(0.62 + 0.30 + 0.33 + 0.28 + 0.18 + 0.18 + 0.35 + 0.27 + 0.50 + 0.41 + 0.46 + 0.24 + 0.28 + 0.37 + 0.44 + 0.43)/16
#TOTAL AVERAGE sampling completeness of pollinators 0.35

#PLANTS
d.pl<-table(d$Site_ID, d$Plant_gen_sp)
d.pl2<-as.data.frame.array(d.pl)

d.pl3 <- t(d.pl2[,1:57])
#head(d.pl3)
#str(d.pl3)
d.pl4<-as.data.frame(d.pl3)
#str(d.pl4)
d.pl5<-as.list(d.pl4)

library(iNEXT)
library(ggplot2)

rar2 <- iNEXT(d.pl5, q=0, datatype="abundance", endpoint = 200)
plant<-ggiNEXT.iNEXT(rar2, color.var="site", se=FALSE) + ylab("plants") + 
  theme_bw()  + theme (legend.position= "none") + theme(text = element_text(size = 15), axis.text=element_text(size=rel(1)),
                                                         axis.title.x = element_blank(),
        axis.title=element_text(size=rel(1),face="bold"), legend.direction="horizontal", legend.text=element_text(size=10))

#plant

#per site sampling completeness for plants
#Aznalcazar 17.000/18.490 = 0.92
#Bonares  13.000/13.990 = 0.93
#ConventodelaLuz  12.000/13.978 = 0.86
#CotitodeSantaTeresa  10.000/11.973 = 0.84
#Elpinar  11.000/23.255 = 0.47
#Elpozo  11.000 /13.219 = 0.83
#Esparragal  12.000 /16.436 = 0.73
#LaCunya  13.000/21.847 = 0.60
#LaRocina  16.000 /21.959 = 0.73 
#Lasmulas  12.000 /17.940 = 0.67
#Niebla  21.000/21.743 = 0.97
#PinaresdeHinojos 14.000/21.889 = 0.64
#Pinodelcuervo  15.000/27.372 = 0.55
#Urbanizaciones  10.000 /10.247 = 0.98
#Villamanriqueeste  9.000 /10.983 = 0.82
#Villamanriquesur  12.000 /12.989 = 0.92

#(0.92 + 0.93 + 0.86 + 0.84 + 0.47 + 0.83 + 0.73 + 0.60 + 0.73 + 0.67 + 0.97 + 0.64 + 0.55 + 0.98 + 0.82 + 0.92)/16

#TOTAL AVERAGE sampling completeness of plants 0.78

#LINKS

d$link<-paste(d$Plant_gen_sp, d$Pollinator_gen_sp)
d.l<-table(d$Site_ID, d$link)
d.l2<-as.data.frame.array(d.l)

d.l3 <- t(d.l2[,1:750])
#head(d.l3)
#str(d.l3)
d.l4<-as.data.frame(d.l3)
#str(d.l4)
d.l5<-as.list(d.l4)

library(iNEXT)
library(ggplot2)

rar3 <- iNEXT(d.l5, q=0, datatype="abundance", endpoint = 500)
link<-ggiNEXT.iNEXT(rar3, color.var="site", se=FALSE) + ylab("links") + theme_bw() +
   theme (legend.position= "none") + theme(text = element_text(size = 15), axis.text=element_text(size=rel(1)),
        axis.title=element_text(size=rel(1),face="bold"), legend.direction="horizontal", legend.text=element_text(size=10))

#link

#per site sampling completeness for links
#Aznalcazar 101.000/244.145 = 0.41
#Bonares  72.000/389.031 = 0.19
#ConventodelaLuz  52.000/221.285 = 0.23
#CotitodeSantaTeresa  64.000/478.893 = 0.13
#Elpinar  37.000/194.026 = 0.19
#Elpozo   46.000/159.994 = 0.29
#Esparragal   52.000/196.900 = 0.26
#LaCunya  44.000/115.025 = 0.38
#LaRocina  98.000/351.931 = 0.28
#Lasmulas  69.000/306.883 = 0.22
#Niebla  84.000/611.776 = 0.14
#PinaresdeHinojos  56.000/186.413 = 0.30
#Pinodelcuervo   77.000/273.425 = 0.28
#Urbanizaciones  55.000/204.100 = 0.27
#Villamanriqueeste  76.000/193.208 = 0.39
#Villamanriquesur  67.000/234.221 = 0.29

#(0.41 + 0.19 + 0.23 + 0.13 + 0.19 + 0.29 + 0.26 + 0.38 + 0.28 + 0.22 + 0.14 + 0.30 + 0.28 + 0.27 + 0.39 + 0.29)/16

#TOTAL AVERAGE sampling completeness of links 0.27

library(ggplot2)
library(grid)
library(dplyr)

grid.newpage()
grid.draw(rbind(ggplotGrob(poll), ggplotGrob(plant), ggplotGrob(link), size = "last"))

```

### Species-level

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}

#compare 3 models: one with degree, i.e. diversity of partners, and number of visits, compared to one where position in a network (centrality) and niche overlap are included with these variables and a 3rd with only this network variable.

#calculate column with fruit set as
f$Plant.sp<-paste(f$Plant_genus, f$Plant_species)

#Fruit_Yes +  Fruit_Preyed + Fruit_Dispersed) / (Fruit_Yes + Fruit_No +Fruit_Preyed + Fruit_Dispersed) #Nacho this equation is wrong in your metadata!

#1st eliminate frutos perdidos
wordList <- c("fruto perdido","frutos perdidos")

require(Hmisc)
f2<-subset(f, Notes %nin% wordList)

f2$tot.fruitset<-(f2$Fruit_Yes +  f2$Fruit_preyed + f2$Fruit_dispersed)/(f2$Fruit_Yes +f2$Fruit_No + f2$Fruit_preyed + f2$Fruit_dispersed)

s2<-subset(s, Notes %nin% wordList)
s2$tot.seedset

#check correlation between different variables

#head(out.site)
#str(out.site)
c<-cor(out.site[,2:20])
c2<-round(c,digits=2)
#write.csv(c2, file= "~/Dropbox/Beefun/Beefun/functioning/tables/variable_correlations.csv", row.names = TRUE, sep = ",")

#♣correlation between weighted nodf and functional complementarity of pollinators : -0.13

#create table with number of individuals per plant species sampled at each site

#tableSx <- aggregate(Plant.ID ~ Site_ID + Plant.sp, data = f2, FUN = function(x){NROW(x)})

#write.csv(tableSx, file= "C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/plantindspersite.csv", row.names = FALSE, sep = ",")

#-------------------------------------------------------------------------------------------
#join plant species level network metrics with fruit and seed set for each site, also with niche overlap and number of visits

#calculate total number of visits per plant sps
d.vis<-ddply(d, c("Site_ID", "Plant_gen_sp"), summarise,
            tot.visits= sum(Frequency))

d.vis$j<-paste(d.vis$Site_ID, d.vis$Plant_gen_sp)

#calculate average niche overlap per species

library(reshape2)
library(spaa)
sites <- unique(d$Site_ID)

out.niche <- data.frame(Site_id = NA, row = NA, col = NA,value  = NA)

webs <- list()
for(i in 1:length(sites)){
  temp <- subset(d, Site_ID == sites[i])
  temp2<-droplevels(temp)

  web <- table(temp2$Pollinator_gen_sp, temp2$Plant_gen_sp)

  ni<-niche.overlap(web, method="morisita")
  df <- melt(as.matrix(ni), varnames = c("row", "col"))
  df$row<-as.character(df$row)
  df$col<-as.character(df$col)

  n <- nrow(out.niche)

  out.niche[n + seq(nrow(df)),1] <- as.character(sites[i])
  out.niche[n + seq(nrow(df)),2:3] <- (df[,1:2])
  out.niche[n + seq(nrow(df)),4] <-df[,3]

}

out.niche.agg <- ddply(out.niche, c("Site_id", "col"), summarise,
               mean.niche.over    = mean(value))

out.niche.agg$j<-paste(out.niche.agg$Site_id, out.niche.agg$col)

#use unaggregated data

f2$weighted_NODF<-out.site$weighted_NODF[match(f2$Site_ID, out.site$Site_id)]
f2$int_evenness<-out.site$int_evenness[match(f2$Site_ID, out.site$Site_id)]
f2$H2<-out.site$H2[match(f2$Site_ID, out.site$Site_id)]
f2$functional.comp.poll<-out.site$functional.comp.poll[match(f2$Site_ID, out.site$Site_id)]
f2$niche.overlap.plant<-out.site$niche.overlap.plant[match(f2$Site_ID, out.site$Site_id)]
f2$modularity<-out.site$modularity[match(f2$Site_ID, out.site$Site_id)]
f2$nodf.song<-out.site$nodf.song[match(f2$Site_ID, out.site$Site_id)]
f2$link_dens<-out.site$link_dens[match(f2$Site_ID, out.site$Site_id)]
f2$Shannon<-out.site$Shannon[match(f2$Site_ID, out.site$Site_id)]
f2$species.poll<-out.site$species.poll[match(f2$Site_ID, out.site$Site_id)]
f2$species.pl<-out.site$species.pl[match(f2$Site_ID, out.site$Site_id)]

#also match with plant species level network data
f2$match<-paste(f2$Site_ID, f2$Plant.sp)
outsp.pl.site$match<-paste(outsp.pl.site$Site_id, outsp.pl.site$species)

f2$norm_degree<-outsp.pl.site$norm_degree[match(f2$match, outsp.pl.site$match)]
f2$strength<-outsp.pl.site$strength[match(f2$match, outsp.pl.site$match)]
f2$nestedra<-outsp.pl.site$nestedra[match(f2$match, outsp.pl.site$match)]
f2$weigh_betweeness<-outsp.pl.site$weigh_betweeness[match(f2$match, outsp.pl.site$match)]
f2$weigh_closeness<-outsp.pl.site$weigh_closeness[match(f2$match, outsp.pl.site$match)]
f2$d<-outsp.pl.site$d[match(f2$match, outsp.pl.site$match)]
f2$c<-outsp.pl.site$c[match(f2$match, outsp.pl.site$match)]
f2$z<-outsp.pl.site$z[match(f2$match, outsp.pl.site$match)]

f2$tot.visits<-d.vis$tot.visits[match(f2$match, d.vis$j)]
f2$tot.visits[is.na(f2$tot.visits)]<-0

f2$tot.visits.sc<-((f2$tot.visits-min(f2$tot.visits))/(max(f2$tot.visits)-min(f2$tot.visits)))  #scale number of visits

f2$niche.overlap<-out.niche.agg$mean.niche.over[match(f2$match, out.niche.agg$j)]

#head(f2)

# 
# #check correlations between different species level variables
# 
# cor.test(f2[,c(31,27, 35, 37)])

library(psych)
pairs.panels(f2[,c(31,27, 35, 37)])

 library(glmmTMB)
 library(DHARMa)
 library(jtools) #plot interactions

 m1<-glmmTMB(tot.fruitset ~  norm_degree + tot.visits.sc +  (1|Site_ID) + (1|Site_ID), family="gaussian", data=f2)
 summary(m1)

 m2<-glmmTMB(tot.fruitset ~   weigh_closeness + niche.overlap  + (1|Site_ID) , family="gaussian", data=f2)
 summary(m2)

 m3<-glmmTMB(tot.fruitset ~  norm_degree  + tot.visits.sc + weigh_closeness + niche.overlap + (1|Site_ID), family="gaussian", data=f2)
 summary(m3)

library(bbmle)
AICtab(m1, m2, m3) #best model is m2

#test for problems in residuals
res<-simulateResiduals(m2)
plot(res, rank = TRUE)

pl1<-ggplot(f2,  aes(x=weigh_closeness, y=tot.fruitset, color=Plant.sp))+      
        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
        xlab("Closeness centrality") +      
        ylab("Fruitset") + theme_bw()  + #theme (legend.position= "none") +
        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")

pl1

##ahora con seed set
s$Plant.sp<-paste(s$Plant_genus, s$Plant_species)
#1st eliminate frutos perdidos
wordList <- c("fruto perdido","frutos perdidos")

require(Hmisc)

s<-subset(s, Notes %nin% wordList)

library(plyr)

s2 <- ddply(s, c("Site_ID", "Plant.sp", "Plant.ID"), summarise,
                         mean.seedn    = mean(Seeds2),
                         mean.seedweight = mean(Seed.weight),
                         mean.fruitweight= mean(Fruit.weight2))

s2$weighted_NODF<-out.site$weighted_NODF[match(s2$Site_ID, out.site$Site_id)]
s2$int_evenness<-out.site$int_evenness[match(s2$Site_ID, out.site$Site_id)]
s2$H2<-out.site$H2[match(s2$Site_ID, out.site$Site_id)]
s2$functional.comp.poll<-out.site$functional.comp.poll[match(s2$Site_ID, out.site$Site_id)]
s2$niche.overlap.plant<-out.site$niche.overlap.plant[match(s2$Site_ID, out.site$Site_id)]
s2$modularity<-out.site$modularity[match(s2$Site_ID, out.site$Site_id)]
s2$nodf.song<-out.site$nodf.song[match(s2$Site_ID, out.site$Site_id)]
s2$link_dens<-out.site$link_dens[match(s2$Site_ID, out.site$Site_id)]
s2$Shannon<-out.site$Shannon[match(s2$Site_ID, out.site$Site_id)]
s2$species.poll<-out.site$species.poll[match(s2$Site_ID, out.site$Site_id)]
s2$species.pl<-out.site$species.pl[match(s2$Site_ID, out.site$Site_id)]

#also match with plant species level network data
s2$match<-paste(s2$Site_ID, s2$Plant.sp)
outsp.pl.site$match<-paste(outsp.pl.site$Site_id, outsp.pl.site$species)

s2$norm_degree<-outsp.pl.site$norm_degree[match(s2$match, outsp.pl.site$match)]
s2$strength<-outsp.pl.site$strength[match(s2$match, outsp.pl.site$match)]
s2$nestedra<-outsp.pl.site$nestedra[match(s2$match, outsp.pl.site$match)]
s2$weigh_betweeness<-outsp.pl.site$weigh_betweeness[match(s2$match, outsp.pl.site$match)]
s2$weigh_closeness<-outsp.pl.site$weigh_closeness[match(s2$match, outsp.pl.site$match)]
s2$d<-outsp.pl.site$d[match(s2$match, outsp.pl.site$match)]
s2$c<-outsp.pl.site$c[match(s2$match, outsp.pl.site$match)]
s2$z<-outsp.pl.site$z[match(s2$match, outsp.pl.site$match)]

s2$tot.visits<-d.vis$tot.visits[match(s2$match, d.vis$j)]
s2$tot.visits[is.na(s2$tot.visits)]<-0

s2$tot.visits.sc<-((s2$tot.visits-min(s2$tot.visits))/(max(s2$tot.visits)-min(s2$tot.visits)))  #scale number of visits

s2$niche.overlap<-out.niche.agg$mean.niche.over[match(s2$match, out.niche.agg$j)]

#head(s2)

#scale seed number

s2$mean.seedn.sc<-((s2$mean.seedn-min(s2$mean.seedn))/(max(s2$mean.seedn)-min(s2$mean.seedn)))

h<-hist(s2$mean.seedn)
h2<-hist(s2$mean.seedn.sc)

 m1.seed<-glmmTMB(mean.seedn.sc ~  norm_degree + tot.visits.sc +  (1|Site_ID) + (1|Site_ID), family="poisson", data=s2)
 summary(m1.seed)

 m2.seed<-glmmTMB(mean.seedn.sc ~   weigh_closeness + niche.overlap + (1|Site_ID) , family="poisson", data=s2)
 summary(m2.seed)

m3.seed<-glmmTMB(mean.seedn.sc ~  norm_degree  + tot.visits.sc + weigh_closeness + niche.overlap + (1|Site_ID), family="poisson", data=s2)
summary(m3.seed)

library(bbmle)
AICtab(m1.seed, m2.seed, m3.seed) #best model is m2

#test for problems in residuals
res<-simulateResiduals(m2.seed)
plot(res, rank = TRUE)

pl2<-ggplot(s2,  aes(x=weigh_closeness, y=mean.seedn.sc, color=Plant.sp))+      
        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
        xlab("Closeness centrality") +      
        ylab("Seed number/fruit") + theme_bw()  + #theme (legend.position= "none") +
        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")

pl2

#try removing Cistus ladanifer with very large values

s3<-subset(s2, s2$Plant.sp!="Cistus ladanifer")

 m1.seedb<-glmmTMB(mean.seedn.sc ~  norm_degree + tot.visits.sc +  (1|Site_ID) + (1|Site_ID), family="poisson", data=s3)
 summary(m1.seedb)

 m2.seedb<-glmmTMB(mean.seedn.sc ~   weigh_closeness + niche.overlap + (1|Site_ID) , family="poisson", data=s3)
 summary(m2.seedb)

m3.seedb<-glmmTMB(mean.seedn.sc ~  norm_degree  + tot.visits.sc + weigh_closeness + niche.overlap + (1|Site_ID), family="poisson", data=s3)
summary(m3.seedb)

library(bbmle)
AICtab(m1.seedb, m2.seedb, m3.seedb) #best model is m2

pl2b<-ggplot(s3,  aes(x=weigh_closeness, y=mean.seedn.sc, color=Plant.sp))+      
        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
        xlab("Closeness centrality") +      
        ylab("Seed number/fruit") + theme_bw()  + #theme (legend.position= "none") +
        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")

pl2b

#seed weight

h<-hist(s2$mean.seedweight)

 m1.seedw<-glmmTMB(mean.seedweight ~  norm_degree + tot.visits.sc +  (1|Site_ID) , family="poisson", data=s2)
 summary(m1.seedw)

 m2.seedw<-glmmTMB(mean.seedweight ~   weigh_closeness + niche.overlap + (1|Site_ID) , family="poisson", data=s2)
 summary(m2.seedw)

m3.seedw<-glmmTMB(mean.seedweight ~  norm_degree  + tot.visits.sc + weigh_closeness + niche.overlap + (1|Site_ID), family="poisson", data=s2)
summary(m3.seedw)

library(bbmle)
AICtab(m1.seedw, m2.seedw, m3.seedw) #best model is m2

#test for problems in residuals
res<-simulateResiduals(m2.seedw)
plot(res, rank = TRUE)

#fruit weight

h<-hist(s2$mean.fruitweight)

 m1.fruitw<-glmmTMB(mean.fruitweight ~  norm_degree + tot.visits.sc +  (1|Site_ID) , family="poisson", data=s2)
 summary(m1.fruitw)

 m2.fruitw<-glmmTMB(mean.fruitweight ~   weigh_closeness + niche.overlap + (1|Site_ID) , family="poisson", data=s2)
 summary(m2.fruitw)

m3.fruitw<-glmmTMB(mean.fruitweight ~  norm_degree  + tot.visits.sc + weigh_closeness + niche.overlap + (1|Site_ID), family="poisson", data=s2)
summary(m3.fruitw)

library(bbmle)
AICtab(m1.fruitw, m2.fruitw, m3.fruitw) #best model is m2

#test for problems in residuals
res<-simulateResiduals(m2.seedw)
plot(res, rank = TRUE)

```

### Network-level
#### FRUITSET
We find that at the level of the whole communty, differences in average fruit set are driven particularly by the diversity of pollinator species. In this sense, we find that communities with greater pollinator diversity have lower values of fruit set but consistent higher values of other function aspects measured: seed number per fruit, fruit and seed weight. In contrast, we found that metrics accounting for the structure of interactions between plants and pollinators had little or no effect for functioning.

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
#####################################################################################################################
######################## NTW STRUCTURE ~ ECOSYSTEM FUNCTION #########################################################
######################################################################################################################

library(glmmTMB)
library(DHARMa)
library(MuMIn)
library(jtools) #plot interactions

library(plyr)

f.agg <- ddply(f2, c("Site_ID", "nodf.song", "functional.comp.poll", "species.poll"), summarise, tot.visits    = sum(tot.visits),
                         mean.fruitset = mean(tot.fruitset))

m1.fr<-glmmTMB(mean.fruitset ~ tot.visits + species.poll, family="gaussian", data=f.agg)
summary(m1.fr)

m2.fr<-glmmTMB(mean.fruitset ~ nodf.song +  functional.comp.poll, family="gaussian", data=f.agg)
summary(m2.fr)

m3.fr<-glmmTMB(mean.fruitset ~ tot.visits + species.poll + nodf.song +  functional.comp.poll, family="gaussian", data=f.agg)
summary(m3.fr)

library(bbmle)
AICtab(m1.fr, m2.fr, m3.fr) #best model is m2

#test for problems in residuals
res<-simulateResiduals(m1.fr)
plot(res, rank = TRUE)

pl3<-ggplot(f.agg,  aes(x=species.poll, y=mean.fruitset))+      
        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
        xlab("Pollinator species diversity") +      
        ylab("Average fruit set") + theme_bw()  + #theme (legend.position= "none") +
        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")

pl3

#seed number

library(plyr)

s.comm <- ddply(s2, c("Site_ID", "nodf.song", "functional.comp.poll", "species.poll"), summarise, tot.visits    = sum(tot.visits),
                         mean.seedset = mean(mean.seedn),
                          mean.seedweight = mean(mean.seedweight),
                          mean.fruitweight = mean(mean.fruitweight))

m1.seedcomm<-glmmTMB(mean.seedset ~ tot.visits + species.poll, family="nbinom2", data=s.comm)
summary(m1.seedcomm)

m2.seedcomm<-glmmTMB(mean.seedset ~ nodf.song +  functional.comp.poll, family="nbinom2", data=s.comm)
summary(m2.seedcomm)

m3.seedcomm<-glmmTMB(mean.seedset ~ tot.visits + species.poll + nodf.song +  functional.comp.poll, family="nbinom2", data=s.comm)
summary(m3.seedcomm)

library(bbmle)
AICtab(m1.seedcomm, m2.seedcomm, m3.seedcomm) #best model is m2

#test for problems in residuals
res<-simulateResiduals(m1.seedcomm)
plot(res, rank = TRUE)

pl4<-ggplot(s.comm,  aes(x=species.poll, y=mean.seedset))+      
        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
        xlab("Pollinator species diversity") +      
        ylab("Average number of seeds/fruit") + theme_bw()  + #theme (legend.position= "none") +
        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")

pl4

pl5<-ggplot(s.comm,  aes(x=tot.visits, y=mean.seedset))+      
        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
        xlab("Total number of visits") +      
        ylab("Average number of seeds/fruit") + theme_bw()  + #theme (legend.position= "none") +
        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")

pl5

#fruit weight

m1.fwcomm<-glmmTMB(mean.fruitweight ~ tot.visits + species.poll, family="gaussian", data=s.comm)
summary(m1.fwcomm)

m2.fwcomm<-glmmTMB(mean.fruitweight ~ nodf.song +  functional.comp.poll, family="gaussian", data=s.comm)
summary(m2.fwcomm)

m3.fwcomm<-glmmTMB(mean.fruitweight ~ tot.visits + species.poll + nodf.song +  functional.comp.poll, family="gaussian", data=s.comm)
summary(m3.fwcomm)

library(bbmle)
AICtab(m1.fwcomm, m2.fwcomm, m3.fwcomm) #best model is m2

#test for problems in residuals
res<-simulateResiduals(m1.fwcomm)
plot(res, rank = TRUE)

pl6<-ggplot(s.comm,  aes(x=species.poll, y=mean.fruitweight))+      
        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
        xlab("Pollinator species diversity") +      
        ylab("Average fruit weight") + theme_bw()  + #theme (legend.position= "none") +
        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")

pl6

#seed weight

m1.swcomm<-glmmTMB(mean.seedweight ~ tot.visits + species.poll, family="gaussian", data=s.comm)
summary(m1.swcomm)

m2.swcomm<-glmmTMB(mean.seedweight ~ nodf.song +  functional.comp.poll, family="gaussian", data=s.comm)
summary(m2.swcomm)

m3.swcomm<-glmmTMB(mean.seedweight ~ tot.visits + species.poll + nodf.song +  functional.comp.poll, family="gaussian", data=s.comm)
summary(m3.swcomm)

library(bbmle)
AICtab(m1.swcomm, m2.swcomm, m3.swcomm) #best model is m2

#test for problems in residuals
res<-simulateResiduals(m1.swcomm)
plot(res, rank = TRUE)

pl7<-ggplot(s.comm,  aes(x=species.poll, y=mean.seedweight))+      
        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
        xlab("Pollinator species diversity") +      
        ylab("Average seed weight") + theme_bw()  + #theme (legend.position= "none") +
        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")

pl7
```

### EQUITY IN FRUIT PRODUCTION

LOOK AT EVENNESSS IN FUNCTION. within a site most plant species have very low reproductive success and thus we get incredibly high evenness values. therefore we use thresholds, for each sps and site we calculate the # of individuals that are above 50% in fruit production.

AS before we find that the best model is that including the diversity of pollinator species, which has a significant positive effect on equity in fruitset.

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}

library(vegan)
library(dplyr)

f2$Plant.sp<-paste(f2$Plant_genus, f2$Plant_species)
f3<-f2[,c(1,13:14)]

f4 <- ddply(f3, c("Site_ID", "Plant.sp"), summarise,
                         mean.fruitset    = mean(tot.fruitset))

#f4

fr.max<-aggregate(.~ Plant.sp, f4, FUN=max)

f4$fruit.max<-fr.max$mean.fruitset[match(f4$Plant.sp, fr.max$Plant.sp)]

f4$fruit.prop<-f4$mean.fruitset/f4$fruit.max
f5<-subset(f4, f4$fruit.prop>0.5)
f5$no_rows<-rep(1, nrow(f5))

#for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
f6<- aggregate(no_rows ~ Site_ID, f5, length)

#join this with fruitset data used previously

f6$nodf.song<-out.site$nodf.song[match(f6$Site_ID, out.site$Site_id)]
f6$int_evenness<-out.site$int_evenness[match(f6$Site_ID, out.site$Site_id)]
f6$H2<-out.site$H2[match(f6$Site_ID, out.site$Site_id)]
f6$functional.comp.poll<-out.site$functional.comp.poll[match(f6$Site_ID, out.site$Site_id)]
f6$niche.overlap.plant<-out.site$niche.overlap.plant[match(f6$Site_ID, out.site$Site_id)]
f6$modularity<-out.site$modularity[match(f6$Site_ID, out.site$Site_id)]
f6$species.poll<-out.site$species.poll[match(f6$Site_ID, out.site$Site_id)]
f6$species.pl<-out.site$species.pl[match(f6$Site_ID, out.site$Site_id)]

f6$tot.visits<-f.agg$tot.visits[match(f6$Site_ID, f.agg$Site_ID)]

m1.eq<-glmmTMB(no_rows ~ tot.visits + species.poll, family="gaussian", data=f6)
summary(m1.eq)

m2.eq<-glmmTMB(no_rows ~ nodf.song +  functional.comp.poll, family="gaussian", data=f6)
summary(m2.eq)

m3.eq<-glmmTMB(no_rows ~ tot.visits + species.poll + nodf.song +  functional.comp.poll, family="gaussian", data=f6)
summary(m3.eq)

library(bbmle)
AICtab(m1.eq, m2.eq, m3.eq)

#test for problems in residuals
res<-simulateResiduals(m1.eq)
plot(res, rank = TRUE)

pl.th<-ggplot(f6,  aes(x=species.poll, y=no_rows))+      
        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
        xlab("Pollinator species diversity") +      
        ylab("Equity in fruitset") + theme_bw() + 
        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))

pl.th

pl.th2<-ggplot(f6,  aes(x=functional.comp.poll, y=no_rows))+      
        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
        xlab("Functional complementarity") +      
        ylab("Equity in fruitset") + theme_bw() + 
        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))

pl.th2
```

Now look at motifs and indirect interactions. To this end, we compare the roles of plant species at each site with low (<0.5) and high (>0.5) fruit set. We calculate for each plant species at each site the sum-normalised roles of all plant species in motifs up to 5 nodes and plot them using NMDS. ALthough we find a large overlap between the roles of both types ofplant species, we do find that plant species with high fruit set tend to be located in the higher values of NMDS1 which is related to network positions in which a generalist plant species interacts with highly specialized pollinator partners (e.g, positions 16 and 46, see Fig. 1 in bmotif paper, Simmons et al preprint)

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
#First attempt to load the data, etc...

#prepare stuff-----
#If you don't have devtools install it
#install.packages("devtools")
library(devtools)
#Then install the data package. Reprot issues 
#install_github("ibartomeus/BeeFunData", ref = "fun")
library(BeeFunData)

# load packages
library(bmotif)
library(vegan)

#make the data available
#analysis...----

d<-all_interactions
f<-fruitset
s<-seedset

d2<-subset(d, d$Plant_gen_sp!="NA NA")
#d2$Plant_gen_sp

sites <- unique(d2$Site_ID)

empty_web <- function(x) {
  # Removes all-zero rows and columns from a matrix
  cempty <- which(colSums(x) == 0)
  rempty <- which(rowSums(x) == 0)
  if(length(rempty) != 0 & length(cempty) == 0){
    return(x[-rempty,,drop = FALSE])
  } else if(length(rempty) == 0 & length(cempty) != 0){
    return(x[,-cempty,drop = FALSE])
  } else if(length(rempty) != 0 & length(cempty) != 0){
    return(x[-rempty,-cempty,drop = FALSE])
  } else if(length(rempty) == 0 & length(cempty) == 0){
    return(x)
  }
}

webs <- list()
webs.or3<-list()
for(i in 1:length(sites)){
  temp <- subset(d2, Site_ID == sites[i])
  # for(j in 1:length(rounds)){
  #   temp2 <- subset(temp, Round == rounds[j])
  #   if (nrow(temp2) == 0) next

  web <- as.matrix.data.frame(table(temp$Plant_gen_sp, temp$Pollinator_gen_sp))
  web.or<-table(temp$Plant_gen_sp, temp$Pollinator_gen_sp)#keeps names of species

  web2<-empty_web(web)
  web.or2<-empty_web(web.or)

  webs.or3[[i]]<-web.or2 #keeps names of species
  webs[[i]]<-as.matrix(web2)
}

names(webs)<-sites
names(webs.or3)<-sites

out <- data.frame(web = NA, nrow = NA)

#calculates number of rows in each web and then sums everything to see how many rows we need in total
for(i in 1:length(webs)){
  s<- sum(nrow(webs[[i]]))

  n<-nrow(out)
  out[n + 1,1] <- as.character(sites[i])
  out[n + 1,2] <- s

}

out<-out[-1,]
out2<-sum(out$nrow)

mp <- as.data.frame(matrix(nrow = out2, ncol = 48, dimnames = list(NULL,c("web","species",paste0("m",1:46)))))
wr <- 0
for(i in names(webs)){

    pv <- positions(webs[[i]], six_node = FALSE, level = "rows", normalisation = "sum") # calculate species positions
    start_row <- which(is.na(mp$web))[1]
    end_row <- (start_row + nrow(pv)) - 1
    wr <- start_row:end_row
    mp[wr,"web"] <- i
    mp[wr,"species"] <- rownames(webs.or3[[i]])
    mp[wr,paste0("m",1:46)] <- pv
  }

#SUBSET ONLY PLANTS FOR WHICH WE HAVE DATA ON FRUISET
#f4
f4$j<-paste(f4$Site_ID, f4$Plant.sp)

mp$j<-paste(mp$web, mp$species)

mp$mean.fruitset<-f4$mean.fruitset[match(mp$j, f4$j)]

mp2<-subset(mp, mp$mean.fruitset!="NA")
mp2$class[mp2$mean.fruitset>0.5]<-"high"
mp2$class[mp2$mean.fruitset<0.5]<-"low"

# How many native and introduced species?
mp2 <- mp2[order(mp2$class, decreasing = TRUE),]
class_f <- table(mp2$class)

# NMDS
example_NMDS <- metaMDS(vegdist(mp2[,paste0("m",1:46)], method = "bray"), k=2, distance = "bray", trymax = 100)
mds.fig <- ordiplot(example_NMDS, type = "none")
colors=c(rep("darkorange2",class_f["low"]),rep("purple",class_f["high"]))
treat <- mp2$class
for(i in unique(treat)) {
  ordihull(example_NMDS$point[grep(i,treat),],draw="polygon",
           groups=treat[treat==i],col=colors[grep(i,treat)],label=F) } 
with(mp2, legend("topright", legend = unique(mp2$class), bty = "n",
                col = unique(colors), pch = 21, pt.bg = unique(colors)))
points(mds.fig, "sites", pch = 19, col = "darkorange3", select = mp2$class == 
         "low")
points(mds.fig, "sites", pch = 19, col = "purple", select = mp2$class == 
         "high")

#example_NMDS <- metaMDS(mp2[,paste0("m",1:46)], k=2, distance = "bray", trymax = 100)
#example_NMDS$species # which positions are associated with which axes
#example_NMDS$species[order(example_NMDS$species[,"MDS2"]),]

#permanova

adonis(mp2[,3:48]~ mean.fruitset, data=mp2, method = "bray")

#no significant differences

```

### 2018-11-30 paper_round2.Rmd
changes

@@
 ---
-title: "Paper"
+title: "Paper round 2"
 author: "Ainhoa Magrach"
@@
 library(bbmle)
-AICtab(m1.seed, m2.seed, m3.seed) #best model is m2
+AICtab(m1.seed, m2.seed, m3.seed)
 
@@
 library(bbmle)
-AICtab(m1.seedb, m2.seedb, m3.seedb) #best model is m2
+AICtab(m1.seedb, m2.seedb, m3.seedb)
 
@@
 library(bbmle)
-AICtab(m1.seedw, m2.seedw, m3.seedw) #best model is m2
+AICtab(m1.seedw, m2.seedw, m3.seedw)
 
@@
 library(bbmle)
-AICtab(m1.fruitw, m2.fruitw, m3.fruitw) #best model is m2
+AICtab(m1.fruitw, m2.fruitw, m3.fruitw)
 
@@
 library(bbmle)
-AICtab(m1.fr, m2.fr, m3.fr) #best model is m2
+AICtab(m1.fr, m2.fr, m3.fr)
 
@@
 library(bbmle)
-AICtab(m1.seedcomm, m2.seedcomm, m3.seedcomm) #best model is m2
+AICtab(m1.seedcomm, m2.seedcomm, m3.seedcomm)
 
@@
 library(bbmle)
-AICtab(m1.fwcomm, m2.fwcomm, m3.fwcomm) #best model is m2
+AICtab(m1.fwcomm, m2.fwcomm, m3.fwcomm)
 
@@
 library(bbmle)
-AICtab(m1.swcomm, m2.swcomm, m3.swcomm) #best model is m2
+AICtab(m1.swcomm, m2.swcomm, m3.swcomm)
 

### 2018-12-04 paper_round2.Rmd
commit paper round 2
include FP Molina as author

@@
 ---
-title: "Paper round 2"
-author: "Ainhoa Magrach"
+title: "Paper round 2 simplified"
+author: "Magrach, A, Molina, FP, Bartomeus, I"
 date: "6 November 2018"
@@
 title: Impact of interaction network structure on community-level plant reproductive success 
-author: "Magrach, A & Bartomeus, I"
+author: "Magrach, A, Molina, FP, Bartomeus, I"
 date: "6 November 2018"
@@
 
-#no significant differences
+#permanova... we need to control for the web, right? not sure what you mean here, random effect?
+
+adonis(mp2[,3:48]~ mean.fruitset, data=mp2, method = "euclidean", strata = mp2$web)
+adonis(mp2[,3:48]~ class, data=mp2, method = "bray")
+
+#no significant differences at all.
 

### 2018-12-05 paper_round2.Rmd
temp

@@
 ---
-title: "Paper round 2 simplified"
-author: "Magrach, A, Molina, FP, Bartomeus, I"
-date: "6 November 2018"
+title: "Impact of interaction network structure on community-level plant reproductive success"
+author: "Magrach, A, Molina, C, Bartomeus, I"
 output: html_document
 bibliography: library.bib
----
-
----
-title: Impact of interaction network structure on community-level plant reproductive success 
-author: "Magrach, A, Molina, FP, Bartomeus, I"
-date: "6 November 2018"
-output: html_document
+editor_options: 
+  chunk_output_type: console
 ---
@@
 #INTRODUCTION
-POllinators provide key services to plants by facilitating pollen flow between individuals.
+Pollinators provide key services to plants by facilitating pollen flow between individuals.
 Given recent declining trends found for some pollinator species in some regions of the planet [@Potts2010], efforts have been devoted to study the effect of decreasing pollinator diversity and abundance for plant reproduction.
@@
 
-Our study was conducted in SE Spain within the area of influence of Doñana National Park??
+Our study was conducted in SE Spain within the area of influence of Doñana National Park.
 Here, we surveyed 16 Mediterranean woodland patches.
@@
 Along each transect we identified all plant species and the pollinators that legitimately visited them.
-In addition, within each site we evaluated fruit set, seed number per fruit and seed weight for several individuals belonging to 15 plant species.
+In addition, within each site we evaluated fruit set, seed number per fruit and seed weight for several individuals belonging to 15 [in abstract you menton 19]() plant species.
 Not all plant species were present in all transects.
@@
 
-Species-level
+__Species-level__
 
 The data for all rounds was pooled to construct one plant-pollinator interaction network per site, for which we calculated a set of relevant network metrics.
-At the species level, we focused on: degree (i.e., number of pollinator species visiting a particular plant), total number of visits, centrality and average niche overlap between a focal species and other plant species in the community.
+At the species level, we focused on: degree (i.e., number of pollinator species visiting a particular plant), total number of visits recieved, centrality and average niche overlap between a focal species and other plant species in the community.
 We fit three models, one including only the diversity of pollinator species and the total number of species.
@@
 We included plant species nested within site as random effect to account for non-independence of several individuals measured for the same plant species.
+[is seed set scaled across plants?]()
 
-Network level
+__Network level__
 
-We scaled this at the community following the same logic and evaluated the importance of pollinator diversity and visits compared to that of network structure.
+We followed the same logic at the community level, where we evaluated the importance of pollinator diversity and total visitation compared to that of network structure.
 Including in this case nestedness and functional complementarity as metrics.
-In the case of nestedness.
-Many approaches to measure it use null-model approaches to compare across different networks.
-However, this approach has the problem that z-scores depend strongly on network size and connectance as shown by this recent paper by Song et al.
+In the case of nestedness it is known that it can be biased by network size.
+One approach to correct for that is to use null-model and compare the null-corrcted netwedness values across different networks.
+However, this approach has the problem that the corrected z-scores values still depend on network size and connectance as shown by this recent paper by Song et al.
 What these authors propose is to use a normalized value of nestedness, and to control by the effect of connectance and network size, thus obtaining a new value of nestedness NODFc which is independent of network size and thus comparable across different networks.
@@
 
+[is seed set scaled across plants?]()
+
 #RESULTS
 
-Within our transects we recorded 57 species of plants and 277 species of pollinators (HAY QUE MIRAR MORFOESPECIES!).
-Our sampling completeness analyses revealed that with our survey we were able to capture 18-62% of pollinator species (average= 35%), 47-98% for plant species (average= 78%) and 13-41% for plant-pollinator links (average=27%), in line with that obtained with other studies (e.g., Chacoff et al), yet slghtly smaller in the case of pollinators given the great diversity of pollinators found in the Mediterranean region in particular and in the our study area, a hotspot of insect diversity (?¿?).
+Within our transects we recorded 57 species of plants and 277 species of pollinators (HAY QUE MIRAR MORFOESPECIES!
+[IB: yes, but most should be identified to species level, to unique morphospecies.
+Ask Curro.]()).
+Our sampling completeness analyses revealed that with our survey we were able to capture 18-62% of pollinator species (average= 35%), 47-98% for plant species (average= 78%) and 13-41% for plant-pollinator links (average=27%), in line with that obtained with other studies (e.g., Chacoff et al), yet slightly smaller in the case of pollinators given the great diversity of pollinators found in the Mediterranean region in particular and in the our study area, a hotspot of insect diversity (?¿?).
 
@@
  summary(m1)
+ #why (1|Site_ID) is repeated?? and plant?
 
@@
 AICtab(m1, m2, m3) #best model is m2
+#yes, but m3 is 0.6 AIC away... which is nothing...
 
@@
 #scale seed number
-
+head(s2)
 s2$mean.seedn.sc<-((s2$mean.seedn-min(s2$mean.seedn))/(max(s2$mean.seedn)-min(s2$mean.seedn))) 
+#This scaling is not working like that. 1) scale() will do that for you. 2) you need to scale each plant in turn.
+library(dplyr)
+s2 %>% 
+  group_by(Plant.sp) %>%
 
@@
  summary(m1.seed)
-
+#Ojo, AIC changes if the second (1|Site_ID) is removed.
  m2.seed<-glmmTMB(mean.seedn.sc ~   weigh_closeness + niche.overlap + (1|Site_ID) , family="poisson", data=s2)
@@
 #try removing Cistus ladanifer with very large values 
+#But this do not makes much sense, if they are scaled by species...
 

### 2018-12-05 paper_round2.Rmd
finish comenting in this.

@@
 f2$tot.visits.sc<-((f2$tot.visits-min(f2$tot.visits))/(max(f2$tot.visits)-min(f2$tot.visits)))  #scale number of visits
+head(f2)
+#why this is done? visits whould be all in the same scale already? 
+#If it is to correct for different atractiveness, you should scale as below (by plant)
+#If it is to scale the predictors and make estimates comparable, you should do that to all predictors.
 
@@
 AICtab(m1, m2, m3) #best model is m2
-#yes, but m3 is 0.6 AIC away... which is nothing...
+#yes, but m3 is 0.6 AIC away... which is nothing... and m1 with just one random is almost equal too!
 
@@
 library(dplyr)
-s2 %>% 
+s3 <- s2 %>% 
   group_by(Plant.sp) %>% 
+  mutate(mean.seedn.sc = scale(mean.seedn, center = T, scale = T))
+dim(s2)
+dim(s3)
+head(s3)
+
+#FOR TESTING PUROSES I overwrite s2
+s2 <- s3
 
@@
 
- m1.seed<-glmmTMB(mean.seedn.sc ~  norm_degree + tot.visits.sc +  (1|Site_ID) + (1|Site_ID), family="poisson", data=s2)
+ m1.seed<-glmmTMB(mean.seedn.sc ~  norm_degree + tot.visits.sc +  (1|Site_ID) + (1|Site_ID), family="gaussian", data=s2)
  summary(m1.seed)
 #Ojo, AIC changes if the second (1|Site_ID) is removed.
- m2.seed<-glmmTMB(mean.seedn.sc ~   weigh_closeness + niche.overlap + (1|Site_ID) , family="poisson", data=s2)
+ m2.seed<-glmmTMB(mean.seedn.sc ~   weigh_closeness + niche.overlap + (1|Site_ID) , family="gaussian", data=s2)
  summary(m2.seed)
 
-m3.seed<-glmmTMB(mean.seedn.sc ~  norm_degree  + tot.visits.sc + weigh_closeness + niche.overlap + (1|Site_ID), family="poisson", data=s2)
+m3.seed<-glmmTMB(mean.seedn.sc ~  norm_degree  + tot.visits.sc + weigh_closeness + niche.overlap + (1|Site_ID), family="gaussian", data=s2)
 summary(m3.seed)
@@
 library(bbmle)
-AICtab(m1.seed, m2.seed, m3.seed)
+AICtab(m1.seed, m2.seed, m3.seed) #2 is better, but all of them are pretty bad...
 
@@
 plot(res, rank = TRUE)
+#residuals good with scaled and gaussian
 
@@
 #try removing Cistus ladanifer with very large values 
-#But this do not makes much sense, if they are scaled by species...
+#But this do not makes much sense, if they are scaled by species... see above.
 
@@
 library(bbmle)
-AICtab(m1.seedw, m2.seedw, m3.seedw)
+AICtab(m1.seedw, m2.seedw, m3.seedw) #again, very similar (and bad) models.
 
@@
 ```
-
+[IB: I wonder if AIC is what we want here. Why compare models 1 and 2? One option is to present directly m3. Or m1 vs m3 maybe. I don't have a clear idea... skype?]
 ### Network-level
@@
 library(bbmle)
-AICtab(m1.fr, m2.fr, m3.fr)
+AICtab(m1.fr, m2.fr, m3.fr) #m3 is as good!!!
+##I hate models... m2 nodf is sig, m3 fc is sig!! WHY!!! colineality issues?
 
@@
 #seed number
+#How mean seed number is calculated?? scaled first would be better, right?
 
@@
 #fruit weight
+#How mean seed number is calculated?? scaled first would be better, right? At least if fruits vary in orders of magnitude.
 
@@
 f5$no_rows<-rep(1, nrow(f5))
+head(f5)
+
+#NOTE TO SELF: Here is where we want to subsample 1 to 6 species per site to test the idea of increasing plants, complementarity increase.
 
@@
 f6<- aggregate(no_rows ~ Site_ID, f5, length)
+head(f6)
 
@@
 library(bbmle)
-AICtab(m1.eq, m2.eq, m3.eq)
+AICtab(m1.eq, m2.eq, m3.eq) #m3 as good almost
 
@@
 ```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+#IB edited this in paper.Rmd
 #First attempt to load the data, etc...

### 2018-12-07 paper_round2.Rmd
n

--- 2018-12-04 paper_round2.Rmd
@@
 ---
-title: "Paper round 2 simplified"
-author: "Magrach, A, Molina, FP, Bartomeus, I"
+title: "Impact of interaction network structure on community-level plant reproduction success"
+author: "Magrach, A, Molina, C, Bartomeus, I"
 date: "6 November 2018"
@@
 bibliography: library.bib
----
-
----
-title: Impact of interaction network structure on community-level plant reproductive success 
-author: "Magrach, A, Molina, FP, Bartomeus, I"
-date: "6 November 2018"
-output: html_document
+editor options:
+  chunk_output_type: console
 ---
@@
 Thus, a major knowledge gap at the moment is a mechanistic understanding of how pollinator visitation and the structure of plant-pollinator visitation networks affect plant reproduction.
-Here, we use 16 well-resolved plant-pollinator networks from Mediterranean shrub ecosystems to evaluate how pollinator species diversity, community composition and interaction network structure affect plant reproduction for 19 species of plants.
+Here, we use 16 well-resolved plant-pollinator networks from Mediterranean shrub ecosystems to evaluate how pollinator species diversity, community composition and interaction network structure affect plant reproduction for 15 species of plants.
 Further, we link pollinator visitation frequencies with the efficiency of individual pollinator species.
@@
 In addition, other aspects of community structure and trade-offs between them remain to be explored.
+
 Indeed, we know that the diversity of pollinators visiting a plant (the degree in network terms) and the total number of visits they provide, have an important effect for reproductive success.
@@
 its centrality within the network, where central species are those receiving the greatest number of connections from other species, could have an influence in a plant´s reproductive success.
+
 Furthermore, we do not know how the overall structure of a community, and the architecture of the network of interactions it hosts, affects the reproductive success of the whole community.
@@
 We thus also focus on the effect of community structure for equity in reproductive success across the plant community.
+
 Our study aims to answer the following questions:
@@
 
-Species-level
+_Species-level_
 
 The data for all rounds was pooled to construct one plant-pollinator interaction network per site, for which we calculated a set of relevant network metrics.
-At the species level, we focused on: degree (i.e., number of pollinator species visiting a particular plant), total number of visits, centrality and average niche overlap between a focal species and other plant species in the community.
-We fit three models, one including only the diversity of pollinator species and the total number of species.
-One including only metrics related to a plant´s position in the community and a third one combining both sets of models and used information criterion methods to find the best model.
+At the species level, we focused on: degree (i.e., number of pollinator species visiting a particular plant), total number of visits received, centrality, and average niche overlap between a focal species and other plant species in the community.
+We fit three models, (i) one including only the diversity of pollinator species and the total number of species, (ii) a model including metrics related to a plant´s position in the community and (iii) a model combining both sets of models.
+We then used information criterion methods to find the best model.
 We included plant species nested within site as random effect to account for non-independence of several individuals measured for the same plant species.
 
-Network level
+_Network level_
 
-We scaled this at the community following the same logic and evaluated the importance of pollinator diversity and visits compared to that of network structure.
-Including in this case nestedness and functional complementarity as metrics.
-In the case of nestedness.
-Many approaches to measure it use null-model approaches to compare across different networks.
-However, this approach has the problem that z-scores depend strongly on network size and connectance as shown by this recent paper by Song et al.
-What these authors propose is to use a normalized value of nestedness, and to control by the effect of connectance and network size, thus obtaining a new value of nestedness NODFc which is independent of network size and thus comparable across different networks.
+We followed the same logic at the community level, where we evaluated the importance of pollinator diversity and total visitation compared to that of network structure, in this case including nestedness and functional complementarity as metrics.
+In the case of nestedness we know it can be affected by network size.
+An approach to correct for this it to use null models and to compare null-model corrected nestedness values across different networks.
+However, this approach has the problem that z-scores depend on network size and connectance as shown by this recent paper by Song et al.
+What these authors propose is to use a normalized value of nestedness, and to control by the effect of connectance and network size, thus obtaining a new value of nestedness, NODFc, which is independent of network size and thus comparable across different networks.
 
-Equity in reproductive success
+_Equity in reproductive success_
 
@@
 
-Within our transects we recorded 57 species of plants and 277 species of pollinators (HAY QUE MIRAR MORFOESPECIES!).
-Our sampling completeness analyses revealed that with our survey we were able to capture 18-62% of pollinator species (average= 35%), 47-98% for plant species (average= 78%) and 13-41% for plant-pollinator links (average=27%), in line with that obtained with other studies (e.g., Chacoff et al), yet slghtly smaller in the case of pollinators given the great diversity of pollinators found in the Mediterranean region in particular and in the our study area, a hotspot of insect diversity (?¿?).
+Within our transects we recorded 57 species of plants and 277 species of pollinators.
+Our sampling completeness analyses revealed that with our survey we were able to capture 18-62% of pollinator species (average= 35%), 47-98% for plant species (average= 78%) and 13-41% for plant-pollinator links (average=27%), in line with that obtained with other studies (e.g., Chacoff et al), yet slightly smaller in the case of pollinators given the great diversity of pollinators found in the Mediterranean region in particular and in the our study area, a hotspot of insect diversity.
 
@@
 library(plyr)
-
-setwd("~/Dropbox/Beefun/Beefun/functioning")
-#setwd("C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning")
 
@@
 
-f2$tot.visits.sc<-((f2$tot.visits-min(f2$tot.visits))/(max(f2$tot.visits)-min(f2$tot.visits)))  #scale number of visits
-
 f2$niche.overlap<-out.niche.agg$mean.niche.over[match(f2$match, out.niche.agg$j)]
@@
 
- m1<-glmmTMB(tot.fruitset ~  norm_degree + tot.visits.sc +  (1|Site_ID) + (1|Site_ID), family="gaussian", data=f2)
+ m1<-glmmTMB(tot.fruitset ~  norm_degree + tot.visits  + (1|Plant.sp/Site_ID) , family="gaussian", data=f2)
  summary(m1)
 
- m2<-glmmTMB(tot.fruitset ~   weigh_closeness + niche.overlap  + (1|Site_ID) , family="gaussian", data=f2)
+ m2<-glmmTMB(tot.fruitset ~   weigh_closeness + niche.overlap  + (1|Plant.sp/Site_ID) , family="gaussian", data=f2)
  summary(m2)
 
- m3<-glmmTMB(tot.fruitset ~  norm_degree  + tot.visits.sc + weigh_closeness + niche.overlap + (1|Site_ID), family="gaussian", data=f2)
+ m3<-glmmTMB(tot.fruitset ~  norm_degree  + tot.visits + weigh_closeness + niche.overlap + (1|Plant.sp/Site_ID), family="gaussian", data=f2)
  summary(m3)
@@
 library(bbmle)
-AICtab(m1, m2, m3) #best model is m2
+AICtab(m1, m2, m3)
 
@@
 
-s2$tot.visits.sc<-((s2$tot.visits-min(s2$tot.visits))/(max(s2$tot.visits)-min(s2$tot.visits)))  #scale number of visits
+s2$tot.visits.sc<-scale(s2$tot.visits) #scale number of visits
 
@@
 
-s2$mean.seedn.sc<-((s2$mean.seedn-min(s2$mean.seedn))/(max(s2$mean.seedn)-min(s2$mean.seedn)))
+library(dplyr)
+s2_scaled <- s2 %>% group_by(Plant.sp) %>% mutate(mean.seedn = scale(mean.seedn, center = T, scale = T))
 
-h<-hist(s2$mean.seedn)
-h2<-hist(s2$mean.seedn.sc)
+h<-hist(s2_scaled$mean.seedn)
 
- m1.seed<-glmmTMB(mean.seedn.sc ~  norm_degree + tot.visits.sc +  (1|Site_ID) + (1|Site_ID), family="poisson", data=s2)
+ m1.seed<-glmmTMB(mean.seedn ~  norm_degree + tot.visits.sc +  (1|Plant.sp/Site_ID), family="gaussian", data=s2_scaled)
  summary(m1.seed)
 
- m2.seed<-glmmTMB(mean.seedn.sc ~   weigh_closeness + niche.overlap + (1|Site_ID) , family="poisson", data=s2)
+ m2.seed<-glmmTMB(mean.seedn ~   weigh_closeness + niche.overlap + (1|Plant.sp/Site_ID) , family="gaussian", data=s2_scaled)
  summary(m2.seed)
 
-m3.seed<-glmmTMB(mean.seedn.sc ~  norm_degree  + tot.visits.sc + weigh_closeness + niche.overlap + (1|Site_ID), family="poisson", data=s2)
+m3.seed<-glmmTMB(mean.seedn ~  norm_degree  + tot.visits.sc + weigh_closeness + niche.overlap + (1|Plant.sp/Site_ID), family="gaussian", data=s2_scaled)
 summary(m3.seed)
@@
 
-pl2<-ggplot(s2,  aes(x=weigh_closeness, y=mean.seedn.sc, color=Plant.sp))+      
+pl2<-ggplot(s2_scaled,  aes(x=weigh_closeness, y=mean.seedn, color=Plant.sp))+      
         geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
@@
 
-#try removing Cistus ladanifer with very large values
-
-s3<-subset(s2, s2$Plant.sp!="Cistus ladanifer")
-
- m1.seedb<-glmmTMB(mean.seedn.sc ~  norm_degree + tot.visits.sc +  (1|Site_ID) + (1|Site_ID), family="poisson", data=s3)
- summary(m1.seedb)
-
- m2.seedb<-glmmTMB(mean.seedn.sc ~   weigh_closeness + niche.overlap + (1|Site_ID) , family="poisson", data=s3)
- summary(m2.seedb)
-
-m3.seedb<-glmmTMB(mean.seedn.sc ~  norm_degree  + tot.visits.sc + weigh_closeness + niche.overlap + (1|Site_ID), family="poisson", data=s3)
-summary(m3.seedb)
-
-library(bbmle)
-AICtab(m1.seedb, m2.seedb, m3.seedb)
-
-pl2b<-ggplot(s3,  aes(x=weigh_closeness, y=mean.seedn.sc, color=Plant.sp))+      
-        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
-        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
-        xlab("Closeness centrality") +      
-        ylab("Seed number/fruit") + theme_bw()  + #theme (legend.position= "none") +
-        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
-
-pl2b
-
 #seed weight
@@
 
- m1.seedw<-glmmTMB(mean.seedweight ~  norm_degree + tot.visits.sc +  (1|Site_ID) , family="poisson", data=s2)
+ m1.seedw<-glmmTMB(mean.seedweight ~  norm_degree + tot.visits +  (1|Plant.sp/Site_ID) , family="poisson", data=s2)
  summary(m1.seedw)
 
- m2.seedw<-glmmTMB(mean.seedweight ~   weigh_closeness + niche.overlap + (1|Site_ID) , family="poisson", data=s2)
+ m2.seedw<-glmmTMB(mean.seedweight ~   weigh_closeness + niche.overlap + (1|Plant.sp/Site_ID) , family="poisson", data=s2)
  summary(m2.seedw)
 
-m3.seedw<-glmmTMB(mean.seedweight ~  norm_degree  + tot.visits.sc + weigh_closeness + niche.overlap + (1|Site_ID), family="poisson", data=s2)
+m3.seedw<-glmmTMB(mean.seedweight ~  norm_degree  + tot.visits.sc + weigh_closeness + niche.overlap + (1|Plant.sp/Site_ID), family="poisson", data=s2)
 summary(m3.seedw)
@@
 
- m1.fruitw<-glmmTMB(mean.fruitweight ~  norm_degree + tot.visits.sc +  (1|Site_ID) , family="poisson", data=s2)
+ m1.fruitw<-glmmTMB(mean.fruitweight ~  norm_degree + tot.visits +  (1|Plant.sp/Site_ID) , family="poisson", data=s2)
  summary(m1.fruitw)
 
- m2.fruitw<-glmmTMB(mean.fruitweight ~   weigh_closeness + niche.overlap + (1|Site_ID) , family="poisson", data=s2)
+ m2.fruitw<-glmmTMB(mean.fruitweight ~   weigh_closeness + niche.overlap + (1|Plant.sp/Site_ID) , family="poisson", data=s2)
  summary(m2.fruitw)
 
-m3.fruitw<-glmmTMB(mean.fruitweight ~  norm_degree  + tot.visits.sc + weigh_closeness + niche.overlap + (1|Site_ID), family="poisson", data=s2)
+m3.fruitw<-glmmTMB(mean.fruitweight ~  norm_degree  + tot.visits + weigh_closeness + niche.overlap + (1|Plant.sp/Site_ID), family="poisson", data=s2)
 summary(m3.fruitw)

### 2018-12-13 scripts/path analysis.R
included a path analysis for fruitset at species and community level to show indirect interactions between variables.

@@ -1,0 +1,76 @@
+
+
+library(lavaan)
+library(semPlot)
+library(OpenMx)
+library(tidyverse)
+library(knitr)
+library(kableExtra)
+library(GGally)
+
+# Organizing package information for table
+packages <- c("tidyverse", "knitr", "kableExtra", "lavaan", "semPlot", "OpenMx", "GGally")
+display <- c("Package","Title", "Maintainer", "Version", "URL")
+table <- matrix(NA, 1, NROW(display), dimnames = list(1, display))
+for(i in 1:NROW(packages)){
+  list <- packageDescription(packages[i])
+  table <- rbind(table, matrix(unlist(list[c(display)]), 1, NROW(display), byrow = T))
+}
+table[,NROW(display)] <- stringr::str_extract(table[,NROW(display)], ".+,")
+
+# Table of packages
+kable(table[-1,], format = "html", align = "c") %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+
+
+
+#species level 
+
+
+model <-'
+tot.fruitset ~ norm_degree.sc  + tot.visits.sc + 
+weigh_closeness.sc + niche.overlap.sc
+'
+
+
+fit <- cfa(model, data = f2_scaled)
+summary(fit, fit.measures = TRUE, standardized=T,rsquare=T)
+
+semPaths(fit, 'std', layout = 'circle')
+
+semPaths(fit,"std",layout = 'tree', edge.label.cex=.9, curvePivot = TRUE)
+
+
+
+ggcorr(f2_scaled[,c(14, 26:29)], nbreaks = 6, label = T, low = "red3", high = "green3", 
+       label_round = 2, name = "Correlation Scale", label_alpha = T, hjust = 0.75) +
+  ggtitle(label = "Correlation Plot") +
+  theme(plot.title = element_text(hjust = 0.6))
+
+
+
+
+
+#community level
+
+model <-'
+mean.fruitset ~ species.poll.sc + tot.visits.sc + nodf.song.sc + 
+functional.comp.poll.sc
+'
+
+
+fit <- cfa(model, data = f.agg)
+summary(fit, fit.measures = TRUE, standardized=T,rsquare=T)
+
+semPaths(fit, 'std', layout = 'circle')
+
+semPaths(fit,"std",layout = 'tree', edge.label.cex=.9, curvePivot = TRUE)
+
+
+
[…]

### 2018-12-13 scripts/path analysis.R
include equity in path analysis

@@ -69,8 +69,22 @@ semPaths(fit,"std",layout = 'tree', edge.label.cex=.9, curvePivot = TRUE)
 
 
 
-ggcorr(f2_scaled[,c(14, 26:29)], nbreaks = 6, label = T, low = "red3", high = "green3", 
-       label_round = 2, name = "Correlation Scale", label_alpha = T, hjust = 0.75) +
-  ggtitle(label = "Correlation Plot") +
-  theme(plot.title = element_text(hjust = 0.6))
 
+
+#equity
+
+
+
+
+model <-'
+no_rows ~ species.poll.sc + tot.visits.sc + nodf.song.sc + 
+functional.comp.poll.sc
+'
+
+
+fit <- cfa(model, data = f6)
+summary(fit, fit.measures = TRUE, standardized=T,rsquare=T)
+
+semPaths(fit, 'std', layout = 'circle')
+
+semPaths(fit,"std",layout = 'tree', edge.label.cex=.9, curvePivot = TRUE)

### 2018-12-27 scripts/path analysis.R
last changes path analysis

@@ -65,7 +65,7 @@ summary(fit, fit.measures = TRUE, standardized=T,rsquare=T)
 
 semPaths(fit, 'std', layout = 'circle')
 
-semPaths(fit,"std",layout = 'tree', edge.label.cex=.9, curvePivot = TRUE)
+semPaths(fit,"std",layout = 'tree', edge.label.cex=1.5, curvePivot = TRUE)
 
 
 
@@ -74,17 +74,16 @@ semPaths(fit,"std",layout = 'tree', edge.label.cex=.9, curvePivot = TRUE)
 #equity
 
 
-
+f6red <- f6[, c(1:2, 7:10)]
+colnames(f6red) <- c("Site", "Eq", "N", "F", "D", "V")
 
 model <-'
-no_rows ~ species.poll.sc + tot.visits.sc + nodf.song.sc + 
-functional.comp.poll.sc
-'
+Eq ~ D + V + N + F'
 
 
-fit <- cfa(model, data = f6)
+fit <- cfa(model, data = f6red)
 summary(fit, fit.measures = TRUE, standardized=T,rsquare=T)
 
 semPaths(fit, 'std', layout = 'circle')
 
-semPaths(fit,"std",layout = 'tree', edge.label.cex=.9, curvePivot = TRUE)
+semPaths(fit,"std",layout = 'tree', edge.label.cex=1.5, curvePivot = TRUE)

### 2019-01-17 paper_round2.Rmd
Started writing paper in its pseudo final form. Questions for equity, now calculated as proportion and all results disappear. ALso for simulation. SHouldn't we do the same with both network variables and not just for equity but also for average rep success??

@@
 title: "Impact of interaction network structure on community-level plant reproduction success"
-author: "Magrach, A, Molina, C, Bartomeus, I"
+author: "Magrach, A, Molina, FP, Bartomeus, I"
 date: "6 November 2018"
@@
 
+------------------------------------------------------------------------------------------------
+To be potentially submitted to ECOLOGY LETTERS as a Letter: maximum of 5000 words and 6 figures, tables or text boxes. 
+The abstract page should contain a short summary not exceeding 150 words for Letters.
+
+III. Main text (Sections b-d required for Letters only)
+(a) Introduction. The introduction should summarize briefly the background and aims, and end with a very brief statement of what has been achieved by the work.
+
+(b) Material and methods.
+This section should contain sufficient detail so that all procedures can be repeated (in conjunction with cited references).
+A checklist is provided so that authors can check that their methods report details which our editors regard as essential.
+This checklist is available here.
+Where specific equipment and materials are named, the manufacturer's name, city and country should be given (generally in parentheses after first mention).
+
+(c) Results.
+The Results section should present the experiments that support the conclusions to be drawn later in the Discussion.
+The Results section should conform to a high standard of rigour.
+Extended lines of inference, arguments or speculations should not be placed in the Results.
+
+(d) Discussion.
+The Discussion section should be separate from the Results section.
+It allows authors to propose their interpretation of the results, and to suggest what they might mean in a wider context.
+It should end with a clear statement of the main conclusions of the research, and a clear explanation of their importance and relevance.
+
+(e) Acknowledgements. Acknowledgements should be brief and concise.
+
+(f) References. See below for detailed information to in-text citations and Reference list.]
+
+---------------------------------------------------------------------------------------------------------
+
+Title: Impact of interaction network structure on community-level plant reproduction success
+
+Ainhoa Magrach, Francisco de Paula Molina, Ignasi Bartomeus
+
+Short running title: Network structure effects on function
+
+Keywords: nestedness, functional complementary, fruitset, pollination, plant-pollinator interaction
+
+Type of article: Letter
+
+Words in Abstract: 149 words
+
+Words in main text (excluding abstract, acknowledgements, references, table and figure legends):
+
+Words in text boxes:
+
+Number of references:
+
+Number of figures, tables and text boxes:
+
+Corresponding author: ainhoa.magrach@bc3research.org, nacho.bartomeus@gmail.com
+
 # ABSTRACT
 
-Natural ecosystems across the globe are increasingly suffering from the pressures of on-going global change.
-Pollinators, in particular, have been reported to decline in abundance and diversity in different parts of the world, with potential implications for many plant species given the dependence of 87.5% of plant species on pollinators for reproduction.
-Although a strong body of research has focused on pollinator visitation frequency and plant reproduction, most of these efforts have been done at the individual species level, largely ignoring community-level implications.
-Indeed, interaction network structure can affect pollinator functional roles, their visitation patterns to different plant species and ultimately the pollination service they deliver to plants.
-Thus, a major knowledge gap at the moment is a mechanistic understanding of how pollinator visitation and the structure of plant-pollinator visitation networks affect plant reproduction.
-Here, we use 16 well-resolved plant-pollinator networks from Mediterranean shrub ecosystems to evaluate how pollinator species diversity, community composition and interaction network structure affect plant reproduction for 15 species of plants.
-Further, we link pollinator visitation frequencies with the efficiency of individual pollinator species.
-To this end, we use data on fruit and seed set for all plant species as well as data on the efficiency of a single visit by different pollinator species on 12 of these plant species.
-This work represents one of the first efforts linking pollination visitation and plant reproduction from a community-wide perspective using a well-replicated dataset.
+Declines in pollinator diversity and abundance have been reported across different regions, with implications for the reproductive success of many plant species.
+However, research has targeted the consequences for individual plant species, particularly focusing on pairwise plant-pollinator interactions, and largely overlooking community-level dynamics.
+Yet species do not interact in isolation, they are embedded within larger networks whose structure can affect pollinator functional roles and, ultimately, the pollination service they deliver to plants.
+Here, we present one of the first efforts linking pollinator visitation and plant reproduction from a community-wide perspective using a well-replicated dataset encompassing 16 well-resolved networks and data on reproductive success for 19 plant species from Mediterranean shrub ecosystems.
+We find that for prediction purposes, information on simple visitation metrics is sufficient.
+Contrastingly, a mechanisitic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success, requires additional information on network structure.
 
 #INTRODUCTION
+
 Pollinators provide key services to plants by facilitating pollen flow between individuals.
-Given recent declining trends found for some pollinator species in some regions of the planet [@Potts2010], efforts have been devoted to study the effect of decreasing pollinator diversity and abundance for plant reproduction.
-Many of these approaches focus on pairwise plant-pollinator interactions [doi:10.1111/1365-2745.13055].
-However, community-level analyses remain to be conducted.
-In particular, we have some knowledge on the effect of pollinator species richness for plant reproduction for one species of plant [@Albrecht2012].
-We also have an understanding of the effects of pollinator diversity and niche complementarity between pollinators for plant reproductive success within an artificially-created community of 9 plant species  [@Frund2013].
-Frund et al (2013) found that greater species diversity and functional complementarity led to greater average reproduction for the plant species surveyed.
-However, these approaches are based on experimental research, where plant and pollinator communities are artificially recreated within enclosures and thus may not reflect real-world conditions.
-In addition, other aspects of community structure and trade-offs between them remain to be explored.
-
-Indeed, we know that the diversity of pollinators visiting a plant (the degree in network terms) and the total number of visits they provide, have an important effect for reproductive success.
-However, we have yet to know whether these variables contribute more to plant reproductive success than others related to the position of a particular plant species within the wider plant community that hosts it.
-In particular, our study focuses on the importance of pollinator diversity and total number of visits for plant reproductive success in comparison to that of the plant´s position in the community.
-Specifically, niche overlap between plant species (which could give us a proxy for the existence of competition for pollination between plant species) and the position of the plant given by the connections it establishes with other species, e.g.
-its centrality within the network, where central species are those receiving the greatest number of connections from other species, could have an influence in a plant´s reproductive success.
-
-Furthermore, we do not know how the overall structure of a community, and the architecture of the network of interactions it hosts, affects the reproductive success of the whole community.
-In particular, one of the networks metrics that has received the most attention in the community ecology literature is that of nestedness.
-Nestedness is the property by which specialists interact with a subset of the species that generalists interact with.
-Although there is ongoing debate in the literature, some studies have found that more nested networks are more stable and resilient to perturbations because nestedness implies a certain level of redundancy and thus the possibility for functional replacement in the case of species loss.
-However, plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence.
-Yet at present we do not know how the interplay between redundancy and complementarity determines reproductive success.
-Finally, average values of reproductive success at the community level can be driven to a large degree by one single plant species.
-Yet, what will determine the persistence of a diverse plant community is the presence of some sort of “equity” in reproductive success across the whole community.
-We thus also focus on the effect of community structure for equity in reproductive success across the plant community.
-
-Our study aims to answer the following questions:
-1) How do "pollinator visits" and "plant role" within the community affect its reproductive success? COMO LLAMAMOS A ESTO??
+The recent declining trends found for some pollinator species in some regions of the planet ([@Potts2010], although see [@Herrera2018] for opposite trends), have led many researchers to focus on the functional impacts of these changes in pollinator diversity, with a major focus being placed on the consequences for plant reproductive success [@Biesmeijer2006].
+
+Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012a; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain differences found  across different plant individuals.
+Some have gone a step further by including information on the efficiency of these visits, thus adding a measure of quality to the pollination services (REF).
+Contrastingly, community-level analyses remain scarce [@Bennett2018].
+Yet plants and pollinators do not interact in isolation, but rather are embedded within larger networks of interactions encompassing other plant and pollinator species.
+We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect ones between species within one guild (e.g., plants) through their shared resources [@Lazaro2014].
+Understanding how changes in pollinator diversity affect whole plant assemblages is thus a major challenge that requires attention.
+
+The few pollination studies that have analysed the effects of changing pollinator diversity for reproductive success at the community level, have done so using mainly experimental setups.
+As an example, a study that experimentally recreated a plant community with 9 plant species and differing levels of pollinator diversity across different enclosures, found that not only pollinator species diversity had an effect for average reproductive success, but also they found that the structure that shaped the community had an important effect [@Frund2013].
+In particular, these authors found that functional complementarity between pollinators, in terms of plant species and temperature coverage (a measure of the overlap in the use of plant resources and optimum temperature activity) had a positive effect for average seed set at the community level [@Frund2013].
+This provides added information on the effects of biodiversity for ecosystem functioning, suggesting that not only the diversity of species present but also the diversity of roles and ways in which a community is structured are determinant factors.
+
+Indeed, theoretical research has long suggested that the structure of a community has an effect for ecosystem functioning (reviewed in [@Thompson2012]).
+This line of research, primarliy driven by food-web studies, has greatly advanced theory, but these ideas have not yet been tested with empirical data.
+Specifically, a major knowledge gap resides in understading which aspects of structure determine which aspects of function [@Thompson2012].
+We are now at a point in which there is considerable understanding on the attributes of interaction networks (REF, REF, REF).
+Even further, we now have a substantial understanding of how these attributes vary along different types of gradients [@Pellissier2017; @Tylianakis2016].
+Especially, in the case of pollination, we have ample knowledge on the attributes that shape these mutualistic interactions at the community level, such as a prevalence of nested structures (REF) or the presence of asymmetric specialization as a pervasive feature [@Vazquez2004].
+The time is thus ripe to use this knowledge to explore relationships between community structure and ecosystem functioning, with special emphasis being placed on the underlying mechanisms that drive these relationships.
+
+Here, we present one of the first efforts linking pollinator visitation and plant reproductive success at the community level.
+To this end, we use a well-replicated dataset encompassing 16 well-resolved networks coupled with data on the reproductive success of 19 plant species recorded at Mediterranean shrub ecosystems within the area of influence of Doñana National Park in SW Spain.
+Our study focuses on understanding whether adding information on the structure of the community to previously-used simple visitation metrics (e.g., number of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success.
+In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive succes.
+
+Our results suggest that for prediction purposes, information on simple visitation metrics, particularly regarding the diversity of pollinators that visit a plant species, is sufficient.
+However, we find that a mechanisitic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success requires additional information on network structure, notably information on the complementarity between the functions performed by different pollinator species.
 
@@
 
-Our study was conducted in SE Spain within the area of influence of Doñana National Park.
-Here, we surveyed 16 Mediterranean woodland patches.
-Each site was surveyed 7 times following a 100-m x 2 m transect for 30 mins.
-Along each transect we identified all plant species and the pollinators that legitimately visited them.
-In addition, within each site we evaluated fruit set, seed number per fruit and seed weight for several individuals belonging to 15 plant species.
-Not all plant species were present in all transects.
+_Plant pollinator interactions_
+
+Our study was conducted in SW Spain within the area of influence of Doñana National Park (Figure 1?).
+Here, we surveyed 16 Mediterranean woodland patches, located within a XXX m2 area and with an average distance of XX km between them (min= XX, max= XX).
+[SHOULD WE SAY SOMETHING ABOUT THE MATRIX SURROUNDING THESE SITES OR THE TYPE OF VEGETATION PRESENT IN THEM???] Each site was surveyed 7 times during the flowering season of 2015??
+(February-July???) following a 100-m x 2 m transect for 30 mins.
+Along each transect, we identified all plant species and recorded all the flower visitors (IS IT JUST BEES AND HOVERFLIES?) that legitimately visited them.
+Floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FdPM with the aid of experts in the different taxonomic groups (see acknowledgements).
+All surveys were done under similar weather conditions, avoiding windy or rainy days.
+
+_Plant reproductive success_
+
+Within each site, we marked between 2 and 12 individuals (6.49 +- 2.37) of 1 to 6 plant species (4.06 +- 1.69), depending on availability and presence of flowers during the first sampling event.
+For each individual, we counted the number of flowers at the beginning of the season and recorded fruit set, the number of seeds per fruit (for 2-36 fruits, 11.17 +- 6.84) and average seed weight at the end of the season???.
+Our survey included a total of 19 plant species across our 16 sites.
 
@@
 
-First, we checked for sampling completeness for the pollinator and the plant community as well as for plant-pollinator links using Chao 1 asymptotic species richness estimators.
-We first estimated the richness of pollinators, plants and plant–pollinator links accumulated as sampling effort increased up to 100% sampling coverage using package iNEXT.
-
-_Species-level_
-
-The data for all rounds was pooled to construct one plant-pollinator interaction network per site, for which we calculated a set of relevant network metrics.
-At the species level, we focused on: degree (i.e., number of pollinator species visiting a particular plant), total number of visits received, centrality, and average niche overlap between a focal species and other plant species in the community.
-We fit three models, (i) one including only the diversity of pollinator species and the total number of species, (ii) a model including metrics related to a plant´s position in the community and (iii) a model combining both sets of models.
-We then used information criterion methods to find the best model.
-We included plant species nested within site as random effect to account for non-independence of several individuals measured for the same plant species.
-
-_Network level_
-
-We followed the same logic at the community level, where we evaluated the importance of pollinator diversity and total visitation compared to that of network structure, in this case including nestedness and functional complementarity as metrics.
-In the case of nestedness we know it can be affected by network size.
-An approach to correct for this it to use null models and to compare null-model corrected nestedness values across different networks.
-However, this approach has the problem that z-scores depend on network size and connectance as shown by this recent paper by Song et al.
-What these authors propose is to use a normalized value of nestedness, and to control by the effect of connectance and network size, thus obtaining a new value of nestedness, NODFc, which is independent of network size and thus comparable across different networks.
-
-_Equity in reproductive success_
-
-Finally, we used the same framework to evaluate the contribution of the different variables we consider to equity in plant reproductive success across the community, by including as a response variable the number of plant species that produce 50% of fruit set recorded for our study area at each site.
+In order to evaluate the completeness of our sampling of the pollinator and plant community as well as that of their interactions, we estimated the asymptotic number of species present, including non-detected species, and calculated the proportion detected with our original sampling data.
+We used Chao 1 asymptotic species richness estimators [@Chao2009] and estimated the richness of pollinators, plants and plant–pollinator links accumulated as sampling effort increased up to 100% sampling coverage using package iNEXT [@Hsieh2016] within the R environment [@RDevelopmentCoreTeam2011].
+We then extracted the values covered by our sampling.
+
+In order to analyse how differences within the pollinator community might affect plant reproductive success, we constructed weighted interaction networks by pooling the data for the 7 rounds of sampling.
+We thus obtained one weighted interaction network per site representing the frequency of visits by different pollinator species to different plant species.
+For each network we then proceeded to extract a series of relevant network metrics.
+
+_Species-level network analysis_
+
+At the species level, we focused on attributes defining the position of a focal plant species within the larger community.
+As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap between a focal species and other plant species in the community, which covers the potential indirect interactions between different plant species through shared resources (in this case pollinators), and (ii) centrality, which depicts the importance of the plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness.
+
+_Community-level network analysis_
+
+At the community level, we followed the same logic as the one presented at the species level.
+Thus, we also calculated two network metrics providing complementary non-redundant information.
+In this case we focused on (i) nestedness and (ii) functional complementarity.
+Nestedness is the property by which specialists interact with a subset of the species that generalists interact with (REF).
+Although there is an ongoing debate in the literature, some studies have found that nested networks are more stable and resilient to perturbations because nestedness implies a certain level of redundancy and thus the possibility for functional replacement in the case of species loss (REF).
+However, plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence (reviewed in [@Brosi2016]).
+Yet at present we do not know how the interplay between redundancy and complementarity in species roles determines reproductive success.
+
+Many network attributes vary with network size and complexity [@Bluthgen2006].
+In the case of nestedness, we know it can be affected by network size and connectance (REF).
+An approach that is often used to correct for this, is to use null models and to compare null-model corrected nestedness values across different networks.
+However, this approach has been recently shown to present the same issues, as z-scores also change with network size and connectance [@Song2017].
+Given the dependence of nestedness on network size and connectance, we followed the advice of these researchers by using a normalized value of nestedness, NODFc, which is independent of network size and thus comparable across different networks [@Song2017].
+All network metrics were calculated using package bipartite [@Dormann2009].
+
+_Statistical analyses_
+
+In order to evaluate whether adding information on community structure improves our ability to explain differences in reproductive success both at the species and the community level, we used general linear (GLM) and general linear mixed models (GLMM).
+In both cases (species and community-level models) we fit two types of models: (i) model 1, that only included simple visitation metrics and (ii) model 2, that additionally included information on community structure.
+
+At the species level, model 1 included as explanatory variables the diversity of pollinator species visiting a focal plant and the total number of visits received by that plant species; while model 2, added the two network attributes calculated at the species level: average niche overlap and centrality.
+In this case, we included plant species nested within site as a random effect to account for non-independence of several individuals measured for the same plant species within each site.
+The diversity of pollinator species visiting a focal plant was approximated using the plant´s normalised degree, i.e., the number of links with different pollinator species a plant has, scaled by the number of possible partners [@Dormann2009].
+
+At the community level, we upscaled our species-level analyses.
+In this case, model 1 included total pollinator diversity and the total number of visits received by all plants within the community as explanatory variables.
+Model 2, in turn, added information on community structure by including nestedness and functional complementarity as explanatory variables.
+
+Average values of reproductive success at the community level can be driven to a large extent by one single plant species.
+Yet, what will determine the persistence of a diverse plant community, is the presence of some sort of “equity” in reproductive success across the whole community.
+We therefore calculated a measure of equity in reproductive success at the community level as the proportion of plant species within a site that is at 50% of the maximum value of fruitset recorded for that plant species within our sampling.
+We repeated this using 25% and 75% thresholds.
+We then used the same framework as before and fit the same model 1 and model 2 as those used at the community level but using equity in reproductive success as the response variable.
+
+We used information criterion methods to find the best model for each case and selected the ones with the lowest Akaike Information Criterion (AIC) value.
+Differences in AIC values < 2, were not considered enough to select one model over the other.
+
+_Simulating the effect of community structure as sample size increases_
+
+Finally, we tested whether the effect of community structure metrics increases with the number of plant species whose reproductive success is being considered.
+We expect that when only one plant species is considered, then the effect of community structure will be negligible.
+Further, we expect this effect to increase in importance as more plant species are considered (up to a maximum number of 6 species which is the maximum we have measured in our study).
+
+To test this, we ran a simple simulation in which the number of species increases randomly (increases randomly or the identity of the sps is selected at random???) at each time step and calculate equity in reproductive success.
+Instead of drawing plants randomly for each run, for each plant number level and network, we test all possible combinations, as this number is low (n = 63 possible combiations overall for the network with the largest dataset) and increasing sampling events in our simulation would only result in repeated combinations.
+Then, we test the overall relation between equity in reproductive success and both community-level network metrics we consider: nestedness and functional complementarity within our simulated communities.
+To this end, for each species number level, we randomly combine the generated equity values across the 16 communities as to obtain one random value per species.
+Finally, for each of such combinations we calculated the estimate of equity in relation with functional complementarity and average all estimates from 1000 simulated combinations per number of plants considered.
+We expect that the more plants considered, the larger the resulting average estimates will be.
+Note that we only interpret the mean effects, as the variance among different plant number of species depends on the initial number of combinations.
 
@@
 
-Within our transects we recorded 57 species of plants and 277 species of pollinators.
-Our sampling completeness analyses revealed that with our survey we were able to capture 18-62% of pollinator species (average= 35%), 47-98% for plant species (average= 78%) and 13-41% for plant-pollinator links (average=27%), in line with that obtained with other studies (e.g., Chacoff et al), yet slightly smaller in the case of pollinators given the great diversity of pollinators found in the Mediterranean region in particular and in the our study area, a hotspot of insect diversity.
+Within our sampling we recorded 57 species of plants and 277 species of pollinators. Within the pollinator community XX% of species were solitary bees, XX% hoverflies and XX%% other??
+
+Our sampling completeness analyses revealed that with our survey we were able to capture 18-62% of pollinator species (average= 35%), 47-98% for plant species (average= 78%) and 13-41% for plant-pollinator links (average=27%), in line with that obtained with other studies (e.g., [@Chacoff2012], Figure S1?).
+Our values of sampling completeness are slightly smaller in the case of pollinators probably as a consequence of the great diversity found in the Mediterranean region and within our study area in particular, a hotspot of insect diversity (REF).
 
@@
 s<-seedset
-si<-single_visits
+
+#calculate number of plant and pollinator species in total in our sampling
 
@@
 
-si$Plant.sp<-paste(si$Plant_genus, si$Plant_species)
+#calculate number of plant species per site, number of individuals per plant species and number of fruits per ind surveyed for repr succ
+
+library(plyr)
+
+f$Plant.sp<-paste(f$Plant_genus, f$Plant_species)
+
+f.inds<-ddply(f, c("Site_ID", "Plant.sp"), summarise, 
+                   tot.inds = length(Plant.sp)) #number of individuals per plant sps
+
+#write.csv(f.inds, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/plantindspersite.csv", row.names = FALSE)
+
+mean<-mean(f.inds$tot.inds)
+stdev<-sd(f.inds$tot.inds)
+
+f.sps<-ddply(f.inds, c("Site_ID"), summarise, 
+                   tot.sps = length(Site_ID)) #number of plant sps per site
+
+#write.csv(f.sps, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/plantspspersite.csv", row.names = FALSE)
+
+mean2<-mean(f.sps$tot.sps)
+stdev2<-sd(f.sps$tot.sps)
+
+s$Plant.sp<-paste(s$Plant_genus, s$Plant_species)
+
+s.fruitnum<-ddply(s, c("Site_ID", "Plant.sp"), summarise, 
+                   tot.fruits = length(Plant.ID)) #number of fruits per individual
+
+#write.csv(s.fruitnum, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/fruitnumberperplantindspersite.csv", row.names = FALSE)
+
+mean3<-mean(s.fruitnum$tot.fruits)
+stdev3<-sd(s.fruitnum$tot.fruits)
 
@@
 #####################################################################################################################
-########################CALCULATE SAMPLING COMPLETENESS FOR POLLINATORS, PLANTS AND LINKS#############################
+########################CALCULATE SAMPLING COMPLETENESS FOR POLLINATORS, PLANTS AND LINKS #############################
 ######################################################################################################################
+
+library(iNEXT)
+library(ggplot2)
+library(grid)
 
@@
 
-library(iNEXT)
-library(ggplot2)
-
 rar <- iNEXT(d6, q=0, datatype="abundance", endpoint = 400)
-poll<-ggiNEXT.iNEXT(rar, color.var="site", se=FALSE) + ylab("pollinators") + theme_bw() + 
+poll<-ggiNEXT.iNEXT(rar, color.var="site", se=FALSE) + ylab("Pollinator species richness") + theme_bw() + 
   theme (legend.position= "none") + theme(text = element_text(size = 15), axis.text=element_text(size=rel(1)),
                                           axis.title.x = element_blank(),
-        axis.title=element_text(size=rel(1),face="bold"), legend.direction="horizontal", legend.text=element_text(size=10))
+        axis.title=element_text(size=rel(1),face="bold"), legend.direction="horizontal", legend.text=element_text(size=10)) +
+  scale_color_manual(values=c("#F1BB7B", "#FD6467", "#5B1A18", "#D67236", "#E6A0C4", "#C6CDF7", "#D8A499", "#7294D4", "#D8B70A", "#02401B", "#A2A475", "#81A88D", "#972D15", "#9C964A", "#CDC08C", "#FAD77B"))
 
@@
 
-library(iNEXT)
-library(ggplot2)
-
 rar2 <- iNEXT(d.pl5, q=0, datatype="abundance", endpoint = 200)
-plant<-ggiNEXT.iNEXT(rar2, color.var="site", se=FALSE) + ylab("plants") + 
+plant<-ggiNEXT.iNEXT(rar2, color.var="site", se=FALSE) + ylab("Plant species richness") + 
   theme_bw()  + theme (legend.position= "none") + theme(text = element_text(size = 15), axis.text=element_text(size=rel(1)),
                                                          axis.title.x = element_blank(),
-        axis.title=element_text(size=rel(1),face="bold"), legend.direction="horizontal", legend.text=element_text(size=10))
+        axis.title=element_text(size=rel(1),face="bold"), legend.direction="horizontal", legend.text=element_text(size=10)) +
+  scale_color_manual(values=c("#F1BB7B", "#FD6467", "#5B1A18", "#D67236", "#E6A0C4", "#C6CDF7", "#D8A499", "#7294D4", "#D8B70A", "#02401B", "#A2A475", "#81A88D", "#972D15", "#9C964A", "#CDC08C", "#FAD77B"))
 
@@
 
-library(iNEXT)
-library(ggplot2)
-
 rar3 <- iNEXT(d.l5, q=0, datatype="abundance", endpoint = 500)
-link<-ggiNEXT.iNEXT(rar3, color.var="site", se=FALSE) + ylab("links") + theme_bw() +
+link<-ggiNEXT.iNEXT(rar3, color.var="site", se=FALSE) + ylab("Link richness") + theme_bw() +
    theme (legend.position= "none") + theme(text = element_text(size = 15), axis.text=element_text(size=rel(1)),
-        axis.title=element_text(size=rel(1),face="bold"), legend.direction="horizontal", legend.text=element_text(size=10))
+        axis.title=element_text(size=rel(1),face="bold"), legend.direction="horizontal", legend.text=element_text(size=10)) +
+ scale_color_manual(values=c("#F1BB7B", "#FD6467", "#5B1A18", "#D67236", "#E6A0C4", "#C6CDF7", "#D8A499", "#7294D4", "#D8B70A", "#02401B", "#A2A475", "#81A88D", "#972D15", "#9C964A", "#CDC08C", "#FAD77B"))
 
@@
 
-library(ggplot2)
-library(grid)
-library(dplyr)
-
 grid.newpage()
@@
 
-### Species-level
+### Species-level analyses
+
+At the species level, our results show that for all measures of reproductive success considered (i.e., fruitset, number of seeds per fruit, fruit and seed weight), the best model based on its AIC value was model 1, i.e., the model that only includes simple visitation metrics (i.e., the diversity of visiting pollinators and the total number of visits received by a focal plant species).
+In the case of fruitset, we find a positive effect of the diversity of species visiting a focal plant species (measured using the species´normalised degree, Fig.
+XX).
+Contrastingly, for seed set, fruit and seed weight we find that none of the variables included within our model explain the differences observed.
 
@@
 
-#compare 3 models: one with degree, i.e.
-diversity of partners, and number of visits, compared to one where position in a network (centrality) and niche overlap are included with these variables and a 3rd with only this network variable.
+#compare 2 models: one with degree, i.e. diversity of partners, and number of visits, compared to one where position in a network (centrality) and niche overlap are included with these variables.
 
@@
 f2$tot.fruitset<-(f2$Fruit_Yes +  f2$Fruit_preyed + f2$Fruit_dispersed)/(f2$Fruit_Yes +f2$Fruit_No + f2$Fruit_preyed + f2$Fruit_dispersed)
-
-s2<-subset(s, Notes %nin% wordList)
-s2$tot.seedset
 
@@
 library(spaa)
+library(plyr)
+
 sites <- unique(d$Site_ID)
@@
 
-f2$weighted_NODF<-out.site$weighted_NODF[match(f2$Site_ID, out.site$Site_id)]
-f2$int_evenness<-out.site$int_evenness[match(f2$Site_ID, out.site$Site_id)]
-f2$H2<-out.site$H2[match(f2$Site_ID, out.site$Site_id)]
 f2$functional.comp.poll<-out.site$functional.comp.poll[match(f2$Site_ID, out.site$Site_id)]
-f2$niche.overlap.plant<-out.site$niche.overlap.plant[match(f2$Site_ID, out.site$Site_id)]
-f2$modularity<-out.site$modularity[match(f2$Site_ID, out.site$Site_id)]
 f2$nodf.song<-out.site$nodf.song[match(f2$Site_ID, out.site$Site_id)]
-f2$link_dens<-out.site$link_dens[match(f2$Site_ID, out.site$Site_id)]
-f2$Shannon<-out.site$Shannon[match(f2$Site_ID, out.site$Site_id)]
 f2$species.poll<-out.site$species.poll[match(f2$Site_ID, out.site$Site_id)]
-f2$species.pl<-out.site$species.pl[match(f2$Site_ID, out.site$Site_id)]
 
@@
 f2$norm_degree<-outsp.pl.site$norm_degree[match(f2$match, outsp.pl.site$match)]
-f2$strength<-outsp.pl.site$strength[match(f2$match, outsp.pl.site$match)]
-f2$nestedra<-outsp.pl.site$nestedra[match(f2$match, outsp.pl.site$match)]
-f2$weigh_betweeness<-outsp.pl.site$weigh_betweeness[match(f2$match, outsp.pl.site$match)]
 f2$weigh_closeness<-outsp.pl.site$weigh_closeness[match(f2$match, outsp.pl.site$match)]
-f2$d<-outsp.pl.site$d[match(f2$match, outsp.pl.site$match)]
-f2$c<-outsp.pl.site$c[match(f2$match, outsp.pl.site$match)]
-f2$z<-outsp.pl.site$z[match(f2$match, outsp.pl.site$match)]
+f2$niche.overlap<-out.niche.agg$mean.niche.over[match(f2$match, out.niche.agg$j)]
 
@@
 
-f2$niche.overlap<-out.niche.agg$mean.niche.over[match(f2$match, out.niche.agg$j)]
-
-#head(f2)
+#scale all variables used
+
+f2$functional.comp.poll.sc<-scale(f2$functional.comp.poll, center = T, scale = T)
+f2$nodf.song.sc<-scale(f2$nodf.song, center = T, scale = T)
+f2$species.poll.sc<-scale(f2$species.poll, center = T, scale = T)
+
+f2$norm_degree.sc<-scale(f2$norm_degree, center = T, scale = T)
+f2$weigh_closeness.sc<-scale(f2$weigh_closeness, center = T, scale = T)
+f2$niche.overlap.sc<-scale(f2$niche.overlap, center = T, scale = T)
+
+#scale total visits per plant species
+library(dplyr)
+f2_scaled <- f2 %>% group_by(Plant.sp) %>% mutate(tot.visits.sc = scale(tot.visits, center = T, scale = T))
 
@@
 # 
-# cor.test(f2[,c(31,27, 35, 37)])
+#cor(f2[,23:29])
 
 library(psych)
-pairs.panels(f2[,c(31,27, 35, 37)])
-
- library(glmmTMB)
- library(DHARMa)
- library(jtools) #plot interactions
-
- m1<-glmmTMB(tot.fruitset ~  norm_degree + tot.visits  + (1|Plant.sp/Site_ID) , family="gaussian", data=f2)
+dim(f2)
+pairs.panels(f2[,23:28])
+
+#fit models 1 and 2
+
+library(lme4)
+library(lmerTest) #to calculate coeff and p values
+library(car) #to calculate VIF
+library(bbmle)  #to select best model based on AIC
+library(ggplot2)
+library(DHARMa) #to check for problems in residuals
+
+ m1<-glmer(tot.fruitset ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=f2_scaled)
+
  summary(m1)
 
- m2<-glmmTMB(tot.fruitset ~   weigh_closeness + niche.overlap  + (1|Plant.sp/Site_ID) , family="gaussian", data=f2)
+ vif(m1)  #check for correlations between variables included in model
+
+ m2<-glmer(tot.fruitset ~  norm_degree.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=f2_scaled)
+
  summary(m2)
 
- m3<-glmmTMB(tot.fruitset ~  norm_degree  + tot.visits + weigh_closeness + niche.overlap + (1|Plant.sp/Site_ID), family="gaussian", data=f2)
- summary(m3)
-
-library(bbmle)
-AICtab(m1, m2, m3)
+ vif(m2)
+
+#select best model based on AIC
+
+AICtab(m1, m2)
 
 #test for problems in residuals
-res<-simulateResiduals(m2)
-plot(res, rank = TRUE)
-
-pl1<-ggplot(f2,  aes(x=weigh_closeness, y=tot.fruitset, color=Plant.sp))+      
+
+# res<-simulateResiduals(m1)
+# plot(res, rank = TRUE)
+
+# extract coefficients and p-values for m1 and present them in paper
+coefs.m1 <- data.frame(coef(summary(m1)))
+# use normal distribution to approximate p-value
+coefs.m1$p.z <- 2 * (1 - pnorm(abs(coefs.m1$t.value)))
+coefs.m1
+summ<-round(coefs.m1,digits=2)
+#write.csv(summ, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsfruitsetSPECIES.csv", row.names = TRUE)
+
+#best model is m1, plot significant variable, in this case degree
+
+pl1<-ggplot(f2_scaled,  aes(x=norm_degree.sc, y=tot.fruitset, color=Plant.sp)) +    
         geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
-        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
-        xlab("Closeness centrality") +      
-        ylab("Fruitset") + theme_bw()  + #theme (legend.position= "none") +
-        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
+        #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Normalized degree") +      
+        ylab("Fruitset") + theme_bw()  + theme (legend.position= c(0.85,0.3)) +
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species") +  theme(legend.text = element_text(size = 10, face = "italic"), legend.title = element_text(size=11, face = "bold"))
 
@@
 
+#no color for different species
+
+pl1b<-ggplot(f2_scaled,  aes(x=norm_degree.sc, y=tot.fruitset)) +    
+        geom_point(size=4, color = "darkgrey") + geom_smooth(method=lm,  size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Normalized degree") +      
+        ylab("Fruitset") + theme_bw()  + theme (legend.position= "none") +
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
+
+pl1b
+
 ##ahora con seed set
+
 s$Plant.sp<-paste(s$Plant_genus, s$Plant_species)
+
 #1st eliminate frutos perdidos
@@
 require(Hmisc)
-
-s<-subset(s, Notes %nin% wordList)
-
+s2<-subset(s, Notes %nin% wordList)
+
+#calculate average seed set per plant individual, there are several fruit measurements per plant and would lead to 3 nested random factors
 library(plyr)
 
-s2 <- ddply(s, c("Site_ID", "Plant.sp", "Plant.ID"), summarise,
+s3 <- ddply(s2, c("Site_ID", "Plant.sp", "Plant.ID"), summarise,
                          mean.seedn    = mean(Seeds2),
-                         mean.seedweight = mean(Seed.weight),
-                         mean.fruitweight= mean(Fruit.weight2))
-
-s2$weighted_NODF<-out.site$weighted_NODF[match(s2$Site_ID, out.site$Site_id)]
-s2$int_evenness<-out.site$int_evenness[match(s2$Site_ID, out.site$Site_id)]
-s2$H2<-out.site$H2[match(s2$Site_ID, out.site$Site_id)]
-s2$functional.comp.poll<-out.site$functional.comp.poll[match(s2$Site_ID, out.site$Site_id)]
-s2$niche.overlap.plant<-out.site$niche.overlap.plant[match(s2$Site_ID, out.site$Site_id)]
-s2$modularity<-out.site$modularity[match(s2$Site_ID, out.site$Site_id)]
-s2$nodf.song<-out.site$nodf.song[match(s2$Site_ID, out.site$Site_id)]
-s2$link_dens<-out.site$link_dens[match(s2$Site_ID, out.site$Site_id)]
-s2$Shannon<-out.site$Shannon[match(s2$Site_ID, out.site$Site_id)]
-s2$species.poll<-out.site$species.poll[match(s2$Site_ID, out.site$Site_id)]
-s2$species.pl<-out.site$species.pl[match(s2$Site_ID, out.site$Site_id)]
+                          mean.seedw = mean(Seed.weight),
+                          mean.fruitweight = mean(Fruit.weight2))
+
+#use unaggregated data
+
+s3$functional.comp.poll<-out.site$functional.comp.poll[match(s3$Site_ID, out.site$Site_id)]
+s3$nodf.song<-out.site$nodf.song[match(s3$Site_ID, out.site$Site_id)]
+s3$species.poll<-out.site$species.poll[match(s3$Site_ID, out.site$Site_id)]
 
 #also match with plant species level network data
-s2$match<-paste(s2$Site_ID, s2$Plant.sp)
+s3$match<-paste(s3$Site_ID, s3$Plant.sp)
 outsp.pl.site$match<-paste(outsp.pl.site$Site_id, outsp.pl.site$species)
 
-s2$norm_degree<-outsp.pl.site$norm_degree[match(s2$match, outsp.pl.site$match)]
-s2$strength<-outsp.pl.site$strength[match(s2$match, outsp.pl.site$match)]
-s2$nestedra<-outsp.pl.site$nestedra[match(s2$match, outsp.pl.site$match)]
-s2$weigh_betweeness<-outsp.pl.site$weigh_betweeness[match(s2$match, outsp.pl.site$match)]
-s2$weigh_closeness<-outsp.pl.site$weigh_closeness[match(s2$match, outsp.pl.site$match)]
-s2$d<-outsp.pl.site$d[match(s2$match, outsp.pl.site$match)]
-s2$c<-outsp.pl.site$c[match(s2$match, outsp.pl.site$match)]
-s2$z<-outsp.pl.site$z[match(s2$match, outsp.pl.site$match)]
-
-s2$tot.visits<-d.vis$tot.visits[match(s2$match, d.vis$j)]
-s2$tot.visits[is.na(s2$tot.visits)]<-0
-
-s2$tot.visits.sc<-scale(s2$tot.visits) #scale number of visits
-
-s2$niche.overlap<-out.niche.agg$mean.niche.over[match(s2$match, out.niche.agg$j)]
-
-#head(s2)
-
-#scale seed number
-
+s3$norm_degree<-outsp.pl.site$norm_degree[match(s3$match, outsp.pl.site$match)]
+s3$weigh_closeness<-outsp.pl.site$weigh_closeness[match(s3$match, outsp.pl.site$match)]
+s3$niche.overlap<-out.niche.agg$mean.niche.over[match(s3$match, out.niche.agg$j)]
+
+s3$tot.visits<-d.vis$tot.visits[match(s3$match, d.vis$j)]
+s3$tot.visits[is.na(s3$tot.visits)]<-0
+
+#scale all variables used
+
+s3$functional.comp.poll.sc<-scale(s3$functional.comp.poll, center = T, scale = T)
+s3$nodf.song.sc<-scale(s3$nodf.song, center = T, scale = T)
+s3$species.poll.sc<-scale(s3$species.poll, center = T, scale = T)
+
+s3$norm_degree.sc<-scale(s3$norm_degree, center = T, scale = T)
+s3$weigh_closeness.sc<-scale(s3$weigh_closeness, center = T, scale = T)
+s3$niche.overlap.sc<-scale(s3$niche.overlap, center = T, scale = T)
+
+#scale total visits per plant species
 library(dplyr)
-s2_scaled <- s2 %>% group_by(Plant.sp) %>% mutate(mean.seedn = scale(mean.seedn, center = T, scale = T))
-
-h<-hist(s2_scaled$mean.seedn)
-
- m1.seed<-glmmTMB(mean.seedn ~  norm_degree + tot.visits.sc +  (1|Plant.sp/Site_ID), family="gaussian", data=s2_scaled)
+s3_scaled <- s3 %>% group_by(Plant.sp) %>% mutate(tot.visits.sc = scale(tot.visits, center = T, scale = T))
+
+s4_scaled <- s3_scaled %>% group_by(Plant.sp) %>% mutate(mean.seedn.sc = scale(mean.seedn, center = T, scale = T))
+
+#fit two models
+
+m1.seed<-glmer(mean.seedn.sc ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s4_scaled)
+
 summary(m1.seed)
 
- m2.seed<-glmmTMB(mean.seedn ~   weigh_closeness + niche.overlap + (1|Plant.sp/Site_ID) , family="gaussian", data=s2_scaled)
+vif(m1.seed)
+
+m2.seed<-glmer(mean.seedn.sc ~  norm_degree.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s4_scaled)
+
 summary(m2.seed)
 
-m3.seed<-glmmTMB(mean.seedn ~  norm_degree  + tot.visits.sc + weigh_closeness + niche.overlap + (1|Plant.sp/Site_ID), family="gaussian", data=s2_scaled)
-summary(m3.seed)
-
-library(bbmle)
-AICtab(m1.seed, m2.seed, m3.seed)
+vif(m2.seed)
+
+AICtab(m1.seed, m2.seed)
 
 #test for problems in residuals
-res<-simulateResiduals(m2.seed)
-plot(res, rank = TRUE)
-
-pl2<-ggplot(s2_scaled,  aes(x=weigh_closeness, y=mean.seedn, color=Plant.sp))+      
-        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
-        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
-        xlab("Closeness centrality") +      
-        ylab("Seed number/fruit") + theme_bw()  + #theme (legend.position= "none") +
-        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
-
-pl2
-
-#seed weight
-
-h<-hist(s2$mean.seedweight)
-
- m1.seedw<-glmmTMB(mean.seedweight ~  norm_degree + tot.visits +  (1|Plant.sp/Site_ID) , family="poisson", data=s2)
- summary(m1.seedw)
-
- m2.seedw<-glmmTMB(mean.seedweight ~   weigh_closeness + niche.overlap + (1|Plant.sp/Site_ID) , family="poisson", data=s2)
- summary(m2.seedw)
-
-m3.seedw<-glmmTMB(mean.seedweight ~  norm_degree  + tot.visits.sc + weigh_closeness + niche.overlap + (1|Plant.sp/Site_ID), family="poisson", data=s2)
-summary(m3.seedw)
-
-library(bbmle)
-AICtab(m1.seedw, m2.seedw, m3.seedw)
+# res<-simulateResiduals(m1.seed)
+# plot(res, rank = TRUE)
+
+# extract coefficients and p-values for m1 and present them in paper
+coefs.m1.seed <- data.frame(coef(summary(m1.seed)))
+# use normal distribution to approximate p-value
+coefs.m1.seed$p.z <- 2 * (1 - pnorm(abs(coefs.m1.seed$t.value)))
+coefs.m1.seed
+summ.seed<-round(coefs.m1.seed,digits=2)
+#write.csv(summ.seed, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsseedsetSPECIES.csv", row.names = TRUE)
+
+#SEED WEIGHT
+
+m1.seed.w<-glmer(mean.seedw ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s3_scaled)
+
+summary(m1.seed.w)
+
+vif(m1.seed.w)
+
+m2.seed.w<-glmer(mean.seedw ~  norm_degree.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s3_scaled)
+
+summary(m2.seed.w)
+
+vif(m2.seed.w)
+
+#select best model based on AIC
+
+AICtab(m1.seed.w, m2.seed.w)
 
 #test for problems in residuals
-res<-simulateResiduals(m2.seedw)
-plot(res, rank = TRUE)
-
-#fruit weight
-
-h<-hist(s2$mean.fruitweight)
-
- m1.fruitw<-glmmTMB(mean.fruitweight ~  norm_degree + tot.visits +  (1|Plant.sp/Site_ID) , family="poisson", data=s2)
- summary(m1.fruitw)
-
- m2.fruitw<-glmmTMB(mean.fruitweight ~   weigh_closeness + niche.overlap + (1|Plant.sp/Site_ID) , family="poisson", data=s2)
- summary(m2.fruitw)
-
-m3.fruitw<-glmmTMB(mean.fruitweight ~  norm_degree  + tot.visits + weigh_closeness + niche.overlap + (1|Plant.sp/Site_ID), family="poisson", data=s2)
-summary(m3.fruitw)
-
-library(bbmle)
-AICtab(m1.fruitw, m2.fruitw, m3.fruitw)
+# res<-simulateResiduals(m1.seed.w)
+# plot(res, rank = TRUE)
+
+# extract coefficients and p-values for m1 and present them in paper
+coefs.m1.seed.w <- data.frame(coef(summary(m1.seed.w)))
+# use normal distribution to approximate p-value
+coefs.m1.seed.w$p.z <- 2 * (1 - pnorm(abs(coefs.m1.seed.w$t.value)))
+coefs.m1.seed.w
+summ.seed.w<-round(coefs.m1.seed.w,digits=2)
+#write.csv(summ.seed.w, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsseedweightSPECIES.csv", row.names = TRUE)
+
+#FRUIT WEIGHT
+
+m1.fruit.w<-glmer(mean.fruitweight ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s3_scaled)
+
+summary(m1.fruit.w)
+
+vif(m1.fruit.w)
+
+m2.fruit.w<-glmer(mean.fruitweight ~  norm_degree.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s3_scaled)
+
+summary(m2.fruit.w)
+
+vif(m2.fruit.w)
+
+#select best model based on AIC
+
+AICtab(m1.fruit.w, m2.fruit.w)
 
 #test for problems in residuals
-res<-simulateResiduals(m2.seedw)
-plot(res, rank = TRUE)
+# res<-simulateResiduals(m1.fruit.w)
+# plot(res, rank = TRUE)
+
+# extract coefficients and p-values for m1 and present them in paper
+coefs.m1.fruit.w <- data.frame(coef(summary(m1.fruit.w)))
+# use normal distribution to approximate p-value
+coefs.m1.fruit.w$p.z <- 2 * (1 - pnorm(abs(coefs.m1.fruit.w$t.value)))
+coefs.m1.fruit.w
+summ.fruit.w<-round(coefs.m1.fruit.w,digits=2)
+#write.csv(summ.seed.w, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsfruitweightSPECIES.csv", row.names = TRUE)
 
@@
 
-### Network-level
-#### FRUITSET
-We find that at the level of the whole communty, differences in average fruit set are driven particularly by the diversity of pollinator species.
-In this sense, we find that communities with greater pollinator diversity have lower values of fruit set but consistent higher values of other function aspects measured: seed number per fruit, fruit and seed weight.
-In contrast, we found that metrics accounting for the structure of interactions between plants and pollinators had little or no effect for functioning.
+### Network-level analyses
+
+At the network level, we find different patterns for fruitset and the number of seeds per fruit as compared to those for fruit and seed weight.
+In the case of fruitset and the number of seeds per fruit we find that the best model describing the differences observed is model 2, i.e., that including community-level network attributes in addition to simple visitation metrics.
+In particular, we find that fruitset is positively related to functional complementarity, while we find a similar yet marginal and non-significant trend in the case of the number of seeds per fruit.
+Additionally, we find a negative effect of community-level pollinator species diversity on average fruitset.
+Contrastingly, in the case of weight variables (fruit and seed weight), in both cases we find that the best model is model 1, i.e., that only including simple visitation metrics.
+Here, we find a consistent positive effect of community-level pollinator diversity for both weight descriptors.
 
@@
 
-library(glmmTMB)
-library(DHARMa)
-library(MuMIn)
-library(jtools) #plot interactions
-
 library(plyr)
-
-f.agg <- ddply(f2, c("Site_ID", "nodf.song", "functional.comp.poll", "species.poll"), summarise, tot.visits    = sum(tot.visits),
+#this is how i did originally, average of everything together, now following Nacho´s advice changing to mean of means previously calculated per sps
+
+f.agg.prev <- ddply(f2, c("Site_ID", "nodf.song", "functional.comp.poll", "species.poll"), 
+                    summarise, tot.visits    = sum(tot.visits),
                          mean.fruitset = mean(tot.fruitset))
 
-m1.fr<-glmmTMB(mean.fruitset ~ tot.visits + species.poll, family="gaussian", data=f.agg)
-summary(m1.fr)
-
-m2.fr<-glmmTMB(mean.fruitset ~ nodf.song +  functional.comp.poll, family="gaussian", data=f.agg)
-summary(m2.fr)
-
-m3.fr<-glmmTMB(mean.fruitset ~ tot.visits + species.poll + nodf.song +  functional.comp.poll, family="gaussian", data=f.agg)
-summary(m3.fr)
-
-library(bbmle)
-AICtab(m1.fr, m2.fr, m3.fr)
+#I see what you mean, no weghting for plant species... maybe is good doing it... mean on means? I don't think it will change much the result.
+#Doing mean of means here, it does change some values a bit!!
+f.ag <- ddply(f2, c("Site_ID", "Plant.sp", "nodf.song", "functional.comp.poll", "species.poll"), 
+               summarise, tot.visits    = sum(tot.visits),
+                         mean.fruitset = mean(tot.fruitset))
+
+f.agg <- ddply(f.ag, c("Site_ID",  "nodf.song", "functional.comp.poll", "species.poll"), 
+               summarise, tot.visits    = sum(tot.visits),
+                         mean.fruitset = mean(mean.fruitset))
+
+#scale all variables to be able to compare effect sizes
+
+f.agg$nodf.song.sc <- scale(f.agg$nodf.song, center = T, scale = T)
+f.agg$functional.comp.poll.sc <- scale(f.agg$functional.comp.poll, center = T, scale = T)
+f.agg$species.poll.sc <- scale(f.agg$species.poll, center = T, scale = T)
+f.agg$tot.visits.sc <- scale(f.agg$tot.visits, center = T, scale = T)
+
+#average FRUITset
+
+m1.fruit.net<-glm(mean.fruitset ~  species.poll.sc + tot.visits.sc, family="gaussian", data=f.agg)
+
+summary(m1.fruit.net)
+
+vif(m1.fruit.net)
+
+m2.fruit.net<-glm(mean.fruitset ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="gaussian", data=f.agg)
+
+#note estimate of niche part do not overlap zero 0.06105  +-  0.03637 and it's moderatelly big.
+
+summary(m2.fruit.net)
+
+vif(m2.fruit.net)
+
+#select best model based on AIC
+
+AICtab(m1.fruit.net, m2.fruit.net) #Almost as good.
+The take home message would be.
+If interested in predictions, go for simplicity.
+If interested in mechanisms, nich part is a mechanism to take into account.
+
+#when changing values to mean of means actually model2 is best and funct compl is significant!! YUHUUUU
+
+#save table with results for paper
+summ.fruit.net<-round(summary(m2.fruit.net)$coef, digits=2)
+#write.csv(summ.fruit.net, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsfruitsetNETWORK.csv", row.names = TRUE)
+
+#TRYING TO MANUALLY CREATE PARTIAL RESIDUAL PLOTS
+
+pred<-m2.fruit.net$coef[1]+ (m2.fruit.net$coef[2] * mean(f.agg$species.poll.sc)) + (m2.fruit.net$coef[3] * mean(f.agg$tot.visits.sc)) + (m2.fruit.net$coef[4]* mean(f.agg$nodf.song.sc)) + (m2.fruit.net$coef[5] * f.agg$functional.comp.poll.sc)
+
+res<-pred-f.agg$mean.fruitset
+
+pl2 <- ggplot(f.agg,  aes(x=functional.comp.poll.sc, y= res)) +    
+        geom_point(size=4, color="darkgrey") + 
+  stat_smooth(method = 'lm', size=1.5, se=TRUE, color = "black", alpha=0.2) +     
+        xlab("Functional complementarity") +      
+        ylab("Fruitset") + theme_bw()  + #theme (legend.position= "none") +
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
+
+pl2
+
+#SPECIFIC PACKAGE TO DO PARTIAL RES PLOTS BUT DIFFICULT TO CUSTOMIZE
+
+#partial residual plots to see real value of each variable eliminating noise from others
+library(car)
+
+crPlots(m2.fruit.net, smooth=FALSE, terms = ~  species.poll.sc + functional.comp.poll.sc, main = "", ylab = "Mean fruitset", col.lines= "black", pch=19, col= "black", bg = "darkgrey", cex=2, cex.axis=1.2, cex.lab=1.5,
+        xlab = c("Pollinator diversity", "Functional complementarity"))
+
+#ORINGINAL PLOTS DO NOT SHOW EFFECTS OF VARIABLES IN ISOLATION
+
+pl2<-ggplot(f.agg,  aes(x=species.poll.sc, y=mean.fruitset)) +    
+        geom_point(size=4, color="darkgrey") + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        xlab("Pollinator species diversity") +      
+        ylab("Fruitset") + theme_bw()  + #theme (legend.position= "none") +
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
+
+pl2
+
+pl2b <-ggplot(f.agg,  aes(x=functional.comp.poll.sc, y=mean.fruitset)) +    
+        geom_point(size=4, color="darkgrey") + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        xlab("Functional complementarity") +      
+        ylab("Fruitset") + theme_bw()  + #theme (legend.position= "none") +
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
+
+pl2b #Well, moderate... without scaling it was more pronunced?
 
 #test for problems in residuals
-res<-simulateResiduals(m1.fr)
-plot(res, rank = TRUE)
-
-pl3<-ggplot(f.agg,  aes(x=species.poll, y=mean.fruitset))+      
-        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
-        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
-        xlab("Pollinator species diversity") +      
-        ylab("Average fruit set") + theme_bw()  + #theme (legend.position= "none") +
-        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
-
-pl3
+# res<-simulateResiduals(m2.fruit.net)
+# plot(res, rank = TRUE)
 
 #seed number
+#How mean seed number is calculated?? scaled first would be better, right? Yes using scaled values
+
+#same as before now averaging per species first and then per site
 
@@
 
-s.comm <- ddply(s2, c("Site_ID", "nodf.song", "functional.comp.poll", "species.poll"), summarise, tot.visits    = sum(tot.visits),
+s.comm.prev <- ddply(s4_scaled, c("Site_ID", "nodf.song", "functional.comp.poll", "species.poll"), summarise, tot.visits    = sum(tot.visits),
                          mean.seedset = mean(mean.seedn),
+                          mean.seedweight = mean(mean.seedw),
+                          mean.fruitweight = mean(mean.fruitweight))
+
+#mean of means!
+
+s.com <- ddply(s4_scaled, c("Site_ID", "Plant.sp", "nodf.song", "functional.comp.poll", "species.poll"), 
+               summarise, tot.visits    = sum(tot.visits),
+                         mean.seedset = mean(mean.seedn),
+                          mean.seedweight = mean(mean.seedw),
+                          mean.fruitweight = mean(mean.fruitweight))
+
+s.comm <- ddply(s.com, c("Site_ID", "nodf.song", "functional.comp.poll", "species.poll"), 
+               summarise, tot.visits    = sum(tot.visits),
+                         mean.seedset = mean(mean.seedset),
                           mean.seedweight = mean(mean.seedweight),
@@
 
-m1.seedcomm<-glmmTMB(mean.seedset ~ tot.visits + species.poll, family="nbinom2", data=s.comm)
-summary(m1.seedcomm)
-
-m2.seedcomm<-glmmTMB(mean.seedset ~ nodf.song +  functional.comp.poll, family="nbinom2", data=s.comm)
-summary(m2.seedcomm)
-
-m3.seedcomm<-glmmTMB(mean.seedset ~ tot.visits + species.poll + nodf.song +  functional.comp.poll, family="nbinom2", data=s.comm)
-summary(m3.seedcomm)
-
-library(bbmle)
-AICtab(m1.seedcomm, m2.seedcomm, m3.seedcomm)
+#scale variables for comparison of effect sizes
+
+s.comm$nodf.song.sc <- scale(s.comm$nodf.song, center = T, scale = T)
+s.comm$functional.comp.poll.sc <- scale(s.comm$functional.comp.poll, center = T, scale = T)
+s.comm$species.poll.sc <- scale(s.comm$species.poll, center = T, scale = T)
+s.comm$tot.visits.sc <- scale(s.comm$tot.visits, center = T, scale = T)
+
+#average seed set
+
+m1.seed.net<-glm(mean.seedset ~  species.poll.sc + tot.visits.sc, family="gaussian", data=s.comm)
+
+summary(m1.seed.net)
+
+vif(m1.seed.net)
+
+m2.seed.net<-glm(mean.seedset ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="gaussian", data=s.comm)
+
+summary(m2.seed.net)
+
+vif(m2.seed.net)
+
+#select best model based on AIC
+
+AICtab(m1.seed.net, m2.seed.net)
 
 #test for problems in residuals
-res<-simulateResiduals(m1.seedcomm)
-plot(res, rank = TRUE)
-
-pl4<-ggplot(s.comm,  aes(x=species.poll, y=mean.seedset))+      
-        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
-        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+# res<-simulateResiduals(m2.seed.net)
+# plot(res, rank = TRUE)
+
+#save table with results for paper
+summ.seed.net<-round(summary(m2.seed.net)$coef, digits=2)
+#write.csv(summ.seed.net, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsseedsetNETWORK.csv", row.names = TRUE)
+
+#functional comp only marginally significant so no plot here but just to see partial residual plot
+
+crPlots(m2.seed.net, smooth=FALSE, terms = ~  functional.comp.poll.sc, main = "", ylab = "Mean number of seeds per fruit", col.lines= "black", pch=19, col= "black", bg = "darkgrey", cex=2, cex.axis=1.2, cex.lab=1.5,
+        xlab = "Functional complementarity")
+
+#fruit weight
+
+m1.fruitw.net<-glm(mean.fruitweight ~  species.poll.sc + tot.visits.sc, family="gaussian", data=s.comm)
+
+summary(m1.fruitw.net)
+
+ vif(m1.fruitw.net)
+
+m2.fruitw.net<-glm(mean.fruitweight ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="gaussian", data=s.comm)
+
+ summary(m2.fruitw.net)
+
+ vif(m2.fruitw.net)
+
+#select best model based on AIC
+
+AICtab(m1.fruitw.net, m2.fruitw.net)
+
+#test for problems in residuals
+# res<-simulateResiduals(m1.fruitw.net)
+# plot(res, rank = TRUE)
+
+#save table with results for paper
+summ.fruitw.net<-round(summary(m1.fruitw.net)$coef, digits=2)
+#write.csv(summ.fruitw.net, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsfruitweightNETWORK.csv", row.names = TRUE)
+
+crPlots(m1.fruitw.net, smooth=FALSE, terms = ~  species.poll.sc, main = "", ylab = "Mean fruit weight", col.lines= "black", pch=19, col= "black", bg = "darkgrey", cex=2, cex.axis=1.2, cex.lab=1.5, 
+        xlab = "Pollinator species diversity")
+
+pl4<-ggplot(s.comm,  aes(x=species.poll.sc, y=mean.fruitweight))+      
+        geom_point(size=4, color="darkgrey") + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
         xlab("Pollinator species diversity") +      
-        ylab("Average number of seeds/fruit") + theme_bw()  + #theme (legend.position= "none") +
+        ylab("Fruit weight (g)") + theme_bw()  + #theme (legend.position= "none") +
         theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
@@
 
-pl5<-ggplot(s.comm,  aes(x=tot.visits, y=mean.seedset))+      
-        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
-        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
-        xlab("Total number of visits") +      
-        ylab("Average number of seeds/fruit") + theme_bw()  + #theme (legend.position= "none") +
+#seed weight
+
+m1.seedw.net<-glm(mean.seedweight ~  species.poll.sc + tot.visits.sc, family="gaussian", data=s.comm)
+
+summary(m1.seedw.net)
+
+vif(m1.seedw.net)
+
+m2.seedw.net<-glm(mean.seedweight ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="gaussian", data=s.comm)
+
+summary(m2.seedw.net)
+
+vif(m2.seedw.net)
+
+#select best model based on AIC
+
+AICtab(m1.seedw.net, m2.seedw.net)
+
+#test for problems in residuals
+# res<-simulateResiduals(m1.seedw.net)
+# plot(res, rank = TRUE)
+
+#save table with results for paper
+summ.seedw.net<-round(summary(m1.seedw.net)$coef, digits=2)
+#write.csv(summ.fruitw.net, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsseedweightNETWORK.csv", row.names = TRUE)
+
+crPlots(m1.seedw.net, smooth=FALSE, terms = ~  species.poll.sc, main = "", ylab = "Mean seed weight", col.lines= "black", pch=19, col= "black", bg = "darkgrey", cex=2, cex.axis=1.2, cex.lab=1.5, 
+        xlab = "Pollinator species diversity")
+
+pl5<-ggplot(s.comm,  aes(x=species.poll.sc, y=mean.seedweight))+      
+        geom_point(size=4, color="darkgrey") + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Pollinator species diversity") +      
+        ylab("Seed weight (g)") + theme_bw()  + #theme (legend.position= "none") +
         theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
@@
 
-#fruit weight
-
-m1.fwcomm<-glmmTMB(mean.fruitweight ~ tot.visits + species.poll, family="gaussian", data=s.comm)
-summary(m1.fwcomm)
-
-m2.fwcomm<-glmmTMB(mean.fruitweight ~ nodf.song +  functional.comp.poll, family="gaussian", data=s.comm)
-summary(m2.fwcomm)
-
-m3.fwcomm<-glmmTMB(mean.fruitweight ~ tot.visits + species.poll + nodf.song +  functional.comp.poll, family="gaussian", data=s.comm)
-summary(m3.fwcomm)
-
-library(bbmle)
-AICtab(m1.fwcomm, m2.fwcomm, m3.fwcomm)
-
-#test for problems in residuals
-res<-simulateResiduals(m1.fwcomm)
-plot(res, rank = TRUE)
-
-pl6<-ggplot(s.comm,  aes(x=species.poll, y=mean.fruitweight))+      
-        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
-        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
-        xlab("Pollinator species diversity") +      
-        ylab("Average fruit weight") + theme_bw()  + #theme (legend.position= "none") +
-        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
-
-pl6
-
-#seed weight
-
-m1.swcomm<-glmmTMB(mean.seedweight ~ tot.visits + species.poll, family="gaussian", data=s.comm)
-summary(m1.swcomm)
-
-m2.swcomm<-glmmTMB(mean.seedweight ~ nodf.song +  functional.comp.poll, family="gaussian", data=s.comm)
-summary(m2.swcomm)
-
-m3.swcomm<-glmmTMB(mean.seedweight ~ tot.visits + species.poll + nodf.song +  functional.comp.poll, family="gaussian", data=s.comm)
-summary(m3.swcomm)
-
-library(bbmle)
-AICtab(m1.swcomm, m2.swcomm, m3.swcomm)
-
-#test for problems in residuals
-res<-simulateResiduals(m1.swcomm)
-plot(res, rank = TRUE)
-
-pl7<-ggplot(s.comm,  aes(x=species.poll, y=mean.seedweight))+      
-        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
-        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
-        xlab("Pollinator species diversity") +      
-        ylab("Average seed weight") + theme_bw()  + #theme (legend.position= "none") +
-        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
-
-pl7
 ```
 
-### EQUITY IN FRUIT PRODUCTION
-
-LOOK AT EVENNESSS IN FUNCTION.
-within a site most plant species have very low reproductive success and thus we get incredibly high evenness values.
-therefore we use thresholds, for each sps and site we calculate the # of individuals that are above 50% in fruit production.
-
-AS before we find that the best model is that including the diversity of pollinator species, which has a significant positive effect on equity in fruitset.
+### Equity in fruitset
+
+When evaluating the effect of differences in community composition and structure for equity in reproductive success across the different plant species, we find that both model 1 and model 2 are equally good (AIC diff < 2) and thus we cannot select one over the other.
+This suggests that, the penalty that should be given to model 2 given its greater complexity (greater number of variables) is smaller than the additional information that is being provided by including data on community structure.
+Specifically, regarding the results for model 2 we find a significant and positive effect of both the total number of visits received by the community and the functional complementarity within it (mean +- sd not overlapping 0, Table X, Fig.
+X).
+This effect that we find when using a 50% threshold of productivity (i.e., when looking at plant species that are producing 50% of the maximum fruitset observed for the area), is maintained when using 25 and 75% thresholds.
+In the case of the 75% thershold we find an additional positive effect of pollinator species diversity.
+
+ALL THESE RESULTS NOW CHANGE WHEN USING PROPORTION OF SPS RATHER THAN NUMBER, NOTHING IS SIG :()
 
 ```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+#calculate column with fruit set as
+f$Plant.sp<-paste(f$Plant_genus, f$Plant_species)
+
+#Fruit_Yes +  Fruit_Preyed + Fruit_Dispersed) / (Fruit_Yes + Fruit_No +Fruit_Preyed + Fruit_Dispersed) #Nacho this equation is wrong in your metadata!
+
+#1st eliminate frutos perdidos
+wordList <- c("fruto perdido","frutos perdidos")
+
+require(Hmisc)
+f2<-subset(f, Notes %nin% wordList)
+
+f2$tot.fruitset<-(f2$Fruit_Yes +  f2$Fruit_preyed + f2$Fruit_dispersed)/(f2$Fruit_Yes +f2$Fruit_No + f2$Fruit_preyed + f2$Fruit_dispersed)
 
@@
 f6<- aggregate(no_rows ~ Site_ID, f5, length)
+head(f6)
+
+#because when calculating thresholds, sites with 6 plants can score up to 6, but sites with 4 sites can oscar max = 4 we corrected for this doing % above threshold, and no number.
+
+f4$no_rows<-rep(1, nrow(f4))
+f4b<- aggregate(no_rows ~ Site_ID, f4, length)
+head(f4b)
+
+f6$total.plant.numb<-f4b$no_rows[match(f6$Site_ID, f4b$Site_ID)]
+f6$equity<-f6$no_rows/f6$total.plant.numb
 
@@
 f6$nodf.song<-out.site$nodf.song[match(f6$Site_ID, out.site$Site_id)]
-f6$int_evenness<-out.site$int_evenness[match(f6$Site_ID, out.site$Site_id)]
-f6$H2<-out.site$H2[match(f6$Site_ID, out.site$Site_id)]
 f6$functional.comp.poll<-out.site$functional.comp.poll[match(f6$Site_ID, out.site$Site_id)]
-f6$niche.overlap.plant<-out.site$niche.overlap.plant[match(f6$Site_ID, out.site$Site_id)]
-f6$modularity<-out.site$modularity[match(f6$Site_ID, out.site$Site_id)]
 f6$species.poll<-out.site$species.poll[match(f6$Site_ID, out.site$Site_id)]
-f6$species.pl<-out.site$species.pl[match(f6$Site_ID, out.site$Site_id)]
-
 f6$tot.visits<-f.agg$tot.visits[match(f6$Site_ID, f.agg$Site_ID)]
 
-m1.eq<-glmmTMB(no_rows ~ tot.visits + species.poll, family="gaussian", data=f6)
+#scale all variables
+
+f6$nodf.song.sc <- scale(f6$nodf.song, center = T, scale = T)
+f6$functional.comp.poll.sc <- scale(f6$functional.comp.poll, center = T, scale = T)
+f6$species.poll.sc <- scale(f6$species.poll, center = T, scale = T)
+f6$tot.visits.sc <- scale(f6$tot.visits, center = T, scale = T)
+
+#fit two models
+ m1.eq<-glm(equity ~  species.poll.sc + tot.visits.sc, family="binomial", data=f6)
+
  summary(m1.eq)
 
-m2.eq<-glmmTMB(no_rows ~ nodf.song +  functional.comp.poll, family="gaussian", data=f6)
+vif(m1.eq)
+
+m2.eq<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="binomial", data=f6)
+ #nich estimate not overlaping zero: 0.6178     0.4354, second higher effect size!
 summary(m2.eq)
 
-m3.eq<-glmmTMB(no_rows ~ tot.visits + species.poll + nodf.song +  functional.comp.poll, family="gaussian", data=f6)
-summary(m3.eq)
-
-library(bbmle)
-AICtab(m1.eq, m2.eq, m3.eq)
-
-#test for problems in residuals
-res<-simulateResiduals(m1.eq)
-plot(res, rank = TRUE)
-
-pl.th<-ggplot(f6,  aes(x=species.poll, y=no_rows))+      
-        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
-        xlab("Pollinator species diversity") +      
-        ylab("Equity in fruitset") + theme_bw() + 
-        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
-
-pl.th
-
-pl.th2<-ggplot(f6,  aes(x=functional.comp.poll, y=no_rows))+      
-        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+vif(m2.eq)
+
+#select best model based on AIC
+
+AICtab(m1.eq, m2.eq) #Almost equal... Again, for prediction, go with the simple, for mechanistic understanding, look into niche partitioning.
+
+#save table with results for paper, both models are equally good so save both tables
+summ.eq<-round(summary(m1.eq)$coef, digits=2)
+#write.csv(summ.eq, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsequityNETWORKm1.csv", row.names = TRUE)
+
+summ.eq2<-round(summary(m2.eq)$coef, digits=2)
+#write.csv(summ.eq2, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsequityNETWORKm2.csv", row.names = TRUE)
+
+#partial residual plots
+
+crPlots(m2.eq, smooth=FALSE, terms = ~  tot.visits.sc + functional.comp.poll.sc, main = "", ylab = "Equity in fruitset", col.lines= "black", pch=19, col= "black", bg = "darkgrey", cex=2, cex.axis=1.2, cex.lab=1.5)
+
+pl.th_ <-ggplot(f6,  aes(x=functional.comp.poll.sc, y=no_rows))+      
+        geom_point(size=4, color="darkgrey") + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
         xlab("Functional complementarity") +      
@@
 
-pl.th2
+pl.th_ #oh yeah!
+
+pl.th<-ggplot(f6,  aes(x=tot.visits.sc, y=no_rows))+      
+        geom_point(size=4, color="darkgrey") + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        xlab("Total number of visits") +      
+        ylab("Equity in fruitset") + theme_bw() + 
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
+
+pl.th
+
+-------------------------------------------------------------------------------
+
+m3.eq_ <-glm(no_rows ~ functional.comp.poll.sc, family="gaussian", data=f6)
+ #Oh yeah. It works for doing my null simulation.
+ summary(m3.eq_)
+
+#test for problems in residuals
+# res<-simulateResiduals(m1.eq)
+# plot(res, rank = TRUE)
+
+# 
+# #check whether it is driven by that one point with large number of visits
+# 
+# f7 <- subset(f6, f6$tot.visits.sc < 2)
+# 
+#  m1.eqb<-glm(no_rows ~  species.poll.sc + tot.visits.sc, family="gaussian", data=f7)
+# 
+#  summary(m1.eqb)
+#  
+#  
+#  
+# pl.th2<-ggplot(f7,  aes(x=tot.visits.sc, y=no_rows))+      
+#         geom_point(size=4, color="darkgrey") + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+#         xlab("Total number of visits") +      
+#         ylab("Equity in fruitset") + theme_bw() + 
+#         theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) 
+# 
+# pl.th2
+#
+
+#Repeat with 75% threshold
+
+f75<-subset(f4, f4$fruit.prop>0.75)
+f75$no_rows<-rep(1, nrow(f75))
+head(f75)
+
+#for each site here is the number of sps whose fruitset exceeds 75% of maximum fruitset observed in the whole study area
+f75b<- aggregate(no_rows ~ Site_ID, f75, length)
+head(f75b)
+f75b$total.numb.plants<-f6$total.plant.numb[match(f75b$Site_ID, f6$Site_ID)]
+f75b$equity<-f75b$no_rows/f75b$total.numb.plants
+
+#join this with fruitset data used previously
+
+f75b$nodf.song<-out.site$nodf.song[match(f75b$Site_ID, out.site$Site_id)]
+f75b$functional.comp.poll<-out.site$functional.comp.poll[match(f75b$Site_ID, out.site$Site_id)]
+f75b$species.poll<-out.site$species.poll[match(f75b$Site_ID, out.site$Site_id)]
+f75b$tot.visits<-f.agg$tot.visits[match(f75b$Site_ID, f.agg$Site_ID)]
+
+#scale all variables
+
+f75b$nodf.song.sc <- scale(f75b$nodf.song, center = T, scale = T)
+f75b$functional.comp.poll.sc <- scale(f75b$functional.comp.poll, center = T, scale = T)
+f75b$species.poll.sc <- scale(f75b$species.poll, center = T, scale = T)
+f75b$tot.visits.sc <- scale(f75b$tot.visits, center = T, scale = T)
+
+ m1.eq.75<-glm(equity ~  species.poll.sc + tot.visits.sc, family="gaussian", data=f75b)
+
+ summary(m1.eq.75)
+
+ vif(m1.eq.75)
+
+m2.eq.75<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="gaussian", data=f75b)
+
+ summary(m2.eq.75)
+
+ vif(m2.eq.75)
+
+#select best model based on AIC
+
+AICtab(m1.eq.75, m2.eq.75) #as before both models are equally good.
+
+# #test for problems in residuals
+# res<-simulateResiduals(m1.eq.75)
+# plot(res, rank = TRUE)
+
+#and for 25% threshold
+
+f25<-subset(f4, f4$fruit.prop>0.25)
+f25$no_rows<-rep(1, nrow(f25))
+head(f25)
+
+#for each site here is the number of sps whose fruitset exceeds 25% of maximum fruitset observed in the whole study area
+f25b<- aggregate(no_rows ~ Site_ID, f25, length)
+head(f25b)
+f25b$total.numb.plants<-f6$total.plant.numb[match(f25b$Site_ID, f6$Site_ID)]
+f25b$equity<-f25b$no_rows/f25b$total.numb.plants
+
+f25b$nodf.song<-out.site$nodf.song[match(f25b$Site_ID, out.site$Site_id)]
+f25b$functional.comp.poll<-out.site$functional.comp.poll[match(f25b$Site_ID, out.site$Site_id)]
+f25b$species.poll<-out.site$species.poll[match(f25b$Site_ID, out.site$Site_id)]
+f25b$tot.visits<-f.agg$tot.visits[match(f25b$Site_ID, f.agg$Site_ID)]
+
+#scale all variables
+
+f25b$nodf.song.sc <- scale(f25b$nodf.song, center = T, scale = T)
+f25b$functional.comp.poll.sc <- scale(f25b$functional.comp.poll, center = T, scale = T)
+f25b$species.poll.sc <- scale(f25b$species.poll, center = T, scale = T)
+f25b$tot.visits.sc <- scale(f25b$tot.visits, center = T, scale = T)
+
+ m1.eq.25<-glm(equity ~  species.poll.sc + tot.visits.sc, family="gaussian", data=f25b)
+
+ summary(m1.eq.25)
+
+  vif(m1.eq.25)
+
+m2.eq.25<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="gaussian", data=f25b)
+
+ summary(m2.eq.25)
+
+ vif(m2.eq.25)
+
+#select best model based on AIC
+
+AICtab(m1.eq.25, m2.eq.25)
+
+#test for problems in residuals
+# res<-simulateResiduals(m1.eq.25)
+# plot(res, rank = TRUE)
+
+##equity in seed number
+
+library(vegan)
+library(dplyr)
+
+s5 <- ddply(s4_scaled, c("Site_ID", "Plant.sp", "functional.comp.poll.sc", "nodf.song.sc", "species.poll.sc", "tot.visits.sc"), summarise,
+                         mean.seedset    = mean(mean.seedn))
+
+s5.max<-aggregate(.~ Plant.sp, s5, FUN=max)
+
+s5$seed.max<-s5.max$mean.seedset[match(s5$Plant.sp, s5.max$Plant.sp)]
+
+s5$seed.prop<-s5$mean.seedset/s5$seed.max
+s6<-subset(s5, s5$seed.prop>0.5)
+s6$no_rows<-rep(1, nrow(s6))
+head(s6)
+
+#for each site here is the number of sps whose seedset exceeds 50% of maximum seedset observed in the whole study area
+s7<- aggregate(no_rows ~ Site_ID, s6, length)
+head(s7)
+
+#calculate proportion of sps at threshold because number depends on number of sps per site which is different
+
+s5$no_rows<-rep(1, nrow(s5))
+s5b<- aggregate(no_rows ~ Site_ID, s5, length)
+head(s5b)
+
+s7$total.plant.numb<-s5b$no_rows[match(s7$Site_ID, s5b$Site_ID)]
+s7$equity<-s7$no_rows/s7$total.plant.numb
+
+#join this with fruitset data used previously
+
+s7$nodf.song<-out.site$nodf.song[match(s7$Site_ID, out.site$Site_id)]
+s7$functional.comp.poll<-out.site$functional.comp.poll[match(s7$Site_ID, out.site$Site_id)]
+s7$species.poll<-out.site$species.poll[match(s7$Site_ID, out.site$Site_id)]
+s7$tot.visits<-f.agg$tot.visits[match(s7$Site_ID, f.agg$Site_ID)]
+
+#scale all variables
+
+s7$nodf.song.sc <- scale(s7$nodf.song, center = T, scale = T)
+s7$functional.comp.poll.sc <- scale(s7$functional.comp.poll, center = T, scale = T)
+s7$species.poll.sc <- scale(s7$species.poll, center = T, scale = T)
+s7$tot.visits.sc <- scale(s7$tot.visits, center = T, scale = T)
+
+#fit two models
+
+ m1.eq.seed<-glm(equity ~  species.poll.sc + tot.visits.sc, family="binomial", data=s7)
+
+ summary(m1.eq.seed)
+
+ vif(m1.eq.seed)
+
+m2.eq.seed<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="binomial", data=s7)
+
+ summary(m2.eq.seed)
+
+ vif(m2.eq)
+
+#select best model based on AIC
+
+AICtab(m1.eq.seed, m2.eq.seed)
+
+#test for problems in residuals
+# res<-simulateResiduals(m1.eq.seed)
+# plot(res, rank = TRUE)
+
 ```
 
-Now look at motifs and indirect interactions.
-To this end, we compare the roles of plant species at each site with low (<0.5) and high (>0.5) fruit set.
-We calculate for each plant species at each site the sum-normalised roles of all plant species in motifs up to 5 nodes and plot them using NMDS.
-ALthough we find a large overlap between the roles of both types ofplant species, we do find that plant species with high fruit set tend to be located in the higher values of NMDS1 which is related to network positions in which a generalist plant species interacts with highly specialized pollinator partners (e.g, positions 16 and 46, see Fig.
-1 in bmotif paper, Simmons et al preprint)
+Now, we ask if the effect of niche complementariety increases with the number of species considered in the network.
+We expect that for any single species, the effect should be almost zero (as shown in our single species analysis above), but when you take into account up to 6 species, network metrics start to be important (see also above the community level results).
+This implies that if we would be able to measure reproductive success on all plant species in the community in all networks (not done for effort constrains) the effects of network configuartion may be even more prevalent.
+To test this, we ran a simple simulation where we first increase randomly the number of selected species per network and calculate the equitativity for each run.
+Instead of drawing random plants for each run, for each plant number level and network we test all possible combinations, as this number is low (n = 63 possible combiations overall for the network with the largest dataset) and increasing sampling events in our simulation would only result in repeated combinations.
+Second, we test the overall relation between equitativity in fruit set and niche complementariety in our simulated communities.
+To this end, for each species number level, we randomly combine the generated equitativity values across the 16 communities as to obtain one random value per species.
+Finally, for each of such combinations we calculated the estimate of equitativity in relation with niche partitioning and average all estimates from 1000 simulated combinations per number of plants considered.
+We expect that the more plants considered, the larger are the resulting average estimates.
+Note that We only interpret the mean effects, as the variance among different plant number of species depends on the initial number of combinations.
+
+I ALSO INCLUDED HERE NESTEDNESS WHICH STARTS AS LESS IMPORTANT AND THEN BECOMES MORE IMPORTANT WITH NO ASYMPTOTE.
+
+ONE QUESTION, WHY DO WE DO THIS SIMULATION ONLY FOR EQUITY AND NOT ALSO FOR AVERAGE REP SUCCESS?
 
 ```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
-#First attempt to load the data, etc...
-
-#prepare stuff-----
-#If you don't have devtools install it
-#install.packages("devtools")
-library(devtools)
-#Then install the data package. Reprot issues 
-#install_github("ibartomeus/BeeFunData", ref = "fun")
-library(BeeFunData)
-
-# load packages
-library(bmotif)
+
 library(vegan)
-
-#make the data available
-#analysis...----
-
-d<-all_interactions
-f<-fruitset
-s<-seedset
-
-d2<-subset(d, d$Plant_gen_sp!="NA NA")
-#d2$Plant_gen_sp
-
-sites <- unique(d2$Site_ID)
-
-empty_web <- function(x) {
-  # Removes all-zero rows and columns from a matrix
-  cempty <- which(colSums(x) == 0)
-  rempty <- which(rowSums(x) == 0)
-  if(length(rempty) != 0 & length(cempty) == 0){
-    return(x[-rempty,,drop = FALSE])
-  } else if(length(rempty) == 0 & length(cempty) != 0){
-    return(x[,-cempty,drop = FALSE])
-  } else if(length(rempty) != 0 & length(cempty) != 0){
-    return(x[-rempty,-cempty,drop = FALSE])
-  } else if(length(rempty) == 0 & length(cempty) == 0){
-    return(x)
+library(dplyr)
+
+f2$Plant.sp<-paste(f2$Plant_genus, f2$Plant_species)
+f3<-f2[,c(1,13:14)]
+
+f4 <- ddply(f3, c("Site_ID", "Plant.sp"), summarise,
+                         mean.fruitset    = mean(tot.fruitset))
+
+table(f4$Plant.sp)
+#Astragalus lusitanicus and Cistus albidus is causing problems later on.
+It has a very low fruit set, but as there is only one value, when correcting for max fruit set, gets a value of 1.
+Both are in Cotito...
+This is problematic.
+Similar with Anchusa azurea.
+
+#I am removing them here.
+f4 <- subset(f4, !Plant.sp %in% c("Astragalus lusitanicus", "Cistus albidus", "Anchusa azurea"))
+#Alternative, we use raw values (not dividing by max.)
+
+#Ainhoa, another question, this is a mean per species, right? So, for some species we may have more than one value.
+
+#f4
+
+fr.max<-aggregate(.~ Plant.sp, f4, FUN=max)
+
+f4$fruit.max<-fr.max$mean.fruitset[match(f4$Plant.sp, fr.max$Plant.sp)]
+
+f4$fruit.prop<-f4$mean.fruitset/f4$fruit.max
+head(f4) #this is ok, I guess, but imply we are correcting for differences in production across plants.
+
+#Quick dirty fix to see if things change a lot for uncorrected values
+#f4$fruit.prop <- f4$mean.fruitset
+
+#1) First let's calculate all combinations of 1,2,3,4,5,6 species per network.
+combinatorials_all <-  matrix(ncol = 6, nrow = 1, NA) 
+colnames(combinatorials_all) <- c("SiteID", "Plant_number_level", "iteration", "equity", "functional.comp", "nestedness")
+uniqueSite_ID <- unique(f4$Site_ID)
+for(k in 1:length(uniqueSite_ID)){ #sites
+  Site_temp <- subset(f4, Site_ID == uniqueSite_ID[k]) #1:SiteID
+  n <- length(Site_temp$Plant.sp)
+  combinatorials <- matrix(ncol = 6, nrow = 1, NA) #flexible
+  colnames(combinatorials) <- c("SiteID", "Plant_number_level", "iteration", "equity", "functional.comp", "nestedness")
+  combinatorials <- as.data.frame(combinatorials)
+  for (i in 1:n){ #levels
+    combinatorials_1 <- combn(x = Site_temp$Plant.sp, m = i) #1:n
+    for (j in 1:ncol(combinatorials_1)){ #different combinations
+      temp1 <- Site_temp[which(Site_temp$Plant.sp %in% combinatorials_1[,j]),]
+      combinatorials_2 <- subset(temp1, temp1$fruit.prop > 0.5)
+      if(dim(combinatorials_2)[1] == 0) {
+        combinatorials_2 <- temp1
+        combinatorials_2$no_rows <- 0
+      } else{
+        combinatorials_2$no_rows<-rep(1, nrow(combinatorials_2))
       }
+      #head(combinatorials_2)
+      #for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
+      combinatorials_3 <- aggregate(no_rows ~ Site_ID, combinatorials_2, sum)
+      #head(combinatorials_3)
+      combinatorials_3$functional.comp.poll <- out.site$functional.comp.poll[match(combinatorials_3$Site_ID, out.site$Site_id)]
+      combinatorials_3$nestedness <- out.site$nodf.song[match(combinatorials_3$Site_ID, out.site$Site_id)]
+      #now save for later.
+      index <- dim(combinatorials)[1]
+      combinatorials[index+1,1] <-  as.character(combinatorials_3$Site_ID) #1:SiteID
+      combinatorials[index+1,2] <-  i #Plant number level
+      #combinatorials[index+1,3] <-    #"iteration" let's asume we don' care, but would be good for unit testing
+      combinatorials[index+1,4] <- combinatorials_3$no_rows/i #above threshold in %
+      combinatorials[index+1,5] <-  combinatorials_3$functional.comp.poll #nich comp value...
+      combinatorials[index+1,6] <-  combinatorials_3$nestedness #nestedness value...
+    } #close different combinations
+  } #close levels
+  combinatorials_all <- rbind(combinatorials_all, combinatorials[-1,])
+} #close sites
+
+combinatorials_all <- combinatorials_all[-1,]
+
+#plot overall (asi a saco)
+
+scatter.smooth(combinatorials_all$equity ~ combinatorials_all$functional.comp) #no relationship, good
+scatter.smooth(combinatorials_all$equity ~ combinatorials_all$nestedness) #no relationship, good
+
+#scale variables
+
+combinatorials_all$functional.comp.sc<-scale(combinatorials_all$functional.comp, center = T, scale = T)
+combinatorials_all$nestedness.sc<-scale(combinatorials_all$nestedness, center = T, scale = T)
+
+#now try overall, per level.
+estimate <- rep(NA,6)
+for (i in unique(combinatorials_all$Plant_number_level)){
+  temp <- subset(combinatorials_all, Plant_number_level == i)
+  m <- lm(temp$equity ~ temp$functional.comp.sc)
+  plot(temp$equity ~ temp$functional.comp.sc) 
+  abline(m)
+  estimate[i] <- m$coefficients[2]
   }
 
-webs <- list()
-webs.or3<-list()
-for(i in 1:length(sites)){
-  temp <- subset(d2, Site_ID == sites[i])
-  # for(j in 1:length(rounds)){
-  #   temp2 <- subset(temp, Round == rounds[j])
-  #   if (nrow(temp2) == 0) next
-
-  web <- as.matrix.data.frame(table(temp$Plant_gen_sp, temp$Pollinator_gen_sp))
-  web.or<-table(temp$Plant_gen_sp, temp$Pollinator_gen_sp)#keeps names of species
-
-  web2<-empty_web(web)
-  web.or2<-empty_web(web.or)
-
-  webs.or3[[i]]<-web.or2 #keeps names of species
-  webs[[i]]<-as.matrix(web2)
+plot(unique(combinatorials_all$Plant_number_level) , estimate, las = 1, ylim = c(0, 0.1) ,
+     ylab = "importance of niche partitioning", xlab = "number of plants considered")
+
+#now try overall, per level.
+estimate <- rep(NA,6)
+for (i in unique(combinatorials_all$Plant_number_level)){
+  temp <- subset(combinatorials_all, Plant_number_level == i)
+  m <- lm(temp$equity ~ temp$nestedness.sc)
+  plot(temp$equity ~ temp$nestedness.sc) 
+  abline(m)
+  estimate[i] <- m$coefficients[2]
   }
 
-names(webs)<-sites
-names(webs.or3)<-sites
-
-out <- data.frame(web = NA, nrow = NA)
-
-#calculates number of rows in each web and then sums everything to see how many rows we need in total
-for(i in 1:length(webs)){
-  s<- sum(nrow(webs[[i]]))
-
-  n<-nrow(out)
-  out[n + 1,1] <- as.character(sites[i])
-  out[n + 1,2] <- s
-
+plot(unique(combinatorials_all$Plant_number_level) , estimate,  las = 1, ylim = c(0, 0.1) ,
+     ylab = "importance of nestedness", xlab = "number of plants considered")
+
+# I think this is a true pattern, as the for the cnetral limit theorem a mean of means should equal the grand mean, but worth check it.
+
+#now we subsample 16 combinations at a time 100 timeas and make the average.
+estimate_i <- data.frame(level = NA, estimate = NA)
+estimate_k <- data.frame(level = NA, estimate = NA)
+head(combinatorials_all)
+for (i in 1:length(unique(combinatorials_all$Plant_number_level))){ # over levels
+  temp <- subset(combinatorials_all, Plant_number_level == unique(combinatorials_all$Plant_number_level)[i])
+  for(k in 1:100){ #iterations
+    value <- data.frame(site = NA, eq = NA, nich = NA)
+    for(j in 1:length(unique(temp$SiteID))){ # over sites
+      temp2 <- subset(temp, SiteID == unique(temp$SiteID)[j]) #why only one record at Elpinar??
+      value_temp <- temp2[sample(x = 1:nrow(temp2), 1),]
+      value[j,1] <- value_temp$SiteID
+      value[j,2] <- value_temp$equity
+      value[j,3] <- value_temp$functional.comp
+    } #close sites
+    m <- lm(value$eq ~ value$nich)
+    #plot(value$eq ~ value$nich)
+    estimate_k[k,1] <- i
+    estimate_k[k,2] <- m$coefficients[2]  
+  } #close iteration
+  #unique(estimate_k) #only 5 unique ombinations for n = 5. All negative. highly influenced by one data point of low niche part and equ = 1. "CotitodeSantaTeresa"
+  #subset(f4, Site_ID == "CotitodeSantaTeresa") #Super high values!
+  estimate_mean <- aggregate(estimate ~ level, estimate_k, mean)
+  estimate_i[i,1] <- estimate_mean$level
+  estimate_i[i,2] <- estimate_mean$estimate
   }
 
-out<-out[-1,]
-out2<-sum(out$nrow)
-
-mp <- as.data.frame(matrix(nrow = out2, ncol = 48, dimnames = list(NULL,c("web","species",paste0("m",1:46)))))
-wr <- 0
-for(i in names(webs)){
-
-    pv <- positions(webs[[i]], six_node = FALSE, level = "rows", normalisation = "sum") # calculate species positions
-    start_row <- which(is.na(mp$web))[1]
-    end_row <- (start_row + nrow(pv)) - 1
-    wr <- start_row:end_row
-    mp[wr,"web"] <- i
-    mp[wr,"species"] <- rownames(webs.or3[[i]])
-    mp[wr,paste0("m",1:46)] <- pv
-  }
-
-#SUBSET ONLY PLANTS FOR WHICH WE HAVE DATA ON FRUISET
-#f4
-f4$j<-paste(f4$Site_ID, f4$Plant.sp)
-
-mp$j<-paste(mp$web, mp$species)
-
-mp$mean.fruitset<-f4$mean.fruitset[match(mp$j, f4$j)]
-
-mp2<-subset(mp, mp$mean.fruitset!="NA")
-mp2$class[mp2$mean.fruitset>0.5]<-"high"
-mp2$class[mp2$mean.fruitset<0.5]<-"low"
-
-# How many native and introduced species?
-mp2 <- mp2[order(mp2$class, decreasing = TRUE),]
-class_f <- table(mp2$class)
-
-# NMDS
-example_NMDS <- metaMDS(vegdist(mp2[,paste0("m",1:46)], method = "bray"), k=2, distance = "bray", trymax = 100)
-mds.fig <- ordiplot(example_NMDS, type = "none")
-colors=c(rep("darkorange2",class_f["low"]),rep("purple",class_f["high"]))
-treat <- mp2$class
-for(i in unique(treat)) {
-  ordihull(example_NMDS$point[grep(i,treat),],draw="polygon",
-           groups=treat[treat==i],col=colors[grep(i,treat)],label=F) } 
-with(mp2, legend("topright", legend = unique(mp2$class), bty = "n",
-                col = unique(colors), pch = 21, pt.bg = unique(colors)))
-points(mds.fig, "sites", pch = 19, col = "darkorange3", select = mp2$class == 
-         "low")
-points(mds.fig, "sites", pch = 19, col = "purple", select = mp2$class == 
-         "high")
-
-#example_NMDS <- metaMDS(mp2[,paste0("m",1:46)], k=2, distance = "bray", trymax = 100)
-#example_NMDS$species # which positions are associated with which axes
-#example_NMDS$species[order(example_NMDS$species[,"MDS2"]),]
-
-#permanova
-
-adonis(mp2[,3:48]~ mean.fruitset, data=mp2, method = "bray")
-
-#permanova... we need to control for the web, right? not sure what you mean here, random effect?
-
-adonis(mp2[,3:48]~ mean.fruitset, data=mp2, method = "euclidean", strata = mp2$web)
-adonis(mp2[,3:48]~ class, data=mp2, method = "bray")
-
-#no significant differences at all.
+estimate_i
+
+plot(estimate_i$level, estimate_i$estimate, las = 1,
+     ylab = "importance of niche partitioning", xlab = "number of plants considered")
+#we had an issue for n = 5 ...
+this is cause by cotito de santa teresa having a huge influence when only 7 datasets are used.
+Once This is fixed, the plot looks nice.
+It's a shame that with 5 and 6 plants it asimptotes, but on the other hand, for 6 plants we only have very few sites.
+
+#One option is removing n = 6 from the simulation, as there is only one model for n = 6, and hence, while all other models estimate better the uncertainty on plant choice, the last model we have just 4 communities.
+
+#Ainhoa, this akes me think that when calculating thresholds, sites with 6 plants can score up to 6, but sites with 4 sites can oscar max = 4.
+I corrected for this doing % above threshold, and no number.
+Worth doing the same in the above models.
+
+#I only did it for fruit set.... no seeds, no weight...
 
 ```
+
+#DISCUSSION
+Importance of functional complementarity found in artificial [@Frund2013] and natural [@Fontaine2005] communities.
+
+The analysis of natural communities of interacting species using network analysis represents an ideal way of visualizing and grasping the complexity present.
+
+we have yet to know whether these variables contribute more to plant reproductive success than others related to the position of a particular plant species within the wider plant community that hosts it.
+In particular, our study focuses on the importance of pollinator diversity and total number of visits for plant reproductive success in comparison to that of the plant´s position in the community.
+Specifically, niche overlap between plant species (which could give us a proxy for the existence of competition for pollination between plant species) and the position of the plant given by the connections it establishes with other species, e.g.
+its centrality within the network, where central species are those receiving the greatest number of connections from other species, could have an influence in a plant´s reproductive success.
+
+Furthermore, we do not know how the overall structure of a community, and the architecture of the network of interactions it hosts, affects the reproductive success of the whole community.
+In particular, one of the networks metrics that has received the most attention in the community ecology literature is that of nestedness.
+Nestedness is the property by which specialists interact with a subset of the species that generalists interact with.
+Although there is ongoing debate in the literature, some studies have found that more nested networks are more stable and resilient to perturbations because nestedness implies a certain level of redundancy and thus the possibility for functional replacement in the case of species loss.
+However, plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence.
+Yet at present we do not know how the interplay between redundancy and complementarity determines reproductive success.
+Finally, average values of reproductive success at the community level can be driven to a large degree by one single plant species.
+Yet, what will determine the persistence of a diverse plant community is the presence of some sort of “equity” in reproductive success across the whole community.
+We thus also focus on the effect of community structure for equity in reproductive success across the plant community.

### 2019-01-17 paper_round2.Rmd
small changes in partial residual plots

@@
 
-#best model is m1, plot significant variable, in this case degree
+#best model is m1, plot significant variable, in this case degree, do partial residual plots to show the effect of that variable in isolation of the others
+
+crPlots(m1, smooth=FALSE, terms = ~  norm_degree.sc, main = "", ylab = "Fruitset", col.lines= "black", pch=19, col= "black", bg = "darkgrey", cex=2, cex.axis=1.2, cex.lab=1.5, 
+        xlab = "Pollinator species diversity")  #PROBLEM HERE BECAUSE OF RANDOM EFFECTS, NEED TO CHECK!
+
+#or do original plots, no partial residuals
 

### 2019-02-14 paper_round2.Rmd
paper half written

--- 2019-01-17 paper_round2.Rmd
@@
 bibliography: library.bib
+csl: ecology-letters.csl
 editor options:
@@
 ------------------------------------------------------------------------------------------------
-To be potentially submitted to ECOLOGY LETTERS as a Letter: maximum of 5000 words and 6 figures, tables or text boxes. 
+[To be potentially submitted to ECOLOGY LETTERS as a Letter: maximum of 5000 words and 6 figures, tables or text boxes. 
 The abstract page should contain a short summary not exceeding 150 words for Letters.
@@
 
----------------------------------------------------------------------------------------------------------
-
 Title: Impact of interaction network structure on community-level plant reproduction success
@@
 However, research has targeted the consequences for individual plant species, particularly focusing on pairwise plant-pollinator interactions, and largely overlooking community-level dynamics.
-Yet species do not interact in isolation, they are embedded within larger networks whose structure can affect pollinator functional roles and, ultimately, the pollination service they deliver to plants.
-Here, we present one of the first efforts linking pollinator visitation and plant reproduction from a community-wide perspective using a well-replicated dataset encompassing 16 well-resolved networks and data on reproductive success for 19 plant species from Mediterranean shrub ecosystems.
-We find that for prediction purposes, information on simple visitation metrics is sufficient.
+Yet species do not interact in isolation, they are embedded within larger networks whose structure can affect pollinator functional roles and, ultimately, the pollination services they deliver to plants.
+Here, we present one of the first efforts linking pollinator visitation to plant reproduction from a community-wide perspective using a well-replicated dataset encompassing 16 well-resolved networks and data on reproductive success for 19 plant species from Mediterranean shrub ecosystems.
+We find that, for prediction purposes, information on simple visitation metrics is sufficient.
 Contrastingly, a mechanisitic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success, requires additional information on network structure.
@@
 We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect ones between species within one guild (e.g., plants) through their shared resources [@Lazaro2014].
-Understanding how changes in pollinator diversity affect whole plant assemblages is thus a major challenge that requires attention.
+Understanding how changes in pollinator diversity affect whole community assemblages is thus a major challenge that requires attention.
 
@@
 As an example, a study that experimentally recreated a plant community with 9 plant species and differing levels of pollinator diversity across different enclosures, found that not only pollinator species diversity had an effect for average reproductive success, but also they found that the structure that shaped the community had an important effect [@Frund2013].
-In particular, these authors found that functional complementarity between pollinators, in terms of plant species and temperature coverage (a measure of the overlap in the use of plant resources and optimum temperature activity) had a positive effect for average seed set at the community level [@Frund2013].
+In particular, these authors found that the functional complementarity between pollinators, in terms of plant species and temperature coverage (a measure of the overlap in the use of plant resources and optimum temperature activity) had a positive effect for average seed set at the community level [@Frund2013].
 This provides added information on the effects of biodiversity for ecosystem functioning, suggesting that not only the diversity of species present but also the diversity of roles and ways in which a community is structured are determinant factors.
@@
 Indeed, theoretical research has long suggested that the structure of a community has an effect for ecosystem functioning (reviewed in [@Thompson2012]).
-This line of research, primarliy driven by food-web studies, has greatly advanced theory, but these ideas have not yet been tested with empirical data.
+This line of research, primarliy driven by food-web studies, has greatly advanced theory, but these ideas have not yet been tested using empirical data.
 Specifically, a major knowledge gap resides in understading which aspects of structure determine which aspects of function [@Thompson2012].
@@
 Our study focuses on understanding whether adding information on the structure of the community to previously-used simple visitation metrics (e.g., number of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success.
-In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive succes.
+In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success.
 
@@
 
-Within each site, we marked between 2 and 12 individuals (6.49 +- 2.37) of 1 to 6 plant species (4.06 +- 1.69), depending on availability and presence of flowers during the first sampling event.
+Within each site, we marked between 2 and 12 individuals (6.49 +- 2.37) of 1 to 6 plant species (4.06 +- 1.69), depending on the availability and presence of flowers during the first sampling event.
 For each individual, we counted the number of flowers at the beginning of the season and recorded fruit set, the number of seeds per fruit (for 2-36 fruits, 11.17 +- 6.84) and average seed weight at the end of the season???.
@@
 In order to analyse how differences within the pollinator community might affect plant reproductive success, we constructed weighted interaction networks by pooling the data for the 7 rounds of sampling.
-We thus obtained one weighted interaction network per site representing the frequency of visits by different pollinator species to different plant species.
-For each network we then proceeded to extract a series of relevant network metrics.
+We thus obtained one weighted interaction network per site, representing the frequency of visits by different pollinator species to different plant species.
+For each network, we then proceeded to extract a series of relevant network metrics.
 
@@
 At the species level, we focused on attributes defining the position of a focal plant species within the larger community.
-As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap between a focal species and other plant species in the community, which covers the potential indirect interactions between different plant species through shared resources (in this case pollinators), and (ii) centrality, which depicts the importance of the plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness.
+As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap between a focal plant species and other plant species in the community, which covers the potential indirect interactions between different plant species through shared resources (in this case pollinators), and (ii) centrality, which depicts the importance of the plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness.
 
@@
 However, this approach has been recently shown to present the same issues, as z-scores also change with network size and connectance [@Song2017].
-Given the dependence of nestedness on network size and connectance, we followed the advice of these researchers by using a normalized value of nestedness, NODFc, which is independent of network size and thus comparable across different networks [@Song2017].
+Given the dependence of nestedness on network size and connectance, we followed the advice of these researchers by using a normalized value of nestedness, NODFc, calculated as XXXX, where XXXXX [INCLUDE FORMULA AND DEFINE CONCEPTS], which is independent of network size and thus comparable across different networks [@Song2017].
 All network metrics were calculated using package bipartite [@Dormann2009].
@@
 
-In order to evaluate whether adding information on community structure improves our ability to explain differences in reproductive success both at the species and the community level, we used general linear (GLM) and general linear mixed models (GLMM).
+In order to evaluate whether adding information on community structure improves our ability to explain differences in reproductive success - both at the species and the community level - we used general linear (GLMs) and general linear mixed models (GLMMs).
 In both cases (species and community-level models) we fit two types of models: (i) model 1, that only included simple visitation metrics and (ii) model 2, that additionally included information on community structure.
@@
 At the species level, model 1 included as explanatory variables the diversity of pollinator species visiting a focal plant and the total number of visits received by that plant species; while model 2, added the two network attributes calculated at the species level: average niche overlap and centrality.
-In this case, we included plant species nested within site as a random effect to account for non-independence of several individuals measured for the same plant species within each site.
+In this case, we included plant species nested within site as a random effect to account for the non-independence of several individuals measured for the same plant species within each site.
 The diversity of pollinator species visiting a focal plant was approximated using the plant´s normalised degree, i.e., the number of links with different pollinator species a plant has, scaled by the number of possible partners [@Dormann2009].
@@
 Model 2, in turn, added information on community structure by including nestedness and functional complementarity as explanatory variables.
-
-Average values of reproductive success at the community level can be driven to a large extent by one single plant species.
+As response variable we had the average reproductive success for the whole community (i.e., average fruitset, average number of seeds per fruit previously scaled for each species, average fruit and seed weight).
+We thus, had a single value per site and no random effects are needed in this case.
+
+Average values of reproductive success at the community level can be driven to a large extent by a single plant species.
 Yet, what will determine the persistence of a diverse plant community, is the presence of some sort of “equity” in reproductive success across the whole community.
@@
 We repeated this using 25% and 75% thresholds.
-We then used the same framework as before and fit the same model 1 and model 2 as those used at the community level but using equity in reproductive success as the response variable.
+We then used the same framework as before and fit the same models 1 and 2 as the ones used at the community level, but using equity in reproductive success as the response variable.
 
 We used information criterion methods to find the best model for each case and selected the ones with the lowest Akaike Information Criterion (AIC) value.
-Differences in AIC values < 2, were not considered enough to select one model over the other.
+Differences in AIC values < 2, were not considered enough to select one model over the other [@Burnham2011].
 
@@
 
-Finally, we tested whether the effect of community structure metrics increases with the number of plant species whose reproductive success is being considered.
-We expect that when only one plant species is considered, then the effect of community structure will be negligible.
-Further, we expect this effect to increase in importance as more plant species are considered (up to a maximum number of 6 species which is the maximum we have measured in our study).
-
-To test this, we ran a simple simulation in which the number of species increases randomly (increases randomly or the identity of the sps is selected at random???) at each time step and calculate equity in reproductive success.
-Instead of drawing plants randomly for each run, for each plant number level and network, we test all possible combinations, as this number is low (n = 63 possible combiations overall for the network with the largest dataset) and increasing sampling events in our simulation would only result in repeated combinations.
-Then, we test the overall relation between equity in reproductive success and both community-level network metrics we consider: nestedness and functional complementarity within our simulated communities.
-To this end, for each species number level, we randomly combine the generated equity values across the 16 communities as to obtain one random value per species.
-Finally, for each of such combinations we calculated the estimate of equity in relation with functional complementarity and average all estimates from 1000 simulated combinations per number of plants considered.
+Finally, we tested whether the importance of community structure in explaining differences in reproductive success increases with the number of plant species being considered.
+We expect that when only one plant species is considered, then the importance of community structure will be negligible, while we expect this importance to increase as more plant species are considered (up to a maximum number of 6 species which is the maximum we have measured in our study at a particular site).
+
+To test this, we ran a simple simulation in which the number of species increased randomly at each time step and calculated equity in reproductive success.
+Instead of drawing plants randomly for each run, we tested all possible combinations for each plant number level and network, as this number is low (n = X x X = 63 possible combiations overall for the network with the largest dataset).
+Increasing sampling events in our simulation would only result in repeated combinations.
+Then, we tested the overall relationship between equity in reproductive success and both community-level network metrics we measured: nestedness and functional complementarity within our simulated communities.
+To this end, for each species number level, we randomly combined the generated equity values across the 16 communities as to obtain one random value per species.
+Finally, for each of such combinations we extracted the model estimate from a linear model relating equity in relation with functional complementarity and averaged all estimates from 1,000 simulated combinations per number of plants considered.
 We expect that the more plants considered, the larger the resulting average estimates will be.
@@
 
-Within our sampling we recorded 57 species of plants and 277 species of pollinators. Within the pollinator community XX% of species were solitary bees, XX% hoverflies and XX%% other??
-
-Our sampling completeness analyses revealed that with our survey we were able to capture 18-62% of pollinator species (average= 35%), 47-98% for plant species (average= 78%) and 13-41% for plant-pollinator links (average=27%), in line with that obtained with other studies (e.g., [@Chacoff2012], Figure S1?).
-Our values of sampling completeness are slightly smaller in the case of pollinators probably as a consequence of the great diversity found in the Mediterranean region and within our study area in particular, a hotspot of insect diversity (REF).
+Within our sampling we recorded `r nrow(d)` pollinator individuals belonging to 57 species of plants and 277 species of pollinators.
+Within the pollinator community XX% of species were solitary bees, XX% hoverflies, 20% honeybees, and XX%% other??
 
 ```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=9}
-
-library(citr) #to include citations. use addins to insert references
-
-#First attempt to load the data, etc...
 
@@
 library(BeeFunData)
+
+#devtools::install_github("jonocarroll/mathpix") #package to include mathematical formulas
+library(mathpix)
+
 library(plyr)
@@
 
-#write.csv(f.inds, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/plantindspersite.csv", row.names = FALSE)
+#write.csv(f.inds, file="tables/plantindspersite.csv", row.names = FALSE)
 
@@
 
-#write.csv(f.sps, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/plantspspersite.csv", row.names = FALSE)
+#write.csv(f.sps, file="tables/plantspspersite.csv", row.names = FALSE)
 
@@
 
-#write.csv(s.fruitnum, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/fruitnumberperplantindspersite.csv", row.names = FALSE)
+#write.csv(s.fruitnum, file="tables/fruitnumberperplantindspersite.csv", row.names = FALSE)
 
@@
 out.site<-read.csv("SITE_network_level_metrics.csv")
-
-#####################################################################################################################
-########################CALCULATE SAMPLING COMPLETENESS FOR POLLINATORS, PLANTS AND LINKS #############################
-######################################################################################################################
+```
+
+Our sampling completeness analyses revealed that with our survey we were able to capture 18-62% of pollinator species (average= 35%), 47-98% for plant species (average= 78%) and 13-41% for plant-pollinator links (average=27%), in line with that obtained with other studies (e.g., [@Chacoff2012], Figure S1?).
+Our values of sampling completeness are slightly smaller in the case of pollinators probably as a consequence of the great diversity found in the Mediterranean region and within our study area in particular, a hotspot of insect diversity (REF).
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+
+#######CALCULATE SAMPLING COMPLETENESS FOR POLLINATORS, PLANTS AND LINKS
 
@@
 
-At the species level, our results show that for all measures of reproductive success considered (i.e., fruitset, number of seeds per fruit, fruit and seed weight), the best model based on its AIC value was model 1, i.e., the model that only includes simple visitation metrics (i.e., the diversity of visiting pollinators and the total number of visits received by a focal plant species).
-In the case of fruitset, we find a positive effect of the diversity of species visiting a focal plant species (measured using the species´normalised degree, Fig.
-XX).
-Contrastingly, for seed set, fruit and seed weight we find that none of the variables included within our model explain the differences observed.
+At the species level, our results show that in the case of fruitset, both model 1 and model 2 are equally good in explaining the variability observed (i.e.,$\Delta AIC<2$), and therefore we cannot select one over the other.
+This is despite the fact that model 2 has a greater number of variables and should be penalized for the added complexity it represents.
+We will thus comment results only for model 2, which in the case of fruitset shows a positive effect of the diversity of species visiting a focal plant species (measured using the species´normalised degree, Fig.
+XX) as well as a positive effect of the centrality of the focal plant on its fruitset.
 
 ```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+
+library(ggplot2)
+library(grid)
 
@@
 c2<-round(c,digits=2)
-#write.csv(c2, file= "~/Dropbox/Beefun/Beefun/functioning/tables/variable_correlations.csv", row.names = TRUE, sep = ",")
+#write.csv(c2, file= "tables/variable_correlations.csv", row.names = TRUE, sep = ",")
 
@@
 
-#write.csv(tableSx, file= "C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/plantindspersite.csv", row.names = FALSE, sep = ",")
+#write.csv(tableSx, file= "tables/plantindspersite.csv", row.names = FALSE, sep = ",")
 
@@
 #calculate total number of visits per plant sps
+
+library(plyr)
+
 d.vis<-ddply(d, c("Site_ID", "Plant_gen_sp"), summarise,
@@
 
- m1<-glmer(tot.fruitset ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=f2_scaled)
+ m1<-glmer(tot.fruitset ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2_scaled)
 
@@
 
- m2<-glmer(tot.fruitset ~  norm_degree.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=f2_scaled)
-
- summary(m2)
+ m2<-glmer(tot.fruitset ~  norm_degree.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2_scaled)
+
+ summary(m2) #both norm degree and weigh closeness have intervals not overlapping 0
 
@@
 
-AICtab(m1, m2)
+AICtab(m1, m2) #both are equally good using binomial distribution!!
 
@@
 # extract coefficients and p-values for m1 and present them in paper
-coefs.m1 <- data.frame(coef(summary(m1)))
+coefs.m2 <- data.frame(coef(summary(m2)))
 # use normal distribution to approximate p-value
-coefs.m1$p.z <- 2 * (1 - pnorm(abs(coefs.m1$t.value)))
-coefs.m1
-summ<-round(coefs.m1,digits=2)
-#write.csv(summ, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsfruitsetSPECIES.csv", row.names = TRUE)
-
-#best model is m1, plot significant variable, in this case degree
-
-pl1<-ggplot(f2_scaled,  aes(x=norm_degree.sc, y=tot.fruitset, color=Plant.sp)) +    
-        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+coefs.m2$p.z <- 2 * (1 - pnorm(abs(coefs.m2$z.value)))
+coefs.m2
+summ<-round(coefs.m2,digits=2)
+#write.csv(summ, file="tables/resultsfruitsetSPECIES.csv", row.names = TRUE)
+
+#both models equally good, plot significant variables, in this case degree, do partial residual plots to show the effect of that variable in isolation of the others
+
+#devtools::install_github("hohenstein/remef")  USE THIS PACKAGE TO DO PARTIAL RESIDUAL PLOTS OF SIGNIFICANT VARIABLES
+
+library(remef)
+y_partial_norm <- remef(m2, fix= c( "tot.visits.sc", "weigh_closeness.sc", "niche.overlap.sc"), ran = "all", inverse = F)
+#With this we remove the influece of x2 and the random effects from the dependent variable
+y_partial_norm_inv<-exp(y_partial_norm)/(1+exp(y_partial_norm))
+#then we use this new variable to plot. We use m1@frame as dataset because not all observations are used in modeldue to presence of NAs
+
+pl1<-ggplot(m2@frame,  aes(x=m2@frame$norm_degree.sc[1:325,1], y=y_partial_norm_inv)) +    
+  geom_point(size=4) + stat_smooth(method=lm,  size=1.5, se=TRUE, color = "black", alpha=0.2) + 
   #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
@@
   ylab("Fruitset") + theme_bw()  + theme (legend.position= c(0.85,0.3)) +
-        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species") +  theme(legend.text = element_text(size = 10, face = "italic"), legend.title = element_text(size=11, face = "bold"))
-
-pl1
-
-#no color for different species
-
-pl1b<-ggplot(f2_scaled,  aes(x=norm_degree.sc, y=tot.fruitset)) +    
-        geom_point(size=4, color = "darkgrey") + geom_smooth(method=lm,  size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+  theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + 
+  labs(col="Plant species") +  theme(legend.text = element_text(size = 10, face = "italic"), legend.title = element_text(size=11, face = "bold"))
+
+#pl1
+
+y_partial_weigh <- remef(m2, fix= c( "tot.visits.sc", "norm_degree.sc", "niche.overlap.sc"), ran = "all", inverse = F)
+#With this we remove the influece of x2 and the random effects from the dependent variable
+y_partial_weigh_inv<-exp(y_partial_weigh)/(1+exp(y_partial_weigh))
+
+pl1b<-ggplot(m2@frame,  aes(x=m2@frame$weigh_closeness.sc[1:325,1], y=y_partial_weigh_inv)) +    
+  geom_point(size=4) + stat_smooth(method=lm,  size=1.5, se=TRUE, color = "black", alpha=0.2) + 
   #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
-        xlab("Normalized degree") +      
-        ylab("Fruitset") + theme_bw()  + theme (legend.position= "none") +
-        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
-
-pl1b
-
+  xlab("Centrality") +      
+  ylab("Fruitset") + theme_bw()  + theme (legend.position= c(0.85,0.3)) +
+  theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + 
+  labs(col="Plant species") +  theme(legend.text = element_text(size = 10, face = "italic"), legend.title = element_text(size=11, face = "bold"))
+
+#pl1b
+
+library(cowplot)
+plot_grid(pl1, pl1b, labels = c("A", "B"))
+
+```
+
+Figure X.
+Partial residual plots showing the effect of a) pollinator species diversity (approximated using normalized degree) and b) species centrality on fruitset for each of the plant species considered.
+Dots represent each of the individuals sampled for each species within each site.
+
+For all other measures of reproductive success considered (i.e., the number of seeds per fruit, fruit and seed weight), the best model based on its AIC value was model 1, i.e., the model that only included simple visitation metrics (in this case, the diversity of visiting pollinators and the total number of visits received by a focal plant species).
+In this case, we find that none of the variables included within our model explain the differences observed.
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
 ##ahora con seed set
@@
 
-AICtab(m1.seed, m2.seed)
+AICtab(m1.seed, m2.seed) #m1 here is best model with m2 having a differnce of 4. However m2 has niche overlap as significant.
 
@@
 summ.seed<-round(coefs.m1.seed,digits=2)
-#write.csv(summ.seed, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsseedsetSPECIES.csv", row.names = TRUE)
+#write.csv(summ.seed, file="tables/resultsseedsetSPECIES.csv", row.names = TRUE)
 
 #SEED WEIGHT
-
-m1.seed.w<-glmer(mean.seedw ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s3_scaled)
+library(glmmTMB)
+m1.seed.w<-glmmTMB(mean.seedw ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3_scaled)
 
@@
 
-vif(m1.seed.w)
-
-m2.seed.w<-glmer(mean.seedw ~  norm_degree.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s3_scaled)
+m2.seed.w<-glmmTMB(mean.seedw ~  norm_degree.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3_scaled)
 
 summary(m2.seed.w)
-
-vif(m2.seed.w)
 
@@
 # extract coefficients and p-values for m1 and present them in paper
-coefs.m1.seed.w <- data.frame(coef(summary(m1.seed.w)))
-# use normal distribution to approximate p-value
-coefs.m1.seed.w$p.z <- 2 * (1 - pnorm(abs(coefs.m1.seed.w$t.value)))
-coefs.m1.seed.w
-summ.seed.w<-round(coefs.m1.seed.w,digits=2)
-#write.csv(summ.seed.w, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsseedweightSPECIES.csv", row.names = TRUE)
+summ.seed.w<-summary(m1.seed.w)$coefficients$cond
+#write.csv(summ.seed.w, file="tables/resultsseedweightSPECIES.csv", row.names = TRUE)
 
@@
 
-m1.fruit.w<-glmer(mean.fruitweight ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s3_scaled)
+m1.fruit.w<-glmmTMB(mean.fruitweight ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3_scaled)
 
@@
 
-vif(m1.fruit.w)
-
-m2.fruit.w<-glmer(mean.fruitweight ~  norm_degree.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s3_scaled)
+m2.fruit.w<-glmmTMB(mean.fruitweight ~  norm_degree.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3_scaled)
 
 summary(m2.fruit.w)
-
-vif(m2.fruit.w)
 
@@
 # extract coefficients and p-values for m1 and present them in paper
-coefs.m1.fruit.w <- data.frame(coef(summary(m1.fruit.w)))
-# use normal distribution to approximate p-value
-coefs.m1.fruit.w$p.z <- 2 * (1 - pnorm(abs(coefs.m1.fruit.w$t.value)))
-coefs.m1.fruit.w
-summ.fruit.w<-round(coefs.m1.fruit.w,digits=2)
-#write.csv(summ.seed.w, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsfruitweightSPECIES.csv", row.names = TRUE)
+summ.fruit.w<-summary(m1.fruit.w)$coefficients$cond
+#write.csv(summ.seed.w, file="tables/resultsfruitweightSPECIES.csv", row.names = TRUE)
 
@@
 
-### Network-level analyses
+### Community-level analyses
 
 At the network level, we find different patterns for fruitset and the number of seeds per fruit as compared to those for fruit and seed weight.
-In the case of fruitset and the number of seeds per fruit we find that the best model describing the differences observed is model 2, i.e., that including community-level network attributes in addition to simple visitation metrics.
-In particular, we find that fruitset is positively related to functional complementarity, while we find a similar yet marginal and non-significant trend in the case of the number of seeds per fruit.
+In the case of fruitset and the number of seeds per fruit, we find that both model 1 and 2 are equally good in describing the differences observed (i.e.,$\Delta AIC<2$).
+Again, because this suggests model 2 is a good model despite its added complexity we will comment results for this model only.
+In particular, we find that both fruitset and the number of seeds per fruit are positively related to functional complementarity between pollinators.
 Additionally, we find a negative effect of community-level pollinator species diversity on average fruitset.
-Contrastingly, in the case of weight variables (fruit and seed weight), in both cases we find that the best model is model 1, i.e., that only including simple visitation metrics.
-Here, we find a consistent positive effect of community-level pollinator diversity for both weight descriptors.
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
-#####################################################################################################################
-######################## NTW STRUCTURE ~ ECOSYSTEM FUNCTION #########################################################
-######################################################################################################################
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=10}
+
+######################## NTW STRUCTURE ~ ECOSYSTEM FUNCTION
 
@@
 
-m1.fruit.net<-glm(mean.fruitset ~  species.poll.sc + tot.visits.sc, family="gaussian", data=f.agg)
+m1.fruit.net<-glmmTMB(mean.fruitset ~  species.poll.sc + tot.visits.sc, family="beta_family", data=f.agg)
 
@@
 
-vif(m1.fruit.net)
-
-m2.fruit.net<-glm(mean.fruitset ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="gaussian", data=f.agg)
+m2.fruit.net<-glmmTMB(mean.fruitset ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="beta_family", data=f.agg)
 
@@
 summary(m2.fruit.net)
-
-vif(m2.fruit.net)
 
@@
 
-#when changing values to mean of means actually model2 is best and funct compl is significant!! YUHUUUU
+#test for problems in residuals
+# res<-simulateResiduals(m2.fruit.net)
+# plot(res, rank = TRUE)
+
+#when changing values to mean of means actually model2 is best and funct compl is significant!!
 
 #save table with results for paper
-summ.fruit.net<-round(summary(m2.fruit.net)$coef, digits=2)
-#write.csv(summ.fruit.net, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsfruitsetNETWORK.csv", row.names = TRUE)
+summ.fruit.net<-round(summary(m2.fruit.net)$coefficients$cond, digits=2)
+#write.csv(summ.fruit.net, file="tables/resultsfruitsetNETWORK.csv", row.names = TRUE)
 
@@
 
-pred<-m2.fruit.net$coef[1]+ (m2.fruit.net$coef[2] * mean(f.agg$species.poll.sc)) + (m2.fruit.net$coef[3] * mean(f.agg$tot.visits.sc)) + (m2.fruit.net$coef[4]* mean(f.agg$nodf.song.sc)) + (m2.fruit.net$coef[5] * f.agg$functional.comp.poll.sc)
+pred<-summary(m2.fruit.net)$coefficients$cond[1]+ (summary(m2.fruit.net)$coefficients$cond[2] * mean(f.agg$species.poll.sc)) + (summary(m2.fruit.net)$coefficients$cond[3] * mean(f.agg$tot.visits.sc)) + (summary(m2.fruit.net)$coefficients$cond[4]* mean(f.agg$nodf.song.sc)) + (summary(m2.fruit.net)$coefficients$cond[5] * f.agg$functional.comp.poll.sc)
 
 res<-pred-f.agg$mean.fruitset
-
-pl2 <- ggplot(f.agg,  aes(x=functional.comp.poll.sc, y= res)) +    
-        geom_point(size=4, color="darkgrey") + 
+res.tr<-exp(res)/(1+exp(res)) #transform using logit back transformation
+
+pl2 <- ggplot(f.agg,  aes(x=functional.comp.poll.sc, y= res.tr)) +    
+        geom_point(size=4, color="black") + 
   stat_smooth(method = 'lm', size=1.5, se=TRUE, color = "black", alpha=0.2) +     
@@
 
-#SPECIFIC PACKAGE TO DO PARTIAL RES PLOTS BUT DIFFICULT TO CUSTOMIZE
-
-#partial residual plots to see real value of each variable eliminating noise from others
-library(car)
-
-crPlots(m2.fruit.net, smooth=FALSE, terms = ~  species.poll.sc + functional.comp.poll.sc, main = "", ylab = "Mean fruitset", col.lines= "black", pch=19, col= "black", bg = "darkgrey", cex=2, cex.axis=1.2, cex.lab=1.5,
-        xlab = c("Pollinator diversity", "Functional complementarity"))
-
-#ORINGINAL PLOTS DO NOT SHOW EFFECTS OF VARIABLES IN ISOLATION
-
-pl2<-ggplot(f.agg,  aes(x=species.poll.sc, y=mean.fruitset)) +    
-        geom_point(size=4, color="darkgrey") + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+pred2<-summary(m2.fruit.net)$coefficients$cond[1]+ (summary(m2.fruit.net)$coefficients$cond[2] * f.agg$species.poll.sc) + (summary(m2.fruit.net)$coefficients$cond[3] * mean(f.agg$tot.visits.sc)) + (summary(m2.fruit.net)$coefficients$cond[4]* mean(f.agg$nodf.song.sc)) + (summary(m2.fruit.net)$coefficients$cond[5] * mean(f.agg$functional.comp.poll.sc))
+
+res2<-pred2-f.agg$mean.fruitset
+res.tr2<-exp(res2)/(1+exp(res2))
+
+pl3 <- ggplot(f.agg,  aes(x=species.poll.sc, y= res.tr2)) +    
+        geom_point(size=4, color="black") + 
+  stat_smooth(method = 'lm', size=1.5, se=TRUE, color = "black", alpha=0.2) +     
         xlab("Pollinator species diversity") +      
@@
 
-pl2
-
-pl2b <-ggplot(f.agg,  aes(x=functional.comp.poll.sc, y=mean.fruitset)) +    
-        geom_point(size=4, color="darkgrey") + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
-        xlab("Functional complementarity") +      
-        ylab("Fruitset") + theme_bw()  + #theme (legend.position= "none") +
-        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
-
-pl2b #Well, moderate... without scaling it was more pronunced?
+pl3
 
@@
 # plot(res, rank = TRUE)
+
+library(cowplot)
+plot_grid(pl3, pl2, labels = c("A", "B"))
+
+```
+
+Figure X.
+Partial residual plots showing the effect of a) total pollinator species diversity at the community level and b) functional complementarity between pollinator species on average fruitset at the community level.
+Dots represent average vaues of fruitset at the level of the community for all plant species considered (N=16 sites).
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=10}
 
@@
 #average seed set
-
-m1.seed.net<-glm(mean.seedset ~  species.poll.sc + tot.visits.sc, family="gaussian", data=s.comm)
+#TRY ZERO-INFLATED POISSON!
+
+m1.seed.net <- lm(mean.seedset ~  species.poll.sc + tot.visits.sc,
+    data=s.comm,family="gaussian")
 
@@
 
-vif(m1.seed.net)
-
-m2.seed.net<-glm(mean.seedset ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="gaussian", data=s.comm)
+m2.seed.net <- glm(mean.seedset ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, data=s.comm,family="gaussian")
 
@@
 
-vif(m2.seed.net)
-
 #select best model based on AIC 
-
-AICtab(m1.seed.net, m2.seed.net)
+AICtab(m1.seed.net, m2.seed.net)#both models are equally good
 
 #test for problems in residuals
-# res<-simulateResiduals(m2.seed.net)
+res<-simulateResiduals(m2.seed.net)
 # plot(res, rank = TRUE)
@@
 #save table with results for paper
-summ.seed.net<-round(summary(m2.seed.net)$coef, digits=2)
-#write.csv(summ.seed.net, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsseedsetNETWORK.csv", row.names = TRUE)
-
-#functional comp only marginally significant so no plot here but just to see partial residual plot
-
-crPlots(m2.seed.net, smooth=FALSE, terms = ~  functional.comp.poll.sc, main = "", ylab = "Mean number of seeds per fruit", col.lines= "black", pch=19, col= "black", bg = "darkgrey", cex=2, cex.axis=1.2, cex.lab=1.5,
-        xlab = "Functional complementarity")
+summ.seed.net<-round(summary(m2.seed.net)$coef$cond, digits=2)
+#write.csv(summ.seed.net, file="tables/resultsseedsetNETWORK.csv", row.names = TRUE)
+
+y_partial_seed<-keepef(m2.seed.net, fix= c( "tot.visits.sc", "species.poll.sc ", "nodf.song.sc"), ran = "all", keep.intercept = F, grouping = F)
+
+pl4<-ggplot(s.comm,  aes(x=tot.visits.sc, y=mean.seedset))+      
+        geom_point(size=4, color="black") + stat_smooth(method=lm,  size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Total number of visits") +      
+        ylab("Number of seeds/fruit") + theme_bw()  + #theme (legend.position= "none") +
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
+
+#pl4
+
+pl5<-ggplot(s.comm,  aes(x=functional.comp.poll.sc, y=mean.seedset))+      
+        geom_point(size=4, color="black") + stat_smooth(method=lm,  size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Functional complementarity") +      
+        ylab("Number of seeds/fruit") + theme_bw()  + #theme (legend.position= "none") +
+        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
+
+#pl5
+
+library(cowplot)
+plot_grid(pl4, pl5, labels = c("A", "B")) #NEED TO DO PARTIAL RESIDUAL PLOTS FOR THIS ONE, BUT BECAUSE I DO NOT KNOW WHETHER THIS FIG WILL ALSO GO ON THE MS NOT DOING IT NOW!
+```
+
+Figure X.
+Partial residual plots showing the effect of a) the total number of pollinator visits received at the community level and b) functional complementarity between pollinator species on the scaled average number of seeds per fruit at the community level.
+Dots represent average vaues of previously scaled values of the number of seeds per fruit at the level of the community for all plant species considered (N=16 sites).
+
+Contrastingly, in the case of weight variables (fruit and seed weight), in both cases we find that the best model is model 1, i.e., that only including simple visitation metrics.
+Here, we find a consistent positive effect of community-level pollinator diversity for both weight descriptors.
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=10}
 
@@
 summ.fruitw.net<-round(summary(m1.fruitw.net)$coef, digits=2)
-#write.csv(summ.fruitw.net, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsfruitweightNETWORK.csv", row.names = TRUE)
+#write.csv(summ.fruitw.net, file="tables/resultsfruitweightNETWORK.csv", row.names = TRUE)
 
@@
 
-pl4<-ggplot(s.comm,  aes(x=species.poll.sc, y=mean.fruitweight))+      
-        geom_point(size=4, color="darkgrey") + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+pred3<-m1.fruitw.net$coef[1]+ (m1.fruitw.net$coef[2] * s.comm$species.poll.sc) + (m1.fruitw.net$coef[3] * mean(s.comm$tot.visits.sc)) 
+res3<-pred3-s.comm$mean.fruitweight
+
+#need to see how to change the line of fit
+
+pl6<-ggplot(s.comm,  aes(x=species.poll.sc, y=res3))+      
+        geom_point(size=4, color="black") + stat_smooth(method=lm,  size=1.5, se=TRUE, color = "black", alpha=0.2) + 
         #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
@@
 
-pl4
+pl6
 
@@
 
-AICtab(m1.seedw.net, m2.seedw.net)
+AICtab(m1.seedw.net, m2.seedw.net) #m1 is better
 
@@
 summ.seedw.net<-round(summary(m1.seedw.net)$coef, digits=2)
-#write.csv(summ.fruitw.net, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsseedweightNETWORK.csv", row.names = TRUE)
+#write.csv(summ.fruitw.net, file="tables/resultsseedweightNETWORK.csv", row.names = TRUE)
 
@@
 
-pl5<-ggplot(s.comm,  aes(x=species.poll.sc, y=mean.seedweight))+      
-        geom_point(size=4, color="darkgrey") + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+pred4<-m1.seedw.net$coef[1]+ (m1.seedw.net$coef[2] * s.comm$species.poll.sc) + (m1.seedw.net$coef[3] * mean(s.comm$tot.visits.sc)) 
+res4<-pred4-s.comm$mean.seedweight
+
+#need to see how to change the line of fit
+
+pl7<-ggplot(s.comm,  aes(x=species.poll.sc, y=mean.seedweight))+      
+        geom_point(size=4, color="black") + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
         #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
@@
 
-pl5
+pl7
+
+library(cowplot)
+plot_grid(pl6, pl7, labels = c("A", "B"))
 
 ```
+Figure X.
+Partial residual plots showing the effect of community-level pollinator species diversity on average a) fruit and b) seed weight at the community level.
+Dots represent average vaues of weight at the level of the community for all plant species considered (N=16 sites).
 
@@
 
-When evaluating the effect of differences in community composition and structure for equity in reproductive success across the different plant species, we find that both model 1 and model 2 are equally good (AIC diff < 2) and thus we cannot select one over the other.
-This suggests that, the penalty that should be given to model 2 given its greater complexity (greater number of variables) is smaller than the additional information that is being provided by including data on community structure.
-Specifically, regarding the results for model 2 we find a significant and positive effect of both the total number of visits received by the community and the functional complementarity within it (mean +- sd not overlapping 0, Table X, Fig.
+When evaluating the effect of differences in community composition and structure for equity in reproductive success across the different individuals within a species and site we find that both model 1 and model 2 are equally good (i.e.,$\Delta AIC<2$) and thus we cannot select one over the other.
+Specifically, regarding the results for model 2, we find a significant and positive effect of nestedness for equity between individuals of a species (Table X, Fig.
 X).
-This effect that we find when using a 50% threshold of productivity (i.e., when looking at plant species that are producing 50% of the maximum fruitset observed for the area), is maintained when using 25 and 75% thresholds.
-In the case of the 75% thershold we find an additional positive effect of pollinator species diversity.
-
-ALL THESE RESULTS NOW CHANGE WHEN USING PROPORTION OF SPS RATHER THAN NUMBER, NOTHING IS SIG :()
+This effect that we find when using a 50% threshold of productivity (i.e., when looking at plant species that are producing 50% of the maximum fruitset observed for the area), is however not maintained when using 25 and 75% thresholds.
+In particular, when using a 25% threshold we find model 1 is the best model and none of the variables considered are able to explain the differences observed.
+Contrastingly in the case of the 75% threshold, we find again that both model 1 and 2 are equally plausible but in this case we find a positive effect of functional complementarity between pollinators for equity in fruitset across individuals within a species.
 
 ```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+
+#EQUITY IN INDIVIDUALS WITHIN SPECIES
+
 #calculate column with fruit set as
@@
 library(vegan)
-library(dplyr)
+library(plyr)
 
@@
 
-f4 <- ddply(f3, c("Site_ID", "Plant.sp"), summarise,
-                         mean.fruitset    = mean(tot.fruitset))
-
-#f4
-
-fr.max<-aggregate(.~ Plant.sp, f4, FUN=max)
-
-f4$fruit.max<-fr.max$mean.fruitset[match(f4$Plant.sp, fr.max$Plant.sp)]
-
-f4$fruit.prop<-f4$mean.fruitset/f4$fruit.max
-f5<-subset(f4, f4$fruit.prop>0.5)
+fr.max<-aggregate(.~ Plant.sp, f3, FUN=max)
+
+f3$fruit.max<-fr.max$tot.fruitset[match(f3$Plant.sp, fr.max$Plant.sp)]
+
+f3$fruit.prop<-f3$tot.fruitset/f3$fruit.max
+f5<-subset(f3, f3$fruit.prop>0.5)
 f5$no_rows<-rep(1, nrow(f5))
@@
 #for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
-f6<- aggregate(no_rows ~ Site_ID, f5, length)
+f6<- aggregate(no_rows ~ Site_ID + Plant.sp, f5, length)
 head(f6)
@@
 
-f4$no_rows<-rep(1, nrow(f4))
-f4b<- aggregate(no_rows ~ Site_ID, f4, length)
-head(f4b)
-
-f6$total.plant.numb<-f4b$no_rows[match(f6$Site_ID, f4b$Site_ID)]
+f3$no_rows<-rep(1, nrow(f3))
+f3b<- aggregate(no_rows ~ Site_ID + Plant.sp, f3, length)
+head(f3b)
+
+f3b$j<- paste(f3b$Site_ID, f3b$Plant.sp)
+f6$j<- paste(f6$Site_ID, f6$Plant.sp)
+
+f6$total.plant.numb<-f3b$no_rows[match(f6$j, f3b$j)]
 f6$equity<-f6$no_rows/f6$total.plant.numb
@@
 #fit two models
- m1.eq<-glm(equity ~  species.poll.sc + tot.visits.sc, family="binomial", data=f6)
+m1.eq<-glmer(equity ~  species.poll.sc + tot.visits.sc + (1|Site_ID), family="binomial", data=f6)
 
@@
 
-m2.eq<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="binomial", data=f6)
+m2.eq<-glmer(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc+ (1|Site_ID), family="binomial", data=f6)
 #nich estimate not overlaping zero: 0.6178     0.4354, second higher effect size!
@@
 AICtab(m1.eq, m2.eq) #Almost equal... Again, for prediction, go with the simple, for mechanistic understanding, look into niche partitioning. 
-
-#save table with results for paper, both models are equally good so save both tables
-summ.eq<-round(summary(m1.eq)$coef, digits=2)
-#write.csv(summ.eq, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsequityNETWORKm1.csv", row.names = TRUE)
-
-summ.eq2<-round(summary(m2.eq)$coef, digits=2)
-#write.csv(summ.eq2, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsequityNETWORKm2.csv", row.names = TRUE)
-
-#partial residual plots
-
-crPlots(m2.eq, smooth=FALSE, terms = ~  tot.visits.sc + functional.comp.poll.sc, main = "", ylab = "Equity in fruitset", col.lines= "black", pch=19, col= "black", bg = "darkgrey", cex=2, cex.axis=1.2, cex.lab=1.5)
-
-pl.th_ <-ggplot(f6,  aes(x=functional.comp.poll.sc, y=no_rows))+      
-        geom_point(size=4, color="darkgrey") + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+library(remef)
+y_partial_eq <- remef(m2.eq, fix = c("species.poll.sc", "tot.visits.sc", "functional.comp.poll.sc"), ran = "all", inverse = F)
+y_partial_eq_inv<-exp(y_partial_eq)/(1+exp(y_partial_eq))
+
+pl.th_ <-ggplot(f6,  aes(x=nodf.song.sc, y=y_partial_eq_inv ))+      
+  geom_point(size=4, color="black") + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) +  ylim(0,1.1) +
+  xlab("Nestedness") +      
+  ylab("Equity in fruitset") + theme_bw() + 
+  theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
+
+#pl.th_ #oh yeah!
+
+#now 75% threshold
+f5.75<-subset(f3, f3$fruit.prop>0.75)
+f5.75$no_rows<-rep(1, nrow(f5.75))
+head(f5.75)
+
+#NOTE TO SELF: Here is where we want to subsample 1 to 6 species per site to test the idea of increasing plants, complementarity increase.
+
+#for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
+f6.75<- aggregate(no_rows ~ Site_ID + Plant.sp, f5.75, length)
+head(f6.75)
+
+#because when calculating thresholds, sites with 6 plants can score up to 6, but sites with 4 sites can oscar max = 4 we corrected for this doing % above threshold, and no number.
+
+f3$no_rows<-rep(1, nrow(f3))
+f3b<- aggregate(no_rows ~ Site_ID + Plant.sp, f3, length)
+head(f3b)
+
+f3b$j<- paste(f3b$Site_ID, f3b$Plant.sp)
+f6.75$j<- paste(f6.75$Site_ID, f6.75$Plant.sp)
+
+f6.75$total.plant.numb<-f3b$no_rows[match(f6.75$j, f3b$j)]
+f6.75$equity<-f6.75$no_rows/f6.75$total.plant.numb
+
+#join this with fruitset data used previously
+
+f6.75$nodf.song<-out.site$nodf.song[match(f6.75$Site_ID, out.site$Site_id)]
+f6.75$functional.comp.poll<-out.site$functional.comp.poll[match(f6.75$Site_ID, out.site$Site_id)]
+f6.75$species.poll<-out.site$species.poll[match(f6.75$Site_ID, out.site$Site_id)]
+f6.75$tot.visits<-f.agg$tot.visits[match(f6.75$Site_ID, f.agg$Site_ID)]
+
+#scale all variables
+
+f6.75$nodf.song.sc <- scale(f6.75$nodf.song, center = T, scale = T)
+f6.75$functional.comp.poll.sc <- scale(f6.75$functional.comp.poll, center = T, scale = T)
+f6.75$species.poll.sc <- scale(f6.75$species.poll, center = T, scale = T)
+f6.75$tot.visits.sc <- scale(f6.75$tot.visits, center = T, scale = T)
+
+#fit two models
+m1.eq.75<-glmer(equity ~  species.poll.sc + tot.visits.sc + (1|Site_ID), family="binomial", data=f6.75)
+
+summary(m1.eq.75)
+
+m2.eq.75<-glmer(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc+ (1|Site_ID), family="binomial", data=f6.75)
+#nich estimate not overlaping zero: 0.6178     0.4354, second higher effect size!
+summary(m2.eq.75)
+
+#select best model based on AIC
+
+AICtab(m1.eq.75, m2.eq.75) #Almost equal... Again, for prediction, go with the simple, for mechanistic understanding, look into niche partitioning. 
+library(remef)
+y_partial_eq.75 <- remef(m2.eq.75, fix = c("species.poll.sc", "tot.visits.sc", "nodf.song.sc"), ran = "all", inverse = F)
+y_partial_eq.75_inv<-exp(y_partial_eq.75)/(1+exp(y_partial_eq.75))
+
+pl.th_75 <-ggplot(f6.75,  aes(x=functional.comp.poll.sc, y=y_partial_eq.75_inv ))+      
+  geom_point(size=4, color="black") + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + ylim(0,1.1) +
   xlab("Functional complementarity") +      
@@
 
-pl.th_ #oh yeah!
-
-pl.th<-ggplot(f6,  aes(x=tot.visits.sc, y=no_rows))+      
-        geom_point(size=4, color="darkgrey") + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
-        xlab("Total number of visits") +      
-        ylab("Equity in fruitset") + theme_bw() + 
-        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
-
-pl.th
-
--------------------------------------------------------------------------------
-
-m3.eq_ <-glm(no_rows ~ functional.comp.poll.sc, family="gaussian", data=f6)
- #Oh yeah. It works for doing my null simulation.
- summary(m3.eq_)
+#pl.th_75 #oh yeah!
+
+library(cowplot)
+plot_grid(pl.th_, pl.th_75, labels = c("A", "B"))
+
+#now 25% threshold
+f5.25<-subset(f3, f3$fruit.prop>0.25)
+f5.25$no_rows<-rep(1, nrow(f5.25))
+head(f5.25)
+
+#NOTE TO SELF: Here is where we want to subsample 1 to 6 species per site to test the idea of increasing plants, complementarity increase.
+
+#for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
+f6.25<- aggregate(no_rows ~ Site_ID + Plant.sp, f5.25, length)
+head(f6.25)
+
+#because when calculating thresholds, sites with 6 plants can score up to 6, but sites with 4 sites can oscar max = 4 we corrected for this doing % above threshold, and no number.
+
+f3$no_rows<-rep(1, nrow(f3))
+f3b<- aggregate(no_rows ~ Site_ID + Plant.sp, f3, length)
+head(f3b)
+
+f3b$j<- paste(f3b$Site_ID, f3b$Plant.sp)
+f6.25$j<- paste(f6.25$Site_ID, f6.25$Plant.sp)
+
+f6.25$total.plant.numb<-f3b$no_rows[match(f6.25$j, f3b$j)]
+f6.25$equity<-f6.25$no_rows/f6.25$total.plant.numb
+
+#join this with fruitset data used previously
+
+f6.25$nodf.song<-out.site$nodf.song[match(f6.25$Site_ID, out.site$Site_id)]
+f6.25$functional.comp.poll<-out.site$functional.comp.poll[match(f6.25$Site_ID, out.site$Site_id)]
+f6.25$species.poll<-out.site$species.poll[match(f6.25$Site_ID, out.site$Site_id)]
+f6.25$tot.visits<-f.agg$tot.visits[match(f6.25$Site_ID, f.agg$Site_ID)]
+
+#scale all variables
+
+f6.25$nodf.song.sc <- scale(f6.25$nodf.song, center = T, scale = T)
+f6.25$functional.comp.poll.sc <- scale(f6.25$functional.comp.poll, center = T, scale = T)
+f6.25$species.poll.sc <- scale(f6.25$species.poll, center = T, scale = T)
+f6.25$tot.visits.sc <- scale(f6.25$tot.visits, center = T, scale = T)
+
+#fit two models
+m1.eq.25<-glmer(equity ~  species.poll.sc + tot.visits.sc + (1|Site_ID), family="binomial", data=f6.25)
+
+summary(m1.eq.25)
+
+m2.eq.25<-glmer(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc+ (1|Site_ID), family="binomial", data=f6.25)
+#nich estimate not overlaping zero: 0.6178     0.4354, second higher effect size!
+summary(m2.eq.25)
+
+#select best model based on AIC
+
+AICtab(m1.eq.25, m2.eq.25) #m1 is better.
+
+```
+Figure X.
+Partial residual plots showing the effect of a) nestedness and b) functional complementarity on equity in reproductive success between individuals of a species within a site, measured as the proportion of individuals producing at least 50% or 75% of maximum fruitset observed for the study area respectively.
+Dots represent values for each species within a site (N=63)
+
+Contrastingly, in the case of equity in average reproductive success across species within a site we find that model 1, the one including only simple visitation metrics is the best one, and we find none of the variables explain the differences observed at any of the thresholds considered (25, 50 and 75%).
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+
+#EQUITY SPECIES WITHIN COMMUNITIES
+
+f4 <- ddply(f3, c("Site_ID", "Plant.sp"), summarise,
+                         mean.fruitset    = mean(tot.fruitset))
+
+#f4
+
+fr.max.comm<-aggregate(.~ Plant.sp, f4, FUN=max)
+
+f4$fruit.max<-fr.max.comm$mean.fruitset[match(f4$Plant.sp, fr.max.comm$Plant.sp)]
+
+f4$fruit.prop<-f4$mean.fruitset/f4$fruit.max
+
+f4b<-subset(f4, f4$fruit.prop>0.5)
+f4b$no_rows<-rep(1, nrow(f4b))
+head(f4b)
+
+#NOTE TO SELF: Here is where we want to subsample 1 to 6 species per site to test the idea of increasing plants, complementarity increase.
+
+#for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
+f4c<- aggregate(no_rows ~ Site_ID, f4b, length)
+head(f4c)
+
+#because when calculating thresholds, sites with 6 plants can score up to 6, but sites with 4 sites can score max = 4 we corrected for this doing % above threshold, and no number.
+
+f4$no_rows<-rep(1, nrow(f4))
+f4d<- aggregate(no_rows ~ Site_ID, f4, length)
+head(f4d)
+
+f4c$total.plant.numb<-f4d$no_rows[match(f4c$Site_ID, f4d$Site_ID)]
+f4c$equity<-f4c$no_rows/f4c$total.plant.numb
+
+#join this with fruitset data used previously
+
+f4c$nodf.song<-out.site$nodf.song[match(f4c$Site_ID, out.site$Site_id)]
+f4c$functional.comp.poll<-out.site$functional.comp.poll[match(f4c$Site_ID, out.site$Site_id)]
+f4c$species.poll<-out.site$species.poll[match(f4c$Site_ID, out.site$Site_id)]
+f4c$tot.visits<-f.agg$tot.visits[match(f4c$Site_ID, f.agg$Site_ID)]
+
+#scale all variables
+
+f4c$nodf.song.sc <- scale(f4c$nodf.song, center = T, scale = T)
+f4c$functional.comp.poll.sc <- scale(f4c$functional.comp.poll, center = T, scale = T)
+f4c$species.poll.sc <- scale(f4c$species.poll, center = T, scale = T)
+f4c$tot.visits.sc <- scale(f4c$tot.visits, center = T, scale = T)
+
+#fit two models
+ m1.eq.comm<-glm(equity ~  species.poll.sc + tot.visits.sc, family="binomial", data=f4c)
+
+ summary(m1.eq.comm)
+
+ m2.eq.comm<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="binomial", data=f4c)
+summary(m2.eq.comm)
+
+#select best model based on AIC
+
+AICtab(m1.eq.comm, m2.eq.comm)
+
+#save table with results for paper, both models are equally good so save both tables
+summ.eq<-round(summary(m1.eq)$coef, digits=2)
+#write.csv(summ.eq, file="tables/resultsequityNETWORKm1.csv", row.names = TRUE)
+
+#partial residual plots
 
@@
 
-# 
-# #check whether it is driven by that one point with large number of visits
-# 
-# f7 <- subset(f6, f6$tot.visits.sc < 2)
-# 
-#  m1.eqb<-glm(no_rows ~  species.poll.sc + tot.visits.sc, family="gaussian", data=f7)
-# 
-#  summary(m1.eqb)
-#  
-#  
-#  
-# pl.th2<-ggplot(f7,  aes(x=tot.visits.sc, y=no_rows))+      
-#         geom_point(size=4, color="darkgrey") + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
-#         xlab("Total number of visits") +      
-#         ylab("Equity in fruitset") + theme_bw() + 
-#         theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) 
-# 
-# pl.th2
-#
-
 #Repeat with 75% threshold
@@
 head(f75b)
-f75b$total.numb.plants<-f6$total.plant.numb[match(f75b$Site_ID, f6$Site_ID)]
+f75b$total.numb.plants<-f4d$no_rows[match(f75b$Site_ID, f4d$Site_ID)]
 f75b$equity<-f75b$no_rows/f75b$total.numb.plants
@@
 
- m1.eq.75<-glm(equity ~  species.poll.sc + tot.visits.sc, family="gaussian", data=f75b)
+ m1.eq.75<-glm(equity ~  species.poll.sc + tot.visits.sc, family="binomial", data=f75b)
 
@@
 
-m2.eq.75<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="gaussian", data=f75b)
+m2.eq.75<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="binomial", data=f75b)
 
@@
 head(f25b)
-f25b$total.numb.plants<-f6$total.plant.numb[match(f25b$Site_ID, f6$Site_ID)]
+f25b$total.numb.plants<-f4d$no_rows[match(f25b$Site_ID, f4d$Site_ID)]
 f25b$equity<-f25b$no_rows/f25b$total.numb.plants
+
+#join this with fruitset data used previously
 
@@
 
- m1.eq.25<-glm(equity ~  species.poll.sc + tot.visits.sc, family="gaussian", data=f25b)
+ m1.eq.25<-glm(equity ~  species.poll.sc + tot.visits.sc, family="binomial", data=f25b)
 
@@
 
-m2.eq.25<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="gaussian", data=f25b)
+m2.eq.25<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="binomial", data=f25b)
 
@@
 
-AICtab(m1.eq.25, m2.eq.25)
-
-#test for problems in residuals
+AICtab(m1.eq.25, m2.eq.25) #as before both models are equally good.
+
+# #test for problems in residuals
 # res<-simulateResiduals(m1.eq.25)
@@
 
-##equity in seed number
+##equity in seed number???
 
@@
 ```
+
+###Simulating the effect of community structure as sample size increases
+
+CHECK THIS IN LIGHT OF NEW RESULTS!!
 
@@
 #DISCUSSION
-Importance of functional complementarity found in artificial [@Frund2013] and natural [@Fontaine2005] communities.
-
-The analysis of natural communities of interacting species using network analysis represents an ideal way of visualizing and grasping the complexity present.
-
-we have yet to know whether these variables contribute more to plant reproductive success than others related to the position of a particular plant species within the wider plant community that hosts it.
-In particular, our study focuses on the importance of pollinator diversity and total number of visits for plant reproductive success in comparison to that of the plant´s position in the community.
-Specifically, niche overlap between plant species (which could give us a proxy for the existence of competition for pollination between plant species) and the position of the plant given by the connections it establishes with other species, e.g.
-its centrality within the network, where central species are those receiving the greatest number of connections from other species, could have an influence in a plant´s reproductive success.
-
-Furthermore, we do not know how the overall structure of a community, and the architecture of the network of interactions it hosts, affects the reproductive success of the whole community.
-In particular, one of the networks metrics that has received the most attention in the community ecology literature is that of nestedness.
-Nestedness is the property by which specialists interact with a subset of the species that generalists interact with.
-Although there is ongoing debate in the literature, some studies have found that more nested networks are more stable and resilient to perturbations because nestedness implies a certain level of redundancy and thus the possibility for functional replacement in the case of species loss.
-However, plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence.
-Yet at present we do not know how the interplay between redundancy and complementarity determines reproductive success.
-Finally, average values of reproductive success at the community level can be driven to a large degree by one single plant species.
-Yet, what will determine the persistence of a diverse plant community is the presence of some sort of “equity” in reproductive success across the whole community.
-We thus also focus on the effect of community structure for equity in reproductive success across the plant community.
+
+The relationship between community structure and ecosystem function has been long suggested, yet the specific mechanisms by which structure influences function remain elusive.
+Our results show that different aspects of community structure affect different dimensions of functioning.
+In particular, we find that the functional complementarity between pollinators, a measure of the overlap in the niches of different species in terms of plant coverage, has an important effect for direct measures of reproductive success (e.g., fruitset).
+However, we also find that nestedness, a measure of the redundancy in ecological functions between pollinators is important in determining a stable and equitable function across whole communities.
+
+One of the first conclusions we can extract from the fact that in most cases both of the models we considered (i.e., the simple model based on visitation metrics and the more complex one including community structure metrics) were equally good, is that for simple predictive purposes, simple visitation metrics, such as the diversity of pollinators visiting a plant, might be enough.
+Yet, a mechanistic understanding of the underlying processes requires that we take into account measures of community structure.
+
+Consistent with previous studies in artificial [@Frund2013] and natural [@Fontaine2005] communities, we find that functional complementarity is very important in determining differences in reproductive outputs.
+Indeed, this reflects the fact that reproductive success in plant species requires of the delivery of conspecific pollen and thus of a certain degree of specialization amongst pollinator species on a particular plant resource in order to avoid the negative effects of inter-specific pollen deposition (e.g., pollen loss [@Flanagan2009] or interference with conspecific pollen [@Morales2008]).
+
+Nevertheless, we also find that redundancy in pollinator functions is also important in determining a certain stability in the pollination service across a larger number of individuals within a plant species.
+Indeed, our results also support previous accounts of the importance of nestedness for plant-pollinator communities [@Bascompte2003] as it ensures that reproductive success is distributed amongst a larger number of individuals, thus ensuring the maintenance of a greater genetic diversity in natural populations.
+This aspect of reproductive, which is seldom taken into account, is however of great importance, as genetic diversity will ensure the resilience of populations to further change.
+
+Our findings show that the analysis of natural communities of interacting species using network analysis not only represents an ideal way of visualizing and grasping the complexity present, but also represents a manner of mechanisitically understanding differences observed across individuals and/or species.
+
+Future studies should focus on the long-lasting effects of community structure for plant fitness, by evaluating the consequences of different community structures for heritability.
+
+##References

### 2019-02-26 paper_round2.Rmd
Comments varios.

@@
 author: "Magrach, A, Molina, FP, Bartomeus, I"
-date: "6 November 2018"
 output: html_document
@@
 Title: Impact of interaction network structure on community-level plant reproduction success  
+or "Interaction network structure maximizes community-level plant reproduction success via [niche complmentariety?]()"
 
@@
 We find that, for prediction purposes, information on simple visitation metrics is sufficient.
-Contrastingly, a mechanisitic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success, requires additional information on network structure.
+Contrastingly, a mechanisitic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success, requires additional information on network structure [such as...]().
 
@@
 Pollinators provide key services to plants by facilitating pollen flow between individuals.
-The recent declining trends found for some pollinator species in some regions of the planet ([@Potts2010], although see [@Herrera2018] for opposite trends), have led many researchers to focus on the functional impacts of these changes in pollinator diversity, with a major focus being placed on the consequences for plant reproductive success [@Biesmeijer2006].
+The recent declining trends found for some pollinator species in some regions of the planet ([@Potts2010], although see [@Herrera2018] for opposite trends[IB: I think Herrea paper is not needed here, as is quite local.
+My 2018 Phil Trans paper sumarizs the lack of knowledge for the world]()), have led many researchers to focus on the functional impacts of these changes in pollinator diversity, with a major focus being placed on the consequences for plant reproductive success [@Biesmeijer2006].
 
 Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012a; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain differences found  across different plant individuals.
-Some have gone a step further by including information on the efficiency of these visits, thus adding a measure of quality to the pollination services (REF).
+Some have gone a step further by including information on the efficiency of these visits, thus adding a measure of quality to the pollination services (REF[I only know refs for crops, e.g.
+winfree.
+Check Morris Ecology 2010 to see if there is something tehere]()).
 Contrastingly, community-level analyses remain scarce [@Bennett2018].
 Yet plants and pollinators do not interact in isolation, but rather are embedded within larger networks of interactions encompassing other plant and pollinator species.
-We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect ones between species within one guild (e.g., plants) through their shared resources [@Lazaro2014].
-Understanding how changes in pollinator diversity affect whole community assemblages is thus a major challenge that requires attention.
+We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect ones between species within one guild (e.g., plants) through their shared resources [@Lazaro2014, [Carvalheiro et al 2014 Ecol Lett, and Mayfield ans Stouffer 2017 Nature EcoEvo]()].
+Understanding how changes in pollinator diversity [diversity or interaction structure?]() affect whole community assemblages is thus a major challenge that requires attention.
 
@@
 Indeed, theoretical research has long suggested that the structure of a community has an effect for ecosystem functioning (reviewed in [@Thompson2012]).
-This line of research, primarliy driven by food-web studies, has greatly advanced theory, but these ideas have not yet been tested using empirical data.
+This line of research, primarliy driven by food-web studies, has greatly advanced theory, but these ideas have not yet been tested using empirical data [(but see Poisot and Gravel Ecol Let?)]().
 Specifically, a major knowledge gap resides in understading which aspects of structure determine which aspects of function [@Thompson2012].
-We are now at a point in which there is considerable understanding on the attributes of interaction networks (REF, REF, REF).
-Even further, we now have a substantial understanding of how these attributes vary along different types of gradients [@Pellissier2017; @Tylianakis2016].
-Especially, in the case of pollination, we have ample knowledge on the attributes that shape these mutualistic interactions at the community level, such as a prevalence of nested structures (REF) or the presence of asymmetric specialization as a pervasive feature [@Vazquez2004].
+We are now at a point in which there is considerable understanding on the attributes characterizing mutualistic interaction networks ([Bacompte and H¿JOrdano AREES review]() REF, REF, REF) and we have a substantial understanding of how these attributes vary along different types of gradients [@Pellissier2017; @Tylianakis2016].
+Especially, in the case of pollination, we have ample knowledge on the attributes that shape these mutualistic interactions at the community level, such as a prevalence of nested structures ([Bascompte et al 2013 PNAS]()) or the presence of asymmetric specialization as a pervasive feature [@Vazquez2004].
+However, how the structure formed by this network of interactions afects key ecosystem functions such as plant reproduction remains untested [(Winfree BAAE opinion paper is good to cite "Global change, biodiversity, and ecosystem services: What can we learn from 6 studies of pollinators?")]().
 The time is thus ripe to use this knowledge to explore relationships between community structure and ecosystem functioning, with special emphasis being placed on the underlying mechanisms that drive these relationships.
@@
 Our study focuses on understanding whether adding information on the structure of the community to previously-used simple visitation metrics (e.g., number of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success.
-In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success.
+In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success [and equity acorss species.]()
 
@@
 
+[IB: this intro is brilliant!]()
+
 # METHODS
@@
 Here, we surveyed 16 Mediterranean woodland patches, located within a XXX m2 area and with an average distance of XX km between them (min= XX, max= XX).
-[SHOULD WE SAY SOMETHING ABOUT THE MATRIX SURROUNDING THESE SITES OR THE TYPE OF VEGETATION PRESENT IN THEM???] Each site was surveyed 7 times during the flowering season of 2015??
-(February-July???) following a 100-m x 2 m transect for 30 mins.
-Along each transect, we identified all plant species and recorded all the flower visitors (IS IT JUST BEES AND HOVERFLIES?) that legitimately visited them.
+[SHOULD WE SAY SOMETHING ABOUT THE MATRIX SURROUNDING THESE SITES OR THE TYPE OF VEGETATION PRESENT IN THEM???
+IB: I don't think is relevant.
+ASK CURRO ABOUT THE NUMBERS ABOVE.]() Each site was surveyed 7 times during the flowering season of 2015 (from February to May) following a 100-m x 2 m transect for 30 mins.
+Along each transect, we identified all plant species and recorded all the flower visitors [IS IT JUST BEES AND HOVERFLIES?
+IB: NO, ALL VISITORS!]() that legitimately visited them.
 Floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FdPM with the aid of experts in the different taxonomic groups (see acknowledgements).
@@
 
-Within each site, we marked between 2 and 12 individuals (6.49 +- 2.37) of 1 to 6 plant species (4.06 +- 1.69), depending on the availability and presence of flowers during the first sampling event.
-For each individual, we counted the number of flowers at the beginning of the season and recorded fruit set, the number of seeds per fruit (for 2-36 fruits, 11.17 +- 6.84) and average seed weight at the end of the season???.
-Our survey included a total of 19 plant species across our 16 sites.
+Within each site, we marked between 2 and 12 individuals (6.49 +- 2.37) of 1 [NB: Which site has only one species!]() to 6 plant species (4.06 +- 1.69), depending on the availability and presence of flowers during the sampling events.
+For each individual, we counted the number of flowers at each sampling point and recorded fruit set, the number of seeds per fruit (for 2-36 fruits, 11.17 +- 6.84) and average seed weight per fruit at the end of the season.
+Our survey included a total of 19 different plant species across our 16 sites.
 
@@
 In this case we focused on (i) nestedness and (ii) functional complementarity.
-Nestedness is the property by which specialists interact with a subset of the species that generalists interact with (REF).
+Nestedness is the property by which specialists interact with a subset of the species that generalists interact with ([Bascompte et al 2003 PNAS]).
 Although there is an ongoing debate in the literature, some studies have found that nested networks are more stable and resilient to perturbations because nestedness implies a certain level of redundancy and thus the possibility for functional replacement in the case of species loss (REF).
-However, plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence (reviewed in [@Brosi2016]).
+[We used the widely accepted NODF metric to calculate Nestedness]() However, plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence (reviewed in [@Brosi2016]).
 Yet at present we do not know how the interplay between redundancy and complementarity in species roles determines reproductive success.
+[To calculate functional complmentariey we used ...]().
+All network analysis were perfeormed using bipartite package.
 
@@
 Model 2, in turn, added information on community structure by including nestedness and functional complementarity as explanatory variables.
-As response variable we had the average reproductive success for the whole community (i.e., average fruitset, average number of seeds per fruit previously scaled for each species, average fruit and seed weight).
+As response variable we had the average reproductive success for the whole community (i.e., average fruitset, average number of seeds per fruit previously scaled for each species, and average fruit and seed weight [IB: also scaled?]()).
 We thus, had a single value per site and no random effects are needed in this case.
@@
 We then used the same framework as before and fit the same models 1 and 2 as the ones used at the community level, but using equity in reproductive success as the response variable.
+[Here is unclear how the proportion is calculated.
+This is: average fruit set per species is > 50%?
+Or as we discussed a more coplex option can be: % of species which > 50 % of individuals had seed set > 50%.
+Now that I see this I would only used if we gain a lot, otherwise is too complicated.
+Also, I removed species present is only one (or two) sites for this analysis, because the % was forces to be 1.
+If you kept this in your analysis, should be explained]().
 
@@
 
-To test this, we ran a simple simulation in which the number of species increased randomly at each time step and calculated equity in reproductive success.
-Instead of drawing plants randomly for each run, we tested all possible combinations for each plant number level and network, as this number is low (n = X x X = 63 possible combiations overall for the network with the largest dataset).
-Increasing sampling events in our simulation would only result in repeated combinations.
+To test this, we ran a simple simulation in which the number of species considered increased at each time step and for each time step we re-calculated equity in reproductive success.
+Instead of drawing plant species randomly for each run, we tested all possible combinations for each plant number level and network, as the number of combinations is low (e.g.
+for n = 3 plant selected out of 6 there is only 20 possible combiations).
 Then, we tested the overall relationship between equity in reproductive success and both community-level network metrics we measured: nestedness and functional complementarity within our simulated communities.
-To this end, for each species number level, we randomly combined the generated equity values across the 16 communities as to obtain one random value per species.
-Finally, for each of such combinations we extracted the model estimate from a linear model relating equity in relation with functional complementarity and averaged all estimates from 1,000 simulated combinations per number of plants considered.
+To this end, for each species number level considered, we randomly selected one of the generated equity values across each of the 16 communities, regress this against our netrok level predictors and extracted the model estimates.
+We averaged all estimates from 1,000 simulated combinations per number of plants considered.
 We expect that the more plants considered, the larger the resulting average estimates will be.
@@
 Within the pollinator community XX% of species were solitary bees, XX% hoverflies, 20% honeybees, and XX%% other??
+[Curro can calculate this if needed]()
 
@@
 d<-all_interactions
+#head(d)
+#I just realized here we are using all data available. 
+#This is ok, but a few rare interactions are taken outside the transect (which can be removed?), and we are including focal 3' observations, which can be explained in methods.
+#d <- subset(d, subset = Out != "out") #SHould we do that?
 f<-fruitset
@@
 
-d4 <- t(d3[,1:277])
+d4 <- t(d3[,1:ncol(d3)]) #I updated this to use defensive programming.
 #head(d4)
@@
 
-At the species level, our results show that in the case of fruitset, both model 1 and model 2 are equally good in explaining the variability observed (i.e.,$\Delta AIC<2$), and therefore we cannot select one over the other.
-This is despite the fact that model 2 has a greater number of variables and should be penalized for the added complexity it represents.
-We will thus comment results only for model 2, which in the case of fruitset shows a positive effect of the diversity of species visiting a focal plant species (measured using the species´normalised degree, Fig.
+At the species level, our results show that in the case of fruitset, both model 1 and model 2 are equally good in explaining the variability observed when accounting for model complexity (i.e.,$\Delta AIC<2$), and therefore we cannot select one over the other.
+Given that model 2 has a greater number of variables which penalize for the added complexity, we will thus comment results only for model 2, which in the case of fruitset shows a positive effect of the diversity of species visiting a focal plant species (measured using the species´normalised degree, Fig.
 XX) as well as a positive effect of the centrality of the focal plant on its fruitset.
@@
 
-  ni<-niche.overlap(web, method="morisita")
+  ni<-niche.overlap(web, method="morisita") #THIS SHOULD BE EXPLAINED IN METHODS
   df <- melt(as.matrix(ni), varnames = c("row", "col"))
@@
 
+#devtools::install_github("hohenstein/remef")
 library(remef)
@@
 For all other measures of reproductive success considered (i.e., the number of seeds per fruit, fruit and seed weight), the best model based on its AIC value was model 1, i.e., the model that only included simple visitation metrics (in this case, the diversity of visiting pollinators and the total number of visits received by a focal plant species).
-In this case, we find that none of the variables included within our model explain the differences observed.
+However, none of the variables included within our model explain the differences observed.
+[show in sup mat?]()
 
@@
 Contrastingly in the case of the 75% threshold, we find again that both model 1 and 2 are equally plausible but in this case we find a positive effect of functional complementarity between pollinators for equity in fruitset across individuals within a species.
+[this is interesting, as selfing rates I expect to be ~ 40%... In any case I am confused now on this calculation]()
 
@@
 head(f5)
-
-#NOTE TO SELF: Here is where we want to subsample 1 to 6 species per site to test the idea of increasing plants, complementarity increase.
 
@@
 #now 75% threshold
+#head(f3)
 f5.75<-subset(f3, f3$fruit.prop>0.75)
@@
 head(f5.75)
-
-#NOTE TO SELF: Here is where we want to subsample 1 to 6 species per site to test the idea of increasing plants, complementarity increase.
 
@@
 
-#NOTE TO SELF: Here is where we want to subsample 1 to 6 species per site to test the idea of increasing plants, complementarity increase.
-
 #for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
@@
 head(f4b)
-
-#NOTE TO SELF: Here is where we want to subsample 1 to 6 species per site to test the idea of increasing plants, complementarity increase.
 
@@
 ONE QUESTION, WHY DO WE DO THIS SIMULATION ONLY FOR EQUITY AND NOT ALSO FOR AVERAGE REP SUCCESS?
+Because i do not expect the average to change as dramatically when considering more species.
 
@@
 
-plot(unique(combinatorials_all$Plant_number_level) , estimate, las = 1, ylim = c(0, 0.1) ,
+plot(unique(combinatorials_all$Plant_number_level) , estimate, las = 1, ylim = c(-0.01, 0.1) ,
      ylab = "importance of niche partitioning", xlab = "number of plants considered")
@@
   #subset(f4, Site_ID == "CotitodeSantaTeresa") #Super high values!
-  estimate_mean <- aggregate(estimate ~ level, estimate_k, mean)
+  estimate_mean <- aggregate(estimate ~ level, data = estimate_k, FUN = "mean")
   estimate_i[i,1] <- estimate_mean$level
@@
 
-One of the first conclusions we can extract from the fact that in most cases both of the models we considered (i.e., the simple model based on visitation metrics and the more complex one including community structure metrics) were equally good, is that for simple predictive purposes, simple visitation metrics, such as the diversity of pollinators visiting a plant, might be enough.
+One of the first conclusions we can extract from the fact that in most cases both of the models we considered (i.e., the simple model based on visitation metrics and the more complex one including community structure metrics) were equally good, is that for simple predictive purposes, simple visitation metrics, such as the diversity of pollinators visiting a plant, might be enough [cite Garibaldi papers using them]().
 Yet, a mechanistic understanding of the underlying processes requires that we take into account measures of community structure.
@@
 
+Paragraph somewhere about the importance of how you measure functioning (average vs equity).
+
 Our findings show that the analysis of natural communities of interacting species using network analysis not only represents an ideal way of visualizing and grasping the complexity present, but also represents a manner of mechanisitically understanding differences observed across individuals and/or species.

### 2019-02-28 paper_round2.Rmd
new changes in response to Nacho´s comments. Discussion advanced.

@@
 
-Title: Impact of interaction network structure on community-level plant reproduction success  
-or "Interaction network structure maximizes community-level plant reproduction success via [niche complmentariety?]()"
+Title: Interaction network structure maximizes community-level plant reproduction success via niche complementarity
 
@@
 
-Short running title: Network structure effects on function
-
-Keywords: nestedness, functional complementary, fruitset, pollination, plant-pollinator interaction
+Short running title: Network structure effects on reproductive success
+
+Keywords: nestedness, niche complementary, fruitset, pollination, plant-pollinator interaction
 
@@
 
-Words in Abstract: 149 words
+Words in Abstract: 147 words
 
@@
 
-Declines in pollinator diversity and abundance have been reported across different regions, with implications for the reproductive success of many plant species.
-However, research has targeted the consequences for individual plant species, particularly focusing on pairwise plant-pollinator interactions, and largely overlooking community-level dynamics.
+Declines in pollinator diversity and abundance have been reported across different regions, with implications for the reproductive success of plant species.
+However, research has focused primarily on pairwise plant-pollinator interactions, largely overlooking community-level dynamics.
 Yet species do not interact in isolation, they are embedded within larger networks whose structure can affect pollinator functional roles and, ultimately, the pollination services they deliver to plants.
@@
 We find that, for prediction purposes, information on simple visitation metrics is sufficient.
-Contrastingly, a mechanisitic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success, requires additional information on network structure [such as...]().
+Contrastingly, a mechanisitic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success, requires additional information on community structure, particularly that reflecting niche complementarity between pollinators.
 
@@
 Pollinators provide key services to plants by facilitating pollen flow between individuals.
-The recent declining trends found for some pollinator species in some regions of the planet ([@Potts2010], although see [@Herrera2018] for opposite trends[IB: I think Herrea paper is not needed here, as is quite local.
-My 2018 Phil Trans paper sumarizs the lack of knowledge for the world]()), have led many researchers to focus on the functional impacts of these changes in pollinator diversity, with a major focus being placed on the consequences for plant reproductive success [@Biesmeijer2006].
+The recent declining trends found for some pollinator species in some regions of the planet ([@Potts2010], although see [@I.2019] reflecting general lack of knowledge at the global level), have led many researchers to focus on the functional impacts of these changes in pollinator diversity, with a major focus being placed on the consequences for plant reproductive success [@Biesmeijer2006].
 
 Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012a; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain differences found  across different plant individuals.
-Some have gone a step further by including information on the efficiency of these visits, thus adding a measure of quality to the pollination services (REF[I only know refs for crops, e.g.
-winfree.
-Check Morris Ecology 2010 to see if there is something tehere]()).
+Some have gone a step further by including information on the efficiency of these visits, thus adding a measure of quality to the pollination services [@Willcox2017].
 Contrastingly, community-level analyses remain scarce [@Bennett2018].
 Yet plants and pollinators do not interact in isolation, but rather are embedded within larger networks of interactions encompassing other plant and pollinator species.
-We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect ones between species within one guild (e.g., plants) through their shared resources [@Lazaro2014, [Carvalheiro et al 2014 Ecol Lett, and Mayfield ans Stouffer 2017 Nature EcoEvo]()].
-Understanding how changes in pollinator diversity [diversity or interaction structure?]() affect whole community assemblages is thus a major challenge that requires attention.
+We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect ones between species within one guild (e.g., plants) through their shared resources [@Carvalheiro2014; @Lazaro2014; @Mayfield2017].
+Understanding how changes in pollinator diversity and interaction structure affect whole community assemblages is thus a major challenge that requires attention.
 
 The few pollination studies that have analysed the effects of changing pollinator diversity for reproductive success at the community level, have done so using mainly experimental setups.
-As an example, a study that experimentally recreated a plant community with 9 plant species and differing levels of pollinator diversity across different enclosures, found that not only pollinator species diversity had an effect for average reproductive success, but also they found that the structure that shaped the community had an important effect [@Frund2013].
-In particular, these authors found that the functional complementarity between pollinators, in terms of plant species and temperature coverage (a measure of the overlap in the use of plant resources and optimum temperature activity) had a positive effect for average seed set at the community level [@Frund2013].
+As an example, a study that experimentally recreated a plant community with 9 plant species and differing levels of pollinator diversity across different enclosures, found that not only pollinator species diversity had an effect for average reproductive success, but also they found that community structure had an important effect [@Frund2013].
+In particular, these authors found that niche complementarity between pollinators, in terms of plant species and temperature coverage (a measure of the overlap in the use of plant resources and optimum temperature activity) had a positive effect for average seed set at the community level [@Frund2013].
 This provides added information on the effects of biodiversity for ecosystem functioning, suggesting that not only the diversity of species present but also the diversity of roles and ways in which a community is structured are determinant factors.
@@
 Indeed, theoretical research has long suggested that the structure of a community has an effect for ecosystem functioning (reviewed in [@Thompson2012]).
-This line of research, primarliy driven by food-web studies, has greatly advanced theory, but these ideas have not yet been tested using empirical data [(but see Poisot and Gravel Ecol Let?)]().
+This line of research, primarliy driven by food-web studies, has greatly advanced theory, but these ideas have not yet been tested using empirical data (but see [@Poisot2013]).
 Specifically, a major knowledge gap resides in understading which aspects of structure determine which aspects of function [@Thompson2012].
-We are now at a point in which there is considerable understanding on the attributes characterizing mutualistic interaction networks ([Bacompte and H¿JOrdano AREES review]() REF, REF, REF) and we have a substantial understanding of how these attributes vary along different types of gradients [@Pellissier2017; @Tylianakis2016].
-Especially, in the case of pollination, we have ample knowledge on the attributes that shape these mutualistic interactions at the community level, such as a prevalence of nested structures ([Bascompte et al 2013 PNAS]()) or the presence of asymmetric specialization as a pervasive feature [@Vazquez2004].
-However, how the structure formed by this network of interactions afects key ecosystem functions such as plant reproduction remains untested [(Winfree BAAE opinion paper is good to cite "Global change, biodiversity, and ecosystem services: What can we learn from 6 studies of pollinators?")]().
+We are now at a point in which there is considerable understanding on the attributes characterizing mutualistic interaction networks [@Bascompte2007b] and we have a substantial understanding of how these attributes vary along different types of gradients [@Pellissier2017; @Tylianakis2016].
+Especially, in the case of pollination, we have ample knowledge on the attributes that shape these mutualistic interactions at the community level, such as a prevalence of nested structures [Bascompte et al 2013 PNAS] or the presence of asymmetric specialization as a pervasive feature [@Vazquez2004].
+However, how the structure shaping this network of interactions affects key ecosystem functions such as plant reproduction remains untested [@Winfree2013].
 The time is thus ripe to use this knowledge to explore relationships between community structure and ecosystem functioning, with special emphasis being placed on the underlying mechanisms that drive these relationships.
@@
 Here, we present one of the first efforts linking pollinator visitation and plant reproductive success at the community level.
-To this end, we use a well-replicated dataset encompassing 16 well-resolved networks coupled with data on the reproductive success of 19 plant species recorded at Mediterranean shrub ecosystems within the area of influence of Doñana National Park in SW Spain.
+To this end, we use a well-replicated dataset encompassing 16 well-resolved plant-pollinator interaction networks coupled with data on the reproductive success of 19 plant species recorded at Mediterranean shrub ecosystems within the area of influence of Doñana National Park in SW Spain.
 Our study focuses on understanding whether adding information on the structure of the community to previously-used simple visitation metrics (e.g., number of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success.
-In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success [and equity acorss species.]()
+In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success, and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success.
+In addition, we evaluate whether community structure helps us explain differences in equity in reproductive success across individuals within a species and species within a community as a measure of evenness and [stability in the pollination service??]()
 
 Our results suggest that for prediction purposes, information on simple visitation metrics, particularly regarding the diversity of pollinators that visit a plant species, is sufficient.
-However, we find that a mechanisitic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success requires additional information on network structure, notably information on the complementarity between the functions performed by different pollinator species.
-
-[IB: this intro is brilliant!]()
+However, we find that a mechanisitic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success requires additional information on network structure, notably information on the complementarity between the functions performed and the niches occupied by different pollinator species.
+
+[IB: this intro is brilliant!]() THANK YOU!! :) :)
 
@@
 ASK CURRO ABOUT THE NUMBERS ABOVE.]() Each site was surveyed 7 times during the flowering season of 2015 (from February to May) following a 100-m x 2 m transect for 30 mins.
-Along each transect, we identified all plant species and recorded all the flower visitors [IS IT JUST BEES AND HOVERFLIES?
+Along each transect, we identified all plant species and recorded all the flower visitors (including bees, hoverflies, beetles and XX) [IS IT JUST BEES AND HOVERFLIES?
 IB: NO, ALL VISITORS!]() that legitimately visited them.
@@
 
-Within each site, we marked between 2 and 12 individuals (6.49 +- 2.37) of 1 [NB: Which site has only one species!]() to 6 plant species (4.06 +- 1.69), depending on the availability and presence of flowers during the sampling events.
-For each individual, we counted the number of flowers at each sampling point and recorded fruit set, the number of seeds per fruit (for 2-36 fruits, 11.17 +- 6.84) and average seed weight per fruit at the end of the season.
+Within each site, we marked between 2 and 12 individuals (6.49 +- 2.37) of 1 [NB: Which site has only one species!]() [AM: Elpinar only has Rosmarinus and Villamanriqueeste only Cistus salvifolius]() to 6 plant species (4.06 +- 1.69), depending on the availability and presence of flowers during the sampling events.
+For each individual, we counted the number of flowers at each sampling point and recorded fruitset, the number of seeds per fruit (for 2-36 fruits, 11.17 +- 6.84) and average seed weight per fruit at the end of the season.
 Our survey included a total of 19 different plant species across our 16 sites.
@@
 
-In order to analyse how differences within the pollinator community might affect plant reproductive success, we constructed weighted interaction networks by pooling the data for the 7 rounds of sampling.
+In order to analyse how differences within the community structure might affect plant reproductive success, we constructed weighted plant-pollinator interaction networks by pooling the data for the 7 rounds of sampling.
 We thus obtained one weighted interaction network per site, representing the frequency of visits by different pollinator species to different plant species.
@@
 Thus, we also calculated two network metrics providing complementary non-redundant information.
-In this case we focused on (i) nestedness and (ii) functional complementarity.
-Nestedness is the property by which specialists interact with a subset of the species that generalists interact with ([Bascompte et al 2003 PNAS]).
-Although there is an ongoing debate in the literature, some studies have found that nested networks are more stable and resilient to perturbations because nestedness implies a certain level of redundancy and thus the possibility for functional replacement in the case of species loss (REF).
-[We used the widely accepted NODF metric to calculate Nestedness]() However, plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence (reviewed in [@Brosi2016]).
-Yet at present we do not know how the interplay between redundancy and complementarity in species roles determines reproductive success.
-[To calculate functional complmentariey we used ...]().
-All network analysis were perfeormed using bipartite package.
-
-Many network attributes vary with network size and complexity [@Bluthgen2006].
-In the case of nestedness, we know it can be affected by network size and connectance (REF).
+In this case we focused on (i) nestedness and (ii) niche complementarity.
+Nestedness is the property by which specialists interact with a subset of the species that generalists interact with [@Bascompte2003].
+Although there is an ongoing debate in the literature, some studies have found that nested networks are more stable and resilient to perturbations because nestedness promotes a greater diversity by minimizing competition among species in a community [@Bastolla2009].
+However, many network attributes vary with network size and complexity [@Bluthgen2006].
+In the case of nestedness, we know it can be affected by network size and connectance [@Song2017].
 An approach that is often used to correct for this, is to use null models and to compare null-model corrected nestedness values across different networks.
 However, this approach has been recently shown to present the same issues, as z-scores also change with network size and connectance [@Song2017].
-Given the dependence of nestedness on network size and connectance, we followed the advice of these researchers by using a normalized value of nestedness, NODFc, calculated as XXXX, where XXXXX [INCLUDE FORMULA AND DEFINE CONCEPTS], which is independent of network size and thus comparable across different networks [@Song2017].
+We thus followed the advice provided by Song et al.
+(2017) by using a normalized value of the widely-used nestedness metric NODF [@Almeida-Neto2011], $NODF_c$.
+This normalized value is calculated as $NODF_c = NODF_n/(C * log(S))$, where C is connectance, S is network size and $NODF_n = NODF/max(NODF)$, which is independent of network size and thus comparable across different networks [@Song2017].
+
+Nevertheless, plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence (reviewed in [@Brosi2016]).
+Yet at present we do not know how the interplay between redundancy and complementarity in species roles determines reproductive success.
+To calculate niche complmentarity we used a community-level measure defined as the total branch length of a functional dendrogram based on qualitative differences in visitor assemblages between plants [@Devoto2012; @Petchey2007a].
 All network metrics were calculated using package bipartite [@Dormann2009].
@@
 The diversity of pollinator species visiting a focal plant was approximated using the plant´s normalised degree, i.e., the number of links with different pollinator species a plant has, scaled by the number of possible partners [@Dormann2009].
+Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the morisita index  (@Manual{,
+    title = {spaa: SPecies Association Analysis},
+    author = {Jinlong Zhang},
+    year = {2016},
+    note = {R package version 0.2.2},
+    url = {https://CRAN.R-project.org/package=spaa},
+  }).
+As a measure of centrality we used weighted closeness centrality which describes centrality through the path lengths of a species to other species in the network using a weighted representation of the network [@Dormann2009].
+Response variables included fruitset for different individuals measured per species analyzed using a binomial distribution, the number of seeds per species for different individuals analyzed using normal distribution and average values per species of fruit and seed weight fitted to poisson distributions.
 
@@
 In this case, model 1 included total pollinator diversity and the total number of visits received by all plants within the community as explanatory variables.
-Model 2, in turn, added information on community structure by including nestedness and functional complementarity as explanatory variables.
-As response variable we had the average reproductive success for the whole community (i.e., average fruitset, average number of seeds per fruit previously scaled for each species, and average fruit and seed weight [IB: also scaled?]()).
-We thus, had a single value per site and no random effects are needed in this case.
+Model 2, in turn, added information on community structure by including nestedness and niche complementarity as explanatory variables.
+As response variable we had the average reproductive success for the whole community (i.e., average fruitset analyzed using a binomial distribution, average number of seeds per fruit and average fruit and seed weight previously scaled for each species for which we used normal distributions).
+We thus had a single value per site and no random effects are needed in this case.
 
 Average values of reproductive success at the community level can be driven to a large extent by a single plant species.
-Yet, what will determine the persistence of a diverse plant community, is the presence of some sort of “equity” in reproductive success across the whole community.
-We therefore calculated a measure of equity in reproductive success at the community level as the proportion of plant species within a site that is at 50% of the maximum value of fruitset recorded for that plant species within our sampling.
-We repeated this using 25% and 75% thresholds.
-We then used the same framework as before and fit the same models 1 and 2 as the ones used at the community level, but using equity in reproductive success as the response variable.
-[Here is unclear how the proportion is calculated.
-This is: average fruit set per species is > 50%?
-Or as we discussed a more coplex option can be: % of species which > 50 % of individuals had seed set > 50%.
-Now that I see this I would only used if we gain a lot, otherwise is too complicated.
-Also, I removed species present is only one (or two) sites for this analysis, because the % was forces to be 1.
-If you kept this in your analysis, should be explained]().
-
+Yet, what will determine the persistence of a diverse plant community, is the presence of some sort of “equity” or evenness in reproductive success across the whole community.
+We therefore calculated a measure of equity in reproductive success at the community level as the proportion of species within a community with normalized average fruitset values above 0.5.
+We repeated this using 0.25 and 0.75 thresholds.
+We then used the same framework as before and fit the same models 1 and 2 GLMs as the ones used at the community level, but using equity in reproductive success as the response variable and a binomial distribution.
+In this case, we retained only sites for which we had at least measured reproductive success for 2 plant species (N=14 sites).
 We used information criterion methods to find the best model for each case and selected the ones with the lowest Akaike Information Criterion (AIC) value.
-Differences in AIC values < 2, were not considered enough to select one model over the other [@Burnham2011].
+$\Delta AIC<2$, were not considered enough to select one model over the other [@Burnham2011].
 
@@
 
-Finally, we tested whether the importance of community structure in explaining differences in reproductive success increases with the number of plant species being considered.
+Finally, we tested whether the importance of community structure in explaining differences in equity in reproductive success within communities increases with the number of plant species being considered.
 We expect that when only one plant species is considered, then the importance of community structure will be negligible, while we expect this importance to increase as more plant species are considered (up to a maximum number of 6 species which is the maximum we have measured in our study at a particular site).
@@
 
-At the species level, our results show that in the case of fruitset, both model 1 and model 2 are equally good in explaining the variability observed when accounting for model complexity (i.e.,$\Delta AIC<2$), and therefore we cannot select one over the other.
-Given that model 2 has a greater number of variables which penalize for the added complexity, we will thus comment results only for model 2, which in the case of fruitset shows a positive effect of the diversity of species visiting a focal plant species (measured using the species´normalised degree, Fig.
+At the species level, in the case of fruitset, our results show that both model 1 and model 2 are equally good in explaining the variability observed (i.e.,$\Delta AIC<2$), and therefore we cannot select one over the other.
+Given that model 2 has a greater number of variables which should be penalized given the added complexity it provides, we will comment results only for model 2.
+In this case, we find a positive effect of pollinator species diversity (measured using the species´normalised degree, Fig.
 XX) as well as a positive effect of the centrality of the focal plant on its fruitset.
@@
 
-For all other measures of reproductive success considered (i.e., the number of seeds per fruit, fruit and seed weight), the best model based on its AIC value was model 1, i.e., the model that only included simple visitation metrics (in this case, the diversity of visiting pollinators and the total number of visits received by a focal plant species).
+For all other measures of reproductive success considered (i.e., the number of seeds per fruit, fruit and seed weight), the best model based on its AIC value was model 1, i.e., the model that only included simple visitation metrics (in this case, pollinator species diversity and the total number of visits received by a focal plant species).
 However, none of the variables included within our model explain the differences observed.
@@
 In the case of fruitset and the number of seeds per fruit, we find that both model 1 and 2 are equally good in describing the differences observed (i.e.,$\Delta AIC<2$).
-Again, because this suggests model 2 is a good model despite its added complexity we will comment results for this model only.
-In particular, we find that both fruitset and the number of seeds per fruit are positively related to functional complementarity between pollinators.
+Again, because this suggests model 2 is a good model despite its added complexity, we will comment results for this model only.
+In particular, we find that both fruitset and the number of seeds per fruit are positively related to niche complementarity between pollinators.
 Additionally, we find a negative effect of community-level pollinator species diversity on average fruitset.
@@
 
-When evaluating the effect of differences in community composition and structure for equity in reproductive success across the different individuals within a species and site we find that both model 1 and model 2 are equally good (i.e.,$\Delta AIC<2$) and thus we cannot select one over the other.
-Specifically, regarding the results for model 2, we find a significant and positive effect of nestedness for equity between individuals of a species (Table X, Fig.
-X).
-This effect that we find when using a 50% threshold of productivity (i.e., when looking at plant species that are producing 50% of the maximum fruitset observed for the area), is however not maintained when using 25 and 75% thresholds.
-In particular, when using a 25% threshold we find model 1 is the best model and none of the variables considered are able to explain the differences observed.
-Contrastingly in the case of the 75% threshold, we find again that both model 1 and 2 are equally plausible but in this case we find a positive effect of functional complementarity between pollinators for equity in fruitset across individuals within a species.
+When evaluating the effect of differences in community composition and structure for equity in reproductive success across the different species within a community we find that model 1 is the best model for all the thresholds considered (50%, 25% and 75%).
+However, we find that none of the variables considered are able to explain the differences observed.
 [this is interesting, as selfing rates I expect to be ~ 40%... In any case I am confused now on this calculation]()
@@
 
-#EQUITY IN INDIVIDUALS WITHIN SPECIES
-
-#calculate column with fruit set as
-f$Plant.sp<-paste(f$Plant_genus, f$Plant_species)
-
-#Fruit_Yes +  Fruit_Preyed + Fruit_Dispersed) / (Fruit_Yes + Fruit_No +Fruit_Preyed + Fruit_Dispersed) #Nacho this equation is wrong in your metadata!
-
-#1st eliminate frutos perdidos
-wordList <- c("fruto perdido","frutos perdidos")
-
-require(Hmisc)
-f2<-subset(f, Notes %nin% wordList)
-
-f2$tot.fruitset<-(f2$Fruit_Yes +  f2$Fruit_preyed + f2$Fruit_dispersed)/(f2$Fruit_Yes +f2$Fruit_No + f2$Fruit_preyed + f2$Fruit_dispersed)
-
-library(vegan)
-library(plyr)
-
-f2$Plant.sp<-paste(f2$Plant_genus, f2$Plant_species)
-f3<-f2[,c(1,13:14)]
-
-fr.max<-aggregate(.~ Plant.sp, f3, FUN=max)
-
-f3$fruit.max<-fr.max$tot.fruitset[match(f3$Plant.sp, fr.max$Plant.sp)]
-
-f3$fruit.prop<-f3$tot.fruitset/f3$fruit.max
-f5<-subset(f3, f3$fruit.prop>0.5)
-f5$no_rows<-rep(1, nrow(f5))
-head(f5)
+#EQUITY SPECIES WITHIN COMMUNITIES
+
+#normalize fruitset values for individuals within species and sites, to have values between 0 and 1
+
+range01 <- function(x){(x-min(x))/(max(x)-min(x))}
+f2_scaled_fruit <- f2 %>% group_by(Plant.sp) %>% mutate(tot.fruitset = range01(tot.fruitset))
+
+#calculate average normalized fruitset values per site to have one unique value per site
+f.ag.pr <- ddply(f2_scaled_fruit, c("Site_ID", "Plant.sp", "nodf.song", "functional.comp.poll", "species.poll"), 
+              summarise, tot.visits    = sum(tot.visits),
+              mean.fruitset = mean(tot.fruitset))
+
+#select species with normalized values >0.5
+f.ag_scaledb<-subset(f.ag.pr, f.ag.pr$mean.fruitset>0.50)
 
 #for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
-f6<- aggregate(no_rows ~ Site_ID + Plant.sp, f5, length)
-head(f6)
-
-#because when calculating thresholds, sites with 6 plants can score up to 6, but sites with 4 sites can oscar max = 4 we corrected for this doing % above threshold, and no number.
-
-f3$no_rows<-rep(1, nrow(f3))
-f3b<- aggregate(no_rows ~ Site_ID + Plant.sp, f3, length)
-head(f3b)
-
-f3b$j<- paste(f3b$Site_ID, f3b$Plant.sp)
-f6$j<- paste(f6$Site_ID, f6$Plant.sp)
-
-f6$total.plant.numb<-f3b$no_rows[match(f6$j, f3b$j)]
-f6$equity<-f6$no_rows/f6$total.plant.numb
-
-#join this with fruitset data used previously
-
-f6$nodf.song<-out.site$nodf.song[match(f6$Site_ID, out.site$Site_id)]
-f6$functional.comp.poll<-out.site$functional.comp.poll[match(f6$Site_ID, out.site$Site_id)]
-f6$species.poll<-out.site$species.poll[match(f6$Site_ID, out.site$Site_id)]
-f6$tot.visits<-f.agg$tot.visits[match(f6$Site_ID, f.agg$Site_ID)]
-
-#scale all variables
-
-f6$nodf.song.sc <- scale(f6$nodf.song, center = T, scale = T)
-f6$functional.comp.poll.sc <- scale(f6$functional.comp.poll, center = T, scale = T)
-f6$species.poll.sc <- scale(f6$species.poll, center = T, scale = T)
-f6$tot.visits.sc <- scale(f6$tot.visits, center = T, scale = T)
-
-#fit two models
-m1.eq<-glmer(equity ~  species.poll.sc + tot.visits.sc + (1|Site_ID), family="binomial", data=f6)
-
-summary(m1.eq)
-
-vif(m1.eq)
-
-m2.eq<-glmer(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc+ (1|Site_ID), family="binomial", data=f6)
-#nich estimate not overlaping zero: 0.6178     0.4354, second higher effect size!
-summary(m2.eq)
-
-vif(m2.eq)
-
-#select best model based on AIC
-
-AICtab(m1.eq, m2.eq) #Almost equal... Again, for prediction, go with the simple, for mechanistic understanding, look into niche partitioning. 
-library(remef)
-y_partial_eq <- remef(m2.eq, fix = c("species.poll.sc", "tot.visits.sc", "functional.comp.poll.sc"), ran = "all", inverse = F)
-y_partial_eq_inv<-exp(y_partial_eq)/(1+exp(y_partial_eq))
-
-pl.th_ <-ggplot(f6,  aes(x=nodf.song.sc, y=y_partial_eq_inv ))+      
-  geom_point(size=4, color="black") + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) +  ylim(0,1.1) +
-  xlab("Nestedness") +      
-  ylab("Equity in fruitset") + theme_bw() + 
-  theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
-
-#pl.th_ #oh yeah!
-
-#now 75% threshold
-#head(f3)
-f5.75<-subset(f3, f3$fruit.prop>0.75)
-f5.75$no_rows<-rep(1, nrow(f5.75))
-head(f5.75)
-
-#for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
-f6.75<- aggregate(no_rows ~ Site_ID + Plant.sp, f5.75, length)
-head(f6.75)
-
-#because when calculating thresholds, sites with 6 plants can score up to 6, but sites with 4 sites can oscar max = 4 we corrected for this doing % above threshold, and no number.
-
-f3$no_rows<-rep(1, nrow(f3))
-f3b<- aggregate(no_rows ~ Site_ID + Plant.sp, f3, length)
-head(f3b)
-
-f3b$j<- paste(f3b$Site_ID, f3b$Plant.sp)
-f6.75$j<- paste(f6.75$Site_ID, f6.75$Plant.sp)
-
-f6.75$total.plant.numb<-f3b$no_rows[match(f6.75$j, f3b$j)]
-f6.75$equity<-f6.75$no_rows/f6.75$total.plant.numb
-
-#join this with fruitset data used previously
-
-f6.75$nodf.song<-out.site$nodf.song[match(f6.75$Site_ID, out.site$Site_id)]
-f6.75$functional.comp.poll<-out.site$functional.comp.poll[match(f6.75$Site_ID, out.site$Site_id)]
-f6.75$species.poll<-out.site$species.poll[match(f6.75$Site_ID, out.site$Site_id)]
-f6.75$tot.visits<-f.agg$tot.visits[match(f6.75$Site_ID, f.agg$Site_ID)]
-
-#scale all variables
-
-f6.75$nodf.song.sc <- scale(f6.75$nodf.song, center = T, scale = T)
-f6.75$functional.comp.poll.sc <- scale(f6.75$functional.comp.poll, center = T, scale = T)
-f6.75$species.poll.sc <- scale(f6.75$species.poll, center = T, scale = T)
-f6.75$tot.visits.sc <- scale(f6.75$tot.visits, center = T, scale = T)
-
-#fit two models
-m1.eq.75<-glmer(equity ~  species.poll.sc + tot.visits.sc + (1|Site_ID), family="binomial", data=f6.75)
-
-summary(m1.eq.75)
-
-m2.eq.75<-glmer(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc+ (1|Site_ID), family="binomial", data=f6.75)
-#nich estimate not overlaping zero: 0.6178     0.4354, second higher effect size!
-summary(m2.eq.75)
-
-#select best model based on AIC
-
-AICtab(m1.eq.75, m2.eq.75) #Almost equal... Again, for prediction, go with the simple, for mechanistic understanding, look into niche partitioning. 
-library(remef)
-y_partial_eq.75 <- remef(m2.eq.75, fix = c("species.poll.sc", "tot.visits.sc", "nodf.song.sc"), ran = "all", inverse = F)
-y_partial_eq.75_inv<-exp(y_partial_eq.75)/(1+exp(y_partial_eq.75))
-
-pl.th_75 <-ggplot(f6.75,  aes(x=functional.comp.poll.sc, y=y_partial_eq.75_inv ))+      
-  geom_point(size=4, color="black") + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + ylim(0,1.1) +
-  xlab("Functional complementarity") +      
-  ylab("Equity in fruitset") + theme_bw() + 
-  theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
-
-#pl.th_75 #oh yeah!
-
-library(cowplot)
-plot_grid(pl.th_, pl.th_75, labels = c("A", "B"))
-
-#now 25% threshold
-f5.25<-subset(f3, f3$fruit.prop>0.25)
-f5.25$no_rows<-rep(1, nrow(f5.25))
-head(f5.25)
-
-#for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
-f6.25<- aggregate(no_rows ~ Site_ID + Plant.sp, f5.25, length)
-head(f6.25)
-
-#because when calculating thresholds, sites with 6 plants can score up to 6, but sites with 4 sites can oscar max = 4 we corrected for this doing % above threshold, and no number.
-
-f3$no_rows<-rep(1, nrow(f3))
-f3b<- aggregate(no_rows ~ Site_ID + Plant.sp, f3, length)
-head(f3b)
-
-f3b$j<- paste(f3b$Site_ID, f3b$Plant.sp)
-f6.25$j<- paste(f6.25$Site_ID, f6.25$Plant.sp)
-
-f6.25$total.plant.numb<-f3b$no_rows[match(f6.25$j, f3b$j)]
-f6.25$equity<-f6.25$no_rows/f6.25$total.plant.numb
-
-#join this with fruitset data used previously
-
-f6.25$nodf.song<-out.site$nodf.song[match(f6.25$Site_ID, out.site$Site_id)]
-f6.25$functional.comp.poll<-out.site$functional.comp.poll[match(f6.25$Site_ID, out.site$Site_id)]
-f6.25$species.poll<-out.site$species.poll[match(f6.25$Site_ID, out.site$Site_id)]
-f6.25$tot.visits<-f.agg$tot.visits[match(f6.25$Site_ID, f.agg$Site_ID)]
-
-#scale all variables
-
-f6.25$nodf.song.sc <- scale(f6.25$nodf.song, center = T, scale = T)
-f6.25$functional.comp.poll.sc <- scale(f6.25$functional.comp.poll, center = T, scale = T)
-f6.25$species.poll.sc <- scale(f6.25$species.poll, center = T, scale = T)
-f6.25$tot.visits.sc <- scale(f6.25$tot.visits, center = T, scale = T)
-
-#fit two models
-m1.eq.25<-glmer(equity ~  species.poll.sc + tot.visits.sc + (1|Site_ID), family="binomial", data=f6.25)
-
-summary(m1.eq.25)
-
-m2.eq.25<-glmer(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc+ (1|Site_ID), family="binomial", data=f6.25)
-#nich estimate not overlaping zero: 0.6178     0.4354, second higher effect size!
-summary(m2.eq.25)
-
-#select best model based on AIC
-
-AICtab(m1.eq.25, m2.eq.25) #m1 is better.
-
-```
-Figure X.
-Partial residual plots showing the effect of a) nestedness and b) functional complementarity on equity in reproductive success between individuals of a species within a site, measured as the proportion of individuals producing at least 50% or 75% of maximum fruitset observed for the study area respectively.
-Dots represent values for each species within a site (N=63)
-
-Contrastingly, in the case of equity in average reproductive success across species within a site we find that model 1, the one including only simple visitation metrics is the best one, and we find none of the variables explain the differences observed at any of the thresholds considered (25, 50 and 75%).
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
-
-#EQUITY SPECIES WITHIN COMMUNITIES
-
-f4 <- ddply(f3, c("Site_ID", "Plant.sp"), summarise,
-                         mean.fruitset    = mean(tot.fruitset))
-
-#f4
-
-fr.max.comm<-aggregate(.~ Plant.sp, f4, FUN=max)
-
-f4$fruit.max<-fr.max.comm$mean.fruitset[match(f4$Plant.sp, fr.max.comm$Plant.sp)]
-
-f4$fruit.prop<-f4$mean.fruitset/f4$fruit.max
-
-f4b<-subset(f4, f4$fruit.prop>0.5)
-f4b$no_rows<-rep(1, nrow(f4b))
-head(f4b)
-
-#for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
-f4c<- aggregate(no_rows ~ Site_ID, f4b, length)
+f.ag_scaledb$no_rows<-rep(1, nrow(f.ag_scaledb))
+f4c<- aggregate(no_rows ~ Site_ID, f.ag_scaledb, length)
 head(f4c)
@@
 #because when calculating thresholds, sites with 6 plants can score up to 6, but sites with 4 sites can score max = 4 we corrected for this doing % above threshold, and no number. 
-
+#calculate total number of species per site
 f4$no_rows<-rep(1, nrow(f4))
@@
 f4c$total.plant.numb<-f4d$no_rows[match(f4c$Site_ID, f4d$Site_ID)]
-f4c$equity<-f4c$no_rows/f4c$total.plant.numb
+
+#remove sites that only have one plant sps, Elpinar and Villamanriqueeste
+f4e<-subset(f4c, f4c$total.plant.numb>1)
+
+#calculate equity as proportion of species with >50% of fruitset compared to total number of sps
+f4e$equity<-f4e$no_rows/f4e$total.plant.numb
 
@@
 
-f4c$nodf.song<-out.site$nodf.song[match(f4c$Site_ID, out.site$Site_id)]
-f4c$functional.comp.poll<-out.site$functional.comp.poll[match(f4c$Site_ID, out.site$Site_id)]
-f4c$species.poll<-out.site$species.poll[match(f4c$Site_ID, out.site$Site_id)]
-f4c$tot.visits<-f.agg$tot.visits[match(f4c$Site_ID, f.agg$Site_ID)]
-
+f4e$nodf.song<-out.site$nodf.song[match(f4e$Site_ID, out.site$Site_id)]
+f4e$functional.comp.poll<-out.site$functional.comp.poll[match(f4e$Site_ID, out.site$Site_id)]
+f4e$species.poll<-out.site$species.poll[match(f4e$Site_ID, out.site$Site_id)]
+f4e$tot.visits<-f.agg$tot.visits[match(f4e$Site_ID, f.agg$Site_ID)]
+
+f4e$species.pl<-out.site$species.pl[match(f4e$Site_ID, out.site$Site_id)]
 #scale all variables
 
-f4c$nodf.song.sc <- scale(f4c$nodf.song, center = T, scale = T)
-f4c$functional.comp.poll.sc <- scale(f4c$functional.comp.poll, center = T, scale = T)
-f4c$species.poll.sc <- scale(f4c$species.poll, center = T, scale = T)
-f4c$tot.visits.sc <- scale(f4c$tot.visits, center = T, scale = T)
+f4e$nodf.song.sc <- scale(f4e$nodf.song, center = T, scale = T)
+f4e$functional.comp.poll.sc <- scale(f4e$functional.comp.poll, center = T, scale = T)
+f4e$species.poll.sc <- scale(f4e$species.poll, center = T, scale = T)
+f4e$tot.visits.sc <- scale(f4e$tot.visits, center = T, scale = T)
+f4e$species.pl.sc <- scale(f4e$species.pl, center = T, scale = T)
 
 #fit two models
- m1.eq.comm<-glm(equity ~  species.poll.sc + tot.visits.sc, family="binomial", data=f4c)
+ m1.eq.comm<-glm(equity ~  species.poll.sc + tot.visits.sc , family="binomial", data=f4e)
 
@@
 
- m2.eq.comm<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="binomial", data=f4c)
+ m2.eq.comm<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc , family="binomial", data=f4e)
 summary(m2.eq.comm)
@@
 
-AICtab(m1.eq.comm, m2.eq.comm)
+AICtab(m1.eq.comm, m2.eq.comm) #m1 is best no variables significant
 
 #save table with results for paper, both models are equally good so save both tables
-summ.eq<-round(summary(m1.eq)$coef, digits=2)
+summ.eq<-round(summary(m1.eq.comm)$coef, digits=2)
 #write.csv(summ.eq, file="tables/resultsequityNETWORKm1.csv", row.names = TRUE)
@@
 #test for problems in residuals
-# res<-simulateResiduals(m1.eq)
+# res<-simulateResiduals(m1.eq.comm)
 # plot(res, rank = TRUE)
@@
 
-f75<-subset(f4, f4$fruit.prop>0.75)
+f75<-subset(f.ag.pr, f.ag.pr$mean.fruitset>0.75)
+
+#for each site here is the number of sps whose fruitset exceeds 75% of maximum fruitset observed in the whole study area
 f75$no_rows<-rep(1, nrow(f75))
-head(f75)
-
-#for each site here is the number of sps whose fruitset exceeds 75% of maximum fruitset observed in the whole study area
 f75b<- aggregate(no_rows ~ Site_ID, f75, length)
 head(f75b)
-f75b$total.numb.plants<-f4d$no_rows[match(f75b$Site_ID, f4d$Site_ID)]
-f75b$equity<-f75b$no_rows/f75b$total.numb.plants
+
+#because when calculating thresholds, sites with 6 plants can score up to 6, but sites with 4 sites can score max = 4 we corrected for this doing % above threshold, and no number. 
+#calculate total number of species per site
+f4$no_rows<-rep(1, nrow(f4))
+f4d<- aggregate(no_rows ~ Site_ID, f4, length)
+head(f4d)
+
+f75b$total.plant.numb<-f4d$no_rows[match(f75b$Site_ID, f4d$Site_ID)]
+
+#remove sites that only have one plant sps, Elpinar and Villamanriqueeste
+f75c<-subset(f75b, f75b$total.plant.numb>1)
+
+#calculate equity as proportion of species with >50% of fruitset compared to total number of sps
+f75c$equity<-f75c$no_rows/f75c$total.plant.numb
 
@@
 
-f75b$nodf.song<-out.site$nodf.song[match(f75b$Site_ID, out.site$Site_id)]
-f75b$functional.comp.poll<-out.site$functional.comp.poll[match(f75b$Site_ID, out.site$Site_id)]
-f75b$species.poll<-out.site$species.poll[match(f75b$Site_ID, out.site$Site_id)]
-f75b$tot.visits<-f.agg$tot.visits[match(f75b$Site_ID, f.agg$Site_ID)]
-
+f75c$nodf.song<-out.site$nodf.song[match(f75c$Site_ID, out.site$Site_id)]
+f75c$functional.comp.poll<-out.site$functional.comp.poll[match(f75c$Site_ID, out.site$Site_id)]
+f75c$species.poll<-out.site$species.poll[match(f75c$Site_ID, out.site$Site_id)]
+f75c$tot.visits<-f.agg$tot.visits[match(f75c$Site_ID, f.agg$Site_ID)]
+
+f75c$species.pl<-out.site$species.pl[match(f75c$Site_ID, out.site$Site_id)]
 #scale all variables
 
-f75b$nodf.song.sc <- scale(f75b$nodf.song, center = T, scale = T)
-f75b$functional.comp.poll.sc <- scale(f75b$functional.comp.poll, center = T, scale = T)
-f75b$species.poll.sc <- scale(f75b$species.poll, center = T, scale = T)
-f75b$tot.visits.sc <- scale(f75b$tot.visits, center = T, scale = T)
-
- m1.eq.75<-glm(equity ~  species.poll.sc + tot.visits.sc, family="binomial", data=f75b)
+f75c$nodf.song.sc <- scale(f75c$nodf.song, center = T, scale = T)
+f75c$functional.comp.poll.sc <- scale(f75c$functional.comp.poll, center = T, scale = T)
+f75c$species.poll.sc <- scale(f75c$species.poll, center = T, scale = T)
+f75c$tot.visits.sc <- scale(f75c$tot.visits, center = T, scale = T)
+
+f75c$species.pl.sc <- scale(f75c$species.pl, center = T, scale = T)
+
+#fit two models
+ m1.eq.75<-glm(equity ~  species.poll.sc + tot.visits.sc , family="binomial", data=f75c)
 
@@
 
- vif(m1.eq.75)
-
-m2.eq.75<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="binomial", data=f75b)
+m2.eq.75<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc , family="binomial", data=f75c)
 
@@
 
- vif(m2.eq.75)
-
 #select best model based on AIC
 
-AICtab(m1.eq.75, m2.eq.75) #as before both models are equally good.
+AICtab(m1.eq.75, m2.eq.75) #m1 better model
 
@@
 
-#and for 25% threshold
-
-f25<-subset(f4, f4$fruit.prop>0.25)
+#Repeat with 25% threshold
+
+f25<-subset(f.ag.pr, f.ag.pr$mean.fruitset>0.25)
+
+#for each site here is the number of sps whose fruitset exceeds 25% of maximum fruitset observed in the whole study area
 f25$no_rows<-rep(1, nrow(f25))
-head(f25)
-
-#for each site here is the number of sps whose fruitset exceeds 25% of maximum fruitset observed in the whole study area
 f25b<- aggregate(no_rows ~ Site_ID, f25, length)
 head(f25b)
-f25b$total.numb.plants<-f4d$no_rows[match(f25b$Site_ID, f4d$Site_ID)]
-f25b$equity<-f25b$no_rows/f25b$total.numb.plants
+
+#because when calculating thresholds, sites with 6 plants can score up to 6, but sites with 4 sites can score max = 4 we corrected for this doing % above threshold, and no number. 
+#calculate total number of species per site
+f4$no_rows<-rep(1, nrow(f4))
+f4d<- aggregate(no_rows ~ Site_ID, f4, length)
+head(f4d)
+
+f25b$total.plant.numb<-f4d$no_rows[match(f25b$Site_ID, f4d$Site_ID)]
+
+#remove sites that only have one plant sps, Elpinar and Villamanriqueeste
+f25c<-subset(f25b, f25b$total.plant.numb>1)
+
+#calculate equity as proportion of species with >50% of fruitset compared to total number of sps
+f25c$equity<-f25c$no_rows/f25c$total.plant.numb
 
@@
 
-f25b$nodf.song<-out.site$nodf.song[match(f25b$Site_ID, out.site$Site_id)]
-f25b$functional.comp.poll<-out.site$functional.comp.poll[match(f25b$Site_ID, out.site$Site_id)]
-f25b$species.poll<-out.site$species.poll[match(f25b$Site_ID, out.site$Site_id)]
-f25b$tot.visits<-f.agg$tot.visits[match(f25b$Site_ID, f.agg$Site_ID)]
-
+f25c$nodf.song<-out.site$nodf.song[match(f25c$Site_ID, out.site$Site_id)]
+f25c$functional.comp.poll<-out.site$functional.comp.poll[match(f25c$Site_ID, out.site$Site_id)]
+f25c$species.poll<-out.site$species.poll[match(f25c$Site_ID, out.site$Site_id)]
+f25c$tot.visits<-f.agg$tot.visits[match(f25c$Site_ID, f.agg$Site_ID)]
+
+f25c$species.pl<-out.site$species.pl[match(f25c$Site_ID, out.site$Site_id)]
 #scale all variables
 
-f25b$nodf.song.sc <- scale(f25b$nodf.song, center = T, scale = T)
-f25b$functional.comp.poll.sc <- scale(f25b$functional.comp.poll, center = T, scale = T)
-f25b$species.poll.sc <- scale(f25b$species.poll, center = T, scale = T)
-f25b$tot.visits.sc <- scale(f25b$tot.visits, center = T, scale = T)
-
- m1.eq.25<-glm(equity ~  species.poll.sc + tot.visits.sc, family="binomial", data=f25b)
+f25c$nodf.song.sc <- scale(f25c$nodf.song, center = T, scale = T)
+f25c$functional.comp.poll.sc <- scale(f25c$functional.comp.poll, center = T, scale = T)
+f25c$species.poll.sc <- scale(f25c$species.poll, center = T, scale = T)
+f25c$tot.visits.sc <- scale(f25c$tot.visits, center = T, scale = T)
+
+f25c$species.pl.sc <- scale(f25c$species.pl, center = T, scale = T)
+
+#fit two models
+ m1.eq.25<-glm(equity ~  species.poll.sc + tot.visits.sc , family="binomial", data=f25c)
 
@@
 
- vif(m1.eq.25)
-
-m2.eq.25<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="binomial", data=f25b)
+m2.eq.25<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc , family="binomial", data=f25c)
 
@@
 
- vif(m2.eq.25)
-
 #select best model based on AIC
 
-AICtab(m1.eq.25, m2.eq.25) #as before both models are equally good.
+AICtab(m1.eq.25, m2.eq.25) #m1 is better.
 
@@
 
-##equity in seed number???
-
-library(vegan)
-library(dplyr)
-
-s5 <- ddply(s4_scaled, c("Site_ID", "Plant.sp", "functional.comp.poll.sc", "nodf.song.sc", "species.poll.sc", "tot.visits.sc"), summarise,
-                         mean.seedset    = mean(mean.seedn))
-
-s5.max<-aggregate(.~ Plant.sp, s5, FUN=max)
-
-s5$seed.max<-s5.max$mean.seedset[match(s5$Plant.sp, s5.max$Plant.sp)]
-
-s5$seed.prop<-s5$mean.seedset/s5$seed.max
-s6<-subset(s5, s5$seed.prop>0.5)
-s6$no_rows<-rep(1, nrow(s6))
-head(s6)
-
-#for each site here is the number of sps whose seedset exceeds 50% of maximum seedset observed in the whole study area
-s7<- aggregate(no_rows ~ Site_ID, s6, length)
-head(s7)
-
-#calculate proportion of sps at threshold because number depends on number of sps per site which is different
-
-s5$no_rows<-rep(1, nrow(s5))
-s5b<- aggregate(no_rows ~ Site_ID, s5, length)
-head(s5b)
-
-s7$total.plant.numb<-s5b$no_rows[match(s7$Site_ID, s5b$Site_ID)]
-s7$equity<-s7$no_rows/s7$total.plant.numb
-
-#join this with fruitset data used previously
-
-s7$nodf.song<-out.site$nodf.song[match(s7$Site_ID, out.site$Site_id)]
-s7$functional.comp.poll<-out.site$functional.comp.poll[match(s7$Site_ID, out.site$Site_id)]
-s7$species.poll<-out.site$species.poll[match(s7$Site_ID, out.site$Site_id)]
-s7$tot.visits<-f.agg$tot.visits[match(s7$Site_ID, f.agg$Site_ID)]
-
-#scale all variables
-
-s7$nodf.song.sc <- scale(s7$nodf.song, center = T, scale = T)
-s7$functional.comp.poll.sc <- scale(s7$functional.comp.poll, center = T, scale = T)
-s7$species.poll.sc <- scale(s7$species.poll, center = T, scale = T)
-s7$tot.visits.sc <- scale(s7$tot.visits, center = T, scale = T)
-
-#fit two models
-
- m1.eq.seed<-glm(equity ~  species.poll.sc + tot.visits.sc, family="binomial", data=s7)
-
- summary(m1.eq.seed)
-
- vif(m1.eq.seed)
-
-m2.eq.seed<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="binomial", data=s7)
-
- summary(m2.eq.seed)
-
- vif(m2.eq)
-
-#select best model based on AIC
-
-AICtab(m1.eq.seed, m2.eq.seed)
-
-#test for problems in residuals
-# res<-simulateResiduals(m1.eq.seed)
-# plot(res, rank = TRUE)
-
 ```
@@
 
-CHECK THIS IN LIGHT OF NEW RESULTS!!
-
-Now, we ask if the effect of niche complementariety increases with the number of species considered in the network.
-We expect that for any single species, the effect should be almost zero (as shown in our single species analysis above), but when you take into account up to 6 species, network metrics start to be important (see also above the community level results).
-This implies that if we would be able to measure reproductive success on all plant species in the community in all networks (not done for effort constrains) the effects of network configuartion may be even more prevalent.
-To test this, we ran a simple simulation where we first increase randomly the number of selected species per network and calculate the equitativity for each run.
-Instead of drawing random plants for each run, for each plant number level and network we test all possible combinations, as this number is low (n = 63 possible combiations overall for the network with the largest dataset) and increasing sampling events in our simulation would only result in repeated combinations.
-Second, we test the overall relation between equitativity in fruit set and niche complementariety in our simulated communities.
-To this end, for each species number level, we randomly combine the generated equitativity values across the 16 communities as to obtain one random value per species.
-Finally, for each of such combinations we calculated the estimate of equitativity in relation with niche partitioning and average all estimates from 1000 simulated combinations per number of plants considered.
-We expect that the more plants considered, the larger are the resulting average estimates.
-Note that We only interpret the mean effects, as the variance among different plant number of species depends on the initial number of combinations.
-
-I ALSO INCLUDED HERE NESTEDNESS WHICH STARTS AS LESS IMPORTANT AND THEN BECOMES MORE IMPORTANT WITH NO ASYMPTOTE.
-
-ONE QUESTION, WHY DO WE DO THIS SIMULATION ONLY FOR EQUITY AND NOT ALSO FOR AVERAGE REP SUCCESS?
-Because i do not expect the average to change as dramatically when considering more species.
+Within our simulation evaluating the effect of niche complementarity on equity in reproductive success, we find that the effect of complementarity becomes more important as the reproductive success of more species is considered (Fig.
+X).
+This importance seems to reach some sort of plateau at 6 species, however, this should be further evaluated as this is the maximum number of species simultaneously observed in a community for our study which precludes us from simulating further numbers of species.
 
@@
 #1) First let's calculate all combinations of 1,2,3,4,5,6 species per network.
-combinatorials_all <-  matrix(ncol = 6, nrow = 1, NA) 
-colnames(combinatorials_all) <- c("SiteID", "Plant_number_level", "iteration", "equity", "functional.comp", "nestedness")
+combinatorials_all <-  matrix(ncol = 5, nrow = 1, NA) 
+colnames(combinatorials_all) <- c("SiteID", "Plant_number_level", "iteration", "equity", "functional.comp")
 uniqueSite_ID <- unique(f4$Site_ID)
@@
   n <- length(Site_temp$Plant.sp)
-  combinatorials <- matrix(ncol = 6, nrow = 1, NA) #flexible
-  colnames(combinatorials) <- c("SiteID", "Plant_number_level", "iteration", "equity", "functional.comp", "nestedness")
+  combinatorials <- matrix(ncol = 5, nrow = 1, NA) #flexible
+  colnames(combinatorials) <- c("SiteID", "Plant_number_level", "iteration", "equity", "functional.comp")
   combinatorials <- as.data.frame(combinatorials)
@@
       combinatorials_3$functional.comp.poll <- out.site$functional.comp.poll[match(combinatorials_3$Site_ID, out.site$Site_id)]
-      combinatorials_3$nestedness <- out.site$nodf.song[match(combinatorials_3$Site_ID, out.site$Site_id)]
       #now save for later.
@@
       combinatorials[index+1,5] <-  combinatorials_3$functional.comp.poll #nich comp value...
-      combinatorials[index+1,6] <-  combinatorials_3$nestedness #nestedness value...
+
     } #close different combinations
@@
 
-scatter.smooth(combinatorials_all$equity ~ combinatorials_all$functional.comp) #no relationship, good
-scatter.smooth(combinatorials_all$equity ~ combinatorials_all$nestedness) #no relationship, good
+#scatter.smooth(combinatorials_all$equity ~ combinatorials_all$functional.comp) #no relationship, good
 
@@
 combinatorials_all$functional.comp.sc<-scale(combinatorials_all$functional.comp, center = T, scale = T)
-combinatorials_all$nestedness.sc<-scale(combinatorials_all$nestedness, center = T, scale = T)
 
@@
 
-plot(unique(combinatorials_all$Plant_number_level) , estimate, las = 1, ylim = c(-0.01, 0.1) ,
-     ylab = "importance of niche partitioning", xlab = "number of plants considered")
-
-#now try overall, per level.
-estimate <- rep(NA,6)
-for (i in unique(combinatorials_all$Plant_number_level)){
-  temp <- subset(combinatorials_all, Plant_number_level == i)
-  m <- lm(temp$equity ~ temp$nestedness.sc)
-  plot(temp$equity ~ temp$nestedness.sc) 
-  abline(m)
-  estimate[i] <- m$coefficients[2]
-  }
-
-plot(unique(combinatorials_all$Plant_number_level) , estimate,  las = 1, ylim = c(0, 0.1) ,
-     ylab = "importance of nestedness", xlab = "number of plants considered")
+#plot(unique(combinatorials_all$Plant_number_level) , estimate, las = 1, ylim = c(-0.01, 0.1) ,
+   #  ylab = "importance of niche partitioning", xlab = "number of plants considered")
 
@@
 
-plot(estimate_i$level, estimate_i$estimate, las = 1,
-     ylab = "importance of niche partitioning", xlab = "number of plants considered")
+#plot(estimate_i$level, estimate_i$estimate, las = 1,
+    # ylab = "importance of niche partitioning", xlab = "number of plants considered")
+
+ggplot(estimate_i,  aes(x=level, y=estimate)) +    
+  geom_point(size=4) + stat_smooth(method=loess,  size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+  #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+  xlab("Number of plant species considered") +      
+  ylab("Importance of niche complementarity") + theme_bw()  +
+  theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
+
+#AM: NOT SURE WHICH FIGURE WE WANT TO USE HERE
+
 #we had an issue for n = 5 ...
@@
 ```
+Figure X.
+Results of simulation evaluating the importance of niche complementarity in determining differences in equity in reproductive across communities harboring from one to six species.
+Points represent average values for 16 combinations of XXXX 100 times???
+[can you fill this Nacho?]()
 
@@
 
-The relationship between community structure and ecosystem function has been long suggested, yet the specific mechanisms by which structure influences function remain elusive.
+The existence of a relationship between community structure and ecosystem function has been long hypothesized, yet, the specific mechanisms by which structure influences function remain elusive [@Thompson2012].
 Our results show that different aspects of community structure affect different dimensions of functioning.
-In particular, we find that the functional complementarity between pollinators, a measure of the overlap in the niches of different species in terms of plant coverage, has an important effect for direct measures of reproductive success (e.g., fruitset).
-However, we also find that nestedness, a measure of the redundancy in ecological functions between pollinators is important in determining a stable and equitable function across whole communities.
-
-One of the first conclusions we can extract from the fact that in most cases both of the models we considered (i.e., the simple model based on visitation metrics and the more complex one including community structure metrics) were equally good, is that for simple predictive purposes, simple visitation metrics, such as the diversity of pollinators visiting a plant, might be enough [cite Garibaldi papers using them]().
-Yet, a mechanistic understanding of the underlying processes requires that we take into account measures of community structure.
-
-Consistent with previous studies in artificial [@Frund2013] and natural [@Fontaine2005] communities, we find that functional complementarity is very important in determining differences in reproductive outputs.
+In particular, we find that the centrality of a species within a community, which measures the number of connections it received from other species in the community, had a positive effect for its fruitset.
+At the community level, however, we find that niche complementarity between pollinators, a measure of the overlap in the niches of different species in terms of plant coverage, has an important effect for average fruitset.
+
+One of the first conclusions we can extract from the fact that in most cases both of the models we considered (i.e., the simple model based on visitation metrics and the more complex one including community structure metrics) were equally good, is that for simple predictive purposes, simple visitation metrics, such as pollinator diversity, might be enough [@Garibaldi2013; @Garibaldi2015 estos???][cite Garibaldi papers using them]().
+Yet, a mechanistic understanding of the underlying processes requires that we take into account measures of community structure, and in particular those related to the overlap in the niches of interacting species.
+
+Consistent with previous studies conducted within experimental [@Fontaine2005; @Frund2013] and natural [@Valdovinos2016] communities, we find that niche complementarity is very important in determining differences in reproductive outputs.
+Similar to these previous studies, we find that communities where there is less overlap in the niches occupied by pollinator species had greater values of reproductive success, both greater fruitset values and larger numbers of seeds per fruit.
 Indeed, this reflects the fact that reproductive success in plant species requires of the delivery of conspecific pollen and thus of a certain degree of specialization amongst pollinator species on a particular plant resource in order to avoid the negative effects of inter-specific pollen deposition (e.g., pollen loss [@Flanagan2009] or interference with conspecific pollen [@Morales2008]).
 
-Nevertheless, we also find that redundancy in pollinator functions is also important in determining a certain stability in the pollination service across a larger number of individuals within a plant species.
-Indeed, our results also support previous accounts of the importance of nestedness for plant-pollinator communities [@Bascompte2003] as it ensures that reproductive success is distributed amongst a larger number of individuals, thus ensuring the maintenance of a greater genetic diversity in natural populations.
-This aspect of reproductive, which is seldom taken into account, is however of great importance, as genetic diversity will ensure the resilience of populations to further change.
-
-Paragraph somewhere about the importance of how you measure functioning (average vs equity).
-
-Our findings show that the analysis of natural communities of interacting species using network analysis not only represents an ideal way of visualizing and grasping the complexity present, but also represents a manner of mechanisitically understanding differences observed across individuals and/or species.
-
-Future studies should focus on the long-lasting effects of community structure for plant fitness, by evaluating the consequences of different community structures for heritability.
+In our study, we did not find an effect of nestedness for reproductive success in any case.
+This metric, widely used across network analysis, and which is deemed to stabilize [@Bastolla2009] or destabilize [@James2012] natural communities, does not seem to play a direct role in ecosystem function measured as plant reproductive success.
+However, our study is limited to a maximum of six plant species per community, and including more species might reveal different patterns, in which nestedness and the redundancy it implies might play a more important role.
+
+Community-level plant reproductive success, measured as average fruit or seed set across all the species considered [@Frund2013], is an important part of the functions delivered by pollinators to plants.
+However, these average values might be masking a great deal of variability amongst species, and thus a nuanced view of the effect of pollinators on whole-plant ensembles is that which we include in our analyses: the effect of pollinators on equity in reproductive succes across plant species.
+This aspect ensures that reproductive success is equally distributed amongst a larger number of species, thus contributing to the maintenance of a greater species diversity in natural populations.
+Indeed, we know that plant species diversity within a community is largely driven by different types of direct and indirect interactions including those amongst plant species (e.g., resource competition [@Goldberg1992] or facilitation [@Bruno2003]), as well as those defining antagonistic (e.g., involving pathogens [@Bagchi2010], or mutualistic interactions (e.g, pollinators [@Benadi2013]).
+However, equitability in reproductive success across species is seldom taken into account, despite its importance in maintaining genetic diversity and ensuring the resilience of populations to further change (REF).
+
+In the case of equity we did not find a significant effect of either simple visitation or community structure metrics.
+However, the results of our simulation on the importance of community structure as the number of plant species considered increases shows us that this effect dramatically increases when more than four plant species are considered.
+This implies that if we were able to measure reproductive success for all the plant species in all the communities (which we cannot do due to constraints on sampling effort), we might find that the effects of community structure might be even more prevalent.
+
+In summary, our findings show that the analysis of natural communities of interacting species using network analysis not only represents an ideal way of visualizing and grasping the complexity present within these communities, but also represents a manner of mechanisitically understanding differences observed across individuals and/or species.
+
+Future studies could build on this body of research by focusing on the long-lasting effects of community structure for plant fitness, by evaluating the consequences of different community structures for heritability.
 

### 2019-03-19 paper_round2.Rmd
try to understand the code

@@
 To this end, we use a well-replicated dataset encompassing 16 well-resolved plant-pollinator interaction networks coupled with data on the reproductive success of 19 plant species recorded at Mediterranean shrub ecosystems within the area of influence of Doñana National Park in SW Spain.
-Our study focuses on understanding whether adding information on the structure of the community to previously-used simple visitation metrics (e.g., number of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success.
+Our study focuses on understanding whether adding information on the structure of the community to previously-used simple visitation metrics (e.g., number and diversity of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success.
 In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success, and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success.
@@
 (2017) by using a normalized value of the widely-used nestedness metric NODF [@Almeida-Neto2011], $NODF_c$.
-This normalized value is calculated as $NODF_c = NODF_n/(C * log(S))$, where C is connectance, S is network size and $NODF_n = NODF/max(NODF)$, which is independent of network size and thus comparable across different networks [@Song2017].
+This normalized value is calculated as $NODF_c = NODF_n/(C * log(S))$, where C is connectance, S is network size and $NODF_n = NODF/max(NODF)$, which is independent of network size and thus comparable across different networks [@Song2017].[See new paper by Benno simons updating Song method :(]()
 
@@
 #This is ok, but a few rare interactions are taken outside the transect (which can be removed?), and we are including focal 3' observations, which can be explained in methods.
-#d <- subset(d, subset = Out != "out") #SHould we do that?
+#d <- subset(d, subset = Out != "out") #Should we do that?
 f<-fruitset
@@
 f2_scaled_fruit <- f2 %>% group_by(Plant.sp) %>% mutate(tot.fruitset = range01(tot.fruitset))
+f2_scaled_fruit2 <- f2 %>% group_by(Plant.sp) %>% mutate(tot.fruitset = scale(tot.fruitset, center = TRUE, scale = TRUE))
 
@@
               mean.fruitset = mean(tot.fruitset))
-
+f.ag.pr2 <- ddply(f2_scaled_fruit2, c("Site_ID", "Plant.sp", "nodf.song", "functional.comp.poll", "species.poll"), 
+              summarise, tot.visits    = sum(tot.visits),
+              mean.fruitset = mean(tot.fruitset))
+hist(f.ag.pr2$mean.fruitset)
 #select species with normalized values >0.5
 f.ag_scaledb<-subset(f.ag.pr, f.ag.pr$mean.fruitset>0.50)
+f.ag_scaledb2<-subset(f.ag.pr2, f.ag.pr$mean.fruitset>0)
 
 #for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
-f.ag_scaledb$no_rows<-rep(1, nrow(f.ag_scaledb))
-f4c<- aggregate(no_rows ~ Site_ID, f.ag_scaledb, length)
+f.ag_scaledb2$no_rows<-rep(1, nrow(f.ag_scaledb2))
+f4c<- aggregate(no_rows ~ Site_ID, f.ag_scaledb2, length)
 head(f4c)
@@
 #scale all variables
-
 f4e$nodf.song.sc <- scale(f4e$nodf.song, center = T, scale = T)
@@
 f4e$species.pl.sc <- scale(f4e$species.pl, center = T, scale = T)
+
+#Nacho depart##
+#plot
+plot(f4e$equity ~ f4e$functional.comp.poll.sc, las = 1)
+#WARNING! Fails, because f4 (as calculated below) removes plants with n = 1 across trials). Hence 1.6 value...
+
+m1 <- glm(equity ~  functional.comp.poll.sc , family="binomial", data=f4e)
+m2 <- glm(cbind(no_rows, total.plant.numb) ~  functional.comp.poll.sc , family="binomial", data=f4e)
+m3 <- glm(equity ~  functional.comp.poll.sc , weights = total.plant.numb, family="binomial", data=f4e)
+
+summary(m1)
+summary(m2)
+summary(m3)
+#bah...
+####
 
@@
 f4 <- subset(f4, !Plant.sp %in% c("Astragalus lusitanicus", "Cistus albidus", "Anchusa azurea"))
-#Alternative, we use raw values (not dividing by max.)
+#Alternative, we use raw values (not dividing by max. and scale. Thos will take value of 0, which is equally arbitrary...)
 

### 2019-03-27 paper_round2.Rmd
paper written

@@
 ---
-title: "Impact of interaction network structure on community-level plant reproduction success"
+title: Interaction network structure maximizes community-level plant reproduction success via niche complementarity
 author: "Magrach, A, Molina, FP, Bartomeus, I"
-output: html_document
-bibliography: library.bib
 csl: ecology-letters.csl
+output:
+  word_document: default
+  html_document: default
+  pdf_document: default
 editor options:
   chunk_output_type: console
+bibliography: library.bib
 ---
 
-------------------------------------------------------------------------------------------------
-[To be potentially submitted to ECOLOGY LETTERS as a Letter: maximum of 5000 words and 6 figures, tables or text boxes. 
-The abstract page should contain a short summary not exceeding 150 words for Letters.
-
-III. Main text (Sections b-d required for Letters only)
-(a) Introduction. The introduction should summarize briefly the background and aims, and end with a very brief statement of what has been achieved by the work.
-
-(b) Material and methods.
-This section should contain sufficient detail so that all procedures can be repeated (in conjunction with cited references).
-A checklist is provided so that authors can check that their methods report details which our editors regard as essential.
-This checklist is available here.
-Where specific equipment and materials are named, the manufacturer's name, city and country should be given (generally in parentheses after first mention).
-
-(c) Results.
-The Results section should present the experiments that support the conclusions to be drawn later in the Discussion.
-The Results section should conform to a high standard of rigour.
-Extended lines of inference, arguments or speculations should not be placed in the Results.
-
-(d) Discussion.
-The Discussion section should be separate from the Results section.
-It allows authors to propose their interpretation of the results, and to suggest what they might mean in a wider context.
-It should end with a clear statement of the main conclusions of the research, and a clear explanation of their importance and relevance.
-
-(e) Acknowledgements. Acknowledgements should be brief and concise.
-
-(f) References. See below for detailed information to in-text citations and Reference list.]
-
-Title: Interaction network structure maximizes community-level plant reproduction success via niche complementarity
+**Interaction network structure maximizes community-level plant reproduction success via niche complementarity**
 
@@
 
-# ABSTRACT
+\nextpage
+
+**Abstract**
 
@@
 Contrastingly, a mechanisitic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success, requires additional information on community structure, particularly that reflecting niche complementarity between pollinators.
-
-#INTRODUCTION
+\nextpage
+
+**Introduction**
 
@@
 In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success, and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success.
-In addition, we evaluate whether community structure helps us explain differences in equity in reproductive success across individuals within a species and species within a community as a measure of evenness and [stability in the pollination service??]()
+In addition, we evaluate whether community structure helps us explain differences in equity in reproductive success across individuals within a species and species within a community as a measure of evenness and stability in the pollination service.
 
@@
 
-[IB: this intro is brilliant!]() THANK YOU!! :) :)
-
-# METHODS
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=9}
+
+#LOAD ALL NECESSARY DATA AND PACKAGES
+
+#R PACKAGES
+
+library(devtools)
+#Then install the data package. Reprot issues 
+#install_github("ibartomeus/BeeFunData", ref = "fun")
+
+library(BeeFunData)
+library(plyr)
+library(dplyr)
+library(ggplot2)
+library(grid)
+library(iNEXT)
+require(Hmisc)
+library(knitr)
+library(lme4)
+library(lmerTest) #to calculate coeff and p values
+library(car) #to calculate VIF
+library(bbmle)  #to select best model based on AIC
+library(ggplot2)
+library(DHARMa) #to check for problems in residuals
+library(reshape2)
+library(spaa)
+library(cowplot)
+#devtools::install_github("hohenstein/remef")
+library(remef)
+library(glmmTMB)
+library(vegan)
+
+#LOAD ALL DATA
+
+d<-all_interactions
+f<-fruitset
+s<-seedset
+
+f$Plant.sp<-paste(f$Plant_genus, f$Plant_species)
+f$Plant.sp<-as.factor(f$Plant.sp)
+
+s$Plant.sp<-paste(s$Plant_genus, s$Plant_species)
+s$Plant.sp<-as.factor(s$Plant.sp)
+
+#calculate column with fruit set as
+
+#Fruit_Yes +  Fruit_Preyed + Fruit_Dispersed) / (Fruit_Yes + Fruit_No +Fruit_Preyed + Fruit_Dispersed) #Nacho this equation is wrong in your metadata!
+
+#1st eliminate frutos perdidos
+wordList <- c("fruto perdido","frutos perdidos")
+
+f2<-subset(f, Notes %nin% wordList)
+
+f2$tot.fruitset<-(f2$Fruit_Yes +  f2$Fruit_preyed + f2$Fruit_dispersed)/(f2$Fruit_Yes +f2$Fruit_No + f2$Fruit_preyed + f2$Fruit_dispersed)
+
+s2<-subset(s, Notes %nin% wordList)
+#calculate average seed set per plant individual, there are several fruit measurements per plant and would lead to 3 nested random factors
+
+s3 <- ddply(s2, c("Site_ID", "Plant.sp", "Plant.ID"), summarise,
+                         mean.seedn    = mean(Seeds2),
+                          mean.seedw = mean(Seed.weight),
+                          mean.fruitweight = mean(Fruit.weight2))
+
+###### read network and species level files (network analyses to be found at "...scripts/network analysis.R")
+
+outsp.pl.site<-read.csv("SITE_plant_species_level_metrics.csv")
+outsp.site<-read.csv("SITE_species_level_metrics.csv")
+out.site<-read.csv("SITE_network_level_metrics.csv")
+
+outsp.pl.site.sinout<-read.csv("SITE_plant_species_level_metrics_sinout.csv")
+outsp.site.sinout<-read.csv("SITE_species_level_metrics_sinout.csv")
+out.site.sinout<-read.csv("SITE_network_level_metrics_sinout.csv")
+
+```
+
+**Methods**
 
@@
 
-Our study was conducted in SW Spain within the area of influence of Doñana National Park (Figure 1?).
-Here, we surveyed 16 Mediterranean woodland patches, located within a XXX m2 area and with an average distance of XX km between them (min= XX, max= XX).
-[SHOULD WE SAY SOMETHING ABOUT THE MATRIX SURROUNDING THESE SITES OR THE TYPE OF VEGETATION PRESENT IN THEM???
-IB: I don't think is relevant.
-ASK CURRO ABOUT THE NUMBERS ABOVE.]() Each site was surveyed 7 times during the flowering season of 2015 (from February to May) following a 100-m x 2 m transect for 30 mins.
-Along each transect, we identified all plant species and recorded all the flower visitors (including bees, hoverflies, beetles and XX) [IS IT JUST BEES AND HOVERFLIES?
-IB: NO, ALL VISITORS!]() that legitimately visited them.
+Our study was conducted in SW Spain within the area of influence of Doñana National Park (Figure 1).
+Here, we surveyed 16 Mediterranean woodland patches with an average distance of 7 km between them (min= 3 km, max= 46.5 km).
+Each site was surveyed 7 times during the flowering season of 2015 (from February to May) following a 100-m x 2 m transect for 30 mins.
+Along each transect, we identified all plant species and recorded all the flower visitors that legitimately visited them during each 30-min period.
+In addition, we conducted focal observations of XX specific plant individuals during XX [????]().
+We also recorded other rare interactions observed out of the basic surveys [explicar un poco mejor]().
 Floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FdPM with the aid of experts in the different taxonomic groups (see acknowledgements).
@@
 
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=9}
+
+f.inds<-ddply(f, c("Site_ID", "Plant.sp"), summarise, 
+                   tot.inds = length(Plant.sp)) #number of individuals per plant sps
+
+tableS1<-ddply(f.inds, c("Site_ID"), summarise, 
+                   tot.sps = length(Site_ID)) #number of plant sps per site
+
+s.fruitnum<-ddply(s, c("Site_ID", "Plant.sp"), summarise, 
+                   tot.fruits = length(Plant.ID)) #number of fruits per individual
+```
+
 _Plant reproductive success_
 
-Within each site, we marked between 2 and 12 individuals (6.49 +- 2.37) of 1 [NB: Which site has only one species!]() [AM: Elpinar only has Rosmarinus and Villamanriqueeste only Cistus salvifolius]() to 6 plant species (4.06 +- 1.69), depending on the availability and presence of flowers during the sampling events.
-For each individual, we counted the number of flowers at each sampling point and recorded fruitset, the number of seeds per fruit (for 2-36 fruits, 11.17 +- 6.84) and average seed weight per fruit at the end of the season.
-Our survey included a total of 19 different plant species across our 16 sites.
-
-#DATA ANALYSES
+Within each site, we marked between `r min(f.inds$tot.inds)` and `r max(f.inds$tot.inds)` individuals (`r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`) of `r min(tableS1$tot.sps)` to `r max(tableS1$tot.sps)` plant species (`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`), depending on the availability and presence of flowers during the sampling events.
+For each individual, we counted the number of flowers at each sampling point and recorded fruitset, the number of seeds per fruit (for `r min(s.fruitnum$tot.fruits)`-`r max(s.fruitnum$tot.fruits)` fruits, `r round(mean(s.fruitnum$tot.fruits), digits=2)` $\pm$ `r round(sd(s.fruitnum$tot.fruits), digits=2)`) and average seed weight per fruit at the end of the season.
+Our survey included a total of `r nlevels(f2$Plant.sp)` different plant species across our `r nlevels(f2$Site_ID)` sites.
+
+**Data analyses**
 
@@
 The diversity of pollinator species visiting a focal plant was approximated using the plant´s normalised degree, i.e., the number of links with different pollinator species a plant has, scaled by the number of possible partners [@Dormann2009].
-Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the morisita index  (@Manual{,
-    title = {spaa: SPecies Association Analysis},
-    author = {Jinlong Zhang},
-    year = {2016},
-    note = {R package version 0.2.2},
-    url = {https://CRAN.R-project.org/package=spaa},
-  }).
+Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the morisita index [@Zhang2016].
 As a measure of centrality we used weighted closeness centrality which describes centrality through the path lengths of a species to other species in the network using a weighted representation of the network [@Dormann2009].
@@
 
-#RESULTS
-
-Within our sampling we recorded `r nrow(d)` pollinator individuals belonging to 57 species of plants and 277 species of pollinators.
-Within the pollinator community XX% of species were solitary bees, XX% hoverflies, 20% honeybees, and XX%% other??
-[Curro can calculate this if needed]()
+**Results**
 
@@
 
-#prepare stuff-----
-#If you don't have devtools install it
-#install.packages("devtools")
-#library(devtools)
-#Then install the data package. Reprot issues 
-#install_github("ibartomeus/BeeFunData", ref = "fun")
-library(BeeFunData)
-
-#devtools::install_github("jonocarroll/mathpix") #package to include mathematical formulas
-library(mathpix)
-
-library(plyr)
-
-d<-all_interactions
-#head(d)
-#I just realized here we are using all data available. 
-#This is ok, but a few rare interactions are taken outside the transect (which can be removed?), and we are including focal 3' observations, which can be explained in methods.
-#d <- subset(d, subset = Out != "out") #Should we do that?
-f<-fruitset
-s<-seedset
-
-#calculate number of plant and pollinator species in total in our sampling
-
-d.pl<-unique(all_interactions$Plant_gen_sp)
-d.poll<-unique(all_interactions$Pollinator_gen_sp)
-
-#calculate number of plant species per site, number of individuals per plant species and number of fruits per ind surveyed for repr succ
-
-library(plyr)
-
-f$Plant.sp<-paste(f$Plant_genus, f$Plant_species)
-
-f.inds<-ddply(f, c("Site_ID", "Plant.sp"), summarise, 
-                   tot.inds = length(Plant.sp)) #number of individuals per plant sps
-
-#write.csv(f.inds, file="tables/plantindspersite.csv", row.names = FALSE)
-
-mean<-mean(f.inds$tot.inds)
-stdev<-sd(f.inds$tot.inds)
-
-f.sps<-ddply(f.inds, c("Site_ID"), summarise, 
-                   tot.sps = length(Site_ID)) #number of plant sps per site
-
-#write.csv(f.sps, file="tables/plantspspersite.csv", row.names = FALSE)
-
-mean2<-mean(f.sps$tot.sps)
-stdev2<-sd(f.sps$tot.sps)
-
-s$Plant.sp<-paste(s$Plant_genus, s$Plant_species)
-
-s.fruitnum<-ddply(s, c("Site_ID", "Plant.sp"), summarise, 
-                   tot.fruits = length(Plant.ID)) #number of fruits per individual
-
-#write.csv(s.fruitnum, file="tables/fruitnumberperplantindspersite.csv", row.names = FALSE)
-
-mean3<-mean(s.fruitnum$tot.fruits)
-stdev3<-sd(s.fruitnum$tot.fruits)
-
-###### read network and species level files (network analyses to be found at "...scripts/network analysis.R")
-
-outsp.pl.site<-read.csv("SITE_plant_species_level_metrics.csv")
-outsp.site<-read.csv("SITE_species_level_metrics.csv")
-out.site<-read.csv("SITE_network_level_metrics.csv")
-```
-
-Our sampling completeness analyses revealed that with our survey we were able to capture 18-62% of pollinator species (average= 35%), 47-98% for plant species (average= 78%) and 13-41% for plant-pollinator links (average=27%), in line with that obtained with other studies (e.g., [@Chacoff2012], Figure S1?).
-Our values of sampling completeness are slightly smaller in the case of pollinators probably as a consequence of the great diversity found in the Mediterranean region and within our study area in particular, a hotspot of insect diversity (REF).
+#check proportion represented by each order, hymenoptera, diptera, coleoptera...
+ tr<-read.csv("traits_ainhoa.csv")
+# #head(tr)
+# 
+ d$order<-tr$order[match(d$Pollinator_gen_sp, tr$Pollinator_gen_sp)]
+ d.order<- aggregate(Frequency ~ order, d, sum)
+ d.order$prop<-d.order$Frequency/sum(d.order$Frequency)
+
+```
+
+Within our sampling we recorded `r nrow(d)` pollinator individuals belonging to `r nlevels(unique(d$Plant_gen_sp))` species of plants and `r nlevels(unique(d$Pollinator_gen_sp))` species of pollinators.
+Within the pollinator community the distribution in different orders was: `r round(d.order$prop[d.order$order=="Hymenoptera"]*100, digits=2)`% Hymenoptera, `r round(d.order$prop[d.order$order=="Diptera"]*100, digits=2)`% Diptera, `r round(d.order$prop[d.order$order=="Coleoptera"]*100, digits=2)`% Coleoptera, `r round(d.order$prop[d.order$order=="Lepidoptera"]*100, digits=2)`% Lepidoptera, while Araneaeae and Neuroptera represented `r round(d.order$prop[d.order$order=="Araneae"]*100, digits=2)`% each.
 
@@
 #######CALCULATE SAMPLING COMPLETENESS FOR POLLINATORS, PLANTS AND LINKS
-
-library(iNEXT)
-library(ggplot2)
-library(grid)
 
@@
 rar <- iNEXT(d6, q=0, datatype="abundance", endpoint = 400)
-poll<-ggiNEXT.iNEXT(rar, color.var="site", se=FALSE) + ylab("Pollinator species richness") + theme_bw() + 
+poll<-ggiNEXT.iNEXT(rar, color.var="site", se=FALSE) + ylab("Pollinator sps richness") + theme_bw() + 
   theme (legend.position= "none") + theme(text = element_text(size = 15), axis.text=element_text(size=rel(1)),
@@
 rar2 <- iNEXT(d.pl5, q=0, datatype="abundance", endpoint = 200)
-plant<-ggiNEXT.iNEXT(rar2, color.var="site", se=FALSE) + ylab("Plant species richness") + 
+plant<-ggiNEXT.iNEXT(rar2, color.var="site", se=FALSE) + ylab("Plant sps richness") + 
   theme_bw()  + theme (legend.position= "none") + theme(text = element_text(size = 15), axis.text=element_text(size=rel(1)),
@@
 
-grid.newpage()
-grid.draw(rbind(ggplotGrob(poll), ggplotGrob(plant), ggplotGrob(link), size = "last"))
-
-```
-
-### Species-level analyses
-
-At the species level, in the case of fruitset, our results show that both model 1 and model 2 are equally good in explaining the variability observed (i.e.,$\Delta AIC<2$), and therefore we cannot select one over the other.
-Given that model 2 has a greater number of variables which should be penalized given the added complexity it provides, we will comment results only for model 2.
-In this case, we find a positive effect of pollinator species diversity (measured using the species´normalised degree, Fig.
-XX) as well as a positive effect of the centrality of the focal plant on its fruitset.
+#FIGURE S1 AT THE END OF THE PAPER
+
+# grid.newpage()
+# grid.draw(rbind(ggplotGrob(poll), ggplotGrob(plant), ggplotGrob(link), size = "last"))
+
+```
+
+Our sampling completeness analyses revealed that with our survey we were able to capture 18-62% of pollinator species (average= 35%), 47-98% for plant species (average= 78%) and 13-41% for plant-pollinator links (average=27%), in line with that obtained with other studies (e.g., [@Chacoff2012], Figure S1).
+Our values of sampling completeness are slightly smaller in the case of pollinators probably as a consequence of the great diversity found in the Mediterranean region and within our study area in particular, a hotspot of insect diversity [@Nieto2014a].
 
@@
 
-library(ggplot2)
-library(grid)
-
-#compare 2 models: one with degree, i.e. diversity of partners, and number of visits, compared to one where position in a network (centrality) and niche overlap are included with these variables.
-
-#calculate column with fruit set as
-f$Plant.sp<-paste(f$Plant_genus, f$Plant_species)
-
-#Fruit_Yes +  Fruit_Preyed + Fruit_Dispersed) / (Fruit_Yes + Fruit_No +Fruit_Preyed + Fruit_Dispersed) #Nacho this equation is wrong in your metadata!
-
-#1st eliminate frutos perdidos
-wordList <- c("fruto perdido","frutos perdidos")
-
-require(Hmisc)
-f2<-subset(f, Notes %nin% wordList)
-
-f2$tot.fruitset<-(f2$Fruit_Yes +  f2$Fruit_preyed + f2$Fruit_dispersed)/(f2$Fruit_Yes +f2$Fruit_No + f2$Fruit_preyed + f2$Fruit_dispersed)
-
-#check correlation between different variables
-
-#head(out.site)
-#str(out.site)
-c<-cor(out.site[,2:20])
-c2<-round(c,digits=2)
-#write.csv(c2, file= "tables/variable_correlations.csv", row.names = TRUE, sep = ",")
-
-#♣correlation between weighted nodf and functional complementarity of pollinators : -0.13
-
-#create table with number of individuals per plant species sampled at each site
-
-#tableSx <- aggregate(Plant.ID ~ Site_ID + Plant.sp, data = f2, FUN = function(x){NROW(x)})
-
-#write.csv(tableSx, file= "tables/plantindspersite.csv", row.names = FALSE, sep = ",")
-
-#-------------------------------------------------------------------------------------------
-#join plant species level network metrics with fruit and seed set for each site, also with niche overlap and number of visits
+# CALCULATE NICHE OVERLAP BETWEEN PLANT SPECIES AND TOTAL NUMBER OF VISITS AND JOIN FRUITSET DATA WITH NETWORK METRICS
 
 #calculate total number of visits per plant sps
-
-library(plyr)
 
@@
 #calculate average niche overlap per species
-
-library(reshape2)
-library(spaa)
-library(plyr)
 
@@
 
-#use unaggregated data
+#use unaggregated data and join it with network metrics
 
@@
 f2$weigh_closeness<-outsp.pl.site$weigh_closeness[match(f2$match, outsp.pl.site$match)]
+
+#and with niche overlap and total number of visits
 f2$niche.overlap<-out.niche.agg$mean.niche.over[match(f2$match, out.niche.agg$j)]
@@
 f2$species.poll.sc<-scale(f2$species.poll, center = T, scale = T)
-
 f2$norm_degree.sc<-scale(f2$norm_degree, center = T, scale = T)
@@
 #scale total visits per plant species
-library(dplyr)
-f2_scaled <- f2 %>% group_by(Plant.sp) %>% mutate(tot.visits.sc = scale(tot.visits, center = T, scale = T))
-
-# 
-# #check correlations between different species level variables
-# 
-#cor(f2[,23:29])
-
-library(psych)
-dim(f2)
-pairs.panels(f2[,23:28])
-
-#fit models 1 and 2
-
-library(lme4)
-library(lmerTest) #to calculate coeff and p values
-library(car) #to calculate VIF
-library(bbmle)  #to select best model based on AIC
-library(ggplot2)
-library(DHARMa) #to check for problems in residuals
+f2_scaled <- f2 %>% group_by(Plant.sp) %>% mutate(tot.visits.sc = scale(tot.visits, center = T, scale = T), na.rm=TRUE)
+```
+
+_Species-level analyses_
+
+At the species level, in the case of fruitset, our results show that model 2 is the best model explaining the variability observed.
+In this case, we find a positive effect of pollinator species diversity (measured using the species´normalised degree, Fig.
+2) as well as a positive effect of the centrality of the focal plant on its fruitset (Fig.
+2).
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
+
+#compare 2 models: one with degree, i.e. diversity of partners, and number of visits, compared to one where position in a network (centrality) and niche overlap are included with these variables.
 
@@
 summary(m1)
-
 vif(m1)  #check for correlations between variables included in model
@@
 
-summary(m2) #both norm degree and weigh closeness have intervals not overlapping 0
-
+summary(m2) #norm degree and weigh closeness have intervals not overlapping 0
 vif(m2)
@@
 
-AICtab(m1, m2) #both are equally good using binomial distribution!!
+AICtab(m1, m2) #M2 is best!!
 
@@
 
-# extract coefficients and p-values for m1 and present them in paper
+# extract coefficients and p-values for m2 and present them in paper
 coefs.m2 <- data.frame(coef(summary(m2)))
-# use normal distribution to approximate p-value
-coefs.m2$p.z <- 2 * (1 - pnorm(abs(coefs.m2$z.value)))
 coefs.m2
-summ<-round(coefs.m2,digits=2)
-#write.csv(summ, file="tables/resultsfruitsetSPECIES.csv", row.names = TRUE)
+Table1<-round(coefs.m2[,1:3],digits=2)
+rownames(Table1)<-c("(Intercept)", "Normalized degree", "Total number of visits", "Weighted closeness", "Niche overlap")
+#at the end of the paper
 
@@
 
-#devtools::install_github("hohenstein/remef")
-library(remef)
 y_partial_norm <- remef(m2, fix= c( "tot.visits.sc", "weigh_closeness.sc", "niche.overlap.sc"), ran = "all", inverse = F)
@@
 
-pl1<-ggplot(m2@frame,  aes(x=m2@frame$norm_degree.sc[1:325,1], y=y_partial_norm_inv)) +    
-  geom_point(size=4) + stat_smooth(method=lm,  size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+pl1<-ggplot(m2@frame,  aes(x=m2@frame$norm_degree.sc, y=y_partial_norm_inv, color=Plant.sp)) +    
+  geom_point(size=2.5, shape=21, colour="black", aes(fill=factor(Plant.sp))) + stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
   #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
   xlab("Normalized degree") +      
-  ylab("Fruitset") + theme_bw()  + theme (legend.position= c(0.85,0.3)) +
-  theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + 
-  labs(col="Plant species") +  theme(legend.text = element_text(size = 10, face = "italic"), legend.title = element_text(size=11, face = "bold"))
+  ylab("Fruitset") + theme_bw()  + theme (legend.position= c(0.85,0.35)) +
+  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.1), face="bold")) + 
+  scale_fill_discrete(name="Plant species") +  theme(legend.text = element_text(size = 6, face = "italic"), legend.title = element_text(size=11, face = "bold"), legend.direction = "horizontal")
 
@@
 
-pl1b<-ggplot(m2@frame,  aes(x=m2@frame$weigh_closeness.sc[1:325,1], y=y_partial_weigh_inv)) +    
-  geom_point(size=4) + stat_smooth(method=lm,  size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+pl1b<-ggplot(m2@frame,  aes(x=m2@frame$weigh_closeness.sc, y=y_partial_weigh_inv, color= Plant.sp)) +    
+  geom_point(size=2.5, shape=21, colour="black", aes(fill=factor(Plant.sp))) + stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
   #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
   xlab("Centrality") +      
-  ylab("Fruitset") + theme_bw()  + theme (legend.position= c(0.85,0.3)) +
-  theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + 
-  labs(col="Plant species") +  theme(legend.text = element_text(size = 10, face = "italic"), legend.title = element_text(size=11, face = "bold"))
+  ylab(" ") + theme_bw()  + theme (legend.position= "top") +
+  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.3), face="bold")) + 
+  scale_fill_discrete(name="Plant species") +  theme(legend.text = element_text(size = 6, face = "italic"), legend.title = element_text(size=11, face = "bold"), legend.direction = "horizontal")
 
@@
 
-library(cowplot)
-plot_grid(pl1, pl1b, labels = c("A", "B"))
-
-```
-
-Figure X.
-Partial residual plots showing the effect of a) pollinator species diversity (approximated using normalized degree) and b) species centrality on fruitset for each of the plant species considered.
-Dots represent each of the individuals sampled for each species within each site.
-
-For all other measures of reproductive success considered (i.e., the number of seeds per fruit, fruit and seed weight), the best model based on its AIC value was model 1, i.e., the model that only included simple visitation metrics (in this case, pollinator species diversity and the total number of visits received by a focal plant species).
-However, none of the variables included within our model explain the differences observed.
-[show in sup mat?]()
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+ prow <- plot_grid( pl1 + theme(legend.position="none"),
+           pl1b + theme(legend.position="none"),
+           align = 'vh',
+           labels = c("A", "B"),
+           hjust = -1,
+           nrow = 1
+           )
+
+# extract the legend from one of the plots
+legend_b <- get_legend(pl1 + theme(legend.position="bottom"))
+
+# add the legend underneath the row we made earlier. Give it 10% of the height
+# of one plot (via rel_heights).
+Figure2 <- plot_grid( prow, legend_b, ncol = 1, rel_heights = c(1, .2))
+
+```
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
 ##ahora con seed set
-
-s$Plant.sp<-paste(s$Plant_genus, s$Plant_species)
-
-#1st eliminate frutos perdidos
-wordList <- c("fruto perdido","frutos perdidos")
-
-require(Hmisc)
-s2<-subset(s, Notes %nin% wordList)
-
-#calculate average seed set per plant individual, there are several fruit measurements per plant and would lead to 3 nested random factors
-library(plyr)
-
-s3 <- ddply(s2, c("Site_ID", "Plant.sp", "Plant.ID"), summarise,
-                         mean.seedn    = mean(Seeds2),
-                          mean.seedw = mean(Seed.weight),
-                          mean.fruitweight = mean(Fruit.weight2))
-
-#use unaggregated data
 
@@
 
+```
+
+For the number of seeds per fruit, our results show that both model 1 and model 2 are equally good in explaining the variability observed (i.e.,$\Delta AIC<2$), and therefore we cannot select one over the other.
+Given that model 2 has a greater number of variables which should be penalized given the added complexity it provides, we will comment results only for model 2.
+In this case, we find a positive effect of the niche overlap between plant species (Fig.
+3).
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
 #fit two models
@@
 summary(m1.seed)
-
 vif(m1.seed)
@@
 summary(m2.seed)
-
 vif(m2.seed)
 
-AICtab(m1.seed, m2.seed) #m1 here is best model with m2 having a differnce of 4. However m2 has niche overlap as significant.
+AICtab(m1.seed, m2.seed) #both models are equally good.
 
@@
 # extract coefficients and p-values for m1 and present them in paper
-coefs.m1.seed <- data.frame(coef(summary(m1.seed)))
+coefs.m2.seed <- data.frame(coef(summary(m2.seed)))
 # use normal distribution to approximate p-value
-coefs.m1.seed$p.z <- 2 * (1 - pnorm(abs(coefs.m1.seed$t.value)))
-coefs.m1.seed
-summ.seed<-round(coefs.m1.seed,digits=2)
-#write.csv(summ.seed, file="tables/resultsseedsetSPECIES.csv", row.names = TRUE)
+#coefs.m2.seed$p.z <- 2 * (1 - pnorm(abs(coefs.m2.seed$t.value)))
+coefs.m2.seed
+Table2<-round(coefs.m2.seed,digits=2)
+rownames(Table2)<-c("(Intercept)", "Normalized degree", "Total number of visits", "Weighted closeness", "Niche overlap")
+
+#plot significant variables
+y_partial_norm_seed <- remef(m2.seed, fix= c("norm_degree.sc", "tot.visits.sc", "weigh_closeness.sc"), ran = "all", inverse = F)
+#With this we remove the influece of x2 and the random effects from the dependent variable
+y_partial_norm_seed_inv<-exp(y_partial_norm_seed)/(1+exp(y_partial_norm_seed))
+#then we use this new variable to plot. We use m1@frame as dataset because not all observations are used in modeldue to presence of NAs
+
+Figure3<-ggplot(m2.seed@frame,  aes(x=m2.seed@frame$niche.overlap.sc, y=y_partial_norm_seed_inv, color= Plant.sp)) +    
+  geom_point(size=2.5, shape=21, colour="black", aes(fill=factor(Plant.sp))) + stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
+  #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+  xlab("Niche overlap") +      
+  ylab("Seeds per fruit") + theme_bw()  + theme (legend.position= "bottom") +
+  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.3), face="bold")) + 
+  scale_fill_discrete(name="Plant species") +  theme(legend.text = element_text(size = 6, face = "italic"), legend.title = element_text(size=11, face = "bold"))
+
+#Figure3  #al final del paper
+
+```
+
+For all other measures of reproductive success considered (i.e., fruit and seed weight), the best model based on its AIC value was model 1, i.e., the model that only included simple visitation metrics (in this case, pollinator species diversity and the total number of visits received by a focal plant species).
+However, none of the variables included within our model explain the differences observed.
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
 
 #SEED WEIGHT
-library(glmmTMB)
+
 m1.seed.w<-glmmTMB(mean.seedw ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3_scaled)
@@
 # extract coefficients and p-values for m1 and present them in paper
-summ.seed.w<-summary(m1.seed.w)$coefficients$cond
-#write.csv(summ.seed.w, file="tables/resultsseedweightSPECIES.csv", row.names = TRUE)
+tableS4<-round(summary(m1.seed.w)$coefficients$cond[,1:3], digits=2)
+rownames(tableS4)<-c("(Intercept)", "Normalized degree", "Total number of visits")
 
@@
 # extract coefficients and p-values for m1 and present them in paper
-summ.fruit.w<-summary(m1.fruit.w)$coefficients$cond
-#write.csv(summ.seed.w, file="tables/resultsfruitweightSPECIES.csv", row.names = TRUE)
-
-```
-
-### Community-level analyses
-
-At the network level, we find different patterns for fruitset and the number of seeds per fruit as compared to those for fruit and seed weight.
-In the case of fruitset and the number of seeds per fruit, we find that both model 1 and 2 are equally good in describing the differences observed (i.e.,$\Delta AIC<2$).
-Again, because this suggests model 2 is a good model despite its added complexity, we will comment results for this model only.
-In particular, we find that both fruitset and the number of seeds per fruit are positively related to niche complementarity between pollinators.
-Additionally, we find a negative effect of community-level pollinator species diversity on average fruitset.
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=10}
+tableS5<-round(summary(m1.fruit.w)$coefficients$cond[,1:3], digits=2)
+rownames(tableS5)<-c("(Intercept)", "Normalized degree", "Total number of visits")
+
+```
+
+_Community-level analyses_
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
 
@@
 
-library(plyr)
 #this is how i did originally, average of everything together, now following Nacho´s advice changing to mean of means previously calculated per sps
@@
 f.agg$tot.visits.sc <- scale(f.agg$tot.visits, center = T, scale = T)
+```
+
+At the community level, we find different patterns for fruitset and the number of seeds per fruit as compared to those for fruit and seed weight.
+In the case of fruitset and the number of seeds per fruit, we find that both model 1 and 2 are equally good in describing the differences observed (i.e.,$\Delta AIC<2$).
+Again, because this suggests model 2 is a good model despite its added complexity, we will comment results for this model only.
+In particular, we find that both fruitset and the number of seeds per fruit are positively related to niche complementarity between pollinators (Fig.
+4).
+Additionally, we find a negative effect of community-level pollinator species diversity and the total number of visits on average fruitset (Fig.
+4).
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
 
@@
 m2.fruit.net<-glmmTMB(mean.fruitset ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="beta_family", data=f.agg)
-
-#note estimate of niche part do not overlap zero 0.06105  +-  0.03637 and it's moderatelly big.
 
@@
 
-#save table with results for paper
-summ.fruit.net<-round(summary(m2.fruit.net)$coefficients$cond, digits=2)
-#write.csv(summ.fruit.net, file="tables/resultsfruitsetNETWORK.csv", row.names = TRUE)
+#table with results for paper
+Table3<-round(summary(m2.fruit.net)$coefficients$cond, digits=2)
+rownames(Table3)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Nestedness", "Niche complementarity")
+#at the end of paper
 
@@
 pl2 <- ggplot(f.agg,  aes(x=functional.comp.poll.sc, y= res.tr)) +    
-        geom_point(size=4, color="black") + 
-  stat_smooth(method = 'lm', size=1.5, se=TRUE, color = "black", alpha=0.2) +     
-        xlab("Functional complementarity") +      
-        ylab("Fruitset") + theme_bw()  + #theme (legend.position= "none") +
-        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
-
-pl2
+        geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
+  stat_smooth(method = 'lm', size=1, se=TRUE, color = "black", alpha=0.4) +     
+        xlab("Niche complementarity") +      
+        ylab(" ") + theme_bw()  + #theme (legend.position= "none") +
+        theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
 
@@
 pl3 <- ggplot(f.agg,  aes(x=species.poll.sc, y= res.tr2)) +    
-        geom_point(size=4, color="black") + 
-  stat_smooth(method = 'lm', size=1.5, se=TRUE, color = "black", alpha=0.2) +     
-        xlab("Pollinator species diversity") +      
+        geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
+  stat_smooth(method = 'lm', size=1, se=TRUE, color = "black", alpha=0.4) +      
+        xlab("Pollinator sps diversity") +      
         ylab("Fruitset") + theme_bw()  + #theme (legend.position= "none") +
-        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
-
-pl3
+        theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
+
+pred3<-summary(m2.fruit.net)$coefficients$cond[1]+ (summary(m2.fruit.net)$coefficients$cond[2] * mean(f.agg$species.poll.sc)) + (summary(m2.fruit.net)$coefficients$cond[3] * f.agg$tot.visits.sc) + (summary(m2.fruit.net)$coefficients$cond[4]* mean(f.agg$nodf.song.sc)) + (summary(m2.fruit.net)$coefficients$cond[5] * mean(f.agg$functional.comp.poll.sc))
+
+res3<-pred3-f.agg$mean.fruitset
+res.tr3<-exp(res3)/(1+exp(res3))
+
+pl4 <- ggplot(f.agg,  aes(x=tot.visits.sc, y= res.tr3)) +    
+        geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
+  stat_smooth(method = 'lm', size=1, se=TRUE, color = "black", alpha=0.4) +    
+        xlab("Total number of visits") +      
+        ylab(" ") + theme_bw()  + #theme (legend.position= "none") +
+        theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
 
@@
 
-library(cowplot)
-plot_grid(pl3, pl2, labels = c("A", "B"))
-
-```
-
-Figure X.
-Partial residual plots showing the effect of a) total pollinator species diversity at the community level and b) functional complementarity between pollinator species on average fruitset at the community level.
-Dots represent average vaues of fruitset at the level of the community for all plant species considered (N=16 sites).
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=10}
+Figure4<-plot_grid(pl3, pl4, pl2, labels = c("A", "B", "C"), nrow=1) #al final del paper
+
+```
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
 
@@
 #same as before now averaging per species first and then per site
-
-library(plyr)
 
@@
 
+```
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
+
 #average seed set
-#TRY ZERO-INFLATED POISSON!
 
@@
 
-m2.seed.net <- glm(mean.seedset ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, data=s.comm,family="gaussian")
+m2.seed.net <- lm(mean.seedset ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, data=s.comm,family="gaussian")
 
@@
 #save table with results for paper
-summ.seed.net<-round(summary(m2.seed.net)$coef$cond, digits=2)
-#write.csv(summ.seed.net, file="tables/resultsseedsetNETWORK.csv", row.names = TRUE)
-
-y_partial_seed<-keepef(m2.seed.net, fix= c( "tot.visits.sc", "species.poll.sc ", "nodf.song.sc"), ran = "all", keep.intercept = F, grouping = F)
-
-pl4<-ggplot(s.comm,  aes(x=tot.visits.sc, y=mean.seedset))+      
-        geom_point(size=4, color="black") + stat_smooth(method=lm,  size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+Table4<-round(summary(m2.seed.net)$coefficients[,1:3], digits=2)
+rownames(Table4)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Nestedness", "Niche complementarity") #end of paper
+
+pl5<-ggplot(s.comm,  aes(x=tot.visits.sc, y=mean.seedset))+      
+       geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
         #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
         xlab("Total number of visits") +      
-        ylab("Number of seeds/fruit") + theme_bw()  + #theme (legend.position= "none") +
-        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
-
-#pl4
-
-pl5<-ggplot(s.comm,  aes(x=functional.comp.poll.sc, y=mean.seedset))+      
-        geom_point(size=4, color="black") + stat_smooth(method=lm,  size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+        ylab("Number of seeds/fruit") + theme_bw()  + 
+  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
+
+#pl5
+
+pl6<-ggplot(s.comm,  aes(x=functional.comp.poll.sc, y=mean.seedset))+      
+        geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
         #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
-        xlab("Functional complementarity") +      
-        ylab("Number of seeds/fruit") + theme_bw()  + #theme (legend.position= "none") +
-        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
-
-#pl5
-
-library(cowplot)
-plot_grid(pl4, pl5, labels = c("A", "B")) #NEED TO DO PARTIAL RESIDUAL PLOTS FOR THIS ONE, BUT BECAUSE I DO NOT KNOW WHETHER THIS FIG WILL ALSO GO ON THE MS NOT DOING IT NOW!
-```
-
-Figure X.
-Partial residual plots showing the effect of a) the total number of pollinator visits received at the community level and b) functional complementarity between pollinator species on the scaled average number of seeds per fruit at the community level.
-Dots represent average vaues of previously scaled values of the number of seeds per fruit at the level of the community for all plant species considered (N=16 sites).
+        xlab("Niche complementarity") +      
+        ylab(" ") + theme_bw()  + #theme (legend.position= "none") +
+        theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
+
+#pl6
+
+Figure5<-plot_grid(pl5, pl6, labels = c("A", "B")) 
+```
 
 Contrastingly, in the case of weight variables (fruit and seed weight), in both cases we find that the best model is model 1, i.e., that only including simple visitation metrics.
-Here, we find a consistent positive effect of community-level pollinator diversity for both weight descriptors.
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=10}
+Here, we find a consistent positive effect of community-level pollinator diversity for both weight descriptors (Tables S6-S7, Figs.
+S2-S3).
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
 
@@
 #save table with results for paper
-summ.fruitw.net<-round(summary(m1.fruitw.net)$coef, digits=2)
-#write.csv(summ.fruitw.net, file="tables/resultsfruitweightNETWORK.csv", row.names = TRUE)
-
-crPlots(m1.fruitw.net, smooth=FALSE, terms = ~  species.poll.sc, main = "", ylab = "Mean fruit weight", col.lines= "black", pch=19, col= "black", bg = "darkgrey", cex=2, cex.axis=1.2, cex.lab=1.5, 
-        xlab = "Pollinator species diversity")
-
-pred3<-m1.fruitw.net$coef[1]+ (m1.fruitw.net$coef[2] * s.comm$species.poll.sc) + (m1.fruitw.net$coef[3] * mean(s.comm$tot.visits.sc)) 
-res3<-pred3-s.comm$mean.fruitweight
-
-#need to see how to change the line of fit
-
-pl6<-ggplot(s.comm,  aes(x=species.poll.sc, y=res3))+      
-        geom_point(size=4, color="black") + stat_smooth(method=lm,  size=1.5, se=TRUE, color = "black", alpha=0.2) + 
-        #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
-        xlab("Pollinator species diversity") +      
-        ylab("Fruit weight (g)") + theme_bw()  + #theme (legend.position= "none") +
-        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
-
-pl6
-
+tableS6<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)
+rownames(tableS6)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")#end of paper
+
+# crPlots(m1.fruitw.net, smooth=FALSE, terms = ~  species.poll.sc, main = "", ylab = "Mean fruit weight", col.lines= "black", pch=19, col= "black", bg = "darkgrey", cex=2, cex.axis=1.2, cex.lab=1.5, 
+#         xlab = "Pollinator species diversity") #end of paper
+
+```
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
 #seed weight
@@
 #save table with results for paper
-summ.seedw.net<-round(summary(m1.seedw.net)$coef, digits=2)
-#write.csv(summ.fruitw.net, file="tables/resultsseedweightNETWORK.csv", row.names = TRUE)
-
-crPlots(m1.seedw.net, smooth=FALSE, terms = ~  species.poll.sc, main = "", ylab = "Mean seed weight", col.lines= "black", pch=19, col= "black", bg = "darkgrey", cex=2, cex.axis=1.2, cex.lab=1.5, 
-        xlab = "Pollinator species diversity")
-
-pred4<-m1.seedw.net$coef[1]+ (m1.seedw.net$coef[2] * s.comm$species.poll.sc) + (m1.seedw.net$coef[3] * mean(s.comm$tot.visits.sc)) 
-res4<-pred4-s.comm$mean.seedweight
-
-#need to see how to change the line of fit
-
-pl7<-ggplot(s.comm,  aes(x=species.poll.sc, y=mean.seedweight))+      
-        geom_point(size=4, color="black") + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
-        #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
-        xlab("Pollinator species diversity") +      
-        ylab("Seed weight (g)") + theme_bw()  + #theme (legend.position= "none") +
-        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species")
-
-pl7
-
-library(cowplot)
-plot_grid(pl6, pl7, labels = c("A", "B"))
-
-```
-Figure X.
-Partial residual plots showing the effect of community-level pollinator species diversity on average a) fruit and b) seed weight at the community level.
-Dots represent average vaues of weight at the level of the community for all plant species considered (N=16 sites).
-
-### Equity in fruitset
+tableS7<-round(summary(m1.seedw.net)$coef[,1:3], digits=2)
+rownames(tableS7) <-c("(Intercept)", "Pollinator species diversity", "Total number of visits")#end of paper
+
+# crPlots(m1.seedw.net, smooth=FALSE,  main = "", ylab = "Mean seed weight", col.lines= "black", pch=19, col= "black", bg = "darkgrey", cex=2, cex.axis=1.2, cex.lab=1.5)
+
+```
+
+_Equity in fruitset_
 
 When evaluating the effect of differences in community composition and structure for equity in reproductive success across the different species within a community we find that model 1 is the best model for all the thresholds considered (50%, 25% and 75%).
-However, we find that none of the variables considered are able to explain the differences observed.
-[this is interesting, as selfing rates I expect to be ~ 40%... In any case I am confused now on this calculation]()
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+However, we only find a significant negative relationship between equity and pollinator species diversity using the 75% threshold (Fig.
+6, Tables S8, S9, S10).
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
 
 #EQUITY SPECIES WITHIN COMMUNITIES
-
-#normalize fruitset values for individuals within species and sites, to have values between 0 and 1
-
-range01 <- function(x){(x-min(x))/(max(x)-min(x))}
-f2_scaled_fruit <- f2 %>% group_by(Plant.sp) %>% mutate(tot.fruitset = range01(tot.fruitset))
-f2_scaled_fruit2 <- f2 %>% group_by(Plant.sp) %>% mutate(tot.fruitset = scale(tot.fruitset, center = TRUE, scale = TRUE))
-
-#calculate average normalized fruitset values per site to have one unique value per site
-f.ag.pr <- ddply(f2_scaled_fruit, c("Site_ID", "Plant.sp", "nodf.song", "functional.comp.poll", "species.poll"), 
-              summarise, tot.visits    = sum(tot.visits),
-              mean.fruitset = mean(tot.fruitset))
-f.ag.pr2 <- ddply(f2_scaled_fruit2, c("Site_ID", "Plant.sp", "nodf.song", "functional.comp.poll", "species.poll"), 
-              summarise, tot.visits    = sum(tot.visits),
-              mean.fruitset = mean(tot.fruitset))
-hist(f.ag.pr2$mean.fruitset)
-#select species with normalized values >0.5
-f.ag_scaledb<-subset(f.ag.pr, f.ag.pr$mean.fruitset>0.50)
-f.ag_scaledb2<-subset(f.ag.pr2, f.ag.pr$mean.fruitset>0)
-
-#for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
-f.ag_scaledb2$no_rows<-rep(1, nrow(f.ag_scaledb2))
-f4c<- aggregate(no_rows ~ Site_ID, f.ag_scaledb2, length)
-head(f4c)
-
-#because when calculating thresholds, sites with 6 plants can score up to 6, but sites with 4 sites can score max = 4 we corrected for this doing % above threshold, and no number. 
-#calculate total number of species per site
-f4$no_rows<-rep(1, nrow(f4))
-f4d<- aggregate(no_rows ~ Site_ID, f4, length)
-head(f4d)
-
-f4c$total.plant.numb<-f4d$no_rows[match(f4c$Site_ID, f4d$Site_ID)]
-
-#remove sites that only have one plant sps, Elpinar and Villamanriqueeste
-f4e<-subset(f4c, f4c$total.plant.numb>1)
-
-#calculate equity as proportion of species with >50% of fruitset compared to total number of sps
-f4e$equity<-f4e$no_rows/f4e$total.plant.numb
-
-#join this with fruitset data used previously
-
-f4e$nodf.song<-out.site$nodf.song[match(f4e$Site_ID, out.site$Site_id)]
-f4e$functional.comp.poll<-out.site$functional.comp.poll[match(f4e$Site_ID, out.site$Site_id)]
-f4e$species.poll<-out.site$species.poll[match(f4e$Site_ID, out.site$Site_id)]
-f4e$tot.visits<-f.agg$tot.visits[match(f4e$Site_ID, f.agg$Site_ID)]
-
-f4e$species.pl<-out.site$species.pl[match(f4e$Site_ID, out.site$Site_id)]
-#scale all variables
-f4e$nodf.song.sc <- scale(f4e$nodf.song, center = T, scale = T)
-f4e$functional.comp.poll.sc <- scale(f4e$functional.comp.poll, center = T, scale = T)
-f4e$species.poll.sc <- scale(f4e$species.poll, center = T, scale = T)
-f4e$tot.visits.sc <- scale(f4e$tot.visits, center = T, scale = T)
-f4e$species.pl.sc <- scale(f4e$species.pl, center = T, scale = T)
-
-#Nacho depart##
-#plot
-plot(f4e$equity ~ f4e$functional.comp.poll.sc, las = 1)
-#WARNING! Fails, because f4 (as calculated below) removes plants with n = 1 across trials). Hence 1.6 value...
-
-m1 <- glm(equity ~  functional.comp.poll.sc , family="binomial", data=f4e)
-m2 <- glm(cbind(no_rows, total.plant.numb) ~  functional.comp.poll.sc , family="binomial", data=f4e)
-m3 <- glm(equity ~  functional.comp.poll.sc , weights = total.plant.numb, family="binomial", data=f4e)
-
-summary(m1)
-summary(m2)
-summary(m3)
-#bah...
-####
+#using raw values of mean fruitset for each species at each site
+#dataset f.ag
+#number of species per site tableS1
+
+#calculate number of sps per site producing more than 0.5 in fruitset
+
+highprod<-subset(f.ag, f.ag$mean.fruitset>0.5)
+highprod.sps<-ddply(highprod, "Site_ID", summarise, 
+                   high.sps = length(Plant.sp))
+
+#equity as proportion of high producing compared to total
+highprod.sps$tot.sps<-tableS1$tot.sps[match(highprod.sps$Site_ID, tableS1$Site_ID)]
+highprod.sps$equity<-highprod.sps$high.sps/highprod.sps$tot.sps
+
+highprod.sps$nodf.song.sc<-f.agg$nodf.song.sc[match(highprod.sps$Site_ID, f.agg$Site_ID)]
+highprod.sps$functional.comp.poll.sc<-f.agg$functional.comp.poll.sc[match(highprod.sps$Site_ID, f.agg$Site_ID)]
+highprod.sps$species.poll.sc<-f.agg$species.poll.sc[match(highprod.sps$Site_ID, f.agg$Site_ID)]
+highprod.sps$tot.visits.sc<-f.agg$tot.visits.sc[match(highprod.sps$Site_ID, f.agg$Site_ID)]
+```
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
 
 #fit two models
- m1.eq.comm<-glm(equity ~  species.poll.sc + tot.visits.sc , family="binomial", data=f4e)
+ m1.eq.comm<-glm(equity ~  species.poll.sc + tot.visits.sc , family="binomial", data=highprod.sps)
 
@@
 
- m2.eq.comm<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc , family="binomial", data=f4e)
+ m2.eq.comm<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc , family="binomial", data=highprod.sps)
 summary(m2.eq.comm)
@@
 #save table with results for paper, both models are equally good so save both tables
-summ.eq<-round(summary(m1.eq.comm)$coef, digits=2)
-#write.csv(summ.eq, file="tables/resultsequityNETWORKm1.csv", row.names = TRUE)
-
-#partial residual plots
+tableS8<-round(summary(m1.eq.comm)$coef[,1:3], digits=2)
+rownames(tableS8)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")
 
@@
 
-#Repeat with 75% threshold
-
-f75<-subset(f.ag.pr, f.ag.pr$mean.fruitset>0.75)
-
-#for each site here is the number of sps whose fruitset exceeds 75% of maximum fruitset observed in the whole study area
-f75$no_rows<-rep(1, nrow(f75))
-f75b<- aggregate(no_rows ~ Site_ID, f75, length)
-head(f75b)
-
-#because when calculating thresholds, sites with 6 plants can score up to 6, but sites with 4 sites can score max = 4 we corrected for this doing % above threshold, and no number. 
-#calculate total number of species per site
-f4$no_rows<-rep(1, nrow(f4))
-f4d<- aggregate(no_rows ~ Site_ID, f4, length)
-head(f4d)
-
-f75b$total.plant.numb<-f4d$no_rows[match(f75b$Site_ID, f4d$Site_ID)]
-
-#remove sites that only have one plant sps, Elpinar and Villamanriqueeste
-f75c<-subset(f75b, f75b$total.plant.numb>1)
-
-#calculate equity as proportion of species with >50% of fruitset compared to total number of sps
-f75c$equity<-f75c$no_rows/f75c$total.plant.numb
-
-#join this with fruitset data used previously
-
-f75c$nodf.song<-out.site$nodf.song[match(f75c$Site_ID, out.site$Site_id)]
-f75c$functional.comp.poll<-out.site$functional.comp.poll[match(f75c$Site_ID, out.site$Site_id)]
-f75c$species.poll<-out.site$species.poll[match(f75c$Site_ID, out.site$Site_id)]
-f75c$tot.visits<-f.agg$tot.visits[match(f75c$Site_ID, f.agg$Site_ID)]
-
-f75c$species.pl<-out.site$species.pl[match(f75c$Site_ID, out.site$Site_id)]
-#scale all variables
-
-f75c$nodf.song.sc <- scale(f75c$nodf.song, center = T, scale = T)
-f75c$functional.comp.poll.sc <- scale(f75c$functional.comp.poll, center = T, scale = T)
-f75c$species.poll.sc <- scale(f75c$species.poll, center = T, scale = T)
-f75c$tot.visits.sc <- scale(f75c$tot.visits, center = T, scale = T)
-
-f75c$species.pl.sc <- scale(f75c$species.pl, center = T, scale = T)
+```
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
+
+#EQUITY SPECIES WITHIN COMMUNITIES 75% threshold
+#using raw values of mean fruitset for each species at each site
+#dataset f.ag
+#number of species per site tableS1
+
+#calculate number of sps per site producing more than 0.5 in fruitset
+
+highprod75<-subset(f.ag, f.ag$mean.fruitset>0.75)
+highprod75.sps<-ddply(highprod75, "Site_ID", summarise, 
+                   high.sps = length(Plant.sp))
+
+#equity as proportion of high producing compared to total
+highprod75.sps$tot.sps<-tableS1$tot.sps[match(highprod75.sps$Site_ID, tableS1$Site_ID)]
+highprod75.sps$equity<-highprod75.sps$high.sps/highprod75.sps$tot.sps
+
+highprod75.sps$nodf.song.sc<-f.agg$nodf.song.sc[match(highprod75.sps$Site_ID, f.agg$Site_ID)]
+highprod75.sps$functional.comp.poll.sc<-f.agg$functional.comp.poll.sc[match(highprod75.sps$Site_ID, f.agg$Site_ID)]
+highprod75.sps$species.poll.sc<-f.agg$species.poll.sc[match(highprod75.sps$Site_ID, f.agg$Site_ID)]
+highprod75.sps$tot.visits.sc<-f.agg$tot.visits.sc[match(highprod75.sps$Site_ID, f.agg$Site_ID)]
+```
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
 
 #fit two models
- m1.eq.75<-glm(equity ~  species.poll.sc + tot.visits.sc , family="binomial", data=f75c)
-
- summary(m1.eq.75)
-
-m2.eq.75<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc , family="binomial", data=f75c)
-
- summary(m2.eq.75)
+ m1.eq.comm75<-glm(equity ~  species.poll.sc + tot.visits.sc , family="binomial", data=highprod75.sps)
+
+ summary(m1.eq.comm75)
+
+ m2.eq.comm75<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc , family="binomial", data=highprod75.sps)
+summary(m2.eq.comm75)
 
@@
 
-AICtab(m1.eq.75, m2.eq.75) #m1 better model
-
-# #test for problems in residuals
-# res<-simulateResiduals(m1.eq.75)
+AICtab(m1.eq.comm75, m2.eq.comm75) #m1 is best no variables significant
+
+tableS9<-round(summary(m1.eq.comm75)$coef[,1:3], digits=2)
+rownames(tableS9)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")
+
+#partial residual plots
+
+#test for problems in residuals
+# res<-simulateResiduals(m1.eq.comm)
 # plot(res, rank = TRUE)
 
-#Repeat with 25% threshold
-
-f25<-subset(f.ag.pr, f.ag.pr$mean.fruitset>0.25)
-
-#for each site here is the number of sps whose fruitset exceeds 25% of maximum fruitset observed in the whole study area
-f25$no_rows<-rep(1, nrow(f25))
-f25b<- aggregate(no_rows ~ Site_ID, f25, length)
-head(f25b)
-
-#because when calculating thresholds, sites with 6 plants can score up to 6, but sites with 4 sites can score max = 4 we corrected for this doing % above threshold, and no number. 
-#calculate total number of species per site
-f4$no_rows<-rep(1, nrow(f4))
-f4d<- aggregate(no_rows ~ Site_ID, f4, length)
-head(f4d)
-
-f25b$total.plant.numb<-f4d$no_rows[match(f25b$Site_ID, f4d$Site_ID)]
-
-#remove sites that only have one plant sps, Elpinar and Villamanriqueeste
-f25c<-subset(f25b, f25b$total.plant.numb>1)
-
-#calculate equity as proportion of species with >50% of fruitset compared to total number of sps
-f25c$equity<-f25c$no_rows/f25c$total.plant.numb
-
-#join this with fruitset data used previously
-
-f25c$nodf.song<-out.site$nodf.song[match(f25c$Site_ID, out.site$Site_id)]
-f25c$functional.comp.poll<-out.site$functional.comp.poll[match(f25c$Site_ID, out.site$Site_id)]
-f25c$species.poll<-out.site$species.poll[match(f25c$Site_ID, out.site$Site_id)]
-f25c$tot.visits<-f.agg$tot.visits[match(f25c$Site_ID, f.agg$Site_ID)]
-
-f25c$species.pl<-out.site$species.pl[match(f25c$Site_ID, out.site$Site_id)]
-#scale all variables
-
-f25c$nodf.song.sc <- scale(f25c$nodf.song, center = T, scale = T)
-f25c$functional.comp.poll.sc <- scale(f25c$functional.comp.poll, center = T, scale = T)
-f25c$species.poll.sc <- scale(f25c$species.poll, center = T, scale = T)
-f25c$tot.visits.sc <- scale(f25c$tot.visits, center = T, scale = T)
-
-f25c$species.pl.sc <- scale(f25c$species.pl, center = T, scale = T)
+pred.eq<-summary(m1.eq.comm)$coef[1] + (summary(m1.eq.comm)$coef[2]*highprod75.sps$species.poll.sc) + (summary(m1.eq.comm)$coef[3]*mean(highprod75.sps$tot.visits.sc))
+
+res.eq<-pred.eq-highprod75.sps$equity
+res.eq.retro<-exp(res.eq)/(1+exp(res.eq))
+
+Figure6 <- ggplot(highprod75.sps,  aes(x=species.poll.sc, y= res.eq.retro)) +    
+        geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
+  stat_smooth(method = 'lm', size=1, se=TRUE, color = "black", alpha=0.4) +    
+        xlab("Pollinator sps diversity") +      
+        ylab("Equity in fruitset") + theme_bw()  + #theme (legend.position= "none") +
+        theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
+
+```
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
+
+#EQUITY SPECIES WITHIN COMMUNITIES 25% threshold
+#using raw values of mean fruitset for each species at each site
+#dataset f.ag
+#number of species per site tableS1
+
+#calculate number of sps per site producing more than 0.5 in fruitset
+
+highprod25<-subset(f.ag, f.ag$mean.fruitset>0.25)
+highprod25.sps<-ddply(highprod25, "Site_ID", summarise, 
+                   high.sps = length(Plant.sp))
+
+#equity as proportion of high producing compared to total
+highprod25.sps$tot.sps<-tableS1$tot.sps[match(highprod25.sps$Site_ID, tableS1$Site_ID)]
+highprod25.sps$equity<-highprod25.sps$high.sps/highprod25.sps$tot.sps
+
+highprod25.sps$nodf.song.sc<-f.agg$nodf.song.sc[match(highprod25.sps$Site_ID, f.agg$Site_ID)]
+highprod25.sps$functional.comp.poll.sc<-f.agg$functional.comp.poll.sc[match(highprod25.sps$Site_ID, f.agg$Site_ID)]
+highprod25.sps$species.poll.sc<-f.agg$species.poll.sc[match(highprod25.sps$Site_ID, f.agg$Site_ID)]
+highprod25.sps$tot.visits.sc<-f.agg$tot.visits.sc[match(highprod25.sps$Site_ID, f.agg$Site_ID)]
+```
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
 
 #fit two models
- m1.eq.25<-glm(equity ~  species.poll.sc + tot.visits.sc , family="binomial", data=f25c)
-
- summary(m1.eq.25)
-
-m2.eq.25<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc , family="binomial", data=f25c)
-
- summary(m2.eq.25)
+ m1.eq.comm25<-glm(equity ~  species.poll.sc + tot.visits.sc , family="binomial", data=highprod25.sps)
+
+ summary(m1.eq.comm25)
+
+ m2.eq.comm25<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc , family="binomial", data=highprod25.sps)
+summary(m2.eq.comm25)
 
@@
 
-AICtab(m1.eq.25, m2.eq.25) #m1 is better.
-
-# #test for problems in residuals
-# res<-simulateResiduals(m1.eq.25)
-# plot(res, rank = TRUE)
-
-```
-
-###Simulating the effect of community structure as sample size increases
+AICtab(m1.eq.comm25, m2.eq.comm25) #m1 is best no variables significant
+
+tableS10<-round(summary(m1.eq.comm25)$coef[,1:3], digits=2)
+rownames(tableS10)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")
+
+```
+
+_Simulating the effect of community structure as sample size increases_
 
@@
 
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
-
-library(vegan)
-library(dplyr)
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide', fig.show = 'hide'}
 
@@
 
-#DISCUSSION
+**Discussion**
 
@@
 Our results show that different aspects of community structure affect different dimensions of functioning.
-In particular, we find that the centrality of a species within a community, which measures the number of connections it received from other species in the community, had a positive effect for its fruitset.
+In particular, we find that the centrality of a species within a community, which measures the number of connections it receives from other species in the community, has a positive effect for its fruitset.
 At the community level, however, we find that niche complementarity between pollinators, a measure of the overlap in the niches of different species in terms of plant coverage, has an important effect for average fruitset.
 
-One of the first conclusions we can extract from the fact that in most cases both of the models we considered (i.e., the simple model based on visitation metrics and the more complex one including community structure metrics) were equally good, is that for simple predictive purposes, simple visitation metrics, such as pollinator diversity, might be enough [@Garibaldi2013; @Garibaldi2015 estos???][cite Garibaldi papers using them]().
-Yet, a mechanistic understanding of the underlying processes requires that we take into account measures of community structure, and in particular those related to the overlap in the niches of interacting species.
-
-Consistent with previous studies conducted within experimental [@Fontaine2005; @Frund2013] and natural [@Valdovinos2016] communities, we find that niche complementarity is very important in determining differences in reproductive outputs.
-Similar to these previous studies, we find that communities where there is less overlap in the niches occupied by pollinator species had greater values of reproductive success, both greater fruitset values and larger numbers of seeds per fruit.
-Indeed, this reflects the fact that reproductive success in plant species requires of the delivery of conspecific pollen and thus of a certain degree of specialization amongst pollinator species on a particular plant resource in order to avoid the negative effects of inter-specific pollen deposition (e.g., pollen loss [@Flanagan2009] or interference with conspecific pollen [@Morales2008]).
+One of the first conclusions we can extract from the fact that in most cases both of the models we considered (i.e., the simple model based on visitation metrics and the more complex one including community structure metrics) were equally good, is that for predictive purposes, simple visitation metrics, such as pollinator diversity, might be enough [@Garibaldi2013; @Garibaldi2015].
+Yet, a mechanistic understanding of the underlying processes driving these observed patterns, requires that we take into account measures of community structure, and, in particular, those related to the overlap in the niches of interacting species.
+
+Consistent with previous experimental [@Fontaine2005; @Frund2013] theoretical, and empirical studies [@Valdovinos2016], we find that niche complementarity is key in determining differences in reproductive outputs.
+Indeed, we find that communities where there is less overlap in the niches occupied by pollinator species had greater values of reproductive success, both greater fruitset values and larger numbers of seeds per fruit.
+This therefore reflects the fact that reproductive success in plant species requires of the delivery of conspecific pollen and thus of a certain degree of specialization amongst pollinator species on a particular plant resource in order to avoid the negative effects of inter-specific pollen deposition (e.g., pollen loss [@Flanagan2009] or interference with conspecific pollen [@Morales2008]).
 
@@
 In the case of equity we did not find a significant effect of either simple visitation or community structure metrics.
-However, the results of our simulation on the importance of community structure as the number of plant species considered increases shows us that this effect dramatically increases when more than four plant species are considered.
-This implies that if we were able to measure reproductive success for all the plant species in all the communities (which we cannot do due to constraints on sampling effort), we might find that the effects of community structure might be even more prevalent.
-
-In summary, our findings show that the analysis of natural communities of interacting species using network analysis not only represents an ideal way of visualizing and grasping the complexity present within these communities, but also represents a manner of mechanisitically understanding differences observed across individuals and/or species.
+However, the results of our simulation on the importance of community structure as the number of plant species considered increases, shows us that this effect dramatically increases when more than four plant species are considered.
+This implies that if we were able to measure reproductive success for all the plant species in all the communities (which is not feasible given constraints in sampling effort), we might find that the effects of community structure on equity might be even more prevalent.
+
+In summary, our findings show that the analysis of natural communities of interacting species using network analysis not only represents an ideal way of visualizing and grasping the complexity present within these communities, but also represents a manner of mechanisitically understanding differences observed across the reproductive success of individuals and/or species.
 
@@
 
-##References
+**Acknowledgements**
+
+The authors would like to thank Oscar Aguado, Javier ??
+and XX for help in identifying pollinator species.
+In addition, XX.
+AM received funding from a Juan de la Cierva and Ikerbasque fellowships.
+IB acknowledges funding from Career integration grant????
+
+\nextpage
+
+##Tables
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+# extract coefficients and p-values for m2 and present them in paper
+# coefs.m2 <- data.frame(coef(summary(m2)))
+# Table1<-round(coefs.m2[,1:3],digits=2)
+# rownames(Table1)<-c("(Intercept)", "Normalized degree", "Total number of visits", "Weighted closeness", "Niche overlap")
+
+kable(Table1, caption = "Table 1. Results of GLMM showing effect of simple visitation and community structure metrics on species-level fruitset based on best model selected.")
+```
+\newpage
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+# # extract coefficients and p-values for m1 and present them in paper
+# coefs.m2.seed <- data.frame(coef(summary(m2.seed)))
+# # use normal distribution to approximate p-value
+# #coefs.m2.seed$p.z <- 2 * (1 - pnorm(abs(coefs.m2.seed$t.value)))
+
+# Table2<-round(coefs.m2.seed,digits=2)
+# rownames(Table2)<-c("(Intercept)", "Normalized degree", "Total number of visits", "Weighted closeness", "Niche overlap")
+
+kable(Table2, caption = "Table 2. Results of GLMM showing effect of simple visitation and community structure metrics on species-level number of seeds/fruit based on best model selected.")
+```
+\newpage
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+# #table with results for paper
+# Table3<-round(summary(m2.fruit.net)$coefficients$cond[,1:3], digits=2)
+# rownames(Table3)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Nestedness", "Niche complementarity")
+
+kable(Table3, caption = "Table 3. Results of GLM showing effect of simple visitation and community structure metrics on community-level average fruitset based on best model selected.")
+
+```
+\newpage
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+# #save table with results for paper
+# Table4<-round(summary(m2.seed.net)$coefficients[,1:3], digits=2)
+# rownames(Table4)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Nestedness", "Niche complementarity")
+
+kable(Table4, caption = "Table 4.
+Results of GLM showing effect of simple visitation and community structure metrics on community-level average number of seeds per fruit based on best model selected.")
+```
+\newpage
+
+**Figure legends**
+
+**Figure 1.** Map showing location of 16 study sites, green colors indicate different elevations. Inset shows location of study area within SW Spain.
+
+**Figure 2**.
+Partial residual plots showing the effect of A) pollinator species diversity (approximated using normalized degree) and B) species centrality on fruitset for each of the plant species considered.
+Dots represent each of the individuals sampled for each species within each site.
+
+**Figure 3.** Partial residual plot showing the effect of average niche overlap between plant species on the average number of seeds per fruit for each of the plant species considered.
+Dots represent each of the individuals sampled for each species within each site.
+
+**Figure 4.** Partial residual plots showing the effect of A) pollinator species diversity, B) total number of visits received and C) niche complementarity between pollinator species on community-level average fruitset.
+Dots represent average vaues of fruitset at the level of the community for all plant species considered (N=16 sites).
+
+**Figure 5.** Partial residual plots showing the effect of A) the total number of pollinator visits received at the community level and B) niche complementarity between pollinator species on the scaled average number of seeds per fruit at the community level.
+Dots represent average vaues of previously scaled values of the number of seeds per fruit at the level of the community for all plant species considered (N=16 sites).
+
+**Figure 6.** Partial residual plots showing the effect of pollinator species diversity on equity in reproductive success across species within a community (75% threshold).
+Dots represent values for each site (N=16 sites).
+
+\newpage
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=7, fig.width=8}
+
+#FIGURE 1
+
+mydf <- read.csv("site_coordinates.csv")
+
+# Making a data frame *spatial*
+library(devtools)
+# install_github("edzer/sfr")
+# install_github("edzer/rgdal2")
+library(rgdal)
+library(sf)
+library(sp)
+library(raster)
+library(tmap)
+library(dplyr)
+library(spData)
+library(leaflet)
+library(ggplot2)
+library(grid)
+
+#devtools::install_github("Nowosad/spDataLarge")
+library(spDataLarge)
+
+occs <- st_as_sf(mydf, coords = c("longitude", "latitude"))
+
+#setting projection
+st_crs(occs) <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +init=epsg:3042"
+
+data(world)
+sp<-subset(world, world$iso_a2==c("ES", "PT"))
+
+#extent(occs)  #to calculate xmin, xmax, ymin, ymax
+doñana_region = st_bbox(c(xmin = -7.000000, xmax = -6.00000,
+                      ymin = 37.10000, ymax = 37.51200),
+                    crs = st_crs(sp)) %>% 
+  st_as_sfc()
+
+sp_map = tm_shape(sp) + tm_polygons() +
+  tm_shape(occs) + tm_symbols(shape = 16, col = "black", size = 0.03) + 
+ tm_shape(doñana_region) + tm_borders(lwd = 3) #map of all spain
+
+# Get elevation data from the internet 
+elev <- getData("alt", country = "Spain")
+
+# Crop raster to desired extent
+ele <- crop(elev, c(-7.000000, -6.00000, 37.10000, 37.51200))
+
+sp_points_map = tm_shape(ele, bbox = doñana_region) +
+ tm_raster(legend.show = TRUE, title = "Elevation (m)") +
+  tm_shape(occs) + tm_symbols(shape = 24, col = "darkgrey", size = 0.5) +
+  tm_scale_bar(position = c("left", "bottom"), size=0.75)
+
+sp_points_map
+print(sp_map, vp = viewport(0.8335, 0.6812, width = 0.35, height = 0.35))
+
+```
+**Figure 1**
+
+\newpage
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=8}
+
+#FIGURE 2
+Figure2 <- plot_grid( prow, legend_b, ncol = 1, rel_heights = c(1, .2))
+Figure2
+```
+**Figure 2**
+
+\newpage
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=6, fig.width=8}
+
+#FIGURE 3
+Figure3
+```
+**Figure 3**
+
+\newpage
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=3, fig.width=10}
+
+#FIGURE 4
+Figure4
+```
+**Figure 4**
+
+\newpage
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=7}
+
+#FIGURE 5
+Figure5
+```
+**Figure 5**
+
+\newpage
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=3, fig.width=4}
+
+#FIGURE 5
+Figure6
+```
+**Figure 6**
+
+\newpage
+
+#Supplementary material
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=13, fig.width=7}
+
+#######FIG S1 SAMPLING COMPLETENESS
+
+grid.newpage()
+grid.draw(rbind(ggplotGrob(poll), ggplotGrob(plant), ggplotGrob(link), size = "last"))
+
+```
+
+**Figure S1.** Accumulation curves of pollinator, plant and plant-pollinator link richness with increasing sampling effort up to 100% sample coverage.
+Solid lines and points indicate observed richness while dashed lines show expected richness at increasing sample size, (i.e., extrapolated).
+
+\newpage
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=3, fig.width=4}
+
+crPlots(m1.fruitw.net, smooth=FALSE, terms = ~  species.poll.sc, main = "", ylab = "Mean fruit weight", col.lines= "black", pch=19, col= "black", bg = "darkgrey", cex=2, cex.axis=1.2, cex.lab=1.5, 
+        xlab = "Pollinator species diversity") #end of paper
+```
+
+**Figure S2.** Partial residual plots showing the effect of the total number of pollinator visits received at the community level on the average fruit weight.
+Dots represent average vaues at the level of the community for all plant species considered (N=16 sites).
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=8}
+crPlots(m1.seedw.net, smooth=FALSE,  main = "", ylab = "Mean seed weight", col.lines= "black", pch=19, col= "black", bg = "darkgrey", cex=2, cex.axis=1.2, cex.lab=1.5)
+```
+
+**Figure S3.** Partial residual plots showing the effect of the the diversity of pollinators and the total number of pollinator visits received at the community level on the average seed weight.
+Dots represent average vaues at the level of the community for all plant species considered (N=16 sites).
+
+\newpage
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE}
+
+#calculate number of plant species per site, number of individuals per plant species and number of fruits per ind surveyed for repr succ
+
+f.inds<-ddply(f, c("Site_ID", "Plant.sp"), summarise, 
+                   tot.inds = length(Plant.sp)) #number of individuals per plant sps
+
+tableS1<-ddply(f.inds, c("Site_ID"), summarise, 
+                   tot.sps = length(Site_ID)) #number of plant sps per site
+
+colnames(tableS1)<-c("Site", "Number of plant species")
+
+kable(tableS1, caption = "Table S1. Number of species sampled at each site.")
+
+tableS2 <- aggregate(Plant.ID ~ Site_ID + Plant.sp, data = f2, FUN = function(x){NROW(x)})
+
+colnames(tableS2)<-c("Site", "Plant species", "Number of individuals")
+
+kable(tableS2, caption = "Table S2. Number of individuals per plant species sampled at each site.")
+
+tableS3<-ddply(s, c("Site_ID", "Plant.sp"), summarise, 
+                   tot.fruits = length(Plant.ID)) #number of fruits per individual
+
+colnames(tableS3)<- c("Site", "Plant species", "Number of fruits")
+
+kable(tableS3, caption = "Table S3. Number of fruits per plant species sampled at each site.")
+```
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+
+tableS4<-round(summary(m1.seed.w)$coefficients$cond[,1:3], digits=2)
+rownames(tableS4)<-c("(Intercept)", "Normalized degree", "Total number of visits")
+kable(tableS4, caption="Table S4. Results of GLMM showing effect of simple visitation metrics on species-level average seed weight based on best model selected.")
+
+tableS5<-round(summary(m1.fruit.w)$coefficients$cond[,1:3], digits=2)
+rownames(tableS5)<-c("(Intercept)", "Normalized degree", "Total number of visits")
+kable(tableS5, caption="Table S5. Results of GLMM showing effect of simple visitation metrics on species-level average fruit weight based on best model selected.")
+```
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+
+tableS6<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)
+rownames(tableS6)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")
+
+kable(tableS6, caption="Table S6. Results of GLM showing effect of simple visitation metrics on community-level average fruit weight based on best model selected.")
+```
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+#save table with results for paper
+tableS7<-round(summary(m1.seedw.net)$coef[,1:3], digits=2)
+rownames(tableS7) <-c("(Intercept)", "Pollinator species diversity", "Total number of visits")
+
+kable(tableS7, caption="Table S7. Results of GLM showing effect of simple visitation metrics on community-level average seed weight based on best model selected.")
+```
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+
+kable(tableS8, caption="Table S8.
+Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a community based on best model selected (50% threshold).")
+
+kable(tableS9, caption="Table S9.
+Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a community based on best model selected (75% threshold).")
+
+kable(tableS10, caption="Table S10.
+Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a community based on best model selected (25% threshold).")
+```
+
+\newpage
+
+**References**

### 2019-04-22 paper_round2.Rmd
Comments!

@@
 
-Ainhoa Magrach, Francisco de Paula Molina, Ignasi Bartomeus
-
-Short running title: Network structure effects on reproductive success
+Ainhoa Magrach, Francisco de Paula [or Curro, ask him]() Molina, Ignasi Bartomeus
+
+Short running title: Network structure effects on ecosystem functioning
 
@@
 Yet species do not interact in isolation, they are embedded within larger networks whose structure can affect pollinator functional roles and, ultimately, the pollination services they deliver to plants.
-Here, we present one of the first efforts linking pollinator visitation to plant reproduction from a community-wide perspective using a well-replicated dataset encompassing 16 well-resolved networks and data on reproductive success for 19 plant species from Mediterranean shrub ecosystems.
+Here, we present one of the first efforts linking pollinator visitation to plant reproduction from a community-wide perspective using a well-replicated dataset encompassing 16 well-resolved plant-pollinator networks and data on reproductive success for 19 plant species from Mediterranean shrub ecosystems.
 We find that, for prediction purposes, information on simple visitation metrics is sufficient.
@@
 Pollinators provide key services to plants by facilitating pollen flow between individuals.
-The recent declining trends found for some pollinator species in some regions of the planet ([@Potts2010], although see [@I.2019] reflecting general lack of knowledge at the global level), have led many researchers to focus on the functional impacts of these changes in pollinator diversity, with a major focus being placed on the consequences for plant reproductive success [@Biesmeijer2006].
-
-Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012a; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain differences found  across different plant individuals.
-Some have gone a step further by including information on the efficiency of these visits, thus adding a measure of quality to the pollination services [@Willcox2017].
+The recent declining trends found for some pollinator species in some regions of the planet ([@Potts2010], [@I.2019]) have led many researchers to focus on the functional impacts of these changes in pollinator diversity, with a major focus being placed on the consequences for plant reproductive success [@Biesmeijer2006].
+
+Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012a; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain the differences observed across different plant individuals.
+Some have gone a step further by including information on the efficiency of these visits, thus adding a measure of quality to the pollination services [@Willcox2017](I wonder if the preceeding sentence is necesary, given our paper is not about efficiency).
 Contrastingly, community-level analyses remain scarce [@Bennett2018].
@@
 
-Indeed, theoretical research has long suggested that the structure of a community has an effect for ecosystem functioning (reviewed in [@Thompson2012]).
+Indeed, theoretical research has long suggested that the structure of multitrophic communities has an effect for ecosystem functioning (reviewed in [@Thompson2012]).
 This line of research, primarliy driven by food-web studies, has greatly advanced theory, but these ideas have not yet been tested using empirical data (but see [@Poisot2013]).
@@
 In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success, and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success.
-In addition, we evaluate whether community structure helps us explain differences in equity in reproductive success across individuals within a species and species within a community as a measure of evenness and stability in the pollination service.
+In addition to average values, we also evaluate whether community structure helps us explain differences in equity in reproductive success across individuals within a species and species within a community as a measure of evenness and stability in the pollination service.
 
@@
 Along each transect, we identified all plant species and recorded all the flower visitors that legitimately visited them during each 30-min period.
-In addition, we conducted focal observations of XX specific plant individuals during XX [????]().
-We also recorded other rare interactions observed out of the basic surveys [explicar un poco mejor]().
+In addition, in each round we conducted 3 minutes focal observations of 3 individuals belonging to the 19 most common species totalling X census [give mean per site?](Curro).
+In addition, unrecorded interactions between plant and pollinators during the sampling were recorded when observed out of the timed periods, as this dificult to observe interactions may be important for defining the network structure.
 Floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FdPM with the aid of experts in the different taxonomic groups (see acknowledgements).
 All surveys were done under similar weather conditions, avoiding windy or rainy days.
+[maybe say we tried excluding singletons and analysis do not change?]()
 
@@
 At the species level, we focused on attributes defining the position of a focal plant species within the larger community.
-As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap between a focal plant species and other plant species in the community, which covers the potential indirect interactions between different plant species through shared resources (in this case pollinators), and (ii) centrality, which depicts the importance of the plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness.
+As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap between a focal plant species and other plant species in the community, which covers the potential indirect interactions between different plant species through shared resources (in this case pollinators), and (ii) centrality [is this calculated onto the unipartite plant network?
+If so explain](), which depicts the [importance](importance can mean anything, can you be more especific?) of the plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness.
 
@@
 In this case we focused on (i) nestedness and (ii) niche complementarity.
+
 Nestedness is the property by which specialists interact with a subset of the species that generalists interact with [@Bascompte2003].
@@
 
-Nevertheless, plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence (reviewed in [@Brosi2016]).
-Yet at present we do not know how the interplay between redundancy and complementarity in species roles determines reproductive success.
+Niche complementariety metrics are important because plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence (reviewed in [@Brosi2016]).
 To calculate niche complmentarity we used a community-level measure defined as the total branch length of a functional dendrogram based on qualitative differences in visitor assemblages between plants [@Devoto2012; @Petchey2007a].
 All network metrics were calculated using package bipartite [@Dormann2009].
+
+[Yet at present we do not know how the interplay between redundancy and complementarity in species roles determines reproductive success.](I don't see where to place this sentence.
+I like it, but was breaking the flow.
+Discusion?)
 
@@
 The diversity of pollinator species visiting a focal plant was approximated using the plant´s normalised degree, i.e., the number of links with different pollinator species a plant has, scaled by the number of possible partners [@Dormann2009].
-Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the morisita index [@Zhang2016].
+Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the Morisita index [@Zhang2016].
 As a measure of centrality we used weighted closeness centrality which describes centrality through the path lengths of a species to other species in the network using a weighted representation of the network [@Dormann2009].
@@
 Yet, what will determine the persistence of a diverse plant community, is the presence of some sort of “equity” or evenness in reproductive success across the whole community.
-We therefore calculated a measure of equity in reproductive success at the community level as the proportion of species within a community with normalized average fruitset values above 0.5.
+We therefore calculated a measure of equity in reproductive success at the community level as the proportion of species within a community with normalized [explain how, normalizations usually make 0 centred values, and values above 0.5 makes no sense]() average fruitset values above 0.5.
 We repeated this using 0.25 and 0.75 thresholds.
@@
 
-_Simulating the effect of community structure as sample size increases_
+_Simulating the effect of community structure as sample size increases_ [no se si le pondria titulo aparte o no, quizas no hace falta, yo o uniria a estatistical analysis]()
 
@@
 Then, we tested the overall relationship between equity in reproductive success and both community-level network metrics we measured: nestedness and functional complementarity within our simulated communities.
-To this end, for each species number level considered, we randomly selected one of the generated equity values across each of the 16 communities, regress this against our netrok level predictors and extracted the model estimates.
+To this end, for each species number level considered, we randomly selected one of the generated equity values across each of the 16 communities, regress this against our netrwock level predictors and extracted the model estimates.
 We averaged all estimates from 1,000 simulated combinations per number of plants considered.
@@
 Our values of sampling completeness are slightly smaller in the case of pollinators probably as a consequence of the great diversity found in the Mediterranean region and within our study area in particular, a hotspot of insect diversity [@Nieto2014a].
+[well, and the fact that we added "outs", which are singletons, a key piece used by Chao estimators!, SHould we mention this?]()
 
@@
 2).
+[to what extent ND is a network level metric i.e.
+not a simple metric like number of links¿?
+I am playing devils advocate here.]()
 
@@
 The existence of a relationship between community structure and ecosystem function has been long hypothesized, yet, the specific mechanisms by which structure influences function remain elusive [@Thompson2012].
-Our results show that different aspects of community structure affect different dimensions of functioning.
+Our results show that different aspects of community structure affect different dimensions of community functioning.
 In particular, we find that the centrality of a species within a community, which measures the number of connections it receives from other species in the community, has a positive effect for its fruitset.
@@
 
-Consistent with previous experimental [@Fontaine2005; @Frund2013] theoretical, and empirical studies [@Valdovinos2016], we find that niche complementarity is key in determining differences in reproductive outputs.
+Consistent with previous experimental [@Fontaine2005; @Frund2013], theoretical [ref: Gravel probably has something](), and empirical studies [@Valdovinos2016], we find that niche complementarity is key in determining differences in reproductive outputs.
 Indeed, we find that communities where there is less overlap in the niches occupied by pollinator species had greater values of reproductive success, both greater fruitset values and larger numbers of seeds per fruit.
@@
 Community-level plant reproductive success, measured as average fruit or seed set across all the species considered [@Frund2013], is an important part of the functions delivered by pollinators to plants.
-However, these average values might be masking a great deal of variability amongst species, and thus a nuanced view of the effect of pollinators on whole-plant ensembles is that which we include in our analyses: the effect of pollinators on equity in reproductive succes across plant species.
+However, these average values might be masking a great deal of variability amongst species, and thus a nuanced view of the effect of pollinators on whole-plant ensembles is needed.
+This can be captured by the effect of pollinators on equity in reproductive succes across plant species.
 This aspect ensures that reproductive success is equally distributed amongst a larger number of species, thus contributing to the maintenance of a greater species diversity in natural populations.
-Indeed, we know that plant species diversity within a community is largely driven by different types of direct and indirect interactions including those amongst plant species (e.g., resource competition [@Goldberg1992] or facilitation [@Bruno2003]), as well as those defining antagonistic (e.g., involving pathogens [@Bagchi2010], or mutualistic interactions (e.g, pollinators [@Benadi2013]).
+Indeed, we know that plant species diversity within a community is largely driven by different types of direct and indirect interactions including those amongst plant species (e.g., resource competition [@Goldberg1992] or facilitation [@Bruno2003]), as well as those defining antagonistic (e.g., involving pathogens [@Bagchi2010], or mutualistic interactions (e.g, pollinators [@Benadi2013, Lanuza Ecology Letters!]()).
 However, equitability in reproductive success across species is seldom taken into account, despite its importance in maintaining genetic diversity and ensuring the resilience of populations to further change (REF).
@@
 AM received funding from a Juan de la Cierva and Ikerbasque fellowships.
-IB acknowledges funding from Career integration grant????
+IB acknowledges funding from MSC-PCIG14-GA-2013-631653 BeeFun Project.
 

### 2019-04-23 paper_round2.Rmd
slight change in intro

--- 2019-03-27 paper_round2.Rmd
@@
 In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success, and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success.
-In addition, we evaluate whether community structure helps us explain differences in equity in reproductive success across individuals within a species and species within a community as a measure of evenness and stability in the pollination service.
+In addition, we evaluate whether community structure helps us explain differences in equity in reproductive success across species within a community as a measure of evenness and stability in the pollination service.
 

### 2019-04-26 paper_round2.Rmd
minor changes to script and inclusion of word documents: paper, cover letter and suppl mat

--- 2019-04-22 paper_round2.Rmd
@@
 
-Ainhoa Magrach, Francisco de Paula [or Curro, ask him]() Molina, Ignasi Bartomeus
+Ainhoa Magrach^1^, Francisco P. Molina^2^, Ignasi Bartomeus^2^
 
@@
 
-Keywords: nestedness, niche complementary, fruitset, pollination, plant-pollinator interaction
+^1^Basque Centre for Climate Change-BC3, Edif. Sede 1, 1º, Parque Científico UPV-EHU, Barrio Sarriena s/n, 48940, Leioa, Spain
+
+^2Estación Biológica de Doñana (EBD-CSIC), Avda. Américo Vespucio 26, Isla de la Cartuja, 41092, Sevilla, Spain
 
@@
 
-Words in Abstract: 147 words
+Words in Abstract: 148 words
 
@@
 
-Words in text boxes:
-
-Number of references:
+Number of references: 45
 
@@
 Corresponding author: ainhoa.magrach@bc3research.org, nacho.bartomeus@gmail.com
+
+Keywords: nestedness, niche complementary, fruitset, pollination, plant-pollinator interactions
 
@@
 Pollinators provide key services to plants by facilitating pollen flow between individuals.
-The recent declining trends found for some pollinator species in some regions of the planet ([@Potts2010], [@I.2019]) have led many researchers to focus on the functional impacts of these changes in pollinator diversity, with a major focus being placed on the consequences for plant reproductive success [@Biesmeijer2006].
+The recent declining trends found for some pollinator species in some regions of the planet ([@Potts2010; @I.2019]) have led many researchers to focus on the functional impacts of these changes in pollinator diversity, with a major focus being placed on the consequences for plant reproductive success [@Biesmeijer2006].
 
   Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012a; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain the differences observed across different plant individuals.
-Some have gone a step further by including information on the efficiency of these visits, thus adding a measure of quality to the pollination services [@Willcox2017](I wonder if the preceeding sentence is necesary, given our paper is not about efficiency).
 Contrastingly, community-level analyses remain scarce [@Bennett2018].
@@
 
-The few pollination studies that have analysed the effects of changing pollinator diversity for reproductive success at the community level, have done so using mainly experimental setups.
+  The few pollination studies that have analysed the effects of changing pollinator diversity for reproductive success at the community level have done so using mainly experimental setups.
 As an example, a study that experimentally recreated a plant community with 9 plant species and differing levels of pollinator diversity across different enclosures, found that not only pollinator species diversity had an effect for average reproductive success, but also they found that community structure had an important effect [@Frund2013].
 In particular, these authors found that niche complementarity between pollinators, in terms of plant species and temperature coverage (a measure of the overlap in the use of plant resources and optimum temperature activity) had a positive effect for average seed set at the community level [@Frund2013].
-This provides added information on the effects of biodiversity for ecosystem functioning, suggesting that not only the diversity of species present but also the diversity of roles and ways in which a community is structured are determinant factors.
+This provides added information on the effects of biodiversity for ecosystem functioning, suggesting that not only the diversity of species present, but also the diversity of roles and ways in which a community is structured, are determinant factors.
 
@@
 We are now at a point in which there is considerable understanding on the attributes characterizing mutualistic interaction networks [@Bascompte2007b] and we have a substantial understanding of how these attributes vary along different types of gradients [@Pellissier2017; @Tylianakis2016].
-Especially, in the case of pollination, we have ample knowledge on the attributes that shape these mutualistic interactions at the community level, such as a prevalence of nested structures [Bascompte et al 2013 PNAS] or the presence of asymmetric specialization as a pervasive feature [@Vazquez2004].
-However, how the structure shaping this network of interactions affects key ecosystem functions such as plant reproduction remains untested [@Winfree2013].
+Especially, in the case of pollination, we have ample knowledge on the attributes that shape these mutualistic interactions at the community level, such as a prevalence of nested structures [@Bascompte2003] or the presence of asymmetric specialization as a pervasive feature [@Vazquez2004].
+However, the pathways by which the structure of these networks of interactions affect key ecosystem functions such as plant reproduction remain to be understood [@Winfree2013].
 The time is thus ripe to use this knowledge to explore relationships between community structure and ecosystem functioning, with special emphasis being placed on the underlying mechanisms that drive these relationships.
@@
 To this end, we use a well-replicated dataset encompassing 16 well-resolved plant-pollinator interaction networks coupled with data on the reproductive success of 19 plant species recorded at Mediterranean shrub ecosystems within the area of influence of Doñana National Park in SW Spain.
-Our study focuses on understanding whether adding information on the structure of the community to previously-used simple visitation metrics (e.g., number and diversity of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success.
+Our study focuses on understanding whether adding information on the structure of the community to previously used simple visitation metrics (e.g., the number and diversity of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success.
 In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success, and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success.
-In addition to average values, we also evaluate whether community structure helps us explain differences in equity in reproductive success across individuals within a species and species within a community as a measure of evenness and stability in the pollination service.
+In addition to average values, we also evaluate whether community structure helps us explain differences in equity in reproductive success across species within a community, as a measure of evenness and stability in the pollination service.
 
@@
 
+#check number of sps per site surveyed in the focal analyses
+
+foc<-subset(d, d$Out=="focal")
+foc2<-ddply(foc, c("Site_ID", "Plant_gen_sp"), summarise, 
+              tot.species = length(Plant_gen_sp)) #number of species per site
+foc3<-ddply(foc2, c("Site_ID"), summarise, 
+            tot.species = length(Site_ID)) #number of species per site
+
 ```
@@
 
-Our study was conducted in SW Spain within the area of influence of Doñana National Park (Figure 1).
+Our study was conducted in SW Spain within the area of influence of Doñana National Park (Fig.
+1).
 Here, we surveyed 16 Mediterranean woodland patches with an average distance of 7 km between them (min= 3 km, max= 46.5 km).
@@
 Along each transect, we identified all plant species and recorded all the flower visitors that legitimately visited them during each 30-min period.
-In addition, in each round we conducted 3 minutes focal observations of 3 individuals belonging to the 19 most common species totalling X census [give mean per site?](Curro).
-In addition, unrecorded interactions between plant and pollinators during the sampling were recorded when observed out of the timed periods, as this dificult to observe interactions may be important for defining the network structure.
-Floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FdPM with the aid of experts in the different taxonomic groups (see acknowledgements).
+In addition, at each round we conducted 3 minutes of focal observations on 3 individuals per species belonging to the 19 most common species across the study area (`r round(mean(foc3$tot.species), digits=2)` $\pm$ `r round(sd(foc3$tot.species), digits=2)` species per site).
+Furthermore, we included some interactions between plant and pollinator individuals that were not observed during the sampling but that were seen immediately after, as some of these interactions are difficult so see and might be important to define network structure.
+Floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FPM with the aid of experts in the different taxonomic groups (see acknowledgements).
 All surveys were done under similar weather conditions, avoiding windy or rainy days.
-[maybe say we tried excluding singletons and analysis do not change?]()
 
@@
 
-Within each site, we marked between `r min(f.inds$tot.inds)` and `r max(f.inds$tot.inds)` individuals (`r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`) of `r min(tableS1$tot.sps)` to `r max(tableS1$tot.sps)` plant species (`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`), depending on the availability and presence of flowers during the sampling events.
+Within each site, we marked between `r min(f.inds$tot.inds)` and `r max(f.inds$tot.inds)` individuals (`r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`) belonging to `r min(tableS1$tot.sps)` to `r max(tableS1$tot.sps)` plant species (`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`), depending on the availability and presence of flowers during the sampling events.
 For each individual, we counted the number of flowers at each sampling point and recorded fruitset, the number of seeds per fruit (for `r min(s.fruitnum$tot.fruits)`-`r max(s.fruitnum$tot.fruits)` fruits, `r round(mean(s.fruitnum$tot.fruits), digits=2)` $\pm$ `r round(sd(s.fruitnum$tot.fruits), digits=2)`) and average seed weight per fruit at the end of the season.
@@
 
-**Data analyses**
+_Data analyses_
 
@@
 
-In order to analyse how differences within the community structure might affect plant reproductive success, we constructed weighted plant-pollinator interaction networks by pooling the data for the 7 rounds of sampling.
+  In order to analyse how differences in community structure might affect plant reproductive success, we constructed weighted plant-pollinator interaction networks by pooling the data for the 7 rounds of sampling.
 We thus obtained one weighted interaction network per site, representing the frequency of visits by different pollinator species to different plant species.
-For each network, we then proceeded to extract a series of relevant network metrics.
+For each network, we then proceeded to extract a series of relevant network metrics at the species and community levels.
 
@@
 At the species level, we focused on attributes defining the position of a focal plant species within the larger community.
-As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap between a focal plant species and other plant species in the community, which covers the potential indirect interactions between different plant species through shared resources (in this case pollinators), and (ii) centrality [is this calculated onto the unipartite plant network?
-If so explain](), which depicts the [importance](importance can mean anything, can you be more especific?) of the plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness.
+As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap between a focal plant species and other plant species in the community, which covers the potential indirect interactions between different plant species through shared resources (in this case pollinators), and (ii) centrality, which depicts the importance of the role played by a plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness.
+Centrality represents the number of shortest paths going through a focal plant based on a unipartite projection of the bipartite plant-pollinator network, where links between plant species represent shared pollinator species.
+As a measure of centrality we used weighted closeness centrality, which represents the number of shortest paths going through a focal plant based on a unipartite projection of the bipartite plant-pollinator network using a weighted representation of the network [@Dormann2009].
+Here, links between plant species represent shared pollinator species.
+  Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the Morisita index [@Zhang2016].
 
@@
 (2017) by using a normalized value of the widely-used nestedness metric NODF [@Almeida-Neto2011], $NODF_c$.
-This normalized value is calculated as $NODF_c = NODF_n/(C * log(S))$, where C is connectance, S is network size and $NODF_n = NODF/max(NODF)$, which is independent of network size and thus comparable across different networks [@Song2017].[See new paper by Benno simons updating Song method :(]()
+This normalized value is calculated as $NODF_c = NODF_n/(C * log(S))$, where C is connectance, S is network size and $NODF_n = NODF/max(NODF)$, which is independent of network size and thus comparable across different networks [@Song2017].
 
   Niche complementariety metrics are important because plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence (reviewed in [@Brosi2016]).
-To calculate niche complmentarity we used a community-level measure defined as the total branch length of a functional dendrogram based on qualitative differences in visitor assemblages between plants [@Devoto2012; @Petchey2007a].
+To calculate niche complmentarity, we used a community-level measure defined as the total branch length of a functional dendrogram based on qualitative differences in visitor assemblages between plants [@Devoto2012; @Petchey2007a].
 All network metrics were calculated using package bipartite [@Dormann2009].
 
-[Yet at present we do not know how the interplay between redundancy and complementarity in species roles determines reproductive success.](I don't see where to place this sentence.
-I like it, but was breaking the flow.
-Discusion?)
+  All of these metrics were calculated using all the data as well as for the subset of the data excluding interactions observed outside of sampling periods.
+Differences between results are minimal for both and thus we will only present results for the analysis using the full dataset.
 
@@
 In order to evaluate whether adding information on community structure improves our ability to explain differences in reproductive success - both at the species and the community level - we used general linear (GLMs) and general linear mixed models (GLMMs).
-In both cases (species and community-level models) we fit two types of models: (i) model 1, that only included simple visitation metrics and (ii) model 2, that additionally included information on community structure.
+In both cases (species and community-level models) we fit two types of models: (i) model 1, that only included simple visitation metrics and (ii) model 2 that additionally included information on community structure.
 
@@
 The diversity of pollinator species visiting a focal plant was approximated using the plant´s normalised degree, i.e., the number of links with different pollinator species a plant has, scaled by the number of possible partners [@Dormann2009].
-Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the Morisita index [@Zhang2016].
-As a measure of centrality we used weighted closeness centrality which describes centrality through the path lengths of a species to other species in the network using a weighted representation of the network [@Dormann2009].
-Response variables included fruitset for different individuals measured per species analyzed using a binomial distribution, the number of seeds per species for different individuals analyzed using normal distribution and average values per species of fruit and seed weight fitted to poisson distributions.
+Response variables included fruitset for different individuals measured per species analyzed using a binomial distribution, the number of seeds per species for different individuals analyzed using a normal distribution and average values per species of fruit and seed weight fitted to poisson distributions.
 
@@
 Model 2, in turn, added information on community structure by including nestedness and niche complementarity as explanatory variables.
-As response variable we had the average reproductive success for the whole community (i.e., average fruitset analyzed using a binomial distribution, average number of seeds per fruit and average fruit and seed weight previously scaled for each species for which we used normal distributions).
+As response variable we had the average reproductive success for the whole community (i.e., average fruitset analyzed using a binomial distribution, average number of seeds per fruit and average fruit and seed weight previously scaled, for each species for which we used normal distributions).
 We thus had a single value per site and no random effects are needed in this case.
@@
 We repeated this using 0.25 and 0.75 thresholds.
-We then used the same framework as before and fit the same models 1 and 2 GLMs as the ones used at the community level, but using equity in reproductive success as the response variable and a binomial distribution.
-In this case, we retained only sites for which we had at least measured reproductive success for 2 plant species (N=14 sites).
-We used information criterion methods to find the best model for each case and selected the ones with the lowest Akaike Information Criterion (AIC) value.
-$\Delta AIC<2$, were not considered enough to select one model over the other [@Burnham2011].
-
-_Simulating the effect of community structure as sample size increases_ [no se si le pondria titulo aparte o no, quizas no hace falta, yo o uniria a estatistical analysis]()
+We then used the same framework as that used for species and community-level analyses and fit the same models 1 and 2 GLMs, but using equity in reproductive success as the response variable fitting a binomial distribution.
+In all cases, we used information criterion methods to find the best model and selected the ones with the lowest Akaike Information Criterion (AIC) value.
+Whenever the difference between the AIC of both models was < 2 ($\Delta AIC<2$), we considered that both models were equally good [@Burnham2011].
 
@@
 for n = 3 plant selected out of 6 there is only 20 possible combiations).
-Then, we tested the overall relationship between equity in reproductive success and both community-level network metrics we measured: nestedness and functional complementarity within our simulated communities.
-To this end, for each species number level considered, we randomly selected one of the generated equity values across each of the 16 communities, regress this against our netrwock level predictors and extracted the model estimates.
+Then, we tested the overall relationship between equity in reproductive success and functional complementarity (given its importance in determining differences in reproductive success, see Results section) within our simulated communities.
+To this end, for each species number level considered, we randomly selected one of the generated equity values across each of the 16 communities, regressed this against our network level predictor and extracted the model estimates.
 We averaged all estimates from 1,000 simulated combinations per number of plants considered.
@@
 Within our sampling we recorded `r nrow(d)` pollinator individuals belonging to `r nlevels(unique(d$Plant_gen_sp))` species of plants and `r nlevels(unique(d$Pollinator_gen_sp))` species of pollinators.
-Within the pollinator community the distribution in different orders was: `r round(d.order$prop[d.order$order=="Hymenoptera"]*100, digits=2)`% Hymenoptera, `r round(d.order$prop[d.order$order=="Diptera"]*100, digits=2)`% Diptera, `r round(d.order$prop[d.order$order=="Coleoptera"]*100, digits=2)`% Coleoptera, `r round(d.order$prop[d.order$order=="Lepidoptera"]*100, digits=2)`% Lepidoptera, while Araneaeae and Neuroptera represented `r round(d.order$prop[d.order$order=="Araneae"]*100, digits=2)`% each.
+Within the pollinator community the distribution in different orders was: `r round(d.order$prop[d.order$order=="Hymenoptera"]*100, digits=2)`% Hymenoptera, `r round(d.order$prop[d.order$order=="Diptera"]*100, digits=2)`% Diptera, `r round(d.order$prop[d.order$order=="Coleoptera"]*100, digits=2)`% Coleoptera, `r round(d.order$prop[d.order$order=="Lepidoptera"]*100, digits=2)`% Lepidoptera, while Araneaeae and Neuroptera representing `r round(d.order$prop[d.order$order=="Araneae"]*100, digits=2)`% each.
 
@@
 
-Our sampling completeness analyses revealed that with our survey we were able to capture 18-62% of pollinator species (average= 35%), 47-98% for plant species (average= 78%) and 13-41% for plant-pollinator links (average=27%), in line with that obtained with other studies (e.g., [@Chacoff2012], Figure S1).
-Our values of sampling completeness are slightly smaller in the case of pollinators probably as a consequence of the great diversity found in the Mediterranean region and within our study area in particular, a hotspot of insect diversity [@Nieto2014a].
-[well, and the fact that we added "outs", which are singletons, a key piece used by Chao estimators!, SHould we mention this?]()
+  Our sampling completeness analyses revealed that with our survey we were able to capture 18-62% of pollinator species (average= 35%), 47-98% for plant species (average= 78%) and 13-41% for plant-pollinator links (average=27%), in line with that obtained with other studies (e.g., [@Chacoff2012], Fig.
+S1).
+Our values of sampling completeness are slightly smaller in the case of pollinators, probably as a consequence of the great diversity found in the Mediterranean region and within our study area in particular, a hotspot of insect diversity [@Nieto2014a].
+In addition, the fact that we include rare interactions observed outside of our main sampling, or singletons, might also be affecting our results.
 
@@
 At the species level, in the case of fruitset, our results show that model 2 is the best model explaining the variability observed.
-In this case, we find a positive effect of pollinator species diversity (measured using the species´normalised degree, Fig.
-2) as well as a positive effect of the centrality of the focal plant on its fruitset (Fig.
+In this case, we find a positive effect of a simple visitation metric, pollinator species diversity (measured using the species´normalised degree, Fig.
+2) as well as a positive effect of a community structure metric, the centrality of the focal plant on its fruitset (Table 1, Fig.
 2).
-[to what extent ND is a network level metric i.e.
-not a simple metric like number of links¿?
-I am playing devils advocate here.]()
 
@@
 Table1<-round(coefs.m2[,1:3],digits=2)
-rownames(Table1)<-c("(Intercept)", "Normalized degree", "Total number of visits", "Weighted closeness", "Niche overlap")
+rownames(Table1)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Centrality", "Niche overlap")
 #at the end of the paper
@@
 Given that model 2 has a greater number of variables which should be penalized given the added complexity it provides, we will comment results only for model 2.
-In this case, we find a positive effect of the niche overlap between plant species (Fig.
+In this case, we find a positive effect of the niche overlap between plant species (Table 2, Fig.
 3).
@@
 Table2<-round(coefs.m2.seed,digits=2)
-rownames(Table2)<-c("(Intercept)", "Normalized degree", "Total number of visits", "Weighted closeness", "Niche overlap")
+rownames(Table2)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Centrality", "Niche overlap")
 
@@
   xlab("Niche overlap") +      
-  ylab("Seeds per fruit") + theme_bw()  + theme (legend.position= "bottom") +
+  ylab("Seeds per fruit") + theme_bw()  + theme (legend.position= "right") +
   theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.3), face="bold")) + 
@@
   For all other measures of reproductive success considered (i.e., fruit and seed weight), the best model based on its AIC value was model 1, i.e., the model that only included simple visitation metrics (in this case, pollinator species diversity and the total number of visits received by a focal plant species).
-However, none of the variables included within our model explain the differences observed.
+However, none of the variables included within our model explain the differences observed (Tables S4-S5).
 
@@
 tableS4<-round(summary(m1.seed.w)$coefficients$cond[,1:3], digits=2)
-rownames(tableS4)<-c("(Intercept)", "Normalized degree", "Total number of visits")
+rownames(tableS4)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")
 
@@
 tableS5<-round(summary(m1.fruit.w)$coefficients$cond[,1:3], digits=2)
-rownames(tableS5)<-c("(Intercept)", "Normalized degree", "Total number of visits")
+rownames(tableS5)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")
 
@@
 Again, because this suggests model 2 is a good model despite its added complexity, we will comment results for this model only.
-In particular, we find that both fruitset and the number of seeds per fruit are positively related to niche complementarity between pollinators (Fig.
+In particular, we find that both fruitset and the number of seeds per fruit are positively related to niche complementarity between pollinators (Tables 3-4, Fig.
 4).
-Additionally, we find a negative effect of community-level pollinator species diversity and the total number of visits on average fruitset (Fig.
+Additionally, we find a negative effect of community-level pollinator species diversity and the total number of visits on average fruitset (Table 3, Fig.
 4).
@@
 
-When evaluating the effect of differences in community composition and structure for equity in reproductive success across the different species within a community we find that model 1 is the best model for all the thresholds considered (50%, 25% and 75%).
-However, we only find a significant negative relationship between equity and pollinator species diversity using the 75% threshold (Fig.
+When evaluating the effect of differences in community composition and structure for equity in reproductive success across the different species within a community we find that model 1 is the best model for all the thresholds considered (0.50, 0.25 and 0.75).
+However, we only find a significant negative relationship between equity and pollinator species diversity using the 0.75 threshold (Fig.
 6, Tables S8, S9, S10).
@@
 Within our simulation evaluating the effect of niche complementarity on equity in reproductive success, we find that the effect of complementarity becomes more important as the reproductive success of more species is considered (Fig.
-X).
-This importance seems to reach some sort of plateau at 6 species, however, this should be further evaluated as this is the maximum number of species simultaneously observed in a community for our study which precludes us from simulating further numbers of species.
+S4).
+This importance seems to reach some sort of plateau at 6 species.
+However, this should be further evaluated, as this is the maximum number of species simultaneously observed in a community for our study, which precludes us from simulating further numbers of species.
 
@@
 
-ggplot(estimate_i,  aes(x=level, y=estimate)) +    
-  geom_point(size=4) + stat_smooth(method=loess,  size=1.5, se=TRUE, color = "black", alpha=0.2) + 
+figures4<-ggplot(estimate_i,  aes(x=level, y=estimate)) +    
+  geom_point(size=4) + #stat_smooth(method=loess,  size=1.5, se=TRUE, color = "black", alpha=0.2) + 
   #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
@@
   ylab("Importance of niche complementarity") + theme_bw()  +
-  theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))
+  theme(text = element_text(size = 14), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
 
@@
 ```
-Figure X.
-Results of simulation evaluating the importance of niche complementarity in determining differences in equity in reproductive across communities harboring from one to six species.
-Points represent average values for 16 combinations of XXXX 100 times???
-[can you fill this Nacho?]()
 
@@
 
-The existence of a relationship between community structure and ecosystem function has been long hypothesized, yet, the specific mechanisms by which structure influences function remain elusive [@Thompson2012].
+The existence of a relationship between community structure and ecosystem function has been long hypothesized, yet, the specific mechanisms by which structure influences function have remained elusive until now [@Thompson2012].
 Our results show that different aspects of community structure affect different dimensions of community functioning.
@@
   One of the first conclusions we can extract from the fact that in most cases both of the models we considered (i.e., the simple model based on visitation metrics and the more complex one including community structure metrics) were equally good, is that for predictive purposes, simple visitation metrics, such as pollinator diversity, might be enough [@Garibaldi2013; @Garibaldi2015].
-Yet, a mechanistic understanding of the underlying processes driving these observed patterns, requires that we take into account measures of community structure, and, in particular, those related to the overlap in the niches of interacting species.
+Yet, a mechanistic understanding of the underlying processes driving these observed patterns requires that we take into account measures of community structure, and, in particular, those related to the overlap in the niches of interacting species [@Frund2013].
 
@@
 This can be captured by the effect of pollinators on equity in reproductive succes across plant species.
-This aspect ensures that reproductive success is equally distributed amongst a larger number of species, thus contributing to the maintenance of a greater species diversity in natural populations.
-Indeed, we know that plant species diversity within a community is largely driven by different types of direct and indirect interactions including those amongst plant species (e.g., resource competition [@Goldberg1992] or facilitation [@Bruno2003]), as well as those defining antagonistic (e.g., involving pathogens [@Bagchi2010], or mutualistic interactions (e.g, pollinators [@Benadi2013, Lanuza Ecology Letters!]()).
-However, equitability in reproductive success across species is seldom taken into account, despite its importance in maintaining genetic diversity and ensuring the resilience of populations to further change (REF).
-
-In the case of equity we did not find a significant effect of either simple visitation or community structure metrics.
+This aspect ensures that reproductive success is equally distributed amongst a larger number of species, thus contributing to the maintenance of greater species diversity values in natural populations.
+Indeed, we know that plant species diversity within a community is largely driven by different types of direct and indirect interactions including those amongst plant species (e.g., resource competition [@Goldberg1992] or facilitation [@Bruno2003]), as well as those defining antagonistic (e.g., involving pathogens [@Bagchi2010], or mutualistic interactions (e.g, pollinators [@Benadi2013; @Lanuza2018]).
+However, equitability in reproductive success across species is seldom taken into account, despite its importance in maintaining genetic diversity and ensuring the resilience of populations to further change.
+
+  In the case of equity, we did not find a significant effect of either simple visitation or community structure metrics.
 However, the results of our simulation on the importance of community structure as the number of plant species considered increases, shows us that this effect dramatically increases when more than four plant species are considered.
@@
 
+  One of the unexpected results of our analyses is the strong negative effect of pollinator diversity for fruitset at the community level, as well as a negative effect on equity in reproductive success at the 0.75 threshold.
+An explanation to this might be the fact that pollinator diversity here includes all the pollinators surveyed, while fruitset and equity in fruitset refers to a subset of the plants in the community.
+Nevertheless, we expect to gain further insights into this surprising result as more data in our study area are currently being collected.
+
   In summary, our findings show that the analysis of natural communities of interacting species using network analysis not only represents an ideal way of visualizing and grasping the complexity present within these communities, but also represents a manner of mechanisitically understanding differences observed across the reproductive success of individuals and/or species.
-
 Future studies could build on this body of research by focusing on the long-lasting effects of community structure for plant fitness, by evaluating the consequences of different community structures for heritability.
@@
 
-The authors would like to thank Oscar Aguado, Javier ??
-and XX for help in identifying pollinator species.
-In addition, XX.
-AM received funding from a Juan de la Cierva and Ikerbasque fellowships.
+The authors would like to thank Oscar Aguado for help in identifying pollinator species.
+AM received funding from a Juan de la Cierva (IJCI-2014-22558) and Ikerbasque fellowships.
 IB acknowledges funding from MSC-PCIG14-GA-2013-631653 BeeFun Project.
@@
 # Table1<-round(coefs.m2[,1:3],digits=2)
-# rownames(Table1)<-c("(Intercept)", "Normalized degree", "Total number of visits", "Weighted closeness", "Niche overlap")
-
-kable(Table1, caption = "Table 1. Results of GLMM showing effect of simple visitation and community structure metrics on species-level fruitset based on best model selected.")
+# rownames(Table1)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Centrality", "Niche overlap")
+
+kable(Table1, caption = "Table 1.
+Results of GLMM showing effect of simple visitation and community structure metrics on species-level fruitset based on best model selected.
+Bold letters indicate significant variables.")
 ```
@@
 # Table2<-round(coefs.m2.seed,digits=2)
-# rownames(Table2)<-c("(Intercept)", "Normalized degree", "Total number of visits", "Weighted closeness", "Niche overlap")
-
-kable(Table2, caption = "Table 2. Results of GLMM showing effect of simple visitation and community structure metrics on species-level number of seeds/fruit based on best model selected.")
+# rownames(Table2)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Centrality", "Niche overlap")
+
+kable(Table2, caption = "Table 2.
+Results of GLMM showing effect of simple visitation and community structure metrics on species-level number of seeds/fruit based on best model selected.
+Bold letters indicate significant variables.")
 ```
@@
 
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=8}
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=7, fig.width=9}
 
@@
 Figure2
+
+ # save_plot("figures/Figure2.tiff", Figure2,
+ #           base_height = 7, base_width = 9)
 ```
@@
 
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=6, fig.width=8}
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5.5, fig.width=6}
 
@@
 Figure3
+
+  # save_plot("figures/Figure3.tiff", Figure3,
+  #           base_height = 5.5, base_width = 6)
 ```
@@
 
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=3, fig.width=10}
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=3, fig.width=11}
 
@@
 Figure4
+
+   # save_plot("figures/Figure4.tiff", Figure4,
+   #           base_height = 3, base_width = 11)
 ```
@@
 Figure5
+
+# save_plot("figures/Figure5.tiff", Figure5,
+#              base_height = 4, base_width = 8)
 ```
@@
 Figure6
+# 
+# save_plot("figures/Figure6.tiff", Figure6,
+#              base_height = 5, base_width = 6)
 ```
@@
 
-grid.newpage()
-grid.draw(rbind(ggplotGrob(poll), ggplotGrob(plant), ggplotGrob(link), size = "last"))
-
+figures1<-plot_grid( poll, plant, link, ncol = 1)
+figures1
+
+# save_plot("figures/FigureS1.tiff", figures1,
+#            base_height = 13, base_width = 7)
 ```
@@
 
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=8}
+figures4
+```
+**Figure S4.** Results of simulation evaluating the importance of niche complementarity in determining differences in equity in reproductive across communities harboring from one to six species.
+Points represent average values across 1,000 simulated combinations.
+
 \newpage
@@
 tableS4<-round(summary(m1.seed.w)$coefficients$cond[,1:3], digits=2)
-rownames(tableS4)<-c("(Intercept)", "Normalized degree", "Total number of visits")
+rownames(tableS4)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")
 kable(tableS4, caption="Table S4. Results of GLMM showing effect of simple visitation metrics on species-level average seed weight based on best model selected.")
@@
 kable(tableS8, caption="Table S8.
-Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a community based on best model selected (50% threshold).")
+Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a community based on best model selected (0.50 threshold).")
 
 kable(tableS9, caption="Table S9.
-Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a community based on best model selected (75% threshold).")
+Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a community based on best model selected (0.75 threshold).")
 
 kable(tableS10, caption="Table S10.
-Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a community based on best model selected (25% threshold).")
+Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a community based on best model selected (0.25 threshold).")
 ```

### 2019-06-28 paper_round2.Rmd
last changes before 1st submission to PCI

@@
 
-Words in main text (excluding abstract, acknowledgements, references, table and figure legends):
-
-Number of references: 45
-
-Number of figures, tables and text boxes:
+Words in main text (excluding abstract, acknowledgements, references, table and figure legends): 4,451
+
+Number of references: 48
+
+Number of figures, tables and text boxes: 7
 
@@
 We find that, for prediction purposes, information on simple visitation metrics is sufficient.
-Contrastingly, a mechanisitic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success, requires additional information on community structure, particularly that reflecting niche complementarity between pollinators.
+Contrastingly, a mechanistic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success, requires additional information on community structure, particularly that reflecting niche complementarity between pollinators.
 \nextpage
@@
 Yet plants and pollinators do not interact in isolation, but rather are embedded within larger networks of interactions encompassing other plant and pollinator species.
-We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect ones between species within one guild (e.g., plants) through their shared resources [@Carvalheiro2014; @Lazaro2014; @Mayfield2017].
+We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect interactions between species within one guild (e.g., plants) through their shared resources [@Carvalheiro2014; @Lazaro2014; @Mayfield2017; @Pauw2013].
 Understanding how changes in pollinator diversity and interaction structure affect whole community assemblages is thus a major challenge that requires attention.
@@
   Indeed, theoretical research has long suggested that the structure of multitrophic communities has an effect for ecosystem functioning (reviewed in [@Thompson2012]).
-This line of research, primarliy driven by food-web studies, has greatly advanced theory, but these ideas have not yet been tested using empirical data (but see [@Poisot2013]).
-Specifically, a major knowledge gap resides in understading which aspects of structure determine which aspects of function [@Thompson2012].
+This line of research, primarily driven by food-web studies, has greatly advanced theory, but these ideas have not yet been tested using empirical data (but see [@Poisot2013]).
+Specifically, a major knowledge gap resides in understanding which aspects of structure determine which aspects of function [@Thompson2012].
 We are now at a point in which there is considerable understanding on the attributes characterizing mutualistic interaction networks [@Bascompte2007b] and we have a substantial understanding of how these attributes vary along different types of gradients [@Pellissier2017; @Tylianakis2016].
@@
 In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success, and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success.
-In addition to average values, we also evaluate whether community structure helps us explain differences in equity in reproductive success across species within a community, as a measure of evenness and stability in the pollination service.
+In addition to average values, we also evaluate whether community structure helps us explain differences in equity in reproductive success across species within a community, as a measure of evenness in the pollination service delivered.
 
   Our results suggest that for prediction purposes, information on simple visitation metrics, particularly regarding the diversity of pollinators that visit a plant species, is sufficient.
-However, we find that a mechanisitic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success requires additional information on network structure, notably information on the complementarity between the functions performed and the niches occupied by different pollinator species.
+However, we find that a mechanistic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success requires additional information on network structure, notably information on the complementarity between the functions performed and the niches occupied by different pollinator species.
 
@@
 In addition, at each round we conducted 3 minutes of focal observations on 3 individuals per species belonging to the 19 most common species across the study area (`r round(mean(foc3$tot.species), digits=2)` $\pm$ `r round(sd(foc3$tot.species), digits=2)` species per site).
-Furthermore, we included some interactions between plant and pollinator individuals that were not observed during the sampling but that were seen immediately after, as some of these interactions are difficult so see and might be important to define network structure.
+Furthermore, we included some interactions between plant and pollinator individuals that were not observed during the sampling but that were opportunistically recorded immediately before or after the sampling periods, as some of these interactions are difficult to document and might be important to define network structure [@Jordano2016].
 Floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FPM with the aid of experts in the different taxonomic groups (see acknowledgements).
@@
 
-Within each site, we marked between `r min(f.inds$tot.inds)` and `r max(f.inds$tot.inds)` individuals (`r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`) belonging to `r min(tableS1$tot.sps)` to `r max(tableS1$tot.sps)` plant species (`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`), depending on the availability and presence of flowers during the sampling events.
-For each individual, we counted the number of flowers at each sampling point and recorded fruitset, the number of seeds per fruit (for `r min(s.fruitnum$tot.fruits)`-`r max(s.fruitnum$tot.fruits)` fruits, `r round(mean(s.fruitnum$tot.fruits), digits=2)` $\pm$ `r round(sd(s.fruitnum$tot.fruits), digits=2)`) and average seed weight per fruit at the end of the season.
+Within each site, we marked between 3 and `r max(f.inds$tot.inds)` individuals (`r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`) belonging to `r min(tableS1$tot.sps)` to `r max(tableS1$tot.sps)` plant species (`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`), depending on the availability and presence of flowers during the sampling events.
+For each individual, at the end of the season, we
+recorded fruit set (i.e.
+the proportion of flowers that set fruit), the average number of seeds per fruit and the average seed weight per fruit (`r min(s.fruitnum$tot.fruits)`-`r max(s.fruitnum$tot.fruits)` fruits subsampled, mean = `r round(mean(s.fruitnum$tot.fruits), digits=2)` $\pm$ `r round(sd(s.fruitnum$tot.fruits), digits=2)`).
 Our survey included a total of `r nlevels(f2$Plant.sp)` different plant species across our `r nlevels(f2$Site_ID)` sites.
@@
 At the species level, we focused on attributes defining the position of a focal plant species within the larger community.
-As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap between a focal plant species and other plant species in the community, which covers the potential indirect interactions between different plant species through shared resources (in this case pollinators), and (ii) centrality, which depicts the importance of the role played by a plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness.
-Centrality represents the number of shortest paths going through a focal plant based on a unipartite projection of the bipartite plant-pollinator network, where links between plant species represent shared pollinator species.
+As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap in terms of pollinators between a focal plant species and other plant species in the community, which covers the potential indirect interactions between different plant species through shared resources (in this case pollinators), and (ii) centrality, which depicts the importance of the role played by a plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness.
+ Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the Morisita index [@Zhang2016].
 As a measure of centrality we used weighted closeness centrality, which represents the number of shortest paths going through a focal plant based on a unipartite projection of the bipartite plant-pollinator network using a weighted representation of the network [@Dormann2009].
 Here, links between plant species represent shared pollinator species.
-  Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the Morisita index [@Zhang2016].
 
@@
 
-  Niche complementariety metrics are important because plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence (reviewed in [@Brosi2016]).
-To calculate niche complmentarity, we used a community-level measure defined as the total branch length of a functional dendrogram based on qualitative differences in visitor assemblages between plants [@Devoto2012; @Petchey2007a].
+  Niche complementarity metrics are important because plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence (reviewed in [@Brosi2016]).
+To calculate niche complementarity, we used a community-level measure defined as the total branch length of a functional dendrogram based on qualitative differences measured using a Euclidean distance in visitor assemblages between plants [@Devoto2012; @Petchey2007a].
 All network metrics were calculated using package bipartite [@Dormann2009].
@@
 In both cases (species and community-level models) we fit two types of models: (i) model 1, that only included simple visitation metrics and (ii) model 2 that additionally included information on community structure.
-
-  At the species level, model 1 included as explanatory variables the diversity of pollinator species visiting a focal plant and the total number of visits received by that plant species; while model 2, added the two network attributes calculated at the species level: average niche overlap and centrality.
+All response variables were previously scaled for each species to allow meaningful comparisons across species with contrasting life histories.
+
+  At the species level, model 1 included as explanatory variables the diversity of pollinator species visiting a focal plant (i.e.
+pollinator richness), and the total number of visits received by that plant species; while model 2 added the two network attributes calculated at the species level: average niche overlap and centrality.
 In this case, we included plant species nested within site as a random effect to account for the non-independence of several individuals measured for the same plant species within each site.
-The diversity of pollinator species visiting a focal plant was approximated using the plant´s normalised degree, i.e., the number of links with different pollinator species a plant has, scaled by the number of possible partners [@Dormann2009].
-Response variables included fruitset for different individuals measured per species analyzed using a binomial distribution, the number of seeds per species for different individuals analyzed using a normal distribution and average values per species of fruit and seed weight fitted to poisson distributions.
+Response variables included fruit set for different individuals of each species analyzed using a binomial distribution, the average number of seeds per fruit analyzed using a normal distribution and the average values per species of fruit and seed weight fitted to poisson distributions.
 
   At the community level, we upscaled our species-level analyses.
-In this case, model 1 included total pollinator diversity and the total number of visits received by all plants within the community as explanatory variables.
+In this case, model 1 included total pollinator richness and total pollinator abundance (i.e., the number of visits received by all plants within the community) as explanatory variables.
 Model 2, in turn, added information on community structure by including nestedness and niche complementarity as explanatory variables.
-As response variable we had the average reproductive success for the whole community (i.e., average fruitset analyzed using a binomial distribution, average number of seeds per fruit and average fruit and seed weight previously scaled, for each species for which we used normal distributions).
+As response variable we had the average reproductive success for the whole community (i.e., average fruit set analyzed using a binomial distribution, average number of seeds per fruit and average fruit and seed weight using a normal distribution).
+All metrics were previously scaled for each species to allow meaningful comparisons across species with contrasting life histories.
 We thus had a single value per site and no random effects are needed in this case.
@@
 Yet, what will determine the persistence of a diverse plant community, is the presence of some sort of “equity” or evenness in reproductive success across the whole community.
-We therefore calculated a measure of equity in reproductive success at the community level as the proportion of species within a community with normalized [explain how, normalizations usually make 0 centred values, and values above 0.5 makes no sense]() average fruitset values above 0.5.
+We therefore calculated a measure of equity in reproductive success at the community level as the proportion of species within a community with normalized (between 0 and 1) average fruit set values that were above 0.5.
 We repeated this using 0.25 and 0.75 thresholds.
@@
 Whenever the difference between the AIC of both models was < 2 ($\Delta AIC<2$), we considered that both models were equally good [@Burnham2011].
+All predictor variables were centered prior to analysis.
 
@@
 
-  To test this, we ran a simple simulation in which the number of species considered increased at each time step and for each time step we re-calculated equity in reproductive success.
-Instead of drawing plant species randomly for each run, we tested all possible combinations for each plant number level and network, as the number of combinations is low (e.g.
-for n = 3 plant selected out of 6 there is only 20 possible combiations).
-Then, we tested the overall relationship between equity in reproductive success and functional complementarity (given its importance in determining differences in reproductive success, see Results section) within our simulated communities.
-To this end, for each species number level considered, we randomly selected one of the generated equity values across each of the 16 communities, regressed this against our network level predictor and extracted the model estimates.
-We averaged all estimates from 1,000 simulated combinations per number of plants considered.
+  To test this, we ran a simple simulation in which the number of species considered increased at each step and for each step we re-calculated equity in reproductive success.
+Instead of drawing plant species randomly for each step, we tested all possible combinations for each plant number level and network, as the number of combinations is low (e.g.
+for n = 3 plant selected out of 6 there is only 20 possible combinations).
+Then, we tested if the relationship between equity in reproductive success and functional complementarity (given its importance in determining differences in reproductive success, see Results section) changes as a function of the number of plants considered within our simulated communities.
+To this end, for each level of species number considered, we randomly selected one of the generated equity values across each of the 16 communities, and regressed these 16 values against our network level predictor and extracted the model estimates.
+We repeated this process 1,000 times and averaged all estimates.
 We expect that the more plants considered, the larger the resulting average estimates will be.
-Note that we only interpret the mean effects, as the variance among different plant number of species depends on the initial number of combinations.
+Note that we only interpret the mean effects, as the variance among different plant number of species considered depends on the initial number of combinations.
 
@@
 Within our sampling we recorded `r nrow(d)` pollinator individuals belonging to `r nlevels(unique(d$Plant_gen_sp))` species of plants and `r nlevels(unique(d$Pollinator_gen_sp))` species of pollinators.
-Within the pollinator community the distribution in different orders was: `r round(d.order$prop[d.order$order=="Hymenoptera"]*100, digits=2)`% Hymenoptera, `r round(d.order$prop[d.order$order=="Diptera"]*100, digits=2)`% Diptera, `r round(d.order$prop[d.order$order=="Coleoptera"]*100, digits=2)`% Coleoptera, `r round(d.order$prop[d.order$order=="Lepidoptera"]*100, digits=2)`% Lepidoptera, while Araneaeae and Neuroptera representing `r round(d.order$prop[d.order$order=="Araneae"]*100, digits=2)`% each.
+Within the pollinator community the distribution in different orders was: `r round(d.order$prop[d.order$order=="Hymenoptera"]*100, digits=2)`% Hymenoptera, `r round(d.order$prop[d.order$order=="Diptera"]*100, digits=2)`% Diptera, `r round(d.order$prop[d.order$order=="Coleoptera"]*100, digits=2)`% Coleoptera and `r round(d.order$prop[d.order$order=="Lepidoptera"]*100, digits=2)`% Lepidoptera.
 
@@
 
-  Our sampling completeness analyses revealed that with our survey we were able to capture 18-62% of pollinator species (average= 35%), 47-98% for plant species (average= 78%) and 13-41% for plant-pollinator links (average=27%), in line with that obtained with other studies (e.g., [@Chacoff2012], Fig.
+  Our sampling completeness analyses revealed that with our survey we were able to capture 18-62% of pollinator species (average = 35%), 47-98% for plant species (average = 78%) and 13-41% for plant-pollinator links (average = 27%), in line with that obtained with other studies (e.g., [@Chacoff2012], Fig.
 S1).
 Our values of sampling completeness are slightly smaller in the case of pollinators, probably as a consequence of the great diversity found in the Mediterranean region and within our study area in particular, a hotspot of insect diversity [@Nieto2014a].
-In addition, the fact that we include rare interactions observed outside of our main sampling, or singletons, might also be affecting our results.
+In addition, the fact that we include an extra effort to capture rare interactions observed outside of our main sampling might also increase the number of singletons which directly affect richness estimates.
 
@@
 f2$tot.visits[is.na(f2$tot.visits)]<-0
+
+#calculate number of pollinator species per plant species instead of norm_degree
+
+sites <- unique(d$Site_ID)
+plants<-unique(d$Plant_gen_sp)
+
+out <- data.frame(Site_id = NA, plant.sps = NA, poll.sps = NA)
+
+for(i in 1:length(sites)){
+  temp <- subset(d, Site_ID == sites[i])
+  for(j in 1:length(plants)){
+      temp2 <- subset(temp, Plant_gen_sp == plants[j])
+  temp3<-droplevels(temp2)
+
+  poll<-nlevels(unique(temp3$Pollinator_gen_sp))
+
+  n <- nrow(out)
+
+  out[n + 1,1] <- as.character(sites[i])
+  out[n + 1,2] <- as.character(plants[j])
+  out[n + 1,3] <- poll
+
+}
+}
+out
+
+out2<-out[-1,]
+out2$match<-paste(out2$Site_id, out2$plant.sps)
+
+f2$pollspsperplant<-out2$poll.sps[match(f2$match, out2$match)]
 
@@
 f2$niche.overlap.sc<-scale(f2$niche.overlap, center = T, scale = T)
+f2$pollspsperplant.sc<-scale(f2$pollspsperplant, center = T, scale = T)
 
@@
 In this case, we find a positive effect of a simple visitation metric, pollinator species diversity (measured using the species´normalised degree, Fig.
-2) as well as a positive effect of a community structure metric, the centrality of the focal plant on its fruitset (Table 1, Fig.
-2).
+2) as well as a positive effect of a community structure metric, the centrality of the focal plant on its fruit set (Table 1A, Fig.
+2A).
 
@@
 
-m1<-glmer(tot.fruitset ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2_scaled)
+m1<-glmer(tot.fruitset ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2_scaled)
 
@@
 
-m2<-glmer(tot.fruitset ~  norm_degree.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2_scaled)
+m2<-glmer(tot.fruitset ~  pollspsperplant.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2_scaled)
 
@@
 coefs.m2
-Table1<-round(coefs.m2[,1:3],digits=2)
-rownames(Table1)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Centrality", "Niche overlap")
+Table1A<-round(coefs.m2[,1:3],digits=2)
+rownames(Table1A)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Centrality", "Niche overlap")
 #at the end of the paper
 
-#both models equally good, plot significant variables, in this case degree, do partial residual plots to show the effect of that variable in isolation of the others
+#both models equally good, plot significant variables, in this case centrality, do partial residual plots to show the effect of that variable in isolation of the others
 
@@
 
-y_partial_norm <- remef(m2, fix= c( "tot.visits.sc", "weigh_closeness.sc", "niche.overlap.sc"), ran = "all", inverse = F)
-#With this we remove the influece of x2 and the random effects from the dependent variable
-y_partial_norm_inv<-exp(y_partial_norm)/(1+exp(y_partial_norm))
-#then we use this new variable to plot. We use m1@frame as dataset because not all observations are used in modeldue to presence of NAs
-
-pl1<-ggplot(m2@frame,  aes(x=m2@frame$norm_degree.sc, y=y_partial_norm_inv, color=Plant.sp)) +    
-  geom_point(size=2.5, shape=21, colour="black", aes(fill=factor(Plant.sp))) + stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
-  #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
-  xlab("Normalized degree") +      
-  ylab("Fruitset") + theme_bw()  + theme (legend.position= c(0.85,0.35)) +
-  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.1), face="bold")) + 
-  scale_fill_discrete(name="Plant species") +  theme(legend.text = element_text(size = 6, face = "italic"), legend.title = element_text(size=11, face = "bold"), legend.direction = "horizontal")
-
-#pl1
-
-y_partial_weigh <- remef(m2, fix= c( "tot.visits.sc", "norm_degree.sc", "niche.overlap.sc"), ran = "all", inverse = F)
+y_partial_weigh <- remef(m2, fix= c( "tot.visits.sc", "pollspsperplant.sc", "niche.overlap.sc"), ran = "all", inverse = F)
 #With this we remove the influece of x2 and the random effects from the dependent variable
@@
 
-pl1b<-ggplot(m2@frame,  aes(x=m2@frame$weigh_closeness.sc, y=y_partial_weigh_inv, color= Plant.sp)) +    
+Figure2a<-ggplot(m2@frame,  aes(x=m2@frame$weigh_closeness.sc, y=y_partial_weigh_inv, color= Plant.sp)) +    
   geom_point(size=2.5, shape=21, colour="black", aes(fill=factor(Plant.sp))) + stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
@@
   xlab("Centrality") +      
-  ylab(" ") + theme_bw()  + theme (legend.position= "top") +
+  ylab("Fruit set ") + theme_bw()  + theme (legend.position= "bottom") +
   theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.3), face="bold")) + 
@@
 
-#pl1b
-
- prow <- plot_grid( pl1 + theme(legend.position="none"),
-           pl1b + theme(legend.position="none"),
+#Figure2a
+
+```
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
+##ahora con seed set
+
+s3$functional.comp.poll<-out.site$functional.comp.poll[match(s3$Site_ID, out.site$Site_id)]
+s3$nodf.song<-out.site$nodf.song[match(s3$Site_ID, out.site$Site_id)]
+s3$species.poll<-out.site$species.poll[match(s3$Site_ID, out.site$Site_id)]
+
+#also match with plant species level network data
+s3$match<-paste(s3$Site_ID, s3$Plant.sp)
+outsp.pl.site$match<-paste(outsp.pl.site$Site_id, outsp.pl.site$species)
+
+s3$norm_degree<-outsp.pl.site$norm_degree[match(s3$match, outsp.pl.site$match)]
+s3$weigh_closeness<-outsp.pl.site$weigh_closeness[match(s3$match, outsp.pl.site$match)]
+s3$niche.overlap<-out.niche.agg$mean.niche.over[match(s3$match, out.niche.agg$j)]
+
+s3$tot.visits<-d.vis$tot.visits[match(s3$match, d.vis$j)]
+s3$tot.visits[is.na(s3$tot.visits)]<-0
+
+s3$pollspsperplant<-out2$poll.sps[match(s3$match, out2$match)]
+
+#scale all variables used
+
+s3$functional.comp.poll.sc<-scale(s3$functional.comp.poll, center = T, scale = T)
+s3$nodf.song.sc<-scale(s3$nodf.song, center = T, scale = T)
+s3$species.poll.sc<-scale(s3$species.poll, center = T, scale = T)
+
+s3$norm_degree.sc<-scale(s3$norm_degree, center = T, scale = T)
+s3$weigh_closeness.sc<-scale(s3$weigh_closeness, center = T, scale = T)
+s3$niche.overlap.sc<-scale(s3$niche.overlap, center = T, scale = T)
+s3$pollspsperplant.sc<-scale(s3$pollspsperplant, center = T, scale = T)
+
+#scale total visits per plant species
+library(dplyr)
+s3_scaled <- s3 %>% group_by(Plant.sp) %>% mutate(tot.visits.sc = scale(tot.visits, center = T, scale = T))
+
+s4_scaled <- s3_scaled %>% group_by(Plant.sp) %>% mutate(mean.seedn.sc = scale(mean.seedn, center = T, scale = T))
+
+```
+
+ For the number of seeds per fruit, our results show again that model 2 is the best model. In this case, we find a positive effect of the niche overlap between plant species (Table 1B, Fig. 2B).
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
+#fit two models
+
+m1.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s4_scaled)
+
+summary(m1.seed)
+vif(m1.seed)
+
+m2.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s4_scaled)
+
+summary(m2.seed)
+vif(m2.seed)
+
+AICtab(m1.seed, m2.seed) #m2 is best
+
+#test for problems in residuals
+# res<-simulateResiduals(m1.seed)
+# plot(res, rank = TRUE)
+
+# extract coefficients and p-values for m1 and present them in paper
+coefs.m2.seed <- data.frame(coef(summary(m2.seed)))
+# use normal distribution to approximate p-value
+#coefs.m2.seed$p.z <- 2 * (1 - pnorm(abs(coefs.m2.seed$t.value)))
+coefs.m2.seed
+Table1B<-round(coefs.m2.seed,digits=2)
+rownames(Table1B)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Centrality", "Niche overlap")
+
+#plot significant variables
+y_partial_norm_seed <- remef(m2.seed, fix= c("pollspsperplant.sc", "tot.visits.sc", "weigh_closeness.sc"), ran = "all", inverse = F)
+#With this we remove the influece of x2 and the random effects from the dependent variable
+y_partial_norm_seed_inv<-exp(y_partial_norm_seed)/(1+exp(y_partial_norm_seed))
+#then we use this new variable to plot. We use m1@frame as dataset because not all observations are used in modeldue to presence of NAs
+
+Figure2b<-ggplot(m2.seed@frame,  aes(x=m2.seed@frame$niche.overlap.sc, y=y_partial_norm_seed_inv, color= Plant.sp)) +    
+  geom_point(size=2.5, shape=21, colour="black", aes(fill=factor(Plant.sp))) + stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
+  #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+  xlab("Niche overlap") +      
+  ylab("Average seeds/fruit") + theme_bw()  + theme (legend.position= "right") +
+  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.3), face="bold")) + 
+  scale_fill_discrete(name="Plant species") +  theme(legend.text = element_text(size = 6, face = "italic"), legend.title = element_text(size=11, face = "bold"))
+
+#Figure2b
+
+#how to have two plots with same legend
+
+prow <- plot_grid( Figure2a + theme(legend.position="none"),
+                   Figure2b + theme(legend.position="none"),
                    align = 'vh',
@@
 # extract the legend from one of the plots
-legend_b <- get_legend(pl1 + theme(legend.position="bottom"))
+legend_b <- get_legend(Figure2a + theme(legend.position="bottom"))
 
@@
 # of one plot (via rel_heights).
-Figure2 <- plot_grid( prow, legend_b, ncol = 1, rel_heights = c(1, .2))
-
-```
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
-##ahora con seed set
-
-s3$functional.comp.poll<-out.site$functional.comp.poll[match(s3$Site_ID, out.site$Site_id)]
-s3$nodf.song<-out.site$nodf.song[match(s3$Site_ID, out.site$Site_id)]
-s3$species.poll<-out.site$species.poll[match(s3$Site_ID, out.site$Site_id)]
-
-#also match with plant species level network data
-s3$match<-paste(s3$Site_ID, s3$Plant.sp)
-outsp.pl.site$match<-paste(outsp.pl.site$Site_id, outsp.pl.site$species)
-
-s3$norm_degree<-outsp.pl.site$norm_degree[match(s3$match, outsp.pl.site$match)]
-s3$weigh_closeness<-outsp.pl.site$weigh_closeness[match(s3$match, outsp.pl.site$match)]
-s3$niche.overlap<-out.niche.agg$mean.niche.over[match(s3$match, out.niche.agg$j)]
-
-s3$tot.visits<-d.vis$tot.visits[match(s3$match, d.vis$j)]
-s3$tot.visits[is.na(s3$tot.visits)]<-0
-
-#scale all variables used
-
-s3$functional.comp.poll.sc<-scale(s3$functional.comp.poll, center = T, scale = T)
-s3$nodf.song.sc<-scale(s3$nodf.song, center = T, scale = T)
-s3$species.poll.sc<-scale(s3$species.poll, center = T, scale = T)
-
-s3$norm_degree.sc<-scale(s3$norm_degree, center = T, scale = T)
-s3$weigh_closeness.sc<-scale(s3$weigh_closeness, center = T, scale = T)
-s3$niche.overlap.sc<-scale(s3$niche.overlap, center = T, scale = T)
-
-#scale total visits per plant species
-library(dplyr)
-s3_scaled <- s3 %>% group_by(Plant.sp) %>% mutate(tot.visits.sc = scale(tot.visits, center = T, scale = T))
-
-s4_scaled <- s3_scaled %>% group_by(Plant.sp) %>% mutate(mean.seedn.sc = scale(mean.seedn, center = T, scale = T))
-
-```
-
-  For the number of seeds per fruit, our results show that both model 1 and model 2 are equally good in explaining the variability observed (i.e.,$\Delta AIC<2$), and therefore we cannot select one over the other.
-Given that model 2 has a greater number of variables which should be penalized given the added complexity it provides, we will comment results only for model 2.
-In this case, we find a positive effect of the niche overlap between plant species (Table 2, Fig.
-3).
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
-#fit two models
-
-m1.seed<-glmer(mean.seedn.sc ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s4_scaled)
-
-summary(m1.seed)
-vif(m1.seed)
-
-m2.seed<-glmer(mean.seedn.sc ~  norm_degree.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s4_scaled)
-
-summary(m2.seed)
-vif(m2.seed)
-
-AICtab(m1.seed, m2.seed) #both models are equally good.
-
-#test for problems in residuals
-# res<-simulateResiduals(m1.seed)
-# plot(res, rank = TRUE)
-
-# extract coefficients and p-values for m1 and present them in paper
-coefs.m2.seed <- data.frame(coef(summary(m2.seed)))
-# use normal distribution to approximate p-value
-#coefs.m2.seed$p.z <- 2 * (1 - pnorm(abs(coefs.m2.seed$t.value)))
-coefs.m2.seed
-Table2<-round(coefs.m2.seed,digits=2)
-rownames(Table2)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Centrality", "Niche overlap")
-
-#plot significant variables
-y_partial_norm_seed <- remef(m2.seed, fix= c("norm_degree.sc", "tot.visits.sc", "weigh_closeness.sc"), ran = "all", inverse = F)
-#With this we remove the influece of x2 and the random effects from the dependent variable
-y_partial_norm_seed_inv<-exp(y_partial_norm_seed)/(1+exp(y_partial_norm_seed))
-#then we use this new variable to plot. We use m1@frame as dataset because not all observations are used in modeldue to presence of NAs
-
-Figure3<-ggplot(m2.seed@frame,  aes(x=m2.seed@frame$niche.overlap.sc, y=y_partial_norm_seed_inv, color= Plant.sp)) +    
-  geom_point(size=2.5, shape=21, colour="black", aes(fill=factor(Plant.sp))) + stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
-  #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
-  xlab("Niche overlap") +      
-  ylab("Seeds per fruit") + theme_bw()  + theme (legend.position= "right") +
-  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.3), face="bold")) + 
-  scale_fill_discrete(name="Plant species") +  theme(legend.text = element_text(size = 6, face = "italic"), legend.title = element_text(size=11, face = "bold"))
-
-#Figure3  #al final del paper
+Figure2 <- plot_grid( prow, legend_b, ncol = 1, rel_heights = c(1, .2))#al final del paper
 
@@
 
-m1.seed.w<-glmmTMB(mean.seedw ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3_scaled)
+m1.seed.w<-glmmTMB(mean.seedw ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3_scaled)
 
@@
 
-m2.seed.w<-glmmTMB(mean.seedw ~  norm_degree.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3_scaled)
+m2.seed.w<-glmmTMB(mean.seedw ~  pollspsperplant.sc + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3_scaled)
 
@@
 
-m1.fruit.w<-glmmTMB(mean.fruitweight ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3_scaled)
+m1.fruit.w<-glmmTMB(mean.fruitweight ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3_scaled)
 
@@
 
-m2.fruit.w<-glmmTMB(mean.fruitweight ~  norm_degree.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3_scaled)
+m2.fruit.w<-glmmTMB(mean.fruitweight ~  pollspsperplant.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3_scaled)
 
@@
 
-At the community level, we find different patterns for fruitset and the number of seeds per fruit as compared to those for fruit and seed weight.
-In the case of fruitset and the number of seeds per fruit, we find that both model 1 and 2 are equally good in describing the differences observed (i.e.,$\Delta AIC<2$).
-Again, because this suggests model 2 is a good model despite its added complexity, we will comment results for this model only.
-In particular, we find that both fruitset and the number of seeds per fruit are positively related to niche complementarity between pollinators (Tables 3-4, Fig.
+At the community level, we find different patterns for fruit set and the number of seeds per fruit as compared to those for fruit and seed weight.
+In the case of fruit set and the number of seeds per fruit, we find that both model 1 and 2 are equally good in describing the differences observed (i.e.,$\Delta AIC<2$).
+Because this suggests model 2 is a good model despite its added complexity, we will comment results for this model only.
+In particular, we find that both fruit set and the number of seeds per fruit are positively related to niche complementarity between pollinators (Tables 2, Figs.
+3-4).
+Additionally, we find a negative effect of community-level pollinator species diversity and the total number of visits on average fruit set (Table 2A, Fig.
+3), while the total number of visits positively affected the average number of seeds per fruit (Table 2B, Fig.
 4).
-Additionally, we find a negative effect of community-level pollinator species diversity and the total number of visits on average fruitset (Table 3, Fig.
-4).
+The number of visits for one of the sites was particularly large, yet this did not affect our results as removing this site from the analysis showed the same effect.
 
@@
 #table with results for paper
-Table3<-round(summary(m2.fruit.net)$coefficients$cond, digits=2)
-rownames(Table3)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Nestedness", "Niche complementarity")
+Table2A<-round(summary(m2.fruit.net)$coefficients$cond, digits=2)
+rownames(Table2A)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Nestedness", "Niche complementarity")
 #at the end of paper
@@
         xlab("Pollinator sps diversity") +      
-        ylab("Fruitset") + theme_bw()  + #theme (legend.position= "none") +
+        ylab("Fruit set") + theme_bw()  + #theme (legend.position= "none") +
         theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
@@
 
-Figure4<-plot_grid(pl3, pl4, pl2, labels = c("A", "B", "C"), nrow=1) #al final del paper
+Figure3<-plot_grid(pl3, pl4, pl2, labels = c("A", "B", "C"), nrow=1) #al final del paper
 
@@
 #save table with results for paper
-Table4<-round(summary(m2.seed.net)$coefficients[,1:3], digits=2)
-rownames(Table4)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Nestedness", "Niche complementarity") #end of paper
+Table2B<-round(summary(m2.seed.net)$coefficients[,1:3], digits=2)
+rownames(Table2B)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Nestedness", "Niche complementarity") #end of paper
 
@@
         xlab("Total number of visits") +      
-        ylab("Number of seeds/fruit") + theme_bw()  + 
+        ylab("Average seeds/fruit") + theme_bw()  + 
   theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
@@
 
-Figure5<-plot_grid(pl5, pl6, labels = c("A", "B")) 
+Figure4<-plot_grid(pl5, pl6, labels = c("A", "B")) 
 ```
@@
 When evaluating the effect of differences in community composition and structure for equity in reproductive success across the different species within a community we find that model 1 is the best model for all the thresholds considered (0.50, 0.25 and 0.75).
-However, we only find a significant negative relationship between equity and pollinator species diversity using the 0.75 threshold (Fig.
-6, Tables S8, S9, S10).
+However, we also find a significant negative relationship between equity and pollinator species diversity using the 0.75 threshold (Fig.
+5, Tables S8, S9, S10).
 
@@
 
-Figure6 <- ggplot(highprod75.sps,  aes(x=species.poll.sc, y= res.eq.retro)) +    
+Figure5 <- ggplot(highprod75.sps,  aes(x=species.poll.sc, y= res.eq.retro)) +    
         geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
@@
 
-_Simulating the effect of community structure as sample size increases_
-
-Within our simulation evaluating the effect of niche complementarity on equity in reproductive success, we find that the effect of complementarity becomes more important as the reproductive success of more species is considered (Fig.
+  Within our simulation evaluating the effect of niche complementarity on equity in reproductive success as more plants within the community are considered, we find that the effect of complementarity becomes more important as the reproductive success of more species is considered (Fig.
 S4).
@@
 Our results show that different aspects of community structure affect different dimensions of community functioning.
-In particular, we find that the centrality of a species within a community, which measures the number of connections it receives from other species in the community, has a positive effect for its fruitset.
-At the community level, however, we find that niche complementarity between pollinators, a measure of the overlap in the niches of different species in terms of plant coverage, has an important effect for average fruitset.
-
-  One of the first conclusions we can extract from the fact that in most cases both of the models we considered (i.e., the simple model based on visitation metrics and the more complex one including community structure metrics) were equally good, is that for predictive purposes, simple visitation metrics, such as pollinator diversity, might be enough [@Garibaldi2013; @Garibaldi2015].
+In particular, we find that the centrality of a plant species within a community, which measures the number of connections it receives from other species in the community, has a positive effect for its fruit set.
+At the community level, however, we find that niche complementarity between pollinators, a measure of the overlap in the niches of different species in terms of plant coverage, has an important effect for average fruit set.
+
+  One of the first conclusions we can extract from the fact that in most cases both of the models we considered (i.e., the simple model based on visitation metrics and the more complex one including community structure metrics) were equally good, is that for predictive purposes simple visitation metrics, such as pollinator diversity, might be enough [@Garibaldi2013; @Garibaldi2015].
 Yet, a mechanistic understanding of the underlying processes driving these observed patterns requires that we take into account measures of community structure, and, in particular, those related to the overlap in the niches of interacting species [@Frund2013].
 
-  Consistent with previous experimental [@Fontaine2005; @Frund2013], theoretical [ref: Gravel probably has something](), and empirical studies [@Valdovinos2016], we find that niche complementarity is key in determining differences in reproductive outputs.
-Indeed, we find that communities where there is less overlap in the niches occupied by pollinator species had greater values of reproductive success, both greater fruitset values and larger numbers of seeds per fruit.
+  Consistent with previous experimental [@Fontaine2005; @Frund2013], theoretical [@Pauw2013], and empirical studies [@Poisot2013; @Valdovinos2016], we find that niche complementarity is key in determining differences in reproductive outputs.
+Indeed, we find that communities where there is less overlap in the niches occupied by pollinator species had greater values of reproductive success, both greater fruit set values and larger numbers of seeds per fruit.
 This therefore reflects the fact that reproductive success in plant species requires of the delivery of conspecific pollen and thus of a certain degree of specialization amongst pollinator species on a particular plant resource in order to avoid the negative effects of inter-specific pollen deposition (e.g., pollen loss [@Flanagan2009] or interference with conspecific pollen [@Morales2008]).
@@
 
-  Community-level plant reproductive success, measured as average fruit or seed set across all the species considered [@Frund2013], is an important part of the functions delivered by pollinators to plants.
-However, these average values might be masking a great deal of variability amongst species, and thus a nuanced view of the effect of pollinators on whole-plant ensembles is needed.
-This can be captured by the effect of pollinators on equity in reproductive succes across plant species.
+  Community-level plant reproductive success, measured as average fruit or seed set across all the species considered is an important part of the functions delivered by pollinators to plants.
+However, these average values might be masking a great deal of variability amongst plant species, and thus a nuanced view of the effect of pollinators on whole-plant ensembles is needed.
+This can be captured by the effect of pollinators on equity in reproductive success across plant species.
 This aspect ensures that reproductive success is equally distributed amongst a larger number of species, thus contributing to the maintenance of greater species diversity values in natural populations.
@@
 
-  One of the unexpected results of our analyses is the strong negative effect of pollinator diversity for fruitset at the community level, as well as a negative effect on equity in reproductive success at the 0.75 threshold.
-An explanation to this might be the fact that pollinator diversity here includes all the pollinators surveyed, while fruitset and equity in fruitset refers to a subset of the plants in the community.
-Nevertheless, we expect to gain further insights into this surprising result as more data in our study area are currently being collected.
-
-  In summary, our findings show that the analysis of natural communities of interacting species using network analysis not only represents an ideal way of visualizing and grasping the complexity present within these communities, but also represents a manner of mechanisitically understanding differences observed across the reproductive success of individuals and/or species.
+  One of the unexpected results of our analyses is the strong negative effect of pollinator diversity for fruit set at the community level, as well as a negative effect on equity in reproductive success at the 0.75 threshold.
+An explanation to this might be the fact that pollinator diversity here includes all the pollinators surveyed, while fruit set and equity in fruit set refers to a subset of the plants in the community.
+More complex communities (with more pollinators, but also with more plant species, with a Pearson correlation value of 0.42 in our case) may require stabilizing mechanisms that reduce the competition exerted by the dominant plant species.
+This can be reached, for example, by a reduction in the reproductive success of the dominant species [@Lanuza2018], which are precisely those evaluated in this study.
+These ideas open the door to explore the positive or negative effects of the complete pollinator community on full plant species coexistence, which may be determined by density-dependence effects [@Benadi2018].
+In our case, while fruit set is negatively related to pollinator richness, fruit and seed weight show the opposite relationship, indicating that this density-dependent effect might only be limiting fruit quantity and not fruit quality.
+Thus, taking into account the co-flowering plant species densities may be the next step [@Vanbergen2014].
+
+  In summary, our findings show that the analysis of natural communities of interacting species using network analysis not only represents an ideal way of visualizing and grasping the complexity present within these communities, but also represents a manner of mechanistically understanding differences observed across the reproductive success of individuals and/or species.
 Future studies could build on this body of research by focusing on the long-lasting effects of community structure for plant fitness, by evaluating the consequences of different community structures for heritability.
@@
 IB acknowledges funding from MSC-PCIG14-GA-2013-631653 BeeFun Project.
+We thank Doñana’s Singular Scientific-Technical Infrastructure (ICTS-RBD) for access to the park.
 
@@
 # coefs.m2 <- data.frame(coef(summary(m2)))
-# Table1<-round(coefs.m2[,1:3],digits=2)
-# rownames(Table1)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Centrality", "Niche overlap")
-
-kable(Table1, caption = "Table 1.
+# Table1A<-round(coefs.m2[,1:3],digits=2)
+# rownames(Table1A)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Centrality", "Niche overlap")
+
+kable(Table1A, caption = "Table 1A.
 Results of GLMM showing effect of simple visitation and community structure metrics on species-level fruitset based on best model selected.
@@
 
-# Table2<-round(coefs.m2.seed,digits=2)
-# rownames(Table2)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Centrality", "Niche overlap")
-
-kable(Table2, caption = "Table 2.
+# Table1B<-round(coefs.m2.seed,digits=2)
+# rownames(Table1B)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Centrality", "Niche overlap")
+
+kable(Table1B, caption = "Table 1B.
 Results of GLMM showing effect of simple visitation and community structure metrics on species-level number of seeds/fruit based on best model selected.
@@
 # #table with results for paper
-# Table3<-round(summary(m2.fruit.net)$coefficients$cond[,1:3], digits=2)
-# rownames(Table3)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Nestedness", "Niche complementarity")
-
-kable(Table3, caption = "Table 3. Results of GLM showing effect of simple visitation and community structure metrics on community-level average fruitset based on best model selected.")
+# Table2A<-round(summary(m2.fruit.net)$coefficients$cond[,1:3], digits=2)
+# rownames(Table2A)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Nestedness", "Niche complementarity")
+
+kable(Table2A, caption = "Table 2A. Results of GLM showing effect of simple visitation and community structure metrics on community-level average fruitset based on best model selected.")
 
@@
 # #save table with results for paper
-# Table4<-round(summary(m2.seed.net)$coefficients[,1:3], digits=2)
-# rownames(Table4)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Nestedness", "Niche complementarity")
-
-kable(Table4, caption = "Table 4.
+# Table2B<-round(summary(m2.seed.net)$coefficients[,1:3], digits=2)
+# rownames(Table2B)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Nestedness", "Niche complementarity")
+
+kable(Table2B, caption = "Table 2B.
 Results of GLM showing effect of simple visitation and community structure metrics on community-level average number of seeds per fruit based on best model selected.")
@@
 
-**Figure 1.** Map showing location of 16 study sites, green colors indicate different elevations. Inset shows location of study area within SW Spain.
+**Figure 1.** Map showing location of 16 study sites. Inset shows location of study area within SW Spain.
 
 **Figure 2**.
-Partial residual plots showing the effect of A) pollinator species diversity (approximated using normalized degree) and B) species centrality on fruitset for each of the plant species considered.
+Partial residual plot showing the effect of A) plant species centrality on fruit set for each of the plant species considered and B) plant niche overlap on average number of seeds per fruit.
 Dots represent each of the individuals sampled for each species within each site.
 
-**Figure 3.** Partial residual plot showing the effect of average niche overlap between plant species on the average number of seeds per fruit for each of the plant species considered.
-Dots represent each of the individuals sampled for each species within each site.
-
-**Figure 4.** Partial residual plots showing the effect of A) pollinator species diversity, B) total number of visits received and C) niche complementarity between pollinator species on community-level average fruitset.
-Dots represent average vaues of fruitset at the level of the community for all plant species considered (N=16 sites).
-
-**Figure 5.** Partial residual plots showing the effect of A) the total number of pollinator visits received at the community level and B) niche complementarity between pollinator species on the scaled average number of seeds per fruit at the community level.
-Dots represent average vaues of previously scaled values of the number of seeds per fruit at the level of the community for all plant species considered (N=16 sites).
-
-**Figure 6.** Partial residual plots showing the effect of pollinator species diversity on equity in reproductive success across species within a community (75% threshold).
+**Figure 3.** Partial residual plots showing the effect of A) pollinator species diversity, B) total number of visits received and C) niche complementarity between pollinator species on community-level average fruitset.
+Dots represent average values of fruitset at the level of the community for all plant species considered (N=16 sites).
+
+**Figure 4.** Partial residual plots showing the effect of A) the total number of pollinator visits received at the community level and B) niche complementarity between pollinator species on the scaled average number of seeds per fruit at the community level.
+Dots represent average values of previously scaled values of the number of seeds per fruit at the level of the community for all plant species considered (N=16 sites).
+
+**Figure 5.** Partial residual plots showing the effect of pollinator species diversity on equity in reproductive success across species within a community (75% threshold).
 Dots represent values for each site (N=16 sites).
@@
 
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=7, fig.width=9}
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=9}
 
 #FIGURE 2
-Figure2 <- plot_grid( prow, legend_b, ncol = 1, rel_heights = c(1, .2))
 Figure2
@@
    # save_plot("figures/Figure2.tiff", Figure2,
- #           base_height = 7, base_width = 9)
+   #           base_height = 6, base_width = 9)
 ```
@@
 
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5.5, fig.width=6}
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=3, fig.width=11}
 
@@
     # save_plot("figures/Figure3.tiff", Figure3,
-  #           base_height = 5.5, base_width = 6)
+    #           base_height = 3, base_width = 11)
 ```
@@
 
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=3, fig.width=11}
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=7}
 
@@
  # save_plot("figures/Figure4.tiff", Figure4,
-   #           base_height = 3, base_width = 11)
+ #              base_height = 4, base_width = 8)
 ```
@@
 
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=7}
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=3, fig.width=4}
 
@@
 Figure5
-
+# 
 # save_plot("figures/Figure5.tiff", Figure5,
-#              base_height = 4, base_width = 8)
+#              base_height = 5, base_width = 6)
 ```
 **Figure 5**
-
-\newpage
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=3, fig.width=4}
-
-#FIGURE 5
-Figure6
-# 
-# save_plot("figures/Figure6.tiff", Figure6,
-#              base_height = 5, base_width = 6)
-```
-**Figure 6**
 

### 2019-07-21 paper_round2.Rmd
changes following revision from PCI

@@
 ---
-title: Interaction network structure maximizes community-level plant reproduction success via niche complementarity
+title: Niche complementarity between pollinators increases plant reproductive success 
 author: "Magrach, A, Molina, FP, Bartomeus, I"
@@
 
-**Interaction network structure maximizes community-level plant reproduction success via niche complementarity**
+**Niche complementarity between pollinators increases plant reproductive success**
 
@@
 We find that, for prediction purposes, information on simple visitation metrics is sufficient.
-Contrastingly, a mechanistic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success, requires additional information on community structure, particularly that reflecting niche complementarity between pollinators.
+Contrastingly, a mechanistic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success, requires additional information on network structure, particularly that reflecting niche complementarity between pollinators.
+Specifically, we find a positive effect of increasing niche complementarity between pollinators on plant reproductive success.
 \nextpage
@@
 Yet plants and pollinators do not interact in isolation, but rather are embedded within larger networks of interactions encompassing other plant and pollinator species.
-We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect interactions between species within one guild (e.g., plants) through their shared resources [@Carvalheiro2014; @Lazaro2014; @Mayfield2017; @Pauw2013].
+We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect interactions between species within one guild (e.g., plants) through their shared resources [@Carvalheiro2014; @Lazaro2014; @Mayfield2017; @Pauw2013; @Johnson2019].
 Understanding how changes in pollinator diversity and interaction structure affect whole community assemblages is thus a major challenge that requires attention.
@@
   The few pollination studies that have analysed the effects of changing pollinator diversity for reproductive success at the community level have done so using mainly experimental setups.
-As an example, a study that experimentally recreated a plant community with 9 plant species and differing levels of pollinator diversity across different enclosures, found that not only pollinator species diversity had an effect for average reproductive success, but also they found that community structure had an important effect [@Frund2013].
+As an example, a study that experimentally recreated a plant community with 9 plant species and differing levels of pollinator diversity across different enclosures, found that not only pollinator species diversity had an effect for average reproductive success, but also they found that network structure had an important effect [@Frund2013].
 In particular, these authors found that niche complementarity between pollinators, in terms of plant species and temperature coverage (a measure of the overlap in the use of plant resources and optimum temperature activity) had a positive effect for average seed set at the community level [@Frund2013].
@@
 We are now at a point in which there is considerable understanding on the attributes characterizing mutualistic interaction networks [@Bascompte2007b] and we have a substantial understanding of how these attributes vary along different types of gradients [@Pellissier2017; @Tylianakis2016].
-Especially, in the case of pollination, we have ample knowledge on the attributes that shape these mutualistic interactions at the community level, such as a prevalence of nested structures [@Bascompte2003] or the presence of asymmetric specialization as a pervasive feature [@Vazquez2004].
+Especially, in the case of pollination, we have ample knowledge on the attributes that shape these mutualistic interactions at the community level.
+Amongst them is the prevalence of nested structures, i.e., arrangements where specialist species interact with a subset of the species that generalists interact with [@Bascompte2003] and which is thought to promote species diversity [@Bastolla2009]; or the presence of asymmetric specialization, i.e., specialists tend to interact with generalist species as a pervasive feature [@Vazquez2004].
 However, the pathways by which the structure of these networks of interactions affect key ecosystem functions such as plant reproduction remain to be understood [@Winfree2013].
-The time is thus ripe to use this knowledge to explore relationships between community structure and ecosystem functioning, with special emphasis being placed on the underlying mechanisms that drive these relationships.
-
-  Here, we present one of the first efforts linking pollinator visitation and plant reproductive success at the community level.
-To this end, we use a well-replicated dataset encompassing 16 well-resolved plant-pollinator interaction networks coupled with data on the reproductive success of 19 plant species recorded at Mediterranean shrub ecosystems within the area of influence of Doñana National Park in SW Spain.
-Our study focuses on understanding whether adding information on the structure of the community to previously used simple visitation metrics (e.g., the number and diversity of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success.
-In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success, and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success.
-In addition to average values, we also evaluate whether community structure helps us explain differences in equity in reproductive success across species within a community, as a measure of evenness in the pollination service delivered.
-
-  Our results suggest that for prediction purposes, information on simple visitation metrics, particularly regarding the diversity of pollinators that visit a plant species, is sufficient.
+The time is thus ripe to use the existing knowledge around plant-pollinator network structures to explore the relationship between network structure and ecosystem functioning, with special emphasis being placed on the underlying mechanisms that drive these relationships.
+
+  Here, we present one of the first efforts linking pollinator visitation and plant reproductive success at the community level using empirical data on plant-pollinator interaction networks and plant reproductive success.
+To this end, we use a well-replicated dataset encompassing 16 well-resolved plant-pollinator interaction networks coupled with data on the reproductive success of 19 plant species recorded in Mediterranean shrub ecosystems within the area of influence of Doñana National Park in SW Spain, i.e., within the limits of the Natural Space of Doñana as defined by the local government (Junta de Andalucía).
+Our study focuses on understanding whether adding information on network structure to previously used simple visitation metrics (e.g., the number and diversity of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success.
+In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success, and (ii) at the site level, by evaluating how attributes that describe the whole site might affect average values of reproductive success.
+Specifically, our study focuses on the how the interplay between niche complementarity and redundancy determines reproductive success.
+Plant reproductive success requires of the delivery of conspecific pollen and thus of a certain degree of niche complementarity.
+Yet, greater values of nestedness, which imply redundancy in species functions, are thought to promote species diversity [@Bastolla2009] and stability [@Thebault2010a] within plant-polllinator networks.
+At present, we do not know how either of these network characteristics affects the functions performed by pollinators.
+Finally, in addition to average values, we also evaluate whether network structure helps explain differences in equity in reproductive success across species within a community, as a measure of evenness in the pollination service delivered.
+
+  Our results suggest that for prediction purposes, information on simple visitation metrics, particularly regarding the pollinator richness visiting a plant species, is sufficient.
 However, we find that a mechanistic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success requires additional information on network structure, notably information on the complementarity between the functions performed and the niches occupied by different pollinator species.
 
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=9}
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE}
 
@@
 
-library(BeeFunData)
+library(BeeFunData)#this package holds all the necessary data
 library(plyr)
@@
 library(vegan)
+library(piecewiseSEM)
+library(MuMIn)
 
@@
 
-#calculate column with fruit set as
-
-#Fruit_Yes +  Fruit_Preyed + Fruit_Dispersed) / (Fruit_Yes + Fruit_No +Fruit_Preyed + Fruit_Dispersed) #Nacho this equation is wrong in your metadata!
-
 #1st eliminate frutos perdidos
@@
 
+#calculate column with fruit set as
 f2$tot.fruitset<-(f2$Fruit_Yes +  f2$Fruit_preyed + f2$Fruit_dispersed)/(f2$Fruit_Yes +f2$Fruit_No + f2$Fruit_preyed + f2$Fruit_dispersed)
@@
 s2<-subset(s, Notes %nin% wordList)
+
 #calculate average seed set per plant individual, there are several fruit measurements per plant and would lead to 3 nested random factors
@@
 Each site was surveyed 7 times during the flowering season of 2015 (from February to May) following a 100-m x 2 m transect for 30 mins.
-Along each transect, we identified all plant species and recorded all the flower visitors that legitimately visited them during each 30-min period.
-In addition, at each round we conducted 3 minutes of focal observations on 3 individuals per species belonging to the 19 most common species across the study area (`r round(mean(foc3$tot.species), digits=2)` $\pm$ `r round(sd(foc3$tot.species), digits=2)` species per site).
+Along each transect, we identified all plant species and recorded all the floral visitors that landed on their flowers during each 30-min period.
+Only floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FPM with the aid of experts in the different taxonomic groups (see acknowledgements).
+In addition, at each round we conducted 3 minutes of focal observations recording all floral visitors observed on 3 plant individuals per species belonging to the 19 most common (based on previous surveys) plant species across the study area (mean $\pm$ SD: `r round(mean(foc3$tot.species), digits=2)` $\pm$ `r round(sd(foc3$tot.species), digits=2)` species per site).
 Furthermore, we included some interactions between plant and pollinator individuals that were not observed during the sampling but that were opportunistically recorded immediately before or after the sampling periods, as some of these interactions are difficult to document and might be important to define network structure [@Jordano2016].
-Floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FPM with the aid of experts in the different taxonomic groups (see acknowledgements).
+These opportunistic interactions represented `r round(table(d$Out)[2]/(table(d$Out)[1]+table(d$Out)[2]+table(d$Out)[3])*100, digits=2)` of all interactions recorded.
 All surveys were done under similar weather conditions, avoiding windy or rainy days.
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=9}
+Surveys were done during mornings and afternoons with the sampling order being established randomly.
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE}
 
@@
 
-Within each site, we marked between 3 and `r max(f.inds$tot.inds)` individuals (`r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`) belonging to `r min(tableS1$tot.sps)` to `r max(tableS1$tot.sps)` plant species (`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`), depending on the availability and presence of flowers during the sampling events.
+Within each site, we marked between 3 and `r max(f.inds$tot.inds)` individuals (mean $\pm$ SD: `r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`) belonging to `r min(tableS1$tot.sps)` to `r max(tableS1$tot.sps)` plant species (mean $\pm$ SD:`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`), depending on the availability and presence of flowers during the sampling events.
 For each individual, at the end of the season, we
 recorded fruit set (i.e.
-the proportion of flowers that set fruit), the average number of seeds per fruit and the average seed weight per fruit (`r min(s.fruitnum$tot.fruits)`-`r max(s.fruitnum$tot.fruits)` fruits subsampled, mean = `r round(mean(s.fruitnum$tot.fruits), digits=2)` $\pm$ `r round(sd(s.fruitnum$tot.fruits), digits=2)`).
+the proportion of flowers that set fruit), the average number of seeds per fruit and the average fruit and seed weight per fruit (`r min(s.fruitnum$tot.fruits)`-`r max(s.fruitnum$tot.fruits)` fruits subsampled, mean $\pm$ SD: `r round(mean(s.fruitnum$tot.fruits), digits=2)` $\pm$ `r round(sd(s.fruitnum$tot.fruits), digits=2)`).
 Our survey included a total of `r nlevels(f2$Plant.sp)` different plant species across our `r nlevels(f2$Site_ID)` sites.
+Plants species were selected based on their availability with sampling being focused on the most abundant plant species.
+The values at the species level were then averaged per site to calculate unique reproductive success measures at the site level.
 
@@
 
-In order to evaluate the completeness of our sampling of the pollinator and plant community as well as that of their interactions, we estimated the asymptotic number of species present, including non-detected species, and calculated the proportion detected with our original sampling data.
+In order to evaluate the completeness of our sampling of the pollinator and plant community as well as that of their interactions, we estimated the asymptotic number of species present, a non-parametric estimator of species richness for abundance data.
+This estimator includes non-detected species, and allowed us to calculate the proportion detected with our original sampling data.
 We used Chao 1 asymptotic species richness estimators [@Chao2009] and estimated the richness of pollinators, plants and plant–pollinator links accumulated as sampling effort increased up to 100% sampling coverage using package iNEXT [@Hsieh2016] within the R environment [@RDevelopmentCoreTeam2011].
@@
 
-  In order to analyse how differences in community structure might affect plant reproductive success, we constructed weighted plant-pollinator interaction networks by pooling the data for the 7 rounds of sampling.
+  In order to analyse how differences in network structure might affect plant reproductive success, we constructed weighted plant-pollinator interaction networks by pooling the data for the 7 rounds of sampling.
 We thus obtained one weighted interaction network per site, representing the frequency of visits by different pollinator species to different plant species.
-For each network, we then proceeded to extract a series of relevant network metrics at the species and community levels.
+For each network, we then proceeded to extract a series of relevant network metrics at the species and site levels.
 
@@
 At the species level, we focused on attributes defining the position of a focal plant species within the larger community.
-As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap in terms of pollinators between a focal plant species and other plant species in the community, which covers the potential indirect interactions between different plant species through shared resources (in this case pollinators), and (ii) centrality, which depicts the importance of the role played by a plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness.
- Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the Morisita index [@Zhang2016].
+As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap in terms of pollinators between a focal plant species and each of the other plant species in the community, which estimates the potential indirect interactions between different plant species through shared resources (in this case pollinators), and (ii) centrality, which depicts the importance of the role played by a plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness.
+ Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the Morisita overlap index, a measure of similarity between two sets of data [@Zhang2016].
 As a measure of centrality we used weighted closeness centrality, which represents the number of shortest paths going through a focal plant based on a unipartite projection of the bipartite plant-pollinator network using a weighted representation of the network [@Dormann2009].
@@
 
-_Community-level network analysis_
-
-At the community level, we followed the same logic as the one presented at the species level.
+_Site-level network analysis_
+
+At the site level, we followed the same logic as the one presented at the species level.
 Thus, we also calculated two network metrics providing complementary non-redundant information.
@@
 (2017) by using a normalized value of the widely-used nestedness metric NODF [@Almeida-Neto2011], $NODF_c$.
-This normalized value is calculated as $NODF_c = NODF_n/(C * log(S))$, where C is connectance, S is network size and $NODF_n = NODF/max(NODF)$, which is independent of network size and thus comparable across different networks [@Song2017].
+This normalized value is calculated as $NODF_c = NODF_n/(C * log(S))$, where C is connectance and S is network size.
+$NODF_n$ is calculated as $NODF/max(NODF)$, which is independent of network size and thus comparable across different networks [@Song2017].
 
@@
 
-In order to evaluate whether adding information on community structure improves our ability to explain differences in reproductive success - both at the species and the community level - we used general linear (GLMs) and general linear mixed models (GLMMs).
-In both cases (species and community-level models) we fit two types of models: (i) model 1, that only included simple visitation metrics and (ii) model 2 that additionally included information on community structure.
-All response variables were previously scaled for each species to allow meaningful comparisons across species with contrasting life histories.
-
-  At the species level, model 1 included as explanatory variables the diversity of pollinator species visiting a focal plant (i.e.
-pollinator richness), and the total number of visits received by that plant species; while model 2 added the two network attributes calculated at the species level: average niche overlap and centrality.
-In this case, we included plant species nested within site as a random effect to account for the non-independence of several individuals measured for the same plant species within each site.
-Response variables included fruit set for different individuals of each species analyzed using a binomial distribution, the average number of seeds per fruit analyzed using a normal distribution and the average values per species of fruit and seed weight fitted to poisson distributions.
-
-  At the community level, we upscaled our species-level analyses.
-In this case, model 1 included total pollinator richness and total pollinator abundance (i.e., the number of visits received by all plants within the community) as explanatory variables.
-Model 2, in turn, added information on community structure by including nestedness and niche complementarity as explanatory variables.
-As response variable we had the average reproductive success for the whole community (i.e., average fruit set analyzed using a binomial distribution, average number of seeds per fruit and average fruit and seed weight using a normal distribution).
-All metrics were previously scaled for each species to allow meaningful comparisons across species with contrasting life histories.
+In order to evaluate whether adding information on network structure improves our ability to explain differences in reproductive success - both at the species and the site level - we used generalized linear (GLMs) and generalized linear mixed models (GLMMs).
+In both cases (species and site-level models) we fit two types of models: (i) model 1, that only included simple visitation metrics and (ii) model 2 that additionally included information on network structure.
+
+  At the species level, response variables included the fruit set for different individuals of each species, analyzed using a binomial distribution, the average number of seeds per fruit, analyzed using a normal distribution, and the average values of fruit and seed weight fitted to Poisson distributions.
+The number of seeds per fruit was centered and scaled (i.e., we subtracted column means and divided by standard deviation) to allow meaningful comparisons across species with contrasting life histories.
+As explanatory variables, model 1 included pollinator richness, and the total number of visits received by that plant species; while model 2 added the two network attributes calculated at the species level: average niche overlap and centrality.
+For both models, we included plant species nested within site as a random effect to account for the non-independence of several individuals measured for the same plant species within each site.
+
+	At the site level, we upscaled our species-level analyses.
+As response variable we had the average reproductive success per site (i.e., average fruit set analyzed using a binomial distribution, average number of seeds per fruit and average fruit and seed weight using a normal distribution).
 We thus had a single value per site and no random effects are needed in this case.
-
-  Average values of reproductive success at the community level can be driven to a large extent by a single plant species.
+In this case, model 1 included total pollinator richness and total pollinator abundance (i.e.
+number of visits received by all plants within the community) as explanatory variables.
+Model 2, in turn, added information on network structure by including nestedness and niche complementarity as explanatory variables.
+
+  Average values of reproductive success at the site level can be driven to a large extent by a single plant species.
 Yet, what will determine the persistence of a diverse plant community, is the presence of some sort of “equity” or evenness in reproductive success across the whole community.
-We therefore calculated a measure of equity in reproductive success at the community level as the proportion of species within a community with normalized (between 0 and 1) average fruit set values that were above 0.5.
+We therefore calculated a measure of equity in reproductive success at the site level as the proportion of species with normalized (between 0 and 1) average fruit set values that were above 0.5.
 We repeated this using 0.25 and 0.75 thresholds.
-We then used the same framework as that used for species and community-level analyses and fit the same models 1 and 2 GLMs, but using equity in reproductive success as the response variable fitting a binomial distribution.
-In all cases, we used information criterion methods to find the best model and selected the ones with the lowest Akaike Information Criterion (AIC) value.
+We then used the same framework as that used for species and site-level analyses and fit the same models 1 and 2 GLMs, but using equity in reproductive success as the response variable fitting a binomial distribution.
+In all cases, we used variance inflation factors to check for collinearity between explanatory variables.
+Additionally, we ran residual diagnostics to check if model assumptions were met.
+Then, we used information criterion methods to find the best model and selected the ones with the lowest Akaike Information Criterion (AIC) value.
 Whenever the difference between the AIC of both models was < 2 ($\Delta AIC<2$), we considered that both models were equally good [@Burnham2011].
@@
 
-  Finally, we tested whether the importance of community structure in explaining differences in equity in reproductive success within communities increases with the number of plant species being considered.
-We expect that when only one plant species is considered, then the importance of community structure will be negligible, while we expect this importance to increase as more plant species are considered (up to a maximum number of 6 species which is the maximum we have measured in our study at a particular site).
+  Finally, we tested whether the importance of network structure in explaining differences in equity in reproductive success within communities increases with the number of plant species being considered.
+We expect that when only one plant species is considered, then the importance of network structure will be negligible, while we expect this importance to increase as more plant species are considered (up to a maximum number of 6 species which is the maximum we have measured in our study at a particular site).
 
   To test this, we ran a simple simulation in which the number of species considered increased at each step and for each step we re-calculated equity in reproductive success.
-Instead of drawing plant species randomly for each step, we tested all possible combinations for each plant number level and network, as the number of combinations is low (e.g.
+Instead of drawing plant species randomly for each step, we tested all possible combinations for each plant number level and network, as the number of combinations is small (e.g.
 for n = 3 plant selected out of 6 there is only 20 possible combinations).
@@
 
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=9}
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE}
 
@@
  d$order<-tr$order[match(d$Pollinator_gen_sp, tr$Pollinator_gen_sp)]
- d.order<- aggregate(Frequency ~ order, d, sum)
+ d.order<- aggregate(Frequency ~ order, d, FUN= "sum")
  d.order$prop<-d.order$Frequency/sum(d.order$Frequency)
@@
 
-Within our sampling we recorded `r nrow(d)` pollinator individuals belonging to `r nlevels(unique(d$Plant_gen_sp))` species of plants and `r nlevels(unique(d$Pollinator_gen_sp))` species of pollinators.
-Within the pollinator community the distribution in different orders was: `r round(d.order$prop[d.order$order=="Hymenoptera"]*100, digits=2)`% Hymenoptera, `r round(d.order$prop[d.order$order=="Diptera"]*100, digits=2)`% Diptera, `r round(d.order$prop[d.order$order=="Coleoptera"]*100, digits=2)`% Coleoptera and `r round(d.order$prop[d.order$order=="Lepidoptera"]*100, digits=2)`% Lepidoptera.
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+Within our sampling we recorded `r nrow(d)` plant-pollinator interactions involving `r nlevels(unique(d$Pollinator_gen_sp))` pollinator species and `r nlevels(unique(d$Plant_gen_sp))` plant species.
+Within the pollinator community the distribution of individuals in different orders was: `r round(d.order$prop[d.order$order=="Hymenoptera"]*100, digits=2)`% Hymenoptera, `r round(d.order$prop[d.order$order=="Diptera"]*100, digits=2)`% Diptera, `r round(d.order$prop[d.order$order=="Coleoptera"]*100, digits=2)`% Coleoptera and `r round(d.order$prop[d.order$order=="Lepidoptera"]*100, digits=2)`% Lepidoptera.
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE}
 
@@
 
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE}
 
@@
 f2$functional.comp.poll<-out.site$functional.comp.poll[match(f2$Site_ID, out.site$Site_id)]
+f2$functional.comp.pl<-out.site$functional.comp.pl[match(f2$Site_ID, out.site$Site_id)]
 f2$nodf.song<-out.site$nodf.song[match(f2$Site_ID, out.site$Site_id)]
@@
 f2$functional.comp.poll.sc<-scale(f2$functional.comp.poll, center = T, scale = T)
+f2$functional.comp.pl.sc<-scale(f2$functional.comp.pl, center = T, scale = T)
 f2$nodf.song.sc<-scale(f2$nodf.song, center = T, scale = T)
@@
 f2$pollspsperplant.sc<-scale(f2$pollspsperplant, center = T, scale = T)
-
-#scale total visits per plant species
-f2_scaled <- f2 %>% group_by(Plant.sp) %>% mutate(tot.visits.sc = scale(tot.visits, center = T, scale = T), na.rm=TRUE)
+f2$tot.visits.sc<-scale(f2$tot.visits, center = T, scale = T)
+
 ```
@@
 
-At the species level, in the case of fruitset, our results show that model 2 is the best model explaining the variability observed.
-In this case, we find a positive effect of a simple visitation metric, pollinator species diversity (measured using the species´normalised degree, Fig.
-2) as well as a positive effect of a community structure metric, the centrality of the focal plant on its fruit set (Table 1A, Fig.
-2A).
-
 ```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
 
-#compare 2 models: one with degree, i.e. diversity of partners, and number of visits, compared to one where position in a network (centrality) and niche overlap are included with these variables.
-
-m1<-glmer(tot.fruitset ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2_scaled)
+#compare 2 models: one with simple diversity metrics (pollinator richness and number of visits), compared to one where position in a network (centrality) and niche overlap are included with these variables.
+
+m1<-glmer(tot.fruitset ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2)
 
@@
 
-m2<-glmer(tot.fruitset ~  pollspsperplant.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2_scaled)
-
-summary(m2) #norm degree and weigh closeness have intervals not overlapping 0
+m2<-glmer(tot.fruitset ~  pollspsperplant.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2)
+
+summary(m2) 
 vif(m2)
@@
 
-AICtab(m1, m2) #M2 is best!!
-
-#test for problems in residuals
-
-# res<-simulateResiduals(m1)
-# plot(res, rank = TRUE)
+AICtab(m1, m2)
+
+r2<-rsquared(c(m2, m1)) #check R^2 values for both models
 
@@
 Table1A<-round(coefs.m2[,1:3],digits=2)
-rownames(Table1A)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Centrality", "Niche overlap")
+rownames(Table1A)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Centrality", "Niche overlap")
 #at the end of the paper
 
-#both models equally good, plot significant variables, in this case centrality, do partial residual plots to show the effect of that variable in isolation of the others
+#plot significant variables, in this case centrality, do partial residual plots to show the effect of that variable in isolation of the others
 
@@
   theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.3), face="bold")) + 
-  scale_fill_discrete(name="Plant species") +  theme(legend.text = element_text(size = 6, face = "italic"), legend.title = element_text(size=11, face = "bold"), legend.direction = "horizontal")
+  scale_fill_discrete(name="Plant species") +  theme(legend.text = element_text(size = 14, face = "italic"), legend.title = element_text(size=15, face = "bold"), legend.direction = "vertical") + guides(fill=guide_legend(ncol=4))
 
@@
 
+At the species level, in the case of fruit set, our results show that model 2 shows the best fit to our data (lowest AIC value), explaining `r round(r2$Conditional[1], 2)*100`% of the variability observed.
+In this case, we find a positive effect of a network structure metric, the centrality of a focal plant within the overall network on its fruit set (Table 1, Fig.
+2A).
+
 ```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
-##ahora con seed set
+
+##seed set
 
 s3$functional.comp.poll<-out.site$functional.comp.poll[match(s3$Site_ID, out.site$Site_id)]
+s3$functional.comp.pl<-out.site$functional.comp.pl[match(s3$Site_ID, out.site$Site_id)]
 s3$nodf.song<-out.site$nodf.song[match(s3$Site_ID, out.site$Site_id)]
@@
 s3$functional.comp.poll.sc<-scale(s3$functional.comp.poll, center = T, scale = T)
+s3$functional.comp.pl.sc<-scale(s3$functional.comp.pl, center = T, scale = T)
 s3$nodf.song.sc<-scale(s3$nodf.song, center = T, scale = T)
@@
 s3$pollspsperplant.sc<-scale(s3$pollspsperplant, center = T, scale = T)
-
-#scale total visits per plant species
-library(dplyr)
-s3_scaled <- s3 %>% group_by(Plant.sp) %>% mutate(tot.visits.sc = scale(tot.visits, center = T, scale = T))
-
-s4_scaled <- s3_scaled %>% group_by(Plant.sp) %>% mutate(mean.seedn.sc = scale(mean.seedn, center = T, scale = T))
-
-```
-
- For the number of seeds per fruit, our results show again that model 2 is the best model. In this case, we find a positive effect of the niche overlap between plant species (Table 1B, Fig. 2B).
+s3$tot.visits.sc<-scale(s3$tot.visits, center = T, scale = T)
+
+s3$mean.seedn.sc<-scale(s3$mean.seedn, center = T, scale = T)
+
+```
 
@@
 
-m1.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s4_scaled)
+m1.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3)
 
@@
 
-m2.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s4_scaled)
+m2.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3)
 
@@
 
+r2b<-rsquared(c(m2.seed, m1.seed)) #check R^2 values for both models
+
 #test for problems in residuals
-# res<-simulateResiduals(m1.seed)
+# res<-simulateResiduals(m2.seed)
 # plot(res, rank = TRUE)
@@
 Table1B<-round(coefs.m2.seed,digits=2)
-rownames(Table1B)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Centrality", "Niche overlap")
+rownames(Table1B)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Centrality", "Niche overlap")
 
 #plot significant variables
-y_partial_norm_seed <- remef(m2.seed, fix= c("pollspsperplant.sc", "tot.visits.sc", "weigh_closeness.sc"), ran = "all", inverse = F)
+y_partial_norm_seed <- remef(m2.seed, fix= c("pollspsperplant.sc", "tot.visits.sc", "weigh_closeness.sc"), ran = "all")
 #With this we remove the influece of x2 and the random effects from the dependent variable
-y_partial_norm_seed_inv<-exp(y_partial_norm_seed)/(1+exp(y_partial_norm_seed))
-#then we use this new variable to plot. We use m1@frame as dataset because not all observations are used in modeldue to presence of NAs
-
-Figure2b<-ggplot(m2.seed@frame,  aes(x=m2.seed@frame$niche.overlap.sc, y=y_partial_norm_seed_inv, color= Plant.sp)) +    
+
+Figure2b<-ggplot(m2.seed@frame,  aes(x=m2.seed@frame$niche.overlap.sc, y=y_partial_norm_seed, color= Plant.sp)) +    
   geom_point(size=2.5, shape=21, colour="black", aes(fill=factor(Plant.sp))) + stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
@@
   xlab("Niche overlap") +      
-  ylab("Average seeds/fruit") + theme_bw()  + theme (legend.position= "right") +
+  ylab("Number of \n seeds per fruit") + theme_bw()  + theme (legend.position= "right") +
   theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.3), face="bold")) + 
@@
 # extract the legend from one of the plots
-legend_b <- get_legend(Figure2a + theme(legend.position="bottom"))
+legend_b <- get_legend(Figure2a + theme(legend.position="right"))
 
@@
 # of one plot (via rel_heights).
-Figure2 <- plot_grid( prow, legend_b, ncol = 1, rel_heights = c(1, .2))#al final del paper
-
-```
-
-  For all other measures of reproductive success considered (i.e., fruit and seed weight), the best model based on its AIC value was model 1, i.e., the model that only included simple visitation metrics (in this case, pollinator species diversity and the total number of visits received by a focal plant species).
-However, none of the variables included within our model explain the differences observed (Tables S4-S5).
+Figure2 <- plot_grid( prow, legend_b, ncol = 1, rel_heights = c(2, 1))#al final del paper
+
+```
+
+ For the average number of seeds per fruit, our results show again that model 2 shows the best fit, explaining `r round(r2b$Conditional[1], 2)*100`% of the variability observed in our data.
+In this case, we find a positive effect of the niche overlap between plant species on the number of seeds produced (Table 1B, Fig.
+2B).
 
@@
 
-m1.seed.w<-glmmTMB(mean.seedw ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3_scaled)
+m1.seed.w<-glmmTMB(mean.seedw ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3)
 
@@
 
-m2.seed.w<-glmmTMB(mean.seedw ~  pollspsperplant.sc + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3_scaled)
+m2.seed.w<-glmmTMB(mean.seedw ~  pollspsperplant.sc + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3)
 
@@
 AICtab(m1.seed.w, m2.seed.w)
-
-#test for problems in residuals
-# res<-simulateResiduals(m1.seed.w)
-# plot(res, rank = TRUE)
 
@@
 tableS4<-round(summary(m1.seed.w)$coefficients$cond[,1:3], digits=2)
-rownames(tableS4)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")
+rownames(tableS4)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
 
@@
 
-m1.fruit.w<-glmmTMB(mean.fruitweight ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3_scaled)
+m1.fruit.w<-glmmTMB(mean.fruitweight ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="poisson", data=s3)
 
@@
 
-m2.fruit.w<-glmmTMB(mean.fruitweight ~  pollspsperplant.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3_scaled)
+m2.fruit.w<-glmmTMB(mean.fruitweight ~  pollspsperplant.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="poisson", data=s3)
 
@@
 
-#test for problems in residuals
-# res<-simulateResiduals(m1.fruit.w)
-# plot(res, rank = TRUE)
-
 # extract coefficients and p-values for m1 and present them in paper
-tableS5<-round(summary(m1.fruit.w)$coefficients$cond[,1:3], digits=2)
-rownames(tableS5)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")
-
-```
-
-_Community-level analyses_
+tableS5<-round(summary(m2.fruit.w)$coefficients$cond[,1:3], digits=2)
+rownames(tableS5)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Centrality", "Niche overlap")
+
+```
+ For all other measures of reproductive success considered (i.e., fruit and seed weight), both models had very similar fits, with ($\Delta AIC=2.2$) and 2, respectively.
+However, none of the variables included within our model explain the differences observed (Tables S4-S5).
+
+_Site-level analyses_
 
@@
 
-######################## NTW STRUCTURE ~ ECOSYSTEM FUNCTION
-
-#this is how i did originally, average of everything together, now following Nacho´s advice changing to mean of means previously calculated per sps
-
-f.agg.prev <- ddply(f2, c("Site_ID", "nodf.song", "functional.comp.poll", "species.poll"), 
+######################## NTW STRUCTURE
+
+#aggregate values at site level
+
+f.ag <- ddply(f2, c("Site_ID", "Plant.sp", "nodf.song", "functional.comp.poll",
+                    "functional.comp.pl", "species.poll"), 
                summarise, tot.visits    = sum(tot.visits),
@@
 
-#I see what you mean, no weghting for plant species... maybe is good doing it... mean on means? I don't think it will change much the result.
-#Doing mean of means here, it does change some values a bit!!
-f.ag <- ddply(f2, c("Site_ID", "Plant.sp", "nodf.song", "functional.comp.poll", "species.poll"), 
-               summarise, tot.visits    = sum(tot.visits),
-                         mean.fruitset = mean(tot.fruitset))
-
-f.agg <- ddply(f.ag, c("Site_ID",  "nodf.song", "functional.comp.poll", "species.poll"), 
+f.agg <- ddply(f.ag, c("Site_ID",  "nodf.song", "functional.comp.poll", 
+                       "functional.comp.pl","species.poll"), 
                summarise, tot.visits    = sum(tot.visits),
@@
 f.agg$functional.comp.poll.sc <- scale(f.agg$functional.comp.poll, center = T, scale = T)
+f.agg$functional.comp.pl.sc <- scale(f.agg$functional.comp.pl, center = T, scale = T)
 f.agg$species.poll.sc <- scale(f.agg$species.poll, center = T, scale = T)
@@
 
-At the community level, we find different patterns for fruit set and the number of seeds per fruit as compared to those for fruit and seed weight.
-In the case of fruit set and the number of seeds per fruit, we find that both model 1 and 2 are equally good in describing the differences observed (i.e.,$\Delta AIC<2$).
-Because this suggests model 2 is a good model despite its added complexity, we will comment results for this model only.
-In particular, we find that both fruit set and the number of seeds per fruit are positively related to niche complementarity between pollinators (Tables 2, Figs.
-3-4).
-Additionally, we find a negative effect of community-level pollinator species diversity and the total number of visits on average fruit set (Table 2A, Fig.
-3), while the total number of visits positively affected the average number of seeds per fruit (Table 2B, Fig.
-4).
-The number of visits for one of the sites was particularly large, yet this did not affect our results as removing this site from the analysis showed the same effect.
-
 ```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
 
-#average FRUITset
+#FRUITset
 
@@
 
+#removing one point with large number of visits to see if this is driving the effect of total number of visits (non-overlapping confidence intervals)
+
+novis<-subset(f.agg, f.agg$tot.visits.sc<2)
+
+ m2.fruit.novis<-glmmTMB(mean.fruitset ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="beta_family", data=novis)
+
+summary(m2.fruit.novis) #still non-overlapping values
+
 #select best model based on AIC
@@
 AICtab(m1.fruit.net, m2.fruit.net) #Almost as good.
-The take home message would be.
-If interested in predictions, go for simplicity.
-If interested in mechanisms, nich part is a mechanism to take into account.
-
-#test for problems in residuals
-# res<-simulateResiduals(m2.fruit.net)
-# plot(res, rank = TRUE)
-
-#when changing values to mean of means actually model2 is best and funct compl is significant!!
+With this, you cannot say one is better than the other one.
+The take home message would be: if interested in predictions, go for simplicity.
+If interested in mechanisms, niche part is a mechanism to take into account.
+And actually m2 has better predictive ability (better R2 see below)
+
+#provide R^2 values for both models
+
+#crude alternative suggested by Ben Bolker to calculate R2 for glmmTMb models https://github.com/glmmTMB/glmmTMB/issues/169
+
+r2.m2<-cor(f.agg$mean.fruitset,predict(m2.fruit.net,type="response"))^2
+r2.m1<-cor(f.agg$mean.fruitset,predict(m1.fruit.net,type="response"))^2
 
@@
 Table2A<-round(summary(m2.fruit.net)$coefficients$cond, digits=2)
-rownames(Table2A)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Nestedness", "Niche complementarity")
+rownames(Table2A)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Nestedness", "Niche complementarity")
 #at the end of paper
 
-#TRYING TO MANUALLY CREATE PARTIAL RESIDUAL PLOTS
+#MANUALLY CREATing PARTIAL RESIDUAL PLOTS
 
@@
   stat_smooth(method = 'lm', size=1, se=TRUE, color = "black", alpha=0.4) +     
+        ylim(0.3,0.9) +
         xlab("Niche complementarity") +      
-        ylab(" ") + theme_bw()  + #theme (legend.position= "none") +
+        ylab("Fruit set") + theme_bw()  + #theme (legend.position= "none") +
         theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
@@
   stat_smooth(method = 'lm', size=1, se=TRUE, color = "black", alpha=0.4) +  
-        xlab("Pollinator sps diversity") +      
+        ylim(0.3,0.9) +
+        xlab("Pollinator richness") +      
         ylab("Fruit set") + theme_bw()  + #theme (legend.position= "none") +
@@
   stat_smooth(method = 'lm', size=1, se=TRUE, color = "black", alpha=0.4) +
+        ylim(0.3,0.9) +
         xlab("Total number of visits") +      
-        ylab(" ") + theme_bw()  + #theme (legend.position= "none") +
+        ylab("Fruit set") + theme_bw()  + #theme (legend.position= "none") +
         theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
 
-#test for problems in residuals
-# res<-simulateResiduals(m2.fruit.net)
-# plot(res, rank = TRUE)
-
-Figure3<-plot_grid(pl3, pl4, pl2, labels = c("A", "B", "C"), nrow=1) #al final del paper
-
 ```
@@
 #seed number
-#How mean seed number is calculated?? scaled first would be better, right? Yes using scaled values
-
-#same as before now averaging per species first and then per site
-
-s.comm.prev <- ddply(s4_scaled, c("Site_ID", "nodf.song", "functional.comp.poll", "species.poll"), summarise, tot.visits    = sum(tot.visits),
-                         mean.seedset = mean(mean.seedn),
-                          mean.seedweight = mean(mean.seedw),
-                          mean.fruitweight = mean(mean.fruitweight))
-
-#mean of means!
-
-s.com <- ddply(s4_scaled, c("Site_ID", "Plant.sp", "nodf.song", "functional.comp.poll", "species.poll"), 
+
+s.com <- ddply(s3, c("Site_ID", "Plant.sp", "nodf.song", "functional.comp.poll",
+                     "functional.comp.pl", "species.poll"), 
                summarise, tot.visits    = sum(tot.visits),
@@
 
-s.comm <- ddply(s.com, c("Site_ID", "nodf.song", "functional.comp.poll", "species.poll"), 
+s.comm <- ddply(s.com, c("Site_ID", "nodf.song", "functional.comp.poll", 
+                         "functional.comp.pl","species.poll"), 
                summarise, tot.visits    = sum(tot.visits),
@@
 s.comm$functional.comp.poll.sc <- scale(s.comm$functional.comp.poll, center = T, scale = T)
+s.comm$functional.comp.pl.sc <- scale(s.comm$functional.comp.pl, center = T, scale = T)
 s.comm$species.poll.sc <- scale(s.comm$species.poll, center = T, scale = T)
@@
 
-#average seed set
+#NUMBER OF SEEDS PER FRUIT
 
@@
 
+#provide R^2 values for both models
+
+#crude alternative suggested by Ben Bolker to calculate R2 for glmmTMb models https://github.com/glmmTMB/glmmTMB/issues/169
+
+r2.m2.seed<-cor(s.comm$mean.seedset,predict(m2.seed.net,type="response"))^2
+r2.m1.seed<-cor(s.comm$mean.seedset,predict(m1.seed.net,type="response"))^2
+
 #save table with results for paper
 Table2B<-round(summary(m2.seed.net)$coefficients[,1:3], digits=2)
-rownames(Table2B)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Nestedness", "Niche complementarity") #end of paper
-
-pl5<-ggplot(s.comm,  aes(x=tot.visits.sc, y=mean.seedset))+      
-       geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
-        #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
-        xlab("Total number of visits") +      
-        ylab("Average seeds/fruit") + theme_bw()  + 
-  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
-
-#pl5
+rownames(Table2B)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Nestedness", "Niche complementarity") #end of paper
 
@@
         xlab("Niche complementarity") +      
-        ylab(" ") + theme_bw()  + #theme (legend.position= "none") +
+        ylab("Number of \n seeds per fruit") + theme_bw()  + #theme (legend.position= "none") +
         theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
@@
 
-Figure4<-plot_grid(pl5, pl6, labels = c("A", "B")) 
-```
-
-  Contrastingly, in the case of weight variables (fruit and seed weight), in both cases we find that the best model is model 1, i.e., that only including simple visitation metrics.
-Here, we find a consistent positive effect of community-level pollinator diversity for both weight descriptors (Tables S6-S7, Figs.
-S2-S3).
+Figure3<-plot_grid(pl3, pl4, pl2, pl6, labels = c("A", "B", "C", "D"), nrow=2)  
+```
+
+At the site level, we find different patterns for fruit set and the number of seeds per fruit as compared to those for fruit and seed weight.
+In the case of fruit set and the number of seeds per fruit, we find that both model 1 and 2 are equally good in describing the differences observed (i.e.,$\Delta AIC<2$), and thus we are not able to choose one over the other [@Burnham2002].
+This suggests model 2 is a good model despite its added complexity, and actually shows a better predictive ability than model 1 (R^2 = `r round(r2.m2, 2)` for model 2 versus `r round(r2.m1, 2)` for model 1 in the case of fruit set and R^2 = `r round(r2.m2.seed,2)` for model 2 versus `r round(r2.m1.seed, 2)` for model 1 in the case of the number of seeds per fruit) and therefore we will comment results for this model only.
+In particular, we find that both fruit set and the number of seeds per fruit are positively related to niche complementarity between pollinators (Tables 2, Fig.
+3).
+Additionally, we find a negative effect of site-level pollinator richness and the total number of visits on average fruit set (Table 2A, Fig.
+3).
+The number of visits for one of the sites was particularly large, yet this did not affect our results as removing this site from the analysis showed the same effect (Estimate $\pm$ SE = `r round(summary(m2.fruit.novis$sdr)[3], 2)` $\pm$ `r round(summary(m2.fruit.novis$sdr)[9], 2)`).
 
@@
 
-#fruit weight
+#FRUIT WEIGHT
 
@@
 
+r2.fruitw1<-r.squaredGLMM(m1.fruitw.net)
+r2.fruitw2<-r.squaredGLMM(m2.fruitw.net)
+
 #save table with results for paper
@@
 
+predtest<-summary(m1.fruitw.net)$coefficients[1]+ (summary(m1.fruitw.net)$coefficients[2] * s.comm$species.poll.sc) + (summary(m1.fruitw.net)$coefficients[3] * mean(s.comm$tot.visits.sc))
+
+restest<-predtest-s.comm$mean.fruitweight
+
+pltest <- ggplot(s.comm,  aes(x=species.poll.sc, y= restest)) +    
+  geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
+  stat_smooth(method = 'lm', size=1, se=TRUE, color = "black", alpha=0.4) +
+  #ylim(0.3,0.9) +
+  xlab("Pollinator richness") +      
+  ylab("Fruit weight (g)") + theme_bw()  + #theme (legend.position= "none") +
+  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
+
 # crPlots(m1.fruitw.net, smooth=FALSE, terms = ~  species.poll.sc, main = "", ylab = "Mean fruit weight", col.lines= "black", pch=19, col= "black", bg = "darkgrey", cex=2, cex.axis=1.2, cex.lab=1.5, 
@@
 ```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
-#seed weight
+
+#SEED WEIGHT
 
@@
 
+r2.seedw1<-r.squaredGLMM(m1.seedw.net)
+r2.seedw2<-r.squaredGLMM(m2.seedw.net)
+
 #save table with results for paper
@@
 
+predtest2<-summary(m1.seedw.net)$coefficients[1]+ (summary(m1.seedw.net)$coefficients[2] * s.comm$species.poll.sc) + (summary(m1.seedw.net)$coefficients[3] * mean(s.comm$tot.visits.sc))
+
+restest2<-predtest2-s.comm$mean.seedweight
+
+pltest2 <- ggplot(s.comm,  aes(x=species.poll.sc, y= restest2)) +    
+  geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
+  stat_smooth(method = 'glm', size=1, se=TRUE, color = "black", alpha=0.4) +
+  #ylim(0.3,0.9) +
+  xlab("Pollinator richness") +      
+  ylab("Seed weight (g)") + theme_bw()  + #theme (legend.position= "none") +
+  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
+
 # crPlots(m1.seedw.net, smooth=FALSE,  main = "", ylab = "Mean seed weight", col.lines= "black", pch=19, col= "black", bg = "darkgrey", cex=2, cex.axis=1.2, cex.lab=1.5)
@@
 
+  Contrastingly, in the case of weight variables (fruit and seed weight), in both cases we find that the best model is model 1, i.e., that only including simple visitation metrics (R^2 = `r round(r2.fruitw1[2], 2)` in the case of fruit weight and `r round(r2.seedw1[2], 2)` in the case of seed weight).
+Here, we find a consistent positive effect of site-level pollinator richness for both weight descriptors (Tables S6-S7, Fig.
+4).
+
 _Equity in fruitset_
 
-When evaluating the effect of differences in community composition and structure for equity in reproductive success across the different species within a community we find that model 1 is the best model for all the thresholds considered (0.50, 0.25 and 0.75).
-However, we also find a significant negative relationship between equity and pollinator species diversity using the 0.75 threshold (Fig.
-5, Tables S8, S9, S10).
+When evaluating the effect of differences in community composition and network structure for equity in reproductive success across the different species within a community we find that model 1 is the best model for all the thresholds considered (0.50, 0.25 and 0.75).
+Also, we find a significant negative relationship between equity and pollinator richness using the 0.75 threshold (Fig.
+4C, Tables S8, S9, S10).
 
@@
 tableS8<-round(summary(m1.eq.comm)$coef[,1:3], digits=2)
-rownames(tableS8)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")
+rownames(tableS8)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
 
@@
 tableS9<-round(summary(m1.eq.comm75)$coef[,1:3], digits=2)
-rownames(tableS9)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")
+rownames(tableS9)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
 
@@
 
-Figure5 <- ggplot(highprod75.sps,  aes(x=species.poll.sc, y= res.eq.retro)) +    
+pl75 <- ggplot(highprod75.sps,  aes(x=species.poll.sc, y= res.eq.retro)) +    
         geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
   stat_smooth(method = 'lm', size=1, se=TRUE, color = "black", alpha=0.4) +    
-        xlab("Pollinator sps diversity") +      
+        xlab("Pollinator richness") +      
         ylab("Equity in fruitset") + theme_bw()  + #theme (legend.position= "none") +
@@
 
+Figure4<-plot_grid(pltest, pltest2, pl75, labels = c("A", "B", "C"), nrow=1)  
 ```
@@
 tableS10<-round(summary(m1.eq.comm25)$coef[,1:3], digits=2)
-rownames(tableS10)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")
+rownames(tableS10)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
 
@@
   Within our simulation evaluating the effect of niche complementarity on equity in reproductive success as more plants within the community are considered, we find that the effect of complementarity becomes more important as the reproductive success of more species is considered (Fig.
-S4).
+5).
 This importance seems to reach some sort of plateau at 6 species.
@@
 f4 <- subset(f4, !Plant.sp %in% c("Astragalus lusitanicus", "Cistus albidus", "Anchusa azurea"))
-#Alternative, we use raw values (not dividing by max. and scale. Thos will take value of 0, which is equally arbitrary...)
-
-#Ainhoa, another question, this is a mean per species, right? So, for some species we may have more than one value.
 
@@
 f4$fruit.prop<-f4$mean.fruitset/f4$fruit.max
-head(f4) #this is ok, I guess, but imply we are correcting for differences in production across plants.
-
-#Quick dirty fix to see if things change a lot for uncorrected values
-#f4$fruit.prop <- f4$mean.fruitset
+head(f4)
 
@@
 
-#plot overall (asi a saco)
-
-#scatter.smooth(combinatorials_all$equity ~ combinatorials_all$functional.comp) #no relationship, good
+#plot overall
+
+#scatter.smooth(combinatorials_all$equity ~ combinatorials_all$functional.comp)
 
@@
 
-# I think this is a true pattern, as the for the cnetral limit theorem a mean of means should equal the grand mean, but worth check it.
-
 #now we subsample 16 combinations at a time 100 timeas and make the average.
@@
     for(j in 1:length(unique(temp$SiteID))){ # over sites
-      temp2 <- subset(temp, SiteID == unique(temp$SiteID)[j]) #why only one record at Elpinar??
+      temp2 <- subset(temp, SiteID == unique(temp$SiteID)[j]) 
       value_temp <- temp2[sample(x = 1:nrow(temp2), 1),]
@@
 
-figures4<-ggplot(estimate_i,  aes(x=level, y=estimate)) +    
-  geom_point(size=4) + #stat_smooth(method=loess,  size=1.5, se=TRUE, color = "black", alpha=0.2) + 
-  #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+Figure5<-ggplot(estimate_i,  aes(x=level, y=estimate)) +    
+  geom_point(size=4) + 
   xlab("Number of plant species considered") +      
   ylab("Importance of niche complementarity") + theme_bw()  +
-  theme(text = element_text(size = 14), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
-
-#AM: NOT SURE WHICH FIGURE WE WANT TO USE HERE
-
-#we had an issue for n = 5 ...
-this is cause by cotito de santa teresa having a huge influence when only 7 datasets are used.
-Once This is fixed, the plot looks nice.
-It's a shame that with 5 and 6 plants it asimptotes, but on the other hand, for 6 plants we only have very few sites.
-
-#One option is removing n = 6 from the simulation, as there is only one model for n = 6, and hence, while all other models estimate better the uncertainty on plant choice, the last model we have just 4 communities.
-
-#Ainhoa, this akes me think that when calculating thresholds, sites with 6 plants can score up to 6, but sites with 4 sites can oscar max = 4.
-I corrected for this doing % above threshold, and no number.
-Worth doing the same in the above models.
-
-#I only did it for fruit set.... no seeds, no weight...
+  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
+
+ggplot(s.comm,  aes(x=functional.comp.poll.sc, y=mean.seedset))+      
+        geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
+        #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+        xlab("Niche complementarity") +      
+        ylab("Number of seeds/fruit") + theme_bw()  + #theme (legend.position= "none") +
+        theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
 
@@
 
-The existence of a relationship between community structure and ecosystem function has been long hypothesized, yet, the specific mechanisms by which structure influences function have remained elusive until now [@Thompson2012].
-Our results show that different aspects of community structure affect different dimensions of community functioning.
+The existence of relationships between network structure and ecosystem function has been long hypothesized, yet, the specific mechanisms by which structure influences function have remained elusive until now [@Thompson2012].
+Our results show that different aspects of network structure affect different dimensions of ecosystem functioning.
 In particular, we find that the centrality of a plant species within a community, which measures the number of connections it receives from other species in the community, has a positive effect for its fruit set.
-At the community level, however, we find that niche complementarity between pollinators, a measure of the overlap in the niches of different species in terms of plant coverage, has an important effect for average fruit set.
-
-  One of the first conclusions we can extract from the fact that in most cases both of the models we considered (i.e., the simple model based on visitation metrics and the more complex one including community structure metrics) were equally good, is that for predictive purposes simple visitation metrics, such as pollinator diversity, might be enough [@Garibaldi2013; @Garibaldi2015].
-Yet, a mechanistic understanding of the underlying processes driving these observed patterns requires that we take into account measures of community structure, and, in particular, those related to the overlap in the niches of interacting species [@Frund2013].
+At the site level, we find that greater values of niche complementarity between pollinators result in larger average fruit sets.
+
+  One of the first conclusions we can extract from the fact that in most cases both of the models we considered (i.e., the simple model based on visitation metrics and the more complex one including network structure metrics) were equally good, is that for predictive purposes simple visitation metrics, such as pollinator richness, might be enough [@Garibaldi2013; @Garibaldi2015].
+Yet, a mechanistic understanding of the underlying processes driving these observed patterns requires that we take into account measures of network structure.
 
   Consistent with previous experimental [@Fontaine2005; @Frund2013], theoretical [@Pauw2013], and empirical studies [@Poisot2013; @Valdovinos2016], we find that niche complementarity is key in determining differences in reproductive outputs.
-Indeed, we find that communities where there is less overlap in the niches occupied by pollinator species had greater values of reproductive success, both greater fruit set values and larger numbers of seeds per fruit.
-This therefore reflects the fact that reproductive success in plant species requires of the delivery of conspecific pollen and thus of a certain degree of specialization amongst pollinator species on a particular plant resource in order to avoid the negative effects of inter-specific pollen deposition (e.g., pollen loss [@Flanagan2009] or interference with conspecific pollen [@Morales2008]).
+Indeed, we find that communities where there is less overlap in the niches occupied by pollinator species had greater values of reproductive success, both greater fruit set and larger numbers of seeds per fruit.
+This therefore reflects the fact that reproductive success in plant species requires the delivery of conspecific pollen and thus of a certain degree of specialization amongst pollinator species on a particular plant resource in order to avoid the negative effects of inter-specific pollen deposition (e.g., pollen loss [@Flanagan2009] or interference with conspecific pollen [@Morales2008]).
 
   In our study, we did not find an effect of nestedness for reproductive success in any case.
-This metric, widely used across network analysis, and which is deemed to stabilize [@Bastolla2009] or destabilize [@James2012] natural communities, does not seem to play a direct role in ecosystem function measured as plant reproductive success.
+This metric, widely used across network analysis, and which is deemed to stabilize [@Bastolla2009] or have a null effect [@James2012] on natural communities, does not seem to play a direct role in ecosystem function measured as plant reproductive success.
 However, our study is limited to a maximum of six plant species per community, and including more species might reveal different patterns, in which nestedness and the redundancy it implies might play a more important role.
 
-  Community-level plant reproductive success, measured as average fruit or seed set across all the species considered is an important part of the functions delivered by pollinators to plants.
+  Site-level plant reproductive success, measured as average fruit or seed set across all the species considered is an important part of the functions delivered by pollinators to plants.
 However, these average values might be masking a great deal of variability amongst plant species, and thus a nuanced view of the effect of pollinators on whole-plant ensembles is needed.
@@
 
-  In the case of equity, we did not find a significant effect of either simple visitation or community structure metrics.
-However, the results of our simulation on the importance of community structure as the number of plant species considered increases, shows us that this effect dramatically increases when more than four plant species are considered.
-This implies that if we were able to measure reproductive success for all the plant species in all the communities (which is not feasible given constraints in sampling effort), we might find that the effects of community structure on equity might be even more prevalent.
-
-  One of the unexpected results of our analyses is the strong negative effect of pollinator diversity for fruit set at the community level, as well as a negative effect on equity in reproductive success at the 0.75 threshold.
-An explanation to this might be the fact that pollinator diversity here includes all the pollinators surveyed, while fruit set and equity in fruit set refers to a subset of the plants in the community.
+  In the case of equity, we did not find a significant effect of either simple visitation or network structure metrics.
+However, the results of our simulation on the importance of network structure as the number of plant species considered increases, shows us that this effect dramatically increases when more than four plant species are considered.
+This implies that if we were able to measure reproductive success for all the plant species in all the communities (which is not feasible given constraints in sampling effort), we might find that the effects of network structure on equity might be even more prevalent.
+
+  One of the unexpected results of our analyses is the strong negative effect of pollinator richness for fruit set at the site level, as well as a negative effect on equity in reproductive success at the 0.75 threshold.
+An explanation to this might be the fact that pollinator richness here includes all the pollinators recorded during our sampling efforts, i.e., it includes species that do not pollinate some of the species whose reproductive success was measured.
 More complex communities (with more pollinators, but also with more plant species, with a Pearson correlation value of 0.42 in our case) may require stabilizing mechanisms that reduce the competition exerted by the dominant plant species.
@@
   In summary, our findings show that the analysis of natural communities of interacting species using network analysis not only represents an ideal way of visualizing and grasping the complexity present within these communities, but also represents a manner of mechanistically understanding differences observed across the reproductive success of individuals and/or species.
-Future studies could build on this body of research by focusing on the long-lasting effects of community structure for plant fitness, by evaluating the consequences of different community structures for heritability.
+Future studies could build on this body of research by focusing on the long-lasting effects of network structure for plant fitness, by evaluating the consequences of different network structures on other stages of a plant´slife cycle (e.g., seed viability) and whether these differences are passed on to later generations (e.g., though different survival rates).
 
@@
 # Table1A<-round(coefs.m2[,1:3],digits=2)
-# rownames(Table1A)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Centrality", "Niche overlap")
+# rownames(Table1A)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Centrality", "Niche overlap")
 
 kable(Table1A, caption = "Table 1A.
-Results of GLMM showing effect of simple visitation and community structure metrics on species-level fruitset based on best model selected.
+Results of GLMM showing effect of simple visitation and network structure metrics on species-level fruitset based on best model selected.
 Bold letters indicate significant variables.")
@@
 # Table1B<-round(coefs.m2.seed,digits=2)
-# rownames(Table1B)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Centrality", "Niche overlap")
+# rownames(Table1B)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Centrality", "Niche overlap")
 
 kable(Table1B, caption = "Table 1B.
-Results of GLMM showing effect of simple visitation and community structure metrics on species-level number of seeds/fruit based on best model selected.
+Results of GLMM showing effect of simple visitation and network structure metrics on species-level number of seeds/fruit based on best model selected.
 Bold letters indicate significant variables.")
@@
 # Table2A<-round(summary(m2.fruit.net)$coefficients$cond[,1:3], digits=2)
-# rownames(Table2A)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Nestedness", "Niche complementarity")
-
-kable(Table2A, caption = "Table 2A. Results of GLM showing effect of simple visitation and community structure metrics on community-level average fruitset based on best model selected.")
+# rownames(Table2A)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Nestedness", "Niche complementarity")
+
+kable(Table2A, caption = "Table 2A. Results of GLM showing effect of simple visitation and network structure metrics on site-level average fruit set based on best model selected.")
 
@@
 # Table2B<-round(summary(m2.seed.net)$coefficients[,1:3], digits=2)
-# rownames(Table2B)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Nestedness", "Niche complementarity")
-
-kable(Table2B, caption = "Table 2B.
-Results of GLM showing effect of simple visitation and community structure metrics on community-level average number of seeds per fruit based on best model selected.")
+# rownames(Table2B)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Nestedness", "Niche complementarity")
+
+kable(Table2B, caption = "Table 2B. Results of GLM showing effect of simple visitation and network structure metrics on site-level average number of seeds per fruit based on best model selected.")
 ```
@@
 **Figure 2**.
-Partial residual plot showing the effect of A) plant species centrality on fruit set for each of the plant species considered and B) plant niche overlap on average number of seeds per fruit.
+Partial residual plot showing the effect of a single predictor for the relationship between A) plant species centrality and fruit set for each of the plant species considered and B) plant niche overlap and average number of seeds per fruit.
 Dots represent each of the individuals sampled for each species within each site.
 
-**Figure 3.** Partial residual plots showing the effect of A) pollinator species diversity, B) total number of visits received and C) niche complementarity between pollinator species on community-level average fruitset.
-Dots represent average values of fruitset at the level of the community for all plant species considered (N=16 sites).
-
-**Figure 4.** Partial residual plots showing the effect of A) the total number of pollinator visits received at the community level and B) niche complementarity between pollinator species on the scaled average number of seeds per fruit at the community level.
-Dots represent average values of previously scaled values of the number of seeds per fruit at the level of the community for all plant species considered (N=16 sites).
-
-**Figure 5.** Partial residual plots showing the effect of pollinator species diversity on equity in reproductive success across species within a community (75% threshold).
+**Figure 3.** Partial residual plots showing the effect of A) pollinator richness, B) total number of visits received and C) niche complementarity between pollinator species on site-level average fruitset and D) niche complemenarity between pollinator species on the average number of seeds per fruit at the site level.
+Dots represent average values of fruit set at the level of the site for all plant species considered (N=16 sites).
+
+**Figure 4.** Partial residual plots showing the effect of pollinator richness on site-level average A) fruit and B) seed weight and C) equity in reproductive success across species within a site (75% threshold).
 Dots represent values for each site (N=16 sites).
 
+**Figure 5.** Results of simulation evaluating the importance of niche complementarity in determining differences in equity in reproductive across communities harboring from one to six species.
+Points represent average values across 1,000 simulated combinations.
+
 \newpage
 
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=7, fig.width=8}
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=7, fig.width=10}
 
@@
 
-sp_map = tm_shape(sp) + tm_polygons() +
+sp_map = tm_shape(sp) + tm_polygons() +   tm_compass(type = "8star", position = c("right", "bottom")) +
   tm_shape(occs) + tm_symbols(shape = 16, col = "black", size = 0.03) + 
@@
 sp_points_map = tm_shape(ele, bbox = doñana_region) +
- tm_raster(legend.show = TRUE, title = "Elevation (m)") +
-  tm_shape(occs) + tm_symbols(shape = 24, col = "darkgrey", size = 0.5) +
-  tm_scale_bar(position = c("left", "bottom"), size=0.75)
+ tm_raster(legend.show = TRUE, title = "Elevation \n (m)") + 
+  tm_layout(legend.text.size=1.5, legend.title.size = 1.6, legend.bg.color = "white", legend.frame = TRUE) +
+  tm_shape(occs) + tm_symbols(shape = 24, col = "darkgrey", size = 2) +
+  tm_scale_bar(position = c("left", "bottom"), size=1.5)
 
@@
 
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=9}
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=6, fig.width=9}
 
@@
 
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=7}
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=3, fig.width=10}
 
@@
 Figure4
-
+# 
 # save_plot("figures/Figure4.tiff", Figure4,
- #              base_height = 4, base_width = 8)
+#              base_height = 5, base_width = 10)
 ```
@@
 
-\newpage
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=3, fig.width=4}
-
-#FIGURE 5
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=8}
 Figure5
-# 
-# save_plot("figures/Figure5.tiff", Figure5,
-#              base_height = 5, base_width = 6)
-```
-**Figure 5**
+```
+**Figure 5.**
 
@@
 
-**Figure S2.** Partial residual plots showing the effect of the total number of pollinator visits received at the community level on the average fruit weight.
-Dots represent average vaues at the level of the community for all plant species considered (N=16 sites).
+**Figure S2.** Partial residual plots showing the effect of the total number of pollinator visits received at the site level on the average fruit weight.
+Dots represent average vaues at the level of the site for all plant species considered (N=16 sites).
 
@@
 
-**Figure S3.** Partial residual plots showing the effect of the the diversity of pollinators and the total number of pollinator visits received at the community level on the average seed weight.
-Dots represent average vaues at the level of the community for all plant species considered (N=16 sites).
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=8}
-figures4
-```
-**Figure S4.** Results of simulation evaluating the importance of niche complementarity in determining differences in equity in reproductive across communities harboring from one to six species.
-Points represent average values across 1,000 simulated combinations.
+**Figure S3.** Partial residual plots showing the effect of the the diversity of pollinators and the total number of pollinator visits received at the site level on the average seed weight.
+Dots represent average vaues at the level of the site for all plant species considered (N=16 sites).
 
@@
 tableS4<-round(summary(m1.seed.w)$coefficients$cond[,1:3], digits=2)
-rownames(tableS4)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")
+rownames(tableS4)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
 kable(tableS4, caption="Table S4. Results of GLMM showing effect of simple visitation metrics on species-level average seed weight based on best model selected.")
@@
 tableS5<-round(summary(m1.fruit.w)$coefficients$cond[,1:3], digits=2)
-rownames(tableS5)<-c("(Intercept)", "Normalized degree", "Total number of visits")
+rownames(tableS5)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
 kable(tableS5, caption="Table S5. Results of GLMM showing effect of simple visitation metrics on species-level average fruit weight based on best model selected.")
@@
 tableS6<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)
-rownames(tableS6)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")
-
-kable(tableS6, caption="Table S6. Results of GLM showing effect of simple visitation metrics on community-level average fruit weight based on best model selected.")
+rownames(tableS6)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
+
+kable(tableS6, caption="Table S6. Results of GLM showing effect of simple visitation metrics on site-level average fruit weight based on best model selected.")
 ```
@@
 tableS7<-round(summary(m1.seedw.net)$coef[,1:3], digits=2)
-rownames(tableS7) <-c("(Intercept)", "Pollinator species diversity", "Total number of visits")
-
-kable(tableS7, caption="Table S7. Results of GLM showing effect of simple visitation metrics on community-level average seed weight based on best model selected.")
+rownames(tableS7) <-c("(Intercept)", "Pollinator richness", "Total number of visits")
+
+kable(tableS7, caption="Table S7. Results of GLM showing effect of simple visitation metrics on site-level average seed weight based on best model selected.")
 ```
@@
 kable(tableS8, caption="Table S8.
-Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a community based on best model selected (0.50 threshold).")
+Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a site based on best model selected (0.50 threshold).")
 
 kable(tableS9, caption="Table S9.
-Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a community based on best model selected (0.75 threshold).")
+Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a site based on best model selected (0.75 threshold).")
 
 kable(tableS10, caption="Table S10.
-Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a community based on best model selected (0.25 threshold).")
+Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a site based on best model selected (0.25 threshold).")
 ```

### 2019-07-30 Simmons.R
Add script to understand SImmons. You can ignore this one

@@ -1,0 +1,121 @@
+#test simmons algorithm
+
+#First I use Song example to keep it simple----
+# I also aim to load as less packages as possile to avoid conflicts
+
+#Song approach
+source('Data_and_code_Song_et_al_2017/toolbox.R') #load the toolbox
+
+web <- read.csv("Data_and_code_Song_et_al_2017/network.csv") #load network.csv
+web <- as.matrix(web)
+head(web)
+print(NODF <- nestedness_NODF(web)) # this calculates the raw value of NODF
+print(max_NODF_S <- max_nest(web)) # this calculates the maximum value of NODF for that network
+print(combined_NODF_S <- comb_nest(web,NODF,max_NODF_S)) # this calculates the combined NODF statistic as described in the manuscript
+#works as expected.
+
+#Now Simmons approach. 
+#NODF <- nestedness_NODF(web) # this calculates the raw value of NODF #as in song
+devtools::install_github("CHoeppke/maxnodf")
+library(maxnodf)
+max_NODF <- maxnodf(web=web, quality=2) # this calculates the maximum value of NODF for that network, based on Simmons correction of Song
+#Error in maxnodf(web = web, quality = 2) : 
+ #Invalid network. Ensure all row and column totals are >= 1.
+colSums(web)
+web2 <- web[,-which(colSums(web) < 0.1)]
+#start again
+nestedness_NODF(web)
+(NODF <- nestedness_NODF(web2)) # Fuck, this value changes!!
+max_NODF <- maxnodf(web=web2, quality=2) # this calculates the maximum value of NODF for that network, based on Simmons correction of Song
+#interestin max_nest(web2) has the same exact value!!
+max_NODF_S == max_NODF$max_nodf
+max_nest(web2) == max_NODF$max_nodf
+#combine
+combined_NODF <- comb_nest(web2,NODF,max_NODF$max_nodf) # this calculates the combined NODF statistic as described in the manuscript
+#compatre
+combined_NODF_S == combined_NODF #FALSE
+comb_nest(web2,NODF,max_nest(web2)) == combined_NODF #TRUE
+
+#test issue links > ncol + nrows
+sum(web2)
+ncol(web2) + nrow(web2)
+
+#for failing in network analysis.R
+sum(web4)
+ncol(web4) + nrow(web4) #small difference!
+
+#opening up the black box
+
+#debugged using web4, which should fail.
+web = web4
[…]

### 2019-07-30 scripts/network analysis.R
Update NODF calculation.

@@ -27,7 +27,7 @@ data(single_visits)
 
 #analysis...----
 
-setwd("~/Dropbox/Beefun/Beefun/functioning")
+#setwd("~/Dropbox/Beefun/Beefun/functioning")
 
 d<-all_interactions
 f<-fruitset
@@ -35,7 +35,7 @@ s<-seedset
 si<-single_visits
 
 #we will calculate nestedness based on paper by Song et al 2017 Journal of ANimal ecology based on NODF and its
-#correction by max NODF as NODFc = NODFn/(C  log(S)), where NODFn = NODF/max(NODF).
+#correction by max NODF as NODFc = NODFn/(C * log(S)), where NODFn = NODF/max(NODF).
 #to this end we use the toolbox provided with their paper
 
 source('toolbox.R') #load the toolbox
@@ -83,13 +83,17 @@ outsp.pl.site <- data.frame(Site_id = NA, species=NA,  norm_degree = NA,strength
 
 
 webs <- list()
+#Sites working: c(1:5,7:14) #fails for 6, 15 & 16.
 for(i in 1:length(sites)){
+  print(i)
   temp <- subset(d, Site_ID == sites[i])
   # for(j in 1:length(rounds)){
   #   temp2 <- subset(temp, Round == rounds[j])
   #   if (nrow(temp2) == 0) next
   
-  web <- table(temp$Plant_gen_sp, temp$Pollinator_gen_sp)
+  web <- table(temp$Plant_gen_sp, temp$Pollinator_gen_sp) #WOW, this ignores frequency!!
+  #AINHOA, ANY MERIC USES FREQUENCY? If SO, FREQUENCY HERE IS INCIDENCE; NOT VISITATION.
+  #I AM FINE USING THIS, BUT SHOULD BE CLEAR IN TEXT.
   web2<-as.data.frame.array(web)
   #p1<-plotweb(web)
   spntw <- try(specieslevel(web), TRUE)
@@ -102,44 +106,41 @@ for(i in 1:length(sites)){
   
   #null model 
   nulls <- try(nullmodel(web, N=100, method="r2d"), TRUE)
-  ntw.null <- try(sapply(nulls, networklevel), TRUE)
+  #NACHO comments this out because is slow and is not needed, right?
+  #FEEL FREE TO BRING THEM BACK
+  #ntw.null <- try(sapply(nulls, networklevel), TRUE)
   
   #null value of modularity
[…]

### 2019-07-30 paper_round2.Rmd
Make two small comments about using incidence vs visits.

@@
             tot.visits= sum(Frequency))
+#Here you use visits. Which I agree.
 
@@
   web <- table(temp2$Pollinator_gen_sp, temp2$Plant_gen_sp)
-
+  #SAME HERE, We are assuming INCIDENCE. No Visitation rates.
+  #colSums(web)
+  #rowSums(web)
   ni<-niche.overlap(web, method="morisita") #THIS SHOULD BE EXPLAINED IN METHODS

### 2019-07-31 scripts/network analysis.R
changes previous to nacho´s revision

@@ -90,6 +90,7 @@ for(i in 1:length(sites)){
   #   if (nrow(temp2) == 0) next
   
   web <- table(temp$Plant_gen_sp, temp$Pollinator_gen_sp)
+
   web2<-as.data.frame.array(web)
   #p1<-plotweb(web)
   spntw <- try(specieslevel(web), TRUE)
@@ -119,16 +120,16 @@ NODF <- nestedness_NODF(web) # this calculates the raw value of NODF, ESTO VIENE
 #PERO LUEGO SI EL NUMERO DE LINKS>NUMERO COLUMNAS + NUMERO FILAS SE PARA. Y EN ALGUNOS CASOS
 #DE ALGUNAS DE NUESTRAS REDES ESO PASA PORQUE NO TENEMOS SOLO 0 Y 1 
 
-#devtools::install_github("CHoeppke/maxnodf")
-library(maxnodf)
-#remove all columns and rows with all values=0
-web3<-web[, colSums(web != 0) > 0]
-web4<-web3[rowSums(web3[, -1] > 0) != 0, ]
-max_NODF <- maxnodf(web=web4, quality=2) # this calculates the maximum value of NODF for that network, based on SImmons correction of Song
-
+# #devtools::install_github("CHoeppke/maxnodf")
+# library(maxnodf)
+# #remove all columns and rows with all values=0
+# web3<-web[, colSums(web != 0) > 0]
+# web4<-web3[rowSums(web3[, -1] > 0) != 0, ]
+# max_NODF <- maxnodf(web=web4, quality=2) # this calculates the maximum value of NODF for that network, based on SImmons correction of Song
+max_NODF<-max_nest(web)
 #ESTO VUELVE A SER PARTE DEL SONG ORIGINAL
-combined_NODF <- comb_nest(web,NODF,max_NODF$max_nodf) # this calculates the combined NODF statistic as described in the manuscript
-  
+#combined_NODF <- comb_nest(web,NODF,max_NODF$max_nodf) # this calculates the combined NODF statistic as described in the manuscript
+combined_NODF <- comb_nest(web,NODF,max_NODF)
   
   #species-level c and z values for plants and poll
   
@@ -256,11 +257,19 @@ for(i in 1:length(sites.sinout)){
   
   #song et al nestedness corrected with NODF max
   
+  source('toolbox.R') #load the toolbox
+  
+  
+  
[…]

### 2019-08-05 paper_round2.Rmd

--- 2019-07-21 paper_round2.Rmd
@@
 ---
-title: Niche complementarity between pollinators increases plant reproductive success 
+title: Niche complementarity between pollinators increases community-level plant reproductive success 
 author: "Magrach, A, Molina, FP, Bartomeus, I"
@@
 
-**Niche complementarity between pollinators increases plant reproductive success**
+**Niche complementarity between pollinators increases community-level plant reproductive success**
 
@@
 
-Words in Abstract: 148 words
-
-Words in main text (excluding abstract, acknowledgements, references, table and figure legends): 4,451
-
-Number of references: 48
+Words in Abstract: 170 words
+
+Words in main text (excluding abstract, acknowledgements, references, table and figure legends): 5,302
+
+Number of references: 60
 
@@
 Here, we present one of the first efforts linking pollinator visitation to plant reproduction from a community-wide perspective using a well-replicated dataset encompassing 16 well-resolved plant-pollinator networks and data on reproductive success for 19 plant species from Mediterranean shrub ecosystems.
-We find that, for prediction purposes, information on simple visitation metrics is sufficient.
-Contrastingly, a mechanistic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success, requires additional information on network structure, particularly that reflecting niche complementarity between pollinators.
+We find that models including information on simple visitation metrics alone are good in explaining the variability in reproductive success observed.
+However, insights into the mechanisms through which differences in pollinator diversity translate into changes in reproductive success require additional information on network structure, particularly that reflecting niche complementarity between pollinators.
 Specifically, we find a positive effect of increasing niche complementarity between pollinators on plant reproductive success.
+
 \nextpage
@@
 
-  Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012a; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain the differences observed across different plant individuals.
+  Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain the differences observed across different plant individuals.
 Contrastingly, community-level analyses remain scarce [@Bennett2018].
@@
   The few pollination studies that have analysed the effects of changing pollinator diversity for reproductive success at the community level have done so using mainly experimental setups.
-As an example, a study that experimentally recreated a plant community with 9 plant species and differing levels of pollinator diversity across different enclosures, found that not only pollinator species diversity had an effect for average reproductive success, but also they found that network structure had an important effect [@Frund2013].
+As an example, a study that experimentally recreated a plant community with 9 plant species and differing levels of pollinator diversity across different enclosures, found that not only pollinator species diversity had an effect for average reproductive success, but that plant-pollinator interaction structure also had an important effect [@Frund2013].
 In particular, these authors found that niche complementarity between pollinators, in terms of plant species and temperature coverage (a measure of the overlap in the use of plant resources and optimum temperature activity) had a positive effect for average seed set at the community level [@Frund2013].
@@
   Indeed, theoretical research has long suggested that the structure of multitrophic communities has an effect for ecosystem functioning (reviewed in [@Thompson2012]).
-This line of research, primarily driven by food-web studies, has greatly advanced theory, but these ideas have not yet been tested using empirical data (but see [@Poisot2013]).
+This line of research, rooted in niche theory and revamped by food-web studies [@Godoy2018; @Macarthur1967; @May1972a; @Tilman1982], has greatly advanced theory, but these ideas have not yet been tested using empirical data (but see [@Poisot2013]).
 Specifically, a major knowledge gap resides in understanding which aspects of structure determine which aspects of function [@Thompson2012].
-We are now at a point in which there is considerable understanding on the attributes characterizing mutualistic interaction networks [@Bascompte2007b] and we have a substantial understanding of how these attributes vary along different types of gradients [@Pellissier2017; @Tylianakis2016].
+This is because although a network perspective has promised to encapsulate complex ecological mechanisms occurring at the community level – such as indirect interactions [@Abrams1998; @Holt1977] or niche overlap [@Woodward2002]- less attention has been given to the ways in which these mechanisms relate to observed ecosystem processes [@Bluthgen2010a].
+In contrast, we are now at a point in which there is considerable understanding on the attributes characterizing mutualistic interaction networks [@Bascompte2007a].
 Especially, in the case of pollination, we have ample knowledge on the attributes that shape these mutualistic interactions at the community level.
-Amongst them is the prevalence of nested structures, i.e., arrangements where specialist species interact with a subset of the species that generalists interact with [@Bascompte2003] and which is thought to promote species diversity [@Bastolla2009]; or the presence of asymmetric specialization, i.e., specialists tend to interact with generalist species as a pervasive feature [@Vazquez2004].
-However, the pathways by which the structure of these networks of interactions affect key ecosystem functions such as plant reproduction remain to be understood [@Winfree2013].
-The time is thus ripe to use the existing knowledge around plant-pollinator network structures to explore the relationship between network structure and ecosystem functioning, with special emphasis being placed on the underlying mechanisms that drive these relationships.
+Amongst them is the prevalence of nested structures, i.e., arrangements where specialist species interact with a subset of the species that generalists interact with [@Bascompte2003] and which is thought to promote species diversity [@Bastolla2009]; or the relatively high extent of complementary specialization at the community scale, which may be directly related to key ecosystem functions [@Bluthgen2011].
+However, the mechanisms by which these potential pathways affect plant reproduction remain to be understood [@Winfree2013].
+The time is thus ripe to use the existing knowledge around plant-pollinator network structures to explore the relationship between network structure and ecosystem functioning empirically, with special emphasis being placed on the underlying ecological mechanisms that drive these relationships.
 
   Here, we present one of the first efforts linking pollinator visitation and plant reproductive success at the community level using empirical data on plant-pollinator interaction networks and plant reproductive success.
-To this end, we use a well-replicated dataset encompassing 16 well-resolved plant-pollinator interaction networks coupled with data on the reproductive success of 19 plant species recorded in Mediterranean shrub ecosystems within the area of influence of Doñana National Park in SW Spain, i.e., within the limits of the Natural Space of Doñana as defined by the local government (Junta de Andalucía).
-Our study focuses on understanding whether adding information on network structure to previously used simple visitation metrics (e.g., the number and diversity of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success.
+To this end, we use a well-replicated dataset encompassing 16 well-resolved plant-pollinator interaction networks coupled with data on the reproductive success of 19 plant species recorded in Mediterranean shrub ecosystems.
+Our study focuses on understanding whether adding information on selected interaction network structure indices to previously used simple visitation metrics (e.g., the number and diversity of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success.
 In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success, and (ii) at the site level, by evaluating how attributes that describe the whole site might affect average values of reproductive success.
-Specifically, our study focuses on the how the interplay between niche complementarity and redundancy determines reproductive success.
-Plant reproductive success requires of the delivery of conspecific pollen and thus of a certain degree of niche complementarity.
+Specifically, our study focuses on how the interplay between niche complementarity and redundancy determines reproductive success.
+Plant reproductive success requires of the delivery of conspecific pollen and thus of a certain degree of niche complementarity [@Bluthgen2011].
 Yet, greater values of nestedness, which imply redundancy in species functions, are thought to promote species diversity [@Bastolla2009] and stability [@Thebault2010a] within plant-polllinator networks.
@@
 
-  Our results suggest that for prediction purposes, information on simple visitation metrics, particularly regarding the pollinator richness visiting a plant species, is sufficient.
-However, we find that a mechanistic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success requires additional information on network structure, notably information on the complementarity between the functions performed and the niches occupied by different pollinator species.
+  Our results suggest that models including information on simple visitation metrics alone are good in explaining the variability observed in reproductive success.
+However, insights into the mechanisms through which differences in pollinator diversity translate into changes in reproductive success require additional information on network structure, notably information on the complementarity between the functions performed and the niches occupied by different pollinator species.
+Specifically, we find a positive effect of increasing niche complementarity between pollinators on plant reproductive success.
 
@@
 out.site<-read.csv("SITE_network_level_metrics.csv")
-
-outsp.pl.site.sinout<-read.csv("SITE_plant_species_level_metrics_sinout.csv")
-outsp.site.sinout<-read.csv("SITE_species_level_metrics_sinout.csv")
-out.site.sinout<-read.csv("SITE_network_level_metrics_sinout.csv")
-
+```
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE}
 #check number of sps per site surveyed in the focal analyses
@@
 
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE}
+
+#calculate sorensen index to look at beta-diversity across sites for plants
+library(betapart)
+d.sub<-subset(d, d$Out=="transect") #keep only plants surveyed in transects, remove focals
+d.beta<-table(d.sub$Site_ID, d.sub$Plant_gen_sp)
+d.beta[d.beta>1]<-1 #make it binary
+d.betadiv<-beta.multi(d.beta)
+sor<-d.betadiv[3]
+
+```
+
 **Methods**
@@
 
-Our study was conducted in SW Spain within the area of influence of Doñana National Park (Fig.
+Our study was conducted in SW Spain within the area of influence of Doñana National Park, i.e., within the limits of the Natural Space of Doñana as defined by the local government (Junta de Andalucía, Fig.
 1).
+All sites were located within similar elevations (ranging from 50 to 150 m a.s.l.), similar habitat and soil types, and presented similar plant compositions (plant mean Sørensen beta-diversity among sites = `r round(sor$beta.SOR, 2)`), reducing potential confounding factors.
 Here, we surveyed 16 Mediterranean woodland patches with an average distance of 7 km between them (min= 3 km, max= 46.5 km).
@@
 Our survey included a total of `r nlevels(f2$Plant.sp)` different plant species across our `r nlevels(f2$Site_ID)` sites.
-Plants species were selected based on their availability with sampling being focused on the most abundant plant species.
+Plants species were selected based on their availability, with sampling being focused on the most abundant plant species.
 The values at the species level were then averaged per site to calculate unique reproductive success measures at the site level.
+[X % of the plant species depend on pollinators to maximize their reproduction (Table SX).]()
 
@@
 
-In order to evaluate the completeness of our sampling of the pollinator and plant community as well as that of their interactions, we estimated the asymptotic number of species present, a non-parametric estimator of species richness for abundance data.
-This estimator includes non-detected species, and allowed us to calculate the proportion detected with our original sampling data.
+In order to evaluate the completeness of our sampling of the pollinator and plant community as well as that of their interactions, we estimated the asymptotic number of species present [@Chao2009], a non-parametric estimator of species richness for abundance data.
+This estimator includes non-detected species and allowed us to calculate the proportion detected with our original sampling data.
 We used Chao 1 asymptotic species richness estimators [@Chao2009] and estimated the richness of pollinators, plants and plant–pollinator links accumulated as sampling effort increased up to 100% sampling coverage using package iNEXT [@Hsieh2016] within the R environment [@RDevelopmentCoreTeam2011].
@@
 
-  In order to analyse how differences in network structure might affect plant reproductive success, we constructed weighted plant-pollinator interaction networks by pooling the data for the 7 rounds of sampling.
-We thus obtained one weighted interaction network per site, representing the frequency of visits by different pollinator species to different plant species.
+  In order to analyse how differences in network structure might affect plant reproductive success, we constructed plant-pollinator interaction networks by pooling the data for the 7 rounds of sampling.
+We thus obtained one interaction network per site, representing the incidence of visits by different pollinator species to different plant species.
 For each network, we then proceeded to extract a series of relevant network metrics at the species and site levels.
+
+  In addition, we checked for potential spatial autocorrelation in our data by means of Mantel correlograms. Autocorrelation values were low for all variables included in our analyses (Figure S1).
 
@@
  Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the Morisita overlap index, a measure of similarity between two sets of data [@Zhang2016].
-As a measure of centrality we used weighted closeness centrality, which represents the number of shortest paths going through a focal plant based on a unipartite projection of the bipartite plant-pollinator network using a weighted representation of the network [@Dormann2009].
+As a measure of centrality, we used weighted closeness centrality, which represents the number of shortest paths going through a focal plant based on a unipartite projection of the bipartite plant-pollinator network using a weighted representation of the network [@Dormann2009].
 Here, links between plant species represent shared pollinator species.
@@
 Thus, we also calculated two network metrics providing complementary non-redundant information.
-In this case we focused on (i) nestedness and (ii) niche complementarity.
+In this case we focused on (i) nestedness and (ii) pollinator niche complementarity.
 
@@
 However, many network attributes vary with network size and complexity [@Bluthgen2006].
-In the case of nestedness, we know it can be affected by network size and connectance [@Song2017].
+In the case of nestedness, we know it can be affected by network size and connectance [@Song2017a].
 An approach that is often used to correct for this, is to use null models and to compare null-model corrected nestedness values across different networks.
-However, this approach has been recently shown to present the same issues, as z-scores also change with network size and connectance [@Song2017].
+However, this approach has been recently shown to present the same issues, as z-scores also change with network size and connectance [@Song2017a].
 We thus followed the advice provided by Song et al.
@@
 This normalized value is calculated as $NODF_c = NODF_n/(C * log(S))$, where C is connectance and S is network size.
-$NODF_n$ is calculated as $NODF/max(NODF)$, which is independent of network size and thus comparable across different networks [@Song2017].
+$NODF_n$ is calculated as $NODF/max(NODF)$, which is independent of network size and thus comparable across different networks [@Song2017a].
+To calculate max(NODF) we used a recently corrected version of the algorithm [@Simmons2019a] in all but three sites, where the condition that the number of links>number of species was not met and thus precluded us from using this new version.
 
@@
   All of these metrics were calculated using all the data as well as for the subset of the data excluding interactions observed outside of sampling periods.
-Differences between results are minimal for both and thus we will only present results for the analysis using the full dataset.
+Differences between results are minimal for both and thus we will only present results for the analysis using the full dataset (see Table S11A-H for results removing observations out of transect).
 
@@
 In both cases (species and site-level models) we fit two types of models: (i) model 1, that only included simple visitation metrics and (ii) model 2 that additionally included information on network structure.
-
-  At the species level, response variables included the fruit set for different individuals of each species, analyzed using a binomial distribution, the average number of seeds per fruit, analyzed using a normal distribution, and the average values of fruit and seed weight fitted to Poisson distributions.
+These models are meant to be additive, so that the network metrics included are intended to complement rather than substitute the simple metrics traditionally used.
+
+  At the species level, response variables included the fruit set for different individuals of each species analyzed using a binomial distribution, the average number of seeds per fruit analyzed using a normal distribution, and the average values of fruit and seed weight fitted to Poisson distributions.
 The number of seeds per fruit was centered and scaled (i.e., we subtracted column means and divided by standard deviation) to allow meaningful comparisons across species with contrasting life histories.
-As explanatory variables, model 1 included pollinator richness, and the total number of visits received by that plant species; while model 2 added the two network attributes calculated at the species level: average niche overlap and centrality.
-For both models, we included plant species nested within site as a random effect to account for the non-independence of several individuals measured for the same plant species within each site.
+As explanatory variables, model 1 included pollinator richness, and the total number of visits received by each plant species; while model 2 added the two network attributes calculated at the species level: average plant niche overlap and centrality.
+For both models, we included plant species nested within site and site as random effects to account for the non-indepedence of several individuals measured per species and site.
 
 	At the site level, we upscaled our species-level analyses.
-As response variable we had the average reproductive success per site (i.e., average fruit set analyzed using a binomial distribution, average number of seeds per fruit and average fruit and seed weight using a normal distribution).
+As response variables we had the average reproductive success per site (i.e., average fruit set analyzed using a binomial distribution, average number of seeds per fruit and average fruit and seed weight using a normal distribution).
 We thus had a single value per site and no random effects are needed in this case.
@@
 number of visits received by all plants within the community) as explanatory variables.
-Model 2, in turn, added information on network structure by including nestedness and niche complementarity as explanatory variables.
+Model 2, in turn, added information on network structure by including nestedness and pollinator niche complementarity as explanatory variables.
 
@@
 Yet, what will determine the persistence of a diverse plant community, is the presence of some sort of “equity” or evenness in reproductive success across the whole community.
-We therefore calculated a measure of equity in reproductive success at the site level as the proportion of species with normalized (between 0 and 1) average fruit set values that were above 0.5.
-We repeated this using 0.25 and 0.75 thresholds.
-We then used the same framework as that used for species and site-level analyses and fit the same models 1 and 2 GLMs, but using equity in reproductive success as the response variable fitting a binomial distribution.
+We therefore calculated a measure of equity in reproductive success at the site level as the proportion of species with normalized (between 0 and 1) average fruit set values that were above the 50^th percentile.
+As any selected threshold is arbitrary, we repeated this using the 25^th and 75^th percentile thresholds [@Byrnes2014].
+We then used the same framework as that used for species and site-level analyses and fit the same models 1 and 2 GLMs but using equity in reproductive success as the response variable and fitting a binomial distribution.
+
   In all cases, we used variance inflation factors to check for collinearity between explanatory variables.
 Additionally, we ran residual diagnostics to check if model assumptions were met.
-Then, we used information criterion methods to find the best model and selected the ones with the lowest Akaike Information Criterion (AIC) value.
+Then, we used the Akaike Information Criterion (AIC) to compare model performance and complexity.
 Whenever the difference between the AIC of both models was < 2 ($\Delta AIC<2$), we considered that both models were equally good [@Burnham2011].
-All predictor variables were centered prior to analysis.
+All predictor variables were standardized prior to analysis.
+For every model we also calculate the R2 value using the approximation suggested for generalized mixed models when necessary [@Shinichi2017].
 
@@
 Then, we tested if the relationship between equity in reproductive success and functional complementarity (given its importance in determining differences in reproductive success, see Results section) changes as a function of the number of plants considered within our simulated communities.
-To this end, for each level of species number considered, we randomly selected one of the generated equity values across each of the 16 communities, and regressed these 16 values against our network level predictor and extracted the model estimates.
-We repeated this process 1,000 times and averaged all estimates.
+To this end, for each level of species number considered, we randomly selected one of the generated equity values across each of the 16 communities and regressed these 16 values against our network level predictor and extracted the model slope estimates.
+We repeated this process 1,000 times and averaged all slope estimates.
 We expect that the more plants considered, the larger the resulting average estimates will be.
@@
 
-d4 <- t(d3[,1:ncol(d3)]) #I updated this to use defensive programming.
+d4 <- t(d3[,1:ncol(d3)]) 
 #head(d4)
@@
 
-#FIGURE S1 AT THE END OF THE PAPER
+#FIGURE S2 AT THE END OF THE PAPER
 
@@
   Our sampling completeness analyses revealed that with our survey we were able to capture 18-62% of pollinator species (average = 35%), 47-98% for plant species (average = 78%) and 13-41% for plant-pollinator links (average = 27%), in line with that obtained with other studies (e.g., [@Chacoff2012], Fig.
-S1).
-Our values of sampling completeness are slightly smaller in the case of pollinators, probably as a consequence of the great diversity found in the Mediterranean region and within our study area in particular, a hotspot of insect diversity [@Nieto2014a].
+S2).
+Our values of sampling completeness are slightly smaller in the case of pollinators, probably as a consequence of the great diversity found in the Mediterranean region and within our study area in particular, a hotspot of insect diversity [@Nieto2014].
 In addition, the fact that we include an extra effort to capture rare interactions observed outside of our main sampling might also increase the number of singletons which directly affect richness estimates.
@@
 
-#calculate average niche overlap per species
+#calculate average niche overlap per plant species
 
@@
 
-  web <- table(temp2$Pollinator_gen_sp, temp2$Plant_gen_sp)
+   web<-table(temp2$Pollinator_gen_sp, temp2$Plant_gen_sp)
 
@@
 
-out.niche.agg <- ddply(out.niche, c("Site_id", "col"), summarise,
+#head(out.niche)
+out.niche2<-na.omit(out.niche)
+out.niche.agg <- ddply(out.niche2, c("Site_id", "col"), summarise,
                mean.niche.over    = mean(value))
@@
 
-#use unaggregated data and join it with network metrics
+#join with network metrics
 
@@
 
-#calculate number of pollinator species per plant species instead of norm_degree
+#calculate number of pollinator species per plant species
 
@@
 
-f2$functional.comp.poll.sc<-scale(f2$functional.comp.poll, center = T, scale = T)
-f2$functional.comp.pl.sc<-scale(f2$functional.comp.pl, center = T, scale = T)
-f2$nodf.song.sc<-scale(f2$nodf.song, center = T, scale = T)
-f2$species.poll.sc<-scale(f2$species.poll, center = T, scale = T)
-f2$norm_degree.sc<-scale(f2$norm_degree, center = T, scale = T)
 f2$weigh_closeness.sc<-scale(f2$weigh_closeness, center = T, scale = T)
@@
 m1<-glmer(tot.fruitset ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2)
-
 summary(m1)
@@
 
-# extract coefficients and p-values for m2 and present them in paper
+# extract estimates and st errors to present in table
 coefs.m2 <- data.frame(coef(summary(m2)))
@@
 Table1A<-round(coefs.m2[,1:3],digits=2)
-rownames(Table1A)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Centrality", "Niche overlap")
+rownames(Table1A)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Centrality", "Plant niche overlap")
 #at the end of the paper
 
-#plot significant variables, in this case centrality, do partial residual plots to show the effect of that variable in isolation of the others
+#plot significant variables, in this case centrality and visits, do partial residual plots to show the effect of that variable in isolation of the others
 
@@
 Figure2a<-ggplot(m2@frame,  aes(x=m2@frame$weigh_closeness.sc, y=y_partial_weigh_inv, color= Plant.sp)) +    
-  geom_point(size=2.5, shape=21, colour="black", aes(fill=factor(Plant.sp))) + stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
-  #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
+  geom_point(size=2.5, shape=21,color = "black", aes(fill=factor(Plant.sp))) + 
+  stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
   xlab("Centrality") +      
@@
 
-At the species level, in the case of fruit set, our results show that model 2 shows the best fit to our data (lowest AIC value), explaining `r round(r2$Conditional[1], 2)*100`% of the variability observed.
+At the species level, in the case of fruit set, our results show that model 2 shows the best fit to our data (lowest AIC value), explaining `r round(r2$Marginal[1], 2)*100`% of the variability observed.
 In this case, we find a positive effect of a network structure metric, the centrality of a focal plant within the overall network on its fruit set (Table 1, Fig.
@@
 #scale all variables used
-
-s3$functional.comp.poll.sc<-scale(s3$functional.comp.poll, center = T, scale = T)
-s3$functional.comp.pl.sc<-scale(s3$functional.comp.pl, center = T, scale = T)
-s3$nodf.song.sc<-scale(s3$nodf.song, center = T, scale = T)
-s3$species.poll.sc<-scale(s3$species.poll, center = T, scale = T)
 
@@
 
-m1.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3)
+m1.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3)
 
@@
 
-# extract coefficients and p-values for m1 and present them in paper
+# extract estimates and st errors to present in table
 coefs.m2.seed <- data.frame(coef(summary(m2.seed)))
-# use normal distribution to approximate p-value
-#coefs.m2.seed$p.z <- 2 * (1 - pnorm(abs(coefs.m2.seed$t.value)))
 coefs.m2.seed
 Table1B<-round(coefs.m2.seed,digits=2)
-rownames(Table1B)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Centrality", "Niche overlap")
+rownames(Table1B)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Centrality", "Plant niche overlap")
 
@@
   #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
-  xlab("Niche overlap") +      
+  xlab("Plant niche overlap") +      
   ylab("Number of \n seeds per fruit") + theme_bw()  + theme (legend.position= "right") +
@@
 
- For the average number of seeds per fruit, our results show again that model 2 shows the best fit, explaining `r round(r2b$Conditional[1], 2)*100`% of the variability observed in our data.
+ For the average number of seeds per fruit, our results show again that model 2 shows the best fit, explaining `r round(r2b$Marginal[1], 2)*100`% of the variability observed in our data.
 In this case, we find a positive effect of the niche overlap between plant species on the number of seeds produced (Table 1B, Fig.
@@
 
-m1.seed.w<-glmmTMB(mean.seedw ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3)
+m1.seed.w<-glmmTMB(mean.seedw ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="poisson", data=s3)
 
@@
 
-m2.seed.w<-glmmTMB(mean.seedw ~  pollspsperplant.sc + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3)
+m2.seed.w<-glmmTMB(mean.seedw ~  pollspsperplant.sc + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="poisson", data=s3)
 
@@
 
-# extract coefficients and p-values for m1 and present them in paper
+# extract estimates and st error for m1 and present them in paper
 tableS4<-round(summary(m1.seed.w)$coefficients$cond[,1:3], digits=2)
@@
 
-m1.fruit.w<-glmmTMB(mean.fruitweight ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="poisson", data=s3)
+m1.fruit.w<-glmmTMB(mean.fruitweight ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="poisson", data=s3)
 
@@
 
-# extract coefficients and p-values for m1 and present them in paper
+# extract estimates and st error for m2 and present them in paper
 tableS5<-round(summary(m2.fruit.w)$coefficients$cond[,1:3], digits=2)
-rownames(tableS5)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Centrality", "Niche overlap")
+rownames(tableS5)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Centrality", "Plant niche overlap")
 
@@
 f.agg$tot.visits.sc <- scale(f.agg$tot.visits, center = T, scale = T)
+
 ```
@@
 
-#removing one point with large number of visits to see if this is driving the effect of total number of visits (non-overlapping confidence intervals)
-
+#removing one point with large number of visits to see if this is driving the effect of total number of visits 
 novis<-subset(f.agg, f.agg$tot.visits.sc<2)
@@
 #table with results for paper
-Table2A<-round(summary(m2.fruit.net)$coefficients$cond, digits=2)
-rownames(Table2A)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Nestedness", "Niche complementarity")
+Table2A<-round(summary(m2.fruit.net)$coefficients$cond[,1:3], digits=2)
+rownames(Table2A)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Nestedness", "Pollinator niche complementarity")
 #at the end of paper
@@
         ylim(0.3,0.9) +
-        xlab("Niche complementarity") +      
+        xlab("Pollinator \n niche complementarity") +      
         ylab("Fruit set") + theme_bw()  + #theme (legend.position= "none") +
@@
 
-pred3<-summary(m2.fruit.net)$coefficients$cond[1]+ (summary(m2.fruit.net)$coefficients$cond[2] * mean(f.agg$species.poll.sc)) + (summary(m2.fruit.net)$coefficients$cond[3] * f.agg$tot.visits.sc) + (summary(m2.fruit.net)$coefficients$cond[4]* mean(f.agg$nodf.song.sc)) + (summary(m2.fruit.net)$coefficients$cond[5] * mean(f.agg$functional.comp.poll.sc))
-
-res3<-pred3-f.agg$mean.fruitset
-res.tr3<-exp(res3)/(1+exp(res3))
-
-pl4 <- ggplot(f.agg,  aes(x=tot.visits.sc, y= res.tr3)) +    
-        geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
-  stat_smooth(method = 'lm', size=1, se=TRUE, color = "black", alpha=0.4) +
-        ylim(0.3,0.9) +
-        xlab("Total number of visits") +      
-        ylab("Fruit set") + theme_bw()  + #theme (legend.position= "none") +
-        theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
-
 ```
@@
 Table2B<-round(summary(m2.seed.net)$coefficients[,1:3], digits=2)
-rownames(Table2B)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Nestedness", "Niche complementarity") #end of paper
+rownames(Table2B)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Nestedness", "Pollinator niche complementarity") #end of paper
 
@@
         #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
-        xlab("Niche complementarity") +      
+        xlab("Pollinator \n niche complementarity") +      
         ylab("Number of \n seeds per fruit") + theme_bw()  + #theme (legend.position= "none") +
@@
 
-Figure3<-plot_grid(pl3, pl4, pl2, pl6, labels = c("A", "B", "C", "D"), nrow=2)  
+Figure3<-plot_grid(pl3, pl2, pl6, labels = c("A", "B", "C"), nrow=1)  
 ```
@@
 At the site level, we find different patterns for fruit set and the number of seeds per fruit as compared to those for fruit and seed weight.
-In the case of fruit set and the number of seeds per fruit, we find that both model 1 and 2 are equally good in describing the differences observed (i.e.,$\Delta AIC<2$), and thus we are not able to choose one over the other [@Burnham2002].
-This suggests model 2 is a good model despite its added complexity, and actually shows a better predictive ability than model 1 (R^2 = `r round(r2.m2, 2)` for model 2 versus `r round(r2.m1, 2)` for model 1 in the case of fruit set and R^2 = `r round(r2.m2.seed,2)` for model 2 versus `r round(r2.m1.seed, 2)` for model 1 in the case of the number of seeds per fruit) and therefore we will comment results for this model only.
+In the case of fruit set and the number of seeds per fruit, we find that both model 1 and 2 are equally good in describing the differences observed when penalizing for model complexity (i.e.,$\Delta AIC<2$; [@Burnham2002]).
+This suggests model 2 is a good model despite its added complexity, and actually shows a substantially better predictive ability than model 1 (R^2 = `r round(r2.m2, 2)` for model 2 versus `r round(r2.m1, 2)` for model 1 in the case of fruit set and R^2 = `r round(r2.m2.seed,2)` for model 2 versus `r round(r2.m1.seed, 2)` for model 1 in the case of the number of seeds per fruit) and therefore we will comment results for this model only.
 In particular, we find that both fruit set and the number of seeds per fruit are positively related to niche complementarity between pollinators (Tables 2, Fig.
 3).
-Additionally, we find a negative effect of site-level pollinator richness and the total number of visits on average fruit set (Table 2A, Fig.
+Additionally, we find a negative effect of site-level pollinator richness on average fruit set (Table 2A, Fig.
 3).
-The number of visits for one of the sites was particularly large, yet this did not affect our results as removing this site from the analysis showed the same effect (Estimate $\pm$ SE = `r round(summary(m2.fruit.novis$sdr)[3], 2)` $\pm$ `r round(summary(m2.fruit.novis$sdr)[9], 2)`).
 
@@
 
-m1.fruitw.net<-glm(mean.fruitweight ~  species.poll.sc + tot.visits.sc, family="gaussian", data=s.comm)
+m1.fruitw.net<-lm(mean.fruitweight ~  species.poll.sc + tot.visits.sc, family="gaussian", data=s.comm)
 
@@
 
-m2.fruitw.net<-glm(mean.fruitweight ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="gaussian", data=s.comm)
+m2.fruitw.net<-lm(mean.fruitweight ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="gaussian", data=s.comm)
 
@@
 
-# crPlots(m1.fruitw.net, smooth=FALSE, terms = ~  species.poll.sc, main = "", ylab = "Mean fruit weight", col.lines= "black", pch=19, col= "black", bg = "darkgrey", cex=2, cex.axis=1.2, cex.lab=1.5, 
-#         xlab = "Pollinator species diversity") #end of paper
+ # crPlots(m1.fruitw.net, smooth=FALSE, terms = ~  species.poll.sc, main = "", ylab = "Fruit weight (g)", col.lines= "black", pch=16, col= "darkgrey",  cex=4, cex.axis=1.2, cex.lab=1.5, lwd=3, grid=FALSE, lty="solid",
+ #        xlab = "Pollinator richness") #end of paper
 
@@
 r2.seedw2<-r.squaredGLMM(m2.seedw.net)
+
+confint(m1.seedw.net)
 
@@
 
+Figure4<-plot_grid(pltest, pltest2, labels = c("A", "B"), nrow=1)
+
 ```
@@
 
-When evaluating the effect of differences in community composition and network structure for equity in reproductive success across the different species within a community we find that model 1 is the best model for all the thresholds considered (0.50, 0.25 and 0.75).
-Also, we find a significant negative relationship between equity and pollinator richness using the 0.75 threshold (Fig.
-4C, Tables S8, S9, S10).
+When evaluating the effect of differences in community composition and network structure for equity in reproductive success across the different species within a community we find that model 1 is the best model for all the thresholds considered (50^th, 25^th and 75^th percentiles).
+Here, none of the variables considered are able to explain differences observed in equity across sites (Tables S8, S9, S10).
 
@@
 
-#calculate number of sps per site producing more than 0.5 in fruitset
-
-highprod<-subset(f.ag, f.ag$mean.fruitset>0.5)
+#calculate 25th, 50th and 75th percentiles
+q<-quantile(f.ag$mean.fruitset, c(0.25, 0.50, 0.75))
+
+#calculate number of sps per site producing more 50th percentile in fruitset
+
+highprod<-subset(f.ag, f.ag$mean.fruitset>0.63)
 highprod.sps<-ddply(highprod, "Site_ID", summarise, 
@@
 
-#calculate number of sps per site producing more than 0.5 in fruitset
-
-highprod75<-subset(f.ag, f.ag$mean.fruitset>0.75)
+#calculate number of sps per site producing more than 75th percentile in fruitset
+
+highprod75<-subset(f.ag, f.ag$mean.fruitset>0.91)
 highprod75.sps<-ddply(highprod75, "Site_ID", summarise, 
@@
 
-#partial residual plots
-
 #test for problems in residuals
@@
 
-pred.eq<-summary(m1.eq.comm)$coef[1] + (summary(m1.eq.comm)$coef[2]*highprod75.sps$species.poll.sc) + (summary(m1.eq.comm)$coef[3]*mean(highprod75.sps$tot.visits.sc))
-
-res.eq<-pred.eq-highprod75.sps$equity
-res.eq.retro<-exp(res.eq)/(1+exp(res.eq))
-
-pl75 <- ggplot(highprod75.sps,  aes(x=species.poll.sc, y= res.eq.retro)) +    
-        geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
-  stat_smooth(method = 'lm', size=1, se=TRUE, color = "black", alpha=0.4) +    
-        xlab("Pollinator richness") +      
-        ylab("Equity in fruitset") + theme_bw()  + #theme (legend.position= "none") +
-        theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
-
-Figure4<-plot_grid(pltest, pltest2, pl75, labels = c("A", "B", "C"), nrow=1)  
 ```
@@
 
-#calculate number of sps per site producing more than 0.5 in fruitset
-
-highprod25<-subset(f.ag, f.ag$mean.fruitset>0.25)
+#calculate number of sps per site producing more than 25th percentile in fruitset
+
+highprod25<-subset(f.ag, f.ag$mean.fruitset>0.63)
 highprod25.sps<-ddply(highprod25, "Site_ID", summarise, 
@@
       temp1 <- Site_temp[which(Site_temp$Plant.sp %in% combinatorials_1[,j]),]
-      combinatorials_2 <- subset(temp1, temp1$fruit.prop > 0.5)
+      combinatorials_2 <- subset(temp1, temp1$fruit.prop > 0.8) #use 50th percentile
       if(dim(combinatorials_2)[1] == 0) {
@@
       #head(combinatorials_2)
-      #for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
+      #for each site here is the number of sps whose fruitset exceeds 50th percentile of maximum fruitset observed in the whole study area
       combinatorials_3 <- aggregate(no_rows ~ Site_ID, combinatorials_2, sum)
@@
 
-ggplot(s.comm,  aes(x=functional.comp.poll.sc, y=mean.seedset))+      
-        geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
-        #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
-        xlab("Niche complementarity") +      
-        ylab("Number of seeds/fruit") + theme_bw()  + #theme (legend.position= "none") +
-        theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
-
 ```
@@
 
-The existence of relationships between network structure and ecosystem function has been long hypothesized, yet, the specific mechanisms by which structure influences function have remained elusive until now [@Thompson2012].
+The existence of relationships between interaction network structure and ecosystem function have been long hypothesized, yet, the specific mechanisms by which structure influences function have remained elusive until now [@Thompson2012].
 Our results show that different aspects of network structure affect different dimensions of ecosystem functioning.
 In particular, we find that the centrality of a plant species within a community, which measures the number of connections it receives from other species in the community, has a positive effect for its fruit set.
-At the site level, we find that greater values of niche complementarity between pollinators result in larger average fruit sets.
-
-  One of the first conclusions we can extract from the fact that in most cases both of the models we considered (i.e., the simple model based on visitation metrics and the more complex one including network structure metrics) were equally good, is that for predictive purposes simple visitation metrics, such as pollinator richness, might be enough [@Garibaldi2013; @Garibaldi2015].
-Yet, a mechanistic understanding of the underlying processes driving these observed patterns requires that we take into account measures of network structure.
+At the site level, we find that greater values of niche complementarity between pollinators result in larger average fruit sets and number of seeds per fruit.
+
+  One of the first conclusions we can extract from the fact that in most cases both of the models we considered (i.e., the simple model based on visitation metrics and the more complex one including network structure metrics) were equally good, is that the added complexity of measuring the full network of interactions may not pay off for rapid assessments.
+Hence, simple visitation metrics, such as pollinator richness, might be enough [@Garibaldi2013; @Garibaldi2015].
+Yet, adding network level information may inform us of the potential ecological mechanisms underlying the processes driving these observed patterns.
 
@@
 This therefore reflects the fact that reproductive success in plant species requires the delivery of conspecific pollen and thus of a certain degree of specialization amongst pollinator species on a particular plant resource in order to avoid the negative effects of inter-specific pollen deposition (e.g., pollen loss [@Flanagan2009] or interference with conspecific pollen [@Morales2008]).
+However, we also find that some level of redundancy in these functions is needed as revealed by the positive effect of plant niche overlap on the number of seeds per fruit at the species level.
 
   In our study, we did not find an effect of nestedness for reproductive success in any case.
-This metric, widely used across network analysis, and which is deemed to stabilize [@Bastolla2009] or have a null effect [@James2012] on natural communities, does not seem to play a direct role in ecosystem function measured as plant reproductive success.
-However, our study is limited to a maximum of six plant species per community, and including more species might reveal different patterns, in which nestedness and the redundancy it implies might play a more important role.
-
-  Site-level plant reproductive success, measured as average fruit or seed set across all the species considered is an important part of the functions delivered by pollinators to plants.
+This metric, widely used across network analysis, and which is deemed to stabilize natural communities ([@Bastolla2009] but see [@James2012]), does not seem to play a direct role in ecosystem function measured as plant reproductive success.
+However, our study is limited to a maximum of six common plant species per community, and including more species, including rare species, might reveal different patterns, in which nestedness and the redundancy it implies might play a more important role.
+
+  Site-level plant reproductive success measured as average fruit or seed set across all the species considered, is an important part of the functions delivered by pollinators to plants.
 However, these average values might be masking a great deal of variability amongst plant species, and thus a nuanced view of the effect of pollinators on whole-plant ensembles is needed.
@@
   In the case of equity, we did not find a significant effect of either simple visitation or network structure metrics.
-However, the results of our simulation on the importance of network structure as the number of plant species considered increases, shows us that this effect dramatically increases when more than four plant species are considered.
-This implies that if we were able to measure reproductive success for all the plant species in all the communities (which is not feasible given constraints in sampling effort), we might find that the effects of network structure on equity might be even more prevalent.
-
-  One of the unexpected results of our analyses is the strong negative effect of pollinator richness for fruit set at the site level, as well as a negative effect on equity in reproductive success at the 0.75 threshold.
+However, the results of our simulation on the importance of network structure as the number of plant species considered increases, shows us that this effect increases when more than four plant species are considered.
+This implies that if we were able to measure reproductive success for all the plant species in all the communities (which is not feasible given constraints in sampling effort), we might find that the effects of network structure on equity might be more prevalent.
+
+  One of the unexpected results of our analyses is the strong negative effect of pollinator richness for fruit set at the site level.
 An explanation to this might be the fact that pollinator richness here includes all the pollinators recorded during our sampling efforts, i.e., it includes species that do not pollinate some of the species whose reproductive success was measured.
-More complex communities (with more pollinators, but also with more plant species, with a Pearson correlation value of 0.42 in our case) may require stabilizing mechanisms that reduce the competition exerted by the dominant plant species.
-This can be reached, for example, by a reduction in the reproductive success of the dominant species [@Lanuza2018], which are precisely those evaluated in this study.
-These ideas open the door to explore the positive or negative effects of the complete pollinator community on full plant species coexistence, which may be determined by density-dependence effects [@Benadi2018].
-In our case, while fruit set is negatively related to pollinator richness, fruit and seed weight show the opposite relationship, indicating that this density-dependent effect might only be limiting fruit quantity and not fruit quality.
-Thus, taking into account the co-flowering plant species densities may be the next step [@Vanbergen2014].
-
-  In summary, our findings show that the analysis of natural communities of interacting species using network analysis not only represents an ideal way of visualizing and grasping the complexity present within these communities, but also represents a manner of mechanistically understanding differences observed across the reproductive success of individuals and/or species.
+More complex communities with more pollinators, but also with more plant species (Pearson correlation between plant and pollinator richness  = 0.42 in our case) may require stabilizing mechanisms that reduce the competition exerted by the dominant plant species.
+A way to reduce the competition exerted by these dominant species, which are precisely those evaluated in this study, is by reducing their reproductive success [@Lanuza2018; @Stavert2019].
+These ideas open the door to exploring the positive or negative effects of the complete pollinator community on full plant species coexistence, which may be determined by density-dependence effects [@Benadi2018].
+In our case, while fruit set is negatively related to pollinator richness, it is important to note that fruit and seed weight show the opposite relationship, indicating that this density-dependent effect might only be limiting fruit quantity and not fruit quality.
+Thus, taking into account the densities of co-flowering plant species may be the next step [@Vanbergen2014].
+
+  Our study illustrates the complexity of linking network structure to ecosystem function empirically, because measuring both structure and function is challenging.
+For example, there is an ongoing debate as to which network metrics better reflect classic ecological mechanisms, such as niche partitioning or competition [@Delmas2019].
+Here, we focus on testing two specific hypotheses, but other structural properties can be explored when more data becomes available.
+Furthermore, the structure of plant-pollinators networks is dynamic due to ecological and evolutionary reasons, but so far, we are only able to characterize it for single snap-shots.
+Moreover, different aspects of functioning may be important, such as the presence of non-linear relationships or the need to consider the functioning of both trophic levels [@Godoy2018].
+In terms of plant reproductive success and the functions performed by pollinators we can measure different aspects, ranging from pollen deposition (the direct pollinator function), to its final effects on plant fitness.
+Here, we focus on an intermediate stage including fruit quantity and quality, which is of clear ecological importance.
+
+  In summary, our findings show that the analysis of natural communities of interacting species using network analysis not only represents an ideal way of visualizing and grasping the complexity present within these communities.
+Rather, it also represents a manner of mechanistically understanding differences observed across the reproductive success of individuals and/or species while linking them to potential ecological mechanisms.
 Future studies could build on this body of research by focusing on the long-lasting effects of network structure for plant fitness, by evaluating the consequences of different network structures on other stages of a plant´slife cycle (e.g., seed viability) and whether these differences are passed on to later generations (e.g., though different survival rates).
@@
 The authors would like to thank Oscar Aguado for help in identifying pollinator species.
+We would also like to acknowledge the efforts of the editor Cédric Gaucherel, as well as those of Michael Lattorff, Nicolas Deguines, and three anonymous reviewers who provided very helpful comments and suggestions in a previous version of this manuscript.
 AM received funding from a Juan de la Cierva (IJCI-2014-22558) and Ikerbasque fellowships.
@@
 ```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
-# extract coefficients and p-values for m2 and present them in paper
-# coefs.m2 <- data.frame(coef(summary(m2)))
-# Table1A<-round(coefs.m2[,1:3],digits=2)
-# rownames(Table1A)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Centrality", "Niche overlap")
-
-kable(Table1A, caption = "Table 1A.
-Results of GLMM showing effect of simple visitation and network structure metrics on species-level fruitset based on best model selected.
-Bold letters indicate significant variables.")
+
+knitr::kable(list(Table1A, Table1B), caption = "**Table 1**.
+Results of GLMM showing the effect of simple visitation and network structure metrics on A) species-level fruit set and B) average number of seeds per fruit based on best model selected.
+Bold letters indicate variables with large effects.")
 ```
@@
 ```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
-# # extract coefficients and p-values for m1 and present them in paper
-# coefs.m2.seed <- data.frame(coef(summary(m2.seed)))
-# # use normal distribution to approximate p-value
-# #coefs.m2.seed$p.z <- 2 * (1 - pnorm(abs(coefs.m2.seed$t.value)))
-
-# Table1B<-round(coefs.m2.seed,digits=2)
-# rownames(Table1B)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Centrality", "Niche overlap")
-
-kable(Table1B, caption = "Table 1B.
-Results of GLMM showing effect of simple visitation and network structure metrics on species-level number of seeds/fruit based on best model selected.
-Bold letters indicate significant variables.")
-```
-\newpage
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
-# #table with results for paper
-# Table2A<-round(summary(m2.fruit.net)$coefficients$cond[,1:3], digits=2)
-# rownames(Table2A)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Nestedness", "Niche complementarity")
-
-kable(Table2A, caption = "Table 2A. Results of GLM showing effect of simple visitation and network structure metrics on site-level average fruit set based on best model selected.")
-
-```
-\newpage
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
-# #save table with results for paper
-# Table2B<-round(summary(m2.seed.net)$coefficients[,1:3], digits=2)
-# rownames(Table2B)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Nestedness", "Niche complementarity")
-
-kable(Table2B, caption = "Table 2B. Results of GLM showing effect of simple visitation and network structure metrics on site-level average number of seeds per fruit based on best model selected.")
+knitr::kable(list(Table2A, Table2B), caption = "**Table 2**.
+Results of GLM showing effect of simple visitation and network structure metrics on A) site-level average fruit set and B) site-level average number of seeds per fruit based on best model selected.
+Bold letters indicate variables with large effects.")
+
 ```
@@
 
-**Figure 3.** Partial residual plots showing the effect of A) pollinator richness, B) total number of visits received and C) niche complementarity between pollinator species on site-level average fruitset and D) niche complemenarity between pollinator species on the average number of seeds per fruit at the site level.
-Dots represent average values of fruit set at the level of the site for all plant species considered (N=16 sites).
-
-**Figure 4.** Partial residual plots showing the effect of pollinator richness on site-level average A) fruit and B) seed weight and C) equity in reproductive success across species within a site (75% threshold).
-Dots represent values for each site (N=16 sites).
+**Figure 3.** Partial residual plots showing the effect of A) pollinator richness, and B) niche complementarity between pollinator species on site-level average fruitset and C) niche complementarity between pollinator species on the average number of seeds per fruit at the site level.
+Dots represent average values of fruit set at the level of the community for all plant species considered (N=16 sites).
+
+**Figure 4.** Partial residual plots showing the effect of pollinator richness on site-level average A) fruit and B) seed weight. Dots represent values for each site (N=16 sites).
 
@@
 #######FIG S1 SAMPLING COMPLETENESS 
-
-figures1<-plot_grid( poll, plant, link, ncol = 1)
-figures1
+#FigureS2<-plot_grid( poll, plant, link, ncol = 1)
+#FigureS2
 
@@
 
-**Figure S1.** Accumulation curves of pollinator, plant and plant-pollinator link richness with increasing sampling effort up to 100% sample coverage.
+**Figure S2.** Accumulation curves of pollinator, plant and plant-pollinator link richness with increasing sampling effort up to 100% sample coverage.
 Solid lines and points indicate observed richness while dashed lines show expected richness at increasing sample size, (i.e., extrapolated).
-
-\newpage
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=3, fig.width=4}
-
-crPlots(m1.fruitw.net, smooth=FALSE, terms = ~  species.poll.sc, main = "", ylab = "Mean fruit weight", col.lines= "black", pch=19, col= "black", bg = "darkgrey", cex=2, cex.axis=1.2, cex.lab=1.5, 
-        xlab = "Pollinator species diversity") #end of paper
-```
-
-**Figure S2.** Partial residual plots showing the effect of the total number of pollinator visits received at the site level on the average fruit weight.
-Dots represent average vaues at the level of the site for all plant species considered (N=16 sites).
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=8}
-crPlots(m1.seedw.net, smooth=FALSE,  main = "", ylab = "Mean seed weight", col.lines= "black", pch=19, col= "black", bg = "darkgrey", cex=2, cex.axis=1.2, cex.lab=1.5)
-```
-
-**Figure S3.** Partial residual plots showing the effect of the the diversity of pollinators and the total number of pollinator visits received at the site level on the average seed weight.
-Dots represent average vaues at the level of the site for all plant species considered (N=16 sites).
 

### 2019-08-08 paper_round2.Rmd
Redo sorensen
pequeños cambios

@@
 
-Within each site, we marked between 3 and `r max(f.inds$tot.inds)` individuals (mean $\pm$ SD: `r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`) belonging to `r min(tableS1$tot.sps)` to `r max(tableS1$tot.sps)` plant species (mean $\pm$ SD:`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`), depending on the availability and presence of flowers during the sampling events.
+Within each site, we marked between 3 and `r max(f.inds$tot.inds)` individuals (mean $\pm$ SD: `r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`, Table S2) belonging to `r min(tableS1$tot.sps)` to `r max(tableS1$tot.sps)` plant species (mean $\pm$ SD:`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`, Table S1), depending on the availability and presence of flowers during the sampling events.
 For each individual, at the end of the season, we
 recorded fruit set (i.e.
-the proportion of flowers that set fruit), the average number of seeds per fruit and the average fruit and seed weight per fruit (`r min(s.fruitnum$tot.fruits)`-`r max(s.fruitnum$tot.fruits)` fruits subsampled, mean $\pm$ SD: `r round(mean(s.fruitnum$tot.fruits), digits=2)` $\pm$ `r round(sd(s.fruitnum$tot.fruits), digits=2)`).
+the proportion of flowers that set fruit), the average number of seeds per fruit and the average fruit and seed weight per fruit (`r min(s.fruitnum$tot.fruits)`-`r max(s.fruitnum$tot.fruits)` fruits subsampled, mean $\pm$ SD: `r round(mean(s.fruitnum$tot.fruits), digits=2)` $\pm$ `r round(sd(s.fruitnum$tot.fruits), digits=2)`, Table S3).
 Our survey included a total of `r nlevels(f2$Plant.sp)` different plant species across our `r nlevels(f2$Site_ID)` sites.
@@
 The values at the species level were then averaged per site to calculate unique reproductive success measures at the site level.
-[X % of the plant species depend on pollinators to maximize their reproduction (Table SX).]()
+68% of the plant species depend on pollinators to maximize their reproduction (Table S4).
 
@@
   All of these metrics were calculated using all the data as well as for the subset of the data excluding interactions observed outside of sampling periods.
-Differences between results are minimal for both and thus we will only present results for the analysis using the full dataset (see Table S11A-H for results removing observations out of transect).
+Differences between results are minimal for both and thus we will only present results for the analysis using the full dataset (see Table S12A-H for results removing observations out of transect).
 
@@
 # extract estimates and st error for m1 and present them in paper
-tableS4<-round(summary(m1.seed.w)$coefficients$cond[,1:3], digits=2)
-rownames(tableS4)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
+tableS5<-round(summary(m1.seed.w)$coefficients$cond[,1:3], digits=2) #ch
+rownames(tableS5)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
 
@@
 # extract estimates and st error for m2 and present them in paper
-tableS5<-round(summary(m2.fruit.w)$coefficients$cond[,1:3], digits=2)
-rownames(tableS5)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Centrality", "Plant niche overlap")
+tableS6<-round(summary(m2.fruit.w)$coefficients$cond[,1:3], digits=2)#ch
+rownames(tableS6)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Centrality", "Plant niche overlap")
 
@@
  For all other measures of reproductive success considered (i.e., fruit and seed weight), both models had very similar fits, with ($\Delta AIC=2.2$) and 2, respectively.
-However, none of the variables included within our model explain the differences observed (Tables S4-S5).
+However, none of the variables included within our model explain the differences observed (Tables S5-S6).
 
@@
 At the site level, we find different patterns for fruit set and the number of seeds per fruit as compared to those for fruit and seed weight.
-In the case of fruit set and the number of seeds per fruit, we find that both model 1 and 2 are equally good in describing the differences observed when penalizing for model complexity (i.e.,$\Delta AIC<2$; [@Burnham2002]).
+In the case of fruit set and the number of seeds per fruit, we find that both model 1 and 2 are equally good in describing the differences observed when penalizing for model complexity (i.e.,$\Delta AIC<2$; [@Burnham2002a]).
 This suggests model 2 is a good model despite its added complexity, and actually shows a substantially better predictive ability than model 1 (R^2 = `r round(r2.m2, 2)` for model 2 versus `r round(r2.m1, 2)` for model 1 in the case of fruit set and R^2 = `r round(r2.m2.seed,2)` for model 2 versus `r round(r2.m1.seed, 2)` for model 1 in the case of the number of seeds per fruit) and therefore we will comment results for this model only.
@@
 #save table with results for paper
-tableS6<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)
-rownames(tableS6)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")#end of paper
+tableS7<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)#ch
+rownames(tableS7)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")#end of paper
 
@@
 #save table with results for paper
-tableS7<-round(summary(m1.seedw.net)$coef[,1:3], digits=2)
-rownames(tableS7) <-c("(Intercept)", "Pollinator species diversity", "Total number of visits")#end of paper
+tableS8<-round(summary(m1.seedw.net)$coef[,1:3], digits=2)#ch
+rownames(tableS8) <-c("(Intercept)", "Pollinator species diversity", "Total number of visits")#end of paper
 
@@
   Contrastingly, in the case of weight variables (fruit and seed weight), in both cases we find that the best model is model 1, i.e., that only including simple visitation metrics (R^2 = `r round(r2.fruitw1[2], 2)` in the case of fruit weight and `r round(r2.seedw1[2], 2)` in the case of seed weight).
-Here, we find a consistent positive effect of site-level pollinator richness for both weight descriptors (Tables S6-S7, Fig.
+Here, we find a consistent positive effect of site-level pollinator richness for both weight descriptors (Tables S7-S8, Fig.
 4).
@@
 When evaluating the effect of differences in community composition and network structure for equity in reproductive success across the different species within a community we find that model 1 is the best model for all the thresholds considered (50^th, 25^th and 75^th percentiles).
-Here, none of the variables considered are able to explain differences observed in equity across sites (Tables S8, S9, S10).
+Here, none of the variables considered are able to explain differences observed in equity across sites (Tables S9, S10, S11).
 
@@
 #save table with results for paper, both models are equally good so save both tables
-tableS8<-round(summary(m1.eq.comm)$coef[,1:3], digits=2)
-rownames(tableS8)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
+tableS9<-round(summary(m1.eq.comm)$coef[,1:3], digits=2)#ch
+rownames(tableS9)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
 
@@
 
-tableS9<-round(summary(m1.eq.comm75)$coef[,1:3], digits=2)
-rownames(tableS9)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
+tableS10<-round(summary(m1.eq.comm75)$coef[,1:3], digits=2)#ch
+rownames(tableS10)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
 
@@
 
-tableS10<-round(summary(m1.eq.comm25)$coef[,1:3], digits=2)
-rownames(tableS10)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
+tableS11<-round(summary(m1.eq.comm25)$coef[,1:3], digits=2)#ch
+rownames(tableS11)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
 
@@
 
-tableS4<-round(summary(m1.seed.w)$coefficients$cond[,1:3], digits=2)
-rownames(tableS4)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
-kable(tableS4, caption="Table S4. Results of GLMM showing effect of simple visitation metrics on species-level average seed weight based on best model selected.")
-
-tableS5<-round(summary(m1.fruit.w)$coefficients$cond[,1:3], digits=2)
+tableS5<-round(summary(m1.seed.w)$coefficients$cond[,1:3], digits=2)
 rownames(tableS5)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
-kable(tableS5, caption="Table S5. Results of GLMM showing effect of simple visitation metrics on species-level average fruit weight based on best model selected.")
+kable(tableS5, caption="Table S5. Results of GLMM showing effect of simple visitation metrics on species-level average seed weight based on best model selected.")
+
+tableS6<-round(summary(m1.fruit.w)$coefficients$cond[,1:3], digits=2)
+rownames(tableS6)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
+kable(tableS6, caption="Table S6. Results of GLMM showing effect of simple visitation metrics on species-level average fruit weight based on best model selected.")
 ```
@@
 
-tableS6<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)
-rownames(tableS6)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
-
-kable(tableS6, caption="Table S6. Results of GLM showing effect of simple visitation metrics on site-level average fruit weight based on best model selected.")
+tableS7<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)
+rownames(tableS7)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
+
+kable(tableS7, caption="Table S7. Results of GLM showing effect of simple visitation metrics on site-level average fruit weight based on best model selected.")
 ```
@@
 #save table with results for paper
-tableS7<-round(summary(m1.seedw.net)$coef[,1:3], digits=2)
-rownames(tableS7) <-c("(Intercept)", "Pollinator richness", "Total number of visits")
-
-kable(tableS7, caption="Table S7. Results of GLM showing effect of simple visitation metrics on site-level average seed weight based on best model selected.")
+tableS8<-round(summary(m1.seedw.net)$coef[,1:3], digits=2)
+rownames(tableS8) <-c("(Intercept)", "Pollinator richness", "Total number of visits")
+
+kable(tableS8, caption="Table S8. Results of GLM showing effect of simple visitation metrics on site-level average seed weight based on best model selected.")
 ```
@@
 
-kable(tableS8, caption="Table S8.
+kable(tableS9, caption="Table S9.
 Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a site based on best model selected (0.50 threshold).")
 
-kable(tableS9, caption="Table S9.
+kable(tableS10, caption="Table S10.
 Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a site based on best model selected (0.75 threshold).")
 
-kable(tableS10, caption="Table S10.
+kable(tableS11, caption="Table S11.
 Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a site based on best model selected (0.25 threshold).")

### 2019-08-08 Data_and_code_Song_et_al_2017/example.R
cleaning

@@ -1,12 +1,0 @@
-#R-code of "Why are some plant-pollinator networks more nested than others?" by:
-#Chuliang Song, Rudolf P. Rohr, and Serguei Saavedra
-#Journal of Animal Ecology
-rm(list=ls())
-source('toolbox.R') #load the toolbox
-
-web <- load_data() #load network.csv
-print(NODF <- nestedness_NODF(web)) # this calculates the raw value of NODF
-print(max_NODF <- max_nest(web)) # this calculates the maximum value of NODF for that network
-print(combined_NODF <- comb_nest(web,NODF,max_NODF)) # this calculates the combined NODF statistic as described in the manuscript
-
-

### 2019-08-08 Simmons.R

@@ -1,121 +1,0 @@
-#test simmons algorithm
-
-#First I use Song example to keep it simple----
-# I also aim to load as less packages as possile to avoid conflicts
-
-#Song approach
-source('Data_and_code_Song_et_al_2017/toolbox.R') #load the toolbox
-
-web <- read.csv("Data_and_code_Song_et_al_2017/network.csv") #load network.csv
-web <- as.matrix(web)
-head(web)
-print(NODF <- nestedness_NODF(web)) # this calculates the raw value of NODF
-print(max_NODF_S <- max_nest(web)) # this calculates the maximum value of NODF for that network
-print(combined_NODF_S <- comb_nest(web,NODF,max_NODF_S)) # this calculates the combined NODF statistic as described in the manuscript
-#works as expected.
-
-#Now Simmons approach. 
-#NODF <- nestedness_NODF(web) # this calculates the raw value of NODF #as in song
-devtools::install_github("CHoeppke/maxnodf")
-library(maxnodf)
-max_NODF <- maxnodf(web=web, quality=2) # this calculates the maximum value of NODF for that network, based on Simmons correction of Song
-#Error in maxnodf(web = web, quality = 2) : 
- #Invalid network. Ensure all row and column totals are >= 1.
-colSums(web)
-web2 <- web[,-which(colSums(web) < 0.1)]
-#start again
-nestedness_NODF(web)
-(NODF <- nestedness_NODF(web2)) # Fuck, this value changes!!
-max_NODF <- maxnodf(web=web2, quality=2) # this calculates the maximum value of NODF for that network, based on Simmons correction of Song
-#interestin max_nest(web2) has the same exact value!!
-max_NODF_S == max_NODF$max_nodf
-max_nest(web2) == max_NODF$max_nodf
-#combine
-combined_NODF <- comb_nest(web2,NODF,max_NODF$max_nodf) # this calculates the combined NODF statistic as described in the manuscript
-#compatre
-combined_NODF_S == combined_NODF #FALSE
-comb_nest(web2,NODF,max_nest(web2)) == combined_NODF #TRUE
-
-#test issue links > ncol + nrows
-sum(web2)
-ncol(web2) + nrow(web2)
-
-#for failing in network analysis.R
-sum(web4)
-ncol(web4) + nrow(web4) #small difference!
-
-#opening up the black box
-
-#debugged using web4, which should fail.
-web = web4
[…]

### 2019-08-08 scripts/motif analyses.R

@@ -1,146 +1,0 @@
-
-#First attempt to load the data, etc...
-
-#prepare stuff-----
-#If you don't have devtools install it
-#install.packages("devtools")
-library(devtools)
-#Then install the data package. Reprot issues 
-#install_github("ibartomeus/BeeFunData", ref = "fun")
-library(BeeFunData)
-
-
-# load packages
-library(bmotif)
-library(vegan)
-
-#make the data available
-data(all_interactions)
-head(all_interactions)
-
-
-#analysis...----
-
-setwd("~/Dropbox/Beefun/Beefun/functioning")
-
-d<-all_interactions
-f<-fruitset
-s<-seedset
-
-
-d2<-subset(d, d$Plant_gen_sp!="NA NA")
-d2$Plant_gen_sp
-
-sites <- unique(d2$Site_ID)
-
-
-empty_web <- function(x) {
-  # Removes all-zero rows and columns from a matrix
-  cempty <- which(colSums(x) == 0)
-  rempty <- which(rowSums(x) == 0)
-  if(length(rempty) != 0 & length(cempty) == 0){
-    return(x[-rempty,,drop = FALSE])
-  } else if(length(rempty) == 0 & length(cempty) != 0){
-    return(x[,-cempty,drop = FALSE])
-  } else if(length(rempty) != 0 & length(cempty) != 0){
-    return(x[-rempty,-cempty,drop = FALSE])
-  } else if(length(rempty) == 0 & length(cempty) == 0){
-    return(x)
-  }
-}
-
-
-webs <- list()
-webs.or3<-list()
-for(i in 1:length(sites)){
-  temp <- subset(d2, Site_ID == sites[i])
-  # for(j in 1:length(rounds)){
-  #   temp2 <- subset(temp, Round == rounds[j])
-  #   if (nrow(temp2) == 0) next
-  
-  web <- as.matrix.data.frame(table(temp$Plant_gen_sp, temp$Pollinator_gen_sp))
-  web.or<-table(temp$Plant_gen_sp, temp$Pollinator_gen_sp)#keeps names of species
-  
-  web2<-empty_web(web)
-  web.or2<-empty_web(web.or)
-    
-  webs.or3[[i]]<-web.or2 #keeps names of species
-  webs[[i]]<-as.matrix(web2)
-}
-
-names(webs)<-sites
-names(webs.or3)<-sites
-
-out <- data.frame(web = NA, nrow = NA)
-
[…]

### 2019-08-08 scripts/motif analyses2.R

@@ -1,155 +1,0 @@
-
-
-Now look at motifs and indirect interactions. To this end, we compare the roles of plant species at each site with low (<0.5) and high (>0.5) fruit set. We calculate for each plant species at each site the sum-normalised roles of all plant species in motifs up to 5 nodes and plot them using NMDS. ALthough we find a large overlap between the roles of both types ofplant species, we do find that plant species with high fruit set tend to be located in the higher values of NMDS1 which is related to network positions in which a generalist plant species interacts with highly specialized pollinator partners (e.g, positions 16 and 46, see Fig. 1 in bmotif paper, Simmons et al preprint)
-
-#IB edited this in paper.Rmd
-#First attempt to load the data, etc...
-
-#prepare stuff-----
-#If you don't have devtools install it
-#install.packages("devtools")
-library(devtools)
-#Then install the data package. Reprot issues 
-#install_github("ibartomeus/BeeFunData", ref = "fun")
-library(BeeFunData)
-
-
-# load packages
-library(bmotif)
-library(vegan)
-
-#make the data available
-#analysis...----
-
-
-d<-all_interactions
-f<-fruitset
-s<-seedset
-
-
-d2<-subset(d, d$Plant_gen_sp!="NA NA")
-#d2$Plant_gen_sp
-
-sites <- unique(d2$Site_ID)
-
-
-empty_web <- function(x) {
-  # Removes all-zero rows and columns from a matrix
-  cempty <- which(colSums(x) == 0)
-  rempty <- which(rowSums(x) == 0)
-  if(length(rempty) != 0 & length(cempty) == 0){
-    return(x[-rempty,,drop = FALSE])
-  } else if(length(rempty) == 0 & length(cempty) != 0){
-    return(x[,-cempty,drop = FALSE])
-  } else if(length(rempty) != 0 & length(cempty) != 0){
-    return(x[-rempty,-cempty,drop = FALSE])
-  } else if(length(rempty) == 0 & length(cempty) == 0){
-    return(x)
-  }
-}
-
-
-webs <- list()
-webs.or3<-list()
-for(i in 1:length(sites)){
[…]

### 2019-08-08 scripts/niche overlap.R

@@ -1,32 +1,0 @@
-#calculate average niche overlap
-
-library(reshape2)
-library(spaa)
-sites <- unique(d$Site_ID)
-
-out.niche <- data.frame(Site_id = NA, row = NA, col = NA,value  = NA)
-
-webs <- list()
-for(i in 1:length(sites)){
-  temp <- subset(d, Site_ID == sites[i])
-  temp2<-droplevels(temp)
- 
-  web <- table(temp2$Pollinator_gen_sp, temp2$Plant_gen_sp)
-
-  ni<-niche.overlap(web, method="morisita")
-  df <- melt(as.matrix(ni), varnames = c("row", "col"))
-  df$row<-as.character(df$row)
-  df$col<-as.character(df$col)
-  
-  n <- nrow(out.niche)
- 
-  out.niche[n + seq(nrow(df)),1] <- as.character(sites[i])
-  out.niche[n + seq(nrow(df)),2:3] <- (df[,1:2])
-  out.niche[n + seq(nrow(df)),4] <-df[,3]
-  
-}
-
-
-
-out.niche.agg <- ddply(out.niche, c("Site_id", "col"), summarise,
-               mean.niche.over    = mean(value))

### 2019-08-08 scripts/path analysis.R

@@ -1,89 +1,0 @@
-
-
-library(lavaan)
-library(semPlot)
-library(OpenMx)
-library(tidyverse)
-library(knitr)
-library(kableExtra)
-library(GGally)
-
-# Organizing package information for table
-packages <- c("tidyverse", "knitr", "kableExtra", "lavaan", "semPlot", "OpenMx", "GGally")
-display <- c("Package","Title", "Maintainer", "Version", "URL")
-table <- matrix(NA, 1, NROW(display), dimnames = list(1, display))
-for(i in 1:NROW(packages)){
-  list <- packageDescription(packages[i])
-  table <- rbind(table, matrix(unlist(list[c(display)]), 1, NROW(display), byrow = T))
-}
-table[,NROW(display)] <- stringr::str_extract(table[,NROW(display)], ".+,")
-
-# Table of packages
-kable(table[-1,], format = "html", align = "c") %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
-
-
-
-
-#species level 
-
-
-model <-'
-tot.fruitset ~ norm_degree.sc  + tot.visits.sc + 
-weigh_closeness.sc + niche.overlap.sc
-'
-
-
-fit <- cfa(model, data = f2_scaled)
-summary(fit, fit.measures = TRUE, standardized=T,rsquare=T)
-
-semPaths(fit, 'std', layout = 'circle')
-
-semPaths(fit,"std",layout = 'tree', edge.label.cex=.9, curvePivot = TRUE)
-
-
-
-ggcorr(f2_scaled[,c(14, 26:29)], nbreaks = 6, label = T, low = "red3", high = "green3", 
-       label_round = 2, name = "Correlation Scale", label_alpha = T, hjust = 0.75) +
-  ggtitle(label = "Correlation Plot") +
-  theme(plot.title = element_text(hjust = 0.6))
-
-
-
-
-
-#community level
-
-model <-'
-mean.fruitset ~ species.poll.sc + tot.visits.sc + nodf.song.sc + 
-functional.comp.poll.sc
-'
-
-
-fit <- cfa(model, data = f.agg)
-summary(fit, fit.measures = TRUE, standardized=T,rsquare=T)
-
-semPaths(fit, 'std', layout = 'circle')
-
[…]

### 2019-08-08 Network_structure_and_function.Rmd
rmd

--- 2019-08-08 paper_round2.Rmd
@@
 Plant reproductive success requires of the delivery of conspecific pollen and thus of a certain degree of niche complementarity [@Bluthgen2011].
-Yet, greater values of nestedness, which imply redundancy in species functions, are thought to promote species diversity [@Bastolla2009] and stability [@Thebault2010a] within plant-polllinator networks.
+Yet, greater values of nestedness, which imply redundancy in species functions, are thought to promote species diversity [@Bastolla2009] and stability [@Thebault2010a] within plant-pollinator networks.
 At present, we do not know how either of these network characteristics affects the functions performed by pollinators.
@@
 d.beta[d.beta>1]<-1 #make it binary
-d.betadiv<-beta.multi(d.beta)
-sor<-d.betadiv[3]
-
+d.betadiv<-mean(betadiver(d.beta, method = 11)) 
+#summary(betadiver(d.beta, method = 11)) #max value 0.66.
 ```
@@
 1).
-All sites were located within similar elevations (ranging from 50 to 150 m a.s.l.), similar habitat and soil types, and presented similar plant compositions (plant mean Sørensen beta-diversity among sites = `r round(sor$beta.SOR, 2)`), reducing potential confounding factors.
+All sites were located within similar elevations (ranging from 50 to 150 m a.s.l.), similar habitat and soil types, and presented similar plant composition (plant mean Sørensen beta-diversity among sites = `r round(d.betadiv, 2)`), reducing potential confounding factors.
 Here, we surveyed 16 Mediterranean woodland patches with an average distance of 7 km between them (min= 3 km, max= 46.5 km).
@@
 Along each transect, we identified all plant species and recorded all the floral visitors that landed on their flowers during each 30-min period.
-Only floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FPM with the aid of experts in the different taxonomic groups (see acknowledgements).
+Only floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FPM and experts in the different taxonomic groups (see acknowledgements).
 In addition, at each round we conducted 3 minutes of focal observations recording all floral visitors observed on 3 plant individuals per species belonging to the 19 most common (based on previous surveys) plant species across the study area (mean $\pm$ SD: `r round(mean(foc3$tot.species), digits=2)` $\pm$ `r round(sd(foc3$tot.species), digits=2)` species per site).
@@
 The values at the species level were then averaged per site to calculate unique reproductive success measures at the site level.
-68% of the plant species depend on pollinators to maximize their reproduction (Table S4).
+All plant species depend on pollinators to maximize their reproduction (Table S4).
 
@@
   In order to analyse how differences in network structure might affect plant reproductive success, we constructed plant-pollinator interaction networks by pooling the data for the 7 rounds of sampling.
-We thus obtained one interaction network per site, representing the incidence of visits by different pollinator species to different plant species.
+We thus obtained one interaction network per site, representing the number of individuals of different pollinator species recorded visiting each different plant species.
 For each network, we then proceeded to extract a series of relevant network metrics at the species and site levels.
 
-  In addition, we checked for potential spatial autocorrelation in our data by means of Mantel correlograms. Autocorrelation values were low for all variables included in our analyses (Figure S1).
+  In addition, we checked for potential spatial autocorrelation in our data by means of Mantel correlograms.
+Autocorrelation values were low for all variables included in our analyses (Figure S1) and hence we treat each site as independent in our analysis.
 
@@
 As explanatory variables, model 1 included pollinator richness, and the total number of visits received by each plant species; while model 2 added the two network attributes calculated at the species level: average plant niche overlap and centrality.
-For both models, we included plant species nested within site and site as random effects to account for the non-indepedence of several individuals measured per species and site.
+For both models, we included plant species nested within site and site as random effects to account for the non-independence of several individuals measured per species and site.
 
@@
 As response variables we had the average reproductive success per site (i.e., average fruit set analyzed using a binomial distribution, average number of seeds per fruit and average fruit and seed weight using a normal distribution).
-We thus had a single value per site and no random effects are needed in this case.
+We thus had a single value per site and no random effects are needed.
 In this case, model 1 included total pollinator richness and total pollinator abundance (i.e.
@@
 We expect that the more plants considered, the larger the resulting average estimates will be.
-Note that we only interpret the mean effects, as the variance among different plant number of species considered depends on the initial number of combinations.
+Note that we only interpret the mean effects, as the variance among different plant number of species considered depends on the initial number of possible combinations.
 
@@
 
-At the species level, in the case of fruit set, our results show that model 2 shows the best fit to our data (lowest AIC value), explaining `r round(r2$Marginal[1], 2)*100`% of the variability observed.
+At the species level, in the case of fruit set, our results show that model 2 shows the best fit to our data (lowest AIC value), and fixed  effects explains `r round(r2$Marginal[1], 2)*100`% of the variability observed.
 In this case, we find a positive effect of a network structure metric, the centrality of a focal plant within the overall network on its fruit set (Table 1, Fig.
@@
 
- For the average number of seeds per fruit, our results show again that model 2 shows the best fit, explaining `r round(r2b$Marginal[1], 2)*100`% of the variability observed in our data.
+ For the average number of seeds per fruit, our results show again that model 2 shows the best fit, with fixed effects explaining `r round(r2b$Marginal[1], 2)*100`% of the variability observed in our data.
 In this case, we find a positive effect of the niche overlap between plant species on the number of seeds produced (Table 1B, Fig.
@@
 When evaluating the effect of differences in community composition and network structure for equity in reproductive success across the different species within a community we find that model 1 is the best model for all the thresholds considered (50^th, 25^th and 75^th percentiles).
-Here, none of the variables considered are able to explain differences observed in equity across sites (Tables S9, S10, S11).
+However, none of the variables considered are able to explain differences observed in equity across sites (Tables S9, S10, S11).
 
@@
   One of the first conclusions we can extract from the fact that in most cases both of the models we considered (i.e., the simple model based on visitation metrics and the more complex one including network structure metrics) were equally good, is that the added complexity of measuring the full network of interactions may not pay off for rapid assessments.
-Hence, simple visitation metrics, such as pollinator richness, might be enough [@Garibaldi2013; @Garibaldi2015].
+Hence, simple visitation metrics, such as pollinator richness, might be enough to describe general patterns [@Garibaldi2013; @Garibaldi2015].
 Yet, adding network level information may inform us of the potential ecological mechanisms underlying the processes driving these observed patterns.
@@
 
-  In the case of equity, we did not find a significant effect of either simple visitation or network structure metrics.
+  In the case of equity, we did not find a strong effect of either simple visitation or network structure metrics.
 However, the results of our simulation on the importance of network structure as the number of plant species considered increases, shows us that this effect increases when more than four plant species are considered.
@@
 Rather, it also represents a manner of mechanistically understanding differences observed across the reproductive success of individuals and/or species while linking them to potential ecological mechanisms.
-Future studies could build on this body of research by focusing on the long-lasting effects of network structure for plant fitness, by evaluating the consequences of different network structures on other stages of a plant´slife cycle (e.g., seed viability) and whether these differences are passed on to later generations (e.g., though different survival rates).
 
@@
 
-The authors would like to thank Oscar Aguado for help in identifying pollinator species.
+The authors would like to thank Oscar Aguado for identifying pollinator species.
 We would also like to acknowledge the efforts of the editor Cédric Gaucherel, as well as those of Michael Lattorff, Nicolas Deguines, and three anonymous reviewers who provided very helpful comments and suggestions in a previous version of this manuscript.

### 2019-08-08 Network_structure_and_function.Rmd
data accessibility
clean up

@@
 d.beta<-table(d.sub$Site_ID, d.sub$Plant_gen_sp)
-d.beta[d.beta>1]<-1 #make it binary
+d.beta[d.beta>1]<-1 
 d.betadiv<-mean(betadiver(d.beta, method = 11)) 
@@
 
-#plot significant variables, in this case centrality and visits, do partial residual plots to show the effect of that variable in isolation of the others
-
 #devtools::install_github("hohenstein/remef")  USE THIS PACKAGE TO DO PARTIAL RESIDUAL PLOTS OF SIGNIFICANT VARIABLES
@@
 
-#removing one point with large number of visits to see if this is driving the effect of total number of visits 
-novis<-subset(f.agg, f.agg$tot.visits.sc<2)
-
- m2.fruit.novis<-glmmTMB(mean.fruitset ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="beta_family", data=novis)
-
- summary(m2.fruit.novis) #still non-overlapping values
-
 #select best model based on AIC
@@
 
- # crPlots(m1.fruitw.net, smooth=FALSE, terms = ~  species.poll.sc, main = "", ylab = "Fruit weight (g)", col.lines= "black", pch=16, col= "darkgrey",  cex=4, cex.axis=1.2, cex.lab=1.5, lwd=3, grid=FALSE, lty="solid",
- #        xlab = "Pollinator richness") #end of paper
-
 ```
@@
 
-# crPlots(m1.seedw.net, smooth=FALSE,  main = "", ylab = "Mean seed weight", col.lines= "black", pch=19, col= "black", bg = "darkgrey", cex=2, cex.axis=1.2, cex.lab=1.5)
-
 Figure4<-plot_grid(pltest, pltest2, labels = c("A", "B"), nrow=1)
@@
 table(f4$Plant.sp)
-#Astragalus lusitanicus and Cistus albidus is causing problems later on.
-It has a very low fruit set, but as there is only one value, when correcting for max fruit set, gets a value of 1.
-Both are in Cotito...
-This is problematic.
-Similar with Anchusa azurea.
-
+#Astragalus lusitanicus and Cistus albidus are causing problems because they have very low fruit set, but as there is only one value, when correcting for max fruit set, gets a value of 1. 
 #I am removing them here.
@@
 
+**Data accessibility**
+
+All the data used is available https://zenodo.org/account/settings/github/repository/ibartomeus/BeeFunData 
+and the code used to generate all results can be found at https://doi.org/10.5281/zenodo.3364037.
+
 **Acknowledgements**

### 2019-08-10 scripts/network analysis.R
network analysis

@@ -37,12 +37,7 @@ for(i in 1:length(sites)){
   temp <- subset(d, Site_ID == sites[i])
   
   
-  # 
-  # temp2<-droplevels(ddply(temp, c("Plant_gen_sp", "Pollinator_gen_sp"), 
-  #               summarise,
-  #               tot.visits= sum(Frequency)))
-  # 
-  # web<-as.data.frame.matrix(xtabs(tot.visits ~ Plant_gen_sp + Pollinator_gen_sp, temp2))
+
   web<-table(temp$Plant_gen_sp, temp$Pollinator_gen_sp)
   
    #p1<-plotweb(web)
@@ -51,7 +46,7 @@ for(i in 1:length(sites)){
   if(isTRUE(class(spntw)=="try-error")) {next} 
   
   #song et al nestedness corrected with NODF max by Simmons et al
-  #web2<-table(temp2$Plant_gen_sp, temp2$Pollinator_gen_sp) #song uses incidence so we calculate the table with incidence rather than freq here
+  
   #remove all columns and rows with all values=0
   web3 <- web[, colSums(web != 0) > 0] 
   web4 <- web3[rowSums(web3[, -1] > 0) != 0, ]
@@ -66,10 +61,7 @@ for(i in 1:length(sites)){
       combined_NODF <- comb_nest(web4,NODF,max_NODF$max_nodf) # this calculates the combined NODF statistic as described in the manuscript
     }
   
-   # NODF <- nestedness_NODF(web4) # this calculates the raw value of NODF as in Song
-   # max_NODF <- max_nest(web4)
-   # combined_NODF <- comb_nest(web4,NODF,max_NODF)
-  # 
+   
   
   n <- nrow(out.site)
   webs[[n]] <- web4  

### 2019-11-20 Network_structure_and_function.Rmd
affiliation
Small changes after second round of reviews in PCI Ecology

@@
 
-Ainhoa Magrach^1^, Francisco P. Molina^2^, Ignasi Bartomeus^2^
+Ainhoa Magrach^1^ ^2^, Francisco P. Molina^3^, Ignasi Bartomeus^3^
 
@@
 
-^2Estación Biológica de Doñana (EBD-CSIC), Avda. Américo Vespucio 26, Isla de la Cartuja, 41092, Sevilla, Spain
+^2^IKERBASQUE, Basque Foundation for Science, María Díaz de Haro 3, 48013, Bilbao, Spain
+
+^3^Estación Biológica de Doñana (EBD-CSIC), Avda. Américo Vespucio 26, Isla de la Cartuja, 41092, Sevilla, Spain
 
@@
 However, research has focused primarily on pairwise plant-pollinator interactions, largely overlooking community-level dynamics.
-Yet species do not interact in isolation, they are embedded within larger networks whose structure can affect pollinator functional roles and, ultimately, the pollination services they deliver to plants.
 Here, we present one of the first efforts linking pollinator visitation to plant reproduction from a community-wide perspective using a well-replicated dataset encompassing 16 well-resolved plant-pollinator networks and data on reproductive success for 19 plant species from Mediterranean shrub ecosystems.
-We find that models including information on simple visitation metrics alone are good in explaining the variability in reproductive success observed.
-However, insights into the mechanisms through which differences in pollinator diversity translate into changes in reproductive success require additional information on network structure, particularly that reflecting niche complementarity between pollinators.
+We find that models including simple visitation metrics are good in explaining the variability in reproductive success observed.
+However, insights into the mechanisms through which differences in pollinator diversity translate into changes in reproductive success require additional information on network structure.
 Specifically, we find a positive effect of increasing niche complementarity between pollinators on plant reproductive success.
+This shows that maintaining communities with a diversity of species but also of functions is paramount to preserving natural ecosystems.
 
@@
 Amongst them is the prevalence of nested structures, i.e., arrangements where specialist species interact with a subset of the species that generalists interact with [@Bascompte2003] and which is thought to promote species diversity [@Bastolla2009]; or the relatively high extent of complementary specialization at the community scale, which may be directly related to key ecosystem functions [@Bluthgen2011].
-However, the mechanisms by which these potential pathways affect plant reproduction remain to be understood [@Winfree2013].
+However, the mechanisms by which these attributes affect plant reproduction remain to be understood [@Winfree2013].
 The time is thus ripe to use the existing knowledge around plant-pollinator network structures to explore the relationship between network structure and ecosystem functioning empirically, with special emphasis being placed on the underlying ecological mechanisms that drive these relationships.
@@
 As a measure of centrality, we used weighted closeness centrality, which represents the number of shortest paths going through a focal plant based on a unipartite projection of the bipartite plant-pollinator network using a weighted representation of the network [@Dormann2009].
-Here, links between plant species represent shared pollinator species.
+With this method, links between plant species represent shared pollinator species.
 
@@
 
-In order to evaluate whether adding information on network structure improves our ability to explain differences in reproductive success - both at the species and the site level - we used generalized linear (GLMs) and generalized linear mixed models (GLMMs).
+In order to evaluate whether adding information on network structure improves our ability to explain differences in reproductive success - both at the species and the site level - we used generalized linear (GLMs) and generalized linear mixed models (GLMMs) respectively.
 In both cases (species and site-level models) we fit two types of models: (i) model 1, that only included simple visitation metrics and (ii) model 2 that additionally included information on network structure.
@@
 
-  At the species level, response variables included the fruit set for different individuals of each species analyzed using a binomial distribution, the average number of seeds per fruit analyzed using a normal distribution, and the average values of fruit and seed weight fitted to Poisson distributions.
+  At the species level, response variables included the fruit set for different individuals of each species analyzed using a binomial distribution and the average number of seeds per fruit, the average fruit and seed weight fitted using normal distributions.
 The number of seeds per fruit was centered and scaled (i.e., we subtracted column means and divided by standard deviation) to allow meaningful comparisons across species with contrasting life histories.
@@
   geom_point(size=2.5, shape=21,color = "black", aes(fill=factor(Plant.sp))) + 
-  stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
+  stat_smooth(method=glm,  method.args = list(family = "binomial"), size=1, se=TRUE, color = "black", alpha=0.4) + 
   xlab("Centrality") +      
@@
 
-m1.seed.w<-glmmTMB(mean.seedw ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="poisson", data=s3)
+m1.seed.w<-glmmTMB(mean.seedw ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3)
 
@@
 
-m2.seed.w<-glmmTMB(mean.seedw ~  pollspsperplant.sc + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="poisson", data=s3)
+m2.seed.w<-glmmTMB(mean.seedw ~  pollspsperplant.sc + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3)
 
@@
 
-m1.fruit.w<-glmmTMB(mean.fruitweight ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="poisson", data=s3)
+m1.fruit.w<-glmmTMB(mean.fruitweight ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3)
 
@@
 
-m2.fruit.w<-glmmTMB(mean.fruitweight ~  pollspsperplant.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="poisson", data=s3)
+m2.fruit.w<-glmmTMB(mean.fruitweight ~  pollspsperplant.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3)
 
@@
 # extract estimates and st error for m2 and present them in paper
-tableS6<-round(summary(m2.fruit.w)$coefficients$cond[,1:3], digits=2)#ch
-rownames(tableS6)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Centrality", "Plant niche overlap")
-
-```
- For all other measures of reproductive success considered (i.e., fruit and seed weight), both models had very similar fits, with ($\Delta AIC=2.2$) and 2, respectively.
+tableS6<-round(summary(m1.fruit.w)$coefficients$cond[,1:3], digits=2)#ch
+rownames(tableS6)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
+
+```
+ For all other measures of reproductive success considered (i.e., fruit and seed weight), model 1 showed the best fit.
 However, none of the variables included within our model explain the differences observed (Tables S5-S6).
@@
 #save table with results for paper
-tableS7<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)#ch
-rownames(tableS7)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")#end of paper
+tableS7A<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)#ch
+rownames(tableS7A)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")#end of paper
 
@@
 
+#There is one point that has a larger pollinator diversity than the rest. To test if this point by itself might be driving the whole relationship we are repeating analyses removing this one point.
+
+s.comm2<-subset(s.comm ,s.comm$species.poll.sc<1.9)
+
+m1.fruitw.net2<-lm(mean.fruitweight ~  species.poll.sc + tot.visits.sc, family="gaussian", data=s.comm2)
+
+summary(m1.fruitw.net2)
+
+vif(m1.fruitw.net2)
+
+m2.fruitw.net2<-lm(mean.fruitweight ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="gaussian", data=s.comm2)
+
+summary(m2.fruitw.net2)
+
+vif(m2.fruitw.net2)
+
+#select best model based on AIC
+
+AICtab(m1.fruitw.net2, m2.fruitw.net2)
+
+#save table with results for paper
+tableS7B<-round(summary(m1.fruitw.net2)$coef[,1:3], digits=2)#ch
+rownames(tableS7B)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")#end of paper
+
+predtestb<-summary(m1.fruitw.net2)$coefficients[1]+ (summary(m1.fruitw.net2)$coefficients[2] * s.comm2$species.poll.sc) + (summary(m1.fruitw.net2)$coefficients[3] * mean(s.comm2$tot.visits.sc))
+
+restestb<-predtestb-s.comm2$mean.fruitweight
+
+pltestb <- ggplot(s.comm2,  aes(x=species.poll.sc, y= restestb)) +    
+  geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
+  stat_smooth(method = 'lm', size=1, se=TRUE, color = "black", alpha=0.4) +
+  #ylim(0.3,0.9) +
+  xlab("Pollinator richness") +      
+  ylab("Fruit weight (g)") + theme_bw()  + #theme (legend.position= "none") +
+  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
+
 ```
@@
 
-confint(m1.seedw.net)
+#confint(m1.seedw.net)
 
 #save table with results for paper
-tableS8<-round(summary(m1.seedw.net)$coef[,1:3], digits=2)#ch
-rownames(tableS8) <-c("(Intercept)", "Pollinator species diversity", "Total number of visits")#end of paper
+tableS8A<-round(summary(m1.seedw.net)$coef[,1:3], digits=2)#ch
+rownames(tableS8A) <-c("(Intercept)", "Pollinator species diversity", "Total number of visits")#end of paper
 
@@
 
+#Repeat analyses but removing one site that has a particularly large pollinator richness value to test whether this point might be driving the relationship by itself.
+
+m1.seedw.net2<-glm(mean.seedweight ~  species.poll.sc + tot.visits.sc, family="gaussian", data=s.comm2)
+
+summary(m1.seedw.net2)
+
+vif(m1.seedw.net2)
+
+m2.seedw.net2<-glm(mean.seedweight ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="gaussian", data=s.comm2)
+
+summary(m2.seedw.net2)
+
+vif(m2.seedw.net2)
+
+#select best model based on AIC
+
+AICtab(m1.seedw.net2, m2.seedw.net2) #m1 is better
+
+#save table with results for paper
+tableS8B<-round(summary(m1.seedw.net2)$coef[,1:3], digits=2)#ch
+rownames(tableS8B) <-c("(Intercept)", "Pollinator species diversity", "Total number of visits")#end of paper
+
+predtest2b<-summary(m1.seedw.net2)$coefficients[1]+ (summary(m1.seedw.net2)$coefficients[2] * s.comm2$species.poll.sc) + (summary(m1.seedw.net2)$coefficients[3] * mean(s.comm2$tot.visits.sc))
+
+restest2b<-predtest2b-s.comm2$mean.seedweight
+
+pltest2.sub <- ggplot(s.comm2,  aes(x=species.poll.sc, y= restest2b)) +    
+  geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
+  stat_smooth(method = 'glm', size=1, se=TRUE, color = "black", alpha=0.4) +
+  #ylim(0.3,0.9) +
+  xlab("Pollinator richness") +      
+  ylab("Seed weight (g)") + theme_bw()  + #theme (legend.position= "none") +
+  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))
+
+FigureS3<-plot_grid(pltestb, pltest2.sub, labels = c("A", "B"), nrow=1)
+
 ```
@@
   Contrastingly, in the case of weight variables (fruit and seed weight), in both cases we find that the best model is model 1, i.e., that only including simple visitation metrics (R^2 = `r round(r2.fruitw1[2], 2)` in the case of fruit weight and `r round(r2.seedw1[2], 2)` in the case of seed weight).
-Here, we find a consistent positive effect of site-level pollinator richness for both weight descriptors (Tables S7-S8, Fig.
+Here, we find a consistent positive effect of site-level pollinator richness for both weight descriptors (Tables S7A-S8A, Fig.
 4).
+This effect is maintained even after removing a site that has a particularly large pollinator richness value (Tables S7B-S8B, Fig.
+S3).
 
@@
 
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=6, fig.width=9}
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=9, fig.width=9}
 
@@
 
-#######FIG S1 SAMPLING COMPLETENESS 
+#######FIG S2 SAMPLING COMPLETENESS 
 #FigureS2<-plot_grid( poll, plant, link, ncol = 1)
-#FigureS2
+FigureS2
 
@@
 Solid lines and points indicate observed richness while dashed lines show expected richness at increasing sample size, (i.e., extrapolated).
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=3, fig.width=10}
+
+FigureS3
+
+```
+
+**Figure S3.** Figure S3.
+Partial residual plots showing the effect of pollinator richness on site-level average A) fruit and B) seed weight.
+Here, a site with a particularly large pollinator richness value is removed to test whether it might be driving the significant relationship.
+Dots represent values for each site (N=15 sites).
 
@@
 
-tableS7<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)
+tableS7A<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)
 rownames(tableS7)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
 
-kable(tableS7, caption="Table S7. Results of GLM showing effect of simple visitation metrics on site-level average fruit weight based on best model selected.")
+kable(tableS7A, caption="Table S7.
+Results of GLM showing effect of simple visitation metrics on A) site-level average fruit weight based on best model selected and B) the same analysis removing one site that has a particularly large pollinator richness value to test whether this point might be driving the relationship.")
+```
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+
+tableS7B<-round(summary(m1.fruitw.net2)$coef[,1:3], digits=2)
+rownames(tableS7B)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
+
+kable(tableS7B, caption="Table S7.
+Results of GLM showing effect of simple visitation metrics on A) site-level average fruit weight based on best model selected and B) the same analysis removing one site that has a particularly large pollinator richness value to test whether this point might be driving the relationship.")
 ```
@@
 #save table with results for paper
-tableS8<-round(summary(m1.seedw.net)$coef[,1:3], digits=2)
-rownames(tableS8) <-c("(Intercept)", "Pollinator richness", "Total number of visits")
-
-kable(tableS8, caption="Table S8. Results of GLM showing effect of simple visitation metrics on site-level average seed weight based on best model selected.")
+tableS8A<-round(summary(m1.seedw.net)$coef[,1:3], digits=2)
+rownames(tableS8A) <-c("(Intercept)", "Pollinator richness", "Total number of visits")
+
+kable(tableS8A, caption="Results of GLM showing effect of simple visitation metrics on A) site-level average seed weight based on best model selected and B) the same analysis removing one site that has a particularly large pollinator richness value to test whether this point might be driving the relationship.")
+```
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
+#save table with results for paper
+tableS8B<-round(summary(m1.seedw.net2)$coef[,1:3], digits=2)
+rownames(tableS8B) <-c("(Intercept)", "Pollinator richness", "Total number of visits")
+
+kable(tableS8B, caption="Results of GLM showing effect of simple visitation metrics on A) site-level average seed weight based on best model selected and B) the same analysis removing one site that has a particularly large pollinator richness value to test whether this point might be driving the relationship.")
 ```

### 2019-11-20 scripts/network analysis.R

@@ -9,6 +9,7 @@ source('toolbox.R') #load the toolbox from Song et al paper
 #devtools::install_github("CHoeppke/maxnodf")
 library(maxnodf)#load improved algorithm from Simmons et al
 library(plyr)
+library(nnet)
 
 d<-all_interactions
 

### 2019-11-21 Network_structure_and_function.Rmd
small changes following second review in PCI Ecology

@@
 Here, we present one of the first efforts linking pollinator visitation to plant reproduction from a community-wide perspective using a well-replicated dataset encompassing 16 well-resolved plant-pollinator networks and data on reproductive success for 19 plant species from Mediterranean shrub ecosystems.
-We find that models including simple visitation metrics are good in explaining the variability in reproductive success observed.
+We find that models including simple visitation metrics are sufficient to explain the variability in reproductive success observed.
 However, insights into the mechanisms through which differences in pollinator diversity translate into changes in reproductive success require additional information on network structure.
@@
 To calculate max(NODF) we used a recently corrected version of the algorithm [@Simmons2019a] in all but three sites, where the condition that the number of links>number of species was not met and thus precluded us from using this new version.
+Results did not change qualitatively when using the uncorrected version of the algorithm for all sites.
 
@@
 coefs.m2 <- data.frame(coef(summary(m2)))
-coefs.m2
+#coefs.m2
 Table1A<-round(coefs.m2[,1:3],digits=2)
@@
 coefs.m2.seed <- data.frame(coef(summary(m2.seed)))
-coefs.m2.seed
+#coefs.m2.seed
 Table1B<-round(coefs.m2.seed,digits=2)
@@
 
-m1.seed.w<-glmmTMB(mean.seedw ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3)
+m1.seed.w<-glmer(mean.seedw ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3)
 
@@
 
-m2.seed.w<-glmmTMB(mean.seedw ~  pollspsperplant.sc + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3)
+m2.seed.w<-glmer(mean.seedw ~  pollspsperplant.sc + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3)
 
@@
 # extract estimates and st error for m1 and present them in paper
-tableS5<-round(summary(m1.seed.w)$coefficients$cond[,1:3], digits=2) #ch
+coefs.m1.seed.w <- data.frame(coef(summary(m1.seed.w)))
+tableS5<-round(coefs.m1.seed.w,digits=2)
 rownames(tableS5)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
@@
 
-m1.fruit.w<-glmmTMB(mean.fruitweight ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3)
+m1.fruit.w<-glmer(mean.fruitweight ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3)
 
@@
 
-m2.fruit.w<-glmmTMB(mean.fruitweight ~  pollspsperplant.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3)
+m2.fruit.w<-glmer(mean.fruitweight ~  pollspsperplant.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3)
 
@@
 # extract estimates and st error for m2 and present them in paper
-tableS6<-round(summary(m1.fruit.w)$coefficients$cond[,1:3], digits=2)#ch
+coefs.m1.fruit.w <- data.frame(coef(summary(m1.fruit.w)))
+tableS6<-round(coefs.m1.fruit.w,digits=2)
 rownames(tableS6)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
+
+FigureS3<-plot_summs(m2, m2.seed, m1.fruit.w, m1.seed.w, level=0.95, scale = TRUE, model.names = c("Fruit set", "Number of seeds", "Fruit weight", "Seed weight"), legend.title = "Response variables", cex.axis=2)
 
@@
 
+FigureS4A<-plot_model(m2.fruit.net, title="Fruit set")
 ```
@@
 Figure3<-plot_grid(pl3, pl2, pl6, labels = c("A", "B", "C"), nrow=1)
+
+FigureS4B<-plot_model(m2.seed.net, title="Number of seeds")
 ```
@@
 
-FigureS3<-plot_grid(pltestb, pltest2.sub, labels = c("A", "B"), nrow=1)
-
+FigureS5<-plot_grid(pltestb, pltest2.sub, labels = c("A", "B"), nrow=1)
+
+FigureS4C<-plot_summs(m1.fruitw.net, m1.seedw.net, level=0.95, scale = TRUE, model.names = c("Fruit weight", "Seed weight"), legend.title = "Response variables")
+
+#FigureS4<-plot_grid(FigureS4A, FigureS4B, FigureS4C, labels = c("A", "B", "C"), nrow=3)  
 ```
@@
 This effect is maintained even after removing a site that has a particularly large pollinator richness value (Tables S7B-S8B, Fig.
-S3).
+S5).
 
@@
 
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=8}
+
+FigureS3
+
+```
+**Figure S3.** Forest plots showing confidence intervals for all coefficients included in species-level models.
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=15, fig.width=8}
+
+FigureS4A
+FigureS4B
+FigureS4C
+
+```
+**Figure S4.** Forest plots showing confidence intervals for all coefficients included in site-level models, A) fruit set, B) number of seeds per fruit and C) fruit and seed weight.
+
 ```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=3, fig.width=10}
 
-FigureS3
-
-```
-
-**Figure S3.** Figure S3.
+FigureS5
+
+```
+
+**Figure S5.** Figure S5.
 Partial residual plots showing the effect of pollinator richness on site-level average A) fruit and B) seed weight.

### 2019-11-25 Network_structure_and_function.Rmd
Small changes to figure legends

@@
 ---
-title: Niche complementarity between pollinators increases community-level plant reproductive success 
+title: Niche complementarity among pollinators increases community-level plant reproductive success 
 author: "Magrach, A, Molina, FP, Bartomeus, I"
@@
 
-**Niche complementarity between pollinators increases community-level plant reproductive success**
+**Niche complementarity among pollinators increases community-level plant reproductive success**
 
@@
 We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect interactions between species within one guild (e.g., plants) through their shared resources [@Carvalheiro2014; @Lazaro2014; @Mayfield2017; @Pauw2013; @Johnson2019].
-Understanding how changes in pollinator diversity and interaction structure affect whole community assemblages is thus a major challenge that requires attention.
+Understanding how changes in pollinator diversity and interaction structure affect whole community functioning is thus a major challenge that requires attention.
 
@@
 library(MuMIn)
+library(jtools)
 
@@
 The authors would like to thank Oscar Aguado for identifying pollinator species.
-We would also like to acknowledge the efforts of the editor Cédric Gaucherel, as well as those of Michael Lattorff, Nicolas Deguines, and three anonymous reviewers who provided very helpful comments and suggestions in a previous version of this manuscript.
+We would also like to acknowledge the efforts of the editor Cédric Gaucherel, as well as those of Michael Lattorff, Nicolas Deguines, Alberto Pascual, and three anonymous reviewers who provided very helpful comments and suggestions in a previous version of this manuscript.
 AM received funding from a Juan de la Cierva (IJCI-2014-22558) and Ikerbasque fellowships.
@@
 
-**Figure 1.** Map showing location of 16 study sites. Inset shows location of study area within SW Spain.
+**Figure 1.** Map showing location of 16 Mediterranean woodland patches where plant-pollinator interactions were surveyed from February to May 2015. Inset shows location of study area within SW Spain.
 
 **Figure 2**.
-Partial residual plot showing the effect of a single predictor for the relationship between A) plant species centrality and fruit set for each of the plant species considered and B) plant niche overlap and average number of seeds per fruit.
+Partial residual plots showing the effect of the single predictor which best explains the variability in species-level reproductive success.
+A) Shows the effect of plant species centrality on the fruit set of each of the plant species considered and B) shows the effect of plant niche overlap on the average number of seeds per fruit.
 Dots represent each of the individuals sampled for each species within each site.
 
-**Figure 3.** Partial residual plots showing the effect of A) pollinator richness, and B) niche complementarity between pollinator species on site-level average fruitset and C) niche complementarity between pollinator species on the average number of seeds per fruit at the site level.
+**Figure 3.** Partial residual plots showing the effect of the single predictor which best explains the variability in site-level reproductive success.
+A) Shows the effect of pollinator richness, and B) of niche complementarity among pollinator species on site-level average fruit set.
+C) Shows the effect of niche complementarity among pollinator species on the average number of seeds per fruit at the site level.
 Dots represent average values of fruit set at the level of the community for all plant species considered (N=16 sites).
@@
 ```
-**Figure S3.** Forest plots showing confidence intervals for all coefficients included in species-level models.
+**Figure S3.** Forest plots showing 95% confidence intervals for all coefficients included in species-level models.
 
@@
 ```
-**Figure S4.** Forest plots showing confidence intervals for all coefficients included in site-level models, A) fruit set, B) number of seeds per fruit and C) fruit and seed weight.
+**Figure S4.** Forest plots showing 95% confidence intervals for all coefficients included in site-level models, A) fruit set, B) number of seeds per fruit and C) fruit and seed weight.
 

### 2020-02-27 Network_structure_and_function.Rmd
changes for ecol lett

@@
 
-Declines in pollinator diversity and abundance have been reported across different regions, with implications for the reproductive success of plant species.
-However, research has focused primarily on pairwise plant-pollinator interactions, largely overlooking community-level dynamics.
-Here, we present one of the first efforts linking pollinator visitation to plant reproduction from a community-wide perspective using a well-replicated dataset encompassing 16 well-resolved plant-pollinator networks and data on reproductive success for 19 plant species from Mediterranean shrub ecosystems.
-We find that models including simple visitation metrics are sufficient to explain the variability in reproductive success observed.
-However, insights into the mechanisms through which differences in pollinator diversity translate into changes in reproductive success require additional information on network structure.
-Specifically, we find a positive effect of increasing niche complementarity between pollinators on plant reproductive success.
-This shows that maintaining communities with a diversity of species but also of functions is paramount to preserving natural ecosystems.
+The number of studies analyzing the structure of interactions shaping natural communities has increased, particularly regarding pollination.
+However, research linking pollinator diversity to reproductive success has focused on pairwise plant-pollinator interactions, largely overlooking community-level dynamics.
+Here, we present one of the first single studies linking pollinator visitation to plant reproduction from a community-wide perspective using a well-replicated dataset encompassing 16 plant-pollinator networks and data on reproductive success for 19 plant species from Mediterranean shrub ecosystems.
+We find that statistical models including simple visitation metrics are sufficient to explain the variability observed.
+However, a mechanistic understanding of how pollinator diversity affects reproductive success require additional information on network structure.
+Specifically, we find positive effects of increasing complementarity in the plant species visited by different pollinators on plant reproductive success.
+This shows that maintaining communities with a diversity of species but also of functions is paramount to preserving plant diversity.
 
@@
 Pollinators provide key services to plants by facilitating pollen flow between individuals.
-The recent declining trends found for some pollinator species in some regions of the planet ([@Potts2010; @I.2019]) have led many researchers to focus on the functional impacts of these changes in pollinator diversity, with a major focus being placed on the consequences for plant reproductive success [@Biesmeijer2006].
-
-  Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain the differences observed across different plant individuals.
+Records of declining trends for some pollinator species in some regions ([@Potts2010; @I.2019]) have led researchers to focus on the functional impacts of these changes in pollinator diversity, especially on the consequences for plant reproductive success [@Biesmeijer2006].
+
+  Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain the differences observed.
 Contrastingly, community-level analyses remain scarce [@Bennett2018].
@@
 We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect interactions between species within one guild (e.g., plants) through their shared resources [@Carvalheiro2014; @Lazaro2014; @Mayfield2017; @Pauw2013; @Johnson2019].
-Understanding how changes in pollinator diversity and interaction structure affect whole community functioning is thus a major challenge that requires attention.
+Understanding how changes in pollinator diversity and interaction structure affect whole ecosystem functioning is thus a major challenge that requires attention.
 
   The few pollination studies that have analysed the effects of changing pollinator diversity for reproductive success at the community level have done so using mainly experimental setups.
-As an example, a study that experimentally recreated a plant community with 9 plant species and differing levels of pollinator diversity across different enclosures, found that not only pollinator species diversity had an effect for average reproductive success, but that plant-pollinator interaction structure also had an important effect [@Frund2013].
-In particular, these authors found that niche complementarity between pollinators, in terms of plant species and temperature coverage (a measure of the overlap in the use of plant resources and optimum temperature activity) had a positive effect for average seed set at the community level [@Frund2013].
+As an example, a study that experimentally recreated a plant community with 9 plant species and differing levels of pollinator diversity across different enclosures, found a positive effect of pollinator species diversity on seed set, but also an important effect of niche complementarity between pollinators, a measure of community structure [@Frund2013].
 This provides added information on the effects of biodiversity for ecosystem functioning, suggesting that not only the diversity of species present, but also the diversity of roles and ways in which a community is structured, are determinant factors.
@@
   Indeed, theoretical research has long suggested that the structure of multitrophic communities has an effect for ecosystem functioning (reviewed in [@Thompson2012]).
-This line of research, rooted in niche theory and revamped by food-web studies [@Godoy2018; @Macarthur1967; @May1972a; @Tilman1982], has greatly advanced theory, but these ideas have not yet been tested using empirical data (but see [@Poisot2013]).
-Specifically, a major knowledge gap resides in understanding which aspects of structure determine which aspects of function [@Thompson2012].
+This line of research, rooted in niche theory and revamped by food-web studies [@Godoy2018; @Macarthur1967; @May1972a; @Tilman1982], has greatly advanced theory, but the relationship between structure and function has seldom been tested using empirical data (but see [@Kaiser-Bunbury2017; @Poisot2013; @Saunders2019]).
+This line of research, rooted in niche theory and revamped by food-web studies  has greatly advanced theory, but these ideas have not yet been tested using empirical data  Specifically, a major knowledge gap resides in understanding which aspects of structure determine which aspects of function [@Thompson2012].
 This is because although a network perspective has promised to encapsulate complex ecological mechanisms occurring at the community level – such as indirect interactions [@Abrams1998; @Holt1977] or niche overlap [@Woodward2002]- less attention has been given to the ways in which these mechanisms relate to observed ecosystem processes [@Bluthgen2010a].
@@
 Especially, in the case of pollination, we have ample knowledge on the attributes that shape these mutualistic interactions at the community level.
-Amongst them is the prevalence of nested structures, i.e., arrangements where specialist species interact with a subset of the species that generalists interact with [@Bascompte2003] and which is thought to promote species diversity [@Bastolla2009]; or the relatively high extent of complementary specialization at the community scale, which may be directly related to key ecosystem functions [@Bluthgen2011].
+Amongst them is the prevalence of nested structures, i.e., arrangements where specialist species interact with a subset of the species that generalists interact with [@Bascompte2003] and which is thought to promote species diversity [@Bastolla2009].
+Further, plant-pollinator interaction networks seem to exhibit a relatively high extent of complementary specialization at the community scale, which may be directly related to key ecosystem functions [@Bluthgen2011].
 However, the mechanisms by which these attributes affect plant reproduction remain to be understood [@Winfree2013].
-The time is thus ripe to use the existing knowledge around plant-pollinator network structures to explore the relationship between network structure and ecosystem functioning empirically, with special emphasis being placed on the underlying ecological mechanisms that drive these relationships.
+The time is thus ripe to use the existing knowledge around plant-pollinator network structures to explore the relationship between network structure and ecosystem functioning empirically, with special emphasis on the underlying ecological mechanisms that drive these relationships.
 
   Here, we present one of the first efforts linking pollinator visitation and plant reproductive success at the community level using empirical data on plant-pollinator interaction networks and plant reproductive success.
-To this end, we use a well-replicated dataset encompassing 16 well-resolved plant-pollinator interaction networks coupled with data on the reproductive success of 19 plant species recorded in Mediterranean shrub ecosystems.
+To this end, we use a well-replicated dataset encompassing plant-pollinator interaction networks collected at 16 sites coupled with data on the reproductive success of 19 plant species recorded in Mediterranean shrub ecosystems.
 Our study focuses on understanding whether adding information on selected interaction network structure indices to previously used simple visitation metrics (e.g., the number and diversity of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success.
-In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success, and (ii) at the site level, by evaluating how attributes that describe the whole site might affect average values of reproductive success.
-Specifically, our study focuses on how the interplay between niche complementarity and redundancy determines reproductive success.
+In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the association between the position of a focal species within the larger network and its link to individual reproductive success, and (ii) at the site level, by evaluating how attributes that describe the whole site might affect average values of reproductive success for all species measured within one particular site.
+Specifically, our study focuses on how the interplay between the complementarity in plant species visited by different pollinators (i.e., the complementarity in the functions they perform) and the redundancy in this function relates to reproductive success.
 Plant reproductive success requires of the delivery of conspecific pollen and thus of a certain degree of niche complementarity [@Bluthgen2011].
-Yet, greater values of nestedness, which imply redundancy in species functions, are thought to promote species diversity [@Bastolla2009] and stability [@Thebault2010a] within plant-pollinator networks.
+Yet, greater values of redundancy in species functions (e.g., that provided by nested structures), are thought to promote species diversity [@Bastolla2009] and stability [@Thebault2010a] within plant-pollinator networks.
 At present, we do not know how either of these network characteristics affects the functions performed by pollinators.
-Finally, in addition to average values, we also evaluate whether network structure helps explain differences in equity in reproductive success across species within a community, as a measure of evenness in the pollination service delivered.
 
@@
 library(jtools)
+library(sjPlot)
 
@@
 d<-all_interactions
+dtrans<-subset(d, d$Out=="transect")  #keep only records within transects, eliminate focal and other records outside transects
 f<-fruitset
@@
 library(betapart)
-d.sub<-subset(d, d$Out=="transect") #keep only plants surveyed in transects, remove focals
-d.beta<-table(d.sub$Site_ID, d.sub$Plant_gen_sp)
+dtrans<-subset(d, d$Out=="transect") #keep only plants surveyed in transects, remove focals
+d.beta<-table(dtrans$Site_ID, dtrans$Plant_gen_sp)
 d.beta[d.beta>1]<-1 
@@
 1).
-All sites were located within similar elevations (ranging from 50 to 150 m a.s.l.), similar habitat and soil types, and presented similar plant composition (plant mean Sørensen beta-diversity among sites = `r round(d.betadiv, 2)`), reducing potential confounding factors.
+All 16 sites were located within similar elevations (ranging from 50 to 150 m a.s.l.), similar habitat and soil types, and presented similar plant composition (plant mean Sørensen beta-diversity among sites = `r round(d.betadiv, 2)`), reducing potential confounding factors.
 Here, we surveyed 16 Mediterranean woodland patches with an average distance of 7 km between them (min= 3 km, max= 46.5 km).
-Each site was surveyed 7 times during the flowering season of 2015 (from February to May) following a 100-m x 2 m transect for 30 mins.
+Each site was surveyed every two weeks for a total of 7 times during the flowering season of 2015 (from February to May) following a 100-m x 2 m transect for 30 mins.
 Along each transect, we identified all plant species and recorded all the floral visitors that landed on their flowers during each 30-min period.
-Only floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FPM and experts in the different taxonomic groups (see acknowledgements).
-In addition, at each round we conducted 3 minutes of focal observations recording all floral visitors observed on 3 plant individuals per species belonging to the 19 most common (based on previous surveys) plant species across the study area (mean $\pm$ SD: `r round(mean(foc3$tot.species), digits=2)` $\pm$ `r round(sd(foc3$tot.species), digits=2)` species per site).
-Furthermore, we included some interactions between plant and pollinator individuals that were not observed during the sampling but that were opportunistically recorded immediately before or after the sampling periods, as some of these interactions are difficult to document and might be important to define network structure [@Jordano2016].
-These opportunistic interactions represented `r round(table(d$Out)[2]/(table(d$Out)[1]+table(d$Out)[2]+table(d$Out)[3])*100, digits=2)` of all interactions recorded.
-All surveys were done under similar weather conditions, avoiding windy or rainy days.
-Surveys were done during mornings and afternoons with the sampling order being established randomly.
+Only floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FPM and another expert entomologist (see acknowledgements).
+All surveys were done under similar weather conditions, avoiding windy or rainy days, during mornings and afternoons with the sampling order being established randomly.
 
@@
                    tot.fruits = length(Plant.ID)) #number of fruits per individual
+
 ```
@@
 
-Within each site, we marked between 3 and `r max(f.inds$tot.inds)` individuals (mean $\pm$ SD: `r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`, Table S2) belonging to `r min(tableS1$tot.sps)` to `r max(tableS1$tot.sps)` plant species (mean $\pm$ SD:`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`, Table S1), depending on the availability and presence of flowers during the sampling events.
-For each individual, at the end of the season, we
-recorded fruit set (i.e.
+Within each site, we marked between 3 and `r max(f.inds$tot.inds)` individuals (mean $\pm$ SD: `r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`, Table S2) belonging to `r min(tableS1$tot.sps)` to `r max(tableS1$tot.sps)` plant species (mean $\pm$ SD:`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`, Table S2).
+For each individual, at the end of the season, we recorded fruit set (i.e.
 the proportion of flowers that set fruit), the average number of seeds per fruit and the average fruit and seed weight per fruit (`r min(s.fruitnum$tot.fruits)`-`r max(s.fruitnum$tot.fruits)` fruits subsampled, mean $\pm$ SD: `r round(mean(s.fruitnum$tot.fruits), digits=2)` $\pm$ `r round(sd(s.fruitnum$tot.fruits), digits=2)`, Table S3).
-Our survey included a total of `r nlevels(f2$Plant.sp)` different plant species across our `r nlevels(f2$Site_ID)` sites.
-Plants species were selected based on their availability, with sampling being focused on the most abundant plant species.
-The values at the species level were then averaged per site to calculate unique reproductive success measures at the site level.
-All plant species depend on pollinators to maximize their reproduction (Table S4).
+These variables show strong correlations (Pearson correlation= 0.89), we believe they provide complementary information.
+Our survey included a total of `r nlevels(f2$Plant.sp)` different totally or partially self-incompatible plant species that depend on pollinators to maximize their reproduction (Table S4) across our `r nlevels(f2$Site_ID)` sites.
+All plant species were shrubs selected to be common and widespread species, and individuals were selected depending on the presence of flowers during the sampling events.
+The values of reproductive success obtained at the species level were also averaged per site to calculate unique reproductive success measures at the site level in addition to species-level values..
 
@@
 
-In order to evaluate the completeness of our sampling of the pollinator and plant community as well as that of their interactions, we estimated the asymptotic number of species present [@Chao2009], a non-parametric estimator of species richness for abundance data.
+In order to evaluate the completeness of our sampling, we estimated the asymptotic number of species of plants, pollinators and interactions present [@Chao2009], a non-parametric estimator of species richness for abundance data.
 This estimator includes non-detected species and allowed us to calculate the proportion detected with our original sampling data.
@@
 
-  In order to analyse how differences in network structure might affect plant reproductive success, we constructed plant-pollinator interaction networks by pooling the data for the 7 rounds of sampling.
+  In order to analyse how differences in network structure between communities might affect plant reproductive success, we constructed quantitative plant-pollinator interaction networks by pooling the data for the 7 rounds of sampling.
 We thus obtained one interaction network per site, representing the number of individuals of different pollinator species recorded visiting each different plant species.
-For each network, we then proceeded to extract a series of relevant network metrics at the species and site levels.
+For each network, we then extracted a series of relevant network metrics at the species and site levels.
 
   In addition, we checked for potential spatial autocorrelation in our data by means of Mantel correlograms.
-Autocorrelation values were low for all variables included in our analyses (Figure S1) and hence we treat each site as independent in our analysis.
+Autocorrelation values were non-significant for all variables included in our analyses, except in the case of pollinator richness where we have a significant effect at small spatial scales (Fig.
+S1), and hence we treat each site as independent in our analysis.
 
@@
 At the species level, we focused on attributes defining the position of a focal plant species within the larger community.
-As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap in terms of pollinators between a focal plant species and each of the other plant species in the community, which estimates the potential indirect interactions between different plant species through shared resources (in this case pollinators), and (ii) centrality, which depicts the importance of the role played by a plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness.
+As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap in terms of pollinators between a focal plant species and each of the other plant species in the community, which estimates the potential indirect interactions between different plant species through shared resources (in this case pollinators) and the potential for increased heterospecific pollen [@Arceo-Gomez2019], and (ii) centrality, which depicts the importance of the role played by a plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness.
  Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the Morisita overlap index, a measure of similarity between two sets of data [@Zhang2016].
@@
 Thus, we also calculated two network metrics providing complementary non-redundant information.
-In this case we focused on (i) nestedness and (ii) pollinator niche complementarity.
+In this case we focused on a metric that measures the redundancy in the plants visited by different pollinators, nestedness, and another one, not correlated with the previous one, measuring the complementarity in the plant species visited by the different pollinator species, pollinator niche complementarity
 
   Nestedness is the property by which specialists interact with a subset of the species that generalists interact with [@Bascompte2003].
-Although there is an ongoing debate in the literature, some studies have found that nested networks are more stable and resilient to perturbations because nestedness promotes a greater diversity by minimizing competition among species in a community [@Bastolla2009].
+Although there is an ongoing debate in the literature (e.g., [@James2012]), some studies have found that nested networks are more stable and resilient to perturbations because nestedness promotes a greater diversity by minimizing competition among species in a community [@Bastolla2009].
 However, many network attributes vary with network size and complexity [@Bluthgen2006].
@@
 An approach that is often used to correct for this, is to use null models and to compare null-model corrected nestedness values across different networks.
-However, this approach has been recently shown to present the same issues, as z-scores also change with network size and connectance [@Song2017a].
+However, this approach has been shown to present the same issues, as z-scores also change with network size and connectance [@Song2017a].
 We thus followed the advice provided by Song et al.
 (2017) by using a normalized value of the widely-used nestedness metric NODF [@Almeida-Neto2011], $NODF_c$.
-This normalized value is calculated as $NODF_c = NODF_n/(C * log(S))$, where C is connectance and S is network size.
+This normalized value is calculated as $NODF_c = NODF_n/(C * log(S))$, where C is connectance and S is network size, calculated as $S = \sqrt(ncol(web)*nrow(web))$.
 $NODF_n$ is calculated as $NODF/max(NODF)$, which is independent of network size and thus comparable across different networks [@Song2017a].
-To calculate max(NODF) we used a recently corrected version of the algorithm [@Simmons2019a] in all but three sites, where the condition that the number of links>number of species was not met and thus precluded us from using this new version.
+To calculate max(NODF) we used a corrected version of the algorithm [@Simmons2019a] whenever possible.
 Results did not change qualitatively when using the uncorrected version of the algorithm for all sites.
 
-  Niche complementarity metrics are important because plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence (reviewed in [@Brosi2016]).
-To calculate niche complementarity, we used a community-level measure defined as the total branch length of a functional dendrogram based on qualitative differences measured using a Euclidean distance in visitor assemblages between plants [@Devoto2012; @Petchey2007a].
+ To calculate niche complementarity, we used a community-level measure defined as the total branch length of a dendrogram based on qualitative differences in visitor assemblages between plants [@Devoto2012; @Petchey2007a].
 All network metrics were calculated using package bipartite [@Dormann2009].
 
-  All of these metrics were calculated using all the data as well as for the subset of the data excluding interactions observed outside of sampling periods.
-Differences between results are minimal for both and thus we will only present results for the analysis using the full dataset (see Table S12A-H for results removing observations out of transect).
-
 _Statistical analyses_
 
-In order to evaluate whether adding information on network structure improves our ability to explain differences in reproductive success - both at the species and the site level - we used generalized linear (GLMs) and generalized linear mixed models (GLMMs) respectively.
-In both cases (species and site-level models) we fit two types of models: (i) model 1, that only included simple visitation metrics and (ii) model 2 that additionally included information on network structure.
+To evaluate whether adding information on network structure improves our ability to explain differences in reproductive success - both at the species and the site level - we used generalized linear (GLMs) and generalized linear mixed models (GLMMs) respectively.
+In both cases (species and site-level models) we fit three types of models: (i) model 0, a null model with no explanatory variables,(ii) model 1, that only included simple visitation metrics and (iii) model 2 that additionally included information on network structure.
 These models are meant to be additive, so that the network metrics included are intended to complement rather than substitute the simple metrics traditionally used.
 
-  At the species level, response variables included the fruit set for different individuals of each species analyzed using a binomial distribution and the average number of seeds per fruit, the average fruit and seed weight fitted using normal distributions.
+At the species level, response variables included fruit set analyzed using a binomial distribution and the average number of seeds per fruit, the average fruit and seed weight fitted using normal distributions.
 The number of seeds per fruit was centered and scaled (i.e., we subtracted column means and divided by standard deviation) to allow meaningful comparisons across species with contrasting life histories.
-As explanatory variables, model 1 included pollinator richness, and the total number of visits received by each plant species; while model 2 added the two network attributes calculated at the species level: average plant niche overlap and centrality.
-For both models, we included plant species nested within site and site as random effects to account for the non-independence of several individuals measured per species and site.
-
-	At the site level, we upscaled our species-level analyses.
-As response variables we had the average reproductive success per site (i.e., average fruit set analyzed using a binomial distribution, average number of seeds per fruit and average fruit and seed weight using a normal distribution).
+As explanatory variables, model 1 included pollinator richness, and the relative number of visits received by each plant species, which is calculated as the total number of visits received by a plant species divided by the average number of flowers present in that species.
+In turn, model 2 added the two network attributes calculated at the species level: average plant niche overlap and centrality.
+For both models, we included plant species identity nested within site and site as random effects to account for the fact that several individuals of the same plant species were measured at each site.
+
+	At the site level, response variables were the average reproductive success of all plants surveyed within a site (i.e., average fruit set analyzed using a binomial distribution, average number of seeds per fruit and average fruit and seed weight using a normal distribution).
 We thus had a single value per site and no random effects are needed.
@@
 number of visits received by all plants within the community) as explanatory variables.
-Model 2, in turn, added information on network structure by including nestedness and pollinator niche complementarity as explanatory variables.
+Model 2, in turn, added information on network structure by including nestedness and pollinator niche complementarity.
 
@@
 Yet, what will determine the persistence of a diverse plant community, is the presence of some sort of “equity” or evenness in reproductive success across the whole community.
-We therefore calculated a measure of equity in reproductive success at the site level as the proportion of species with normalized (between 0 and 1) average fruit set values that were above the 50^th percentile.
+We therefore calculated the proportion of species with normalized (between 0 and 1) average fruit set values that were above the 50^th percentile as a measure of equity.
 As any selected threshold is arbitrary, we repeated this using the 25^th and 75^th percentile thresholds [@Byrnes2014].
-We then used the same framework as that used for species and site-level analyses and fit the same models 1 and 2 GLMs but using equity in reproductive success as the response variable and fitting a binomial distribution.
+We then used the same framework as that used for species and site-level analyses and fit the same models 0, 1 and 2 GLMs using equity in reproductive success as response variable and fitting a binomial distribution.
 
   In all cases, we used variance inflation factors to check for collinearity between explanatory variables.
-Additionally, we ran residual diagnostics to check if model assumptions were met.
-Then, we used the Akaike Information Criterion (AIC) to compare model performance and complexity.
-Whenever the difference between the AIC of both models was < 2 ($\Delta AIC<2$), we considered that both models were equally good [@Burnham2011].
+Additionally, we ran residual diagnostics to check if model assumptions were met and used the Akaike Information Criterion (AIC) to compare model performance and complexity.
+Whenever the difference between the AIC of the models was < 2 ($\Delta AIC<2$), we considered that all models were equally good [@Burnham2011].
+In the case of mixed models, for comparison, models were fitted by maximum likelihood and then the best model was refitted using restricted maximum likelihood.
 All predictor variables were standardized prior to analysis.
-For every model we also calculate the R2 value using the approximation suggested for generalized mixed models when necessary [@Shinichi2017].
-
-  Finally, we tested whether the importance of network structure in explaining differences in equity in reproductive success within communities increases with the number of plant species being considered.
-We expect that when only one plant species is considered, then the importance of network structure will be negligible, while we expect this importance to increase as more plant species are considered (up to a maximum number of 6 species which is the maximum we have measured in our study at a particular site).
+For every model we also calculate the R2 value using the approximation suggested for GLMMs when necessary [@Shinichi2017].
+
+  Finally, we tested whether the importance of network structure in explaining differences in equity in reproductive success increases with the number of plant species being considered.
+We expect that when only one plant species is considered the importance of network structure will be negligible, while we expect it to increase as more plant species are considered (up to a maximum number of 6 species which is the maximum we have measured in our study at a particular site).
 
@@
 for n = 3 plant selected out of 6 there is only 20 possible combinations).
-Then, we tested if the relationship between equity in reproductive success and functional complementarity (given its importance in determining differences in reproductive success, see Results section) changes as a function of the number of plants considered within our simulated communities.
+Then, we tested if the relationship between equity in reproductive success and niche complementarity (given its importance in determining differences in reproductive success, see Results section) changes as a function of the number of plants considered within our simulated communities.
 To this end, for each level of species number considered, we randomly selected one of the generated equity values across each of the 16 communities and regressed these 16 values against our network level predictor and extracted the model slope estimates.
@@
 # 
- d$order<-tr$order[match(d$Pollinator_gen_sp, tr$Pollinator_gen_sp)]
- d.order<- aggregate(Frequency ~ order, d, FUN= "sum")
+ dtrans$order<-tr$order[match(dtrans$Pollinator_gen_sp, tr$Pollinator_gen_sp)]
+ d.order<- aggregate(Frequency ~ order, dtrans, FUN= "sum")
  d.order$prop<-d.order$Frequency/sum(d.order$Frequency)
@@
 
-Within our sampling we recorded `r nrow(d)` plant-pollinator interactions involving `r nlevels(unique(d$Pollinator_gen_sp))` pollinator species and `r nlevels(unique(d$Plant_gen_sp))` plant species.
+Within our sampling we recorded `r nrow(dtrans)` plant-pollinator interactions involving `r nlevels(unique(dtrans$Pollinator_gen_sp))` pollinator species and `r nlevels(unique(dtrans$Plant_gen_sp))` plant species (Table S1).
 Within the pollinator community the distribution of individuals in different orders was: `r round(d.order$prop[d.order$order=="Hymenoptera"]*100, digits=2)`% Hymenoptera, `r round(d.order$prop[d.order$order=="Diptera"]*100, digits=2)`% Diptera, `r round(d.order$prop[d.order$order=="Coleoptera"]*100, digits=2)`% Coleoptera and `r round(d.order$prop[d.order$order=="Lepidoptera"]*100, digits=2)`% Lepidoptera.
@@
 #POLLINATORS
-d2<-table(d$Site_ID, d$Pollinator_gen_sp)
+d2<-table(dtrans$Site_ID, dtrans$Pollinator_gen_sp)
 d3<-as.data.frame.array(d2)
@@
 #per site sampling completeness for pollinators
-#Aznalcazar 64/103 = 0.62
-#Bonares  54.000/178.701 = 0.30
-#ConventodelaLuz  33.000/98.950 = 0.33
-#CotitodeSantaTeresa  54.000/190.442 = 0.28
-#Elpinar  29.000/158.657= 0.18
-#Elpozo  32.000/174.000= 0.18
-#Esparragal  39.000/110.859= 0.35
-#LaCunya  32.000/118.672= 0.27
-#LaRocina  74.000/147.129 = 0.50
-#Lasmulas  52.000/127.295 = 0.41
-#Niebla  57.000/124.792 = 0.46
-#PinaresdeHinojos 40.000/168.852 = 0.24
-#Pinodelcuervo  52.000/187.503 = 0.28
-#Urbanizaciones  40.000/109.136 = 0.37 
-#Villamanriqueeste  62.000/141.310 = 0.44
-#Villamanriquesur  48.000/111.326 = 0.43
-
-#(0.62 + 0.30 + 0.33 + 0.28 + 0.18 + 0.18 + 0.35 + 0.27 + 0.50 + 0.41 + 0.46 + 0.24 + 0.28 + 0.37 + 0.44 + 0.43)/16
+#Aznalcazar 37/69.649 = 0.53
+#Bonares  31.000/141.319 = 0.22
+#ConventodelaLuz  14.000/53.512 = 0.26
+#CotitodeSantaTeresa  24.000/67.798 = 0.35
+#Elpinar  12.000/22.105= 0.54
+#Elpozo  17.000/99.015= 0.17
+#Esparragal  18.000/65.185= 0.28
+#LaCunya  18.000/58.842= 0.31
+#LaRocina  35.000/106.621 = 0.33
+#Lasmulas  23.000/102.159 = 0.23
+#Niebla   40.000/91.656 = 0.44
+#PinaresdeHinojos 16.000/35.290  = 0.45
+#Pinodelcuervo  24.000/76.650  = 0.31
+#Urbanizaciones  20.000/74.730 = 0.27
+#Villamanriqueeste  29.000/68.395 = 0.42
+#Villamanriquesur  25.000/56.590 = 0.44
+
+#(0.53+0.22+0.26+0.35+0.54+0.17+0.28+0.31+0.33+0.23+0.44+0.45+0.31+0.27+0.42+0.44)/16
 #TOTAL AVERAGE sampling completeness of pollinators 0.35
@@
 #PLANTS
-d.pl<-table(d$Site_ID, d$Plant_gen_sp)
+d.pl<-table(dtrans$Site_ID, dtrans$Plant_gen_sp)
 d.pl2<-as.data.frame.array(d.pl)
@@
 #per site sampling completeness for plants
-#Aznalcazar 17.000/18.490 = 0.92
-#Bonares  13.000/13.990 = 0.93
-#ConventodelaLuz  12.000/13.978 = 0.86
-#CotitodeSantaTeresa  10.000/11.973 = 0.84
-#Elpinar  11.000/23.255 = 0.47
-#Elpozo  11.000 /13.219 = 0.83
-#Esparragal  12.000 /16.436 = 0.73
-#LaCunya  13.000/21.847 = 0.60
-#LaRocina  16.000 /21.959 = 0.73 
-#Lasmulas  12.000 /17.940 = 0.67
-#Niebla  21.000/21.743 = 0.97
-#PinaresdeHinojos 14.000/21.889 = 0.64
-#Pinodelcuervo  15.000/27.372 = 0.55
-#Urbanizaciones  10.000 /10.247 = 0.98
-#Villamanriqueeste  9.000 /10.983 = 0.82
-#Villamanriquesur  12.000 /12.989 = 0.92
-
-#(0.92 + 0.93 + 0.86 + 0.84 + 0.47 + 0.83 + 0.73 + 0.60 + 0.73 + 0.67 + 0.97 + 0.64 + 0.55 + 0.98 + 0.82 + 0.92)/16
-
-#TOTAL AVERAGE sampling completeness of plants 0.78
+#Aznalcazar 12.000/12.988 = 0.92
+#Bonares  9.000 /9.000 = 1
+#ConventodelaLuz  9.000/9.976 = 0.90
+#CotitodeSantaTeresa   7.000/7.243 = 0.97
+#Elpinar  6.000/8.842 = 0.68
+#Elpozo  5.000/5.000  = 1
+#Esparragal   8.000/8.963 = 0.89
+#LaCunya  11.000/17.042  = 0.65
+#LaRocina  11.000/25.737 =  0.43
+#Lasmulas  9.000/9.977 = 0.90
+#Niebla  19.000/21.948 = 0.87
+#PinaresdeHinojos 8.000/10.152 = 0.79
+#Pinodelcuervo  12.000/26.625 = 0.45
+#Urbanizaciones   9.000/16.784 = 0.54
+#Villamanriqueeste  6.000/6.977 = 0.86
+#Villamanriquesur  9.000/9.975 = 0.90
+
+#(0.92 + 1 + 0.90 + 0.97 + 0.68 + 1 + 0.89 + 0.65 + 0.43 + 0.90 + 0.87 + 0.79 + 0.45 + 0.54 + 0.86 + 0.90)/16
+
+#TOTAL AVERAGE sampling completeness of plants 0.80
 
@@
 
-d$link<-paste(d$Plant_gen_sp, d$Pollinator_gen_sp)
-d.l<-table(d$Site_ID, d$link)
+dtrans$link<-paste(dtrans$Plant_gen_sp, dtrans$Pollinator_gen_sp)
+d.l<-table(dtrans$Site_ID, dtrans$link)
 d.l2<-as.data.frame.array(d.l)
 
-d.l3 <- t(d.l2[,1:750])
+d.l3 <- t(d.l2[,1:384])
 #head(d.l3)
@@
 #per site sampling completeness for links
-#Aznalcazar 101.000/244.145 = 0.41
-#Bonares  72.000/389.031 = 0.19
-#ConventodelaLuz  52.000/221.285 = 0.23
-#CotitodeSantaTeresa  64.000/478.893 = 0.13
-#Elpinar  37.000/194.026 = 0.19
-#Elpozo   46.000/159.994 = 0.29
-#Esparragal   52.000/196.900 = 0.26
-#LaCunya  44.000/115.025 = 0.38
-#LaRocina  98.000/351.931 = 0.28
-#Lasmulas  69.000/306.883 = 0.22
-#Niebla  84.000/611.776 = 0.14
-#PinaresdeHinojos  56.000/186.413 = 0.30
-#Pinodelcuervo   77.000/273.425 = 0.28
-#Urbanizaciones  55.000/204.100 = 0.27
-#Villamanriqueeste  76.000/193.208 = 0.39
-#Villamanriquesur  67.000/234.221 = 0.29
-
-#(0.41 + 0.19 + 0.23 + 0.13 + 0.19 + 0.29 + 0.26 + 0.38 + 0.28 + 0.22 + 0.14 + 0.30 + 0.28 + 0.27 + 0.39 + 0.29)/16
-
-#TOTAL AVERAGE sampling completeness of links 0.27
+#Aznalcazar 58.000/239.782 = 0.24
+#Bonares  39.000/122.556 = 0.32
+#ConventodelaLuz  26.000/114.049 = =0.23
+#CotitodeSantaTeresa  30.000/206.890 = 0.15
+#Elpinar  17.000/70.289 = 0.24
+#Elpozo   23.000/93.125 = 0.25
+#Esparragal   23.000/119.296  = 0.19
+#LaCunya  27.000/119.800 = 0.23
+#LaRocina  43.000/379.246 = 0.11
+#Lasmulas  30.000/94.622 = 0.32
+#Niebla  51.000/397.586 = 0.13
+#PinaresdeHinojos  22.000/232.913 = 0.09
+#Pinodelcuervo   35.000/191.162  = 0.18
+#Urbanizaciones  28.000/168.108 = 0.17
+#Villamanriqueeste  37.000/162.023 = 0.23
+#Villamanriquesur  34.000/253.375  =  0.13
+
+#(0.24 + 0.32 + 0.23 + 0.15 + 0.24 + 0.25 + 0.19 + 0.23 + 0.11 + 0.32 + 0.13 + 0.09 + 0.18 + 0.17 + 0.23 + 0.13)/16
+
+#TOTAL AVERAGE sampling completeness of links 0.20
 
@@
 
-  Our sampling completeness analyses revealed that with our survey we were able to capture 18-62% of pollinator species (average = 35%), 47-98% for plant species (average = 78%) and 13-41% for plant-pollinator links (average = 27%), in line with that obtained with other studies (e.g., [@Chacoff2012], Fig.
+  Our sampling completeness analyses revealed that with our survey we were able to capture 17-54% of pollinator species (average = 35%), 43-100% for plant species (average = 80%) and 9-32% for plant-pollinator links (average = 20%), in line with that obtained with other studies (e.g., [@Chacoff2012], Fig.
 S2).
-Our values of sampling completeness are slightly smaller in the case of pollinators, probably as a consequence of the great diversity found in the Mediterranean region and within our study area in particular, a hotspot of insect diversity [@Nieto2014].
-In addition, the fact that we include an extra effort to capture rare interactions observed outside of our main sampling might also increase the number of singletons which directly affect richness estimates.
+Our values of sampling completeness were slightly smaller in the case of pollinators, probably as a consequence of the great diversity found in the Mediterranean region and within our study area in particular, a hotspot of insect diversity [@Nieto2014].
 
@@
 
-# CALCULATE NICHE OVERLAP BETWEEN PLANT SPECIES AND TOTAL NUMBER OF VISITS AND JOIN FRUITSET DATA WITH NETWORK METRICS
-
-#calculate total number of visits per plant sps
-
-d.vis<-ddply(d, c("Site_ID", "Plant_gen_sp"), summarise,
-            tot.visits= sum(Frequency))
+# CALCULATE NICHE OVERLAP BETWEEN PLANT SPECIES AND RELATIVE 
+#NUMBER OF VISITS AND JOIN FRUITSET DATA WITH NETWORK METRICS
+
+#calculate RELATIVE number of visits per plant sps
+flower_count<-read.csv("Flower_Count_BeeFun_2015.csv")  ###############CAMBIAR POR BASE DE DATOS EN BEEFUN!
+flower_count$Plant_gen_sps<-paste(flower_count$Plant.genus, flower_count$Plant.species)
+
+flower_count2<-ddply(flower_count, c("Site_ID", "Plant_gen_sps"), summarise,
+             tot.flowers= sum(Flower.abundance))
+
+flower_count2$j<-paste(flower_count2$Site_ID, flower_count2$Plant_gen_sps)
+
+dtrans$j<-paste(dtrans$Site_ID, dtrans$Plant_gen_sp)
+
+dtrans$flower_count<-flower_count2$tot.flowers[match(dtrans$j, flower_count2$j)]
+#head(dtrans)
+
+d.vis<-ddply(dtrans, c("Site_ID", "Plant_gen_sp"), summarise,
+             tot.visits= sum(Frequency),
+             tot.flower=sum(flower_count))
+
+#replace NA, species with no flower count for a particular site with 10 (min number of flowers)
+d.vis$tot.flower[is.na(d.vis$tot.flower)] <- 10
+
+d.vis$rel.visits<-d.vis$tot.visits/d.vis$tot.flower #CALCULATE NUMBER OF VISITS AND DIVIDE BY AVERAGE NUMBER OF FLOWERS PER PLANT SPECIES TO GET A RELATIVE VALUE OF VISITS
 
@@
 
-sites <- unique(d$Site_ID)
+sites <- unique(dtrans$Site_ID)
 
@@
 for(i in 1:length(sites)){
-  temp <- subset(d, Site_ID == sites[i])
+  temp <- subset(dtrans, Site_ID == sites[i])
   temp2<-droplevels(temp)
@@
 
-#and with niche overlap and total number of visits
+#and with niche overlap and RELATIVE number of visits
 f2$niche.overlap<-out.niche.agg$mean.niche.over[match(f2$match, out.niche.agg$j)]
 
+f2$rel.visits<-d.vis$rel.visits[match(f2$match, d.vis$j)]
+f2$rel.visits[is.na(f2$rel.visits)]<-0
+
+#also total visits for site level calculation of pollinator abundance
+
 f2$tot.visits<-d.vis$tot.visits[match(f2$match, d.vis$j)]
-f2$tot.visits[is.na(f2$tot.visits)]<-0
+f2$tot.visits[is.na(f2$tot.visits)]<-0  #we use the total number of species to then calculate total number of visits at site level as a proxy for pollinator abundance
 
@@
 
-sites <- unique(d$Site_ID)
-plants<-unique(d$Plant_gen_sp)
+sites <- unique(dtrans$Site_ID)
 
@@
 for(i in 1:length(sites)){
-  temp <- subset(d, Site_ID == sites[i])
+  temp <- subset(dtrans, Site_ID == sites[i])
+  tempb<-droplevels(temp)
+  plants<-unique(tempb$Plant_gen_sp)
   for(j in 1:length(plants)){
-      temp2 <- subset(temp, Plant_gen_sp == plants[j])
+    temp2 <- tempb[tempb$Plant_gen_sp == plants[j],]
   temp3<-droplevels(temp2)
@@
 f2$pollspsperplant.sc<-scale(f2$pollspsperplant, center = T, scale = T)
+f2$rel.visits.sc<-scale(f2$rel.visits, center = T, scale = T)
 f2$tot.visits.sc<-scale(f2$tot.visits, center = T, scale = T)
@@
 
-#compare 2 models: one with simple diversity metrics (pollinator richness and number of visits), compared to one where position in a network (centrality) and niche overlap are included with these variables.
-
-m1<-glmer(tot.fruitset ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2)
+#compare 3 models: one null model, one with simple diversity metrics (pollinator richness and number of visits), compared to one where position in a network (centrality) and niche overlap are included with these variables.
+
+m0<-glmer(tot.fruitset ~ 1 + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2, REML=FALSE)
+summary(m0)
+
+m1<-glmer(tot.fruitset ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2, REML=FALSE)
 summary(m1)
@@
 
-m2<-glmer(tot.fruitset ~  pollspsperplant.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2)
+m2<-glmer(tot.fruitset ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2, REML=FALSE)
 
@@
 
-AICtab(m1, m2)
+AICtab(m0,m1, m2)
+
+#best model fit with REML=TRUE
+
+m2<-glmer(tot.fruitset ~  pollspsperplant.sc  * rel.visits.sc + pollspsperplant.sc  *weigh_closeness.sc + pollspsperplant.sc  *niche.overlap.sc + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2, REML=TRUE)
+
+summary(m2)
 
@@
 Table1A<-round(coefs.m2[,1:3],digits=2)
-rownames(Table1A)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Centrality", "Plant niche overlap")
+rownames(Table1A)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Centrality", "Plant niche overlap")
 #at the end of the paper
@@
 
-y_partial_weigh <- remef(m2, fix= c( "tot.visits.sc", "pollspsperplant.sc", "niche.overlap.sc"), ran = "all", inverse = F)
+y_partial_weigh <- remef(m2, fix= c( "rel.visits.sc", "pollspsperplant.sc", "niche.overlap.sc"), ran = "all", inverse = F)
 #With this we remove the influece of x2 and the random effects from the dependent variable
@@
   xlab("Centrality") +      
-  ylab("Fruit set ") + theme_bw()  + theme (legend.position= "bottom") +
+  ylab("Fruit set") + theme_bw()  + theme (legend.position= "bottom") +
   theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.3), face="bold")) + 
@@
 
-```
-
-At the species level, in the case of fruit set, our results show that model 2 shows the best fit to our data (lowest AIC value), and fixed  effects explains `r round(r2$Marginal[1], 2)*100`% of the variability observed.
-In this case, we find a positive effect of a network structure metric, the centrality of a focal plant within the overall network on its fruit set (Table 1, Fig.
-2A).
+y_partial_weigh2 <- remef(m2, fix= c( "weigh_closeness.sc", "pollspsperplant.sc", "niche.overlap.sc"), ran = "all", inverse = F)
+#With this we remove the influece of x2 and the random effects from the dependent variable
+y_partial_weigh_inv2<-exp(y_partial_weigh2)/(1+exp(y_partial_weigh2))
+
+FigureS4<-ggplot(m2@frame,  aes(x=m2@frame$rel.visits.sc, y=y_partial_weigh_inv, color= Plant.sp)) +
+  geom_point(size=2.5, shape=21,color = "black", aes(fill=factor(Plant.sp))) +
+  stat_smooth(method=glm,  method.args = list(family = "binomial"), size=1, se=TRUE, color = "black", alpha=0.4) +
+  xlab("Relative number of visits") +
+  ylab("Fruit set") + theme_bw()  + theme (legend.position= "bottom") +
+  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.3), face="bold")) +
+  scale_fill_discrete(name="Plant species") +  theme(legend.text = element_text(size = 14, face = "italic"), legend.title = element_text(size=15, face = "bold"), legend.direction = "vertical") + guides(fill=guide_legend(ncol=4))
+#
+
+#This relationship is largely driven by one single point species
+
+#redo analysis removing one plant species with large number of visits
+
+f2.sub<-subset(f2, f2$rel.visits.sc<4)
+
+m2b<-glmer(tot.fruitset ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2.sub, REML=TRUE)
+
+summary(m2b) #This relationship is largely driven by one single point species so we show results remving one species
+
+# extract estimates and st errors to present in table
+coefs.m2b <- data.frame(coef(summary(m2b)))
+#coefs.m2
+TableS5<-round(coefs.m2b[,1:3],digits=2)
+rownames(TableS5)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Centrality", "Plant niche overlap")
+#at the end of the paper
+
+```
+
+At the species level, in the case of fruit set, our results showed that model 2 had the best fit to our data (lowest AIC value), and fixed  effects explained `r round(r2$Marginal[1], 2)*100`% of the variability observed (conditional R^2=`r round(r2$Conditional[1], 2)*100`%).
+In this case, we found a positive relationship between fruit set the relative number of visits, and a network structure metric, the centrality of a focal plant within the overall network (Table 1, Fig.
+2A, Fig.
+S3).
+However, in the case of the relative number of visits a single point seemed to be driving the relationship and removing this single point lead to a decrease in the importance of this variable (Fig.
+S4, Table S5).
 
@@
 
+s3$rel.visits<-d.vis$rel.visits[match(s3$match, d.vis$j)]
+s3$rel.visits[is.na(s3$rel.visits)]<-0
+
 s3$tot.visits<-d.vis$tot.visits[match(s3$match, d.vis$j)]
@@
 s3$pollspsperplant.sc<-scale(s3$pollspsperplant, center = T, scale = T)
+s3$rel.visits.sc<-scale(s3$rel.visits, center = T, scale = T)
 s3$tot.visits.sc<-scale(s3$tot.visits, center = T, scale = T)
@@
 
+#correlation between reproduction variables
+
+ # cor(s3[,4:6], use = "everything",
+ #     method = "pearson")
+
 ```
@@
 ```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
-#fit two models
-
-m1.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3)
+#fit three models
+
+s3$seedcomb<-s3$mean.seedn*s3$mean.seedw
+s3$seedcomb.sc<-scale(s3$seedcomb, center = T, scale = T)
+
+m0.seed<-glmer(mean.seedn.sc ~  1  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3, REML=FALSE)
+summary(m0.seed)
+
+m1.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3, REML=FALSE)
 
@@
 
-m2.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3)
-
+m2.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3, REML=FALSE)
 summary(m2.seed)
@@
 
-AICtab(m1.seed, m2.seed) #m2 is best
+AICtab(m0.seed, m1.seed, m2.seed) #m2 is best
+
+m2.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3, REML=TRUE)
+summary(m2.seed)
 
@@
 Table1B<-round(coefs.m2.seed,digits=2)
-rownames(Table1B)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Centrality", "Plant niche overlap")
+rownames(Table1B)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Centrality", "Plant niche overlap")
 
 #plot significant variables
-y_partial_norm_seed <- remef(m2.seed, fix= c("pollspsperplant.sc", "tot.visits.sc", "weigh_closeness.sc"), ran = "all")
+y_partial_norm_seed <- remef(m2.seed, fix= c("pollspsperplant.sc", "rel.visits.sc", "weigh_closeness.sc"), ran = "all")
 #With this we remove the influece of x2 and the random effects from the dependent variable
@@
   #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
-  xlab("Plant niche overlap") +      
+  xlab("Niche overlap") +      
   ylab("Number of \n seeds per fruit") + theme_bw()  + theme (legend.position= "right") +
@@
 
-#Figure2b
+#Figure2c
 
@@
 
-prow <- plot_grid( Figure2a + theme(legend.position="none"),
+prow <- cowplot::plot_grid( Figure2a + theme(legend.position="none"),
                    Figure2b + theme(legend.position="none"),
@@
 # of one plot (via rel_heights).
-Figure2 <- plot_grid( prow, legend_b, ncol = 1, rel_heights = c(2, 1))#al final del paper
-
-```
-
- For the average number of seeds per fruit, our results show again that model 2 shows the best fit, with fixed effects explaining `r round(r2b$Marginal[1], 2)*100`% of the variability observed in our data.
-In this case, we find a positive effect of the niche overlap between plant species on the number of seeds produced (Table 1B, Fig.
-2B).
+Figure2 <- cowplot::plot_grid( prow, legend_b, ncol = 1, rel_heights = c(2, 1))#al final del paper
+
+FigureS3<-plot_summs(m2, m2.seed, level=0.95, scale = TRUE, model.names = c("Fruit set", "Number of seeds"), legend.title = "Response variables", cex.axis=2)
+
+```
+
+ For the average number of seeds per fruit, our results showed again that model 2 had the best fit, with fixed effects explaining `r round(r2b$Marginal[1], 2)*100`% of the variability observed in our data (conditional R^2 =`r round(r2b$Conditional[1], 2)*100`% ).
+In this case, we found a positive relationship between plant niche overlap and the number of seeds produced (Table 1B, Fig.
+2B, Fig.
+S3).
 
@@
 
-m1.seed.w<-glmer(mean.seedw ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3)
+m0.seed.w<-glmer(mean.seedw ~  1  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3)
+
+summary(m0.seed.w)
+
+m1.seed.w<-glmer(mean.seedw ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3)
 
@@
 
-m2.seed.w<-glmer(mean.seedw ~  pollspsperplant.sc + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3)
+m2.seed.w<-glmer(mean.seedw ~  pollspsperplant.sc + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3)
 
@@
 
-AICtab(m1.seed.w, m2.seed.w)
-
-# extract estimates and st error for m1 and present them in paper
-coefs.m1.seed.w <- data.frame(coef(summary(m1.seed.w)))
-tableS5<-round(coefs.m1.seed.w,digits=2)
-rownames(tableS5)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
+AICtab(m0.seed.w, m1.seed.w, m2.seed.w)
+
+#best model is null model
 
 #FRUIT WEIGHT
-
-m1.fruit.w<-glmer(mean.fruitweight ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3)
+m0.fruit.w<-glmer(mean.fruitweight ~  1  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3, REML=FALSE)
+
+summary(m0.fruit.w)
+
+m1.fruit.w<-glmer(mean.fruitweight ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3, REML=FALSE)
 
@@
 
-m2.fruit.w<-glmer(mean.fruitweight ~  pollspsperplant.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3)
+m2.fruit.w<-glmer(mean.fruitweight ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3, REML=FALSE)
 
@@
 
-AICtab(m1.fruit.w, m2.fruit.w)
-
-# extract estimates and st error for m2 and present them in paper
-coefs.m1.fruit.w <- data.frame(coef(summary(m1.fruit.w)))
-tableS6<-round(coefs.m1.fruit.w,digits=2)
-rownames(tableS6)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
-
-FigureS3<-plot_summs(m2, m2.seed, m1.fruit.w, m1.seed.w, level=0.95, scale = TRUE, model.names = c("Fruit set", "Number of seeds", "Fruit weight", "Seed weight"), legend.title = "Response variables", cex.axis=2)
-
-```
- For all other measures of reproductive success considered (i.e., fruit and seed weight), model 1 showed the best fit.
-However, none of the variables included within our model explain the differences observed (Tables S5-S6).
+AICtab(m0.fruit.w, m1.fruit.w, m2.fruit.w)
+
+#best model is null model
+
+```
+ For all other measures of reproductive success considered (i.e., fruit and seed weight), none of the models fitted showed a better fit than the null model.
 
@@
 
+m0.fruit.net<-glmmTMB(mean.fruitset ~  1, family="beta_family", data=f.agg)
+
+summary(m0.fruit.net)
+
 m1.fruit.net<-glmmTMB(mean.fruitset ~  species.poll.sc + tot.visits.sc, family="beta_family", data=f.agg)
@@
 
-m2.fruit.net<-glmmTMB(mean.fruitset ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="beta_family", data=f.agg)
+m2.fruit.net<-glmmTMB(mean.fruitset ~  species.poll.sc + tot.visits.sc + functional.comp.poll.sc + nodf.song.sc  , family="beta_family", data=f.agg)
 
@@
 
-AICtab(m1.fruit.net, m2.fruit.net) #Almost as good.
+AICtab(m0.fruit.net, m1.fruit.net, m2.fruit.net) #Almost as good.
 With this, you cannot say one is better than the other one.
@@
 
+m2.fruit.net<-glmmTMB(mean.fruitset ~   tot.visits.sc + nodf.song.sc + functional.comp.poll.sc + species.poll.sc , family="beta_family", data=f.agg)
+
+summary(m2.fruit.net)
+
 #table with results for paper
 Table2A<-round(summary(m2.fruit.net)$coefficients$cond[,1:3], digits=2)
-rownames(Table2A)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Nestedness", "Pollinator niche complementarity")
+rownames(Table2A)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Nestedness", "Pollinator niche complementarity")
 #at the end of paper
@@
 
-FigureS4A<-plot_model(m2.fruit.net, title="Fruit set")
+FigureS5A<-plot_model(m2.fruit.net, title="Fruit set")
 ```
@@
 #NUMBER OF SEEDS PER FRUIT
+m0.seed.net <- lm(mean.seedset ~  1,
+    data=s.comm,family="gaussian")
+
+ summary(m0.seed.net)
 
@@
 #select best model based on AIC 
-AICtab(m1.seed.net, m2.seed.net)#both models are equally good
+AICtab(m0.seed.net, m1.seed.net, m2.seed.net)#both models are equally good
 
@@
 Table2B<-round(summary(m2.seed.net)$coefficients[,1:3], digits=2)
-rownames(Table2B)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Nestedness", "Pollinator niche complementarity") #end of paper
+rownames(Table2B)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Nestedness", "Pollinator niche complementarity") #end of paper
 
@@
 
-Figure3<-plot_grid(pl3, pl2, pl6, labels = c("A", "B", "C"), nrow=1)
-
-FigureS4B<-plot_model(m2.seed.net, title="Number of seeds")
-```
-
-At the site level, we find different patterns for fruit set and the number of seeds per fruit as compared to those for fruit and seed weight.
-In the case of fruit set and the number of seeds per fruit, we find that both model 1 and 2 are equally good in describing the differences observed when penalizing for model complexity (i.e.,$\Delta AIC<2$; [@Burnham2002a]).
-This suggests model 2 is a good model despite its added complexity, and actually shows a substantially better predictive ability than model 1 (R^2 = `r round(r2.m2, 2)` for model 2 versus `r round(r2.m1, 2)` for model 1 in the case of fruit set and R^2 = `r round(r2.m2.seed,2)` for model 2 versus `r round(r2.m1.seed, 2)` for model 1 in the case of the number of seeds per fruit) and therefore we will comment results for this model only.
-In particular, we find that both fruit set and the number of seeds per fruit are positively related to niche complementarity between pollinators (Tables 2, Fig.
-3).
-Additionally, we find a negative effect of site-level pollinator richness on average fruit set (Table 2A, Fig.
-3).
+Figure3<-cowplot::plot_grid(pl3, pl2, pl6, labels = c("A", "B", "C"), nrow=1)
+
+FigureS5B<-plot_model(m2.seed.net, title="Number of seeds")
+```
+
+At the site level, in the case of fruit set and the number of seeds per fruit, we found that both model 1 and 2 were equally good in describing the differences observed when penalizing for model complexity (i.e.,$\Delta AIC<2$; [@Burnham2002a]).
+This suggests model 2 was a good model despite its added complexity, and actually shows a substantially better predictive ability than model 1 (R^2 = `r round(r2.m2, 2)` for model 2 versus `r round(r2.m1, 2)` for model 1 in the case of fruit set and R^2 = `r round(r2.m2.seed,2)` for model 2 versus `r round(r2.m1.seed, 2)` for model 1 in the case of the number of seeds per fruit) and therefore we will comment results for this model only.
+In particular, we found that both fruit set and the number of seeds per fruit were positively related to niche complementarity between pollinators (Tables 2, Fig.
+3, Fig.
+S5).
+Additionally, we found a negative association between site-level pollinator richness and average fruit set (Table 2A, Fig.
+3, Fig.
+S5).
 
@@
 #FRUIT WEIGHT
+m0.fruitw.net<-lm(mean.fruitweight ~  1, family="gaussian", data=s.comm)
+
+summary(m0.fruitw.net)
 
@@
 
-AICtab(m1.fruitw.net, m2.fruitw.net)
+AICtab(m0.fruitw.net, m1.fruitw.net, m2.fruitw.net)
 
@@
 r2.fruitw1<-r.squaredGLMM(m1.fruitw.net)
-r2.fruitw2<-r.squaredGLMM(m2.fruitw.net)
 
 #save table with results for paper
-tableS7A<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)#ch
-rownames(tableS7A)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")#end of paper
+tableS6A<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)#ch
+rownames(tableS6A)<-c("(Intercept)", "Pollinator species diversity", "Relative number of visits")#end of paper
 
@@
 
+m0.fruitw.net2<-lm(mean.fruitweight ~  1, family="gaussian", data=s.comm2)
+
+summary(m0.fruitw.net2)
 m1.fruitw.net2<-lm(mean.fruitweight ~  species.poll.sc + tot.visits.sc, family="gaussian", data=s.comm2)
@@
 
-AICtab(m1.fruitw.net2, m2.fruitw.net2)
+AICtab(m0.fruitw.net2, m1.fruitw.net2, m2.fruitw.net2)
 
 #save table with results for paper
-tableS7B<-round(summary(m1.fruitw.net2)$coef[,1:3], digits=2)#ch
-rownames(tableS7B)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")#end of paper
+tableS6B<-round(summary(m1.fruitw.net2)$coef[,1:3], digits=2)#ch
+rownames(tableS6B)<-c("(Intercept)", "Pollinator species diversity", "Relative number of visits")#end of paper
 
@@
 
+m0.seedw.net<-glm(mean.seedweight ~  1, family="gaussian", data=s.comm)
+
+summary(m0.seedw.net)
+
 m1.seedw.net<-glm(mean.seedweight ~  species.poll.sc + tot.visits.sc, family="gaussian", data=s.comm)
@@
 
-AICtab(m1.seedw.net, m2.seedw.net) #m1 is better
+AICtab(m0.seedw.net,m1.seedw.net, m2.seedw.net) #m1 is better
 
@@
 #save table with results for paper
-tableS8A<-round(summary(m1.seedw.net)$coef[,1:3], digits=2)#ch
-rownames(tableS8A) <-c("(Intercept)", "Pollinator species diversity", "Total number of visits")#end of paper
+tableS7A<-round(summary(m1.seedw.net)$coef[,1:3], digits=2)#ch
+rownames(tableS7A) <-c("(Intercept)", "Pollinator species diversity", "Relative number of visits")#end of paper
 
@@
 
-Figure4<-plot_grid(pltest, pltest2, labels = c("A", "B"), nrow=1)
+FigureS6<-cowplot::plot_grid(pltest, pltest2, labels = c("A", "B"), nrow=1)
 
@@
 
+m0.seedw.net2<-glm(mean.seedweight ~  1, family="gaussian", data=s.comm2)
+
+summary(m0.seedw.net2)
 m1.seedw.net2<-glm(mean.seedweight ~  species.poll.sc + tot.visits.sc, family="gaussian", data=s.comm2)
@@
 
-AICtab(m1.seedw.net2, m2.seedw.net2) #m1 is better
+AICtab(m0.seedw.net2, m1.seedw.net2, m2.seedw.net2) #m1 is better
 
 #save table with results for paper
-tableS8B<-round(summary(m1.seedw.net2)$coef[,1:3], digits=2)#ch
-rownames(tableS8B) <-c("(Intercept)", "Pollinator species diversity", "Total number of visits")#end of paper
+tableS7B<-round(summary(m1.seedw.net2)$coef[,1:3], digits=2)#ch
+rownames(tableS7B) <-c("(Intercept)", "Pollinator species diversity", "Relative number of visits")#end of paper
 
@@
 
-FigureS5<-plot_grid(pltestb, pltest2.sub, labels = c("A", "B"), nrow=1)
-
-FigureS4C<-plot_summs(m1.fruitw.net, m1.seedw.net, level=0.95, scale = TRUE, model.names = c("Fruit weight", "Seed weight"), legend.title = "Response variables")
+FigureS7<-cowplot::plot_grid(pltestb, pltest2.sub, labels = c("A", "B"), nrow=1)
+
+FigureS5C<-plot_summs(m1.fruitw.net, m1.seedw.net, level=0.95, scale = TRUE, model.names = c("Fruit weight", "Seed weight"), legend.title = "Response variables")
 
@@
 
-  Contrastingly, in the case of weight variables (fruit and seed weight), in both cases we find that the best model is model 1, i.e., that only including simple visitation metrics (R^2 = `r round(r2.fruitw1[2], 2)` in the case of fruit weight and `r round(r2.seedw1[2], 2)` in the case of seed weight).
-Here, we find a consistent positive effect of site-level pollinator richness for both weight descriptors (Tables S7A-S8A, Fig.
-4).
-This effect is maintained even after removing a site that has a particularly large pollinator richness value (Tables S7B-S8B, Fig.
+  In the case of weight variables (fruit and seed weight), in both cases we found that both the null model, model 0 and model 1 were equally good (i.e.,$\Delta AIC<2$; [@Burnham2002a]).
+Following previous logic, given the both models were equally good despite the added complexity in model 1, we will only comment on this model.
+In this case model 1, i.e., that only including simple visitation metrics, showed an R^2  of  0.23.
+For seed weight, we found model 1 to be the best model too (R^2 = 0.39 in this case).
+In both cases, we found a consistent positive link to site-level pollinator richness (Tables S6A-S7A, Figs.
+S5-S6).
+This association was maintained even after removing a site that has a particularly large pollinator richness value (Tables S6B-S7B, Fig.
+S7, Fig.
 S5).
@@
 
-When evaluating the effect of differences in community composition and network structure for equity in reproductive success across the different species within a community we find that model 1 is the best model for all the thresholds considered (50^th, 25^th and 75^th percentiles).
-However, none of the variables considered are able to explain differences observed in equity across sites (Tables S9, S10, S11).
+When evaluating the relationship between community composition and network structure on equity in reproductive success across the different species within a community, we found that using the 50^th percentile all models were equally good (i.e.,$\Delta AIC<2$; [@Burnham2002a]), and we will thus comment only model 2.
+Here, none of the variables considered showed any strong associations (Table S8).
+In the case of the other two thresholds considered (25^th and 75^th percentiles) model 0, the null model, was the best model.
 
@@
 
-highprod<-subset(f.ag, f.ag$mean.fruitset>0.63)
+highprod<-subset(f.ag, f.ag$mean.fruitset>q[2])
 highprod.sps<-ddply(highprod, "Site_ID", summarise, 
@@
 
-#fit two models
+#fit three models
+ m0.eq.comm<-glm(equity ~  1 , family="binomial", data=highprod.sps)
+
+ summary(m0.eq.comm)
+
  m1.eq.comm<-glm(equity ~  species.poll.sc + tot.visits.sc , family="binomial", data=highprod.sps)
@@
 
- m2.eq.comm<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc , family="binomial", data=highprod.sps)
+ m2.eq.comm<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="binomial", data=highprod.sps)
 summary(m2.eq.comm)
@@
 
-AICtab(m1.eq.comm, m2.eq.comm) #m1 is best no variables significant
-
-#save table with results for paper, both models are equally good so save both tables
-tableS9<-round(summary(m1.eq.comm)$coef[,1:3], digits=2)#ch
-rownames(tableS9)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
+AICtab(m0.eq.comm, m1.eq.comm, m2.eq.comm) #m1 is best no variables significant
+
+r2.eq<-r.squaredGLMM(m1.eq.comm)
+
+#save table with results for paper
+tableS8<-round(summary(m2.eq.comm)$coef[,1:3], digits=2)#ch
+rownames(tableS9)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Nestedness", "Pollinator niche complementarity")
 
@@
 
-highprod75<-subset(f.ag, f.ag$mean.fruitset>0.91)
+highprod75<-subset(f.ag, f.ag$mean.fruitset>q[3])
 highprod75.sps<-ddply(highprod75, "Site_ID", summarise, 
@@
 
-#fit two models
+#fit three models
+
+ m0.eq.comm75<-glm(equity ~  1 , family="binomial", data=highprod75.sps)
+
+ summary(m0.eq.comm75)
+
  m1.eq.comm75<-glm(equity ~  species.poll.sc + tot.visits.sc , family="binomial", data=highprod75.sps)
@@
 
-AICtab(m1.eq.comm75, m2.eq.comm75) #m1 is best no variables significant
-
-tableS10<-round(summary(m1.eq.comm75)$coef[,1:3], digits=2)#ch
-rownames(tableS10)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
+AICtab(m0.eq.comm75,m1.eq.comm75, m2.eq.comm75) #m1 is best no variables significant
 
@@
 
-highprod25<-subset(f.ag, f.ag$mean.fruitset>0.63)
+highprod25<-subset(f.ag, f.ag$mean.fruitset>q[1])
 highprod25.sps<-ddply(highprod25, "Site_ID", summarise, 
@@
 
-#fit two models
+#fit three models
+
+ m0.eq.comm25<-glm(equity ~  1 , family="binomial", data=highprod25.sps)
+
+ summary(m0.eq.comm25)
+
  m1.eq.comm25<-glm(equity ~  species.poll.sc + tot.visits.sc , family="binomial", data=highprod25.sps)
@@
 
-AICtab(m1.eq.comm25, m2.eq.comm25) #m1 is best no variables significant
-
-tableS11<-round(summary(m1.eq.comm25)$coef[,1:3], digits=2)#ch
-rownames(tableS11)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
-
-```
-
-  Within our simulation evaluating the effect of niche complementarity on equity in reproductive success as more plants within the community are considered, we find that the effect of complementarity becomes more important as the reproductive success of more species is considered (Fig.
-5).
-This importance seems to reach some sort of plateau at 6 species.
-However, this should be further evaluated, as this is the maximum number of species simultaneously observed in a community for our study, which precludes us from simulating further numbers of species.
+AICtab(m0.eq.comm25, m1.eq.comm25, m2.eq.comm25) #m1 is best no variables significant
+
+```
+
+  Within our simulation evaluating the relationship between niche complementarity and equity in reproductive success, we found that the link to complementarity became more important as more species were considered (Fig.
+4).
+This importance seemed to reach a plateau at 6 species.
+However, this should be further evaluated, as this was the maximum number of species simultaneously observed in a community for our study, which precludes us from simulating further numbers of species.
 
@@
 
-Figure5<-ggplot(estimate_i,  aes(x=level, y=estimate)) +    
+Figure4<-ggplot(estimate_i,  aes(x=level, y=estimate)) +    
   geom_point(size=4) + 
@@
 
-The existence of relationships between interaction network structure and ecosystem function have been long hypothesized, yet, the specific mechanisms by which structure influences function have remained elusive until now [@Thompson2012].
-Our results show that different aspects of network structure affect different dimensions of ecosystem functioning.
-In particular, we find that the centrality of a plant species within a community, which measures the number of connections it receives from other species in the community, has a positive effect for its fruit set.
-At the site level, we find that greater values of niche complementarity between pollinators result in larger average fruit sets and number of seeds per fruit.
-
-  One of the first conclusions we can extract from the fact that in most cases both of the models we considered (i.e., the simple model based on visitation metrics and the more complex one including network structure metrics) were equally good, is that the added complexity of measuring the full network of interactions may not pay off for rapid assessments.
+The existence of relationships between interaction network structure and ecosystem function have been long hypothesized, yet, the specific mechanisms underlying this relationship remain elusive [@Thompson2012].
+Our results suggest that different aspects of network structure affect different dimensions of ecosystem functioning.
+In particular, we find that the centrality of a plant species within a community has a positive association with its fruit set.
+At the site level, we find that greater values of niche complementarity between pollinators result in larger average values of reproductive success.
+
+ Most of our analyses reveal that both model 1 and 2 were equally good, which suggests that the added complexity of measuring the full network of interactions may not pay off for rapid assessments.
 Hence, simple visitation metrics, such as pollinator richness, might be enough to describe general patterns [@Garibaldi2013; @Garibaldi2015].
 Yet, adding network level information may inform us of the potential ecological mechanisms underlying the processes driving these observed patterns.
-
-  Consistent with previous experimental [@Fontaine2005; @Frund2013], theoretical [@Pauw2013], and empirical studies [@Poisot2013; @Valdovinos2016], we find that niche complementarity is key in determining differences in reproductive outputs.
-Indeed, we find that communities where there is less overlap in the niches occupied by pollinator species had greater values of reproductive success, both greater fruit set and larger numbers of seeds per fruit.
-This therefore reflects the fact that reproductive success in plant species requires the delivery of conspecific pollen and thus of a certain degree of specialization amongst pollinator species on a particular plant resource in order to avoid the negative effects of inter-specific pollen deposition (e.g., pollen loss [@Flanagan2009] or interference with conspecific pollen [@Morales2008]).
+Further, although we sampled each site seven times in a randomized order in an attempt to better represent interactions through time, our surveys were able to capture 20% of interactions given the great diversity of our study system.
+This could be explaining part of the low effect sizes we find at the species level, where a stronger contribution of pollinator visits is expected given their obligate dependence.
+In addition, plant reproductive success is affected by other variables which we do not attempt to measure in this study and that could explain a large portion of the variability observed (e.g., XX).
+
+  Consistent with previous experimental [@Fontaine2005; @Frund2013], theoretical [@Pauw2013], and empirical studies [@Poisot2013; @Valdovinos2016], we find that niche complementarity is key in determining differences in reproductive outputs at the community level, both greater fruit set and larger numbers of seeds per fruit.
+These results show that reproductive success in plants requires of a certain degree of specialization amongst pollinator species on a particular plant resource in order to avoid the negative effects of inter-specific pollen deposition (e.g., pollen loss [@Flanagan2009] or interference with conspecific pollen [@Morales2008]).
 However, we also find that some level of redundancy in these functions is needed as revealed by the positive effect of plant niche overlap on the number of seeds per fruit at the species level.
 
-  In our study, we did not find an effect of nestedness for reproductive success in any case.
+  In our study, we did not find a relationship between nestedness and any of the reproductive success measures.
 This metric, widely used across network analysis, and which is deemed to stabilize natural communities ([@Bastolla2009] but see [@James2012]), does not seem to play a direct role in ecosystem function measured as plant reproductive success.
-However, our study is limited to a maximum of six common plant species per community, and including more species, including rare species, might reveal different patterns, in which nestedness and the redundancy it implies might play a more important role.
-
-  Site-level plant reproductive success measured as average fruit or seed set across all the species considered, is an important part of the functions delivered by pollinators to plants.
+However, our study is limited to a maximum of six common plant species per community, and including more species, especially rare species, might reveal different patterns.
+
+  Our measure of reproductive success at the site level using average values of fruit or seed set represents an important part of the functions delivered by pollinators to plants.
 However, these average values might be masking a great deal of variability amongst plant species, and thus a nuanced view of the effect of pollinators on whole-plant ensembles is needed.
 This can be captured by the effect of pollinators on equity in reproductive success across plant species.
-This aspect ensures that reproductive success is equally distributed amongst a larger number of species, thus contributing to the maintenance of greater species diversity values in natural populations.
+This aspect ensures that reproductive success is equally distributed amongst a larger number of species, thus contributing to the maintenance of greater species diversities in natural populations.
 Indeed, we know that plant species diversity within a community is largely driven by different types of direct and indirect interactions including those amongst plant species (e.g., resource competition [@Goldberg1992] or facilitation [@Bruno2003]), as well as those defining antagonistic (e.g., involving pathogens [@Bagchi2010], or mutualistic interactions (e.g, pollinators [@Benadi2013; @Lanuza2018]).
@@
  In the case of equity, we did not find a strong effect of either simple visitation or network structure metrics.
-However, the results of our simulation on the importance of network structure as the number of plant species considered increases, shows us that this effect increases when more than four plant species are considered.
-This implies that if we were able to measure reproductive success for all the plant species in all the communities (which is not feasible given constraints in sampling effort), we might find that the effects of network structure on equity might be more prevalent.
-
-  One of the unexpected results of our analyses is the strong negative effect of pollinator richness for fruit set at the site level.
-An explanation to this might be the fact that pollinator richness here includes all the pollinators recorded during our sampling efforts, i.e., it includes species that do not pollinate some of the species whose reproductive success was measured.
+However, the results of our simulation, shows us that the effect of network structure increases when more than four plant species are considered.
+This implies that if we were able to measure reproductive success for all the plant species in all the communities (which is not feasible given constraints on sampling effort), we might find that the effects of network structure on equity might be more prevalent.
+
+  One of the unexpected results of our analyses is the strong negative relationship between pollinator richness and fruit set at the site level.
+One possible explanation for this is that greater richness means greater transfer of heterospecific pollen [@Arceo-Gomez2019].
+Another possible explanation to this might be the fact that pollinator richness includes all the pollinators recorded during our sampling efforts, i.e., it includes species that do not pollinate some of the species whose reproductive success was measured.
 More complex communities with more pollinators, but also with more plant species (Pearson correlation between plant and pollinator richness  = 0.42 in our case) may require stabilizing mechanisms that reduce the competition exerted by the dominant plant species.
@@
 
-  Our study illustrates the complexity of linking network structure to ecosystem function empirically, because measuring both structure and function is challenging.
-For example, there is an ongoing debate as to which network metrics better reflect classic ecological mechanisms, such as niche partitioning or competition [@Delmas2019].
-Here, we focus on testing two specific hypotheses, but other structural properties can be explored when more data becomes available.
+Our study illustrates the challenges of measuring and linking network structure to ecosystem function empirically.
+There is an ongoing debate as to which network metrics better reflect classic ecological mechanisms, such as niche partitioning or competition [@Delmas2019].
+Here, we focus on testing two specific hypotheses, but other structural properties can be explored in the future.
 Furthermore, the structure of plant-pollinators networks is dynamic due to ecological and evolutionary reasons, but so far, we are only able to characterize it for single snap-shots.
@@
 
-  In summary, our findings show that the analysis of natural communities of interacting species using network analysis not only represents an ideal way of visualizing and grasping the complexity present within these communities.
-Rather, it also represents a manner of mechanistically understanding differences observed across the reproductive success of individuals and/or species while linking them to potential ecological mechanisms.
+ In summary, our findings show that the analysis of natural communities using network analysis represents an ideal way of visualizing the complexity present within these communities, but also represents a manner of mechanistically representing the differences observed across the reproductive success of individuals and/or species while linking them to potential ecological mechanisms.
+Our findings represent a step forward in our understanding of how community structure affects function, yet they also show that more studies with better resolved communities are needed, with a special focus being placed in evaluating reproductive success of a larger array of plant species.
 
@@
 The authors would like to thank Oscar Aguado for identifying pollinator species.
-We would also like to acknowledge the efforts of the editor Cédric Gaucherel, as well as those of Michael Lattorff, Nicolas Deguines, Alberto Pascual, and three anonymous reviewers who provided very helpful comments and suggestions in a previous version of this manuscript.
+We would also like to acknowledge the efforts of the editor Cédric Gaucherel, as well as those of Michael Lattorff, Nicolas Deguines, Alberto Pascual, Nico Blüthgen and six anonymous reviewers who provided very helpful comments and suggestions in a previous version of this manuscript.
 AM received funding from a Juan de la Cierva (IJCI-2014-22558) and Ikerbasque fellowships.
@@
 We thank Doñana’s Singular Scientific-Technical Infrastructure (ICTS-RBD) for access to the park.
+Research also supported by the Spanish State Research Agency through María de Maeztu Excellence Unit accreditation (MDM-2017-0714) and the Basque Government BERC Programme.
+AM received funding from an Ikerbasque Research Fellowship.
 
@@
 knitr::kable(list(Table1A, Table1B), caption = "**Table 1**.
-Results of GLMM showing the effect of simple visitation and network structure metrics on A) species-level fruit set and B) average number of seeds per fruit based on best model selected.
+Results of GLMM showing the association between simple visitation and network structure metrics and A) species-level fruit set and B) average number of seeds per fruit based on best model selected.
 Bold letters indicate variables with large effects.")
@@
 knitr::kable(list(Table2A, Table2B), caption = "**Table 2**.
-Results of GLM showing effect of simple visitation and network structure metrics on A) site-level average fruit set and B) site-level average number of seeds per fruit based on best model selected.
+Results of GLM showing associations between simple visitation and network structure metrics and A) site-level average fruit set and B) site-level average number of seeds per fruit based on best model selected.
 Bold letters indicate variables with large effects.")
@@
 **Figure 2**.
+Figure 2.
 Partial residual plots showing the effect of the single predictor which best explains the variability in species-level reproductive success.
-A) Shows the effect of plant species centrality on the fruit set of each of the plant species considered and B) shows the effect of plant niche overlap on the average number of seeds per fruit.
+A) shows the effect of plant species centrality on the fruit set of each of the plant species considered and B) shows the effect of plant niche overlap on its average number of seeds per fruit.
 Dots represent each of the individuals sampled for each species within each site.
@@
 
-**Figure 4.** Partial residual plots showing the effect of pollinator richness on site-level average A) fruit and B) seed weight. Dots represent values for each site (N=16 sites).
-
-**Figure 5.** Results of simulation evaluating the importance of niche complementarity in determining differences in equity in reproductive across communities harboring from one to six species.
+**Figure 4.** Results of simulation evaluating the importance of niche complementarity in determining differences in equity in reproductive across communities harboring from one to six species.
 Points represent average values across 1,000 simulated combinations.
@@
 
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=8}
+Figure4
+```
+**Figure 4.**
+
+\newpage
+
+#Supplementary material
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=13, fig.width=7}
+
+#######FIG S2 SAMPLING COMPLETENESS 
+FigureS2<-plot_grid( poll, plant, link, ncol = 1)
+FigureS2
+
+# save_plot("figures/FigureS1.tiff", figures1,
+#            base_height = 13, base_width = 7)
+```
+
+**Figure S2.** Accumulation curves of pollinator, plant and plant-pollinator link richness with increasing sampling effort up to 100% sample coverage.
+Solid lines and points indicate observed richness while dashed lines show expected richness at increasing sample size, (i.e., extrapolated).
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=8}
+
+FigureS3
+
+```
+**Figure S3.** Forest plots showing 95% confidence intervals for all coefficients included in species-level models.
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=8}
+
+FigureS4
+
+```
+**Figure S4.** Scatterplot showing the effect of the relative number of visits received by a focal plant on its reproductive success.
+Relationship is largely driven by one species with a particularly large value of relative visits and removing this point leads to no effect of visitation rate.
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=15, fig.width=8}
+
+FigureS5A
+FigureS5B
+FigureS5C
+
+```
+**Figure S5.** Forest plots showing 95% confidence intervals for all coefficients included in site-level models, A) fruit set, B) number of seeds per fruit and C) fruit and seed weight.
+
 ```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=3, fig.width=10}
@@
 #FIGURE 4
-Figure4
+FigureS6
 # 
@@
 ```
-**Figure 4**
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=8}
-Figure5
-```
-**Figure 5.**
-
-\newpage
-
-#Supplementary material
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=13, fig.width=7}
-
-#######FIG S2 SAMPLING COMPLETENESS 
-#FigureS2<-plot_grid( poll, plant, link, ncol = 1)
-FigureS2
-
-# save_plot("figures/FigureS1.tiff", figures1,
-#            base_height = 13, base_width = 7)
-```
-
-**Figure S2.** Accumulation curves of pollinator, plant and plant-pollinator link richness with increasing sampling effort up to 100% sample coverage.
-Solid lines and points indicate observed richness while dashed lines show expected richness at increasing sample size, (i.e., extrapolated).
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=8}
-
-FigureS3
-
-```
-**Figure S3.** Forest plots showing 95% confidence intervals for all coefficients included in species-level models.
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=15, fig.width=8}
-
-FigureS4A
-FigureS4B
-FigureS4C
-
-```
-**Figure S4.** Forest plots showing 95% confidence intervals for all coefficients included in site-level models, A) fruit set, B) number of seeds per fruit and C) fruit and seed weight.
+**Figure S6.** Partial residual plots showing the effect of pollinator richness on site-level average A) fruit and B) seed weight. Dots represent values for each site (N=16 sites).
 
@@
 
-FigureS5
-
-```
-
-**Figure S5.** Figure S5.
+FigureS7
+
+```
+
+**Figure S7.** Figure S7.
 Partial residual plots showing the effect of pollinator richness on site-level average A) fruit and B) seed weight.
@@
 
+Suppl2a<-ddply(dtrans, c("Site_ID", " Plant_gen_sp"), summarise, 
+                      tot.inds = length( Plant_gen_sp))
+
+Suppl2a<-Suppl2a[,1:2]
+colnames(Suppl2a)<-c("Site", "Plant species")
+
+kable(Suppl2a, caption = "TableS1A. List with all plant species present at each of the sites.")
+
+Suppl2b<-ddply(dtrans, c("Site_ID", " Pollinator_gen_sp "), summarise, 
+                      tot.inds = length( Pollinator_gen_sp ))
+Suppl2b<-Suppl2b[,1:2]
+colnames(Suppl2b)<-c("Site", "Pollinator species")
+
+kable(Suppl2b, caption = "TableS1B. List with all pollinator species present at each of the sites.")
+
+# pruebaA<-ddply(Suppl2a, c("Site_ID"), summarise, 
+#                tot.inds = length(Plant_gen_sp))  #get number of plant species per site included in network analyses
+# 
+# 
+# pruebaB<-ddply(Suppl2b, c("Site_ID"), summarise, 
+#               tot.inds = length(Pollinator_gen_sp))  #get number of pollinator species per site included in network analyses
+
 #calculate number of plant species per site, number of individuals per plant species and number of fruits per ind surveyed for repr succ
-
-f.inds<-ddply(f, c("Site_ID", "Plant.sp"), summarise, 
-                   tot.inds = length(Plant.sp)) #number of individuals per plant sps
-
-tableS1<-ddply(f.inds, c("Site_ID"), summarise, 
-                   tot.sps = length(Site_ID)) #number of plant sps per site
-
-colnames(tableS1)<-c("Site", "Number of plant species")
-
-kable(tableS1, caption = "Table S1. Number of species sampled at each site.")
 
@@
 
-tableS5<-round(summary(m1.seed.w)$coefficients$cond[,1:3], digits=2)
-rownames(tableS5)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
-kable(tableS5, caption="Table S5. Results of GLMM showing effect of simple visitation metrics on species-level average seed weight based on best model selected.")
-
-tableS6<-round(summary(m1.fruit.w)$coefficients$cond[,1:3], digits=2)
-rownames(tableS6)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
-kable(tableS6, caption="Table S6. Results of GLMM showing effect of simple visitation metrics on species-level average fruit weight based on best model selected.")
+#coefs.m2
+TableS5<-round(coefs.m2b[,1:3],digits=2)
+rownames(TableS5)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Centrality", "Plant niche overlap")
+
+kable(TableS5, caption="Table S5.
+Results of GLMM showing effect of simple visitation and network metrics on species-level fruit set based on best model selected as in Table 1, but removing one species point with a particularly large visitation rate which drives this relationship.")
+
 ```
@@
 
-tableS7A<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)
-rownames(tableS7)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
-
-kable(tableS7A, caption="Table S7.
+tableS6A<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)
+rownames(tableS7)<-c("(Intercept)", "Pollinator richness", "Relative number of visits")
+
+kable(tableS6A, caption="Table S6.
 Results of GLM showing effect of simple visitation metrics on A) site-level average fruit weight based on best model selected and B) the same analysis removing one site that has a particularly large pollinator richness value to test whether this point might be driving the relationship.")
@@
 
-tableS7B<-round(summary(m1.fruitw.net2)$coef[,1:3], digits=2)
-rownames(tableS7B)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
-
-kable(tableS7B, caption="Table S7.
+tableS6B<-round(summary(m1.fruitw.net2)$coef[,1:3], digits=2)
+rownames(tableS6B)<-c("(Intercept)", "Pollinator richness", "Relative number of visits")
+
+kable(tableS6B, caption="Table S6.
 Results of GLM showing effect of simple visitation metrics on A) site-level average fruit weight based on best model selected and B) the same analysis removing one site that has a particularly large pollinator richness value to test whether this point might be driving the relationship.")
@@
 #save table with results for paper
-tableS8A<-round(summary(m1.seedw.net)$coef[,1:3], digits=2)
-rownames(tableS8A) <-c("(Intercept)", "Pollinator richness", "Total number of visits")
-
-kable(tableS8A, caption="Results of GLM showing effect of simple visitation metrics on A) site-level average seed weight based on best model selected and B) the same analysis removing one site that has a particularly large pollinator richness value to test whether this point might be driving the relationship.")
+tableS7A<-round(summary(m1.seedw.net)$coef[,1:3], digits=2)
+rownames(tableS7A) <-c("(Intercept)", "Pollinator richness", "Relative number of visits")
+
+kable(tableS7A, caption="Table S7.
+Results of GLM showing effect of simple visitation metrics on A) site-level average seed weight based on best model selected and B) the same analysis removing one site that has a particularly large pollinator richness value to test whether this point might be driving the relationship.")
 ```
@@
 #save table with results for paper
-tableS8B<-round(summary(m1.seedw.net2)$coef[,1:3], digits=2)
-rownames(tableS8B) <-c("(Intercept)", "Pollinator richness", "Total number of visits")
-
-kable(tableS8B, caption="Results of GLM showing effect of simple visitation metrics on A) site-level average seed weight based on best model selected and B) the same analysis removing one site that has a particularly large pollinator richness value to test whether this point might be driving the relationship.")
+tableS7B<-round(summary(m1.seedw.net2)$coef[,1:3], digits=2)
+rownames(tableS8B) <-c("(Intercept)", "Pollinator richness", "Relative number of visits")
+
+kable(tableS7B, caption="Table S7.
+Results of GLM showing effect of simple visitation metrics on A) site-level average seed weight based on best model selected and B) the same analysis removing one site that has a particularly large pollinator richness value to test whether this point might be driving the relationship.")
 ```
@@
 
-kable(tableS9, caption="Table S9.
+kable(tableS8, caption="Table S8.
 Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a site based on best model selected (0.50 threshold).")
 
-kable(tableS10, caption="Table S10.
-Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a site based on best model selected (0.75 threshold).")
-
-kable(tableS11, caption="Table S11.
-Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a site based on best model selected (0.25 threshold).")
 ```

### 2020-03-15 Network_structure_and_function.Rmd
changes after ecol lett review round

@@
 However, research linking pollinator diversity to reproductive success has focused on pairwise plant-pollinator interactions, largely overlooking community-level dynamics.
-Here, we present one of the first single studies linking pollinator visitation to plant reproduction from a community-wide perspective using a well-replicated dataset encompassing 16 plant-pollinator networks and data on reproductive success for 19 plant species from Mediterranean shrub ecosystems.
+Here, we present one of the first empirical studies linking pollinator visitation to plant reproduction from a community-wide perspective using a well-replicated dataset encompassing 16 plant-pollinator networks and data on reproductive success for 19 plant species from Mediterranean shrub ecosystems.
 We find that statistical models including simple visitation metrics are sufficient to explain the variability observed.
-However, a mechanistic understanding of how pollinator diversity affects reproductive success require additional information on network structure.
+However, a mechanistic understanding of how pollinator diversity affects reproductive success requires additional information on network structure.
 Specifically, we find positive effects of increasing complementarity in the plant species visited by different pollinators on plant reproductive success.
@@
 
-Pollinators provide key services to plants by facilitating pollen flow between individuals.
+Pollinators provide key services to plants by facilitating pollen flow between individuals [@Garibaldi2013].
 Records of declining trends for some pollinator species in some regions ([@Potts2010; @I.2019]) have led researchers to focus on the functional impacts of these changes in pollinator diversity, especially on the consequences for plant reproductive success [@Biesmeijer2006].
 
-  Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain the differences observed.
+  Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain the differences observed (e.g., [@Bommarco2012]).
 Contrastingly, community-level analyses remain scarce [@Bennett2018].
-Yet plants and pollinators do not interact in isolation, but rather are embedded within larger networks of interactions encompassing other plant and pollinator species.
+Yet plants and pollinators do not interact in isolation, but rather are embedded within larger networks of interactions encompassing other plant and pollinator species [@Memmott2004a].
 We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect interactions between species within one guild (e.g., plants) through their shared resources [@Carvalheiro2014; @Lazaro2014; @Mayfield2017; @Pauw2013; @Johnson2019].
-Understanding how changes in pollinator diversity and interaction structure affect whole ecosystem functioning is thus a major challenge that requires attention.
-
-  The few pollination studies that have analysed the effects of changing pollinator diversity for reproductive success at the community level have done so using mainly experimental setups.
+Understanding how changes in pollinator diversity and interaction structure affect ecosystem functioning is thus a major challenge that requires attention.
+
+  The few pollination studies that have analyzed the effects of changing pollinator diversity for reproductive success at the community level have done so using mainly experimental setups.
 As an example, a study that experimentally recreated a plant community with 9 plant species and differing levels of pollinator diversity across different enclosures, found a positive effect of pollinator species diversity on seed set, but also an important effect of niche complementarity between pollinators, a measure of community structure [@Frund2013].
-This provides added information on the effects of biodiversity for ecosystem functioning, suggesting that not only the diversity of species present, but also the diversity of roles and ways in which a community is structured, are determinant factors.
+These findings show that not only the diversity of species present, but also the diversity of roles they play and the way in which a community is structured are determinant factors of ecosystem functions.
 
   Indeed, theoretical research has long suggested that the structure of multitrophic communities has an effect for ecosystem functioning (reviewed in [@Thompson2012]).
-This line of research, rooted in niche theory and revamped by food-web studies [@Godoy2018; @Macarthur1967; @May1972a; @Tilman1982], has greatly advanced theory, but the relationship between structure and function has seldom been tested using empirical data (but see [@Kaiser-Bunbury2017; @Poisot2013; @Saunders2019]).
-This line of research, rooted in niche theory and revamped by food-web studies  has greatly advanced theory, but these ideas have not yet been tested using empirical data  Specifically, a major knowledge gap resides in understanding which aspects of structure determine which aspects of function [@Thompson2012].
+This line of research, rooted in niche theory and revamped by food-web studies [@Godoy2018; @Macarthur1967; @May1972a; @Tilman1982], has greatly advanced theory, but the relationship between structure and function has seldom been tested using empirical data (but see [@Kaiser-Bunbury2017; @Poisot2013; @Lazaro2019]).
+Specifically, a major knowledge gap resides in understanding which aspects of structure determine which aspects of function [@Thompson2012].
 This is because although a network perspective has promised to encapsulate complex ecological mechanisms occurring at the community level – such as indirect interactions [@Abrams1998; @Holt1977] or niche overlap [@Woodward2002]- less attention has been given to the ways in which these mechanisms relate to observed ecosystem processes [@Bluthgen2010a].
-In contrast, we are now at a point in which there is considerable understanding on the attributes characterizing mutualistic interaction networks [@Bascompte2007a].
-Especially, in the case of pollination, we have ample knowledge on the attributes that shape these mutualistic interactions at the community level.
-Amongst them is the prevalence of nested structures, i.e., arrangements where specialist species interact with a subset of the species that generalists interact with [@Bascompte2003] and which is thought to promote species diversity [@Bastolla2009].
+In contrast, we are now at a point where we understand some of the emergent patterns characterizing mutualistic interaction networks at the community level, especially in the case of pollination [@Bascompte2007a].
+Amongst them is the prevalence of nested structures, i.e., arrangements where specialist species interact with a subset of the species that generalists interact with [@Bascompte2003].
 Further, plant-pollinator interaction networks seem to exhibit a relatively high extent of complementary specialization at the community scale, which may be directly related to key ecosystem functions [@Bluthgen2011].
 However, the mechanisms by which these attributes affect plant reproduction remain to be understood [@Winfree2013].
-The time is thus ripe to use the existing knowledge around plant-pollinator network structures to explore the relationship between network structure and ecosystem functioning empirically, with special emphasis on the underlying ecological mechanisms that drive these relationships.
-
-  Here, we present one of the first efforts linking pollinator visitation and plant reproductive success at the community level using empirical data on plant-pollinator interaction networks and plant reproductive success.
+The time is thus ripe to explore the relationship between community structure and ecosystem functioning empirically, with special emphasis on the underlying ecological mechanisms that drive these relationships.
+
+  Here, we present an empirical study linking pollinator visitation and plant reproductive success at the community level using empirical data on plant-pollinator interaction networks and plant reproductive success.
 To this end, we use a well-replicated dataset encompassing plant-pollinator interaction networks collected at 16 sites coupled with data on the reproductive success of 19 plant species recorded in Mediterranean shrub ecosystems.
@@
 Our study was conducted in SW Spain within the area of influence of Doñana National Park, i.e., within the limits of the Natural Space of Doñana as defined by the local government (Junta de Andalucía, Fig.
-1).
+S1).
 All 16 sites were located within similar elevations (ranging from 50 to 150 m a.s.l.), similar habitat and soil types, and presented similar plant composition (plant mean Sørensen beta-diversity among sites = `r round(d.betadiv, 2)`), reducing potential confounding factors.
@@
 All surveys were done under similar weather conditions, avoiding windy or rainy days, during mornings and afternoons with the sampling order being established randomly.
+Within each transect every 10 m we surveyed a 2x2 m quadrant where the number of flowers per species were counted, i.e., 10 quadrats per species and a 40m2 area surveyed.
 
@@
 the proportion of flowers that set fruit), the average number of seeds per fruit and the average fruit and seed weight per fruit (`r min(s.fruitnum$tot.fruits)`-`r max(s.fruitnum$tot.fruits)` fruits subsampled, mean $\pm$ SD: `r round(mean(s.fruitnum$tot.fruits), digits=2)` $\pm$ `r round(sd(s.fruitnum$tot.fruits), digits=2)`, Table S3).
-These variables show strong correlations (Pearson correlation= 0.89), we believe they provide complementary information.
+These last two variables show a strong correlation (Pearson correlation= 0.89), but we believe they provide complementary information.
 Our survey included a total of `r nlevels(f2$Plant.sp)` different totally or partially self-incompatible plant species that depend on pollinators to maximize their reproduction (Table S4) across our `r nlevels(f2$Site_ID)` sites.
 All plant species were shrubs selected to be common and widespread species, and individuals were selected depending on the presence of flowers during the sampling events.
-The values of reproductive success obtained at the species level were also averaged per site to calculate unique reproductive success measures at the site level in addition to species-level values..
+In addition to species-level values, we also calculated the average reproductive success at the site level.
+To that end, the values of reproductive success obtained at the species level were averaged per site.
 
@@
   In addition, we checked for potential spatial autocorrelation in our data by means of Mantel correlograms.
-Autocorrelation values were non-significant for all variables included in our analyses, except in the case of pollinator richness where we have a significant effect at small spatial scales (Fig.
-S1), and hence we treat each site as independent in our analysis.
+Autocorrelation values were non-significant for all variables included in our analyses, except in the case of pollinator richness where we have a small but significant effect at small spatial scales (Fig.
+S2), and hence we treat each site as independent in our analysis.
 
@@
 At the species level, we focused on attributes defining the position of a focal plant species within the larger community.
-As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap in terms of pollinators between a focal plant species and each of the other plant species in the community, which estimates the potential indirect interactions between different plant species through shared resources (in this case pollinators) and the potential for increased heterospecific pollen [@Arceo-Gomez2019], and (ii) centrality, which depicts the importance of the role played by a plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness.
+As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap in terms of pollinators between a focal plant species and each of the other plant species in the community, which estimates the potential indirect interactions between different plant species through shared resources (in this case pollinators) and the potential for increased heterospecific pollen deposition [@Arceo-Gomez2019], and (ii) centrality, which depicts the importance of the role played by a plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness.
  Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the Morisita overlap index, a measure of similarity between two sets of data [@Zhang2016].
@@
   Nestedness is the property by which specialists interact with a subset of the species that generalists interact with [@Bascompte2003].
-Although there is an ongoing debate in the literature (e.g., [@James2012]), some studies have found that nested networks are more stable and resilient to perturbations because nestedness promotes a greater diversity by minimizing competition among species in a community [@Bastolla2009].
+Although there is an ongoing debate in the literature (e.g., [@James2012]), some theoretical studies have found that nested networks are more stable and resilient to perturbations because nestedness promotes a greater diversity by minimizing competition among species in a community [@Bastolla2009].
 However, many network attributes vary with network size and complexity [@Bluthgen2006].
@@
 We thus followed the advice provided by Song et al.
-(2017) by using a normalized value of the widely-used nestedness metric NODF [@Almeida-Neto2011], $NODF_c$.
+(2017) by using a normalized value of the widely-used nestedness metric NODF based on binary matrices [@Almeida-Neto2011], $NODF_c$.
 This normalized value is calculated as $NODF_c = NODF_n/(C * log(S))$, where C is connectance and S is network size, calculated as $S = \sqrt(ncol(web)*nrow(web))$.
@@
 The number of seeds per fruit was centered and scaled (i.e., we subtracted column means and divided by standard deviation) to allow meaningful comparisons across species with contrasting life histories.
-As explanatory variables, model 1 included pollinator richness, and the relative number of visits received by each plant species, which is calculated as the total number of visits received by a plant species divided by the average number of flowers present in that species.
+As explanatory variables, model 1 included the number of pollinator species observed, and the visitation rate received by each plant species.
+Visitation rate was calculated as the total number of visits received by a plant species divided by the average number of flowers of that species found in 10 2x2 m quadrats located every 10 m along the transect.
 In turn, model 2 added the two network attributes calculated at the species level: average plant niche overlap and centrality.
@@
   Our sampling completeness analyses revealed that with our survey we were able to capture 17-54% of pollinator species (average = 35%), 43-100% for plant species (average = 80%) and 9-32% for plant-pollinator links (average = 20%), in line with that obtained with other studies (e.g., [@Chacoff2012], Fig.
-S2).
+S3).
 Our values of sampling completeness were slightly smaller in the case of pollinators, probably as a consequence of the great diversity found in the Mediterranean region and within our study area in particular, a hotspot of insect diversity [@Nieto2014].
@@
 At the species level, in the case of fruit set, our results showed that model 2 had the best fit to our data (lowest AIC value), and fixed  effects explained `r round(r2$Marginal[1], 2)*100`% of the variability observed (conditional R^2=`r round(r2$Conditional[1], 2)*100`%).
-In this case, we found a positive relationship between fruit set the relative number of visits, and a network structure metric, the centrality of a focal plant within the overall network (Table 1, Fig.
-2A, Fig.
-S3).
+In this case, we found a positive relationship between fruit set, visitation rate, and a network structure metric, the centrality of a focal plant within the overall network (Table 1, Fig.
+1A, Fig.
+S4).
 However, in the case of the relative number of visits a single point seemed to be driving the relationship and removing this single point lead to a decrease in the importance of this variable (Fig.
-S4, Table S5).
+S5, Table S5).
 
@@
 In this case, we found a positive relationship between plant niche overlap and the number of seeds produced (Table 1B, Fig.
-2B, Fig.
-S3).
+1B, Fig.
+S4).
 
@@
 In particular, we found that both fruit set and the number of seeds per fruit were positively related to niche complementarity between pollinators (Tables 2, Fig.
-3, Fig.
-S5).
+2, Fig.
+S6).
 Additionally, we found a negative association between site-level pollinator richness and average fruit set (Table 2A, Fig.
-3, Fig.
-S5).
+2, Fig.
+S6).
 
@@
   In the case of weight variables (fruit and seed weight), in both cases we found that both the null model, model 0 and model 1 were equally good (i.e.,$\Delta AIC<2$; [@Burnham2002a]).
-Following previous logic, given the both models were equally good despite the added complexity in model 1, we will only comment on this model.
 In this case model 1, i.e., that only including simple visitation metrics, showed an R^2  of  0.23.
@@
 In both cases, we found a consistent positive link to site-level pollinator richness (Tables S6A-S7A, Figs.
-S5-S6).
+S6-S7).
 This association was maintained even after removing a site that has a particularly large pollinator richness value (Tables S6B-S7B, Fig.
-S7, Fig.
-S5).
+S8, Fig.
+S6).
 
@@
 
-When evaluating the relationship between community composition and network structure on equity in reproductive success across the different species within a community, we found that using the 50^th percentile all models were equally good (i.e.,$\Delta AIC<2$; [@Burnham2002a]), and we will thus comment only model 2.
-Here, none of the variables considered showed any strong associations (Table S8).
+When evaluating the relationship between community composition and network structure on equity in reproductive success across the different species within a community, we found that using the 50^th percentile all models were equally good (i.e.,$\Delta AIC<2$; [@Burnham2002a]), but as seen in model 2, none of the variables considered showed any strong associations (Table S8).
 In the case of the other two thresholds considered (25^th and 75^th percentiles) model 0, the null model, was the best model.
@@
 
-  Within our simulation evaluating the relationship between niche complementarity and equity in reproductive success, we found that the link to complementarity became more important as more species were considered (Fig.
-4).
+  Within our simulation evaluating the relationship between niche complementarity and equity in reproductive success at increasing number of plant species considered, we found that the link to complementarity became more important as more species were considered (Fig.
+3).
 This importance seemed to reach a plateau at 6 species.
@@
 Our results suggest that different aspects of network structure affect different dimensions of ecosystem functioning.
-In particular, we find that the centrality of a plant species within a community has a positive association with its fruit set.
+In particular, we find that the centrality of a plant species within a community has a positive association with its fruit set, indicating that from a plant's perspective in this case, being connected to other plant species via shared pollinators has a positive outcome (e.g.
+by ensuring a stable pollinator supply through time) rather than a negative one (e.g.
+via heterospecific pollen transport).
 At the site level, we find that greater values of niche complementarity between pollinators result in larger average values of reproductive success.
@@
 However, our study is limited to a maximum of six common plant species per community, and including more species, especially rare species, might reveal different patterns.
+Further, although we sampled each site seven times in a randomized order in an attempt to better represent interactions through time, our surveys were able to capture ~20% of interactions given the great diversity of our study system.
+This could be explaining part of the low effect sizes we find at the species level, where a stronger contribution of pollinator visits is expected given their obligate dependence [@Garibaldi2013].
+In addition, it is important to note that plant reproductive success is affected by other environmental variables which we do not attempt to measure in this study and that could explain a large portion of the variability observed.
 
@@
 Indeed, we know that plant species diversity within a community is largely driven by different types of direct and indirect interactions including those amongst plant species (e.g., resource competition [@Goldberg1992] or facilitation [@Bruno2003]), as well as those defining antagonistic (e.g., involving pathogens [@Bagchi2010], or mutualistic interactions (e.g, pollinators [@Benadi2013; @Lanuza2018]).
-However, equitability in reproductive success across species is seldom taken into account, despite its importance in maintaining genetic diversity and ensuring the resilience of populations to further change.
+However, equitability in reproductive success across species is seldom taken into account, despite increasing theoretical and empirical support to the idea that minimizing fitness differences among species is an important mechanism of species coexistence [@Godoy2014].
 
@@
 Furthermore, the structure of plant-pollinators networks is dynamic due to ecological and evolutionary reasons, but so far, we are only able to characterize it for single snap-shots.
-Moreover, different aspects of functioning may be important, such as the presence of non-linear relationships or the need to consider the functioning of both trophic levels [@Godoy2018].
+Moreover, different aspects of functioning may be important, such as the need to consider the functioning of both trophic levels [@Godoy2018].
 In terms of plant reproductive success and the functions performed by pollinators we can measure different aspects, ranging from pollen deposition (the direct pollinator function), to its final effects on plant fitness.
@@
 
-**Figure 1.** Map showing location of 16 Mediterranean woodland patches where plant-pollinator interactions were surveyed from February to May 2015. Inset shows location of study area within SW Spain.
-
-**Figure 2**.
+**Figure 1**.
 Figure 2.
@@
 
-**Figure 3.** Partial residual plots showing the effect of the single predictor which best explains the variability in site-level reproductive success.
+**Figure 2.** Partial residual plots showing the effect of the single predictor which best explains the variability in site-level reproductive success.
 A) Shows the effect of pollinator richness, and B) of niche complementarity among pollinator species on site-level average fruit set.
@@
 
-**Figure 4.** Results of simulation evaluating the importance of niche complementarity in determining differences in equity in reproductive across communities harboring from one to six species.
+**Figure 3.** Results of simulation evaluating the importance of niche complementarity in determining differences in equity in reproductive across communities harboring from one to six species.
 Points represent average values across 1,000 simulated combinations.
@@
 \newpage
+
+\newpage
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=9, fig.width=9}
+
+#FIGURE 2
+Figure2
+
+   # save_plot("figures/Figure2.tiff", Figure2,
+   #           base_height = 6, base_width = 9)
+```
+**Figure 1**
+
+\newpage
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=3, fig.width=11}
+
+#FIGURE 3
+Figure3
+
+    # save_plot("figures/Figure3.tiff", Figure3,
+    #           base_height = 3, base_width = 11)
+```
+**Figure 2**
+
+\newpage
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=8}
+Figure4
+```
+**Figure 3.**
+
+\newpage
+
+#Supplementary material
 
@@
 ```
-**Figure 1**
-
-\newpage
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=9, fig.width=9}
-
-#FIGURE 2
-Figure2
-
-   # save_plot("figures/Figure2.tiff", Figure2,
-   #           base_height = 6, base_width = 9)
-```
-**Figure 2**
-
-\newpage
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=3, fig.width=11}
-
-#FIGURE 3
-Figure3
-
-    # save_plot("figures/Figure3.tiff", Figure3,
-    #           base_height = 3, base_width = 11)
-```
-**Figure 3**
-
-\newpage
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=8}
-Figure4
-```
-**Figure 4.**
-
-\newpage
-
-#Supplementary material
+**Figure S1.** Map showing location of 16 Mediterranean woodland patches where plant-pollinator interactions were surveyed from February to May 2015.
+Inset shows location of study area within SW Spain.
 
@@
 
-**Figure S2.** Accumulation curves of pollinator, plant and plant-pollinator link richness with increasing sampling effort up to 100% sample coverage.
+**Figure S3.** Accumulation curves of pollinator, plant and plant-pollinator link richness with increasing sampling effort up to 100% sample coverage.
 Solid lines and points indicate observed richness while dashed lines show expected richness at increasing sample size, (i.e., extrapolated).
@@
 ```
-**Figure S3.** Forest plots showing 95% confidence intervals for all coefficients included in species-level models.
+**Figure S4.** Forest plots showing 95% confidence intervals for all coefficients included in species-level models.
 
@@
 ```
-**Figure S4.** Scatterplot showing the effect of the relative number of visits received by a focal plant on its reproductive success.
+**Figure S5.** Scatterplot showing the effect of the relative number of visits received by a focal plant on its reproductive success.
 Relationship is largely driven by one species with a particularly large value of relative visits and removing this point leads to no effect of visitation rate.
@@
 ```
-**Figure S5.** Forest plots showing 95% confidence intervals for all coefficients included in site-level models, A) fruit set, B) number of seeds per fruit and C) fruit and seed weight.
+**Figure S6.** Forest plots showing 95% confidence intervals for all coefficients included in site-level models, A) fruit set, B) number of seeds per fruit and C) fruit and seed weight.
 
@@
 ```
-**Figure S6.** Partial residual plots showing the effect of pollinator richness on site-level average A) fruit and B) seed weight. Dots represent values for each site (N=16 sites).
+**Figure S7.** Partial residual plots showing the effect of pollinator richness on site-level average A) fruit and B) seed weight. Dots represent values for each site (N=16 sites).
 
@@
 
-**Figure S7.** Figure S7.
+**Figure S8.** Figure S7.
 Partial residual plots showing the effect of pollinator richness on site-level average A) fruit and B) seed weight.

### 2020-03-15 scripts/network analysis.R

@@ -13,15 +13,18 @@ library(nnet)
 
 d<-all_interactions
 
+dtrans<-subset(d, d$Out=="transect")
+dtrans<-droplevels(dtrans)
+
 ##1st create a bipartite matrix for each site MERGING ALL ROUNDS TOGETHER and extract a set of metrics at the network level
 
-sites <- unique(d$Site_ID)
+sites <- unique(dtrans$Site_ID)
 
 
 out.site <- data.frame(Site_id = NA,  
                        species.poll=NA, species.pl=NA, 
                        functional.comp.poll=NA, functional.comp.plant=NA, 
-                       nodf.song=NA)
+                       nodf.song=NA, nodf.song2=NA)
 
 outsp.site <- data.frame(Site_id = NA, species=NA,  norm_degree = NA,
                          weigh_closeness=NA, d=NA)
@@ -35,7 +38,7 @@ outsp.pl.site <- data.frame(Site_id = NA, species=NA,  norm_degree = NA,
 webs <- list()
 for(i in 1:length(sites)){
   print(i)
-  temp <- subset(d, Site_ID == sites[i])
+  temp <- subset(dtrans, Site_ID == sites[i])
   
   
 
@@ -50,10 +53,10 @@ for(i in 1:length(sites)){
   
   #remove all columns and rows with all values=0
   web3 <- web[, colSums(web != 0) > 0] 
-  web4 <- web3[rowSums(web3[, -1] > 0) != 0, ]
+  web4 <- web3[rowSums(web3 > 0) != 0, ]
   
    NODF <- nestedness_NODF(web4) # this calculates the raw value of NODF as in Song
-    if(i %in% c(6,15,16)){ #For sites wchich don't comply, use Song. Only three sites.
+    if(i %in% c(1,2,4, 5,6,7,8, 10,11,12,14, 15,16)){ #For sites wchich don't comply, use Song. 
       max_NODF <- max_nest(web4[,-1])
       combined_NODF <- comb_nest(web4[,-1],NODF,max_NODF) # this calculates the combined NODF statistic as described in the manuscript
     } else {
@@ -62,7 +65,10 @@ for(i in 1:length(sites)){
       combined_NODF <- comb_nest(web4,NODF,max_NODF$max_nodf) # this calculates the combined NODF statistic as described in the manuscript
     }
   
[…]

### 2020-03-16 Network_structure_and_function.Rmd
minor changes in figure numbering

@@
 
-The number of studies analyzing the structure of interactions shaping natural communities has increased, particularly regarding pollination.
+Our understanding of how the structure of species interactions shapes natural communities has increased, particularly regarding plant-pollinator interactions.
 However, research linking pollinator diversity to reproductive success has focused on pairwise plant-pollinator interactions, largely overlooking community-level dynamics.
@@
 Specifically, we find positive effects of increasing complementarity in the plant species visited by different pollinators on plant reproductive success.
-This shows that maintaining communities with a diversity of species but also of functions is paramount to preserving plant diversity.
+Hence, maintaining communities with a diversity of species but also of functions is paramount to preserving plant diversity.
 
@@
 All surveys were done under similar weather conditions, avoiding windy or rainy days, during mornings and afternoons with the sampling order being established randomly.
-Within each transect every 10 m we surveyed a 2x2 m quadrant where the number of flowers per species were counted, i.e., 10 quadrats per species and a 40m2 area surveyed.
+Within each transect every 10 m we surveyed a 2x2 m quadrant where the number of flowers per species were counted, i.e., 10 quadrats per transect which makes 40m2 of area surveyed overall.
 
@@
 As explanatory variables, model 1 included the number of pollinator species observed, and the visitation rate received by each plant species.
-Visitation rate was calculated as the total number of visits received by a plant species divided by the average number of flowers of that species found in 10 2x2 m quadrats located every 10 m along the transect.
+Visitation rate was calculated as the total number of visits received by a plant species divided by the average number of flowers of that species found in the 10 2x2 m quadrats located every 10 m along the transect.
 In turn, model 2 added the two network attributes calculated at the species level: average plant niche overlap and centrality.
@@
 
+FigureS2<-cowplot::plot_grid( poll, plant, link, ncol = 1)
+
 ```
@@
 
-m2<-glmer(tot.fruitset ~  pollspsperplant.sc  * rel.visits.sc + pollspsperplant.sc  *weigh_closeness.sc + pollspsperplant.sc  *niche.overlap.sc + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2, REML=TRUE)
+m2<-glmer(tot.fruitset ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2, REML=TRUE)
 
@@
 tableS8<-round(summary(m2.eq.comm)$coef[,1:3], digits=2)#ch
-rownames(tableS9)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Nestedness", "Pollinator niche complementarity")
+rownames(tableS8)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Nestedness", "Pollinator niche complementarity")
 
@@
 
- In the case of equity, we did not find a strong effect of either simple visitation or network structure metrics.
+ In our case , we did not find a strong effect of either simple visitation or network structure metrics on reproductive equity.
 However, the results of our simulation, shows us that the effect of network structure increases when more than four plant species are considered.
@@
 
-  One of the unexpected results of our analyses is the strong negative relationship between pollinator richness and fruit set at the site level.
+  One of the unexpected results of our analyses is the strong negative relationship between total pollinator richness and fruit set at the site level.
 One possible explanation for this is that greater richness means greater transfer of heterospecific pollen [@Arceo-Gomez2019].
@@
 #######FIG S2 SAMPLING COMPLETENESS 
-FigureS2<-plot_grid( poll, plant, link, ncol = 1)
+#FigureS2<-plot_grid( poll, plant, link, ncol = 1)
 FigureS2
@@
 tableS6A<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)
-rownames(tableS7)<-c("(Intercept)", "Pollinator richness", "Relative number of visits")
+rownames(tableS6A)<-c("(Intercept)", "Pollinator richness", "Relative number of visits")
 
@@
 tableS7B<-round(summary(m1.seedw.net2)$coef[,1:3], digits=2)
-rownames(tableS8B) <-c("(Intercept)", "Pollinator richness", "Relative number of visits")
+rownames(tableS7B) <-c("(Intercept)", "Pollinator richness", "Relative number of visits")
 

### 2020-03-16 Network_structure_and_function.Rmd
figure numbers

@@
 
-Words in Abstract: 170 words
-
-Words in main text (excluding abstract, acknowledgements, references, table and figure legends): 5,302
-
-Number of references: 60
-
-Number of figures, tables and text boxes: 7
+Words in Abstract: 147 words
+
+Words in main text (excluding abstract, acknowledgements, references, table and figure legends): 5,272
+
+Number of references: 67
+
+Number of figures, tables and text boxes: 5
 
@@
 Thus, we also calculated two network metrics providing complementary non-redundant information.
-In this case we focused on a metric that measures the redundancy in the plants visited by different pollinators, nestedness, and another one, not correlated with the previous one, measuring the complementarity in the plant species visited by the different pollinator species, pollinator niche complementarity
+In this case we focused on a metric that measures the redundancy in the plants visited by different pollinators, nestedness, and another one, not correlated with the previous one, measuring the complementarity in the plant species visited by the different pollinator species, pollinator niche complementarity.
 
@@
 To calculate max(NODF) we used a corrected version of the algorithm [@Simmons2019a] whenever possible.
-Results did not change qualitatively when using the uncorrected version of the algorithm for all sites.
+Results did not change qualitatively when using the uncorrected version of the algorithm for all sites as both are highly correlated (Spearman correlation = 0.94).
 
@@
 
-FigureS2<-cowplot::plot_grid( poll, plant, link, ncol = 1)
+FigureS3<-cowplot::plot_grid( poll, plant, link, ncol = 1)
 
@@
 
-Figure2a<-ggplot(m2@frame,  aes(x=m2@frame$weigh_closeness.sc, y=y_partial_weigh_inv, color= Plant.sp)) +    
+Figure1a<-ggplot(m2@frame,  aes(x=m2@frame$weigh_closeness.sc, y=y_partial_weigh_inv, color= Plant.sp)) +    
   geom_point(size=2.5, shape=21,color = "black", aes(fill=factor(Plant.sp))) + 
@@
 
-#Figure2a
+#Figure1a
 
@@
 
-FigureS4<-ggplot(m2@frame,  aes(x=m2@frame$rel.visits.sc, y=y_partial_weigh_inv, color= Plant.sp)) +
+FigureS5<-ggplot(m2@frame,  aes(x=m2@frame$rel.visits.sc, y=y_partial_weigh_inv, color= Plant.sp)) +
   geom_point(size=2.5, shape=21,color = "black", aes(fill=factor(Plant.sp))) +
@@
 
-Figure2b<-ggplot(m2.seed@frame,  aes(x=m2.seed@frame$niche.overlap.sc, y=y_partial_norm_seed, color= Plant.sp)) +    
+Figure1b<-ggplot(m2.seed@frame,  aes(x=m2.seed@frame$niche.overlap.sc, y=y_partial_norm_seed, color= Plant.sp)) +    
   geom_point(size=2.5, shape=21, colour="black", aes(fill=factor(Plant.sp))) + stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
@@
 
-#Figure2c
+#Figure1b
 
@@
 
-prow <- cowplot::plot_grid( Figure2a + theme(legend.position="none"),
-                   Figure2b + theme(legend.position="none"),
+prow <- cowplot::plot_grid( Figure1a + theme(legend.position="none"),
+                   Figure1b + theme(legend.position="none"),
                    align = 'vh',
@@
 # extract the legend from one of the plots
-legend_b <- get_legend(Figure2a + theme(legend.position="right"))
+legend_b <- get_legend(Figure1a + theme(legend.position="right"))
 
@@
 # of one plot (via rel_heights).
-Figure2 <- cowplot::plot_grid( prow, legend_b, ncol = 1, rel_heights = c(2, 1))#al final del paper
-
-FigureS3<-plot_summs(m2, m2.seed, level=0.95, scale = TRUE, model.names = c("Fruit set", "Number of seeds"), legend.title = "Response variables", cex.axis=2)
+Figure1 <- cowplot::plot_grid( prow, legend_b, ncol = 1, rel_heights = c(2, 1))#al final del paper
+
+FigureS4<-plot_summs(m2, m2.seed, level=0.95, scale = TRUE, model.names = c("Fruit set", "Number of seeds"), legend.title = "Response variables", cex.axis=2)
 
@@
 
-FigureS5A<-plot_model(m2.fruit.net, title="Fruit set")
+FigureS6A<-plot_model(m2.fruit.net, title="Fruit set")
 ```
@@
 
-Figure3<-cowplot::plot_grid(pl3, pl2, pl6, labels = c("A", "B", "C"), nrow=1)
-
-FigureS5B<-plot_model(m2.seed.net, title="Number of seeds")
+Figure2<-cowplot::plot_grid(pl3, pl2, pl6, labels = c("A", "B", "C"), nrow=1)
+
+FigureS6B<-plot_model(m2.seed.net, title="Number of seeds")
 ```
@@
 
-FigureS6<-cowplot::plot_grid(pltest, pltest2, labels = c("A", "B"), nrow=1)
+FigureS7<-cowplot::plot_grid(pltest, pltest2, labels = c("A", "B"), nrow=1)
 
@@
 
-FigureS7<-cowplot::plot_grid(pltestb, pltest2.sub, labels = c("A", "B"), nrow=1)
-
-FigureS5C<-plot_summs(m1.fruitw.net, m1.seedw.net, level=0.95, scale = TRUE, model.names = c("Fruit weight", "Seed weight"), legend.title = "Response variables")
+FigureS8<-cowplot::plot_grid(pltestb, pltest2.sub, labels = c("A", "B"), nrow=1)
+
+FigureS6C<-plot_summs(m1.fruitw.net, m1.seedw.net, level=0.95, scale = TRUE, model.names = c("Fruit weight", "Seed weight"), legend.title = "Response variables")
 
@@
 
-Figure4<-ggplot(estimate_i,  aes(x=level, y=estimate)) +    
+Figure3<-ggplot(estimate_i,  aes(x=level, y=estimate)) +    
   geom_point(size=4) + 
@@
 **Figure 1**.
-Figure 2.
 Partial residual plots showing the effect of the single predictor which best explains the variability in species-level reproductive success.
@@
 
+#FIGURE 1
+Figure1
+
+   # save_plot("figures/Figure2.tiff", Figure2,
+   #           base_height = 6, base_width = 9)
+```
+**Figure 1**
+
+\newpage
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=3, fig.width=11}
+
 #FIGURE 2
@@
 
-   # save_plot("figures/Figure2.tiff", Figure2,
-   #           base_height = 6, base_width = 9)
-```
-**Figure 1**
-
-\newpage
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=3, fig.width=11}
-
-#FIGURE 3
-Figure3
-
     # save_plot("figures/Figure3.tiff", Figure3,
@@
 ```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=8}
-Figure4
+Figure3
 ```
@@
 
-#FIGURE 1
+#FIGURE S1
 
@@
 ```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=13, fig.width=7}
+#Figure S2 is autocorrelation analysis
+
+library(BeeFunData)
+
+si<-BeeFunData::sites #lat long data for sites
+
+f.agg$lat<-si$latitude[match(f.agg$Site_ID, si$Site_ID)]
+f.agg$lon<-si$longitude[match(f.agg$Site_ID, si$Site_ID)]
+
+s.comm$lat<-si$latitude[match(s.comm$Site_ID, si$Site_ID)]
+s.comm$lon<-si$longitude[match(s.comm$Site_ID, si$Site_ID)]
+
+library(ecodist)
+
+#distance matrices
+xy <- cbind(as.vector(f.agg$lat), as.vector(f.agg$long))
+xydis <-distance(xy, method="euclidean")
+
+nesteddis<-distance(as.vector(f.agg$nodf.song), method="euclidean")
+functdis<-distance(as.vector(f.agg$functional.comp.poll), method="euclidean")
+richdis<-distance(as.vector(f.agg$species.poll), method="euclidean")
+fruitdis<-distance(as.vector(f.agg$mean.fruitset), method="euclidean")
+visdis<-distance(as.vector(f.agg$tot.visits), method="euclidean")
+seeddis<-distance(as.vector(s.comm$mean.seedset), method="euclidean")
+seedwdis<-distance(as.vector(s.comm$mean.seedweight), method="euclidean")
+fruitwdis<-distance(as.vector(s.comm$mean.fruitweight), method="euclidean")
+
+#correlograms
+Nestcor=mgram(nesteddis, xydis, nperm=10000, nboot=100, nclass=7)
+plot(Nestcor, main="Nestedness")
+
+Functcor=mgram(functdis, xydis, nperm=10000, nboot=100, nclass=7)
+plot(Functcor, main="Pollinator niche complementarity")
+
+Richcor=mgram(richdis, xydis, nperm=10000, nboot=100, nclass=7)
+plot(Richcor, main="Pollinator species richness")
+
+Viscor=mgram(visdis, xydis, nperm=10000, nboot=100, nclass=7)
+plot(Viscor, main="Total visits")
+
+Fruitcor=mgram(fruitdis, xydis, nperm=10000, nboot=100, nclass=7)
+plot(Fruitcor, main="Fruitset")
+
+Seedcor=mgram(seeddis, xydis, nperm=10000, nboot=100, nclass=7)
+plot(Seedcor, main="Seeds per fruit")
+
+Seedwcor=mgram(seedwdis, xydis, nperm=10000, nboot=100, nclass=7)
+plot(Seedwcor, main="Seed weight")
+
+Fruitwcor=mgram(fruitwdis, xydis, nperm=10000, nboot=100, nclass=7)
+plot(Fruitwcor, main="Fruit weight")
+
+par(mfrow=c(3,3))
+plot(Nestcor, main="Nestedness");plot(Functcor, main="Pollinator niche complementarity");
+plot(Richcor, main="Pollinator species richness");plot(Viscor, main="Total visits");
+plot(Fruitcor, main="Fruit set"); plot(Seedcor, main="Seeds per fruit"); plot(Seedwcor, main="Seed weight");
+plot(Fruitwcor, main="Fruit weight")
+
+```
+**Figure S2.**Mantel correlograms showing a low spatial autocorrelation for the different variables included in the analyses.
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=13, fig.width=7}
 
@@
 #FigureS2<-plot_grid( poll, plant, link, ncol = 1)
-FigureS2
+FigureS3
 
@@
 
-FigureS3
+FigureS4
 
@@
 
-FigureS4
+FigureS5
 
@@
 
-FigureS5A
-FigureS5B
-FigureS5C
+FigureS6A
+FigureS6B
+FigureS6C
 
@@
 #FIGURE 4
-FigureS6
+FigureS7
 # 
@@
 
-FigureS7
-
-```
-
-**Figure S8.** Figure S7.
-Partial residual plots showing the effect of pollinator richness on site-level average A) fruit and B) seed weight.
+FigureS8
+
+```
+
+**Figure S8.** Partial residual plots showing the effect of pollinator richness on site-level average A) fruit and B) seed weight.
 Here, a site with a particularly large pollinator richness value is removed to test whether it might be driving the significant relationship.

### 2020-03-16 Network_structure_and_function.Rmd
change in readme to include location of .csv files

@@
 s<-seedset
+flower_count<-flowers
 
@@
 Our survey included a total of `r nlevels(f2$Plant.sp)` different totally or partially self-incompatible plant species that depend on pollinators to maximize their reproduction (Table S4) across our `r nlevels(f2$Site_ID)` sites.
-All plant species were shrubs selected to be common and widespread species, and individuals were selected depending on the presence of flowers during the sampling events.
+All plant species were shrubs selected to be common and widespread species.
+Individuals were selected depending on the presence of flowers during the sampling events.
 In addition to species-level values, we also calculated the average reproductive success at the site level.
@@
 We thus followed the advice provided by Song et al.
-(2017) by using a normalized value of the widely-used nestedness metric NODF based on binary matrices [@Almeida-Neto2011], $NODF_c$.
+(2017) by using a normalized value of the widely used nestedness metric NODF based on binary matrices [@Almeida-Neto2011], $NODF_c$.
 This normalized value is calculated as $NODF_c = NODF_n/(C * log(S))$, where C is connectance and S is network size, calculated as $S = \sqrt(ncol(web)*nrow(web))$.
@@
 #calculate RELATIVE number of visits per plant sps
-flower_count<-read.csv("Flower_Count_BeeFun_2015.csv")  ###############CAMBIAR POR BASE DE DATOS EN BEEFUN!
 flower_count$Plant_gen_sps<-paste(flower_count$Plant.genus, flower_count$Plant.species)

### 2020-03-16 scripts/mantelcorrelograms.R

@@ -24,19 +24,6 @@ seeddis<-distance(as.vector(s.comm$mean.seedset), method="euclidean")
 seedwdis<-distance(as.vector(s.comm$mean.seedweight), method="euclidean")
 fruitwdis<-distance(as.vector(s.comm$mean.fruitweight), method="euclidean")
 
-#relationship among matrices
-Nested_dist <- mantel(xydis ~ nesteddis, nperm=1000)
-Funct_dist <- mantel(xydis ~ functdis, nperm=1000)
-Rich_dist <- mantel(richdis ~ xydis, nperm=1000)
-Vis_dist <- mantel(visdis ~ xydis, nperm=1000)
-Fruit_dist <- mantel(fruitdis ~ xydis, nperm=1000)
-Seed_dist <- mantel(seeddis ~ xydis, nperm=1000)
-Seedw_dist <- mantel(seedwdis ~ xydis, nperm=1000)
-Fruitw_dist <- mantel(fruitwdis ~ xydis, nperm=1000)
-
-Varmantel <- cbind(Nested_dist,Funct_dist, Rich_dist, Vis_dist, Fruit_dist, Seed_dist, Seedw_dist, Fruitw_dist)
-Varmantel
-
 
 #correlograms
 Nestcor=mgram(nesteddis, xydis, nperm=10000, nboot=100, nclass=7)

### 2020-03-17 Network_structure_and_function.Rmd
reducing number of words to 5,000

@@
 
-Words in main text (excluding abstract, acknowledgements, references, table and figure legends): 5,272
+Words in main text (excluding abstract, acknowledgements, references, table and figure legends): 4,997
 
@@
 
-Pollinators provide key services to plants by facilitating pollen flow between individuals [@Garibaldi2013].
-Records of declining trends for some pollinator species in some regions ([@Potts2010; @I.2019]) have led researchers to focus on the functional impacts of these changes in pollinator diversity, especially on the consequences for plant reproductive success [@Biesmeijer2006].
-
-  Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain the differences observed (e.g., [@Bommarco2012]).
+Pollinators provide key services to plants by facilitating pollen flow [@Garibaldi2013].
+Declining trends for some pollinator species in some regions ([@Potts2010; @I.2019]) have led researchers to focus on the functional impacts of these changes in pollinator diversity, especially for plant reproductive success [@Biesmeijer2006].
+
+  Many studies have evaluated reproductive success on individual plant species [@Albrecht2012; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species visiting a plant or the number of visits they perform) to explain the differences observed (e.g., [@Bommarco2012]).
 Contrastingly, community-level analyses remain scarce [@Bennett2018].
-Yet plants and pollinators do not interact in isolation, but rather are embedded within larger networks of interactions encompassing other plant and pollinator species [@Memmott2004a].
-We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect interactions between species within one guild (e.g., plants) through their shared resources [@Carvalheiro2014; @Lazaro2014; @Mayfield2017; @Pauw2013; @Johnson2019].
-Understanding how changes in pollinator diversity and interaction structure affect ecosystem functioning is thus a major challenge that requires attention.
-
-  The few pollination studies that have analyzed the effects of changing pollinator diversity for reproductive success at the community level have done so using mainly experimental setups.
-As an example, a study that experimentally recreated a plant community with 9 plant species and differing levels of pollinator diversity across different enclosures, found a positive effect of pollinator species diversity on seed set, but also an important effect of niche complementarity between pollinators, a measure of community structure [@Frund2013].
-These findings show that not only the diversity of species present, but also the diversity of roles they play and the way in which a community is structured are determinant factors of ecosystem functions.
+Yet plants and pollinators do not interact in isolation but are embedded within larger networks of interactions encompassing other plant and pollinator species [@Memmott2004a].
+We are thus missing an important part of the picture, including direct interactions between the whole ensemble of plants and pollinators, but also indirect ones between species within one guild (e.g., plants) through their shared resources [@Carvalheiro2014; @Lazaro2014; @Mayfield2017; @Pauw2013; @Johnson2019].
+Understanding how changes in pollinator diversity and community structure affect ecosystem functioning is thus a major challenge that requires attention.
+
+  The few studies that have analyzed the effects of pollinator diversity on reproductive success at the community level have mainly used experimental setups.
+As an example, a study that experimentally recreated a plant community with 9 plant species and differing levels of pollinator diversity, found a positive effect of pollinator species diversity on seed set, but also an important effect of niche complementarity between pollinators, a measure of community structure [@Frund2013].
+These findings show that not only the diversity of species present, but also the diversity of roles they play and thus the way in which a community is structured are determinant factors of ecosystem functions.
 
@@
 This is because although a network perspective has promised to encapsulate complex ecological mechanisms occurring at the community level – such as indirect interactions [@Abrams1998; @Holt1977] or niche overlap [@Woodward2002]- less attention has been given to the ways in which these mechanisms relate to observed ecosystem processes [@Bluthgen2010a].
-In contrast, we are now at a point where we understand some of the emergent patterns characterizing mutualistic interaction networks at the community level, especially in the case of pollination [@Bascompte2007a].
+We are now at a point where we understand some of the emergent patterns characterizing mutualistic interaction networks at the community level, especially in the case of pollination [@Bascompte2007a].
 Amongst them is the prevalence of nested structures, i.e., arrangements where specialist species interact with a subset of the species that generalists interact with [@Bascompte2003].
@@
 
-  Here, we present an empirical study linking pollinator visitation and plant reproductive success at the community level using empirical data on plant-pollinator interaction networks and plant reproductive success.
-To this end, we use a well-replicated dataset encompassing plant-pollinator interaction networks collected at 16 sites coupled with data on the reproductive success of 19 plant species recorded in Mediterranean shrub ecosystems.
+  Here, we present an empirical study linking pollinator visitation and plant reproductive success at the community level.
+We use a well-replicated dataset encompassing plant-pollinator interaction networks collected at 16 sites coupled with data on the reproductive success of 19 plant species recorded in Mediterranean shrub ecosystems.
 Our study focuses on understanding whether adding information on selected interaction network structure indices to previously used simple visitation metrics (e.g., the number and diversity of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success.
 In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the association between the position of a focal species within the larger network and its link to individual reproductive success, and (ii) at the site level, by evaluating how attributes that describe the whole site might affect average values of reproductive success for all species measured within one particular site.
-Specifically, our study focuses on how the interplay between the complementarity in plant species visited by different pollinators (i.e., the complementarity in the functions they perform) and the redundancy in this function relates to reproductive success.
+Specifically, our study focuses on how the interplay between the complementarity in plant species visited by different pollinators, and the redundancy in this function relate to reproductive success.
 Plant reproductive success requires of the delivery of conspecific pollen and thus of a certain degree of niche complementarity [@Bluthgen2011].
@@
 
-  Our results suggest that models including information on simple visitation metrics alone are good in explaining the variability observed in reproductive success.
-However, insights into the mechanisms through which differences in pollinator diversity translate into changes in reproductive success require additional information on network structure, notably information on the complementarity between the functions performed and the niches occupied by different pollinator species.
+  Our results suggest that models including information on simple visitation metrics alone are able to explain differences in reproductive success.
+However, a mechanistic understanding requires additional information on network structure, notably information on the complementarity between the niches occupied by different pollinator species.
 Specifically, we find a positive effect of increasing niche complementarity between pollinators on plant reproductive success.
@@
 
-Our study was conducted in SW Spain within the area of influence of Doñana National Park, i.e., within the limits of the Natural Space of Doñana as defined by the local government (Junta de Andalucía, Fig.
+Our study was conducted in SW Spain within the area of influence of Doñana National Park (Fig.
 S1).
-All 16 sites were located within similar elevations (ranging from 50 to 150 m a.s.l.), similar habitat and soil types, and presented similar plant composition (plant mean Sørensen beta-diversity among sites = `r round(d.betadiv, 2)`), reducing potential confounding factors.
-Here, we surveyed 16 Mediterranean woodland patches with an average distance of 7 km between them (min= 3 km, max= 46.5 km).
+Sites were located within similar elevations (ranging from 50 to 150 m a.s.l.), similar habitat and soil types, and presented similar plant composition (plant mean Sørensen beta-diversity among sites = `r round(d.betadiv, 2)`), reducing potential confounding factors.
+We surveyed 16 Mediterranean woodland patches with an average distance of 7 km between them (min= 3 km, max= 46.5 km).
 Each site was surveyed every two weeks for a total of 7 times during the flowering season of 2015 (from February to May) following a 100-m x 2 m transect for 30 mins.
-Along each transect, we identified all plant species and recorded all the floral visitors that landed on their flowers during each 30-min period.
+Along each transect, we identified all plant species and recorded all the floral visitors that landed on their flowers.
 Only floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FPM and another expert entomologist (see acknowledgements).
@@
 
-Within each site, we marked between 3 and `r max(f.inds$tot.inds)` individuals (mean $\pm$ SD: `r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`, Table S2) belonging to `r min(tableS1$tot.sps)` to `r max(tableS1$tot.sps)` plant species (mean $\pm$ SD:`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`, Table S2).
+Within each site, we marked 3-`r max(f.inds$tot.inds)` individuals (mean $\pm$ SD: `r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`) belonging to `r min(tableS1$tot.sps)`-`r max(tableS1$tot.sps)` plant species (mean $\pm$ SD:`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`, Table S2).
 For each individual, at the end of the season, we recorded fruit set (i.e.
 the proportion of flowers that set fruit), the average number of seeds per fruit and the average fruit and seed weight per fruit (`r min(s.fruitnum$tot.fruits)`-`r max(s.fruitnum$tot.fruits)` fruits subsampled, mean $\pm$ SD: `r round(mean(s.fruitnum$tot.fruits), digits=2)` $\pm$ `r round(sd(s.fruitnum$tot.fruits), digits=2)`, Table S3).
-These last two variables show a strong correlation (Pearson correlation= 0.89), but we believe they provide complementary information.
+These last two variables show a strong correlation (Pearson correlation= 0.89), and thus we only present results on fruit weight.
 Our survey included a total of `r nlevels(f2$Plant.sp)` different totally or partially self-incompatible plant species that depend on pollinators to maximize their reproduction (Table S4) across our `r nlevels(f2$Site_ID)` sites.
-All plant species were shrubs selected to be common and widespread species.
+All plant species were common and widespread shrubs.
 Individuals were selected depending on the presence of flowers during the sampling events.
-In addition to species-level values, we also calculated the average reproductive success at the site level.
-To that end, the values of reproductive success obtained at the species level were averaged per site.
+We also calculated the average reproductive success at the site level by averaging values of reproductive success obtained at the species level.
 
@@
 
-In order to evaluate the completeness of our sampling, we estimated the asymptotic number of species of plants, pollinators and interactions present [@Chao2009], a non-parametric estimator of species richness for abundance data.
-This estimator includes non-detected species and allowed us to calculate the proportion detected with our original sampling data.
+To evaluate the sampling completeness, we estimated the asymptotic number of species of plants, pollinators and interactions present [@Chao2009], a non-parametric estimator of species richness for abundance data.
+This estimator includes non-detected species and allowed us to calculate the proportion detected with our original data.
 We used Chao 1 asymptotic species richness estimators [@Chao2009] and estimated the richness of pollinators, plants and plant–pollinator links accumulated as sampling effort increased up to 100% sampling coverage using package iNEXT [@Hsieh2016] within the R environment [@RDevelopmentCoreTeam2011].
@@
 
-  In order to analyse how differences in network structure between communities might affect plant reproductive success, we constructed quantitative plant-pollinator interaction networks by pooling the data for the 7 rounds of sampling.
+  To evaluate differences in network structure between communities, we constructed quantitative plant-pollinator interaction networks by pooling the data for the 7 rounds of sampling.
 We thus obtained one interaction network per site, representing the number of individuals of different pollinator species recorded visiting each different plant species.
-For each network, we then extracted a series of relevant network metrics at the species and site levels.
-
-  In addition, we checked for potential spatial autocorrelation in our data by means of Mantel correlograms.
-Autocorrelation values were non-significant for all variables included in our analyses, except in the case of pollinator richness where we have a small but significant effect at small spatial scales (Fig.
-S2), and hence we treat each site as independent in our analysis.
+For each network, we extracted a series of relevant network metrics at the species and site levels.
+
+  Additionally, we checked for spatial autocorrelation in our data using Mantel correlograms.
+Autocorrelation values were non-significant for all variables, except for pollinator richness where we have a small but significant effect at small spatial scales (Fig.
+S2).
+Hence, we treat each site as independent in our analysis.
 
@@
 At the species level, we focused on attributes defining the position of a focal plant species within the larger community.
-As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap in terms of pollinators between a focal plant species and each of the other plant species in the community, which estimates the potential indirect interactions between different plant species through shared resources (in this case pollinators) and the potential for increased heterospecific pollen deposition [@Arceo-Gomez2019], and (ii) centrality, which depicts the importance of the role played by a plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness.
+As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap in terms of pollinators between a focal plant species and each of the other plant species in the community, which estimates the potential indirect interactions between plant species through shared resources (in this case pollinators) and the potential for increased heterospecific pollen deposition [@Arceo-Gomez2019], and (ii) centrality, which depicts the importance of the role played by a plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness.
  Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the Morisita overlap index, a measure of similarity between two sets of data [@Zhang2016].
@@
 At the site level, we followed the same logic as the one presented at the species level.
-Thus, we also calculated two network metrics providing complementary non-redundant information.
-In this case we focused on a metric that measures the redundancy in the plants visited by different pollinators, nestedness, and another one, not correlated with the previous one, measuring the complementarity in the plant species visited by the different pollinator species, pollinator niche complementarity.
+We also calculated two network metrics providing complementary non-redundant information.
+In this case, we focused on nestedness, a measure of the redundancy in the plants visited by different pollinators, and pollinator niche complementarity, a measure of the complementarity in plant species visited by different pollinator species.
 
@@
 In the case of nestedness, we know it can be affected by network size and connectance [@Song2017a].
-An approach that is often used to correct for this, is to use null models and to compare null-model corrected nestedness values across different networks.
-However, this approach has been shown to present the same issues, as z-scores also change with network size and connectance [@Song2017a].
-We thus followed the advice provided by Song et al.
-(2017) by using a normalized value of the widely used nestedness metric NODF based on binary matrices [@Almeida-Neto2011], $NODF_c$.
+An approach that is often used to correct for this are null models, comparing null-model corrected nestedness values across different networks.
+However, this approach presents the same issues, as z-scores also change with network size and connectance [@Song2017a].
+We thus used a normalized value of the widely used nestedness metric NODF based on binary matrices [@Almeida-Neto2011], $NODF_c$ [@Song2017a].
 This normalized value is calculated as $NODF_c = NODF_n/(C * log(S))$, where C is connectance and S is network size, calculated as $S = \sqrt(ncol(web)*nrow(web))$.
@@
 To evaluate whether adding information on network structure improves our ability to explain differences in reproductive success - both at the species and the site level - we used generalized linear (GLMs) and generalized linear mixed models (GLMMs) respectively.
-In both cases (species and site-level models) we fit three types of models: (i) model 0, a null model with no explanatory variables,(ii) model 1, that only included simple visitation metrics and (iii) model 2 that additionally included information on network structure.
+In both cases we fit three types of models: (i) model 0, a null model with no explanatory variables,(ii) model 1, that only included simple visitation metrics and (iii) model 2 that additionally included information on network structure.
 These models are meant to be additive, so that the network metrics included are intended to complement rather than substitute the simple metrics traditionally used.
 
-At the species level, response variables included fruit set analyzed using a binomial distribution and the average number of seeds per fruit, the average fruit and seed weight fitted using normal distributions.
+At the species level, response variables included fruit set analyzed using a binomial distribution and the average number of seeds per fruit, and the average fruit weight fitted using normal distributions.
 The number of seeds per fruit was centered and scaled (i.e., we subtracted column means and divided by standard deviation) to allow meaningful comparisons across species with contrasting life histories.
 As explanatory variables, model 1 included the number of pollinator species observed, and the visitation rate received by each plant species.
-Visitation rate was calculated as the total number of visits received by a plant species divided by the average number of flowers of that species found in the 10 2x2 m quadrats located every 10 m along the transect.
+Visitation rate was calculated as the total number of visits received by a plant species divided by the average number of flowers of that species found in the 10 2x2 m quadrats per transect.
 In turn, model 2 added the two network attributes calculated at the species level: average plant niche overlap and centrality.
-For both models, we included plant species identity nested within site and site as random effects to account for the fact that several individuals of the same plant species were measured at each site.
-
-	At the site level, response variables were the average reproductive success of all plants surveyed within a site (i.e., average fruit set analyzed using a binomial distribution, average number of seeds per fruit and average fruit and seed weight using a normal distribution).
+For both models, we included plant species identity nested within site and site as random effects to account for multiple individuals of the same plant species measured at each site.
+
+	At the site level, response variables were the average reproductive success of all plants surveyed within a site (i.e., average fruit set analyzed using a binomial distribution, average number of seeds per fruit and average fruit weight using a normal distribution).
 We thus had a single value per site and no random effects are needed.
-In this case, model 1 included total pollinator richness and total pollinator abundance (i.e.
+Here, model 1 included total pollinator richness and total pollinator abundance (i.e.
 number of visits received by all plants within the community) as explanatory variables.
@@
 
-  Average values of reproductive success at the site level can be driven to a large extent by a single plant species.
+  Average values of reproductive success at the site level can be driven by a single plant species.
 Yet, what will determine the persistence of a diverse plant community, is the presence of some sort of “equity” or evenness in reproductive success across the whole community.
@@
 As any selected threshold is arbitrary, we repeated this using the 25^th and 75^th percentile thresholds [@Byrnes2014].
-We then used the same framework as that used for species and site-level analyses and fit the same models 0, 1 and 2 GLMs using equity in reproductive success as response variable and fitting a binomial distribution.
+We then used the same framework as that used for species and site-level analyses and fit the same models 0, 1 and 2 using equity in reproductive success as response variable and fitting a binomial distribution.
 
@@
 Additionally, we ran residual diagnostics to check if model assumptions were met and used the Akaike Information Criterion (AIC) to compare model performance and complexity.
-Whenever the difference between the AIC of the models was < 2 ($\Delta AIC<2$), we considered that all models were equally good [@Burnham2011].
+Whenever the difference between the AIC of the models was < 2 ($\Delta AIC<2$), we considered all models equally good [@Burnham2011].
 In the case of mixed models, for comparison, models were fitted by maximum likelihood and then the best model was refitted using restricted maximum likelihood.
@@
 Instead of drawing plant species randomly for each step, we tested all possible combinations for each plant number level and network, as the number of combinations is small (e.g.
-for n = 3 plant selected out of 6 there is only 20 possible combinations).
+for n = 3 plants selected out of 6 there are only 20 possible combinations).
 Then, we tested if the relationship between equity in reproductive success and niche complementarity (given its importance in determining differences in reproductive success, see Results section) changes as a function of the number of plants considered within our simulated communities.
@@
 
-  Our sampling completeness analyses revealed that with our survey we were able to capture 17-54% of pollinator species (average = 35%), 43-100% for plant species (average = 80%) and 9-32% for plant-pollinator links (average = 20%), in line with that obtained with other studies (e.g., [@Chacoff2012], Fig.
+  Our sampling completeness analyses revealed that our survey was able to capture 17-54% of pollinator species (average = 35%), 43-100% of plant species (average = 80%) and 9-32% of plant-pollinator links (average = 20%), in line with that obtained with other studies (e.g., [@Chacoff2012], Fig.
 S3).
@@
 At the species level, in the case of fruit set, our results showed that model 2 had the best fit to our data (lowest AIC value), and fixed  effects explained `r round(r2$Marginal[1], 2)*100`% of the variability observed (conditional R^2=`r round(r2$Conditional[1], 2)*100`%).
-In this case, we found a positive relationship between fruit set, visitation rate, and a network structure metric, the centrality of a focal plant within the overall network (Table 1, Fig.
+We found a positive relationship between fruit set, visitation rate, and a network structure metric, the centrality of a focal plant within the overall network (Table 1, Fig.
 1A, Fig.
@@
 ```
- For all other measures of reproductive success considered (i.e., fruit and seed weight), none of the models fitted showed a better fit than the null model.
+ For fruit weight, none of the models fitted showed a better fit than the null model.
 
@@
 
-At the site level, in the case of fruit set and the number of seeds per fruit, we found that both model 1 and 2 were equally good in describing the differences observed when penalizing for model complexity (i.e.,$\Delta AIC<2$; [@Burnham2002a]).
+At the site level, in the case of fruit set and the number of seeds per fruit, we found that both model 1 and 2 were equally good when penalizing for model complexity (i.e.,$\Delta AIC<2$; [@Burnham2002a]).
 This suggests model 2 was a good model despite its added complexity, and actually shows a substantially better predictive ability than model 1 (R^2 = `r round(r2.m2, 2)` for model 2 versus `r round(r2.m1, 2)` for model 1 in the case of fruit set and R^2 = `r round(r2.m2.seed,2)` for model 2 versus `r round(r2.m1.seed, 2)` for model 1 in the case of the number of seeds per fruit) and therefore we will comment results for this model only.
-In particular, we found that both fruit set and the number of seeds per fruit were positively related to niche complementarity between pollinators (Tables 2, Fig.
+Specifically, we found that both fruit set and the number of seeds per fruit were positively related to niche complementarity between pollinators (Tables 2, Fig.
 2, Fig.
@@
 
-pltest <- ggplot(s.comm,  aes(x=species.poll.sc, y= restest)) +    
+FigureS7 <- ggplot(s.comm,  aes(x=species.poll.sc, y= restest)) +    
   geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
@@
 
-pltestb <- ggplot(s.comm2,  aes(x=species.poll.sc, y= restestb)) +    
+FigureS8 <- ggplot(s.comm2,  aes(x=species.poll.sc, y= restestb)) +    
   geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
@@
 #confint(m1.seedw.net)
-
-#save table with results for paper
-tableS7A<-round(summary(m1.seedw.net)$coef[,1:3], digits=2)#ch
-rownames(tableS7A) <-c("(Intercept)", "Pollinator species diversity", "Relative number of visits")#end of paper
 
@@
 
-FigureS7<-cowplot::plot_grid(pltest, pltest2, labels = c("A", "B"), nrow=1)
-
 #Repeat analyses but removing one site that has a particularly large pollinator richness value to test whether this point might be driving the relationship by itself.
@@
 AICtab(m0.seedw.net2, m1.seedw.net2, m2.seedw.net2) #m1 is better
-
-#save table with results for paper
-tableS7B<-round(summary(m1.seedw.net2)$coef[,1:3], digits=2)#ch
-rownames(tableS7B) <-c("(Intercept)", "Pollinator species diversity", "Relative number of visits")#end of paper
 
@@
 
-FigureS8<-cowplot::plot_grid(pltestb, pltest2.sub, labels = c("A", "B"), nrow=1)
-
-FigureS6C<-plot_summs(m1.fruitw.net, m1.seedw.net, level=0.95, scale = TRUE, model.names = c("Fruit weight", "Seed weight"), legend.title = "Response variables")
+FigureS6C<-plot_model(m1.fruitw.net, title="Fruit weight")
 
@@
 
-  In the case of weight variables (fruit and seed weight), in both cases we found that both the null model, model 0 and model 1 were equally good (i.e.,$\Delta AIC<2$; [@Burnham2002a]).
-In this case model 1, i.e., that only including simple visitation metrics, showed an R^2  of  0.23.
-For seed weight, we found model 1 to be the best model too (R^2 = 0.39 in this case).
-In both cases, we found a consistent positive link to site-level pollinator richness (Tables S6A-S7A, Figs.
+  In the case of fruit weight, we found that both the null model and model 1 were equally good (i.e.,$\Delta AIC<2$; [@Burnham2002a]).
+Model 1, i.e., that only including simple visitation metrics, showed an R^2  of  0.23.
+In this case, we found a positive link with site-level pollinator richness (Table S6A, Figs.
 S6-S7).
-This association was maintained even after removing a site that has a particularly large pollinator richness value (Tables S6B-S7B, Fig.
+This association was maintained even after removing a site that has a particularly large pollinator richness value (Table S6B, Fig.
 S8, Fig.
@@
 
-When evaluating the relationship between community composition and network structure on equity in reproductive success across the different species within a community, we found that using the 50^th percentile all models were equally good (i.e.,$\Delta AIC<2$; [@Burnham2002a]), but as seen in model 2, none of the variables considered showed any strong associations (Table S8).
+When evaluating the relationship between community composition and network structure on equity in reproductive success across the different species within a community, we found that using the 50^th percentile all models were equally good (i.e.,$\Delta AIC<2$; [@Burnham2002a]), but none of the variables considered showed any strong associations (Table S8).
 In the case of the other two thresholds considered (25^th and 75^th percentiles) model 0, the null model, was the best model.
@@
 #save table with results for paper
-tableS8<-round(summary(m2.eq.comm)$coef[,1:3], digits=2)#ch
-rownames(tableS8)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Nestedness", "Pollinator niche complementarity")
+tableS7<-round(summary(m2.eq.comm)$coef[,1:3], digits=2)#ch
+rownames(tableS7)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Nestedness", "Pollinator niche complementarity")
 
@@
 Our results suggest that different aspects of network structure affect different dimensions of ecosystem functioning.
-In particular, we find that the centrality of a plant species within a community has a positive association with its fruit set, indicating that from a plant's perspective in this case, being connected to other plant species via shared pollinators has a positive outcome (e.g.
+Specifically, we find that the centrality of a plant species within a community has a positive association with its fruit set, indicating that from a plant's perspective, being connected to other plant species via shared pollinators has a positive outcome (e.g.
 by ensuring a stable pollinator supply through time) rather than a negative one (e.g.
@@
 
- Most of our analyses reveal that both model 1 and 2 were equally good, which suggests that the added complexity of measuring the full network of interactions may not pay off for rapid assessments.
+ Most of our analyses reveal that model 1 and 2 were equally good, which suggests that the added complexity of measuring the full network of interactions may not pay off for rapid assessments.
 Hence, simple visitation metrics, such as pollinator richness, might be enough to describe general patterns [@Garibaldi2013; @Garibaldi2015].
@@
 
-  In our study, we did not find a relationship between nestedness and any of the reproductive success measures.
-This metric, widely used across network analysis, and which is deemed to stabilize natural communities ([@Bastolla2009] but see [@James2012]), does not seem to play a direct role in ecosystem function measured as plant reproductive success.
+  We did not find a relationship between nestedness and any of the reproductive success measures.
+This metric, widely used across network analysis, does not seem to play a direct role on plant reproductive success.
 However, our study is limited to a maximum of six common plant species per community, and including more species, especially rare species, might reveal different patterns.
@@
 
-  Our measure of reproductive success at the site level using average values of fruit or seed set represents an important part of the functions delivered by pollinators to plants.
-However, these average values might be masking a great deal of variability amongst plant species, and thus a nuanced view of the effect of pollinators on whole-plant ensembles is needed.
+  Our measure of reproductive success at the site level using average values represents an important part of the functions delivered by pollinators to plants.
+However, average values might mask a great deal of variability amongst plant species, and thus a nuanced view of the effect of pollinators on whole-plant ensembles is needed.
 This can be captured by the effect of pollinators on equity in reproductive success across plant species.
@@
 These ideas open the door to exploring the positive or negative effects of the complete pollinator community on full plant species coexistence, which may be determined by density-dependence effects [@Benadi2018].
-In our case, while fruit set is negatively related to pollinator richness, it is important to note that fruit and seed weight show the opposite relationship, indicating that this density-dependent effect might only be limiting fruit quantity and not fruit quality.
+In our case, while fruit set is negatively related to pollinator richness, it is important to note that fruit weight shows the opposite relationship, indicating that this density-dependent effect might only be limiting fruit quantity and not fruit quality.
 Thus, taking into account the densities of co-flowering plant species may be the next step [@Vanbergen2014].
@@
 ```
-**Figure S7.** Partial residual plots showing the effect of pollinator richness on site-level average A) fruit and B) seed weight. Dots represent values for each site (N=16 sites).
+**Figure S7.** Partial residual plots showing the effect of pollinator richness on site-level average fruit weight. Dots represent values for each site (N=16 sites).
 
@@
 
-**Figure S8.** Partial residual plots showing the effect of pollinator richness on site-level average A) fruit and B) seed weight.
+**Figure S8.** Partial residual plots showing the effect of pollinator richness on site-level average fruit weight.
 Here, a site with a particularly large pollinator richness value is removed to test whether it might be driving the significant relationship.
@@
 ```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
-#save table with results for paper
-tableS7A<-round(summary(m1.seedw.net)$coef[,1:3], digits=2)
-rownames(tableS7A) <-c("(Intercept)", "Pollinator richness", "Relative number of visits")
-
-kable(tableS7A, caption="Table S7.
-Results of GLM showing effect of simple visitation metrics on A) site-level average seed weight based on best model selected and B) the same analysis removing one site that has a particularly large pollinator richness value to test whether this point might be driving the relationship.")
-```
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
-#save table with results for paper
-tableS7B<-round(summary(m1.seedw.net2)$coef[,1:3], digits=2)
-rownames(tableS7B) <-c("(Intercept)", "Pollinator richness", "Relative number of visits")
-
-kable(tableS7B, caption="Table S7.
-Results of GLM showing effect of simple visitation metrics on A) site-level average seed weight based on best model selected and B) the same analysis removing one site that has a particularly large pollinator richness value to test whether this point might be driving the relationship.")
-```
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
-
-kable(tableS8, caption="Table S8.
+
+kable(tableS7, caption="Table S7.
 Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a site based on best model selected (0.50 threshold).")

### 2020-04-28 Network_structure_and_function_PRUEBAS.Rmd
changes in scripts following latest comments from ECOl lett

--- 2020-03-17 Network_structure_and_function.Rmd
@@
 However, research linking pollinator diversity to reproductive success has focused on pairwise plant-pollinator interactions, largely overlooking community-level dynamics.
-Here, we present one of the first empirical studies linking pollinator visitation to plant reproduction from a community-wide perspective using a well-replicated dataset encompassing 16 plant-pollinator networks and data on reproductive success for 19 plant species from Mediterranean shrub ecosystems.
+Here, we present one of the first empirical studies linking pollinator visitation to plant reproduction from a community-wide perspective.
+We use a well-replicated dataset encompassing 16 plant-pollinator networks and data on reproductive success for 19 plant species from Mediterranean shrub ecosystems.
 We find that statistical models including simple visitation metrics are sufficient to explain the variability observed.
@@
 Individuals were selected depending on the presence of flowers during the sampling events.
-We also calculated the average reproductive success at the site level by averaging values of reproductive success obtained at the species level.
+We also calculated the average reproductive success at the site level by averaging values of reproductive success obtained for each species.
 
@@
 
-f2$norm_degree<-outsp.pl.site$norm_degree[match(f2$match, outsp.pl.site$match)]
-f2$weigh_closeness<-outsp.pl.site$weigh_closeness[match(f2$match, outsp.pl.site$match)]
+f2$nested_contribution<-outsp.pl.site$nested_contribution[match(f2$match, outsp.pl.site$match)]
 
@@
 
-f2$weigh_closeness.sc<-scale(f2$weigh_closeness, center = T, scale = T)
 f2$niche.overlap.sc<-scale(f2$niche.overlap, center = T, scale = T)
+f2$nested_contribution.sc<-scale(f2$nested_contribution, center = T, scale = T)
 f2$pollspsperplant.sc<-scale(f2$pollspsperplant, center = T, scale = T)
@@
 
-m0<-glmer(tot.fruitset ~ 1 + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2, REML=FALSE)
+f2.na<-na.omit(f2[, c(1,13:14,27:29,36)]) #omit nas so analyses are done with exact same dataset
+
+m0<-glmer(tot.fruitset ~ 1 + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2.na, REML=FALSE)
 summary(m0)
 
-m1<-glmer(tot.fruitset ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2, REML=FALSE)
+m1<-glmer(tot.fruitset ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2.na, REML=FALSE)
 summary(m1)
@@
 
-m2<-glmer(tot.fruitset ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2, REML=FALSE)
+m2<-glmer(tot.fruitset ~ niche.overlap.sc  + rel.visits.sc +nested_contribution.sc +  pollspsperplant.sc  +  (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2.na, REML=FALSE)
 
@@
 
+stats::anova(m0,m1,m2)
+
 #best model fit with REML=TRUE
 
-m2<-glmer(tot.fruitset ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2, REML=TRUE)
-
+m2<-glmer(tot.fruitset ~   nested_contribution.sc + niche.overlap.sc  + pollspsperplant.sc  + rel.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2.na, REML=TRUE)
 summary(m2)
 
-r2<-rsquared(c(m2, m1)) #check R^2 values for both models
+r2<-rsquared(c(m1, m2)) #check R^2 values for both models
 
@@
 Table1A<-round(coefs.m2[,1:3],digits=2)
-rownames(Table1A)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Centrality", "Plant niche overlap")
+rownames(Table1A)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Contribution to nestedness", "Plant niche overlap")
 #at the end of the paper
@@
 
-y_partial_weigh <- remef(m2, fix= c( "rel.visits.sc", "pollspsperplant.sc", "niche.overlap.sc"), ran = "all", inverse = F)
+y_partial_weigh <- remef(m2, fix= c("pollspsperplant.sc", "rel.visits.sc", "niche.overlap.sc"), ran = "all", inverse = F)
 #With this we remove the influece of x2 and the random effects from the dependent variable
@@
 
-Figure1a<-ggplot(m2@frame,  aes(x=m2@frame$weigh_closeness.sc, y=y_partial_weigh_inv, color= Plant.sp)) +    
+Figure1a<-ggplot(m2@frame,  aes(x=m2@frame$nested_contribution.sc, y=y_partial_weigh_inv, color= Plant.sp)) +    
   geom_point(size=2.5, shape=21,color = "black", aes(fill=factor(Plant.sp))) + 
   stat_smooth(method=glm,  method.args = list(family = "binomial"), size=1, se=TRUE, color = "black", alpha=0.4) + 
-  xlab("Centrality") +      
+  xlab("Contribution to nestedness") +      
   ylab("Fruit set") + theme_bw()  + theme (legend.position= "bottom") +
@@
 
-y_partial_weigh2 <- remef(m2, fix= c( "weigh_closeness.sc", "pollspsperplant.sc", "niche.overlap.sc"), ran = "all", inverse = F)
+ y_partial_weigh2 <- remef(m2, fix= c("niche.overlap.sc", "rel.visits.sc", "nested_contribution.sc"), ran = "all", inverse = F)
  #With this we remove the influece of x2 and the random effects from the dependent variable
@@
 
-FigureS5<-ggplot(m2@frame,  aes(x=m2@frame$rel.visits.sc, y=y_partial_weigh_inv, color= Plant.sp)) +
+ FigureS5<-ggplot(m2@frame,  aes(x=m2@frame$pollspsperplant.sc, y=y_partial_weigh_inv, color= Plant.sp)) +
    geom_point(size=2.5, shape=21,color = "black", aes(fill=factor(Plant.sp))) +
    stat_smooth(method=glm,  method.args = list(family = "binomial"), size=1, se=TRUE, color = "black", alpha=0.4) +
-  xlab("Relative number of visits") +
+   xlab("Pollinator richness") +
    ylab("Fruit set") + theme_bw()  + theme (legend.position= "bottom") +
@@
    scale_fill_discrete(name="Plant species") +  theme(legend.text = element_text(size = 14, face = "italic"), legend.title = element_text(size=15, face = "bold"), legend.direction = "vertical") + guides(fill=guide_legend(ncol=4))
+# #
 #
-
-#This relationship is largely driven by one single point species
-
-#redo analysis removing one plant species with large number of visits
-
-f2.sub<-subset(f2, f2$rel.visits.sc<4)
-
-m2b<-glmer(tot.fruitset ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2.sub, REML=TRUE)
-
-summary(m2b) #This relationship is largely driven by one single point species so we show results remving one species
-
-# extract estimates and st errors to present in table
-coefs.m2b <- data.frame(coef(summary(m2b)))
-#coefs.m2
-TableS5<-round(coefs.m2b[,1:3],digits=2)
-rownames(TableS5)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Centrality", "Plant niche overlap")
-#at the end of the paper
+# 
+# #This relationship is largely driven by one single point species 
+# 
+# #redo analysis removing one plant species with large number of visits
+# 
+# f2.sub<-subset(f2, f2$rel.visits.sc<4)
+# 
+# m2b<-glmer(tot.fruitset ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2.sub, REML=TRUE)
+#  
+# summary(m2b) #This relationship is largely driven by one single point species so we show results remving one species
+# 
+# # extract estimates and st errors to present in table
+# coefs.m2b <- data.frame(coef(summary(m2b)))
+# #coefs.m2
+# TableS5<-round(coefs.m2b[,1:3],digits=2)
+# rownames(TableS5)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Centrality", "Plant niche overlap")
+# #at the end of the paper
+#
 
@@
 s3$norm_degree<-outsp.pl.site$norm_degree[match(s3$match, outsp.pl.site$match)]
+s3$nested_contribution<-outsp.pl.site$nested_contribution[match(s3$match, outsp.pl.site$match)]
 s3$weigh_closeness<-outsp.pl.site$weigh_closeness[match(s3$match, outsp.pl.site$match)]
@@
 s3$weigh_closeness.sc<-scale(s3$weigh_closeness, center = T, scale = T)
+s3$nested_contribution.sc<-scale(s3$nested_contribution, center = T, scale = T)
 s3$niche.overlap.sc<-scale(s3$niche.overlap, center = T, scale = T)
@@
 
-m0.seed<-glmer(mean.seedn.sc ~  1  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3, REML=FALSE)
+s3.na<-na.omit(s3[,c(1:2,5:6,20:22, 24, 30)])
+
+m0.seed<-glmer(mean.seedn.sc ~  1  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3.na, REML=FALSE)
 summary(m0.seed)
 
-m1.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3, REML=FALSE)
+m1.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3.na, REML=FALSE)
 
@@
 
-m2.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3, REML=FALSE)
+m2.seed<-glmer(mean.seedn.sc ~  nested_contribution.sc + niche.overlap.sc  + pollspsperplant.sc  + rel.visits.sc +  (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3.na, REML=FALSE)
 summary(m2.seed)
@@
 AICtab(m0.seed, m1.seed, m2.seed) #m2 is best
+
+stats::anova(m0,m1,m2)
 
@@
 
-m0.seed.w<-glmer(mean.seedw ~  1  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3)
+m0.seed.w<-glmer(mean.seedw ~  1  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3.na)
 
@@
 
-m1.seed.w<-glmer(mean.seedw ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3)
+m1.seed.w<-glmer(mean.seedw ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3.na)
 
@@
 
-m2.seed.w<-glmer(mean.seedw ~  pollspsperplant.sc + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3)
+m2.seed.w<-glmer(mean.seedw ~ nested_contribution.sc + niche.overlap.sc  + pollspsperplant.sc + rel.visits.sc +  (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3.na)
 
@@
 #FRUIT WEIGHT
-m0.fruit.w<-glmer(mean.fruitweight ~  1  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3, REML=FALSE)
+m0.fruit.w<-glmer(mean.fruitweight ~  1  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3.na, REML=FALSE)
 
@@
 
-m1.fruit.w<-glmer(mean.fruitweight ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3, REML=FALSE)
+m1.fruit.w<-glmer(mean.fruitweight ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3.na, REML=FALSE)
 
@@
 
-m2.fruit.w<-glmer(mean.fruitweight ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3, REML=FALSE)
+m2.fruit.w<-glmer(mean.fruitweight ~  nested_contribution.sc + niche.overlap.sc  +pollspsperplant.sc  + rel.visits.sc +  (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3.na, REML=FALSE)
 
@@
 
-m0.fruit.net<-glmmTMB(mean.fruitset ~  1, family="beta_family", data=f.agg)
+f.agg.na<-na.omit(f.agg[, c(1, 7:12)])
+
+m0.fruit.net<-glmmTMB(mean.fruitset ~  1, family="beta_family", data=f.agg.na)
 
@@
 
-m1.fruit.net<-glmmTMB(mean.fruitset ~  species.poll.sc + tot.visits.sc, family="beta_family", data=f.agg)
+m1.fruit.net<-glmmTMB(mean.fruitset ~  species.poll.sc + tot.visits.sc, family="beta_family", data=f.agg.na)
 
@@
 
-m2.fruit.net<-glmmTMB(mean.fruitset ~  species.poll.sc + tot.visits.sc + functional.comp.poll.sc + nodf.song.sc  , family="beta_family", data=f.agg)
+m2.fruit.net<-glmmTMB(mean.fruitset ~  species.poll.sc + tot.visits.sc + functional.comp.poll.sc + nodf.song.sc  , family="beta_family", data=f.agg.na)
 
@@
 
+s.comm.na<-s.comm[, c(1, 7:14)]
+
 #NUMBER OF SEEDS PER FRUIT
 m0.seed.net <- lm(mean.seedset ~  1,
-    data=s.comm,family="gaussian")
+    data=s.comm.na,family="gaussian")
 
@@
 m1.seed.net <- lm(mean.seedset ~  species.poll.sc + tot.visits.sc,
-    data=s.comm,family="gaussian")
+    data=s.comm.na,family="gaussian")
 
@@
 
-m2.seed.net <- lm(mean.seedset ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, data=s.comm,family="gaussian")
+m2.seed.net <- lm(mean.seedset ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, data=s.comm.na,family="gaussian")
 
@@
 AICtab(m0.seed.net, m1.seed.net, m2.seed.net)#both models are equally good
+
+stats::anova(m0.seed.net, m1.seed.net, m2.seed.net)
 
@@
 #FRUIT WEIGHT
-m0.fruitw.net<-lm(mean.fruitweight ~  1, family="gaussian", data=s.comm)
+m0.fruitw.net<-lm(mean.fruitweight ~  1, family="gaussian", data=s.comm.na)
 
@@
 
-m1.fruitw.net<-lm(mean.fruitweight ~  species.poll.sc + tot.visits.sc, family="gaussian", data=s.comm)
+m1.fruitw.net<-lm(mean.fruitweight ~  species.poll.sc + tot.visits.sc, family="gaussian", data=s.comm.na)
 
@@
 
-m2.fruitw.net<-lm(mean.fruitweight ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="gaussian", data=s.comm)
+m2.fruitw.net<-lm(mean.fruitweight ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="gaussian", data=s.comm.na)
 
@@
 
-m0.seedw.net<-glm(mean.seedweight ~  1, family="gaussian", data=s.comm)
+m0.seedw.net<-glm(mean.seedweight ~  1, family="gaussian", data=s.comm.na)
 
@@
 
-m1.seedw.net<-glm(mean.seedweight ~  species.poll.sc + tot.visits.sc, family="gaussian", data=s.comm)
+m1.seedw.net<-glm(mean.seedweight ~  species.poll.sc + tot.visits.sc, family="gaussian", data=s.comm.na)
 
@@
 
-m2.seedw.net<-glm(mean.seedweight ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="gaussian", data=s.comm)
+m2.seedw.net<-glm(mean.seedweight ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc, family="gaussian", data=s.comm.na)
 

### 2020-04-28 scripts/network analysis.R

@@ -26,12 +26,12 @@ out.site <- data.frame(Site_id = NA,
                        functional.comp.poll=NA, functional.comp.plant=NA, 
                        nodf.song=NA, nodf.song2=NA)
 
-outsp.site <- data.frame(Site_id = NA, species=NA,  norm_degree = NA,
-                         weigh_closeness=NA, d=NA)
+outsp.site <- data.frame(Site_id = NA, species=NA,  norm_degree = NA, nested.rank=NA, strength =NA,
+                         weigh_closeness=NA, d=NA, nested_contribution=NA)
 
 
-outsp.pl.site <- data.frame(Site_id = NA, species=NA,  norm_degree = NA,
-                            weigh_closeness=NA, d=NA)
+outsp.pl.site <- data.frame(Site_id = NA, species=NA,  norm_degree = NA, nested.rank=NA,strength =NA,
+                            weigh_closeness=NA, d=NA, nested_contribution=NA)
 
 
 
@@ -46,6 +46,7 @@ for(i in 1:length(sites)){
   
    #p1<-plotweb(web)
   spntw <- try(specieslevel(web), TRUE)
+ 
   ntw <- networklevel(web)
   if(isTRUE(class(spntw)=="try-error")) {next} 
   
@@ -54,6 +55,8 @@ for(i in 1:length(sites)){
   #remove all columns and rows with all values=0
   web3 <- web[, colSums(web != 0) > 0] 
   web4 <- web3[rowSums(web3 > 0) != 0, ]
+  
+  nestedcontr<-nestedcontribution(web4, nsimul=99)
   
    NODF <- nestedness_NODF(web4) # this calculates the raw value of NODF as in Song
     if(i %in% c(1,2,4, 5,6,7,8, 10,11,12,14, 15,16)){ #For sites wchich don't comply, use Song. 
@@ -82,17 +85,23 @@ for(i in 1:length(sites)){
  
   outsp.site[n2+seq(nrow(spntw$`higher level`)),1] <- as.character(sites[i])
   outsp.site[n2+seq(nrow(spntw$`higher level`)),2] <- try(as.character(rownames(spntw$`higher level`)), TRUE)
-  outsp.site[n2+seq(nrow(spntw$`higher level`)),3:5] <- try(c(spntw$`higher level`[2], 
+  outsp.site[n2+seq(nrow(spntw$`higher level`)),3:7] <- try(c(spntw$`higher level`[2], 
+                                                              spntw$`higher level`[5],
[…]

### 2020-04-30 Network_structure_and_function.Rmd
changes to include contribution to nestedness

@@
 S1).
-Sites were located within similar elevations (ranging from 50 to 150 m a.s.l.), similar habitat and soil types, and presented similar plant composition (plant mean Sørensen beta-diversity among sites = `r round(d.betadiv, 2)`), reducing potential confounding factors.
+Sites were located within similar elevations (ranging from 50 to 150 m a.s.l.), and similar habitat and soil types, reducing potential confounding factors.
+Similarity in plant composition between sites was `r round(d.betadiv, 2)` (plant mean Sørensen beta-diversity).
 We surveyed 16 Mediterranean woodland patches with an average distance of 7 km between them (min= 3 km, max= 46.5 km).
@@
 
-  To evaluate differences in network structure between communities, we constructed quantitative plant-pollinator interaction networks by pooling the data for the 7 rounds of sampling.
+  To evaluate differences in network structure between communities, we constructed plant-pollinator interaction networks by pooling the data for the 7 rounds of sampling.
 We thus obtained one interaction network per site, representing the number of individuals of different pollinator species recorded visiting each different plant species.
@@
 At the species level, we focused on attributes defining the position of a focal plant species within the larger community.
-As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap in terms of pollinators between a focal plant species and each of the other plant species in the community, which estimates the potential indirect interactions between plant species through shared resources (in this case pollinators) and the potential for increased heterospecific pollen deposition [@Arceo-Gomez2019], and (ii) centrality, which depicts the importance of the role played by a plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness.
- Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the Morisita overlap index, a measure of similarity between two sets of data [@Zhang2016].
-As a measure of centrality, we used weighted closeness centrality, which represents the number of shortest paths going through a focal plant based on a unipartite projection of the bipartite plant-pollinator network using a weighted representation of the network [@Dormann2009].
-With this method, links between plant species represent shared pollinator species.
+As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap in terms of pollinators between a focal plant species and each of the other plant species in the community, and (ii) the contribution to nestedness of each individual plant species.
+Niche overlap estimates the potential indirect interactions between plant species through shared resources (in this case pollinators) and the potential for increased heterospecific pollen deposition [@Arceo-Gomez2019].
+We calculated it as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the Morisita overlap index, a measure of similarity between two sets of data [@Zhang2016].
+A plant species' contribution to nestedness is calculated by comparing the nestedness observed in a given community to that generated by randomizing the interactions in which a focal species is involved.
+Species that show important contributions to overall nestedness will have values >0, while species that do not contribute to overall nestedness wil show values <0 [@Saavedra2011].
 
@@
 Visitation rate was calculated as the total number of visits received by a plant species divided by the average number of flowers of that species found in the 10 2x2 m quadrats per transect.
-In turn, model 2 added the two network attributes calculated at the species level: average plant niche overlap and centrality.
+In turn, model 2 added the two network attributes calculated at the species level: average plant niche overlap and contribution to nestedness.
 For both models, we included plant species identity nested within site and site as random effects to account for multiple individuals of the same plant species measured at each site.
@@
 
-m0<-glmer(tot.fruitset ~ 1 + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2, REML=FALSE)
+f2.na<-na.omit(f2[, c(1,13:14,25:28)]) #omit nas so analyses are done with exact same dataset
+
+m0<-glmer(tot.fruitset ~ 1 + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2.na, REML=FALSE)
 summary(m0)
 
-m1<-glmer(tot.fruitset ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2, REML=FALSE)
+m1<-glmer(tot.fruitset ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2.na, REML=FALSE)
 summary(m1)
@@
 
-m2<-glmer(tot.fruitset ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2, REML=FALSE)
+m2<-glmer(tot.fruitset ~ pollspsperplant.sc + rel.visits.sc  + niche.overlap.sc + nested_contribution.sc +   (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2.na, REML=FALSE)
 
@@
 
-AICtab(m0,m1, m2)
+AICtab(m0,m1, m2) #m2 is best model
+
+stats::anova(m0,m1,m2) #compare model parsimony, quite similar
+
+r2<-rsquared(c(m1, m2)) #check R^2 values for both models
 
@@
 
-m2<-glmer(tot.fruitset ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2, REML=TRUE)
-
+m2<-glmer(tot.fruitset ~   pollspsperplant.sc + rel.visits.sc  + niche.overlap.sc + nested_contribution.sc + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2.na, REML=TRUE)
 summary(m2)
 
-r2<-rsquared(c(m2, m1)) #check R^2 values for both models
+#Anova(m2)
 
@@
 Table1A<-round(coefs.m2[,1:3],digits=2)
-rownames(Table1A)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Centrality", "Plant niche overlap")
+rownames(Table1A)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Plant niche overlap", "Contribution to nestedness")
 #at the end of the paper
@@
 
-y_partial_weigh <- remef(m2, fix= c( "rel.visits.sc", "pollspsperplant.sc", "niche.overlap.sc"), ran = "all", inverse = F)
+y_partial_weigh <- remef(m2, fix= c("nested_contribution.sc", "rel.visits.sc", "niche.overlap.sc"), ran = "all", inverse = F)
 #With this we remove the influece of x2 and the random effects from the dependent variable
@@
 
-Figure1a<-ggplot(m2@frame,  aes(x=m2@frame$weigh_closeness.sc, y=y_partial_weigh_inv, color= Plant.sp)) +    
+Figure1a<-ggplot(m2@frame,  aes(x=m2@frame$pollspsperplant.sc, y=y_partial_weigh_inv, color= Plant.sp)) +    
   geom_point(size=2.5, shape=21,color = "black", aes(fill=factor(Plant.sp))) + 
   stat_smooth(method=glm,  method.args = list(family = "binomial"), size=1, se=TRUE, color = "black", alpha=0.4) + 
-  xlab("Centrality") +      
+  xlab("Pollinator richness") +      
   ylab("Fruit set") + theme_bw()  + theme (legend.position= "bottom") +
@@
 
-y_partial_weigh2 <- remef(m2, fix= c( "weigh_closeness.sc", "pollspsperplant.sc", "niche.overlap.sc"), ran = "all", inverse = F)
+y_partial_weigh2 <- remef(m2, fix= c("pollspsperplant.sc", "rel.visits.sc", "niche.overlap.sc"), ran = "all", inverse = F)
 #With this we remove the influece of x2 and the random effects from the dependent variable
@@
 
-FigureS5<-ggplot(m2@frame,  aes(x=m2@frame$rel.visits.sc, y=y_partial_weigh_inv, color= Plant.sp)) +
+Figure1b<-ggplot(m2@frame,  aes(x=m2@frame$nested_contribution.sc, y=y_partial_weigh_inv2, color= Plant.sp)) +    
   geom_point(size=2.5, shape=21,color = "black", aes(fill=factor(Plant.sp))) + 
   stat_smooth(method=glm,  method.args = list(family = "binomial"), size=1, se=TRUE, color = "black", alpha=0.4) + 
-  xlab("Relative number of visits") +
+  xlab("Contribution to nestedness") +      
   ylab("Fruit set") + theme_bw()  + theme (legend.position= "bottom") +
@@
   scale_fill_discrete(name="Plant species") +  theme(legend.text = element_text(size = 14, face = "italic"), legend.title = element_text(size=15, face = "bold"), legend.direction = "vertical") + guides(fill=guide_legend(ncol=4))
-#
-
-#This relationship is largely driven by one single point species
-
-#redo analysis removing one plant species with large number of visits
-
-f2.sub<-subset(f2, f2$rel.visits.sc<4)
-
-m2b<-glmer(tot.fruitset ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2.sub, REML=TRUE)
-
-summary(m2b) #This relationship is largely driven by one single point species so we show results remving one species
-
-# extract estimates and st errors to present in table
-coefs.m2b <- data.frame(coef(summary(m2b)))
-#coefs.m2
-TableS5<-round(coefs.m2b[,1:3],digits=2)
-rownames(TableS5)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Centrality", "Plant niche overlap")
-#at the end of the paper
-
-```
-
-At the species level, in the case of fruit set, our results showed that model 2 had the best fit to our data (lowest AIC value), and fixed  effects explained `r round(r2$Marginal[1], 2)*100`% of the variability observed (conditional R^2=`r round(r2$Conditional[1], 2)*100`%).
-We found a positive relationship between fruit set, visitation rate, and a network structure metric, the centrality of a focal plant within the overall network (Table 1, Fig.
-1A, Fig.
-S4).
-However, in the case of the relative number of visits a single point seemed to be driving the relationship and removing this single point lead to a decrease in the importance of this variable (Fig.
-S5, Table S5).
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
-
-##seed set
-
-s3$functional.comp.poll<-out.site$functional.comp.poll[match(s3$Site_ID, out.site$Site_id)]
-s3$functional.comp.pl<-out.site$functional.comp.pl[match(s3$Site_ID, out.site$Site_id)]
-s3$nodf.song<-out.site$nodf.song[match(s3$Site_ID, out.site$Site_id)]
-s3$species.poll<-out.site$species.poll[match(s3$Site_ID, out.site$Site_id)]
-
-#also match with plant species level network data
-s3$match<-paste(s3$Site_ID, s3$Plant.sp)
-outsp.pl.site$match<-paste(outsp.pl.site$Site_id, outsp.pl.site$species)
-
-s3$norm_degree<-outsp.pl.site$norm_degree[match(s3$match, outsp.pl.site$match)]
-s3$weigh_closeness<-outsp.pl.site$weigh_closeness[match(s3$match, outsp.pl.site$match)]
-s3$niche.overlap<-out.niche.agg$mean.niche.over[match(s3$match, out.niche.agg$j)]
-
-s3$rel.visits<-d.vis$rel.visits[match(s3$match, d.vis$j)]
-s3$rel.visits[is.na(s3$rel.visits)]<-0
-
-s3$tot.visits<-d.vis$tot.visits[match(s3$match, d.vis$j)]
-s3$tot.visits[is.na(s3$tot.visits)]<-0
-
-s3$pollspsperplant<-out2$poll.sps[match(s3$match, out2$match)]
-
-#scale all variables used
-
-s3$norm_degree.sc<-scale(s3$norm_degree, center = T, scale = T)
-s3$weigh_closeness.sc<-scale(s3$weigh_closeness, center = T, scale = T)
-s3$niche.overlap.sc<-scale(s3$niche.overlap, center = T, scale = T)
-s3$pollspsperplant.sc<-scale(s3$pollspsperplant, center = T, scale = T)
-s3$rel.visits.sc<-scale(s3$rel.visits, center = T, scale = T)
-s3$tot.visits.sc<-scale(s3$tot.visits, center = T, scale = T)
-
-s3$mean.seedn.sc<-scale(s3$mean.seedn, center = T, scale = T)
-
-#correlation between reproduction variables
-
- # cor(s3[,4:6], use = "everything",
- #     method = "pearson")
-
-```
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
-#fit three models
-
-s3$seedcomb<-s3$mean.seedn*s3$mean.seedw
-s3$seedcomb.sc<-scale(s3$seedcomb, center = T, scale = T)
-
-m0.seed<-glmer(mean.seedn.sc ~  1  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3, REML=FALSE)
-summary(m0.seed)
-
-m1.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3, REML=FALSE)
-
-summary(m1.seed)
-vif(m1.seed)
-
-m2.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3, REML=FALSE)
-summary(m2.seed)
-vif(m2.seed)
-
-AICtab(m0.seed, m1.seed, m2.seed) #m2 is best
-
-m2.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3, REML=TRUE)
-summary(m2.seed)
-
-r2b<-rsquared(c(m2.seed, m1.seed)) #check R^2 values for both models
-
-#test for problems in residuals
-# res<-simulateResiduals(m2.seed)
-# plot(res, rank = TRUE)
-
-# extract estimates and st errors to present in table
-coefs.m2.seed <- data.frame(coef(summary(m2.seed)))
-#coefs.m2.seed
-Table1B<-round(coefs.m2.seed,digits=2)
-rownames(Table1B)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Centrality", "Plant niche overlap")
-
-#plot significant variables
-y_partial_norm_seed <- remef(m2.seed, fix= c("pollspsperplant.sc", "rel.visits.sc", "weigh_closeness.sc"), ran = "all")
-#With this we remove the influece of x2 and the random effects from the dependent variable
-
-Figure1b<-ggplot(m2.seed@frame,  aes(x=m2.seed@frame$niche.overlap.sc, y=y_partial_norm_seed, color= Plant.sp)) +    
-  geom_point(size=2.5, shape=21, colour="black", aes(fill=factor(Plant.sp))) + stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
-  #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
-  xlab("Niche overlap") +      
-  ylab("Number of \n seeds per fruit") + theme_bw()  + theme (legend.position= "right") +
-  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.3), face="bold")) + 
-  scale_fill_discrete(name="Plant species") +  theme(legend.text = element_text(size = 6, face = "italic"), legend.title = element_text(size=11, face = "bold"))
-
-#Figure1b
 
@@
 
-FigureS4<-plot_summs(m2, m2.seed, level=0.95, scale = TRUE, model.names = c("Fruit set", "Number of seeds"), legend.title = "Response variables", cex.axis=2)
-
-```
-
- For the average number of seeds per fruit, our results showed again that model 2 had the best fit, with fixed effects explaining `r round(r2b$Marginal[1], 2)*100`% of the variability observed in our data (conditional R^2 =`r round(r2b$Conditional[1], 2)*100`% ).
-In this case, we found a positive relationship between plant niche overlap and the number of seeds produced (Table 1B, Fig.
-1B, Fig.
+FigureS4<-plot_summs(m2, level=0.95, scale = TRUE, model.names = c("Fruit set"), legend.title = "Response variables", cex.axis=2)
+
+```
+
+At the species level, in the case of fruit set, our results showed that model 2 had the best fit to our data (lowest AIC value), and fixed  effects explained `r round(r2$Marginal[2], 2)*100`% of the variability observed (conditional R^2=`r round(r2$Conditional[2], 2)*100`%).
+We found a positive relationship between fruit set, pollinator species richness, and a network structure metric, the contribution to nestedness of a focal plant within the overall network (Table 1, Fig.
+1, Fig.
 S4).
@@
 
-#SEED WEIGHT
-
-m0.seed.w<-glmer(mean.seedw ~  1  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3)
-
-summary(m0.seed.w)
-
-m1.seed.w<-glmer(mean.seedw ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3)
-
-summary(m1.seed.w)
-
-m2.seed.w<-glmer(mean.seedw ~  pollspsperplant.sc + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3)
-
-summary(m2.seed.w)
+##seed set
+
+s3$functional.comp.poll<-out.site$functional.comp.poll[match(s3$Site_ID, out.site$Site_id)]
+s3$functional.comp.pl<-out.site$functional.comp.pl[match(s3$Site_ID, out.site$Site_id)]
+s3$nodf.song<-out.site$nodf.song[match(s3$Site_ID, out.site$Site_id)]
+s3$species.poll<-out.site$species.poll[match(s3$Site_ID, out.site$Site_id)]
+
+#also match with plant species level network data
+s3$match<-paste(s3$Site_ID, s3$Plant.sp)
+outsp.pl.site$match<-paste(outsp.pl.site$Site_id, outsp.pl.site$species)
+
+s3$nested_contribution<-outsp.pl.site$nested_contribution[match(s3$match, outsp.pl.site$match)]
+s3$niche.overlap<-out.niche.agg$mean.niche.over[match(s3$match, out.niche.agg$j)]
+
+s3$rel.visits<-d.vis$rel.visits[match(s3$match, d.vis$j)]
+s3$rel.visits[is.na(s3$rel.visits)]<-0
+
+s3$tot.visits<-d.vis$tot.visits[match(s3$match, d.vis$j)]
+s3$tot.visits[is.na(s3$tot.visits)]<-0
+
+s3$pollspsperplant<-out2$poll.sps[match(s3$match, out2$match)]
+
+#scale all variables used
+
+s3$nested_contribution.sc<-scale(s3$nested_contribution, center = T, scale = T)
+s3$niche.overlap.sc<-scale(s3$niche.overlap, center = T, scale = T)
+s3$pollspsperplant.sc<-scale(s3$pollspsperplant, center = T, scale = T)
+s3$rel.visits.sc<-scale(s3$rel.visits, center = T, scale = T)
+s3$tot.visits.sc<-scale(s3$tot.visits, center = T, scale = T)
+
+s3$mean.seedn.sc<-scale(s3$mean.seedn, center = T, scale = T)
+
+#correlation between reproduction variables
+
+ # cor(s3[,4:6], use = "everything",
+ #     method = "pearson")
+
+```
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
+#fit three models
+
+# s3$seedcomb<-s3$mean.seedn*s3$mean.seedw
+# s3$seedcomb.sc<-scale(s3$seedcomb, center = T, scale = T)
+
+s3.na<-na.omit(s3[,c(1:2,17:20,22)])
+
+m0.seed<-glmer(mean.seedn.sc ~  1  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3.na, REML=FALSE)
+summary(m0.seed)
+
+m1.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3.na, REML=FALSE)
+
+summary(m1.seed)
+vif(m1.seed)
+
+m2.seed<-glmer(mean.seedn.sc ~ pollspsperplant.sc  + rel.visits.sc +  niche.overlap.sc  + nested_contribution.sc + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3.na, REML=FALSE)
+summary(m2.seed)
+vif(m2.seed)
+
+AICtab(m0.seed, m1.seed, m2.seed) #m0 is best
+
+stats::anova(m0.seed,m1.seed,m2.seed)
+
+```
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
+
+#FRUIT WEIGHT
+
+s3.na2<-na.omit(s3[,c(1:2,6, 17:20)])
+
+m0.fruit.w<-glmer(mean.fruitweight ~  1  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3.na2, REML=FALSE)
+
+summary(m0.fruit.w)
+
+m1.fruit.w<-glmer(mean.fruitweight ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3.na2, REML=FALSE)
+
+summary(m1.fruit.w)
+
+m2.fruit.w<-glmer(mean.fruitweight ~  nested_contribution.sc + niche.overlap.sc  +pollspsperplant.sc  + rel.visits.sc +  (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3.na2, REML=FALSE)
+
+summary(m2.fruit.w)
 
@@
 
-AICtab(m0.seed.w, m1.seed.w, m2.seed.w)
+AICtab(m0.fruit.w, m1.fruit.w, m2.fruit.w)
 
@@
 
-#FRUIT WEIGHT
-m0.fruit.w<-glmer(mean.fruitweight ~  1  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3, REML=FALSE)
-
-summary(m0.fruit.w)
-
-m1.fruit.w<-glmer(mean.fruitweight ~  pollspsperplant.sc + rel.visits.sc  + (1|Plant.sp:Site_ID)+ (1|Site_ID), family="gaussian", data=s3, REML=FALSE)
-
-summary(m1.fruit.w)
-
-m2.fruit.w<-glmer(mean.fruitweight ~  pollspsperplant.sc  + rel.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=s3, REML=FALSE)
-
-summary(m2.fruit.w)
-
-#select best model based on AIC
-
-AICtab(m0.fruit.w, m1.fruit.w, m2.fruit.w)
-
-#best model is null model
-
-```
- For fruit weight, none of the models fitted showed a better fit than the null model.
+```
+For the average number of seeds per fruit at the species level as well as for fruit weight, our results showed that none of the models fitted were better than the null model explaining differences across plant species.
 
@@
 
-FigureS6A<-plot_model(m2.fruit.net, title="Fruit set")
+FigureS5A<-plot_model(m2.fruit.net, title="Fruit set")
 ```
@@
 
-FigureS6B<-plot_model(m2.seed.net, title="Number of seeds")
+FigureS5B<-plot_model(m2.seed.net, title="Number of seeds")
 ```
@@
 2, Fig.
-S6).
+S5).
 Additionally, we found a negative association between site-level pollinator richness and average fruit set (Table 2A, Fig.
 2, Fig.
-S6).
+S5).
 
@@
 #save table with results for paper
-tableS6A<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)#ch
-rownames(tableS6A)<-c("(Intercept)", "Pollinator species diversity", "Relative number of visits")#end of paper
+tableS5A<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)#ch
+rownames(tableS5A)<-c("(Intercept)", "Pollinator species diversity", "Relative number of visits")#end of paper
 
@@
 
-FigureS7 <- ggplot(s.comm,  aes(x=species.poll.sc, y= restest)) +    
+FigureS6 <- ggplot(s.comm,  aes(x=species.poll.sc, y= restest)) +    
   geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
@@
 #save table with results for paper
-tableS6B<-round(summary(m1.fruitw.net2)$coef[,1:3], digits=2)#ch
-rownames(tableS6B)<-c("(Intercept)", "Pollinator species diversity", "Relative number of visits")#end of paper
+tableS5B<-round(summary(m1.fruitw.net2)$coef[,1:3], digits=2)#ch
+rownames(tableS5B)<-c("(Intercept)", "Pollinator species diversity", "Relative number of visits")#end of paper
 
@@
 
-FigureS8 <- ggplot(s.comm2,  aes(x=species.poll.sc, y= restestb)) +    
+FigureS7 <- ggplot(s.comm2,  aes(x=species.poll.sc, y= restestb)) +    
   geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
@@
 
-FigureS6C<-plot_model(m1.fruitw.net, title="Fruit weight")
+FigureS5C<-plot_model(m1.fruitw.net, title="Fruit weight")
 
@@
 Model 1, i.e., that only including simple visitation metrics, showed an R^2  of  0.23.
-In this case, we found a positive link with site-level pollinator richness (Table S6A, Figs.
-S6-S7).
-This association was maintained even after removing a site that has a particularly large pollinator richness value (Table S6B, Fig.
-S8, Fig.
-S6).
+In this case, we found a positive link with site-level pollinator richness (Table S5A, Figs.
+S5-S6).
+This association was maintained even after removing a site that has a particularly large pollinator richness value (Table S5B, Fig.
+S7, Fig.
+S5).
 
@@
 
-When evaluating the relationship between community composition and network structure on equity in reproductive success across the different species within a community, we found that using the 50^th percentile all models were equally good (i.e.,$\Delta AIC<2$; [@Burnham2002a]), but none of the variables considered showed any strong associations (Table S8).
+When evaluating the relationship between community composition and network structure on equity in reproductive success across the different species within a community, we found that using the 50^th percentile all models were equally good (i.e.,$\Delta AIC<2$; [@Burnham2002a]), but none of the variables considered showed any strong associations (Table S6).
 In the case of the other two thresholds considered (25^th and 75^th percentiles) model 0, the null model, was the best model.
@@
 These ideas open the door to exploring the positive or negative effects of the complete pollinator community on full plant species coexistence, which may be determined by density-dependence effects [@Benadi2018].
-In our case, while fruit set is negatively related to pollinator richness, it is important to note that fruit weight shows the opposite relationship, indicating that this density-dependent effect might only be limiting fruit quantity and not fruit quality.
+In our case, while fruit set at the site level is negatively related to pollinator richness, it is important to note that fruit set at the species level and fruit weight show the opposite relationship, indicating that this density-dependent effect might only be limiting fruit quantity and not fruit quality.
 Thus, taking into account the densities of co-flowering plant species may be the next step [@Vanbergen2014].
@@
 
-knitr::kable(list(Table1A, Table1B), caption = "**Table 1**.
-Results of GLMM showing the association between simple visitation and network structure metrics and A) species-level fruit set and B) average number of seeds per fruit based on best model selected.
-Bold letters indicate variables with large effects.")
+knitr::kable(list(Table1A), caption = "**Table 1**.
+Results of GLMM showing the association between simple visitation and network structure metrics and species-level fruit.
+Bold letters indicate variables with large effects (see Figure S4 for estimate confidence intervals).")
 ```
@@
 **Figure 1**.
-Partial residual plots showing the effect of the single predictor which best explains the variability in species-level reproductive success.
-A) shows the effect of plant species centrality on the fruit set of each of the plant species considered and B) shows the effect of plant niche overlap on its average number of seeds per fruit.
+Partial residual plots showing the effect of A) pollinator species richness and B) the contribution to nestedness of each plant species on fruit set.
 Dots represent each of the individuals sampled for each species within each site.
@@
 
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=8}
-
-FigureS5
-
-```
-**Figure S5.** Scatterplot showing the effect of the relative number of visits received by a focal plant on its reproductive success.
-Relationship is largely driven by one species with a particularly large value of relative visits and removing this point leads to no effect of visitation rate.
-
 ```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=15, fig.width=8}
 
-FigureS6A
-FigureS6B
-FigureS6C
-
-```
-**Figure S6.** Forest plots showing 95% confidence intervals for all coefficients included in site-level models, A) fruit set, B) number of seeds per fruit and C) fruit and seed weight.
+FigureS5A
+FigureS5B
+FigureS5C
+
+```
+**Figure S5.** Forest plots showing 95% confidence intervals for all coefficients included in site-level models, A) fruit set, B) number of seeds per fruit and C) fruit and seed weight.
 
@@
 
-#FIGURE 4
+FigureS6
+
+```
+**Figure S6.** Partial residual plots showing the effect of pollinator richness on site-level average fruit weight. Dots represent values for each site (N=16 sites).
+
+```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=3, fig.width=10}
+
 FigureS7
-# 
-# save_plot("figures/Figure4.tiff", Figure4,
-#              base_height = 5, base_width = 10)
-```
-**Figure S7.** Partial residual plots showing the effect of pollinator richness on site-level average fruit weight. Dots represent values for each site (N=16 sites).
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=3, fig.width=10}
-
-FigureS8
-
-```
-
-**Figure S8.** Partial residual plots showing the effect of pollinator richness on site-level average fruit weight.
+
+```
+
+**Figure S7.** Partial residual plots showing the effect of pollinator richness on site-level average fruit weight.
 Here, a site with a particularly large pollinator richness value is removed to test whether it might be driving the significant relationship.
@@
 
-#coefs.m2
-TableS5<-round(coefs.m2b[,1:3],digits=2)
-rownames(TableS5)<-c("(Intercept)", "Pollinator richness", "Relative number of visits", "Centrality", "Plant niche overlap")
-
-kable(TableS5, caption="Table S5.
-Results of GLMM showing effect of simple visitation and network metrics on species-level fruit set based on best model selected as in Table 1, but removing one species point with a particularly large visitation rate which drives this relationship.")
-
+tableS5A<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)
+rownames(tableS5A)<-c("(Intercept)", "Pollinator richness", "Relative number of visits")
+
+kable(tableS5A, caption="Table S5.
+Results of GLM showing effect of simple visitation metrics on A) site-level average fruit weight based on best model selected and B) the same analysis removing one site that has a particularly large pollinator richness value to test whether this point might be driving the relationship.")
 ```
@@
 
-tableS6A<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)
-rownames(tableS6A)<-c("(Intercept)", "Pollinator richness", "Relative number of visits")
-
-kable(tableS6A, caption="Table S6.
+tableS5B<-round(summary(m1.fruitw.net2)$coef[,1:3], digits=2)
+rownames(tableS5B)<-c("(Intercept)", "Pollinator richness", "Relative number of visits")
+
+kable(tableS5B, caption="Table S5.
 Results of GLM showing effect of simple visitation metrics on A) site-level average fruit weight based on best model selected and B) the same analysis removing one site that has a particularly large pollinator richness value to test whether this point might be driving the relationship.")
@@
 
-tableS6B<-round(summary(m1.fruitw.net2)$coef[,1:3], digits=2)
-rownames(tableS6B)<-c("(Intercept)", "Pollinator richness", "Relative number of visits")
-
-kable(tableS6B, caption="Table S6.
-Results of GLM showing effect of simple visitation metrics on A) site-level average fruit weight based on best model selected and B) the same analysis removing one site that has a particularly large pollinator richness value to test whether this point might be driving the relationship.")
-```
-
-```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
-
-kable(tableS7, caption="Table S7.
+kable(tableS6, caption="Table S6.
 Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a site based on best model selected (0.50 threshold).")

### 2020-04-30 scripts/network analysis.R

@@ -16,6 +16,8 @@ d<-all_interactions
 dtrans<-subset(d, d$Out=="transect")
 dtrans<-droplevels(dtrans)
 
+
+
 ##1st create a bipartite matrix for each site MERGING ALL ROUNDS TOGETHER and extract a set of metrics at the network level
 
 sites <- unique(dtrans$Site_ID)

### 2020-04-30 Network_structure_and_function.Rmd
small error in discussion

@@
 Our results suggest that different aspects of network structure affect different dimensions of ecosystem functioning.
-Specifically, we find that the centrality of a plant species within a community has a positive association with its fruit set, indicating that from a plant's perspective, being connected to other plant species via shared pollinators has a positive outcome (e.g.
+Specifically, we find that the contribution to nestedness of a plant species within a community has a positive association with its fruit set.
+From a plant's perspective, this indicates that being connected to other plant species via shared pollinators has a positive outcome (e.g.
 by ensuring a stable pollinator supply through time) rather than a negative one (e.g.
